### 2017-06-25 old-notes/lens.tex
Add some mostly broken tex'd notes from a long time ago

\documentclass[11pt,a4paper]{amsart}
\usepackage[utf8]{inputenc}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\let\amssquare\square
\usepackage{mathtools}
\usepackage{stmaryrd}
\usepackage{tensor}
\usepackage[mathscr]{eucal}
\usepackage{marvosym}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}

\usepackage{tikz-cd}
\usetikzlibrary{cd}
\usetikzlibrary{arrows}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem*{theoremstar}{Theorem}
\newtheorem{fact}[theorem]{Fact}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{convention}[theorem]{Convention}
\newtheorem{construction}[theorem]{Construction}
\newtheorem{example}[theorem]{Example}
\newtheorem{examples}[theorem]{Examples}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{idea}[theorem]{Idea}
\newtheorem{question}[theorem]{Question}

\newcommand{\id}{\mathrm{id}}

\newcommand{\C}{\mathscr{C}}
\newcommand{\homC}{\underline{\C}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\E}{\mathscr{E}}
\newcommand{\M}{\mathscr{M}}
\newcommand{\N}{\mathscr{N}}

\newcommand{\Pastro}{\mathrm{Pastro}}

\newcommand{\Set}{\mathbf{Set}}
\newcommand{\Cat}{\mathbf{Cat}}
\newcommand{\Prof}{\mathbf{Prof}}
\newcommand{\MonCat}{\mathbf{MonCat}}
\newcommand{\LaxMonCat}{\mathbf{LaxMonCat}}

\newcommand{\Act}{\mathbf{Act}}
\newcommand{\Lens}{\mathbf{Lens}}
\newcommand{\Hask}{\mathbf{Hask}}
\newcommand{\Endo}{\mathbf{Endo}}
\newcommand{\Strong}{\mathbf{Strong}}
\newcommand{\Tamb}{\mathbf{Tamb}}
\newcommand{\Point}{\mathbf{Point}}
\newcommand{\CoPoint}{\mathbf{CoPoint}}
\newcommand{\Traversable}{\mathbf{Traversable}}

\newcommand{\op}{\mathrm{op}}
\newcommand{\ob}{\mathrm{ob}\,}

\newcommand{\fget}{\mathrm{get}}
\newcommand{\fput}{\mathrm{put}}
\newcommand{\fmodify}{\mathrm{modify}}

\newcommand{\todo}[1]{\textcolor{red}{\small #1}}

\newcommand{\isoto}{\xrightarrow{
   \,\smash{\raisebox{-0.65ex}{\ensuremath{\scriptstyle\sim}}}\,}}

\title{Profunctor Lenses}
\author{Mitchell Riley}
\begin{document}
\maketitle

\section{Introduction}

A good introduction would include:

Motivation for Lenses

Motivation for van Laarhoven Lenses

Motivation for Profunctor Lenses

\subsection{Laws}
Whatever formulation of standard lenses is used, there are some laws that are expected to hold. When we work in $\Set$ (or $\Hask$), the laws are typically given as follows.

Given:
\begin{align*}
\fget &: \Lens(a, b) \times a \to b \\
\fput &: \Lens(a, b) \times b \times a \to a
\end{align*}
we have that
\begin{align*}
\fget(l, \fput(l, b, a))   &= b \\
\fput(l, \fget(l, a), a)   &= a \\
\fput(l, b', \fput(l, b, a)) &= \fput(l, b', a)
\end{align*}

To express these laws in a general category with products, however, we must rewrite these in a ``pointfree'' style.

Given:
\begin{align*}
\fget &: \Lens(a, b) \to \C(a, b) \\
\fmodify &: \Lens(a, b) \times \C(b, b) \to \C(a, a)
\end{align*}
we have that
\begin{align*}
\fget(l) \circ \fmodify(l, f) &= f \circ \fget(l) \\
\fmodify(l, \id_b) &= \id_a \\
\fmodify(l, f) \circ \fmodify(l, g) &= \fmodify(l, f \circ g)
\end{align*}
We will refer to these as the get/modify laws.

Similarly, the laws for prisms are typically stated as
\todo{todo}

\subsection{Notation}

We use $\homC(a,b)$ to denote the internal hom of a cartesian closed category $\C$.

\section{Lenses}

\subsection{Monoidal actions}

\begin{definition}
An \emph{action} of a monoidal category $(\M, \otimes, 1)$ on a category $\C$ is a functor $\cdot : \M \times \C \to \C$ such that there are natural isomorphisms $m \cdot (n \cdot x) \isoto (m \otimes n) \cdot x$ and $1 \cdot x \isoto x$ for any $m, n \in \M$ and $x \in \C$. These isomorphism must satisfy the expected associativity and unit axioms. We will leave these isomorphisms implicit to reduce the amount of noise in our diagram. \todo{draw diagrams?}

Equivalently, an action of a monoidal category is a strong monoidal functor $\M \to [\C, \C]$, where $[\C, \C]$ is equipped with the monoidal structure $([\C, \C], \circ, \id_\C)$.
\end{definition}

Examples abound: 
\begin{itemize} 
\item Any monoidal category acts on itself via left multiplication. 
\item Any subcategory $\M \subset [\C, \C]$ that is closed under composition is a monoidal category, which acts on $\C$ simply by functor application.
\item If $\C$ is equipped with an action of $\M$, then any functor category $[\D, \C]$ has an action of $\M$ computed pointwise.
\end{itemize}

We will also be interested in actions that are \emph{not} functorial in $\C$:

\begin{definition}
A \emph{dodgy monoidal action} of $\M$ on $\C$ is a functor $\cdot : \M \times \ob \C \to \C$, such that the same conditions hold as above. Here, $\ob \C$ is the category with the same objects as $\C$ but only identity morphisms.
\end{definition}

Most of what follows is still true for dodgy monoidal actions. \todo{But I am yet to check carefully which parts fail}

\subsection{Lenses}

\begin{definition}
Let $\C$ be a category equipped with an action of the monoidal category $(\M, \otimes, 1)$. The \emph{category of lenses $\Lens_\C(\M)$} has objects the objects of $\C$, and morphisms $a$ to $b$ given by pairs $(m \in \M, a \isoto m \cdot b)$, where the second component is an isomorphism. However, we identify lenses that can be connected by an isomorphism in $\M$: $(m \in \M, l : a \isoto m \cdot b)$ is identified with $(m' \in \M, l' : a \isoto m' \cdot b)$ iff there exists an isomorphism $\alpha : m \isoto m'$ such that $l' = (\alpha\cdot b)l$. To save on notation, we will simply write $l : a \isoto m \cdot b$ for a representative of a lens $l$.

The identity lens is simply $\id_a : a \isoto 1 \cdot a$, and the composition of two lenses $a \isoto m \cdot b$ and $b \isoto n \cdot c$ is given by
\begin{align*}
a \isoto m \cdot b \isoto m \cdot (n \cdot c) \isoto (m \otimes n) \cdot c
\end{align*}
It is not difficult to check that this composition is well defined.
\end{definition}
\todo{TODO: Consider flipping the direction of a lens to avoid op later?}

We may consider the slice category $\Act(\C) := \MonCat/[\C, \C]$ of monoidal actions on $\C$, where $\MonCat$ is the category of monoidal categories and strong monoidal functors. For any map $F : \M \to \N$ in $\Act(\C)$, we have a functor $\Lens_\C(\M) \to \Lens_\C(\N)$ which sends any lens $a \isoto m \cdot b$ to $a \isoto Fm \cdot b$. Here, the map is identical: $m \cdot b = Fm \cdot b$.  In this way, $\Lens_\C$ forms a functor $\Act(\C) \to \Cat$.

Unfortunately, the above definition of a lens is difficult to work with, both categoricaly and programmatically. Instead, we embed $\Lens_\C(\M)(a, b)$ inside $\int^{m \in M} \C(a, m\cdot b) \times \C(m\cdot b, a)$, and work with the latter.

\begin{lemma}
The canonical map $I : \Lens_\C(\M)(a, b) \to \int^{m \in M} \C(a, m\cdot b) \times \C(m\cdot b, a)$ that sends $l : a \isoto m \cdot b$ to $[(l, l^{-1})]$ is injective.
\end{lemma}
\begin{proof}

\end{proof}

We now wish to characterise the elements of $\int^{m \in M} \C(a, m\cdot b) \times \C(m\cdot b, a)$ that correspond to lenses.

\begin{proposition}\label{characterise-lenses-in-coend}
An element $[(l, r)] \in \int^{m \in M} \C(a, m\cdot b) \times \C(m\cdot b, a)$ corresponds to a lens iff $rl = \id_A$ and $[lr] = [\id_{m\cdot b}]$ as elements of $\int^{m\in \M} \C(m \cdot b, m \cdot b)$, for some $m \in \M$.
\end{proposition}
\begin{proof}
If an element corresponds to a lens, there is a representative $(l, r)$ such that $rl = \id_a$ and $lr = \id_{m\cdot b}$, so certainly $[lr] = [\id_{m\cdot b}]$ in $\int^{m\in \M} \C(m \cdot b, m \cdot b)$.

\todo{This is wrong} Conversely, suppose $rl = \id_A$ and $[lr] = [\id_{m\cdot b}]$ in $\int^{m\in \M} \C(m \cdot b, m \cdot b)$. The coend relations imply that there exist $p : m \cdot b \to n \cdot b$ and $q : n \cdot b \to m \cdot b$ such that $plrq = \id_{n\cdot b}$ and $qp = \id_{m\cdot b}$.

The same relations hold in $\int^{m \in M} \C(a, m\cdot b) \times \C(m\cdot b, a)$, so $[(l, r)] = [(pl, rq)]$. Now $plrq = \id_{n\cdot b}$ on the nose, and $rqpl = rl = \id_a$, so $[(l, r)]$ represents the lens $pl : a \isoto n \cdot b$.
\end{proof}

\section{Examples}

Viewing lenses as a subset of $\int^{m \in M} \C(a, m\cdot b) \times \C(m\cdot b, a)$ allows for some more practical descriptions of lenses for particular choices of $\M$.

\subsection{Isos}

Let $\M = \mathbf{1}$. Then the set of potential lenses between $a, b \in \C$ is 
\begin{align*}
\int^{m \in \mathbf{1}} \C(a, m \cdot b) \times \C(m \cdot b, a)
&\cong \C(a, 1 \cdot b) \times \C(1 \cdot b, a) \\
&\cong \C(a, b) \times \C(b, a)
\end{align*}

\subsection{Lenses}

Suppose $\C$ has finite products, and let $\M = (\C, \times, 1)$, then
\begin{align*}
(\Pastro_\C(\times)E_b)(a,a) 
&\cong \int^{m \in \C} \C(a, m \times b) \times \C(m \times b, a) \\
&\cong \int^{m \in \C} \C(a, m) \times \C(a, b) \times \C(m \times b, a) \\
&\cong  \C(a, b) \times \C(a \times b, a)
\end{align*}
This is the traditional getter/setter form of lenses.

\begin{proposition}
An element of $\C(a, b) \times \C(a \times b, a)$ corresponds to a lens iff it satisfies the get/modify lens laws.
\end{proposition}
\begin{proof}
\todo{todo}
\end{proof}

\subsection{Prisms}

Suppose $\C$ has finite coproducts, and let $\M = (\C, \sqcup, 0)$, then
\begin{align*}
(\Pastro_\C(\sqcup)E_b)(a,a) 
&\cong \int^{m \in \C} \C(a, m \sqcup b) \times \C(m \sqcup b, a) \\
&\cong \int^{m \in \C} \C(a, m \sqcup b) \times \C(m, a) \times \C(b, a) \\
&\cong \C(a, a \sqcup b) \times \C(b, a)
\end{align*}

\todo{Show that the laws follow from our law}

\subsection{Setters}
To define Setters, we must first define what it means for a functor to be \emph{strong}.

\begin{definition}
\todo{The extra generality may not be necessary}
Suppose $\C$ is equipped with an action of $\M$. A \emph{strength} for a functor $F : \C \to \C$ is a natural transformation
\begin{align*}
s_{m,a} : m \cdot F a \to F(m \cdot a)
\end{align*}
such that both
\[
\begin{tikzcd}
m \cdot n \cdot Fa \ar[r, "s_{n,a}"] \ar[dr, "s_{m\otimes n, a}" below left]  & m \cdot F(n\cdot a) \ar[d, "s_{m, n\cdot a}" right] \\
& F(m \cdot n \cdot a)
\end{tikzcd}
\]
and
\[
\begin{tikzcd}
1 \cdot F a \ar[r, "s_{1,a}"] \ar[dr, "\cong" below left]  & F(1 \cdot a) \ar[d, "\cong" right] \\
& F a
\end{tikzcd}
\]
commute.
\end{definition}

\begin{definition}
There is a category $\Strong_\C(\M)$ of functors equipped with strengths, where the morphisms are natural transformations that respect the extra structure. There is an evident forgetful functor $U : \Strong_\C(\M) \to [\C, \C]$.
\end{definition}

The composition of two strong functors itself has a canonical strength, given by the composite
\begin{align*}
m \cdot FG a \xrightarrow{s_{m, Ga}} F(m \cdot G a) \xrightarrow{Fs_{m,a}} FG (m \cdot a)
\end{align*}

In this way, $\Strong_\C(\M)$ is also a monoidal category under composition. This category also acts on $\C$, via the action of the underlying functors.

Now, returning to Setters, suppose $\C$ is cartesian closed, and let $\M = \Strong_\C(\times)$. First, a lemma:

\begin{lemma}
$\C(a, Fb) \cong \Strong_\C(\times)(a \times \homC(b, -), F)$
\end{lemma}
\begin{proof}
Given a $f \in \C(a, Fb)$, let $\eta$ be the natural transformation with components
\begin{align*}
a \times \homC(b, c) \xrightarrow{f \times \id} Fb \times \homC(b, c) \xrightarrow{s_{\homC(b, c), b}}  F(b \times \homC(b, c)) \xrightarrow{F\epsilon} Fc
\end{align*}
where $s$ is the strength for $F$ and $\epsilon$ is the evaluation map.

Conversely, given an $\eta$, the component at $b$ is a function $g : a \times \homC(b, b) \to Fb$; we recover $f$ as $f(a) = g(a, \id_b)$.

Again, it is routine to check these are inverses.
\end{proof}

This is a generalisation of Proposition 2.2 in \cite{MR3482285}, which only considered functors $\Set \to \Set$ (all of which are strong).

Now, the set of (possibly invalid) lenses with respect to this action is:
\begin{align*}
\int^{F \in \Strong_\C(\times)} \C(a, F b) \times \C(F b, a) 
&\cong \int^{F} \Strong_\C(\times)(a \times \homC(b, -), F) \times \C(F b, a) \\ 
&\cong \C(a \times \homC(b, b), a) \\
&\cong \C(\homC(b, b), \homC(a, a))
\end{align*}

\subsection{Views and Reviews}

Here we make use of dodgy monoidal actions. Let $\M=\Point(\C)$ be the category of \emph{pointed assignments}: functors $
F : \ob C \to C$ equipped with natural transformations $\epsilon : 1 \to F$.

As in earlier sections, we must charactarise $\C(a, Fb)$ as the set of natural transformation from some assignment to $F$. Let $C_{a,b}$ be the pointed assignment such that $C_{a,b}(b) = a \sqcup b$ and $C_{a,b}(c) = c$ for all $c \neq b$.

\begin{lemma}
$\C(a, Fb) \cong \Point(\C)(C_{a,b}, F)$
\end{lemma}
\begin{proof}
\todo{boring}
\end{proof}

Then:

\begin{align*}
\int^{F \in \Point(\C)} \C(a, F b) \times \C(F b, a) 
&\cong \int^{F} \Point(\C)(C_{a,b}, F) \times \C(F b, a) \\ 
&\cong \C(a \sqcup b, a) \\
&\cong \C(a, a) \times \C(b, a)
\end{align*}

\section{Profunctors and Tambara Modules}

\begin{definition}
A \emph{profunctor} between $\C$ and $\D$ is a functor $\C^\op \times \D \to \Set$. We have a category $\Prof(\C, \D) := [\C^\op \times \D, \Set]$.
\end{definition}

\begin{definition}
For any $a \in \C$, define the \emph{exchange} profunctor to be $E_a := \C(-,a) \times \C(a,=)$. 
%\todo{For lack of better names} We also define the \emph{lefty} and \emph{righty} profunctors to be $L_b := \C(-, b)$ and $R_b := \C(b, =)$ respectively.
\end{definition}

\begin{definition}
Given profunctors $P \in \Prof(\C, \D)$ and $Q \in \Prof(\D,\E)$, the composite $Q \star P \in \Prof(\C, \E)$ is given by
\begin{align*}
(Q \star P)(c,e) = \int^{d \in \D} P(c,d) \times Q(d,e)
\end{align*}
In particular, for any $\C$, $\Prof(\C,\C)$ is a monoidal category with respect to $\star$. The identity for this composition is given by $\C(-,=)$. Details and proofs can be found in \cite{loregian2015co}.
\end{definition}

Any functor $F : \C \to \D$ can be turned into a profunctor in two different ways: $F_* \in \Prof(\D, \C)$ given by $F_* = \D(-,F=)$, and  $F^* \in \Prof(\C, \D)$ given by $F^* = \D(F-,=)$.

\begin{lemma}\label{procomp-downstar-is-comp}
Let $F : \C \to \D$ and $G : \D \to \E$, so that $F_* \in \Prof(\D, \C)$ and $G_* \in \Prof(\E,\D)$. Then $F_* \star G_* \cong (GF)_*$
\end{lemma}
\begin{proof}
\todo{todo}
\end{proof}

%It is also easily verified that $L_b \star R_b \cong E_b$, and $R_b \star L_b$ is the constant profunctor at $\C(b,b)$.

The following definition is a generalisation of an idea that appears in \cite{MR2425558}.

\begin{definition}
Suppose $\C$ is equipped with an action of $\M$, and let $P \in \Prof(\C, \C)$ be a profunctor. A \emph{Tambara module structure} for $P$ with respect to $\M$ is a natural family of maps:
\begin{align*}
\alpha_{a,b,m} : P(a, b) \to P(m \cdot a, m \cdot b)
\end{align*}
such that $\alpha_{a,b,1} = \id_{P(a,b)}$, and the following diagram commutes:
\[
\begin{tikzcd}
P(a,b) \ar[r, "\alpha_{a,b,m}"] \ar[dr, "\alpha_{m\otimes n, a, b}" below left] & P(m \cdot a, m \cdot b) \ar[d, "\alpha_{n, m \cdot a, m \cdot b}" right] \\
& P(n \cdot (m \cdot a), n \cdot (m \cdot b))
\end{tikzcd}
\]
\end{definition}

The identity profunctor $\C(-,=)$ has a module structure with respect to any action, as every action is functorial.

If $P \in \Prof(\C, \D)$ and $Q \in \Prof(\D,\E)$ are equipped with module structures $\alpha$ and $\beta$ respectively, there is a canonical module structure on $Q \star P$ given by
\begin{align*}
(Q \star P)(c,e) &= \int^{d \in D} P(c,d) \times Q(d,e) \\ 
&\to \int^{d \in D} P(m \cdot c, m\cdot d) \times Q(m \cdot d, m \cdot e) \\
&\to \int^{d \in D} P(m \cdot c, d) \times Q(d, m \cdot e) \\
&= (Q \star P)(m \cdot c, m \cdot e)
\end{align*}
Here, the second map is induced by the universal property of the coend: Each $P(m \cdot c, m\cdot d) \times Q(m \cdot d, m \cdot e)$ has a canonical inclusion into $\int^{d \in D} P(m \cdot c, d) \times Q(d, m \cdot e)$.

\begin{definition}
There is a category $\Tamb_\C(\M)$ of Tambara modules and natural transformations that respect the extra structure, in the sense that the diagram
\[
\begin{tikzcd}
P(a,b) \ar[r, "\alpha_{a,b,m}"] \ar[d, "l_{a,b}" left] & P(m \cdot a, m \cdot b) \ar[d, "l_{m\cdot a,m\cdot b}" right] \\
Q(a,b) \ar[r, "\alpha_{a,b,m}"] & Q(m \cdot a, m \cdot b)
\end{tikzcd}
\]
commutes.
\end{definition}

This category is monoidal with respect to $\star$ as given above. There is an evident forgetful functor $U : \Tamb_\C(\M) \to \Prof(\C, \C)$ that is strong monoidal.

\begin{definition}
Let $\mathrm{Pastro}_\C(\M) : \Prof(\C, \C) \to \Tamb_\C(\M)$ be the functor
\begin{align*}
\mathrm{Pastro}_\C(\M)(P) := \int^{m \in \M} \C(m \cdot -, =) \star P \star \C(-, m \cdot =)
\end{align*}
Or, in other words, 
\begin{align*}
\mathrm{Pastro}_\C(\M)(P)(a,b) := \int^{m \in \M} \int^{c,d \in \C} \C(a, m \cdot c) \times P(c,d) \times  \C(m \cdot d, b)
\end{align*}
The module structure $\alpha_{a,b,m} : \mathrm{Pastro}_\C(\M)(P)(a, b) \to \mathrm{Pastro}_\C(\M)(P)(m \cdot a, m \cdot b)
$ is given by the composite
\begin{align*}
\mathrm{Pastro}_\C(\M)(P)(a,b) &= \int^{n \in \M} \int^{c,d \in \C} \C(a, n \cdot c) \times P(c,d) \times  \C(n \cdot d, b) \\
&\to \int^{n \in \M} \int^{c,d \in \C} \C(m \cdot a, m \cdot (n \cdot c)) \times P(c,d) \times  \C(m \cdot (n \cdot d), m \cdot b) \\
&\cong \int^{n \in \M} \int^{c,d \in \C} \C(m \cdot a, (m \otimes n) \cdot c) \times P(c,d) \times  \C((m \otimes n) \cdot d, m \cdot b) \\
&\to \int^{n \in \M} \int^{c,d \in \C} \C(m \cdot a, n \cdot c) \times P(c,d) \times  \C(n \cdot d, m \cdot b) \\
&= \mathrm{Pastro}_\C(\M)(P)(m \cdot a, m \cdot b)
\end{align*}
where the final map is again induced by the universal property of the coend. \todo{This does not work if the action is not functorial in $\C$!!!}
\end{definition}

\begin{proposition}
$\Pastro_\C(\M)$ is left adjoint to $U$.
\end{proposition}
\begin{proof}
We prove this directly by providing natural inverse maps
\begin{align*}
\alpha : \Tamb_\C(\M)(\Pastro_\C(\M)(P), Q) \cong \Prof(\C, \C)(P, UQ) : \beta
\end{align*}
Given a natural transformation $f : \Pastro_\C(\M)(P) \to Q$, let $\alpha(f) : P \to UQ$ be the natural transformation with components
\begin{align*}
P(a,b) \xrightarrow{(id, -, id)} \C(a, 1 \cdot a) \times P(a,b) \times \C(1 \cdot b, b) \xrightarrow{f} Q(a,b)
\end{align*} 
Given a $g : P \to UQ$, let $\beta(g) : \Pastro_\C(\M)(P) \to Q$ be the natural transformation with components
\begin{align*}
\Pastro_\C(\M)(P)(a,b) &= \int^{m \in \M} \int^{c,d \in \C} \C(a, m \cdot c) \times P(c,d) \times  \C(m \cdot d, b) \\
&\xrightarrow{g}
\int^{m \in \M} \int^{c,d \in \C} \C(a, m \cdot c) \times Q(c,d) \times  \C(m \cdot d, b) \\
&\xrightarrow{\alpha}
\int^{m \in \M} \int^{c,d \in \C} \C(a, m \cdot c) \times Q(m\cdot c,m\cdot d) \times  \C(m \cdot d, b) \\
&\to Q(a,b) \\
\end{align*}
\todo{Prove that $\beta(g)$ preserves the module structure}\\
It is routine to check that these $\alpha$ and $\beta$ are inverses.
\end{proof}

\section{Profunctor Lenses}

For any $a \in \C$, we have a functor $-(a, a) : \Tamb_\C(\M) \to \Set$. Note that this functor is lax monoidal: there is a canonical inclusion \todo{flip P and Q?}
\begin{align*}
i_{P,Q} : P(a,a)\times Q(a,a) \to \int^{d \in D} Q(a,d) \times P(d,a) = (P \star Q)(a,a)
\end{align*}
and function $i : 1 \to \C(a,a)$ that selects $\id_a$.

\begin{lemma}
The functor $-(a, a) : \Tamb_\C(\M) \to \Set$ is representable: there is a natural isomorphism
$-(a, a) \cong \Tamb_\C(\M)(\Pastro_\C(\M)E_b, -)$
\end{lemma}
\begin{proof}
We have the chain of natural isomorphisms:
\begin{align*}
&-(a,a) \\
&\cong \int_{c,d \in \C} \Set(\C(a, c) \times \C(d, a), -(c,d)) \\
&\cong \int_{c,d \in \C} \Set(E_a(c,d), -(c,d)) \\
&\cong \Prof(E_a, U-) \\
&\cong \Tamb_\C(\M)(\Pastro_\C(\M)E_a, -)
\end{align*}
\end{proof}

To any lens $l = a \isoto m \cdot b$ we associate a natural transformation $l' : -(b, b) \to -(a, a)$ with components 
\begin{align*}
P(b, b) \xrightarrow{\alpha_{b,b,m}} P(m\cdot b, m\cdot b) \xrightarrow{P(l, l^{-1})} P(a,a)
\end{align*}
where $\alpha$ is the module structure on $P$.

Given such a natural transformation $-(b, b) \to -(a, a)$, we would like to recover an object $m \in \M$ and maps $a \to m\cdot b$, $m \cdot b \to a$.

\begin{lemma}
\begin{align*}
[\Tamb_\C(\M), \Set](-(b, b),-(a, a)) &\cong \int^{m \in \M} \C(a, m \cdot b) \times \C(m \cdot b, a)
\end{align*}
\label{pastro-exchange-characterisation}
\end{lemma}
\begin{proof}
We have the chain of isomorphisms:
\begin{align*}
&[\Tamb_\C(\M), \Set](-(b, b),-(a, a)) \\
&\cong [\Tamb_\C(\M), \Set](\Tamb_\C(\M)(\Pastro_\C(\M)E_b, -), -(a, a)) \\
&\cong (\Pastro_\C(\M)E_b)(a,a) \\
&= \int^{m \in \M} \int^{c,d \in \C} \C(a, m \cdot c) \times E_b(c,d) \times \C(m \cdot d, a) \\
&\cong \int^{m \in \M} \int^{c,d \in \C} \C(a, m \cdot c) \times \C(c,b) \times \C(b, d) \times \C(m \cdot d, a) \\
&\cong \int^{m \in \M} \C(a, m \cdot b) \times \C(m \cdot b, a)
\end{align*}
\end{proof}

\begin{corollary}
A natural transformation $l : -(b, b) \to -(a, a)$ is determined by the value of the component of $l$ at $\Pastro_\C(\M)E_b$, on the canonical element $(\id_b, (\id_b,\id_b),\id_b) \in (\Pastro_\C(\M)E_b)(b, b)$.
\end{corollary}
\begin{proof}
This is exhibited by the action of the intermediate isomorphism
\begin{align*}
[\Tamb_\C(\M), \Set](-(b, b),-(a, a))
\cong (\Pastro_\C(\M)E_b)(a,a)
\end{align*}
\end{proof}

We can now characterise the subset of natural transformations $-(b, b) \to -(a, a)$ that correspond to lenses.

\begin{proposition}
A natural transformation 
$l : -(b, b) \to -(a, a)$ corresponds to a lens iff $l$ is a lax monoidal transformation with repect to $\star$ on $\Tamb_\C(\M)$ and $\times$ on $\Set$, i.e., for all $P, Q \in \Tamb_\C(\M)$, both 
\[
\begin{tikzcd}
P(b, b) \times Q(b, b) \ar[d, "i"left ] \ar[r, "l_P \times l_Q" above] & P(a, a) \times Q(a, a) \ar[d, "i"] \\
(Q\star P)(b, b) \ar[r, "l_{P \star Q}" below]  & (Q\star P)(a, a)
\end{tikzcd}
\]
and
\[
\begin{tikzcd}
& 1 \ar[dl, "i" above left] \ar[dr, "i"] \\
\C(b,b) \ar[rr, "l" below] & &\C(a,a)
\end{tikzcd}
\]
commute.
\end{proposition}
\begin{proof}
Let $l : a \isoto m \cdot b$ be a representative of a lens such that $l$ is invertible. Then in the following diagram:
\[
\begin{tikzcd}[column sep=huge]
P(b, b) \times Q(b, b) \ar[d, "i" left ] \ar[r, "\alpha \times \alpha" above] & P(m\cdot b, m\cdot b) \times Q(m\cdot b, m\cdot b) \ar[d, "i"] \ar[r, "{P(l, l^{-1})\times Q(l, l^{-1})}" above] & P(a, a) \times Q(a, a) \ar[d, "i"] \\
(Q\star P)(b, b) \ar[r, "\alpha_{m,b,b}" below] & (Q\star P)(m\cdot b, m\cdot b) \ar[r, "{(Q\star P)(l, l^{-1})}" below] & (Q\star P)(a, a)
\end{tikzcd}
\]

The left hand square commutes by the definition of the module structure structure on $Q\star P$. Further factoring the right hand square:
\[
\begin{tikzcd}[column sep=huge]
P(m\cdot b, m\cdot b) \times Q(m\cdot b, m\cdot b) \ar[d, "i"] \ar[r, "{P(l, \id)\times Q(\id, l^{-1})}" above] & P(a, m\cdot b) \times Q(m\cdot b, a) \ar[d, "i"] \ar[r, "{P(\id, l^{-1})\times Q(l, \id)}" above] & P(a, a) \times Q(a, a) \ar[d, "i"] \\
(Q\star P)(m\cdot b, m\cdot b) \ar[r, "{(Q\star P)(l, l^{-1})}" below] & (Q\star P)(a, a) \ar[r, "\id" below] &(Q\star P)(a, a)
\end{tikzcd}
\]
The left side commutes by functoriality, and the right side commutes by the the definition of coend. Therefore the associated natural transformation is lax monoidal as requried.

Also, the required triangle commutes, as $\id_b \in \C(b,b)$ is sent to 
\begin{align*}
(l \circ - \circ l^{-1})\alpha_{b,b,m}(\id_b) = (l \circ - \circ l^{-1})(\id_{m\cdot b}) = l \circ l^{-1} = \id_a
\end{align*}
Therefore, the associated natural transformation is lax monoidal.

Conversely, suppose we have a lax monoidal natural transformation $-(b, b) \to -(a, a)$, and let $(l, r) \in \int^{m \in \M} \C(a, m \cdot b) \times \C(m \cdot b, a)$ be a representative of the corresponding element of the coend. The triangle condition exactly states that $rl = \id_a$.

Let $L_b := \int^{m \in \M} \C(-,m\cdot b)$ and $R_b := \int^{m \in \M} \C(m\cdot b,=)$ be elements of $\Tamb_\C(\M)$ with the evident module structures. Note that $R_b \star L_b$ is the constant profunctor at $\int^{m\in \M} \C(m \cdot b, m \cdot b)$. Specialising the above digram to $P = R_b$ and $Q = L_b$, we have:
\[
\begin{tikzcd}[column sep=huge]
R_b(b, b) \times L_b(b, b) \ar[d, "i" left ] \ar[r, "\alpha_{m,b,b} \times \alpha_{m,b,b}" above] & R_b(m\cdot b, m\cdot b) \times L_b(m\cdot b, m\cdot b) \ar[d, "i"] \ar[r, "{R_b(l, r)\times L_b(l, r)}" above] & R_b(a, a) \times L_b(a, a) \ar[d, "i"] \\
(R_b\star L_b)(b, b) \ar[r, "\alpha_{m,b,b}" above] \ar[d, "\cong" left] & (R_b\star L_b)(m\cdot b, m\cdot b) \ar[r, "{(R_b\star L_b)(l,r)}" above] \ar[d, "\cong" right] & (R_b\star L_b)(a, a) \ar[d, "\cong" right]\\
\int^{m\in \M} \C(m \cdot b, m \cdot b) \ar[r, "\id" below] & \int^{m\in \M} \C(m \cdot b, m \cdot b) \ar[r, "\id" below] & \int^{m\in \M} \C(m \cdot b, m \cdot b)
\end{tikzcd}
\]

Here, the vertical maps are simply composition of morphisms in $\C$. Inspecting the right-hand rectangle, commutativity of the diagram implies that $[lr] = [\id_{m\cdot b}]$ in $\int^{m\in \M} \C(m \cdot b, m \cdot b)$.

Therefore, by Proposition \ref{characterise-lenses-in-coend}, $(l,r)$ represents a lens.
\end{proof}

We will refer to the above diagrams as the \emph{lens laws}, and say that natural transformations $-(b, b) \to -(a, a)$ are \emph{valid lenses} if they satisfy it.

\begin{theorem}
The functor $I : \Lens_\C(\M) \to \LaxMonCat(\Tamb_\C(\M), \Set)^\op$ is full and faithful, where $\LaxMonCat(\Tamb_\C(\M), \Set)$ is the category of lax monoidal functors and monoidal natural transformations.
\end{theorem}
\begin{proof}
\todo{TODO}
\end{proof}

\subsection{``Polymorphic'' lenses}

\todo{This is an important todo}

\section{Haskell Lenses}
To be completely precise, the above sections should have been written in the enriched setting. Here we will do the usual slight of hand and treat $\Hask$ as equivalent to $\Set$.

One reason that the van Laarhoven/profunctor description of lenses is so effective in Haskell, is the ease with which one can represent ends and coends.

\todo{demonstrate}

\subsection{Lenses in other categories}

\section{Future Work}

"Symmetric" Lenses

\begin{figure}[b]
\begin{tabular}{ll}
\hline
Haskell Name & Acting Category \\
\hline
Iso & $\mathbf{1}$ \\
Lens & $(\Hask, \times)$ \\
Prism & $(\Hask, \sqcup)$ \\
Traversal & $(\Traversable(\Hask), \circ)$ \\
Setter & $(\Endo(\Hask), \circ)$ \\
Review & $(\Point(\Hask), \circ)$ \\
Getter/View & $(\CoPoint(\Hask), \circ)$ \\
Fold & ??? \\
\hline
\end{tabular}
\caption{Classes of $\Lens$es used in Haskell}
\end{figure}

\begin{figure}[b]
\begin{tikzpicture}[node distance=3.5cm,line width=0.5pt]
\node(1) at (0,0) {$1$};
\node(Lens) [above left of =1] {$- \times D$};
\node(Prism) [above right of =1] {$- \sqcup D$};
\node(Traversal) [above right of =Lens] {$\Traversable(\Hask)$};
\node(Setter) [above of =Traversal] {$\Endo(\Hask)$};
\node(Getter) [above left of =Lens] {$\CoPoint(\Hask)$???};
\node(Fold)   [above of=Getter] {Fold ???};
\node(Review) [above right of =Prism] {$\Point(\Hask)$???};

\draw[right hook->](1) -- (Lens);
\draw[right hook->](1) -- (Prism);
\draw[right hook->](Lens) -- (Traversal);
\draw[right hook->](Prism) -- (Traversal);
\draw[right hook->](Traversal) -- (Fold);
\draw[right hook->](Lens) -- (Getter);
\draw[right hook->](Prism) -- (Review);
\draw[right hook->](Getter) -- (Fold);

\draw[->](Traversal) -- (Review);
\draw[->](Traversal) -- (Setter);

\end{tikzpicture}
\caption{Morphisms between various classes of $\Lens$es. Arrows marked with hooks are fully faithful. \todo{figure out if this matters}
}
\end{figure}

\nocite{*}
\bibliographystyle{amsalpha}
\bibliography{lens}
\end{document}

### 2017-06-25 paper.tex
An overly optimistic outline

--- 2017-06-25 old-notes/lens.tex
@@
 
-\title{Profunctor Lenses}
+\title{The Categorical Structure of Profunctor Optics}
 \author{Mitchell Riley}
@@
 \section{Introduction}
-
-A good introduction would include:
-
-Motivation for Lenses
-
-Motivation for van Laarhoven Lenses
-
-Motivation for Profunctor Lenses
-
-\subsection{Laws}
-Whatever formulation of standard lenses is used, there are some laws that are expected to hold. When we work in $\Set$ (or $\Hask$), the laws are typically given as follows.
-
-Given:
-\begin{align*}
-\fget &: \Lens(a, b) \times a \to b \\
-\fput &: \Lens(a, b) \times b \times a \to a
-\end{align*}
-we have that
-\begin{align*}
-\fget(l, \fput(l, b, a))   &= b \\
-\fput(l, \fget(l, a), a)   &= a \\
-\fput(l, b', \fput(l, b, a)) &= \fput(l, b', a)
-\end{align*}
-
-To express these laws in a general category with products, however, we must rewrite these in a ``pointfree'' style.
-
-Given:
-\begin{align*}
-\fget &: \Lens(a, b) \to \C(a, b) \\
-\fmodify &: \Lens(a, b) \times \C(b, b) \to \C(a, a)
-\end{align*}
-we have that
-\begin{align*}
-\fget(l) \circ \fmodify(l, f) &= f \circ \fget(l) \\
-\fmodify(l, \id_b) &= \id_a \\
-\fmodify(l, f) \circ \fmodify(l, g) &= \fmodify(l, f \circ g)
-\end{align*}
-We will refer to these as the get/modify laws.
-
-Similarly, the laws for prisms are typically stated as
-\todo{todo}
-
-\subsection{Notation}
-
-We use $\homC(a,b)$ to denote the internal hom of a cartesian closed category $\C$.
-
-\section{Lenses}
-
-\subsection{Monoidal actions}
-
-\begin{definition}
-An \emph{action} of a monoidal category $(\M, \otimes, 1)$ on a category $\C$ is a functor $\cdot : \M \times \C \to \C$ such that there are natural isomorphisms $m \cdot (n \cdot x) \isoto (m \otimes n) \cdot x$ and $1 \cdot x \isoto x$ for any $m, n \in \M$ and $x \in \C$.
-These isomorphism must satisfy the expected associativity and unit axioms.
-We will leave these isomorphisms implicit to reduce the amount of noise in our diagram.
-\todo{draw diagrams?}
-
-Equivalently, an action of a monoidal category is a strong monoidal functor $\M \to [\C, \C]$, where $[\C, \C]$ is equipped with the monoidal structure $([\C, \C], \circ, \id_\C)$.
-\end{definition}
-
-Examples abound: 
-\begin{itemize} 
-\item Any monoidal category acts on itself via left multiplication. 
-\item Any subcategory $\M \subset [\C, \C]$ that is closed under composition is a monoidal category, which acts on $\C$ simply by functor application.
-\item If $\C$ is equipped with an action of $\M$, then any functor category $[\D, \C]$ has an action of $\M$ computed pointwise.
-\end{itemize}
-
-We will also be interested in actions that are \emph{not} functorial in $\C$:
-
-\begin{definition}
-A \emph{dodgy monoidal action} of $\M$ on $\C$ is a functor $\cdot : \M \times \ob \C \to \C$, such that the same conditions hold as above.
-Here, $\ob \C$ is the category with the same objects as $\C$ but only identity morphisms.
-\end{definition}
-
-Most of what follows is still true for dodgy monoidal actions. \todo{But I am yet to check carefully which parts fail}
-
-\subsection{Lenses}
-
-\begin{definition}
-Let $\C$ be a category equipped with an action of the monoidal category $(\M, \otimes, 1)$.
-The \emph{category of lenses $\Lens_\C(\M)$} has objects the objects of $\C$, and morphisms $a$ to $b$ given by pairs $(m \in \M, a \isoto m \cdot b)$, where the second component is an isomorphism.
-However, we identify lenses that can be connected by an isomorphism in $\M$: $(m \in \M, l : a \isoto m \cdot b)$ is identified with $(m' \in \M, l' : a \isoto m' \cdot b)$ iff there exists an isomorphism $\alpha : m \isoto m'$ such that $l' = (\alpha\cdot b)l$.
-To save on notation, we will simply write $l : a \isoto m \cdot b$ for a representative of a lens $l$.
-
-The identity lens is simply $\id_a : a \isoto 1 \cdot a$, and the composition of two lenses $a \isoto m \cdot b$ and $b \isoto n \cdot c$ is given by
-\begin{align*}
-a \isoto m \cdot b \isoto m \cdot (n \cdot c) \isoto (m \otimes n) \cdot c
-\end{align*}
-It is not difficult to check that this composition is well defined.
-\end{definition}
-\todo{TODO: Consider flipping the direction of a lens to avoid op later?}
-
-We may consider the slice category $\Act(\C) := \MonCat/[\C, \C]$ of monoidal actions on $\C$, where $\MonCat$ is the category of monoidal categories and strong monoidal functors.
-For any map $F : \M \to \N$ in $\Act(\C)$, we have a functor $\Lens_\C(\M) \to \Lens_\C(\N)$ which sends any lens $a \isoto m \cdot b$ to $a \isoto Fm \cdot b$.
-Here, the map is identical: $m \cdot b = Fm \cdot b$.
-In this way, $\Lens_\C$ forms a functor $\Act(\C) \to \Cat$.
-
-Unfortunately, the above definition of a lens is difficult to work with, both categoricaly and programmatically.
-Instead, we embed $\Lens_\C(\M)(a, b)$ inside $\int^{m \in M} \C(a, m\cdot b) \times \C(m\cdot b, a)$, and work with the latter.
-
-\begin{lemma}
-The canonical map $I : \Lens_\C(\M)(a, b) \to \int^{m \in M} \C(a, m\cdot b) \times \C(m\cdot b, a)$ that sends $l : a \isoto m \cdot b$ to $[(l, l^{-1})]$ is injective.
-\end{lemma}
-\begin{proof}
-
-\end{proof}
-
-We now wish to characterise the elements of $\int^{m \in M} \C(a, m\cdot b) \times \C(m\cdot b, a)$ that correspond to lenses.
-
-\begin{proposition}\label{characterise-lenses-in-coend}
-An element $[(l, r)] \in \int^{m \in M} \C(a, m\cdot b) \times \C(m\cdot b, a)$ corresponds to a lens iff $rl = \id_A$ and $[lr] = [\id_{m\cdot b}]$ as elements of $\int^{m\in \M} \C(m \cdot b, m \cdot b)$, for some $m \in \M$.
-\end{proposition}
-\begin{proof}
-If an element corresponds to a lens, there is a representative $(l, r)$ such that $rl = \id_a$ and $lr = \id_{m\cdot b}$, so certainly $[lr] = [\id_{m\cdot b}]$ in $\int^{m\in \M} \C(m \cdot b, m \cdot b)$.
-
-\todo{This is wrong} Conversely, suppose $rl = \id_A$ and $[lr] = [\id_{m\cdot b}]$ in $\int^{m\in \M} \C(m \cdot b, m \cdot b)$.
-The coend relations imply that there exist $p : m \cdot b \to n \cdot b$ and $q : n \cdot b \to m \cdot b$ such that $plrq = \id_{n\cdot b}$ and $qp = \id_{m\cdot b}$.
-
-The same relations hold in $\int^{m \in M} \C(a, m\cdot b) \times \C(m\cdot b, a)$, so $[(l, r)] = [(pl, rq)]$.
-Now $plrq = \id_{n\cdot b}$ on the nose, and $rqpl = rl = \id_a$, so $[(l, r)]$ represents the lens $pl : a \isoto n \cdot b$.
-\end{proof}
-
-\section{Examples}
-
-Viewing lenses as a subset of $\int^{m \in M} \C(a, m\cdot b) \times \C(m\cdot b, a)$ allows for some more practical descriptions of lenses for particular choices of $\M$.
-
-\subsection{Isos}
-
-Let $\M = \mathbf{1}$. Then the set of potential lenses between $a, b \in \C$ is 
-\begin{align*}
-\int^{m \in \mathbf{1}} \C(a, m \cdot b) \times \C(m \cdot b, a)
-&\cong \C(a, 1 \cdot b) \times \C(1 \cdot b, a) \\
-&\cong \C(a, b) \times \C(b, a)
-\end{align*}
-
-\subsection{Lenses}
-
-Suppose $\C$ has finite products, and let $\M = (\C, \times, 1)$, then
-\begin{align*}
-(\Pastro_\C(\times)E_b)(a,a) 
-&\cong \int^{m \in \C} \C(a, m \times b) \times \C(m \times b, a) \\
-&\cong \int^{m \in \C} \C(a, m) \times \C(a, b) \times \C(m \times b, a) \\
-&\cong  \C(a, b) \times \C(a \times b, a)
-\end{align*}
-This is the traditional getter/setter form of lenses.
-
-\begin{proposition}
-An element of $\C(a, b) \times \C(a \times b, a)$ corresponds to a lens iff it satisfies the get/modify lens laws.
-\end{proposition}
-\begin{proof}
-\todo{todo}
-\end{proof}
-
-\subsection{Prisms}
-
-Suppose $\C$ has finite coproducts, and let $\M = (\C, \sqcup, 0)$, then
-\begin{align*}
-(\Pastro_\C(\sqcup)E_b)(a,a) 
-&\cong \int^{m \in \C} \C(a, m \sqcup b) \times \C(m \sqcup b, a) \\
-&\cong \int^{m \in \C} \C(a, m \sqcup b) \times \C(m, a) \times \C(b, a) \\
-&\cong \C(a, a \sqcup b) \times \C(b, a)
-\end{align*}
-
-\todo{Show that the laws follow from our law}
-
-\subsection{Setters}
-To define Setters, we must first define what it means for a functor to be \emph{strong}.
-
-\begin{definition}
-\todo{The extra generality may not be necessary}
-Suppose $\C$ is equipped with an action of $\M$. A \emph{strength} for a functor $F : \C \to \C$ is a natural transformation
-\begin{align*}
-s_{m,a} : m \cdot F a \to F(m \cdot a)
-\end{align*}
-such that both
-\[
-\begin{tikzcd}
-m \cdot n \cdot Fa \ar[r, "s_{n,a}"] \ar[dr, "s_{m\otimes n, a}" below left]  & m \cdot F(n\cdot a) \ar[d, "s_{m, n\cdot a}" right] \\
-& F(m \cdot n \cdot a)
-\end{tikzcd}
-\]
-and
-\[
-\begin{tikzcd}
-1 \cdot F a \ar[r, "s_{1,a}"] \ar[dr, "\cong" below left]  & F(1 \cdot a) \ar[d, "\cong" right] \\
-& F a
-\end{tikzcd}
-\]
-commute.
-\end{definition}
-
-\begin{definition}
-There is a category $\Strong_\C(\M)$ of functors equipped with strengths, where the morphisms are natural transformations that respect the extra structure.
-There is an evident forgetful functor $U : \Strong_\C(\M) \to [\C, \C]$.
-\end{definition}
-
-The composition of two strong functors itself has a canonical strength, given by the composite
-\begin{align*}
-m \cdot FG a \xrightarrow{s_{m, Ga}} F(m \cdot G a) \xrightarrow{Fs_{m,a}} FG (m \cdot a)
-\end{align*}
-
-In this way, $\Strong_\C(\M)$ is also a monoidal category under composition. This category also acts on $\C$, via the action of the underlying functors.
-
-Now, returning to Setters, suppose $\C$ is cartesian closed, and let $\M = \Strong_\C(\times)$. First, a lemma:
-
-\begin{lemma}
-$\C(a, Fb) \cong \Strong_\C(\times)(a \times \homC(b, -), F)$
-\end{lemma}
-\begin{proof}
-Given a $f \in \C(a, Fb)$, let $\eta$ be the natural transformation with components
-\begin{align*}
-a \times \homC(b, c) \xrightarrow{f \times \id} Fb \times \homC(b, c) \xrightarrow{s_{\homC(b, c), b}}  F(b \times \homC(b, c)) \xrightarrow{F\epsilon} Fc
-\end{align*}
-where $s$ is the strength for $F$ and $\epsilon$ is the evaluation map.
-
-Conversely, given an $\eta$, the component at $b$ is a function $g : a \times \homC(b, b) \to Fb$; we recover $f$ as $f(a) = g(a, \id_b)$.
-
-Again, it is routine to check these are inverses.
-\end{proof}
-
-This is a generalisation of Proposition 2.2 in \cite{MR3482285}, which only considered functors $\Set \to \Set$ (all of which are strong).
-
-Now, the set of (possibly invalid) lenses with respect to this action is:
-\begin{align*}
-\int^{F \in \Strong_\C(\times)} \C(a, F b) \times \C(F b, a) 
-&\cong \int^{F} \Strong_\C(\times)(a \times \homC(b, -), F) \times \C(F b, a) \\ 
-&\cong \C(a \times \homC(b, b), a) \\
-&\cong \C(\homC(b, b), \homC(a, a))
-\end{align*}
-
-\subsection{Views and Reviews}
-
-Here we make use of dodgy monoidal actions. Let $\M=\Point(\C)$ be the category of \emph{pointed assignments}: functors $
-F : \ob C \to C$ equipped with natural transformations $\epsilon : 1 \to F$.
-
-As in earlier sections, we must charactarise $\C(a, Fb)$ as the set of natural transformation from some assignment to $F$.
-Let $C_{a,b}$ be the pointed assignment such that $C_{a,b}(b) = a \sqcup b$ and $C_{a,b}(c) = c$ for all $c \neq b$.
-
-\begin{lemma}
-$\C(a, Fb) \cong \Point(\C)(C_{a,b}, F)$
-\end{lemma}
-\begin{proof}
-\todo{boring}
-\end{proof}
-
-Then:
-
-\begin{align*}
-\int^{F \in \Point(\C)} \C(a, F b) \times \C(F b, a) 
-&\cong \int^{F} \Point(\C)(C_{a,b}, F) \times \C(F b, a) \\ 
-&\cong \C(a \sqcup b, a) \\
-&\cong \C(a, a) \times \C(b, a)
-\end{align*}
-
-\section{Profunctors and Tambara Modules}
-
-\begin{definition}
-A \emph{profunctor} between $\C$ and $\D$ is a functor $\C^\op \times \D \to \Set$. We have a category $\Prof(\C, \D) := [\C^\op \times \D, \Set]$.
-\end{definition}
-
-\begin{definition}
-For any $a \in \C$, define the \emph{exchange} profunctor to be $E_a := \C(-,a) \times \C(a,=)$. 
-%\todo{For lack of better names} We also define the \emph{lefty} and \emph{righty} profunctors to be $L_b := \C(-, b)$ and $R_b := \C(b, =)$ respectively.
-\end{definition}
-
-\begin{definition}
-Given profunctors $P \in \Prof(\C, \D)$ and $Q \in \Prof(\D,\E)$, the composite $Q \star P \in \Prof(\C, \E)$ is given by
-\begin{align*}
-(Q \star P)(c,e) = \int^{d \in \D} P(c,d) \times Q(d,e)
-\end{align*}
-In particular, for any $\C$, $\Prof(\C,\C)$ is a monoidal category with respect to $\star$.
-The identity for this composition is given by $\C(-,=)$.
-Details and proofs can be found in \cite{loregian2015co}.
-\end{definition}
-
-Any functor $F : \C \to \D$ can be turned into a profunctor in two different ways: $F_* \in \Prof(\D, \C)$ given by $F_* = \D(-,F=)$, and  $F^* \in \Prof(\C, \D)$ given by $F^* = \D(F-,=)$.
-
-\begin{lemma}\label{procomp-downstar-is-comp}
-Let $F : \C \to \D$ and $G : \D \to \E$, so that $F_* \in \Prof(\D, \C)$ and $G_* \in \Prof(\E,\D)$. Then $F_* \star G_* \cong (GF)_*$
-\end{lemma}
-\begin{proof}
-\todo{todo}
-\end{proof}
-
-%It is also easily verified that $L_b \star R_b \cong E_b$, and $R_b \star L_b$ is the constant profunctor at $\C(b,b)$.
-
-The following definition is a generalisation of an idea that appears in \cite{MR2425558}.
-
-\begin{definition}
-Suppose $\C$ is equipped with an action of $\M$, and let $P \in \Prof(\C, \C)$ be a profunctor. A \emph{Tambara module structure} for $P$ with respect to $\M$ is a natural family of maps:
-\begin{align*}
-\alpha_{a,b,m} : P(a, b) \to P(m \cdot a, m \cdot b)
-\end{align*}
-such that $\alpha_{a,b,1} = \id_{P(a,b)}$, and the following diagram commutes:
-\[
-\begin{tikzcd}
-P(a,b) \ar[r, "\alpha_{a,b,m}"] \ar[dr, "\alpha_{m\otimes n, a, b}" below left] & P(m \cdot a, m \cdot b) \ar[d, "\alpha_{n, m \cdot a, m \cdot b}" right] \\
-& P(n \cdot (m \cdot a), n \cdot (m \cdot b))
-\end{tikzcd}
-\]
-\end{definition}
-
-The identity profunctor $\C(-,=)$ has a module structure with respect to any action, as every action is functorial.
-
-If $P \in \Prof(\C, \D)$ and $Q \in \Prof(\D,\E)$ are equipped with module structures $\alpha$ and $\beta$ respectively, there is a canonical module structure on $Q \star P$ given by
-\begin{align*}
-(Q \star P)(c,e) &= \int^{d \in D} P(c,d) \times Q(d,e) \\ 
-&\to \int^{d \in D} P(m \cdot c, m\cdot d) \times Q(m \cdot d, m \cdot e) \\
-&\to \int^{d \in D} P(m \cdot c, d) \times Q(d, m \cdot e) \\
-&= (Q \star P)(m \cdot c, m \cdot e)
-\end{align*}
-Here, the second map is induced by the universal property of the coend: Each $P(m \cdot c, m\cdot d) \times Q(m \cdot d, m \cdot e)$ has a canonical inclusion into $\int^{d \in D} P(m \cdot c, d) \times Q(d, m \cdot e)$.
-
-\begin{definition}
-There is a category $\Tamb_\C(\M)$ of Tambara modules and natural transformations that respect the extra structure, in the sense that the diagram
-\[
-\begin{tikzcd}
-P(a,b) \ar[r, "\alpha_{a,b,m}"] \ar[d, "l_{a,b}" left] & P(m \cdot a, m \cdot b) \ar[d, "l_{m\cdot a,m\cdot b}" right] \\
-Q(a,b) \ar[r, "\alpha_{a,b,m}"] & Q(m \cdot a, m \cdot b)
-\end{tikzcd}
-\]
-commutes.
-\end{definition}
-
-This category is monoidal with respect to $\star$ as given above. There is an evident forgetful functor $U : \Tamb_\C(\M) \to \Prof(\C, \C)$ that is strong monoidal.
-
-\begin{definition}
-Let $\mathrm{Pastro}_\C(\M) : \Prof(\C, \C) \to \Tamb_\C(\M)$ be the functor
-\begin{align*}
-\mathrm{Pastro}_\C(\M)(P) := \int^{m \in \M} \C(m \cdot -, =) \star P \star \C(-, m \cdot =)
-\end{align*}
-Or, in other words, 
-\begin{align*}
-\mathrm{Pastro}_\C(\M)(P)(a,b) := \int^{m \in \M} \int^{c,d \in \C} \C(a, m \cdot c) \times P(c,d) \times  \C(m \cdot d, b)
-\end{align*}
-The module structure $\alpha_{a,b,m} : \mathrm{Pastro}_\C(\M)(P)(a, b) \to \mathrm{Pastro}_\C(\M)(P)(m \cdot a, m \cdot b)
-$ is given by the composite
-\begin{align*}
-\mathrm{Pastro}_\C(\M)(P)(a,b) &= \int^{n \in \M} \int^{c,d \in \C} \C(a, n \cdot c) \times P(c,d) \times  \C(n \cdot d, b) \\
-&\to \int^{n \in \M} \int^{c,d \in \C} \C(m \cdot a, m \cdot (n \cdot c)) \times P(c,d) \times  \C(m \cdot (n \cdot d), m \cdot b) \\
-&\cong \int^{n \in \M} \int^{c,d \in \C} \C(m \cdot a, (m \otimes n) \cdot c) \times P(c,d) \times  \C((m \otimes n) \cdot d, m \cdot b) \\
-&\to \int^{n \in \M} \int^{c,d \in \C} \C(m \cdot a, n \cdot c) \times P(c,d) \times  \C(n \cdot d, m \cdot b) \\
-&= \mathrm{Pastro}_\C(\M)(P)(m \cdot a, m \cdot b)
-\end{align*}
-where the final map is again induced by the universal property of the coend. \todo{This does not work if the action is not functorial in $\C$!!!}
-\end{definition}
-
-\begin{proposition}
-$\Pastro_\C(\M)$ is left adjoint to $U$.
-\end{proposition}
-\begin{proof}
-We prove this directly by providing natural inverse maps
-\begin{align*}
-\alpha : \Tamb_\C(\M)(\Pastro_\C(\M)(P), Q) \cong \Prof(\C, \C)(P, UQ) : \beta
-\end{align*}
-Given a natural transformation $f : \Pastro_\C(\M)(P) \to Q$, let $\alpha(f) : P \to UQ$ be the natural transformation with components
-\begin{align*}
-P(a,b) \xrightarrow{(id, -, id)} \C(a, 1 \cdot a) \times P(a,b) \times \C(1 \cdot b, b) \xrightarrow{f} Q(a,b)
-\end{align*} 
-Given a $g : P \to UQ$, let $\beta(g) : \Pastro_\C(\M)(P) \to Q$ be the natural transformation with components
-\begin{align*}
-\Pastro_\C(\M)(P)(a,b) &= \int^{m \in \M} \int^{c,d \in \C} \C(a, m \cdot c) \times P(c,d) \times  \C(m \cdot d, b) \\
-&\xrightarrow{g}
-\int^{m \in \M} \int^{c,d \in \C} \C(a, m \cdot c) \times Q(c,d) \times  \C(m \cdot d, b) \\
-&\xrightarrow{\alpha}
-\int^{m \in \M} \int^{c,d \in \C} \C(a, m \cdot c) \times Q(m\cdot c,m\cdot d) \times  \C(m \cdot d, b) \\
-&\to Q(a,b) \\
-\end{align*}
-\todo{Prove that $\beta(g)$ preserves the module structure}\\
-It is routine to check that these $\alpha$ and $\beta$ are inverses.
-\end{proof}
-
-\section{Profunctor Lenses}
-
-For any $a \in \C$, we have a functor $-(a, a) : \Tamb_\C(\M) \to \Set$. Note that this functor is lax monoidal: there is a canonical inclusion \todo{flip P and Q?}
-\begin{align*}
-i_{P,Q} : P(a,a)\times Q(a,a) \to \int^{d \in D} Q(a,d) \times P(d,a) = (P \star Q)(a,a)
-\end{align*}
-and function $i : 1 \to \C(a,a)$ that selects $\id_a$.
-
-\begin{lemma}
-The functor $-(a, a) : \Tamb_\C(\M) \to \Set$ is representable: there is a natural isomorphism
-$-(a, a) \cong \Tamb_\C(\M)(\Pastro_\C(\M)E_b, -)$
-\end{lemma}
-\begin{proof}
-We have the chain of natural isomorphisms:
-\begin{align*}
-&-(a,a) \\
-&\cong \int_{c,d \in \C} \Set(\C(a, c) \times \C(d, a), -(c,d)) \\
-&\cong \int_{c,d \in \C} \Set(E_a(c,d), -(c,d)) \\
-&\cong \Prof(E_a, U-) \\
-&\cong \Tamb_\C(\M)(\Pastro_\C(\M)E_a, -)
-\end{align*}
-\end{proof}
-
-To any lens $l = a \isoto m \cdot b$ we associate a natural transformation $l' : -(b, b) \to -(a, a)$ with components 
-\begin{align*}
-P(b, b) \xrightarrow{\alpha_{b,b,m}} P(m\cdot b, m\cdot b) \xrightarrow{P(l, l^{-1})} P(a,a)
-\end{align*}
-where $\alpha$ is the module structure on $P$.
-
-Given such a natural transformation $-(b, b) \to -(a, a)$, we would like to recover an object $m \in \M$ and maps $a \to m\cdot b$, $m \cdot b \to a$.
-
-\begin{lemma}
-\begin{align*}
-[\Tamb_\C(\M), \Set](-(b, b),-(a, a)) &\cong \int^{m \in \M} \C(a, m \cdot b) \times \C(m \cdot b, a)
-\end{align*}
-\label{pastro-exchange-characterisation}
-\end{lemma}
-\begin{proof}
-We have the chain of isomorphisms:
-\begin{align*}
-&[\Tamb_\C(\M), \Set](-(b, b),-(a, a)) \\
-&\cong [\Tamb_\C(\M), \Set](\Tamb_\C(\M)(\Pastro_\C(\M)E_b, -), -(a, a)) \\
-&\cong (\Pastro_\C(\M)E_b)(a,a) \\
-&= \int^{m \in \M} \int^{c,d \in \C} \C(a, m \cdot c) \times E_b(c,d) \times \C(m \cdot d, a) \\
-&\cong \int^{m \in \M} \int^{c,d \in \C} \C(a, m \cdot c) \times \C(c,b) \times \C(b, d) \times \C(m \cdot d, a) \\
-&\cong \int^{m \in \M} \C(a, m \cdot b) \times \C(m \cdot b, a)
-\end{align*}
-\end{proof}
-
-\begin{corollary}
-A natural transformation $l : -(b, b) \to -(a, a)$ is determined by the value of the component of $l$ at $\Pastro_\C(\M)E_b$, on the canonical element $(\id_b, (\id_b,\id_b),\id_b) \in (\Pastro_\C(\M)E_b)(b, b)$.
-\end{corollary}
-\begin{proof}
-This is exhibited by the action of the intermediate isomorphism
-\begin{align*}
-[\Tamb_\C(\M), \Set](-(b, b),-(a, a))
-\cong (\Pastro_\C(\M)E_b)(a,a)
-\end{align*}
-\end{proof}
-
-We can now characterise the subset of natural transformations $-(b, b) \to -(a, a)$ that correspond to lenses.
-
-\begin{proposition}
-A natural transformation 
-$l : -(b, b) \to -(a, a)$ corresponds to a lens iff $l$ is a lax monoidal transformation with repect to $\star$ on $\Tamb_\C(\M)$ and $\times$ on $\Set$, i.e., for all $P, Q \in \Tamb_\C(\M)$, both 
-\[
-\begin{tikzcd}
-P(b, b) \times Q(b, b) \ar[d, "i"left ] \ar[r, "l_P \times l_Q" above] & P(a, a) \times Q(a, a) \ar[d, "i"] \\
-(Q\star P)(b, b) \ar[r, "l_{P \star Q}" below]  & (Q\star P)(a, a)
-\end{tikzcd}
-\]
-and
-\[
-\begin{tikzcd}
-& 1 \ar[dl, "i" above left] \ar[dr, "i"] \\
-\C(b,b) \ar[rr, "l" below] & &\C(a,a)
-\end{tikzcd}
-\]
-commute.
-\end{proposition}
-\begin{proof}
-Let $l : a \isoto m \cdot b$ be a representative of a lens such that $l$ is invertible. Then in the following diagram:
-\[
-\begin{tikzcd}[column sep=huge]
-P(b, b) \times Q(b, b) \ar[d, "i" left ] \ar[r, "\alpha \times \alpha" above] & P(m\cdot b, m\cdot b) \times Q(m\cdot b, m\cdot b) \ar[d, "i"] \ar[r, "{P(l, l^{-1})\times Q(l, l^{-1})}" above] & P(a, a) \times Q(a, a) \ar[d, "i"] \\
-(Q\star P)(b, b) \ar[r, "\alpha_{m,b,b}" below] & (Q\star P)(m\cdot b, m\cdot b) \ar[r, "{(Q\star P)(l, l^{-1})}" below] & (Q\star P)(a, a)
-\end{tikzcd}
-\]
-
-The left hand square commutes by the definition of the module structure structure on $Q\star P$. Further factoring the right hand square:
-\[
-\begin{tikzcd}[column sep=huge]
-P(m\cdot b, m\cdot b) \times Q(m\cdot b, m\cdot b) \ar[d, "i"] \ar[r, "{P(l, \id)\times Q(\id, l^{-1})}" above] & P(a, m\cdot b) \times Q(m\cdot b, a) \ar[d, "i"] \ar[r, "{P(\id, l^{-1})\times Q(l, \id)}" above] & P(a, a) \times Q(a, a) \ar[d, "i"] \\
-(Q\star P)(m\cdot b, m\cdot b) \ar[r, "{(Q\star P)(l, l^{-1})}" below] & (Q\star P)(a, a) \ar[r, "\id" below] &(Q\star P)(a, a)
-\end{tikzcd}
-\]
-The left side commutes by functoriality, and the right side commutes by the the definition of coend. Therefore the associated natural transformation is lax monoidal as requried.
-
-Also, the required triangle commutes, as $\id_b \in \C(b,b)$ is sent to 
-\begin{align*}
-(l \circ - \circ l^{-1})\alpha_{b,b,m}(\id_b) = (l \circ - \circ l^{-1})(\id_{m\cdot b}) = l \circ l^{-1} = \id_a
-\end{align*}
-Therefore, the associated natural transformation is lax monoidal.
-
-Conversely, suppose we have a lax monoidal natural transformation $-(b, b) \to -(a, a)$, and let $(l, r) \in \int^{m \in \M} \C(a, m \cdot b) \times \C(m \cdot b, a)$ be a representative of the corresponding element of the coend.
-The triangle condition exactly states that $rl = \id_a$.
-
-Let $L_b := \int^{m \in \M} \C(-,m\cdot b)$ and $R_b := \int^{m \in \M} \C(m\cdot b,=)$ be elements of $\Tamb_\C(\M)$ with the evident module structures.
-Note that $R_b \star L_b$ is the constant profunctor at $\int^{m\in \M} \C(m \cdot b, m \cdot b)$.
-Specialising the above digram to $P = R_b$ and $Q = L_b$, we have:
-\[
-\begin{tikzcd}[column sep=huge]
-R_b(b, b) \times L_b(b, b) \ar[d, "i" left ] \ar[r, "\alpha_{m,b,b} \times \alpha_{m,b,b}" above] & R_b(m\cdot b, m\cdot b) \times L_b(m\cdot b, m\cdot b) \ar[d, "i"] \ar[r, "{R_b(l, r)\times L_b(l, r)}" above] & R_b(a, a) \times L_b(a, a) \ar[d, "i"] \\
-(R_b\star L_b)(b, b) \ar[r, "\alpha_{m,b,b}" above] \ar[d, "\cong" left] & (R_b\star L_b)(m\cdot b, m\cdot b) \ar[r, "{(R_b\star L_b)(l,r)}" above] \ar[d, "\cong" right] & (R_b\star L_b)(a, a) \ar[d, "\cong" right]\\
-\int^{m\in \M} \C(m \cdot b, m \cdot b) \ar[r, "\id" below] & \int^{m\in \M} \C(m \cdot b, m \cdot b) \ar[r, "\id" below] & \int^{m\in \M} \C(m \cdot b, m \cdot b)
-\end{tikzcd}
-\]
-
-Here, the vertical maps are simply composition of morphisms in $\C$.
-Inspecting the right-hand rectangle, commutativity of the diagram implies that $[lr] = [\id_{m\cdot b}]$ in $\int^{m\in \M} \C(m \cdot b, m \cdot b)$.
-
-Therefore, by Proposition \ref{characterise-lenses-in-coend}, $(l,r)$ represents a lens.
-\end{proof}
-
-We will refer to the above diagrams as the \emph{lens laws}, and say that natural transformations $-(b, b) \to -(a, a)$ are \emph{valid lenses} if they satisfy it.
-
-\begin{theorem}
-The functor $I : \Lens_\C(\M) \to \LaxMonCat(\Tamb_\C(\M), \Set)^\op$ is full and faithful, where $\LaxMonCat(\Tamb_\C(\M), \Set)$ is the category of lax monoidal functors and monoidal natural transformations.
-\end{theorem}
-\begin{proof}
-\todo{TODO}
-\end{proof}
-
-\subsection{``Polymorphic'' lenses}
-
-\todo{This is an important todo}
-
-\section{Haskell Lenses}
-To be completely precise, the above sections should have been written in the enriched setting. Here we will do the usual slight of hand and treat $\Hask$ as equivalent to $\Set$.
-
-One reason that the van Laarhoven/profunctor description of lenses is so effective in Haskell, is the ease with which one can represent ends and coends.
-
-\todo{demonstrate}
-
-\subsection{Lenses in other categories}
-
-\section{Future Work}
-
-"Symmetric" Lenses
-
-\begin{figure}[b]
-\begin{tabular}{ll}
-\hline
-Haskell Name & Acting Category \\
-\hline
-Iso & $\mathbf{1}$ \\
-Lens & $(\Hask, \times)$ \\
-Prism & $(\Hask, \sqcup)$ \\
-Traversal & $(\Traversable(\Hask), \circ)$ \\
-Setter & $(\Endo(\Hask), \circ)$ \\
-Review & $(\Point(\Hask), \circ)$ \\
-Getter/View & $(\CoPoint(\Hask), \circ)$ \\
-Fold & ??? \\
-\hline
-\end{tabular}
-\caption{Classes of $\Lens$es used in Haskell}
-\end{figure}
-
-\begin{figure}[b]
-\begin{tikzpicture}[node distance=3.5cm,line width=0.5pt]
-\node(1) at (0,0) {$1$};
-\node(Lens) [above left of =1] {$- \times D$};
-\node(Prism) [above right of =1] {$- \sqcup D$};
-\node(Traversal) [above right of =Lens] {$\Traversable(\Hask)$};
-\node(Setter) [above of =Traversal] {$\Endo(\Hask)$};
-\node(Getter) [above left of =Lens] {$\CoPoint(\Hask)$???};
-\node(Fold)   [above of=Getter] {Fold ???};
-\node(Review) [above right of =Prism] {$\Point(\Hask)$???};
-
-\draw[right hook->](1) -- (Lens);
-\draw[right hook->](1) -- (Prism);
-\draw[right hook->](Lens) -- (Traversal);
-\draw[right hook->](Prism) -- (Traversal);
-\draw[right hook->](Traversal) -- (Fold);
-\draw[right hook->](Lens) -- (Getter);
-\draw[right hook->](Prism) -- (Review);
-\draw[right hook->](Getter) -- (Fold);
-
-\draw[->](Traversal) -- (Review);
-\draw[->](Traversal) -- (Setter);
-
-\end{tikzpicture}
-\caption{Morphisms between various classes of $\Lens$es. Arrows marked with hooks are fully faithful. \todo{figure out if this matters}
-}
-\end{figure}
+\section{Profunctor Optics}
+\section{Optic Families}
+\section{The Challenge of Effectful Optics}
+\section{Indexed Optics}
 
@@
 \bibliographystyle{amsalpha}
-\bibliography{lens}
+\bibliography{optics}
 \end{document}

### 2017-07-17 paper.tex
Some more notes

@@
-\documentclass[11pt,a4paper]{amsart}
+\documentclass[11pt,a4paper]{article}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{mathtools}
-\usepackage{stmaryrd}
-\usepackage{tensor}
+%\usepackage{stmaryrd}
+%\usepackage{tensor}
 \usepackage[mathscr]{eucal}
-\usepackage{marvosym}
+%\usepackage{marvosym}
 \usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
@@
 
-\newcommand{\id}{\mathrm{id}}
-
 \newcommand{\C}{\mathscr{C}}
@@
 
-\newcommand{\Pastro}{\mathrm{Pastro}}
+\newcommand{\Pastro}{\Phi}
+%\newcommand{\Pastro}{\mathrm{Pastro}}
+\newcommand{\Double}{\mathcal{D}}
 
@@
 \newcommand{\Act}{\mathbf{Act}}
+\newcommand{\PreOptic}{\mathbf{PreOptic}}
+\newcommand{\Optic}{\mathbf{Optic}}
 \newcommand{\Lens}{\mathbf{Lens}}
@@
 
+\newcommand{\id}{\mathrm{id}}
 \newcommand{\op}{\mathrm{op}}
-\newcommand{\ob}{\mathrm{ob}\,}
+\newcommand{\const}{\mathrm{const}}
+\DeclareMathOperator{\ob}{ob}
+\DeclareMathOperator{\copr}{copr}
 
-\newcommand{\fget}{\mathrm{get}}
-\newcommand{\fput}{\mathrm{put}}
-\newcommand{\fmodify}{\mathrm{modify}}
+\newcommand{\fget}{\mathrm{\underline{get}}}
+\newcommand{\fput}{\mathrm{\underline{put}}}
+\newcommand{\fmodify}{\underline{\mathrm{modify}}}
 
@@
    \,\smash{\raisebox{-0.65ex}{\ensuremath{\scriptstyle\sim}}}\,}}
+
+\makeatletter
+\providecommand{\leftsquigarrow}{%
+  \mathrel{\mathpalette\reflect@squig\relax}%
+}
+\newcommand{\reflect@squig}[2]{%
+  \reflectbox{$\m@th#1\rightsquigarrow$}%
+}
+\makeatother
 
@@
 \section{Introduction}
+
+\todo{Might have to adjust the entire thing because the action of $\M$ on $\C$ is not strictly monoidal.
+On the other hand, through the entire Pastro/Street paper pretends associativity/etc is strict, so maybe who cares?
+What we really want is just a (nonstrict) monoidal functor $\M \to [\C, \C]$ from some $\M$.}
+
+\todo{There might be a lot more to say in terms of Mike's stuff on framed bicategories.
+The ``external product'' operation on profunctors seems key.
+This could be the mechanism behind the indexed stuff?}
+
+\section{Optics}
+
+\begin{proposition}
+Let $\C$ be a category and $\M$ a subcategory of $[\C, \C]$ closed under composition. There is a category $\PreOptic_\M$ that has the same objects as $\C \times \C$, with homsets given by
+\begin{align*}
+\PreOptic_\M((S, S'), (A, A')) = \int^{M \in \M} \C(S, M A) \times \C(M A', S')
+\end{align*}
+\end{proposition}
+If $f : S \to M A$ and $g : M A' \to S'$, we write $\langle l, r \rangle$ for their image in $\PreOptic_\M((S, S'), (A, A'))$. We will refer to $M$ as the \emph{complement} for the pair $(l, r)$.
+\begin{proof}
+\todo{Following the doubles paper, this should be the Kleisli category for the monad on $\Prof$ given by:
+\begin{align*}
+\Phi(S, S', A, A') = \int^{M \in \M} \C(S, M A) \times \C(M A', S')
+\end{align*}
+}
+
+Explicitly, the composition map
+\begin{align*}
+\int^{M \in \M} \left(\C(S, M A) \times \C(M A', S')\right) \times \int^{M \in \M} \left( \C(R, M S) \times \C(M S', R')\right) \to \int^{M \in \M} \C(R, M A) \times \C(M A', R')
+\end{align*}
+of preoptics is induced by the following morphisms for every $M, N \in \M$:
+\begin{align*}
+&\C(S, M A) \times \C(M A', S') \times \C(R, N S) \times \C(N S', R')\\
+\xrightarrow{\text{functoriality}} \quad& \C(NS, NM A) \times \C(NM A', NS') \times \C(R, N S) \times \C(N S', R')\\
+\xrightarrow{\text{composition}} \quad& \C(R, N M A) \times \C(N M A', R') \\
+\xrightarrow{\copr_{NM}} \quad&\int^{M \in \M} \C(R, M A) \times \C(M A', R')
+\end{align*}
+In other words, let $\langle l, r \rangle \in \PreOptic_\M((R, R'), (S, S'))$ and $\langle l', r' \rangle \in \PreOptic_\M((S, S'), (A, A'))$ with $M$ the complement for $(f, g)$.
+The composite is then: $\langle l', r' \rangle \circ \langle l, r \rangle = \langle (M l')l, r(Mr') \rangle$
+\end{proof}
+
+In \cite{Doubles}, a very similar category was considered.
+The \emph{double} $\Double$ of a monoidal category $(\C, \otimes, I)$ is a special case of the above, where $\M$ is chosen to be all functors of the form $X \otimes (-)$ for $X \in \C$.
+
+\todo{Mention the game theory stuff}
+
+For a fixed $M \in \M$, there is a map $\C(S, M A) \times \C(M A, S) \to \C(S, S)$ given by composition.
+This induces a map $outside : \PreOptic_\M((S, S), (A, A)) \to \C(S, S)$.
+By composition in the other direction we have a map $\C(S, M A) \times \C(M A, S) \to \C(M A, M A)$.
+Including this object $\C(M A, M A)$ into the coend $\int^{M \in \M} \C(M A, M A)$, we induce a map $inside : \PreOptic_\M((S, S), (A,A)) \to \int^{M \in \M} \C(M A, M A)$.
+
+\begin{definition}
+An \emph{optic} from $S$ to $A$ is a preoptic $p$ from $(S, S)$ to $(A, A)$ such that $outside(p) = \id_S$, and $inside(p) = \langle \id_{MA} \rangle$ for some $M \in \M$.
+\end{definition}
+
+\begin{proposition}
+\label{prop-onthenose}
+If $p \in \PreOptic_\M(S, A)$ is an optic, then there exists a representative $p = \langle l, r \rangle$ such that $r \circ l = \id_{MA}$ on the nose for some $M$.
+\end{proposition}
+\begin{proof}
+\todo{This is long and painful but seems important. There may be a more general principle at work here but I couldn't see it.}
+
+\todo{Put in an appendix?}
+
+In fact we will prove the more general statement that for $p \in \PreOptic_\M(S, A)$, if $outside(p) = \id_S$ and $inside(p) = \langle t \rangle$ where $t : MA \to MA$ is idempotent, then we can find a representative $\langle l, r \rangle$ with $l \circ r = t$ on the nose.
+
+There is a well known formula for the coend as the coequaliser in the diagram
+\[
+\begin{tikzcd}
+\coprod_{M \to N} S(N, M) \ar[r,shift left=.75ex]  \ar[r,shift right=.75ex] & \coprod_{M \in \M} S(M, M) \ar[r] & \int^{M \in \M} S(M, M)
+\end{tikzcd}
+\]
+where $S$ is some functor $\M^\op \times \M \to \E$.
+
+In our case $\E = \Set$, and unwinding the coequaliser this states that $\int^{M \in \M} \C(M A, M A)$ is a quotient of the set $\coprod_{M \in \M} \C(M A, M A)$.
+Two morphisms $f : M A \to M A$ and $g : N A \to N A$ are identified when there exists a $k : N A \to M A$ and natural transformation $\phi : M \to N$ such that the diagram
+\[
+\begin{tikzcd}
+M A \ar[r, "\phi_A"] \ar[d, "f", swap] & N A \ar[d, "g"] \ar[dl, "k"] \\
+M A \ar[r, "\phi_A", swap] & N A
+\end{tikzcd}
+\]
+commutes.
+This gives a binary relation $f \rightsquigarrow g$ that is not likely to be symmetric or transitive.
+The coend is obtained by identifying all morphisms related in this way, so in all, $\langle f \rangle = \langle g \rangle$ iff there exists a zigzag $f \leftrightsquigarrow u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n \leftrightsquigarrow g$ where the relation may apply in either direction.
+\todo{replace this with $f = u_1 \leftrightsquigarrow \dots u_n = g$ for clarity}
+
+If $f \rightsquigarrow g$ then $f^2 \rightsquigarrow g^2$: this is clear by stacking the above diagram, and then taking $k' = fk = kg$.
+This argument extends to show that $f^n \rightsquigarrow g^n$ for any $n$.
+
+Similarly unwinding the coequaliser for $\int^{M \in \M} \C(S, M A) \times \C(M A, S)$, two pairs $(l, r) : (S \to M A, MA \to S)$ and $(l', r') : (S \to NA, NA \to S)$ in $\coprod_{M \in \M} \C(S, M A) \times \C(M A, S)$ are identified when there exists a $\phi : M \to N$ such that
+\[
+\begin{tikzcd}
+M A \ar[r, "\phi_A"] \ar[d, "r", swap] & N A \ar[d, "r'"] \\
+S \ar[r, equal] \ar[d, "l", swap] & S \ar[d, "l'"]  \\
+MA \ar[r, "\phi_A"] & N A
+\end{tikzcd}
+\]
+commutes. \todo{split the diagram in the middle?}
+
+We will now prove the result by induction.
+Because $inside(p) = \langle t \rangle$, there is a representative $\langle l, r \rangle$ so that $\langle lr \rangle = \langle t \rangle$.
+There therefore must exist a finite chain of relations $lr \leftrightsquigarrow u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n \leftrightsquigarrow t$.
+Supposing that the first relation faces rightwards, we have a diagram:
+\[
+\begin{tikzcd}
+M A \ar[r, "\phi_A"] \ar[d, "r", swap] & N A \ar[dd, "u_1"] \ar[ddl, "k"] \\
+S \ar[d,"l",swap] & \\
+M A \ar[r, "\phi_A", swap] & N A
+\end{tikzcd}
+\]
+Note that $r = rlr = rk\phi_A$. We therefore have the commutative diagram
+\[
+\begin{tikzcd}
+M A \ar[r, "\phi_A"] \ar[d, "r", swap] & N A \ar[d, "rk"] \\
+S \ar[r, equal] \ar[d, "l", swap] & S \ar[d, "\phi_Al"] \\
+MA \ar[r, "\phi_A", swap] & N A
+\end{tikzcd}
+\]
+where the composite of the morphisms on the right is $\phi_A l r k = \phi_A k \phi_A k = u_1^2$.
+Composing in the other direction we have $r k \phi_A l = rlrl = \id_S$.
+We have shown that whenever $rl = \id_S$ and $lr \rightsquigarrow u_1$, then there exist $l_1$ and $r_1$ so that $r_1l_1 = \id_S$, $l_1r_1 = u_1^2$ and $(l, r) \rightsquigarrow (l_1, r_1)$.
+A symmetric argument shows that if instead $lr \leftsquigarrow g$, there exist $l_1$ and $r_1$ so that $r_1l_1 = \id_S$, $l_1r_1 = u_1^2$ and $(l, r) \leftsquigarrow (l_1, r_1)$.
+
+We can now inductively apply the above argument to the chain $u_1^2 \leftrightsquigarrow \dots \leftrightsquigarrow u_n^2 \leftrightsquigarrow t^2 = t$, obtained by squaring each morphism in the original chain.
+We eventually obtain a chain $(l, r) \leftrightsquigarrow (l_1, r_1)\leftrightsquigarrow \dots \leftrightsquigarrow (l_n, r_n) \leftrightsquigarrow (l_t, r_t)$, where $r_tl_t = \id_S$ and $l_t r_t = t$.
+This pair $(l_t, r_t)$ is the required representative.
+\end{proof}
+
+The above argument has a similar form to those that appear in \cite{OnTheTrace}, which considered (among other things) coends of the form $\int^{c \in \C} \C(c, Fc)$ for an endofunctor $F : \C \to \C$.
+
+In view of this Proposition, whenever we posit a representative $\langle l, r \rangle$ of an optic, we will assume that $l$ and $r$ are mutual two-sided inverses.
+
+\begin{proposition}
+There is an subcategory $\Optic_\M$ of $\PreOptic_\M$ given by objects of the form $(X, X)$ and optics between them.
+\end{proposition}
+\begin{proof}
+The identity preoptic $\langle \id_X, \id_X \rangle$ is clearly an optic.
+Suppose we have two optics $\langle l, r \rangle \in \Optic_\M(R, S)$ and $\langle l', r' \rangle \in \Optic_\M(S, A)$, where $\langle l, r \rangle$ has complement $M$.
+Then the composite $\langle (Ml')l, r (Mr')  \rangle$ is certainly also an optic:
+\begin{align*}
+(Ml')l r (Mr') &= (Ml')(Mr') = M(l'r') = \id
+\intertext{and}
+r (Mr')(Ml')l &= r M(r'l') l = rl = \id
+\end{align*}
+\end{proof}
+
+\subsection{Examples}
+
+\todo{For lenses, not actually the full subcategory of $[\C, \C]$, just morphisms of the form $f \times \id$. This is a disadvantage of doing it as functors and not as an action.}
+
+\subsection{Equivalence of Optics}
+
+One issue with the definition of optic given in the last section is that it could be difficult to determine when two optics $\langle l, r \rangle, \langle l', r' \rangle \in \Optic_\M(S, A)$ are equal.
+For some choices of $\M$, however, we can reduce a zigzag of relations to a single one.
+
+\todo{This may work in general with some huge number of conditions: something like $-A$ reflects monomorphisms and preserves binary coproducts, all subobjects in $\M$ have complements.}
+
+\begin{proposition}
+Suppose all epimorphisms split in $\C$, and that $- \times A : \C \to \C$ reflects epis.
+Then two lenses $p = \langle l, r \rangle$ and $q = \langle l', r' \rangle \in \Optic_\times(S, A)$ with complements $M$ and $N$ respectively are equal iff there exists an morphism $\phi : M \to N$ such that $(\phi \times A)l = l'$ and $r = r' (\phi \times A)$.
+\end{proposition}
+\begin{proof}
+The backward direction is clear: the morphism $\phi$ is a witness that $\langle l, r \rangle \rightsquigarrow \langle l', r' \rangle$, so the two optics are equal.
+
+%note that $p$ and $q$ must have identical $\fget$ and $\fput$ functions:
+%\begin{align*}
+%\fget &= \pi_2 l = \pi_2 l' \\
+%\fput &= r (\pi_1 l \times A) = r' (\pi_1 l' \times A)
+%\end{align*}
+For the forward direction, note that the map $(\pi_1 l \times A)$ is a retraction: it has the section $(r, \pi_2)$:
+\begin{align*}
+(\pi_1 l \times A)(r, \pi_2) = (\pi_1 l r, \pi_2) = (\pi_1, \pi_2) = \id_{S \times A}
+\end{align*}
+Now by assumption, $\pi_1 l : S \to M$ is an epi, so has a retraction $f : M \to S$. The claim is that $\phi = \pi_1 l' f$ is the required morphism $M \to N$.
+
+The situation is summarised in the following diagram, which other than the dashed line, we know commutes.
+\[
+\begin{tikzcd}
+M \times A \ar[r, "{(f, \id_A)}", dashed, bend left = 50] \ar[d, "r", swap] & S \times A \ar[d, "\fput"] \ar[r, "{(\pi_1 l', \id_A)}"] \ar[l, "{(\pi_1 l, \id_A)}", swap] & N \times A \ar[d, "r'"] \\
+S \ar[r, equal] \ar[d, "l", swap] & S \ar[d, "{(\id_S, \fget)}"] \ar[r, equal] & S \ar[d, "l'"] \\
+M \times A & S \times A \ar[r] \ar[l] & N \times A
+\end{tikzcd}
+\]
+We can now calculate:
+\begin{align*}
+r = r(\pi_1 l f \times A) = \fput (f \times A) = r' (\pi_1 l' f \times A) = r'(\phi \times A)
+\end{align*}
+as required. The equation relating $l$ and $l'$ follows immediately as they are the inverses of $r$ and $r'$.
+\end{proof}
+
+The conditions of the above Proposition hold in $\Set$, so long as $A$ is not empty.
+
+% Old attempt:
+%\begin{definition}
+%A functor $F : \C \to \D$ satisfies the \emph{splitting morphism condition} (SM) if, for every $f : A \to B$ in $\C$ such that $Ff$ is a split monomorphism, there exists a $g : B \to A$ such that $F(gf) = \id_{FA}$.
+%
+%Similarly, $F$ satisfies the \emph{splitting epimorphism condition} (SE) if for every $f : A \to B$ in $\C$ such that $Ff$ is a split epimorphism, there exists a $g : B \to A$ such that $F(fg) = \id_{FB}$.
+%\end{definition}
+%
+%These definitions are identical to ones given in a (as far as I can tell totally unrelated) paper on triangulated categories \cite{ObjectiveTriangleFunctors}.
+The conditions are not too difficult to satisfy:
+%
+%\begin{proposition}[\todo{cite}]
+%If $F$ is full then it satisfies (SM) and (SE).
+%\end{proposition}
+%\begin{proof}
+%
+%\end{proof}
+%
+%\begin{proposition}[\todo{cite}]
+%If $F$ is faithful then it satisfies (SM) and (SE).
+%\end{proposition}
+%\begin{proof}
+%
+%\end{proof}
+%
+%\begin{theorem}
+%Suppose we have two optics $\langle l, r \rangle$ and $\langle l', r' \rangle \in \Optic_\M(S, A)$ with complements $M$ and $N$ respectively, and suppose $\M$ has the property that the ``evaluation-at-$A$'' functor $(-A) : \M \to \C$ satisfies (SM) and (SE).
+Then the two optics are equal iff there exists an morphism $\phi : M \to N$ such that $\phi_A l = l'$ and $r = r' \phi_A$.
+%\end{theorem}
+%\begin{proof}
+%The backward direction is clear: the morphism $\phi$ is a witness that $\langle l, r \rangle \rightsquigarrow \langle l', r' \rangle$, so the two optics are equal.
+%
+%For the forward direction, as in Proposition \ref{prop-onthenose} we induct on a zigzag \[(l, r) = (l_1, r_1) \leftrightsquigarrow \dots \leftrightsquigarrow (l_n, r_n) = (l', r'),\] where each pair $(l_i, r_i)$ has complement $M_i$.
+As a base case, we can take the identity $\id_M : M \to M = M_1$.
+Now suppose we already have a morphism $\phi : M \to M_{i-1}$ that satisfies $\phi_A l = l_{i-1}$ and $r = r_{i-1} \phi_A$.
+There are two cases to consider:
+%
+%If $(l_{i-1}, r_{i-1}) \rightsquigarrow (l_i, r_i)$, then by definition we have a $\psi : M_{i-1}\to M_i$ that satisfies the equations $\psi_A l_{i-1} = l_i$ and $r_{i-1} = r_i \psi_A$.
+Therefore the composite $\psi\phi$ satisfies $(\psi\phi)_A l = \psi_A l_{i-1} = l_i$ and $r = r_{i-1} \phi_A = r_i (\psi \phi)_A$, so $\psi\phi : M \to M_i$ is the required morphism.
+%
+%If instead $(l_{i-1}, r_{i-1}) \leftsquigarrow (l_i, r_i)$, we have a morphism in the opposite direction $\psi : M_i \to M_{i-1}$, with $\psi_A l_i = l_{i-1}$ and $r_i = r_{i-1} \psi_A$, as shown in the following commutative diagram
+%\[
+%\begin{tikzcd}
+%M A \ar[r, "\phi_A"] \ar[d, "r", swap] & M_{i-1} A \ar[d, "r_{i-1}"] & M_i A \ar[l, "\psi_A", swap] \ar[d, "r_i"]\\
+%S \ar[r, equal] \ar[d, "l", swap] & S \ar[r, equal] \ar[d, "l_{i-1}"] & S \ar[d, "l_i"] \\
+%M A \ar[r, "\phi_A", swap] & M_{i-1} A & M_i A \ar[l, "\psi_A"]
+%\end{tikzcd}
+%\]
+%To construct a morphism $M \to M_i$ we have to perform a slightly awkward switchback maneuver. First note that $\phi_A$ is a split monomorphism, as $(l r_{i-1}) \phi_A = lr = \id_{MA}$.
+%
+%By condition (SM), therefore, there is a morphism $\gamma : M_{i-1} \to M$ such that $\gamma_A \phi_A = \id_{MA}$. But now, the composite $\gamma_A \psi_A : M_i \to M$ is a split epimorphism:
+%\begin{align*}
+%(\gamma_A \psi_A)(l_i r) = \gamma_A l_{i-1} r = \gamma_A \phi_A l r = \gamma_A \phi_A = \id_{MA}
+%\end{align*}
+%and by condition (SE), there is a morphism $\theta : M \to M_i$ with $\gamma_A \psi_A \theta_A = \id_{MA}$.
+It remains to show that $\theta_A l = l_i$ and $r = r_i \theta_A$.
+First some intermediate steps:
+%\begin{align*}
+%r \gamma_A = r_{i-1} l_{i-1} r \gamma_A = r_{i-1} \phi_A l r \gamma_A = r_{i-1} \phi_A \gamma_A = 
+%\end{align*}
+%So finally:
+%\begin{align*}
+%r &= r \gamma_A \psi_A \theta_A	
+%\end{align*}
+%\todo{picture}
+%\end{proof}
+
 \section{Profunctor Optics}
+
+\subsection{Profunctors}
+
+\todo{recall definitions} We use $I$ to refer to the identity profunctor $\C(-,{=})$, and $\odot$ for horizontal profunctor composition.
+
+\subsection{Tambara Modules}
+The following section generalises definitions that first appeared in \cite{Doubles}.
+\begin{definition}
+Suppose $\C$ is acted on by $\M$, a subcategory of $[\C, \C]$ closed under composition, and let $P \in \Prof(\C, \C)$ be a profunctor.
+A \emph{Tambara module structure for $\M$} on $P$ is a natural family of maps:
+\begin{align*}
+\alpha_{A,B,M} : P(A,B) \to P(MA, MB)
+\end{align*}
+such that $\alpha_{A,B,\id_\C} = \id_{P(A,B)}$, and the following diagram commutes:
+\[
+\begin{tikzcd}
+P(A,B) \ar[r, "\alpha_{A,B,M}"] \ar[dr, "\alpha_{A, B, MN}" below left] & P(MA, MB) \ar[d, "\alpha_{MA, MB, N}" right] \\
+& P(NMA, NMB)
+\end{tikzcd}
+\]
+\end{definition}
+
+Note that the hom profunctor $I := \C(-, =) : \C^\op \times \C \to \Set$ has a canonical Tambara module structure for any $\M$, given by functoriality.
+
+If $P, Q \in \Prof(\C, \C)$ are equipped with module structures $\alpha$ and $\beta$ respectively, there is a canonical module structure on $P \odot Q$.
+Given $M \in \M$ and $A,B \in \C$, the structure map $(\alpha \odot \beta)_{A,B,M}$ is induced by
+\begin{align*}
+&P(A,C) \times Q(C,B)  \\
+\xrightarrow{\alpha_{A,C,M} \times \beta_{C,B,M}} \quad& P(MA, MC) \times Q(MC, MB) \\
+\xrightarrow{\copr_{MC}} \quad&\int^{C \in \C} P(MA, C) \times Q(C, MB) \\
+= \quad&(P \odot Q)(MA, MB)
+\end{align*}
+
+\begin{definition}
+There is a category $\Tamb_\C(\M)$ of Tambara modules and natural transformations that respect the extra structure, in the sense that for any $l : P \to Q$, the diagram
+\[
+\begin{tikzcd}
+P(A,B) \ar[r, "\alpha_{A,B,M}"] \ar[d, "l_{A,B}" left] & P(MA, MB) \ar[d, "l_{MA, MB}" right] \\
+Q(A,B) \ar[r, "\beta_{A,B,M}"] & Q(MA, MB)
+\end{tikzcd}
+\]
+commutes.
+\end{definition}
+
+This category is monoidal with respect to $\odot$ as given above, and the monoidal unit is given by $I$.
+There is an evident forgetful functor $U : \Tamb_\C(\M) \to \Prof(\C, \C)$ that is strong monoidal.
+This forgetful functor has both a left and right adjoint; particularly important for us is the left adjoint:
+
+\begin{definition}
+Let $\Pastro_\M : \Prof(\C, \C) \to \Tamb_\C(\M)$ be the functor \todo{change notation? drop $\C$ if we use the same one the whole time?}
+\begin{align*}
+\Pastro_\M(P) := \int^{M \in \M}  \C(-, M{=}) \odot P \odot \C(M-, {=}) 
+\end{align*}
+Or, in other words, 
+\begin{align*}
+\mathrm{Pastro}_\C(\M)(P)(A,B) := \int^{M \in \M} \int^{C,D \in \C} \C(A, MC) \times P(C,D) \times  \C(MD, B)
+\end{align*}
+The module structure $\alpha_{A,B,M} : \Pastro_\M(P)(A,B) \to \Pastro_\M(P)(MA, MB)
+$ is given by map induced by 
+\begin{align*}
+&\int^{C,D \in \C} \C(A, NC) \times P(C,D) \times  \C(ND, B) \\
+\xrightarrow{\text{functoriality}} \quad& \int^{C,D \in \C} \C(MA, MNC) \times P(C,D) \times  \C(MND, MB) \\
+\xrightarrow{\copr_{MN}} \quad&\int^{N \in \M} \int^{C,D \in \C} \C(MA, NC) \times P(C,D) \times  \C(ND, MB) \\
+= \quad&\Pastro_\M(P)(MA, MB)
+\end{align*}
+for all $N \in \M$.
+\end{definition}
+
+\begin{proposition}
+$\Pastro_\M : \Prof(\C, \C) \to \Tamb_\C(\M)$ is left adjoint to $U : \Tamb_\C(\M) \to \Prof(\C, \C)$.
+\end{proposition}
+\begin{proof}
+\todo{Could crunch through this manually, may be a neat way to do it using techniques from P/S}
+\end{proof}
+
+\begin{corollary}
+$\Pastro_\M$ is oplax monoidal.
+\end{corollary}
+\begin{proof}
+This follows by abstract nonsense as a left adjoint of a strong monoidal functor. \todo{reference?}
+\end{proof}
+
+\subsection{Preoptics}
+
+\begin{definition}
+For an object $A \in \C$, the \emph{exchange profunctor} $E_A$ is defined to be $\C(-, A) \times \C(A, {=})$.
+\end{definition}
+
+Given a profunctor, or indeed a Tambara module, we can evaluate it at any two objects of $\C$.
+This process is functorial in the choice of Tambara module, giving a functor $(U-)(A,A) : \Tamb_\C(\M) \to \Set$.
+
+\begin{lemma}
+\label{lemma-rep}
+The functor $(U-)(A,A) : \Tamb_\C(\M) \to \Set$ is representable: there is a natural isomorphism
+$(U-)(A,A) \cong \Tamb_\C(\M)(\Pastro_\M E_A, -)$
+\end{lemma}
+\begin{proof}
+We have the chain of natural isomorphisms:
+\begin{align*}
+&(U-)(A,A) \\
+\cong \;&\int_{X,Y \in \C} \Set(\C(X,A) \times \C(A,Y), (U-)(X,Y)) && \text{(by Yoneda (un)reduction twice)} \\
+=\;&\int_{X,Y \in \C} \Set(E_A(X,Y), (U-)(X,Y)) && \text{(by definition)}\\
+\cong \;&\Prof(E_A, U-) && \text{(natural transformations as ends)} \\
+\cong \;&\Tamb_\C(\M)(\Pastro_\M E_A, -) && \text{(by adjointness)} 
+\end{align*}
+by the co-Yoneda lemma twice followed by the adjunction $\Pastro_\M \dashv U$.
+\end{proof}
+
+We can now show that profunctor preoptics are precisely preoptics in the ordinary sense.
+
+\begin{proposition}
+\label{prop-profunctor-optics-are-optics}
+\begin{align*}
+[\Tamb_\C(\M), \Set]((U-)(A,A),(U-)(S,S)) &\cong \PreOptic_\M((S, S), (A, A))
+\end{align*}
+\end{proposition}
+\begin{proof}
+We have the chain of isomorphisms:
+\begin{align*}
+&[\Tamb_\C(\M), \Set]((U-)(A,A),(U-)(S,S)) \\
+\cong \;&[\Tamb_\C(\M), \Set](\Tamb_\C(\M)(\Pastro_\M E_A, -), (U-)(S,S))  && \text{(by Lemma \ref{lemma-rep})}\\
+\cong \;&(U\Pastro_\M E_A)(S,S)  && \text{(by Yoneda)} \\
+= \;&\int^{M \in \M} \int^{C,D \in \C} \C(S, MC) \times E_A(C,D) \times \C(MD,S) \\
+= \;&\int^{M \in \M} \int^{C,D \in \C} \C(S, MC) \times \C(C,A) \times \C(A,D) \times \C(MD,S) \\
+\cong \;&\int^{M \in \M} \C(S, MA) \times \C(MA, S)  && \text{(by co-Yoneda twice)} \\
+= \;&\PreOptic_\M((S, S), (A, A))
+\end{align*}
+\todo{This works for $\PreOptic_\M((S, S'), (A, A'))$ just fine, fixing the definition of $E_A$.}
+\end{proof}
+
+\begin{corollary}
+A profunctor preoptic is completely determined by its component at $\Pastro_\M E_A$, and furthermore, this component is determine by its value on $\langle \id_A, \id_A, \id_A, \id_A \rangle \in (U \Pastro_\M E_A)(A, A)$.
+\end{corollary}
+\begin{proof}
+This is the content of the first two isomorphisms above.
+\end{proof}
+
+\subsection{Optics}
+
+The next question is: can we characterise the profunctor preoptics that actually correspond to the lawful optics?
+The plan is to chase through the above isomorphisms to see where the lawful optics end up.
+
+The exchange profunctor has a canonical comonoid structure. The comultiplication $\Delta : E_A \to E_A \odot E_A$ is given by the composite
+\begin{align*}
+&E_A(X,Y) \\
+= \quad& \C(X, A) \times \C(A, Y) \\
+\xrightarrow{[\pi_1, \const_{\id_A}, \const_{\id_A}, \pi_2]} \quad& \C(X, A) \times \C(A, A) \times \C(A, A) \times \C(A, Y) \\
+\xrightarrow{\copr_A} \quad& \int^{C \in \C} \C(X, A) \times \C(A, C) \times \C(C, A) \times \C(A, Y) \\
+= \quad& \int^{C \in \C} E_A(X,C) \times E_A(C,Y) \\
+= \quad&  (E_A \odot E_A)(X,Y)
+\end{align*}
+and the counit $\varepsilon : E_A \to I$ simply composes the two morphisms. Because $\Pastro_\M$ is oplax monoidal, the Tambara module $\Pastro_\M E_A$ has an induced comonoid structure.
+
+\begin{lemma}
+For an object $X$ in a monoidal category $\C$, a comonoid structure $(X,\Delta,\varepsilon)$ is equivalent to a lax monoidal structure on $\C(X, -)$.
+\end{lemma}
+\begin{proof}
+\todo{not hard}
+\end{proof}
+
+Therefore the functor $\Tamb_\C(\M)(\Pastro_\M E_A, -)$ is canonically lax monoidal, and so the isomorphic functor $(U-)(A,A)$ is also.
+
+\begin{proposition}
+Any optic $p : (U-)(A,A) \to (U-)(S,S)$ is a lax monoidal transformation with respect to Tambara module composition in the domain and the cartesian product in the codomain.
+\end{proposition}
+\begin{proof}
+The final few isomorphisms used in Proposition \ref{prop-profunctor-optics-are-optics} are essentially window dressing. Suppose we have an element of 
+\begin{align*}
+(U\Pastro_\M E_A)(S,S) = \int^{M \in \M} \int^{C,D \in \C} \C(S, MC) \times E_A(C,D) \times \C(MD,S)
+\end{align*}
+and let $\phi : (U\Pastro_\M E_A)(S,S) \cong \PreOptic_\M((S, S), (A, A))$ be the isomorphism given in the proposition.
+If we have an element of $(U\Pastro_\M E_A)(S,S)$ with representative $\langle l, e_1, e_2, r \rangle$, the round-trip through the isomorphism $\phi$ yields $\langle (M e_1)l, \id_A, \id_A, r(M e_2)\rangle$.
+Hence we may always assume we have a representative of the form $\langle l, \id_A, \id_A, r \rangle$.
+This representative corresponds to an optic via the isomorphism $\phi$ iff both $rl = \id_S$ and $\langle lr\rangle = \langle \id_{NA} \rangle$ in $\int^{M \in \M} \C(M A, M A)$.
+Note that just as we can ``strictify'' a representative of an optic, if we have an element of $(U\Pastro_\M E_A)(S,S)$ that corresponds to an optic we may always choose a representative so that the latter identity holds on the nose.
+
+Now, by the definition of the Yoneda isomorphism, a natural transformation \[ \Tamb_\C(\M)(\Pastro_\M E_A, -) \to (U-)(S,S) \] will correspond to an optic iff the image of the identity morphism in $(U\Pastro_\M E_A)(S, S)$ corresponds to an optic.
+The very first isomorphism in Proposition \ref{prop-profunctor-optics-are-optics} is given by precomposition by the isomorphism of Lemma \ref{lemma-rep}, so in all, a profunctor preoptic $p : (U-)(A, A) \to (U-)(S,S)$ is a lawful optic iff $p(\langle \id_A, \id_A, \id_A, \id_A \rangle)$ is an optic in $(U\Pastro_\M E_A)(S, S)$.
+Our goal is to show that this happens exactly when the natural transformation is monoidal.
+
+Let $\langle l, \id_A, \id_A, r \rangle = p(\langle \id_A, \id_A, \id_A, \id_A \rangle)$ be a representative, where $l : S \to M A$ and $r : M A \to S$.
+We can calculate the component of $p$ at a Tambara module $P$ explicitly:
+\begin{align*}
+p_P = (UP)(l,r) \alpha_{A,A,M}
+\end{align*}
+where $\alpha$ is the module structure for $P$.
+
+To show $p$ is monoidal, we must show that both diagrams
+\[
+\begin{tikzcd}
+UP(A,A) \times UQ(A,A) \ar[r, "p_P \times p_Q"] \ar[d, swap] & UP(S, S) \times UQ(S, S)  \ar[d] \\
+U(P \odot Q)(A,A)  \ar[r, "p_{P \odot Q}", swap] & U(P \odot Q)(S,S)
+\end{tikzcd}
+\]
+and
+\[
+\begin{tikzcd}
+1 \ar[d] \ar[dr] & \\
+UI(A,A)  \ar[r, "p_I", swap] & UI(S,S)
+\end{tikzcd}
+\]
+commute. For the first we have
+\begin{align*}
+\langle (p_P \times p_Q)(x, y) \rangle &= \langle (UP)(l,r) \alpha_{A,A,M} x,  (UQ)(l,r) \beta_{A,A,M} y\rangle \\
+&= \langle (UP)(l,lr) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(by the coend relations \todo{more carefully})} \\
+&= \langle (UP)(l,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $lr = \id_{MA}$)} \\
+&= (U(P \odot Q))(l,r) \langle \alpha_{A,A,M} x, \beta_{A,A,M} y \rangle && \text{(by definition of $P \odot Q$)} \\
+&= (U(P \odot Q))(l,r) (\alpha_{A,A,M} \odot \beta_{A,A,M}) \langle x, y \rangle && \text{(by definition of $\alpha \odot \beta$)} \\
+&= p_{P \odot Q} \langle x, y \rangle
+\end{align*}
+And for the second:
+\begin{align*}
+p_I(\id_A) = (UI)(l,r) (M \id_A) = r \id_{MA} l = rl = \id_S
+\end{align*}
+as required.
+\end{proof}
+
+\todo{I don't see why the converse should be true in general, but it seems to be true in specific situations:}
+
+\begin{proposition}
+Suppose $p \in \Optic_\times(S,A)$ is a pre-lens such that the associated natural transformation $p : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal. Then $p$ is a lens.
+\end{proposition}
+\begin{proof}
+\todo{Show that it satisfies the getput, putget and putput laws. This strategy works only with $\times$ and in $\Set$.}
+\end{proof}
+
+% \section{Degenerate Optics}
 \section{Optic Families}
-\section{The Challenge of Effectful Optics}
 \section{Indexed Optics}
 
-\nocite{*}
-\bibliographystyle{amsalpha}
-\bibliography{optics}
+\todo{These maybe involve profunctors from $\D \times \C$ to $\C$ where the composition does something funny with $\D$.}
+
+%\section{Merely Well-Behaved Optics}
+\section{The Challenge of Effectful Optics}
+%\section{Symmetric Optics}
+
+\bibliographystyle{alpha}
+\bibliography{optics.bib}
 \end{document}

### 2017-07-19 paper.tex
Some more pottering around

@@
 \documentclass[11pt,a4paper]{article}
-\usepackage[utf8]{inputenc}
+%\usepackage[utf8]{inputenc}
 \usepackage{amsthm}
@@
 \usepackage[mathscr]{eucal}
+\usepackage{url}
 %\usepackage{marvosym}
@@
 
+\newcommand{\bN}{\mathbb{N}}
+\newcommand{\bZ}{\mathbb{Z}}
+
 \newcommand{\Pastro}{\Phi}
@@
 
+% Categories
 \newcommand{\Set}{\mathbf{Set}}
@@
 \newcommand{\Optic}{\mathbf{Optic}}
+\newcommand{\SemiOptic}{\mathbf{SemiOptic}}
 \newcommand{\Lens}{\mathbf{Lens}}
@@
 
-\newcommand{\fget}{\mathrm{\underline{get}}}
-\newcommand{\fput}{\mathrm{\underline{put}}}
-\newcommand{\fmodify}{\underline{\mathrm{modify}}}
+\newcommand{\fget}{\textsc{Get}}
+\newcommand{\fput}{\textsc{Put}}
+\newcommand{\fmodify}{\textsc{Modify}}
 
-\newcommand{\todo}[1]{\textcolor{red}{\small #1}}
-
+% Special arrows
 \newcommand{\isoto}{\xrightarrow{
    \,\smash{\raisebox{-0.65ex}{\ensuremath{\scriptstyle\sim}}}\,}}
-
+\newcommand{\hto}{\ensuremath{\,\mathaccent\shortmid\rightarrow\,}}
 \makeatletter
@@
 \makeatother
+
+% Draft helpers
+\newcommand{\todo}[1]{\textcolor{red}{\small #1}}
+
+\newif\ifhideproofs
+%\hideproofstrue %uncomment to hide proofs
+\ifhideproofs
+\usepackage{environ}
+\NewEnviron{hide}{}
+\let\proof\hide
+\let\endproof\endhide
+\fi
 
@@
 On the other hand, through the entire Pastro/Street paper pretends associativity/etc is strict, so maybe who cares?
-What we really want is just a (nonstrict) monoidal functor $\M \to [\C, \C]$ from some $\M$.}
+What we really want is just a (non-strict) monoidal functor $\M \to [\C, \C]$ from some $\M$.}
 
-\todo{There might be a lot more to say in terms of Mike's stuff on framed bicategories.
-The ``external product'' operation on profunctors seems key.
-This could be the mechanism behind the indexed stuff?}
+\todo{People to credit:
+\begin{itemize}
+\item The Haskell lens people: edwardk, shachaf, xplat, roconnor... (TODO: find out who these people are)
+\item The Doubles paper
+\item Bartosz's blog post which was written about the same time I started this. (Only tensor-like optics, no discussion of laws, confusion about enrichment(?))
+\item The profunctor optics paper out of Oxford. (No generality, nothing categorical, no discussion of laws)
+\end{itemize}
+}
 
+\todo{Contributions:
+\begin{itemize}
+\item ...
+\end{itemize}
+}
+
+\todo{Introduction should include:
+\begin{itemize}
+\item Previous attempts to generalise optics
+\item ...
+\end{itemize}
+}
+
+\subsection{Notation}
+\todo{I am open to changing any/all of these}
+\begin{itemize}
+\item Given $f : A \to B$ and $g : A \to C$, I write $[f, g] : A \to B \times C$.
+\item Given $f : A \to B$ and $g : C \to D$, I write $f \times g : A \times C \to B \times D$.
+\item Given a $x \in P(C, C)$, I write $\langle x \rangle \in \int^C P(C, C)$ for its image, and $\copr_C : P(C,C) \to \int^C P(C, C)$
+\end{itemize}
 \section{Optics}
@@
 \begin{proposition}
-Let $\C$ be a category and $\M$ a subcategory of $[\C, \C]$ closed under composition. There is a category $\PreOptic_\M$ that has the same objects as $\C \times \C$, with homsets given by
+Let $\C$ be a category and $\M$ a monoidal category that acts on $\C$. There is a category $\PreOptic_\M$ that has the same objects as $\C \times \C$, with homsets given by
 \begin{align*}
@@
 \end{proposition}
-If $f : S \to M A$ and $g : M A' \to S'$, we write $\langle l, r \rangle$ for their image in $\PreOptic_\M((S, S'), (A, A'))$. We will refer to $M$ as the \emph{complement} for the pair $(l, r)$.
+To distinguish these from morphisms in $\C$, we will write preoptics with a crossed arrow: $p : (S, S') \hto (A, A')$.
+
+If $f : S \to M A$ and $g : M A' \to S'$, we write $\langle l, r \rangle$ for their image in $\PreOptic_\M((S, S'), (A, A'))$.
+We will refer to $M$ as the \emph{complement} for the representative $\langle l, r \rangle$.
 \begin{proof}
@@
 \end{align*}
-In other words, let $\langle l, r \rangle \in \PreOptic_\M((R, R'), (S, S'))$ and $\langle l', r' \rangle \in \PreOptic_\M((S, S'), (A, A'))$ with $M$ the complement for $(f, g)$.
+In other words, let $\langle l, r \rangle : (R, R') \hto (S, S')$ and $\langle l', r' \rangle : (S, S') \hto (A, A')$ with $M$ the complement for $\langle l, r \rangle$.
 The composite is then: $\langle l', r' \rangle \circ \langle l, r \rangle = \langle (M l')l, r(Mr') \rangle$
@@
 \label{prop-onthenose}
-If $p \in \PreOptic_\M(S, A)$ is an optic, then there exists a representative $p = \langle l, r \rangle$ such that $r \circ l = \id_{MA}$ on the nose for some $M$.
+If $p : (S,S) \hto (A,A)$ is an optic, then there exists a representative $p = \langle l, r \rangle$ such that $r \circ l = \id_{MA}$ on the nose for some $M$.
 \end{proposition}
@@
 
-In fact we will prove the more general statement that for $p \in \PreOptic_\M(S, A)$, if $outside(p) = \id_S$ and $inside(p) = \langle t \rangle$ where $t : MA \to MA$ is idempotent, then we can find a representative $\langle l, r \rangle$ with $l \circ r = t$ on the nose.
+In fact we will prove the more general statement that for $p : (S,S) \hto (A,A)$, if $outside(p) = \id_S$ and $inside(p) = \langle t \rangle$ where $t : MA \to MA$ is idempotent, then we can find a representative $\langle l, r \rangle$ with $l \circ r = t$ on the nose.
 
@@
 The identity preoptic $\langle \id_X, \id_X \rangle$ is clearly an optic.
-Suppose we have two optics $\langle l, r \rangle \in \Optic_\M(R, S)$ and $\langle l', r' \rangle \in \Optic_\M(S, A)$, where $\langle l, r \rangle$ has complement $M$.
+Suppose we have two optics $\langle l, r \rangle : R \hto S$ and $\langle l', r' \rangle : S \hto A$ with complements $M$ and $N$ respectively.
 Then the composite $\langle (Ml')l, r (Mr')  \rangle$ is certainly also an optic:
 \begin{align*}
-(Ml')l r (Mr') &= (Ml')(Mr') = M(l'r') = \id
+(Ml')l r (Mr') &= (Ml')(Mr') = M(l'r') = \id_{MNA}
 \intertext{and}
-r (Mr')(Ml')l &= r M(r'l') l = rl = \id
+r (Mr')(Ml')l &= r M(r'l') l = rl = \id_S
 \end{align*}
@@
 
-\todo{For lenses, not actually the full subcategory of $[\C, \C]$, just morphisms of the form $f \times \id$. This is a disadvantage of doing it as functors and not as an action.}
+\subsubsection{Lenses}
+
+Lenses form the ur-example of optics.
+
+\begin{definition}
+Suppose $\C$ has finite products, and let $\C$ act on itself via the bifunctor $\times : \C \times \C \to \C$.
+The \emph{category of lenses} in $\C$ is the category of optics with respect to this action: $\Lens = \Optic_\times$.
+\end{definition}
+
+As remarked in the introduction \todo{(todo: remark in the introduction)}, the preoptics for this action are exactly pairs of $\fget$ and $\fput$ functions.
+\begin{align*}
+\PreOptic_\M((S, S), (A, A)) &= \int^{M \in \M} \C(S, M \times A) \times \C(M \times A, S) \\
+&\cong \int^{M \in \M} \C(S, M) \times \C(S, A) \times \C(M \times A, S) && \text{(universal property of product)} \\
+&\cong \C(S, A) \times \C(S \times A, S) && \text{(co-Yoneda)}
+\end{align*}
+
+Explicitly, given a prelens $\langle l, r \rangle : S \hto A$ these are given by $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
+Conversely, given $\fget$ and $\fput$, the corresponding element in the coend has representative $\langle l, r \rangle$, where $l = [\id_s, \fget]$ and $r = \fput$.
+Note that even if the $\fget$ and $\fput$ correspond to a law-abiding lens, this particular representative will not be an isomorphism.
+
+\todo{talk about ``constant complement'' idea}
+
+\begin{proposition}
+If $\langle l, r \rangle : S \hto A$ is a lens then the associated $\fget$ and $\fput$ functions satisfy the $\fget\fput$, $\fput\fget$ and $\fput\fput$ laws.
+\end{proposition}
+\begin{proof}
+\todo{Straightforward, written out at \cite{IsomorphismLensesPost}, definitely not the origin.}
+\end{proof}
+
+In favourable conditions, the converse holds as we can construct a complement:
+
+\begin{proposition}
+\todo{This is a guess:} Suppose $\C$ has finite limits and coequalisers, and that there is a morphism $1 \to A$.
+Then if $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the three lens laws then the corresponding $\langle l, r \rangle : S \hto A$ is a lens.
+\end{proposition}
+\begin{proof}
+\todo{would be nice if this were true}
+\end{proof}
+
+In particular, this holds in $\Set$ so long as $A$ is not empty. In \cite[Corollary 13]{AlgebrasAndUpdateStrategies} a similar fact is proven for lenses expressed as algebras for a particular monad.
+
+\subsubsection{Prisms}
+\subsubsection{Traversals}
+\subsubsection{Setters}
 
@@
 
-One issue with the definition of optic given in the last section is that it could be difficult to determine when two optics $\langle l, r \rangle, \langle l', r' \rangle \in \Optic_\M(S, A)$ are equal.
+One issue with the definition of optic given in the last section is that it could be difficult to determine when two optics $\langle l, r \rangle, \langle l', r' \rangle : S \hto A$ are equal.
 For some choices of $\M$, however, we can reduce a zigzag of relations to a single one.
@@
 Suppose all epimorphisms split in $\C$, and that $- \times A : \C \to \C$ reflects epis.
-Then two lenses $p = \langle l, r \rangle$ and $q = \langle l', r' \rangle \in \Optic_\times(S, A)$ with complements $M$ and $N$ respectively are equal iff there exists an morphism $\phi : M \to N$ such that $(\phi \times A)l = l'$ and $r = r' (\phi \times A)$.
+Then two lenses $\langle l, r \rangle$ and $\langle l', r' \rangle :  S \hto A$ with complements $M$ and $N$ respectively are equal iff there exists an morphism $\phi : M \to N$ such that $(\phi \times A)l = l'$ and $r = r' (\phi \times A)$.
 \end{proposition}
@@
 
-\todo{recall definitions} We use $I$ to refer to the identity profunctor $\C(-,{=})$, and $\odot$ for horizontal profunctor composition.
+\todo{recall definitions} We use $I$ to refer to the identity profunctor $\C(-,{=})$, and $\odot$ for horizontal profunctor composition. Profunctor composition is written in diagramatic order.
 
@@
 \begin{proof}
-This follows by abstract nonsense as a left adjoint of a strong monoidal functor. \todo{reference?}
+This follows abstractly as a left adjoint of a strong monoidal functor. \todo{reference?}
 \end{proof}
@@
 \end{align*}
-by the co-Yoneda lemma twice followed by the adjunction $\Pastro_\M \dashv U$.
 \end{proof}
@@
 \begin{corollary}
-A profunctor preoptic is completely determined by its component at $\Pastro_\M E_A$, and furthermore, this component is determine by its value on $\langle \id_A, \id_A, \id_A, \id_A \rangle \in (U \Pastro_\M E_A)(A, A)$.
+A profunctor preoptic is completely determined by its component at $\Pastro_\M E_A$, and furthermore, this component is determined by its value on $\langle \id_A, \id_A, \id_A, \id_A \rangle \in (U \Pastro_\M E_A)(A, A)$.
 \end{corollary}
@@
 \begin{proposition}
-Suppose $p \in \Optic_\times(S,A)$ is a pre-lens such that the associated natural transformation $p : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal. Then $p$ is a lens.
+Suppose $p : S \hto A$ is a pre-lens such that the associated natural transformation $p : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal. Then $p$ is a lens.
 \end{proposition}
@@
 
-% \section{Degenerate Optics}
-\section{Optic Families}
+\section{Degenerate Optics}
+% \section{Optic Families}
 \section{Indexed Optics}
+\todo{
+This possibly looks like
+\begin{align*}
+\int^{M \in \M} \C(S, M(IA)) \times \C(M A', S')
+\end{align*}
+with another monoidal action $I$. The $I$ would need to distribute over $M$ in some way.
+}
+\section{Merely Well-Behaved Optics}
+\todo{
+The lenses that the UPenn crew look at are less restricted. They obey the $\fput\fget$ and $\fget\fput$ laws but not the $\fput\fput$ law. 
+}
 
-\todo{These maybe involve profunctors from $\D \times \C$ to $\C$ where the composition does something funny with $\D$.}
+\begin{example}
+The following example is taken from \cite{AClearPictureOfLensLaws}. The ``change counter'' lens $\bN \times A \hto A$ for a set $A$ has $\fput$ and $\fget$ given by:
+\begin{align*}
+\fget(n, a) &= a \\
+\fput((n, a), a') &= \begin{cases}
+(n, a) & \text{if } a = a' \\
+(n+1, a') & \text{otherwise}
+\end{cases}
+\end{align*}
+This example is typical of (merely) well-behaved lenses: there is metadata carried along with the target of a lens that mutates as the lens is used.
+\end{example}
 
-%\section{Merely Well-Behaved Optics}
+\begin{proposition}
+A pre-lens $p : S \hto A$ obeys the $\fput\fget$ and $\fget\fput$ laws iff $outside(p) = \id_S$ and $inside(p) = \langle t \times A \rangle$.
+\end{proposition}
+\begin{proof}
+\todo{I haven't actually checked this yet}
+\end{proof}
+
+This suggests the following definition of merely well-behaved optics, which we \todo{may as well} call semi-optics.
+
+\begin{definition}
+A \emph{semioptic} is a preoptic $p : S \hto A$ such that that $outside(p) = \id_S$ and $inside(p) = \langle t_A \rangle$ for some $t : M \to M$.
+\end{definition}
+
+Note that $t_A$ is necessarily idempotent, so if the ``evaluation-at-$A$'' functor is faithful then $t$ itself is idempotent.
+
+\begin{proposition}
+There is an subcategory $\SemiOptic_\M$ of $\PreOptic_\M$ given by objects of the form $(X, X)$ and semioptics between them.
+\end{proposition}
+
 \section{The Challenge of Effectful Optics}
-%\section{Symmetric Optics}
+
+Past attempts \cite{ReflectionsOnMonadicLenses} to define effectful lenses have wrapped the result of one or both of $\fget$ and $\fput$ with a monad.
+This seems to me a bit ad-hoc; it is not obvious what the laws ought to be, and there is no clear generalisation to other varieties of optic.
+The definition of optic given in this paper suggests we instead set $\C$ to be the Kleisli category for some monad.
+
+\section{The Double-Categorical Perspective}
+
+\todo{There might be a lot more to say in terms of Mike's stuff on framed bicategories.
+The ``external product'' operation on profunctors seems key.
+This could be the mechanism behind the indexed stuff?}
+
+\section{Conclusion}
 

### 2017-07-20 paper.tex
lens laws imply optic

@@
 \begin{itemize}
-\item Given $f : A \to B$ and $g : A \to C$, I write $[f, g] : A \to B \times C$.
+\item Given $f : A \to B$ and $g : A \to C$, I write $[f, g] : A \to B \times C$ and $!_A : A \to 1$.
 \item Given $f : A \to B$ and $g : C \to D$, I write $f \times g : A \times C \to B \times D$.
@@
 
-In favourable conditions, the converse holds as we can construct a complement:
+In favourable conditions, we can show the converse holds by constructing a complement. This is similar to the result proved in \cite[Corollary 13]{AlgebrasAndUpdateStrategies} for $\Set$.
+
+\begin{lemma}
+\todo{maybe delete this lemma, not so important}
+Suppose $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the $\fget\fput$, $\fput\fget$ and $\fput\fput$ laws.
+If we have $x_1, x_2 : 1 \to A$.
+Then the pullbacks $\fget^*(x_1)$ and $\fget^*(x_2)$ are isomorphic.
+\end{lemma}
+\begin{proof}
+We construct a map $f : \fget^*(x_2) \to \fget^*(x_1)$ as the induced map in the diagram
+\[
+\begin{tikzcd}
+\fget^*(x_2) \ar[ddr, bend right = 20] \ar[dr, dashed] \ar[r, "{[x_2^*, x_1 !]}"] & S \times A \ar[dr, "\fput"] & \\
+& \fget^*(x_1) \ar[r, swap] \ar[d] \arrow[dr, phantom, "\lrcorner", very near start] & S \ar[d, "\fget"] \\
+& 1\ar[r, "x_1", swap] & A
+\end{tikzcd}
+\]
+That the outside composite commutes is exactly the $\fput\fget$ law. Similarly, we have a map $g : \fget^*(x_1) \to \fget^*(x_2)$.
+
+\todo{they are inverses by the other laws}
+\end{proof}
 
 \begin{proposition}
-\todo{This is a guess:} Suppose $\C$ has finite limits and coequalisers, and that there is a morphism $1 \to A$.
-Then if $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the three lens laws then the corresponding $\langle l, r \rangle : S \hto A$ is a lens.
+Suppose $\C$ has finite limits and that there is a morphism $x : 1 \to A$.
+Then if $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the three lens laws then the corresponding $p : S \hto A$ is a lens.
 \end{proposition}
 \begin{proof}
-\todo{would be nice if this were true}
+Set $C$ to be the pullback of $\fget$ along $x$, so there is a map $i : C \to S$ with $\fget \, i = x !_C$. There is also a map $j : S \to C$ induced by the following diagram:
+\[
+\begin{tikzcd}
+S \ar[ddr, bend right = 20] \ar[dr, "j", dashed] \ar[r, "{[\id_S, x !_S]}"] & S \times A \ar[dr, "\fput"] & \\
+& C \ar[r, "i"] \ar[d] \arrow[dr, phantom, "\lrcorner", very near start] & S \ar[d, "\fget"] \\
+& 1\ar[r, "x", swap] & A
+\end{tikzcd}
+\]
+which commutes by the $\fput\fget$ law. Note that $ji = \id_C$ by the universal property of pullbacks. Now the commutative diagram
+\[
+\begin{tikzcd}
+C \times A \ar[r, "i \times A"] \ar[d, "\fput (i \times A)", swap] & S \times A \ar[d, "\fput"] \\
+S \ar[r, equal] \ar[d, "{[j,\fget]}", swap] & S \ar[d, "{[\id_S, \fget]}"]  \\
+C \times A \ar[r, "i \times A", swap] & S \times A
+\end{tikzcd}
+\]
+is a witness that $\langle \fput (i \times A), [j,\fget] \rangle = \langle \fput, [\id_S, \fget] \rangle$ as elements of $\PreOptic_\M((S, S), (A, A))$.
+It remains to show that the maps on the left are mutual inverses:
+\begin{align*}
+\fput (i \times A)[j,\fget] &= \fput [ij,\fget] \\
+&= \fput [\fput [\id_S, x!_S],\fget] && \text{(by definition of $j$)} \\
+&= \fput [\id_S,\fget] && \text{(by $\fput\fput$)} \\
+&= \id_S && \text{(by $\fget\fput$)}
+\intertext{and}
+[j,\fget]\fput (i \times A) &= [j\fput (i \times A),\fget\,\fput (i \times A)] && \text{(by universal property of product)} \\
+&= [j\fput (i \times A), \pi_2 (i \times A)] && \text{(by $\fput\fget$)} \\
+&= [j\fput (i \times A), \pi_2] && \\
+&= [jij\fput (i \times A), \pi_2] && \\
+&= [j\fput [\id_S,x !_S] \fput (i \times A), \pi_2] && \\
+&= [j\fput [\id_S, x !_S] \pi_1 (i \times A), \pi_2] && \text{(by $\fput\fput$ \todo{todo: detail})}\\
+&= [jij \pi_1 (i \times A), \pi_2] && \\
+&= [jiji \pi_1, \pi_2] && \\
+&= [\pi_1, \pi_2] && \\
+&= \id_{C \times A}
+\end{align*}
+Therefore $\langle \fput (i \times A), [j,\fget] \rangle$ is an optic, so  $\langle \fput, [\id_S, \fget] \rangle$ is an optic, as we were hoping to show. \todo{maybe do the above in pictures}
 \end{proof}
-
-In particular, this holds in $\Set$ so long as $A$ is not empty. In \cite[Corollary 13]{AlgebrasAndUpdateStrategies} a similar fact is proven for lenses expressed as algebras for a particular monad.
 
@@
 \begin{tikzcd}
-M \times A \ar[r, "{(f, \id_A)}", dashed, bend left = 50] \ar[d, "r", swap] & S \times A \ar[d, "\fput"] \ar[r, "{(\pi_1 l', \id_A)}"] \ar[l, "{(\pi_1 l, \id_A)}", swap] & N \times A \ar[d, "r'"] \\
-S \ar[r, equal] \ar[d, "l", swap] & S \ar[d, "{(\id_S, \fget)}"] \ar[r, equal] & S \ar[d, "l'"] \\
+M \times A \ar[r, "{f \times A}", dashed, bend left = 50] \ar[d, "r", swap] & S \times A \ar[d, "\fput"] \ar[r, "{\pi_1 l' \times A}"] \ar[l, "{\pi_1 l \times A}", swap] & N \times A \ar[d, "r'"] \\
+S \ar[r, equal] \ar[d, "l", swap] & S \ar[d, "{[\id_S, \fget]}"] \ar[r, equal] & S \ar[d, "l'"] \\
 M \times A & S \times A \ar[r] \ar[l] & N \times A

### 2017-07-21 paper.tex
Thinking about semioptics

@@
 }
+A lens from $S$ to $A$ is a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$ that typically obeys three laws (whose names are in diagrammatic order):
+\begin{itemize}
+\item ``$\fput\fget$'': $\fget \; \fput = \pi_2$ as maps $S \times A \to A$, so that any update to $A$ should be \todo{represented faithfully in $S$},
+\item ``$\fget\fput$'': $\fput [\id_S, \fget] = \id_S$ as maps $S \to S$, so that if $A$ is not changed then $S$ should not change; and,
+\item ``$\fput\fput$'': $\fput (\fput \times \id_A) = \fput \, \pi_{1, 3}$ as maps $S \times A \times A \to S$, so any update to $A$ completely overwrites previous updates.
+\end{itemize}
+
+\todo{talk about ``constant complement'' idea}
 
@@
 \begin{tikzcd}
-\coprod_{M \to N} S(N, M) \ar[r,shift left=.75ex]  \ar[r,shift right=.75ex] & \coprod_{M \in \M} S(M, M) \ar[r] & \int^{M \in \M} S(M, M)
+\coprod_{M \to N} P(N, M) \ar[r,shift left=.75ex]  \ar[r,shift right=.75ex] & \coprod_{M \in \M} P(M, M) \ar[r] & \int^{M \in \M} P(M, M)
 \end{tikzcd}
@@
 
-\todo{talk about ``constant complement'' idea}
-
 \begin{proposition}
+\label{prop-OpticImpliesLensLaws}
 If $\langle l, r \rangle : S \hto A$ is a lens then the associated $\fget$ and $\fput$ functions satisfy the $\fget\fput$, $\fput\fget$ and $\fput\fput$ laws.
@@
 \begin{proof}
-\todo{Straightforward, written out at \cite{IsomorphismLensesPost}, definitely not the origin.}
+Let $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$. Verification of the laws is straightforward:
+\begin{align*}
+\fget \; \fput 
+&= \pi_2 l r (\pi_1 l \times A) \\
+&= \pi_2 (\pi_1 l \times A) \\
+&= \pi_2 \\
+\fput [\id_S, \fget] 
+&= r (\pi_1 l \times A) [\id_S, \pi_2 l] \\
+&= r [\pi_1 l, \pi_2 l] \\
+&= rl \\
+&= \id_S \\
+\fput (\fput \times A) 
+&= r (\pi_1 l \times A) (r (\pi_1 l \times A) \times A) \\
+&= r (\pi_1 l  r (\pi_1 l \times A) \times A) \\
+&= r (\pi_1 (\pi_1 l \times A) \times A) \\
+&= r (\pi_1 l \times A) \pi_{1,3} \\
+&= \fput \, \pi_{1, 3}
+\end{align*}
+
+\todo{Written out at \cite{IsomorphismLensesPost}, definitely not the first place though.}
 \end{proof}
@@
 \end{align*}
-Therefore $\langle \fput (i \times A), [j,\fget] \rangle$ is an optic, so  $\langle \fput, [\id_S, \fget] \rangle$ is an optic, as we were hoping to show. \todo{maybe do the above in pictures}
+Therefore $\langle \fput (i \times A), [j,\fget] \rangle$ is a lens, so  $\langle \fput, [\id_S, \fget] \rangle$ is a lens as we were hoping to show. \todo{maybe do the above in pictures}
 \end{proof}
@@
 
+\begin{example}
+A minimal example is the following:
+\begin{align*}
+\fget : \{A,B,C\} &\to \{X, Y\} \\
+A &\mapsto X \\
+B &\mapsto X \\
+C &\mapsto Y 
+\end{align*}
+\begin{align*}
+\fput : \{A,B,C\} \times \{X, Y\} &\to \{A,B,C\} \\
+(A,X) &\mapsto A \\
+(B,X) &\mapsto B \\
+(C,X) &\mapsto B \\
+(A,Y) &\mapsto C \\
+(B,Y) &\mapsto C \\
+(C,Y) &\mapsto C
+\end{align*}
+\end{example}
+
+\todo{THE FOLLOWING IS TOTALLY WRONG, does not capture the right thing, fails for the above example}
+
 \begin{proposition}
-A pre-lens $p : S \hto A$ obeys the $\fput\fget$ and $\fget\fput$ laws iff $outside(p) = \id_S$ and $inside(p) = \langle t \times A \rangle$.
+Suppose the pre-lens $\langle l, r \rangle : S \hto A$ satisfies $rl = \id_S$ and $\langle lr \rangle = \langle t \times A \rangle$ as an element of $\int^{M \in \M} \C(M \times A, M \times A)$.
+Then $p$ obeys the $\fput\fget$ and $\fget\fput$ laws.
 \end{proposition}
 \begin{proof}
-\todo{I haven't actually checked this yet}
+This is nearly identical to Proposition \ref{prop-OpticImpliesLensLaws}. As was mentioned in the proof of Proposition \ref{prop-onthenose}, we may assume that $lr = t \times A$ on the nose.
+
+Now, again letting $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$,
+\begin{align*}
+\fget \; \fput 
+&= \pi_2 l r (\pi_1 l \times A) \\
+&= \pi_2 (t \times A) (\pi_1 l \times A) \\
+&= \pi_2 (t \pi_1 l \times A) \\
+&= \pi_2 \\
+\fput [\id_S, \fget] 
+&= r (\pi_1 l \times A) [\id_S, \pi_2 l] \\
+&= r [\pi_1 l, \pi_2 l] \\
+&= rl \\
+&= \id_S
+\end{align*}
+\end{proof}
+
+\begin{proposition}
+The converse is true.
+\end{proposition}
+\begin{proof}
+
 \end{proof}
@@
 Past attempts \cite{ReflectionsOnMonadicLenses} to define effectful lenses have wrapped the result of one or both of $\fget$ and $\fput$ with a monad.
-This seems to me a bit ad-hoc; it is not obvious what the laws ought to be, and there is no clear generalisation to other varieties of optic.
+This approach is a little ad-hoc; it is not obvious what the laws ought to be and there is no clear generalisation to other varieties of optic.
 The definition of optic given in this paper suggests we instead set $\C$ to be the Kleisli category for some monad.

### 2017-07-26 paper.tex
Start filling out Prisms and Setters

@@
 \newcommand{\Lens}{\mathbf{Lens}}
+\newcommand{\Prism}{\mathbf{Prism}}
 \newcommand{\Hask}{\mathbf{Hask}}
@@
 \DeclareMathOperator{\copr}{copr}
+\newcommand{\inl}{\mathrm{inl}}
+\newcommand{\inr}{\mathrm{inr}}
 
@@
 \newcommand{\fmodify}{\textsc{Modify}}
+\newcommand{\freview}{\textsc{Review}}
+\newcommand{\fmatching}{\textsc{Matching}}
 
@@
 
-\todo{Might have to adjust the entire thing because the action of $\M$ on $\C$ is not strictly monoidal.
+\todo{TODO: Might have to adjust the entire thing because the action of $\M$ on $\C$ is not strictly monoidal.
 On the other hand, through the entire Pastro/Street paper pretends associativity/etc is strict, so maybe who cares?
 What we really want is just a (non-strict) monoidal functor $\M \to [\C, \C]$ from some $\M$.}
+
+\todo{TODO: Think about size issues, we are taking some very big coends...}
 
@@
 \begin{align*}
-\PreOptic_\M((S, S), (A, A)) &= \int^{M \in \M} \C(S, M \times A) \times \C(M \times A, S) \\
+\PreOptic_\times((S, S), (A, A)) &= \int^{M \in \M} \C(S, M \times A) \times \C(M \times A, S) \\
 &\cong \int^{M \in \M} \C(S, M) \times \C(S, A) \times \C(M \times A, S) && \text{(universal property of product)} \\
@@
 \subsubsection{Prisms}
+Prisms are dual to lenses:
+
+\begin{definition}
+Suppose $\C$ has finite coproducts, and let $\C$ act on itself via the bifunctor $\sqcup : \C \times \C \to \C$.
+The \emph{category of prisms} in $\C$ is the category of optics with respect to this action: $\Prism = \Optic_\sqcup$.
+\end{definition}
+
+Just as lenses are given by two concrete maps $\fget : S \to A$ and $\fput : S \times A \to S$, prisms are constructed by two maps $\freview : A \to S$ and $\fmatching : S \to S \sqcup A$.
+These names are taken from the Haskell \texttt{lens} library.
+\begin{align*}
+\PreOptic_\sqcup((S, S), (A, A)) &= \int^{M \in \M} \C(S, M \sqcup A) \times \C(M \sqcup A, S) \\
+&\cong \int^{M \in \M} \C(S, M \sqcup A) \times \C(M, S) \times \C(A, S) && \text{(universal property of coproduct)} \\
+&\cong \C(S, S \sqcup A) \times \C(A, S) && \text{(co-Yoneda)}
+\end{align*}
+So, if we are given a pre-prism $\langle l, r \rangle : (S, S) \hto (A, A)$ then associated $\freview$ and $\fmatching$ morphisms are given by $\freview = r \inr$ and $\fmatching = [r\inl, \id_S]l$
+
+The laws for prisms are:
+\begin{align*}
+\fmatching \; \freview = \inr \\
+[\id_S, \freview] \fmatching = \id_S
+\end{align*}
+
+\begin{proposition}
+\label{prop-OpticImpliesLensLaws}
+If $\langle l, r \rangle : S \hto A$ is a prism then the associated $\fmatching$ and $\freview$ functions satisfy the above laws.
+\end{proposition}
+\begin{proof}
+\todo{Should be straightforward}
+\end{proof}
+
+\todo{unfinished}
+
 \subsubsection{Traversals}
 \subsubsection{Setters}
+
+To define setters we must first recall the notion of a strong functor.
+
+\todo{Taken from http://cs.ioc.ee/~tarmo/ssgep15/ssgep-1a.pdf}
+\begin{definition}
+\todo{Again I am not fussing with associators/unitors, this is probably bad.
+Also this definition should work fine of we instead use an action of some $\M$ on $\C$.} Suppose $(\C, \otimes, I)$ is a monoidal category.
+A \emph{(left) strength} for an endofunctor $F : \C \to \C$ is a natural transformation
+\begin{align*}
+\theta_{A,B} : A \otimes F B \to F(A \otimes B)
+\end{align*}
+such that both
+\[
+\begin{tikzcd}
+A \otimes B \otimes F C \ar[r, "A \otimes \theta_{B,C}"] \ar[d, "\theta_{A \otimes B, C}" left]  & A \otimes F(B\otimes C) \ar[d, "\theta_{A, B\otimes C}" right] \\
+F(A \otimes B \otimes C) \ar[r, equals]& F(A \otimes B \otimes C)
+\end{tikzcd}
+\]
+and
+\[
+\begin{tikzcd}
+1 \otimes F A \ar[r, "s_{1,A}"] \ar[d, "\cong" left]  & F(1 \otimes A) \ar[d, "\cong" right] \\
+F A \ar[r, equals] & F A
+\end{tikzcd}
+\]
+commute.
+A \emph{strong functor} is a functor equipped with a strength.
+A \emph{strong natural transformation} $\tau : (F,\theta) \to (G,\theta')$ is a natural transformation that respects the strength:
+\[
+\begin{tikzcd}
+A \otimes F B \ar[r, "\theta_{A,B}"] \ar[d, "A \otimes \tau_B" left]  & G(A \otimes B) \ar[d, "\tau_{A \otimes B}" right] \\
+A \otimes G B \ar[r, "\theta'_{A, B}"]& G(A \otimes B)
+\end{tikzcd}
+\]
+
+There is an evident category $\Strong(\C)$ of strong endofunctors and strong natural transformations, and a forgetful functor $U : \Strong(\C) \to [\C, \C]$.
+\end{definition}
+
+Every endofunctor on $(\Set, \times, 1)$ has a unique strength, so this concept is invisible for Haskell functors.
+
+\begin{lemma}
+Suppose $\C$ is cartesian closed and $F : \C \to \C$ is strong with respect to $\times$. Then for any objects $A, B \in \C$, \[\C(A, FB) \cong \Strong_\C(\times)(A \times \homC(B, -), F)\]
+\end{lemma}
+\begin{proof}
+Given a $f \in \C(A, FB)$, let $\eta$ be the natural transformation with components
+\begin{align*}
+A \times \homC(B, C) \xrightarrow{f \times \id} FB \times \homC(B, C) \xrightarrow{\theta_{\homC(B, C), B}}  F(B \times \homC(B, C)) \xrightarrow{F\epsilon} FC
+\end{align*}
+where $\theta$ is the strength for $F$ and $\epsilon$ is the evaluation map.
+
+Conversely, given an $\eta : A \times \homC(B, -) \to F$, the component at $B$ is a function $g : A \times \homC(B, B) \to FB$; we recover $f : A \to FB$ as $f = g (\id_A, \const_{\id_B})$.
+
+\todo{These are inverses.}
+\end{proof}
+
+This is a generalisation of \cite[Proposition 2.2]{SecondOrderFunctionals}
+
+\todo{unfinished}
+
+\subsubsection{Affine Traversals}
 
@@
 \begin{definition}
-Suppose $\C$ is acted on by $\M$, a subcategory of $[\C, \C]$ closed under composition, and let $P \in \Prof(\C, \C)$ be a profunctor.
-A \emph{Tambara module structure for $\M$} on $P$ is a natural family of maps:
+Suppose $\C$ is acted on by $(\M, \otimes, I)$ and let $P \in \Prof(\C, \C)$ be a profunctor. A \emph{Tambara module structure for $\M$} on $P$ is a natural family of maps:
 \begin{align*}
@@
 \end{align*}
-such that $\alpha_{A,B,\id_\C} = \id_{P(A,B)}$, and the following diagram commutes:
+such that $\alpha_{A,B,I} = \id_{P(A,B)}$, and the following diagram commutes:
 \[
 \begin{tikzcd}
-P(A,B) \ar[r, "\alpha_{A,B,M}"] \ar[dr, "\alpha_{A, B, MN}" below left] & P(MA, MB) \ar[d, "\alpha_{MA, MB, N}" right] \\
+P(A,B) \ar[r, "\alpha_{A,B,M}"] \ar[dr, "\alpha_{A, B, N \otimes M}" below left] & P(MA, MB) \ar[d, "\alpha_{MA, MB, N}" right] \\
 & P(NMA, NMB)
@@
 \section{Degenerate Optics}
-% \section{Optic Families}
+\todo{The Haskell lens library has some other `optics' that aren't proper optics, but still integrate nicely with the rest of the ecosystem, e.g. Getters, Reviews and Folds}
+
+\section{Optic Families}
 \section{Indexed Optics}
@@
 \end{align*}
-with another monoidal action $I$. The $I$ would need to distribute over $M$ in some way.
+with another monoidal action $I$. The $I$ would need to distribute over $M$ in some way. ``Coindexed'' optics seem to have 
+\begin{align*}
+\int^{M \in \M} \C(S, J(MA)) \times \C(M A', S')
+\end{align*}
+which is why they pass information `in the other direction' but still transform covariantly.
 }
@@
 \end{align*}
+\todo{So here the $\fput\fget$ composite is
+\begin{align*}
+(A,X) &\mapsto (A,X) \\
+(B,X) &\mapsto (B,X) \\
+(C,X) &\mapsto (B,X) \\
+(A,Y) &\mapsto (C,Y) \\
+(B,Y) &\mapsto (C,Y) \\
+(C,Y) &\mapsto (C,Y)
+\end{align*}
+}
 \end{example}
 
-\todo{THE FOLLOWING IS TOTALLY WRONG, does not capture the right thing, fails for the above example}
+\todo{The condition on $\langle l, r \rangle$ seems to be that $rl = \id_S$ and $\pi_2lr = \pi_2$. I can't see how to generalise this second condition to optics other than lenses.}
+
+\todo{The following original attempt is wrong, does not capture the right thing}
 
@@
 
-\begin{proposition}
-The converse is true.
-\end{proposition}
-\begin{proof}
-
-\end{proof}
-
-This suggests the following definition of merely well-behaved optics, which we \todo{may as well} call semi-optics.
+This suggests the following definition of merely well-behaved optics, which we may as well call semi-optics.
 

### 2017-08-03 paper.tex
.
Some thoughts on a weaker definition of optic

@@
 \newtheorem{theorem}{Theorem}[section]
-\newtheorem{axiom}[theorem]{Axiom}
+%\newtheorem{axiom}[theorem]{Axiom}
 \newtheorem*{theoremstar}{Theorem}
-\newtheorem{fact}[theorem]{Fact}
+%\newtheorem{fact}[theorem]{Fact}
 \newtheorem{proposition}[theorem]{Proposition}
@@
 \newtheorem{definition}[theorem]{Definition}
-\newtheorem{convention}[theorem]{Convention}
-\newtheorem{construction}[theorem]{Construction}
+%\newtheorem{convention}[theorem]{Convention}
+%\newtheorem{construction}[theorem]{Construction}
 \newtheorem{example}[theorem]{Example}
-\newtheorem{examples}[theorem]{Examples}
-\newtheorem{notation}[theorem]{Notation}
+%\newtheorem{examples}[theorem]{Examples}
+%\newtheorem{notation}[theorem]{Notation}
 \newtheorem{remark}[theorem]{Remark}
-\newtheorem{idea}[theorem]{Idea}
-\newtheorem{question}[theorem]{Question}
+%\newtheorem{idea}[theorem]{Idea}
+%\newtheorem{question}[theorem]{Question}
 
@@
 
-\todo{People to credit:
+\todo{Past work:
 \begin{itemize}
@@
 \end{itemize}
+
+\todo{
+\subsection{(Co)ends and (Co)Yoneda}
+}
+
 \section{Optics}
@@
 
-Just as lenses are given by two concrete maps $\fget : S \to A$ and $\fput : S \times A \to S$, prisms are constructed by two maps $\freview : A \to S$ and $\fmatching : S \to S \sqcup A$.
+Just as lenses are constructed by two concrete maps $\fget : S \to A$ and $\fput : S \times A \to S$, prisms are constructed by two maps $\freview : A \to S$ and $\fmatching : S \to S \sqcup A$.
 These names are taken from the Haskell \texttt{lens} library.
@@
 \end{align*}
-So, if we are given a pre-prism $\langle l, r \rangle : (S, S) \hto (A, A)$ then associated $\freview$ and $\fmatching$ morphisms are given by $\freview = r \inr$ and $\fmatching = [r\inl, \id_S]l$
+So, if we are given a pre-prism $\langle l, r \rangle : (S, S) \hto (A, A)$ then associated $\freview$ and $\fmatching$ morphisms are given by $\freview = r \inr$ and $\fmatching = (r\inl \sqcup \id_A)l$
 
@@
 \end{align*}
+\todo{Are we missing a law?? Analogous to PutPut? I believe we are}
+\todo{
+\begin{proposition}
+When $\C = \Set$, the third law is implied by the other two.
+\end{proposition}
+}
 
 \begin{proposition}
-\label{prop-OpticImpliesLensLaws}
+\label{prop-OpticImpliesPrismLaws}
 If $\langle l, r \rangle : S \hto A$ is a prism then the associated $\fmatching$ and $\freview$ functions satisfy the above laws.
@@
 \begin{proof}
-\todo{Should be straightforward}
+\todo{Again it seems it is good enough if we only have $lr = t \sqcup A$}
+\begin{align*}
+\fmatching \; \freview 
+&= (r\inl \sqcup \id_A)l r \inr \\
+&= (r\inl \sqcup \id_A) \inr \\
+&= \inr \\
+[\id_S, \freview] \fmatching
+&= [\id_S, r \inr] (r\inl \sqcup \id_A)l \\ 
+&= [r\inl, r \inr] l \\ 
+&= rl \\
+&= \id_S
+\end{align*}
 \end{proof}
@@
 %\end{proof}
+
+\subsection{Change of Action}
+
+\todo{
+\section{Weaker Condition??}
+}
+\begin{proposition}
+Suppose the pre-lens $\langle l, r \rangle : S \hto A$ satisfies $rl = \id_S$ and $\langle lr \rangle = \langle t \times A \rangle$ as an element of $\int^{M \in \M} \C(M \times A, M \times A)$.
+Then $p$ obeys the three lens laws.
+\end{proposition}
+\begin{proof}
+This is nearly identical to Proposition \ref{prop-OpticImpliesLensLaws}. As was mentioned in the proof of Proposition \ref{prop-onthenose}, we may assume that $lr = t \times A$ on the nose.
+
+Now, again letting $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$,
+\begin{align*}
+\fget \; \fput 
+&= \pi_2 l r (\pi_1 l \times A) \\
+&= \pi_2 (t \times A) (\pi_1 l \times A) \\
+&= \pi_2 (t \pi_1 l \times A) \\
+&= \pi_2 \\
+\fput [\id_S, \fget] 
+&= r (\pi_1 l \times A) [\id_S, \pi_2 l] \\
+&= r [\pi_1 l, \pi_2 l] \\
+&= rl \\
+&= \id_S \\
+\fput (\fput \times A) 
+&= r (\pi_1 l \times A) (r (\pi_1 l \times A) \times A) \\
+&= r (\pi_1 l  r (\pi_1 l \times A) \times A) \\
+&= r (\pi_1 (t\pi_1 l \times A) \times A) \\
+&= r (t\pi_1 l \times A) \pi_{1,3} \\
+&= r lr(\pi_1 l \times A) \pi_{1,3} \\
+&= r(\pi_1 l \times A) \pi_{1,3} \\
+&= \fput \, \pi_{1, 3}
+\end{align*}
+\end{proof}
+
+\begin{proposition}
+Suppose there exists a map $x : 1 \to A$. Then if $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the three lens laws then the corresponding $p : S \hto A$ obeys the above weaker condition.
+\end{proposition}
+\begin{proof}
+Recall that the corresponding optic $p : S \hto A$ has representative $\langle [\id_s, \fget], \fput \rangle$.
+
+Let $\fput_x : S \to S$ be the composite $S \to S \times 1 \xrightarrow{x} S \times A \xrightarrow{\fput} S$. The commutative diagram
+\[
+\begin{tikzcd}
+S \times A \ar[r, "\fput_x \times A "] \ar[d, "lr", swap] & S \times A \ar[d, "\fput_x \times A"] \ar[dl, "lr"] \\
+S \times A \ar[r, "\fput_x \times A", swap] & S \times A
+\end{tikzcd}
+\]
+proves that $\langle lr \rangle = \langle \fput_x \times A \rangle$ in $\int^{M \in \M} \C(M A, M A)$.
+\todo{Is there some property of $\times$ used here we can abstract?}
+\end{proof}
 
@@
 
-\todo{The following original attempt is wrong, does not capture the right thing}
-
-\begin{proposition}
-Suppose the pre-lens $\langle l, r \rangle : S \hto A$ satisfies $rl = \id_S$ and $\langle lr \rangle = \langle t \times A \rangle$ as an element of $\int^{M \in \M} \C(M \times A, M \times A)$.
-Then $p$ obeys the $\fput\fget$ and $\fget\fput$ laws.
-\end{proposition}
-\begin{proof}
-This is nearly identical to Proposition \ref{prop-OpticImpliesLensLaws}. As was mentioned in the proof of Proposition \ref{prop-onthenose}, we may assume that $lr = t \times A$ on the nose.
-
-Now, again letting $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$,
-\begin{align*}
-\fget \; \fput 
-&= \pi_2 l r (\pi_1 l \times A) \\
-&= \pi_2 (t \times A) (\pi_1 l \times A) \\
-&= \pi_2 (t \pi_1 l \times A) \\
-&= \pi_2 \\
-\fput [\id_S, \fget] 
-&= r (\pi_1 l \times A) [\id_S, \pi_2 l] \\
-&= r [\pi_1 l, \pi_2 l] \\
-&= rl \\
-&= \id_S
-\end{align*}
-\end{proof}
-
-This suggests the following definition of merely well-behaved optics, which we may as well call semi-optics.
-
-\begin{definition}
-A \emph{semioptic} is a preoptic $p : S \hto A$ such that that $outside(p) = \id_S$ and $inside(p) = \langle t_A \rangle$ for some $t : M \to M$.
-\end{definition}
-
-Note that $t_A$ is necessarily idempotent, so if the ``evaluation-at-$A$'' functor is faithful then $t$ itself is idempotent.
-
-\begin{proposition}
-There is an subcategory $\SemiOptic_\M$ of $\PreOptic_\M$ given by objects of the form $(X, X)$ and semioptics between them.
-\end{proposition}
-
 \section{The Challenge of Effectful Optics}
@@
 
+Some thoughts: obvious thing to try is a double category where objects are the objects of $\C \times \C$, vertical morphisms $(S,T) \to (A, B)$ are maps $S \to A$ and $B \to T$, horizontal morphisms are preoptics.
+This I think is framed, you can always turn a pair of maps into a preoptic.
+
+Note the pair of maps above is also the set of morphisms $E_{S, T} \to E_{A, B}$. Maybe the objects should be profunctors??
+
 \section{Conclusion}

### 2017-08-23 paper.tex
Some cleanup

@@
 On the other hand, through the entire Pastro/Street paper pretends associativity/etc is strict, so maybe who cares?
-What we really want is just a (non-strict) monoidal functor $\M \to [\C, \C]$ from some $\M$.}
+What we really want is just a (non-strict) monoidal functor $\M \to [\C, \C]$ from some $\M$.
+I may also want to put $\otimes$ and $\cdot$ everywhere instead of just writing $MA$ and $NMA$.}
 
@@
 \item Previous attempts to generalise optics
-\item ...
+\item Some remark about how it's hard to isolate exactly what $\Set$-like properties are being used
 \end{itemize}
@@
 \begin{proposition}
-Let $\C$ be a category and $\M$ a monoidal category that acts on $\C$. There is a category $\PreOptic_\M$ that has the same objects as $\C \times \C$, with homsets given by
+Let $\C$ be a category and $(\M, \otimes, I)$ a monoidal category that acts on $\C$. There is a category $\PreOptic_\M$ that has the same objects as $\C \times \C$, with homsets given by
 \begin{align*}
@@
 \end{proposition}
-To distinguish these from morphisms in $\C$, we will write preoptics with a crossed arrow: $p : (S, S') \hto (A, A')$.
+To distinguish these from morphisms in $\C \times \C$, we will write preoptics with a crossed arrow: $p : (S, S') \hto (A, A')$.
 
 If $f : S \to M A$ and $g : M A' \to S'$, we write $\langle l, r \rangle$ for their image in $\PreOptic_\M((S, S'), (A, A'))$.
-We will refer to $M$ as the \emph{complement} for the representative $\langle l, r \rangle$.
 \begin{proof}
@@
 
-In \cite{Doubles}, a very similar category was considered.
-The \emph{double} $\Double$ of a monoidal category $(\C, \otimes, I)$ is a special case of the above, where $\M$ is chosen to be all functors of the form $X \otimes (-)$ for $X \in \C$.
+In \cite{Doubles}, a very similar category was considered. The \emph{double} $\Double$ of a monoidal category $(\C, \otimes, I)$ is a special case of the above, where $\C$ acts on itself by $\otimes$.
 
@@
 \begin{definition}
-An \emph{optic} from $S$ to $A$ is a preoptic $p$ from $(S, S)$ to $(A, A)$ such that $outside(p) = \id_S$, and $inside(p) = \langle \id_{MA} \rangle$ for some $M \in \M$.
+An \emph{optic} from $S$ to $A$ is a preoptic $p$ from $(S, S)$ to $(A, A)$ such that $outside(p) = \id_S$, and $inside(p) = \langle t A \rangle$ for some $t : M \to M \in \M$.
 \end{definition}
@@
 \label{prop-onthenose}
-If $p : (S,S) \hto (A,A)$ is an optic, then there exists a representative $p = \langle l, r \rangle$ such that $r \circ l = \id_{MA}$ on the nose for some $M$.
+If $p : (S,S) \hto (A,A)$ is an optic, then there exists a representative $p = \langle l, r \rangle$ such that $rl = \phi A$ on the nose for some $\phi : M \to M$.
 \end{proposition}
 \begin{proof}
-\todo{This is long and painful but seems important. There may be a more general principle at work here but I couldn't see it.}
+\todo{This is painful but seems important. There may be a more general principle at work here but I couldn't see it.}
 
 \todo{Put in an appendix?}
-
-In fact we will prove the more general statement that for $p : (S,S) \hto (A,A)$, if $outside(p) = \id_S$ and $inside(p) = \langle t \rangle$ where $t : MA \to MA$ is idempotent, then we can find a representative $\langle l, r \rangle$ with $l \circ r = t$ on the nose.
 
@@
 \]
-commutes. \todo{split the diagram in the middle?}
+commutes. \todo{put the $S$ on the outside?}
 
@@
 
-The above argument has a similar form to those that appear in \cite{OnTheTrace}, which considered (among other things) coends of the form $\int^{c \in \C} \C(c, Fc)$ for an endofunctor $F : \C \to \C$.
+The above argument has a similar form to some that appear in \cite{OnTheTrace}, which considered (among other things) coends of the form $\int^{c \in \C} \C(c, Fc)$ for an endofunctor $F : \C \to \C$.
 
-In view of this Proposition, whenever we posit a representative $\langle l, r \rangle$ of an optic, we will assume that $l$ and $r$ are mutual two-sided inverses.
+In view of this Proposition, whenever we posit a representative $\langle l, r \rangle$ of an optic, we may assume that $lr = \phi A$ on the nose, for some $\phi : M \to M$.
 
@@
 \begin{proof}
-The identity preoptic $\langle \id_X, \id_X \rangle$ is clearly an optic.
-Suppose we have two optics $\langle l, r \rangle : R \hto S$ and $\langle l', r' \rangle : S \hto A$ with complements $M$ and $N$ respectively.
-Then the composite $\langle (Ml')l, r (Mr')  \rangle$ is certainly also an optic:
+The identity preoptic $\langle \id_X : X \to IX, \id_X : IX \to X \rangle$ is clearly an optic.
+
+Suppose we have two optics $\langle l, r \rangle : R \hto S$ and $\langle l', r' \rangle : S \hto A$, where $l : R \to MS$ and $l' : S \to NA$, and such that $lr = \phi S$ and $l'r' = \psi A$.
+Then the composite $\langle (Ml')l, r (Mr')  \rangle$ is also an optic:
 \begin{align*}
-(Ml')l r (Mr') &= (Ml')(Mr') = M(l'r') = \id_{MNA}
+r (Mr')(Ml')l &= r M(r'l') l = rl = \id_S
 \intertext{and}
-r (Mr')(Ml')l &= r M(r'l') l = rl = \id_S
+(Ml')l r (Mr') &= (Ml')(\phi S)(Mr') = (\phi NA) M(l')M(r') = (\phi NA) M(l'r') = (\phi NA) M(\psi A) = \phi(\psi A)
 \end{align*}
+by the naturality of the action of $\M$.
 \end{proof}
@@
 
-Lenses form the ur-example of optics.
+Lenses are the ur-example of a class of optics.
 
@@
 Suppose $\C$ has finite products, and let $\C$ act on itself via the bifunctor $\times : \C \times \C \to \C$.
-The \emph{category of lenses} in $\C$ is the category of optics with respect to this action: $\Lens = \Optic_\times$.
+The \emph{category of lenses} $\Lens$ in $\C$ is the category of optics with respect to this action: $\Lens = \Optic_\times$.
 \end{definition}
@@
 
-Explicitly, given a prelens $\langle l, r \rangle : S \hto A$ these are given by $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
-Conversely, given $\fget$ and $\fput$, the corresponding element in the coend has representative $\langle l, r \rangle$, where $l = [\id_s, \fget]$ and $r = \fput$.
+Explicitly this isomorphism states that, given a prelens $\langle l, r \rangle : S \hto A$, the corresponding $\fget$ and $\fput$ functions are given by $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
+In the other direction, given $\fget$ and $\fput$, the corresponding element in the coend has representative $\langle l, r \rangle$, where $l = [\id_s, \fget]$ and $r = \fput$.
 Note that even if the $\fget$ and $\fput$ correspond to a law-abiding lens, this particular representative will not be an isomorphism.
@@
 \label{prop-OpticImpliesLensLaws}
-If $\langle l, r \rangle : S \hto A$ is a lens then the associated $\fget$ and $\fput$ functions satisfy the $\fget\fput$, $\fput\fget$ and $\fput\fput$ laws.
+Suppose $\langle l, r \rangle : S \hto A$ is a pre-lens such that $rl = \id_S$ and $\langle lr \rangle = \langle \phi \times A \rangle$ as an element of $\int^{M \in \M} \C(M \times A, M \times A)$, for some $\phi : M \to M$.
+Then $p$ obeys the three lens laws.
 \end{proposition}
 \begin{proof}
+By Proposition \ref{prop-onthenose}, we may assume that $lr = \phi \times A$ on the nose.
+
 Let $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$. Verification of the laws is straightforward:
@@
 &= \pi_2 l r (\pi_1 l \times A) \\
-&= \pi_2 (\pi_1 l \times A) \\
+&= \pi_2 (t \times A) (\pi_1 l \times A) \\
+&= \pi_2 (t \pi_1 l \times A) \\
 &= \pi_2 \\
@@
 &= r (\pi_1 l  r (\pi_1 l \times A) \times A) \\
-&= r (\pi_1 (\pi_1 l \times A) \times A) \\
-&= r (\pi_1 l \times A) \pi_{1,3} \\
+&= r (\pi_1 (t\pi_1 l \times A) \times A) \\
+&= r (t\pi_1 l \times A) \pi_{1,3} \\
+&= r lr(\pi_1 l \times A) \pi_{1,3} \\
+&= r(\pi_1 l \times A) \pi_{1,3} \\
 &= \fput \, \pi_{1, 3}
@@
 
-In favourable conditions, we can show the converse holds by constructing a complement. This is similar to the result proved in \cite[Corollary 13]{AlgebrasAndUpdateStrategies} for $\Set$.
+\begin{proposition}
+Suppose there exists a map $x : 1 \to A$. Then if $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the three lens laws then the corresponding $p : S \hto A$ is a prelens.
+\end{proposition}
+\begin{proof}
+Recall that the corresponding optic $p : S \hto A$ has representative $\langle [\id_s, \fget], \fput \rangle$.
 
-\begin{lemma}
-\todo{maybe delete this lemma, not so important}
-Suppose $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the $\fget\fput$, $\fput\fget$ and $\fput\fput$ laws.
-If we have $x_1, x_2 : 1 \to A$.
-Then the pullbacks $\fget^*(x_1)$ and $\fget^*(x_2)$ are isomorphic.
-\end{lemma}
-\begin{proof}
-We construct a map $f : \fget^*(x_2) \to \fget^*(x_1)$ as the induced map in the diagram
+Let $\fput_x : S \to S$ be the composite $S \to S \times 1 \xrightarrow{x} S \times A \xrightarrow{\fput} S$. The commutative diagram
 \[
 \begin{tikzcd}
-\fget^*(x_2) \ar[ddr, bend right = 20] \ar[dr, dashed] \ar[r, "{[x_2^*, x_1 !]}"] & S \times A \ar[dr, "\fput"] & \\
-& \fget^*(x_1) \ar[r, swap] \ar[d] \arrow[dr, phantom, "\lrcorner", very near start] & S \ar[d, "\fget"] \\
-& 1\ar[r, "x_1", swap] & A
+S \times A \ar[r, "\fput_x \times A "] \ar[d, "lr", swap] & S \times A \ar[d, "\fput_x \times A"] \ar[dl, "lr"] \\
+S \times A \ar[r, "\fput_x \times A", swap] & S \times A
 \end{tikzcd}
 \]
-That the outside composite commutes is exactly the $\fput\fget$ law. Similarly, we have a map $g : \fget^*(x_1) \to \fget^*(x_2)$.
+is a witness that $\langle lr \rangle = \langle \fput_x \times A \rangle$ in $\int^{M \in \M} \C(M A, M A)$.
+\todo{Is there some property of $\times$ used here we can abstract?}
+\end{proof}
 
-\todo{they are inverses by the other laws}
-\end{proof}
+In favourable conditions, we can upgrade this result to show that a lens $S \hto A$ in fact implies that $S \cong M \times A$ for some $M$.
+This is similar to the result proved in \cite[Corollary 13]{AlgebrasAndUpdateStrategies} for $\Set$.
 
@@
 Suppose $\C$ has finite limits and that there is a morphism $x : 1 \to A$.
-Then if $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the three lens laws then the corresponding $p : S \hto A$ is a lens.
+Then if $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the three lens laws then there exists $C \in \C$ with $S \cong C \times A$.
 \end{proposition}
 \begin{proof}
+\todo{TODO: This isn't really what we want to show, we want to start from an optic, not from something obeying the $\fget/\fput$ laws.}
+
 Set $C$ to be the pullback of $\fget$ along $x$, so there is a map $i : C \to S$ with $\fget \, i = x !_C$. There is also a map $j : S \to C$ induced by the following diagram:
@@
 \]
-which commutes by the $\fput\fget$ law. Note that $ji = \id_C$ by the universal property of pullbacks. Now the commutative diagram
-\[
-\begin{tikzcd}
-C \times A \ar[r, "i \times A"] \ar[d, "\fput (i \times A)", swap] & S \times A \ar[d, "\fput"] \\
-S \ar[r, equal] \ar[d, "{[j,\fget]}", swap] & S \ar[d, "{[\id_S, \fget]}"]  \\
-C \times A \ar[r, "i \times A", swap] & S \times A
-\end{tikzcd}
-\]
-is a witness that $\langle \fput (i \times A), [j,\fget] \rangle = \langle \fput, [\id_S, \fget] \rangle$ as elements of $\PreOptic_\M((S, S), (A, A))$.
-It remains to show that the maps on the left are mutual inverses:
+which commutes by the $\fput\fget$ law.
+Note that $ji = \id_C$ by the universal property of pullbacks.
+The claim is that $\fput (i \times A) : C \times A \to S$ and $[j,\fget] : S \to C \times A$ are mutual inverses.
+This is easily checked:
 \begin{align*}
@@
 \end{align*}
-Therefore $\langle \fput (i \times A), [j,\fget] \rangle$ is a lens, so  $\langle \fput, [\id_S, \fget] \rangle$ is a lens as we were hoping to show. \todo{maybe do the above in pictures}
+
+Additionally, the commutative diagram
+\[
+\begin{tikzcd}
+C \times A \ar[r, "i \times A"] \ar[d, "\fput (i \times A)", swap] & S \times A \ar[d, "\fput"] \\
+S \ar[r, equal] \ar[d, "{[j,\fget]}", swap] & S \ar[d, "{[\id_S, \fget]}"]  \\
+C \times A \ar[r, "i \times A", swap] & S \times A
+\end{tikzcd}
+\]
+is a witness that $\langle \fput (i \times A), [j,\fget] \rangle = \langle \fput, [\id_S, \fget] \rangle$ as elements of $\PreOptic_\M((S, S), (A, A))$.
 \end{proof}
@@
 
-The laws for prisms are:
+The laws for prisms are the obvious duals to the lens laws. 
 \begin{align*}
-\fmatching \; \freview = \inr \\
-[\id_S, \freview] \fmatching = \id_S
+\fmatching \; \freview &= \inr \\
+[\id_S, \freview] \fmatching &= \id_S \\
+(\fmatching \sqcup \id_A) \fmatching &= \mathrm{in}_{1,3} \, \fmatching
 \end{align*}
-\todo{Are we missing a law?? Analogous to PutPut? I believe we are}
 \todo{
 \begin{proposition}
-When $\C = \Set$, the third law is implied by the other two.
+When $\C = \Set$, and probably more generally, the third law is implied by the other two.
 \end{proposition}
@@
 
-\todo{
-\section{Weaker Condition??}
-}
-\begin{proposition}
-Suppose the pre-lens $\langle l, r \rangle : S \hto A$ satisfies $rl = \id_S$ and $\langle lr \rangle = \langle t \times A \rangle$ as an element of $\int^{M \in \M} \C(M \times A, M \times A)$.
-Then $p$ obeys the three lens laws.
-\end{proposition}
-\begin{proof}
-This is nearly identical to Proposition \ref{prop-OpticImpliesLensLaws}. As was mentioned in the proof of Proposition \ref{prop-onthenose}, we may assume that $lr = t \times A$ on the nose.
-
-Now, again letting $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$,
-\begin{align*}
-\fget \; \fput 
-&= \pi_2 l r (\pi_1 l \times A) \\
-&= \pi_2 (t \times A) (\pi_1 l \times A) \\
-&= \pi_2 (t \pi_1 l \times A) \\
-&= \pi_2 \\
-\fput [\id_S, \fget] 
-&= r (\pi_1 l \times A) [\id_S, \pi_2 l] \\
-&= r [\pi_1 l, \pi_2 l] \\
-&= rl \\
-&= \id_S \\
-\fput (\fput \times A) 
-&= r (\pi_1 l \times A) (r (\pi_1 l \times A) \times A) \\
-&= r (\pi_1 l  r (\pi_1 l \times A) \times A) \\
-&= r (\pi_1 (t\pi_1 l \times A) \times A) \\
-&= r (t\pi_1 l \times A) \pi_{1,3} \\
-&= r lr(\pi_1 l \times A) \pi_{1,3} \\
-&= r(\pi_1 l \times A) \pi_{1,3} \\
-&= \fput \, \pi_{1, 3}
-\end{align*}
-\end{proof}
-
-\begin{proposition}
-Suppose there exists a map $x : 1 \to A$. Then if $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the three lens laws then the corresponding $p : S \hto A$ obeys the above weaker condition.
-\end{proposition}
-\begin{proof}
-Recall that the corresponding optic $p : S \hto A$ has representative $\langle [\id_s, \fget], \fput \rangle$.
-
-Let $\fput_x : S \to S$ be the composite $S \to S \times 1 \xrightarrow{x} S \times A \xrightarrow{\fput} S$. The commutative diagram
-\[
-\begin{tikzcd}
-S \times A \ar[r, "\fput_x \times A "] \ar[d, "lr", swap] & S \times A \ar[d, "\fput_x \times A"] \ar[dl, "lr"] \\
-S \times A \ar[r, "\fput_x \times A", swap] & S \times A
-\end{tikzcd}
-\]
-proves that $\langle lr \rangle = \langle \fput_x \times A \rangle$ in $\int^{M \in \M} \C(M A, M A)$.
-\todo{Is there some property of $\times$ used here we can abstract?}
-\end{proof}
-
 \section{Profunctor Optics}
@@
 \end{align*}
-\todo{This works for $\PreOptic_\M((S, S'), (A, A'))$ just fine, fixing the definition of $E_A$.}
+\todo{This works for $\PreOptic_\M((S, S'), (A, A'))$ just fine, just define $E_{A,A'}$ in the obvious way.}
 \end{proof}
@@
 \langle (p_P \times p_Q)(x, y) \rangle &= \langle (UP)(l,r) \alpha_{A,A,M} x,  (UQ)(l,r) \beta_{A,A,M} y\rangle \\
-&= \langle (UP)(l,lr) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(by the coend relations \todo{more carefully})} \\
-&= \langle (UP)(l,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $lr = \id_{MA}$)} \\
+&= \langle (UP)(l,lr) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(by the coend relations)} \\
+&= \langle (UP)(l,\phi A) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $lr = \phi A$)} \\
+&= \langle (UP)((\phi A)l,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(by the coend relations again)} \\
+&= \langle (UP)(lrl,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $lr = \phi A$ again)} \\
+&= \langle (UP)(l,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $rl = \id_S$)} \\
 &= (U(P \odot Q))(l,r) \langle \alpha_{A,A,M} x, \beta_{A,A,M} y \rangle && \text{(by definition of $P \odot Q$)} \\
@@
 
+\todo{
 \section{Degenerate Optics}
-\todo{The Haskell lens library has some other `optics' that aren't proper optics, but still integrate nicely with the rest of the ecosystem, e.g. Getters, Reviews and Folds}
+The Haskell lens library has some other `optics' that aren't proper optics, but still integrate nicely with the rest of the ecosystem, e.g.
+Getters, Reviews and Folds.
+I am starting to doubt those fit into this framework though.}
 

### 2017-08-31 paper.tex
Small edits

@@
 \todo{This works for $\PreOptic_\M((S, S'), (A, A'))$ just fine, just define $E_{A,A'}$ in the obvious way.}
+
+\todo{Flip the order of the isomorphisms top to bottom?}
 \end{proof}
@@
 \begin{corollary}
-A profunctor preoptic is completely determined by its component at $\Pastro_\M E_A$, and furthermore, this component is determined by its value on $\langle \id_A, \id_A, \id_A, \id_A \rangle \in (U \Pastro_\M E_A)(A, A)$.
+A profunctor preoptic is determined by its component at $\Pastro_\M E_A$, and furthermore, this component is determined by its value on $\langle \id_A, \id_A, \id_A, \id_A \rangle \in (U \Pastro_\M E_A)(A, A)$.
 \end{corollary}
@@
 This is the content of the first two isomorphisms above.
+
+Explicitly, let $p_{\Pastro_\M E_A}(\langle \id_A, \id_A, \id_A, \id_A \rangle) = \langle l, \id_A, \id_A, r \rangle$, where $l : S \to M A$ and $r : M A \to S$.
+Then the component of $p$ at any other Tambara module $P$ is given by
+\begin{align*}
+p_P = (UP)(l,r) \alpha_{A,A,M}
+\end{align*}
+where $\alpha$ is the module structure for $P$.
 \end{proof}
@@
 \begin{proposition}
-Any optic $p : (U-)(A,A) \to (U-)(S,S)$ is a lax monoidal transformation with respect to Tambara module composition in the domain and the cartesian product in the codomain.
+If $p : S \hto A$ is an optic then the associated natural transformation $(U-)(A,A) \to (U-)(S,S)$ is a lax monoidal.
 \end{proposition}
 \begin{proof}
-The final few isomorphisms used in Proposition \ref{prop-profunctor-optics-are-optics} are essentially window dressing. Suppose we have an element of 
+The final few isomorphisms used in Proposition \ref{prop-profunctor-optics-are-optics} are essentially window dressing. Suppose we have an element $\langle l, e_1, e_2, r \rangle$ of 
 \begin{align*}
-(U\Pastro_\M E_A)(S,S) = \int^{M \in \M} \int^{C,D \in \C} \C(S, MC) \times E_A(C,D) \times \C(MD,S)
+(U\Pastro_\M E_A)(S,S) = \int^{M \in \M} \int^{C,D \in \C} \C(S, MC) \times E_A(C,D) \times \C(MD,S).
 \end{align*}
-and let $\phi : (U\Pastro_\M E_A)(S,S) \cong \PreOptic_\M((S, S), (A, A))$ be the isomorphism given in the proposition.
-If we have an element of $(U\Pastro_\M E_A)(S,S)$ with representative $\langle l, e_1, e_2, r \rangle$, the round-trip through the isomorphism $\phi$ yields $\langle (M e_1)l, \id_A, \id_A, r(M e_2)\rangle$.
+The round trip through the isomorphism $\Phi : (U\Pastro_\M E_A)(S,S) \cong \PreOptic_\M((S, S), (A, A))$ demonstrates that $\langle l, e_1, e_2, r \rangle = \langle (M e_1)l, \id_A, \id_A, r(M e_2)\rangle$.
 Hence we may always assume we have a representative of the form $\langle l, \id_A, \id_A, r \rangle$.
-This representative corresponds to an optic via the isomorphism $\phi$ iff both $rl = \id_S$ and $\langle lr\rangle = \langle \id_{NA} \rangle$ in $\int^{M \in \M} \C(M A, M A)$.
+This representative corresponds to an optic via the isomorphism $\Phi$ if both $rl = \id_S$ and $\langle lr\rangle = \langle \phi A \rangle$ in $\int^{M \in \M} \C(M A, M A)$.
 Note that just as we can ``strictify'' a representative of an optic, if we have an element of $(U\Pastro_\M E_A)(S,S)$ that corresponds to an optic we may always choose a representative so that the latter identity holds on the nose.
 
-Now, by the definition of the Yoneda isomorphism, a natural transformation \[ \Tamb_\C(\M)(\Pastro_\M E_A, -) \to (U-)(S,S) \] will correspond to an optic iff the image of the identity morphism in $(U\Pastro_\M E_A)(S, S)$ corresponds to an optic.
-The very first isomorphism in Proposition \ref{prop-profunctor-optics-are-optics} is given by precomposition by the isomorphism of Lemma \ref{lemma-rep}, so in all, a profunctor preoptic $p : (U-)(A, A) \to (U-)(S,S)$ is a lawful optic iff $p(\langle \id_A, \id_A, \id_A, \id_A \rangle)$ is an optic in $(U\Pastro_\M E_A)(S, S)$.
-Our goal is to show that this happens exactly when the natural transformation is monoidal.
+Next we examine the image of the optics through the Yoneda isomorphism \[ (U\Pastro_\M E_A)(S,S) \cong [\Tamb_\C(\M), \Set](\Tamb_\C(\M)(\Pastro_\M E_A, -), (U-)(S,S)) \] 
+By the definition of the Yoneda isomorphism, a natural transformation \[ p : \Tamb_\C(\M)(\Pastro_\M E_A, -) \to (U-)(S,S) \] will correspond to an optic iff the image of the identity morphism $\id : \Pastro_\M E_A \to \Pastro_\M E_A$ through the component $p_{\Pastro_\M E_A}$ is an optic in $(U\Pastro_\M E_A)(S, S)$.
 
-Let $\langle l, \id_A, \id_A, r \rangle = p(\langle \id_A, \id_A, \id_A, \id_A \rangle)$ be a representative, where $l : S \to M A$ and $r : M A \to S$.
-We can calculate the component of $p$ at a Tambara module $P$ explicitly:
-\begin{align*}
-p_P = (UP)(l,r) \alpha_{A,A,M}
-\end{align*}
-where $\alpha$ is the module structure for $P$.
+Finally the isomorphism \[ [\Tamb_\C(\M), \Set](\Tamb_\C(\M)(\Pastro_\M E_A, -), (U-)(S,S)) \cong \; [\Tamb_\C(\M), \Set]((U-)(A,A),(U-)(S,S)) \] is given by precomposition by the isomorphism of Lemma \ref{lemma-rep}, so in summary, a ``profunctor preoptic'' $p : (U-)(A, A) \to (U-)(S,S)$ is a lawful optic iff $p_{\Pastro_\M E_A}(\langle \id_A, \id_A, \id_A, \id_A \rangle)$ is an optic in $(U\Pastro_\M E_A)(S, S)$.
 
@@
 
+\section{Lenses in Linear Types}
+
 \section{The Double-Categorical Perspective}

### 2017-09-15 paper.tex
Work on some proofs

@@
 \item Given a $x \in P(C, C)$, I write $\langle x \rangle \in \int^C P(C, C)$ for its image, and $\copr_C : P(C,C) \to \int^C P(C, C)$
+\item For a monoidal category, the structure maps are $\alpha$, $\lambda$ and $\rho$. A symmetry is $s$.
 \end{itemize}
@@
 
-\begin{proposition}
-Let $\C$ be a category and $(\M, \otimes, I)$ a monoidal category that acts on $\C$. There is a category $\PreOptic_\M$ that has the same objects as $\C \times \C$, with homsets given by
+\todo{ Notation: For a monoidal category, the structure maps are $\alpha$, $\lambda$ and $\rho$, symmetry is $s$.
+For an action of $(\M, \otimes, I)$ on $\C$ we have two structure maps that are isomorphisms: $\epsilon_A : A \to IA$ and $\mu_{M,N,A} = MNA \to (M \otimes N)A$.
+}
+
+\todo{ We elide boring uses of the structure maps so we can stay sane...}
+
+\begin{proposition}
+Let $\C$ be a category and $(\M, \otimes, I)$ a monoidal category that acts on $\C$. There is a category $\PreOptic_\M$ that has the same objects as $\C \times \C^\op$, with homsets given by
 \begin{align*}
@@
 \end{proposition}
-To distinguish these from morphisms in $\C \times \C$, we will write preoptics with a crossed arrow: $p : (S, S') \hto (A, A')$.
-
-If $f : S \to M A$ and $g : M A' \to S'$, we write $\langle l, r \rangle$ for their image in $\PreOptic_\M((S, S'), (A, A'))$.
-\begin{proof}
-\todo{Following the doubles paper, this should be the Kleisli category for the monad on $\Prof$ given by:
-\begin{align*}
-\Phi(S, S', A, A') = \int^{M \in \M} \C(S, M A) \times \C(M A', S')
-\end{align*}
-}
-
-Explicitly, the composition map
+To distinguish these from morphisms in $\C \times \C^\op$, we will write preoptics with a crossed arrow: $p : (S, S') \hto (A, A')$.
+If $(l,r) : (S \to M A, M A' \to S')$, we write $\langle l, r \rangle : (S, S') \hto (A, A')$ for their image in $\PreOptic_\M((S, S'), (A, A'))$, and say that $M$ is the complement for this representative.
+\begin{proof}
+In \cite[Section 6]{Doubles} this is proven abstractly, by exhibiting this category as the Kleisli category for a monad in the bicategory $\Prof$. Here we give a direct proof.
+
+The composition map
 \begin{align*}
@@
 In other words, let $\langle l, r \rangle : (R, R') \hto (S, S')$ and $\langle l', r' \rangle : (S, S') \hto (A, A')$ with $M$ the complement for $\langle l, r \rangle$.
-The composite is then: $\langle l', r' \rangle \circ \langle l, r \rangle = \langle (M l')l, r(Mr') \rangle$
-\end{proof}
-
-In \cite{Doubles}, a very similar category was considered. The \emph{double} $\Double$ of a monoidal category $(\C, \otimes, I)$ is a special case of the above, where $\C$ acts on itself by $\otimes$.
-
-\todo{Mention the game theory stuff}
-
+The composite is then: $\langle l', r' \rangle \circ \langle l, r \rangle = \langle (M l')l, r(Mr') \rangle$.
+
+The identity morphism $(S, S') \hto (S, S')$ is given by $\langle \epsilon_S, \epsilon_{S'}^{-1} \rangle$. \todo{which will later be described as $(\id_S, \id_{S'})_*$}
+
+Associativity of composition can be checked equationally. Given $(l_1, r_1) : (R \to MS, MS' \to R')$ and $(l_2, r_2) : (S \to NA, NA' \to S')$ and $(l_3, r_3) : (A \to PB, PB' \to S')$:
+\begin{align*}
+(\langle l_3, r_3 \rangle \circ \langle l_2, r_2 \rangle) \circ \langle l_1, r_1 \rangle 
+&= \langle (N l_3)l_2, r_2(Nr_3) \rangle \circ \langle l_1, r_1 \rangle \\
+&= \langle M((N l_3)l_2)l_1, r_1M(r_2(Nr_3)) \rangle \\
+&= \langle (M N l_3)(M l_2)l_1, r_1(M r_2)(MNr_3)) \rangle \\
+&= \langle l_3, r_3 \rangle \circ (\langle (M l_2)l_1, r_1(Mr_2) \rangle) \\
+&= \langle l_3, r_3 \rangle \circ (\langle l_2, r_2 \rangle \circ \langle l_1, r_1 \rangle)
+\end{align*}
+
+\todo{To justify this kind of equational reasoning: We use that products in $\Set$ preserve colimits, so the coends can be floated to the outside and we may pick representatives for all 3 preoptics simultaneously.
+In the middle we include into the coend then immediately pick a representative, so by the universal property of coends we may as well use the representative we already have.
+It seems like this would also work in an enriched setting (if you really wanted it to)}
+
+Finally, we have the unit laws. For $(l, r) : (S \to MA, MA' \to S')$ we calculate:
+\begin{align*}
+\id_{A, A'} \circ \langle l, r\rangle 
+&= \langle \epsilon_A, \epsilon_{A'}^{-1} \rangle \circ \langle l, r\rangle \\
+&= \langle (M\epsilon_A) l, r (M\epsilon_{A'}^{-1})\rangle \\
+&= \langle (\lambda_M A) l, r (\lambda_M^{-1} A')\rangle \\
+&= \langle l, r (\lambda_M^{-1} A') (\lambda_M A')\rangle \\
+&= \langle l, r \rangle  \\
+\langle l, r \rangle \circ \id_{S, S'} 
+&= \langle l, r \rangle \circ \langle \epsilon_S, \epsilon_{S'}^{-1} \rangle  \\
+&= \langle (Il)\epsilon_S, \epsilon_{S'}^{-1} (Ir) \rangle \\
+&= \langle (\lambda_M S)l, r (\lambda_{S'}^{-1} S') \rangle \\
+&= \langle l, r (\lambda_{S'}^{-1} S')(\lambda_M S') \rangle \\
+&= \langle l, r \rangle
+\end{align*}
+Where in both cases we have used the coend relations to move $\lambda_M$ to the other side.
+\end{proof}
+
+In \cite[Section 6]{Doubles} a very similar category was considered.
+The \emph{double} $\Double_l \C$ of a monoidal category $(\C, \otimes, I)$ is \todo{the opposite category of} a special case of the above, where $\C$ is allowed to act on itself via left tensor.
+We will denote this case by $\PreOptic_\otimes$.
+
+\begin{proposition}
+For any $\C$ and $\M$, there is a functor $(-, -)_* : \C \times \C^\op \to \PreOptic_\M$, which is given on objects by $(S, S')_* = (S, S')$ and for a morphism $(f, g) : (S, S') \to (A, A')$ by $(f, g)_* = \langle \epsilon_A f, g \epsilon_{A'}^{-1} \rangle$.
+\end{proposition}
+\begin{proof}
+To check functoriality, suppose we have $(f, g) : (S, S') \to (A, A')$ and $(f', g') : (A, A') \to (B, B')$ in $\C \times \C^\op$. Then:
+\begin{align*}
+(f', g')_* \circ (f, g)_* 
+&= \langle \epsilon_B f', g' \epsilon_{B'}^{-1} \rangle \circ \langle \epsilon_A f, g \epsilon_{A'}^{-1} \rangle \\
+&= \langle (I(\epsilon_B f'))\epsilon_A f, g \epsilon_{A'}^{-1} (I(g' \epsilon_{B'}^{-1}))\rangle && \text{(By definition of $\circ$)}\\
+&= \langle (I\epsilon_B) (I f')\epsilon_A f, g \epsilon_{A'}^{-1} (I g')(I\epsilon_{B'}^{-1})\rangle && \text{(Functoriality of action of $I$)}\\
+&= \langle (I\epsilon_B) \epsilon_B f' f, g g' \epsilon_{B'}^{-1} (I\epsilon_{B'}^{-1})\rangle && \text{(Naturality of $\epsilon$)}\\
+&= \langle (\lambda_I B) \epsilon_B f' f, g g' \epsilon_{B'}^{-1} (\lambda_I^{-1}B')\rangle && \text{(Unitality of action)} \\
+&= \langle \epsilon_B f' f, g g' \epsilon_{B'}^{-1} (\lambda_I^{-1}B') (\lambda_I B') \rangle && \text{(Coend relation)}  \\
+&= \langle \epsilon_B f'f, g g' \epsilon_{B'}^{-1} \rangle \\
+&= (f'f, gg')_*
+\end{align*}
+\end{proof}
+\todo{Is this functor monoidal?}
+
+\todo{Is this functor faithful? What if $I$ is terminal? No! Take $S = \emptyset$}
+
+\todo{This doesn't give us the structure of a `framing', we can only lift vertical arrows to horizontal arrows facing one direction.}
+
+\begin{theorem}
+If $(\C, \otimes, I)$ is a symmetric monoidal category, then $\PreOptic_\otimes$ is also symmetric monoidal. \todo{braided?}
+\end{theorem}
+\begin{proof}
+On objects, we define $(S, S') \otimes (T, T') := (S \otimes T, S' \otimes T')$. The unit is given by the object $(I, I)$. The action of $\otimes$ on morphisms is induced by
+\begin{align*}
+&\C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(T, N \otimes B) \times \C(N \otimes B', T')\\
+\to \quad&\C(S \otimes T, M \otimes A \otimes N \otimes B) \times \C(M \otimes A' \otimes N \otimes B', S' \otimes T') && \text{(action of $\otimes$ on morphisms in $\C$)}\\
+\to \quad&\C(S \otimes T, M \otimes N \otimes A \otimes B) \times \C(M \otimes N \otimes A' \otimes B', S' \otimes T') && \text{($\otimes$ in $\C$ is symmetric)}\\
+\to \quad&\int^{M \in \C} \C(S \otimes T, M \otimes A \otimes B) \times \C(M \otimes A' \otimes B', S' \otimes T') && \text{(inclusion into coend)}
+\end{align*}
+yielding a function $\PreOptic_\otimes((S, S'), (A, A')) \times \PreOptic_\otimes((T, T'), (B, B')) \to \PreOptic_\otimes((S \otimes T, S' \otimes T'), (A \otimes B, A' \otimes B'))$.
+
+Equationally, suppose we have representatives $(l, r) : (S \to M \otimes A, M \otimes A' \to S')$ and $(l', r') : (T \to N \otimes B, N \otimes B' \to T')$. Then:
+\begin{align*}
+\langle l, r \rangle \otimes \langle l', r' \rangle &:= \langle (M \otimes s_{A,N} \otimes B)(l \otimes l'), (r \otimes r')(M \otimes s_{A',N} \otimes B') \rangle
+\end{align*}
+
+Now we check functoriality. Suppose we have:
+\begin{align*}
+\langle l_1, r_1 \rangle : (S_1, S_1') &\hto (S_2, S_2') \\
+\langle l_2, r_2 \rangle : (S_2, S_2') &\hto (S_3, S_3') \\
+\langle p_1, q_1 \rangle : (T_1, T_1') &\hto (T_2, T_2') \\
+\langle p_2, q_2 \rangle : (T_2, T_2') &\hto (T_3, T_3')
+\end{align*}
+with complements $M_1, M_2, N_1, N_2$ respectively. Then: \todo {(This is a mess. String diagram?)}
+\begin{align*}
+&(\langle l_2, r_2 \rangle \otimes \langle p_2, q_2 \rangle) \circ (\langle l_1, r_1 \rangle \otimes \langle p_1, q_1 \rangle) \\
+= \; &\langle (M_2 \otimes s_{S_3,N_2} \otimes T_3)(l_2 \otimes p_2), (r_2 \otimes q_2)(M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+&\circ \langle (M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), (r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2') \rangle \\
+= \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes N_1 \otimes l_2 \otimes p_2)(M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), \\
+&\;(r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2')(M_1 \otimes N_1 \otimes r_2 \otimes q_2)(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+= \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)(M_1 \otimes  l_2 \otimes N_1 \otimes p_2)(l_1 \otimes p_1), \\
+&\;(r_1 \otimes q_1)(M_1 \otimes r_2 \otimes N_1 \otimes q_2)(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+= \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1), \\
+&\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+= \; & \text{\todo{(Move all structure isomorphisms to one side of the coend, then appeal to coherence)}} \\
+= \; &\langle (M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S_3} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1) ,  \\
+&\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S'_3} \otimes T'_3) \rangle \\
+= \; &\langle (M_1 \otimes l_2)l_1, r_1(M_1 \otimes r_2) \rangle \otimes \langle (N_1 \otimes p_2)p_1, q_1(N_1 \otimes q_2) \rangle \\
+= \; &(\langle l_2, r_2 \rangle  \circ \langle l_1, r_1 \rangle) \otimes (\langle p_2, q_2 \rangle \circ \langle p_1, q_1 \rangle)
+\end{align*}
+
+The structure morphisms are all lifted from the structure morphisms in $\C$:
+\begin{align*}
+\alpha_{(R, R'), (S, S'), (T, T')} &:= (\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1})_* \\
+\lambda_{(S, S')} &:= (\lambda_{(S, S')}, \lambda_{(S, S')}^{-1})_* \\
+\rho_{(S, S')} &:= (\rho_{(S, S')}, \rho_{(S, S')}^{-1})_* \\
+s_{(S, S'), (T, T')} &:= (s_{S, T}, s_{T', S'})_*
+\end{align*}
+
+\todo{Once we know that $(-, -)_*$ is monoidal, the pentagon and triangle axioms should lift straight from $\C$ and we're done}
+
+\end{proof}
+
+In the Haskell \texttt{lens} library, the action of the monoidal product on optics is denoted ``\texttt{alongside}'' for the product and ``\texttt{without}'' for the coproduct.
+
+\subsection{Optics}
 For a fixed $M \in \M$, there is a map $\C(S, M A) \times \C(M A, S) \to \C(S, S)$ given by composition.
@@
 Including this object $\C(M A, M A)$ into the coend $\int^{M \in \M} \C(M A, M A)$, we induce a map $inside : \PreOptic_\M((S, S), (A,A)) \to \int^{M \in \M} \C(M A, M A)$.
-
 \begin{definition}
@@
 \begin{proof}
-The identity preoptic $\langle \id_X : X \to IX, \id_X : IX \to X \rangle$ is clearly an optic.
+The identity preoptic $(\id_X, \id_X)_*$ is clearly an optic.
 
@@
 \begin{proposition}
-Suppose $p : S \hto A$ is a pre-lens such that the associated natural transformation $p : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal. Then $p$ is a lens.
+Let $\C = \Set$ and suppose $p : S \hto A$ is a pre-lens such that the associated natural transformation $p : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal. Then $p$ is a lens.
 \end{proposition}
@@
 \section{Optic Families}
+
 \section{Indexed Optics}

### 2017-10-24 paper.tex
Many tiny updates

@@
 &\C(S, M A) \times \C(M A', S') \times \C(R, N S) \times \C(N S', R')\\
-\xrightarrow{\text{functoriality}} \quad& \C(NS, NM A) \times \C(NM A', NS') \times \C(R, N S) \times \C(N S', R')\\
-\xrightarrow{\text{composition}} \quad& \C(R, N M A) \times \C(N M A', R') \\
-\xrightarrow{\copr_{NM}} \quad&\int^{M \in \M} \C(R, M A) \times \C(M A', R')
+\to \,& \C(NS, NM A) \times \C(NM A', NS') \times \C(R, N S) \times \C(N S', R') && \text{(functoriality of action of $N$)} \\
+\to \,& \C(R, N M A) \times \C(N M A', R') && \text{(composition)} \\
+\to \,& \C(R, (N \otimes M) A) \times \C((N \otimes M) A', R') && \text{(composition with $\mu_{M,N,A}$)} \\
+\to \,&\int^{M \in \M} \C(R, M A) \times \C(M A', R') && \text{($\copr_{N \otimes M}$)}
 \end{align*}
 In other words, let $\langle l, r \rangle : (R, R') \hto (S, S')$ and $\langle l', r' \rangle : (S, S') \hto (A, A')$ with $M$ the complement for $\langle l, r \rangle$.
-The composite is then: $\langle l', r' \rangle \circ \langle l, r \rangle = \langle (M l')l, r(Mr') \rangle$.
+The composite is then: $\langle l', r' \rangle \circ \langle l, r \rangle = \langle \mu_{M,N,A}(M l')l, r(Mr')\mu^{-1}_{M,N,A'} \rangle$.
 
@@
 \begin{proof}
+This preserves identities, as the identity on an object $(S, S')$ in $\PreOptic_\M$ is defined to be exactly $\langle \epsilon_S, \epsilon_{S'}^{-1} \rangle$.
+
 To check functoriality, suppose we have $(f, g) : (S, S') \to (A, A')$ and $(f', g') : (A, A') \to (B, B')$ in $\C \times \C^\op$. Then:
@@
 \end{align*}
-
+For future convenience, note that 
+\begin{align*}
+\langle l, r \rangle \otimes (T, T') &= \langle (M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T') \rangle \\
+&= \langle (\lambda^{-1}_M \otimes A \otimes T)(M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T')(\lambda_M \otimes A' \otimes T') \rangle \\
+&= \langle l \otimes T, r \otimes T' \rangle
+\end{align*}
 Now we check functoriality. Suppose we have:
@@
 &\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-= \; & \text{\todo{(Move all structure isomorphisms to one side of the coend, then appeal to coherence)}} \\
+= \; & \text{\todo{(Add a $s_{M_2, N_1}$ to either side of the coend, then appeal to coherence)}} \\
 = \; &\langle (M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S_3} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1) ,  \\
@@
 
-\todo{Once we know that $(-, -)_*$ is monoidal, the pentagon and triangle axioms should lift straight from $\C$ and we're done}
-
+Note that because $(S, S')_* = (S, S')$, required equations for $(-, -)_*$ to be a monoidal functor hold by definition (although we don't yet know that $\PreOptic_\otimes$ is monoidal).
+The pentagon and triangle axioms then hold in $\PreOptic_\otimes$, as they are the image of the same axioms in $\C \times \C^\op$ under $(-, -)_*$.
+The only remaining piece to verify is that these structure maps are natural in $\PreOptic_\otimes$.
+
+Let us check that $\alpha_{(R, R'), (S, S'), (T, T')}$ is natural in $(R, R')$. Suppose $f : (Q, Q') \hto (R, R')$ has representative $(l, r) : (Q \to M \otimes R, M \otimes R' \to Q')$, then:
+\begin{align*}
+&\alpha_{(R, R'), (S, S'), (T, T')} \circ (f \otimes (S, S')) \otimes (T, T') \\
+&= (\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1})_*  \circ (\langle l, r \rangle \otimes (S, S')) \otimes (T, T') \\
+&= \langle\lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} \rangle  \circ \left\langle (l \otimes S) \otimes T, (r \otimes S') \otimes T' \right\rangle \\
+&=\left\langle (M \otimes \lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T})((l \otimes S) \otimes T), ((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} ) \right\rangle \\
+&=\left\langle (M \otimes \alpha_{R,S,T})((l \otimes S) \otimes T), ((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} )\right\rangle \\
+&=\left\langle (l \otimes (S \otimes T))\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}(r \otimes (S' \otimes T')) \right\rangle \\
+&= \langle (I \otimes l \otimes (S \otimes T)) \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}, (I \times r \otimes (S' \otimes T')) \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')}\rangle \\
+&= \langle l \otimes (S \otimes T), r \otimes (S' \otimes T')\rangle \circ \left\langle \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')} \right\rangle \\
+&= \langle l, r \rangle \otimes ((S, S') \otimes (T, T')) \circ (\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1})_* \\
+&= f \otimes ((S, S') \otimes (T, T')) \circ \alpha_{(Q, Q'), (S, S'), (T, T')} 
+\end{align*}
+\todo{There is some cheating going on here, composition actually adds an extra $\alpha$, but that wouldn't get in the way.}
 \end{proof}
@@
 
+There is some further useful structure in $\PreOptic_\otimes$. The set of costates $(S, S') \hto (I, I)$ is isomorphic to $\C(S, S')$:
+\begin{align*}
+\PreOptic_\otimes((S, S'), (I, I)) 
+&= \int^{M \in \C} \C(S, M \otimes I) \times \C(M \otimes I, S') \\
+&\cong \int^{M \in \C} \C(S, M) \times \C(M, S') \\
+&\cong \C(S, S')
+\end{align*}
+The identity morphism $\C(S, S)$ gives us a preoptic $\varepsilon : (S, S) \to (I, I)$ that we call the \emph{counit}.
+
+States are not as easy to describe in general.
+
+\begin{proposition}
+Suppose the monoidal unit $I$ of $\C$ is terminal. Then the set of states $(I, I) \hto (A, A')$ is isomorphic to $\C(I, A)$.
+\end{proposition}
+\begin{proof}
+\begin{align*}
+\PreOptic_\otimes((I,I), (A,A')) 
+&= \int^{M \in \C} \C(I, M \otimes A) \times \C(M \otimes A', I) \\
+&\cong \int^{M \in \C} \C(I, M \otimes A)
+\end{align*}
+Because the interior of this coend is mute in the contravariant position, the coend is equal to the colimit of the functor $\C(I, - \otimes A) : \C \to \Set$.
+But $\C$ has a terminal object, so $\int^{M \in \C} \C(I, M \otimes A) \cong \C(I, I \otimes A) \cong \C(I, A)$.
+\end{proof}
+
 \subsection{Optics}
+In this section we will focus only on preoptics of the form $p : (S,S) \hto (A, A)$.
+In what follows, we abbreviate $\PreOptic_\M((S, S), (A, A))$ as $\PreOptic_\M(S, A)$ and $p : (S, S) \hto (A, A)$ as $p : S \hto A$.
+
 For a fixed $M \in \M$, there is a map $\C(S, M A) \times \C(M A, S) \to \C(S, S)$ given by composition.
-This induces a map $outside : \PreOptic_\M((S, S), (A, A)) \to \C(S, S)$.
+This induces a map $outside : \PreOptic_\M(S, A) \to \C(S, S)$.
 By composition in the other direction we have a map $\C(S, M A) \times \C(M A, S) \to \C(M A, M A)$.
-Including this object $\C(M A, M A)$ into the coend $\int^{M \in \M} \C(M A, M A)$, we induce a map $inside : \PreOptic_\M((S, S), (A,A)) \to \int^{M \in \M} \C(M A, M A)$.
+Including this object $\C(M A, M A)$ into the coend $\int^{M \in \M} \C(M A, M A)$, we induce a map $inside : \PreOptic_\M(S, A) \to \int^{M \in \M} \C(M A, M A)$.
 \begin{definition}
-An \emph{optic} from $S$ to $A$ is a preoptic $p$ from $(S, S)$ to $(A, A)$ such that $outside(p) = \id_S$, and $inside(p) = \langle t A \rangle$ for some $t : M \to M \in \M$.
+An preoptic $p : S \hto A$ is an \emph{optic} if $outside(p) = \id_S$, and $inside(p) = \langle t A \rangle$ for some $t : M \to M$ in $\M$.
 \end{definition}
@@
 \label{prop-onthenose}
-If $p : (S,S) \hto (A,A)$ is an optic, then there exists a representative $p = \langle l, r \rangle$ such that $rl = \phi A$ on the nose for some $\phi : M \to M$.
+If $p : S \to A$ is an optic, then there exists a representative $p = \langle l, r \rangle$ such that $rl = \phi A$ on the nose for some $\phi : M \to M$.
 \end{proposition}
@@
 
-Lenses are the ur-example of a class of optics.
+Lenses form the ur-example of a category of optics.
 
@@
 \begin{align*}
-\PreOptic_\times((S, S), (A, A)) &= \int^{M \in \M} \C(S, M \times A) \times \C(M \times A, S) \\
+\PreOptic_\times(S, A) &= \int^{M \in \M} \C(S, M \times A) \times \C(M \times A, S) \\
 &\cong \int^{M \in \M} \C(S, M) \times \C(S, A) \times \C(M \times A, S) && \text{(universal property of product)} \\
@@
 \begin{proposition}
-Suppose there exists a map $x : 1 \to A$. Then if $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the three lens laws then the corresponding $p : S \hto A$ is a prelens.
-\end{proposition}
-\begin{proof}
-Recall that the corresponding optic $p : S \hto A$ has representative $\langle [\id_s, \fget], \fput \rangle$.
+Suppose there exists a map $x : 1 \to A$. Then if $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the three lens laws then the corresponding $p : S \hto A$ is a lens.
+\end{proposition}
+\begin{proof}
+Recall that the corresponding optic $p : S \hto A$ has as a representative $\langle [\id_s, \fget], \fput \rangle$.
 
@@
 is a witness that $\langle lr \rangle = \langle \fput_x \times A \rangle$ in $\int^{M \in \M} \C(M A, M A)$.
-\todo{Is there some property of $\times$ used here we can abstract?}
+\todo{Is there some property of $\times$ used here we can abstract? Having a map $1 \to A$ guarantees that $- \times A$ is faithful, is this the trick?}
 \end{proof}
@@
 \begin{proof}
-\todo{TODO: This isn't really what we want to show, we want to start from an optic, not from something obeying the $\fget/\fput$ laws.}
-
 Set $C$ to be the pullback of $\fget$ along $x$, so there is a map $i : C \to S$ with $\fget \, i = x !_C$. There is also a map $j : S \to C$ induced by the following diagram:
@@
 \]
-is a witness that $\langle \fput (i \times A), [j,\fget] \rangle = \langle \fput, [\id_S, \fget] \rangle$ as elements of $\PreOptic_\M((S, S), (A, A))$.
+is a witness that $\langle \fput (i \times A), [j,\fget] \rangle = \langle \fput, [\id_S, \fget] \rangle$ as elements of $\PreOptic_\M(S, A)$.
 \end{proof}
@@
 \begin{align*}
-\PreOptic_\sqcup((S, S), (A, A)) &= \int^{M \in \M} \C(S, M \sqcup A) \times \C(M \sqcup A, S) \\
+\PreOptic_\sqcup(S, A) &= \int^{M \in \M} \C(S, M \sqcup A) \times \C(M \sqcup A, S) \\
 &\cong \int^{M \in \M} \C(S, M \sqcup A) \times \C(M, S) \times \C(A, S) && \text{(universal property of coproduct)} \\
@@
 \end{align*}
+
 \todo{
@@
 
-\section{The Double-Categorical Perspective}
-
-\todo{There might be a lot more to say in terms of Mike's stuff on framed bicategories.
-The ``external product'' operation on profunctors seems key.
-This could be the mechanism behind the indexed stuff?}
-
-Some thoughts: obvious thing to try is a double category where objects are the objects of $\C \times \C$, vertical morphisms $(S,T) \to (A, B)$ are maps $S \to A$ and $B \to T$, horizontal morphisms are preoptics.
-This I think is framed, you can always turn a pair of maps into a preoptic.
-
-Note the pair of maps above is also the set of morphisms $E_{S, T} \to E_{A, B}$. Maybe the objects should be profunctors??
+\section{A Double-Categorical Perspective?}
+
+Dual pairs for the functors $(- \times A) : \M \to \C$ give a monoid in $PProf$.
 

### 2017-10-24 paper.tex
Third law for prisms in Set

@@
 \newcommand{\inr}{\mathrm{inr}}
+\DeclareMathOperator{\im}{im}
 
@@
 % Special arrows
-\newcommand{\isoto}{\xrightarrow{
-   \,\smash{\raisebox{-0.65ex}{\ensuremath{\scriptstyle\sim}}}\,}}
+\newcommand{\isoto}{\xrightarrow{\cong}}
 \newcommand{\hto}{\ensuremath{\,\mathaccent\shortmid\rightarrow\,}}
+
 \makeatletter
@@
 
-\todo{
-\begin{proposition}
-When $\C = \Set$, and probably more generally, the third law is implied by the other two.
-\end{proposition}
-}
+In the \texttt{lens} library documentation the third law is missing, due to the following:
+
+\begin{proposition}
+When $\C = \Set$\todo{, and probably more generally,} the third law is implied by the other two.
+\end{proposition}
+\begin{proof}
+The key is that in $\Set$, for any map $f : X \to Y$, the set $Y$ splits into the coproduct of $\im f$ and its complement.
+The first law implies that $\freview$ is injective, so $S \cong C \sqcup A$ for some complement $C$.
+Identifying $A$ with its image in $S$, the second law implies that if $a\in A \subset S$ then $\fmatching(a) = \inr(a)$ and if $c\in C \subset S$ then $\fmatching(c) = \inl(c)$.
+The third law then follows easily by checking both cases.
+\end{proof}
 

### 2017-10-30 paper.tex
Skip dual proof for prism laws

@@
 \end{align*}
-So, if we are given a pre-prism $\langle l, r \rangle : (S, S) \hto (A, A)$ then associated $\freview$ and $\fmatching$ morphisms are given by $\freview = r \inr$ and $\fmatching = (r\inl \sqcup \id_A)l$
+So, if we are given a pre-prism $\langle l, r \rangle : (S, S) \hto (A, A)$ then associated $\freview$ and $\fmatching$ morphisms are given by $\freview = r \inr$ and $\fmatching = (r\inl \sqcup A)l$
 
@@
 [\id_S, \freview] \fmatching &= \id_S \\
-(\fmatching \sqcup \id_A) \fmatching &= \mathrm{in}_{1,3} \, \fmatching
+(\fmatching \sqcup A) \fmatching &= \mathrm{in}_{1,3} \, \fmatching
 \end{align*}
@@
 \begin{proof}
-The key is that in $\Set$, for any map $f : X \to Y$, the set $Y$ splits into the coproduct of $\im f$ and its complement.
+The key is that in $\Set$, for any map $f : X \to Y$, the set $Y$ is equal to the union of $\im f$ and its complement.
 The first law implies that $\freview$ is injective, so $S \cong C \sqcup A$ for some complement $C$.
@@
 
+The following is then the dual of Proposition \ref{prop-OpticImpliesLensLaws}.
 \begin{proposition}
 \label{prop-OpticImpliesPrismLaws}
-If $\langle l, r \rangle : S \hto A$ is a prism then the associated $\fmatching$ and $\freview$ functions satisfy the above laws.
-\end{proposition}
-\begin{proof}
-\todo{Again it seems it is good enough if we only have $lr = t \sqcup A$}
-\begin{align*}
-\fmatching \; \freview 
-&= (r\inl \sqcup \id_A)l r \inr \\
-&= (r\inl \sqcup \id_A) \inr \\
-&= \inr \\
-[\id_S, \freview] \fmatching
-&= [\id_S, r \inr] (r\inl \sqcup \id_A)l \\ 
-&= [r\inl, r \inr] l \\ 
-&= rl \\
-&= \id_S
-\end{align*}
-\end{proof}
-
-\todo{unfinished}
+If $p : S \hto A$ is a prism then the associated $\fmatching$ and $\freview$ functions satisfy the three prism laws. \qed
+\end{proposition}
 
 \subsubsection{Traversals}
+\todo{Do it}
+
 \subsubsection{Setters}

### 2017-11-01 paper.tex
Tiny changes

@@
 }
+
 \section{Merely Well-Behaved Optics}
@@
 \begin{example}
-A minimal example is the following:
+A minimal example of a prelens that obeys $\fget\fput$ and $\fput\fget$ but not $\fput\fput$ is the following. Let $p : \{A,B,C\} \hto \{X, Y\}$ be the prelens with
 \begin{align*}
@@
 \end{align*}
-\todo{So here the $\fput\fget$ composite is
-\begin{align*}
-(A,X) &\mapsto (A,X) \\
-(B,X) &\mapsto (B,X) \\
-(C,X) &\mapsto (B,X) \\
-(A,Y) &\mapsto (C,Y) \\
-(B,Y) &\mapsto (C,Y) \\
-(C,Y) &\mapsto (C,Y)
-\end{align*}
-}
 \end{example}
 
-\todo{The condition on $\langle l, r \rangle$ seems to be that $rl = \id_S$ and $\pi_2lr = \pi_2$. I can't see how to generalise this second condition to optics other than lenses.}
+Prelenses that satisfy the first two laws correspond to pairs $\langle l, r \rangle$ such that $rl = \id_S$ and $\pi_2lr = \pi_2$.
+\todo{prove?} This condition seems unavoidably tied to the product structure on $\C$; it is not clear whether this weakened notion of lens can be generalised to other optics.
 
@@
 
-Past attempts \cite{ReflectionsOnMonadicLenses} to define effectful lenses have wrapped the result of one or both of $\fget$ and $\fput$ with a monad.
+Many attempts \cite{ReflectionsOnMonadicLenses} \todo{more} to define effectful lenses have wrapped the result of one or both of $\fget$ and $\fput$ with a monad.
 This approach is a little ad-hoc; it is not obvious what the laws ought to be and there is no clear generalisation to other varieties of optic.

### 2017-11-03 paper.tex
Add reference for doctrinal adjunction
Typoes etc

@@
 \begin{proof}
-On objects, we define $(S, S') \otimes (T, T') := (S \otimes T, S' \otimes T')$. The unit is given by the object $(I, I)$. The action of $\otimes$ on morphisms is induced by
+On objects we define $(S, S') \otimes (T, T') := (S \otimes T, S' \otimes T')$. The unit is given by the object $(I, I)$. The action of $\otimes$ on morphisms is induced by
 \begin{align*}
@@
 \intertext{and}
-(Ml')l r (Mr') &= (Ml')(\phi S)(Mr') = (\phi NA) M(l')M(r') = (\phi NA) M(l'r') = (\phi NA) M(\psi A) = \phi(\psi A)
+(Ml')l r (Mr') &= (Ml')(\phi S)(Mr') \\ 
+&= (\phi NA) M(l')M(r') \\ 
+&= (\phi NA) M(l'r') \\
+&= (\phi NA) M(\psi A) \\
+&= \phi(\psi A)
 \end{align*}
@@
 \end{align*}
-
-\todo{Written out at \cite{IsomorphismLensesPost}, definitely not the first place though.}
-\end{proof}
+\end{proof}
+
+This has been written out many times before in the case when $lr$ is the identity \cite{IsomorphismLensesPost} \todo{more}.
 
@@
 
-In favourable conditions, we can upgrade this result to show that a lens $S \hto A$ in fact implies that $S \cong M \times A$ for some $M$.
-This is similar to the result proved in \cite[Corollary 13]{AlgebrasAndUpdateStrategies} for $\Set$.
+In favourable conditions, we can upgrade this result to show that the existence of a lens $S \hto A$ implies that $S \cong M \times A$ for some $M$.
+This is a more general version of the argument given in \cite[Corollary 13]{AlgebrasAndUpdateStrategies} for $\Set$.
 
@@
 Suppose $\C$ has finite limits and that there is a morphism $x : 1 \to A$.
-Then if $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the three lens laws then there exists $C \in \C$ with $S \cong C \times A$.
+If $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the three lens laws then there exists $C \in \C$ with $S \cong C \times A$.
 \end{proposition}
@@
 
+\todo{TODO}
+
 \section{Profunctor Optics}
-
-\subsection{Profunctors}
-
-\todo{recall definitions} We use $I$ to refer to the identity profunctor $\C(-,{=})$, and $\odot$ for horizontal profunctor composition. Profunctor composition is written in diagramatic order.
-
-\subsection{Tambara Modules}
+Let $I = \C(-,{=}) : \C \hto \C$ be the identity profunctor and $\odot$ be profunctor composition, written in diagrammatic order.
 The following section generalises definitions that first appeared in \cite{Doubles}.
@@
 \begin{proof}
-This follows abstractly as a left adjoint of a strong monoidal functor. \todo{reference?}
+This follows abstractly as a left adjoint of a strong monoidal functor \cite{Kelly1974}.
 \end{proof}
@@
 This approach is a little ad-hoc; it is not obvious what the laws ought to be and there is no clear generalisation to other varieties of optic.
-The definition of optic given in this paper suggests we instead set $\C$ to be the Kleisli category for some monad.
-
-\section{Lenses in Linear Types}
+The definition of optic given here suggests we instead set $\C$ to be the Kleisli category for some monad $T$.
+
+\section{Lenses in Linear Types?}
 

### 2017-11-06 paper.tex
Get junk out of proof

@@
 
+\begin{proposition}
+The category $\PreOptic_\M$ is isomorphic to the full subcategory on objects of the form $E_A$ in the Kleisli category for the monad $U \Pastro_\M : \Prof(\C, \C) \to \Prof(\C, \C)$.
+\end{proposition}
+\begin{proof}
+\todo{Is there a point to proving this?}
+\end{proof}
+
 Given a profunctor, or indeed a Tambara module, we can evaluate it at any two objects of $\C$.
@@
 \begin{align*}
-[\Tamb_\C(\M), \Set]((U-)(A,A),(U-)(S,S)) &\cong \PreOptic_\M((S, S), (A, A))
+[\Tamb_\C(\M), \Set]((U-)(A,A),(U-)(S,S)) &\cong \PreOptic_\M(S, A)
 \end{align*}
@@
 \cong \;&\int^{M \in \M} \C(S, MA) \times \C(MA, S)  && \text{(by co-Yoneda twice)} \\
-= \;&\PreOptic_\M((S, S), (A, A))
+= \;&\PreOptic_\M(S, A)
 \end{align*}
@@
 \begin{proposition}
-If $p : S \hto A$ is an optic then the associated natural transformation $(U-)(A,A) \to (U-)(S,S)$ is a lax monoidal.
-\end{proposition}
-\begin{proof}
-The final few isomorphisms used in Proposition \ref{prop-profunctor-optics-are-optics} are essentially window dressing. Suppose we have an element $\langle l, e_1, e_2, r \rangle$ of 
-\begin{align*}
-(U\Pastro_\M E_A)(S,S) = \int^{M \in \M} \int^{C,D \in \C} \C(S, MC) \times E_A(C,D) \times \C(MD,S).
-\end{align*}
-The round trip through the isomorphism $\Phi : (U\Pastro_\M E_A)(S,S) \cong \PreOptic_\M((S, S), (A, A))$ demonstrates that $\langle l, e_1, e_2, r \rangle = \langle (M e_1)l, \id_A, \id_A, r(M e_2)\rangle$.
-Hence we may always assume we have a representative of the form $\langle l, \id_A, \id_A, r \rangle$.
-This representative corresponds to an optic via the isomorphism $\Phi$ if both $rl = \id_S$ and $\langle lr\rangle = \langle \phi A \rangle$ in $\int^{M \in \M} \C(M A, M A)$.
-Note that just as we can ``strictify'' a representative of an optic, if we have an element of $(U\Pastro_\M E_A)(S,S)$ that corresponds to an optic we may always choose a representative so that the latter identity holds on the nose.
-
-Next we examine the image of the optics through the Yoneda isomorphism \[ (U\Pastro_\M E_A)(S,S) \cong [\Tamb_\C(\M), \Set](\Tamb_\C(\M)(\Pastro_\M E_A, -), (U-)(S,S)) \] 
-By the definition of the Yoneda isomorphism, a natural transformation \[ p : \Tamb_\C(\M)(\Pastro_\M E_A, -) \to (U-)(S,S) \] will correspond to an optic iff the image of the identity morphism $\id : \Pastro_\M E_A \to \Pastro_\M E_A$ through the component $p_{\Pastro_\M E_A}$ is an optic in $(U\Pastro_\M E_A)(S, S)$.
-
-Finally the isomorphism \[ [\Tamb_\C(\M), \Set](\Tamb_\C(\M)(\Pastro_\M E_A, -), (U-)(S,S)) \cong \; [\Tamb_\C(\M), \Set]((U-)(A,A),(U-)(S,S)) \] is given by precomposition by the isomorphism of Lemma \ref{lemma-rep}, so in summary, a ``profunctor preoptic'' $p : (U-)(A, A) \to (U-)(S,S)$ is a lawful optic iff $p_{\Pastro_\M E_A}(\langle \id_A, \id_A, \id_A, \id_A \rangle)$ is an optic in $(U\Pastro_\M E_A)(S, S)$.
-
-To show $p$ is monoidal, we must show that both diagrams
+If $p : S \hto A$ is an optic then the associated natural transformation $(U-)(A,A) \to (U-)(S,S)$ is a lax monoidal. \todo{Rename the natural transformation $p$}
+\end{proposition}
+\begin{proof}
+Let $\langle l, r \rangle$ be a representative for $p$ in $\PreOptic_\M(S,A)$ via the isomorphism of Proposition \ref{prop-profunctor-optics-are-optics}, so that
+\begin{align*}
+p_P = (UP)(l,r) \alpha_{A,A,M}
+\end{align*}
+on each Tambara module $P$.
+
+To show $p$ is monoidal, we must show that both
 \[

### 2017-11-08 paper.tex
Typoes etc

@@
 Suppose $\C$ has finite products, and let $\C$ act on itself via the bifunctor $\times : \C \times \C \to \C$.
-The \emph{category of lenses} $\Lens$ in $\C$ is the category of optics with respect to this action: $\Lens = \Optic_\times$.
+The \emph{category of lenses} $\Lens$ is the category of optics with respect to this action: $\Lens = \Optic_\times$.
 \end{definition}
@@
 \label{prop-OpticImpliesLensLaws}
-Suppose $\langle l, r \rangle : S \hto A$ is a pre-lens such that $rl = \id_S$ and $\langle lr \rangle = \langle \phi \times A \rangle$ as an element of $\int^{M \in \M} \C(M \times A, M \times A)$, for some $\phi : M \to M$.
-Then $p$ obeys the three lens laws.
+Suppose $\langle l, r \rangle : S \hto A$ is a lens, i.e. that that $rl = \id_S$ and $\langle lr \rangle = \langle \phi \times A \rangle$ for some $\phi : M \to M$. Then $p$ obeys the three lens laws.
 \end{proposition}
@@
 In favourable conditions, we can upgrade this result to show that the existence of a lens $S \hto A$ implies that $S \cong M \times A$ for some $M$.
-This is a more general version of the argument given in \cite[Corollary 13]{AlgebrasAndUpdateStrategies} for $\Set$.
+This is a generalised from the argument given in \cite[Corollary 13]{AlgebrasAndUpdateStrategies} for $\Set$.
 
@@
 Suppose $\C$ has finite coproducts, and let $\C$ act on itself via the bifunctor $\sqcup : \C \times \C \to \C$.
-The \emph{category of prisms} in $\C$ is the category of optics with respect to this action: $\Prism = \Optic_\sqcup$.
+The \emph{category of prisms} is the category of optics with respect to this action: $\Prism = \Optic_\sqcup$.
 \end{definition}
 
-Just as lenses are constructed by two concrete maps $\fget : S \to A$ and $\fput : S \times A \to S$, prisms are constructed by two maps $\freview : A \to S$ and $\fmatching : S \to S \sqcup A$.
+Just as prelenses correspond to a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$, prisms correspond to pairs of maps $\freview : A \to S$ and $\fmatching : S \to S \sqcup A$.
 These names are taken from the Haskell \texttt{lens} library.
@@
 The key is that in $\Set$, for any map $f : X \to Y$, the set $Y$ is equal to the union of $\im f$ and its complement.
-The first law implies that $\freview$ is injective, so $S \cong C \sqcup A$ for some complement $C$.
+The first law implies that $\freview$ is injective, so $S \cong C \sqcup A$ for some complement $C$ \todo{name this map and use it properly}.
 Identifying $A$ with its image in $S$, the second law implies that if $a\in A \subset S$ then $\fmatching(a) = \inr(a)$ and if $c\in C \subset S$ then $\fmatching(c) = \inl(c)$.

### 2017-11-10 paper.tex
Comment out proof that might not be relevant

@@
 
-\subsection{Equivalence of Optics}
-
-One issue with the definition of optic given in the last section is that it could be difficult to determine when two optics $\langle l, r \rangle, \langle l', r' \rangle : S \hto A$ are equal.
+%\subsection{Equivalence of Optics}
+%
+%One issue with the definition of optic given in the last section is that it could be difficult to determine when two optics $\langle l, r \rangle, \langle l', r' \rangle : S \hto A$ are equal.
 For some choices of $\M$, however, we can reduce a zigzag of relations to a single one.
-
-\todo{This may work in general with some huge number of conditions: something like $-A$ reflects monomorphisms and preserves binary coproducts, all subobjects in $\M$ have complements.}
-
-\begin{proposition}
-Suppose all epimorphisms split in $\C$, and that $- \times A : \C \to \C$ reflects epis.
+%
+%\todo{This may work in general with some huge number of conditions: something like $-A$ reflects monomorphisms and preserves binary coproducts, all subobjects in $\M$ have complements.}
+%
+%\begin{proposition}
+%Suppose all epimorphisms split in $\C$, and that $- \times A : \C \to \C$ reflects epis.
 Then two lenses $\langle l, r \rangle$ and $\langle l', r' \rangle :  S \hto A$ with complements $M$ and $N$ respectively are equal iff there exists an morphism $\phi : M \to N$ such that $(\phi \times A)l = l'$ and $r = r' (\phi \times A)$.
-\end{proposition}
-\begin{proof}
-The backward direction is clear: the morphism $\phi$ is a witness that $\langle l, r \rangle \rightsquigarrow \langle l', r' \rangle$, so the two optics are equal.
-
-%note that $p$ and $q$ must have identical $\fget$ and $\fput$ functions:
+%\end{proposition}
+%\begin{proof}
+%The backward direction is clear: the morphism $\phi$ is a witness that $\langle l, r \rangle \rightsquigarrow \langle l', r' \rangle$, so the two optics are equal.
+%
+%%note that $p$ and $q$ must have identical $\fget$ and $\fput$ functions:
+%%\begin{align*}
+%%\fget &= \pi_2 l = \pi_2 l' \\
+%%\fput &= r (\pi_1 l \times A) = r' (\pi_1 l' \times A)
+%%\end{align*}
+%For the forward direction, note that the map $(\pi_1 l \times A)$ is a retraction: it has the section $(r, \pi_2)$:
 %\begin{align*}
-%\fget &= \pi_2 l = \pi_2 l' \\
-%\fput &= r (\pi_1 l \times A) = r' (\pi_1 l' \times A)
+%(\pi_1 l \times A)(r, \pi_2) = (\pi_1 l r, \pi_2) = (\pi_1, \pi_2) = \id_{S \times A}
 %\end{align*}
-For the forward direction, note that the map $(\pi_1 l \times A)$ is a retraction: it has the section $(r, \pi_2)$:
-\begin{align*}
-(\pi_1 l \times A)(r, \pi_2) = (\pi_1 l r, \pi_2) = (\pi_1, \pi_2) = \id_{S \times A}
-\end{align*}
-Now by assumption, $\pi_1 l : S \to M$ is an epi, so has a retraction $f : M \to S$. The claim is that $\phi = \pi_1 l' f$ is the required morphism $M \to N$.
-
-The situation is summarised in the following diagram, which other than the dashed line, we know commutes.
-\[
-\begin{tikzcd}
-M \times A \ar[r, "{f \times A}", dashed, bend left = 50] \ar[d, "r", swap] & S \times A \ar[d, "\fput"] \ar[r, "{\pi_1 l' \times A}"] \ar[l, "{\pi_1 l \times A}", swap] & N \times A \ar[d, "r'"] \\
-S \ar[r, equal] \ar[d, "l", swap] & S \ar[d, "{[\id_S, \fget]}"] \ar[r, equal] & S \ar[d, "l'"] \\
-M \times A & S \times A \ar[r] \ar[l] & N \times A
-\end{tikzcd}
-\]
-We can now calculate:
-\begin{align*}
-r = r(\pi_1 l f \times A) = \fput (f \times A) = r' (\pi_1 l' f \times A) = r'(\phi \times A)
-\end{align*}
-as required. The equation relating $l$ and $l'$ follows immediately as they are the inverses of $r$ and $r'$.
-\end{proof}
-
-The conditions of the above Proposition hold in $\Set$, so long as $A$ is not empty.
+%Now by assumption, $\pi_1 l : S \to M$ is an epi, so has a retraction $f : M \to S$. The claim is that $\phi = \pi_1 l' f$ is the required morphism $M \to N$.
+%
+%The situation is summarised in the following diagram, which other than the dashed line, we know commutes.
+%\[
+%\begin{tikzcd}
+%M \times A \ar[r, "{f \times A}", dashed, bend left = 50] \ar[d, "r", swap] & S \times A \ar[d, "\fput"] \ar[r, "{\pi_1 l' \times A}"] \ar[l, "{\pi_1 l \times A}", swap] & N \times A \ar[d, "r'"] \\
+%S \ar[r, equal] \ar[d, "l", swap] & S \ar[d, "{[\id_S, \fget]}"] \ar[r, equal] & S \ar[d, "l'"] \\
+%M \times A & S \times A \ar[r] \ar[l] & N \times A
+%\end{tikzcd}
+%\]
+%We can now calculate:
+%\begin{align*}
+%r = r(\pi_1 l f \times A) = \fput (f \times A) = r' (\pi_1 l' f \times A) = r'(\phi \times A)
+%\end{align*}
+%as required. The equation relating $l$ and $l'$ follows immediately as they are the inverses of $r$ and $r'$.
+%\end{proof}
+%
+%The conditions of the above Proposition hold in $\Set$, so long as $A$ is not empty.
 

### 2017-11-17 src/BadPrism.hs
Example of "law abiding" prism

@@ -1,0 +1,11 @@
+module BadPrism where
+
+import Control.Lens
+
+data MissCounter a = Misses Int a deriving (Show)
+
+bad :: Eq a => Prism' (MissCounter a) a
+bad = prism review matching
+  where review = Misses 0
+        matching (Misses 0 a) = Right a
+        matching (Misses n a) = Left (Misses (n + 1) a)

### 2018-01-25 paper.tex
Typo
Reorder deckchairs
Updates

@@
 \newcommand{\LaxMonCat}{\mathbf{LaxMonCat}}
+\newcommand{\SymmMonCat}{\mathbf{SymmMonCat}}
 
 \newcommand{\Act}{\mathbf{Act}}
-\newcommand{\PreOptic}{\mathbf{PreOptic}}
 \newcommand{\Optic}{\mathbf{Optic}}
+\newcommand{\Lawful}{\mathbf{Lawful}}
 \newcommand{\SemiOptic}{\mathbf{SemiOptic}}
@@
 
-\title{The Categorical Structure of Profunctor Optics}
+\title{The Categorical Structure of Optics}
 \author{Mitchell Riley}
@@
 I may also want to put $\otimes$ and $\cdot$ everywhere instead of just writing $MA$ and $NMA$.}
-
-\todo{TODO: Think about size issues, we are taking some very big coends...}
 
@@
 
-\todo{ We elide boring uses of the structure maps so we can stay sane...}
-
-\begin{proposition}
-Let $\C$ be a category and $(\M, \otimes, I)$ a monoidal category that acts on $\C$. There is a category $\PreOptic_\M$ that has the same objects as $\C \times \C^\op$, with homsets given by
-\begin{align*}
-\PreOptic_\M((S, S'), (A, A')) = \int^{M \in \M} \C(S, M A) \times \C(M A', S')
-\end{align*}
-\end{proposition}
-To distinguish these from morphisms in $\C \times \C^\op$, we will write preoptics with a crossed arrow: $p : (S, S') \hto (A, A')$.
-If $(l,r) : (S \to M A, M A' \to S')$, we write $\langle l, r \rangle : (S, S') \hto (A, A')$ for their image in $\PreOptic_\M((S, S'), (A, A'))$, and say that $M$ is the complement for this representative.
-\begin{proof}
-In \cite[Section 6]{Doubles} this is proven abstractly, by exhibiting this category as the Kleisli category for a monad in the bicategory $\Prof$. Here we give a direct proof.
-
-The composition map
-\begin{align*}
-\int^{M \in \M} \left(\C(S, M A) \times \C(M A', S')\right) \times \int^{M \in \M} \left( \C(R, M S) \times \C(M S', R')\right) \to \int^{M \in \M} \C(R, M A) \times \C(M A', R')
-\end{align*}
-of preoptics is induced by the following morphisms for every $M, N \in \M$:
-\begin{align*}
-&\C(S, M A) \times \C(M A', S') \times \C(R, N S) \times \C(N S', R')\\
-\to \,& \C(NS, NM A) \times \C(NM A', NS') \times \C(R, N S) \times \C(N S', R') && \text{(functoriality of action of $N$)} \\
-\to \,& \C(R, N M A) \times \C(N M A', R') && \text{(composition)} \\
-\to \,& \C(R, (N \otimes M) A) \times \C((N \otimes M) A', R') && \text{(composition with $\mu_{M,N,A}$)} \\
-\to \,&\int^{M \in \M} \C(R, M A) \times \C(M A', R') && \text{($\copr_{N \otimes M}$)}
+We begin by constructing the category of optics in a symmetric monoidal category $\C$.
+This category was first defined in \cite[Section 6]{Doubles} to investigate the relationship between Tambara modules and the center of a monoidal category.
+There it is called the \emph{double} $\Double_l \C$ of a monoidal category, and our definition is identical, other than flipping the direction of the arrows to match the existing literature on lenses.
+
+\begin{remark}
+\todo{I hope I can get away with this...} In what follows, we use the standard cheat of omitting associativity isomorphisms
+\end{remark}
+
+Let $\C$ be a symmetric monoidal category, and suppose we have two pairs of objects $(S, S')$ and $(A, A')$. An \emph{optic} $p : (S, S') \hto (A, A')$ is an element of the set
+\begin{align*}
+\Optic_\C((S, S'), (A, A')) := \int^{M \in \C} \C(S, M \otimes A) \times \C(M \otimes A', S')
+\end{align*}
+If $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\langle l, r \rangle : (S, S') \hto (A, A')$ for the image of this pair in $\Optic_\C((S, S'), (A, A'))$, and say that $M$ is the complement for this representative.
+
+\begin{remark}
+Optics will always be written with a crossed arrow $\hto$, to distinguish them from morphisms of $\C$.
+\end{remark}
+
+Elements of $\Optic_\C((S, S'), (A, A'))$ have a suggestive interpretation as string diagrams with a ``hole'' missing. We draw the pair $\langle l, r \rangle$ as
+\begin{center}
+\input{diagrams/generic-optic.tikz}
+\end{center}
+using the \todo{strange} convention of reading string diagrams from bottom to top.
+
+Two optics can be composed as follows: \todo{I give possibly too much detail here.} We wish to construct a map
+\begin{align*}
+&\left(\int^{M \in \C} \C(S, M \otimes A) \times \C(M \otimes A', S')\right) \times \left(\int^{M \in \C} \C(R, M \otimes S) \times \C(M \otimes S', R')\right) \\ &
+ \quad \to \int^{M \in \C} \C(R, M \otimes A) \times \C(M \otimes A', R').
+\end{align*}
+The product in $\Set$ preserves colimits, so in particular coends. Using this fact, and the Fubini theorem for coends \cite[Remark 1.9]{CoendCofriend}, the domain is isomorphic to
+\begin{align*}
+\int^{(M, N) \in \C \times \C} \C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(R, N \otimes S) \times \C(N \otimes S', R').
+\end{align*}
+So by the universal property of coends, it suffices to construct natural maps 
+\begin{align*}
+& \C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(R, N \otimes S) \times \C(N \otimes S', R') \\ &
+ \quad \to \int^{M \in \C} \C(R, M \otimes A) \times \C(M \otimes A', R').
+\end{align*}
+for each $M, N \in \C$. For this we use the composites
+\begin{align*}
+&\C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(R, N \otimes S) \times \C(N \otimes S', R')\\
+\to \,& \C(N \otimes S, N \otimes M \otimes A) \times \C(N \otimes M \otimes A', N \otimes S') \times \C(R, N \otimes S) \times \C(N \otimes S', R') && \text{(functoriality of $N \otimes  -$)} \\
+\to \,& \C(R, N \otimes  M \otimes A) \times \C(N \otimes M \otimes A', R') && \text{(composition in $\C$)} \\
+\to \,&\int^{M \in \M} \C(R, M \otimes A) \times \C(M \otimes A', R') && \text{($\copr_{N \otimes M}$)}
 \end{align*}
 In other words, let $\langle l, r \rangle : (R, R') \hto (S, S')$ and $\langle l', r' \rangle : (S, S') \hto (A, A')$ with $M$ the complement for $\langle l, r \rangle$.
-The composite is then: $\langle l', r' \rangle \circ \langle l, r \rangle = \langle \mu_{M,N,A}(M l')l, r(Mr')\mu^{-1}_{M,N,A'} \rangle$.
-
-The identity morphism $(S, S') \hto (S, S')$ is given by $\langle \epsilon_S, \epsilon_{S'}^{-1} \rangle$. \todo{which will later be described as $(\id_S, \id_{S'})_*$}
-
-Associativity of composition can be checked equationally. Given $(l_1, r_1) : (R \to MS, MS' \to R')$ and $(l_2, r_2) : (S \to NA, NA' \to S')$ and $(l_3, r_3) : (A \to PB, PB' \to S')$:
+The composite is then: $\langle l', r' \rangle \circ \langle l, r \rangle = \langle (M l')l, r(Mr')\rangle$.
+
+Graphically, this is placing the second optic into the hole of the first:
+\begin{center}
+\todo{todo}
+\end{center}
+
+The identity optic $(S, S') \hto (S, S')$ is given by $\langle \lambda^{-1}_S, \lambda_{S'} \rangle$, where $\lambda_S : I \otimes S \to S$ is the left unitor for $S$.
+
+\begin{proposition}
+The above data form a category $\Optic_\C$.
+\end{proposition}
+\begin{proof}
+In \cite[Section 6]{Doubles} this is proven abstractly, by exhibiting this category as the Kleisli category for a monad in the bicategory $\Prof$. Here we prove the properties directly.
+
+We check associativity of composition equationally.
+As in the definition of composition, the Fubini theorem allows us to choose representatives for all three optics simultaneously.
+Suppose we have representatives of three optics $\langle l_1, r_1\rangle : (R, R) \hto (S, S')$ and $\langle l_2, r_2 \rangle : (S, S') \hto (A, A')$ and $\langle l_3, r_3 \rangle : (A, A') \hto (B, B')$, that have complements $M$, $N$ and $P$ respectively.
+Then:
 \begin{align*}
 (\langle l_3, r_3 \rangle \circ \langle l_2, r_2 \rangle) \circ \langle l_1, r_1 \rangle 
-&= \langle (N l_3)l_2, r_2(Nr_3) \rangle \circ \langle l_1, r_1 \rangle \\
-&= \langle M((N l_3)l_2)l_1, r_1M(r_2(Nr_3)) \rangle \\
-&= \langle (M N l_3)(M l_2)l_1, r_1(M r_2)(MNr_3)) \rangle \\
-&= \langle l_3, r_3 \rangle \circ (\langle (M l_2)l_1, r_1(Mr_2) \rangle) \\
+&= \langle (N \otimes l_3)l_2, r_2(N \otimes r_3) \rangle \circ \langle l_1, r_1 \rangle \\
+&= \langle (M \otimes ((N \otimes l_3)l_2))l_1, r_1(M \otimes (r_2(N \otimes r_3))) \rangle \\
+&= \langle (M \otimes N \otimes l_3)(M \otimes l_2)l_1, r_1(M \otimes r_2)(M \otimes N \otimes r_3)) \rangle \\
+&= \langle l_3, r_3 \rangle \circ (\langle (M \otimes l_2)l_1, r_1(M \otimes r_2) \rangle) \\
 &= \langle l_3, r_3 \rangle \circ (\langle l_2, r_2 \rangle \circ \langle l_1, r_1 \rangle)
 \end{align*}
-
-\todo{To justify this kind of equational reasoning: We use that products in $\Set$ preserve colimits, so the coends can be floated to the outside and we may pick representatives for all 3 preoptics simultaneously.
-In the middle we include into the coend then immediately pick a representative, so by the universal property of coends we may as well use the representative we already have.
-It seems like this would also work in an enriched setting (if you really wanted it to)}
-
-Finally, we have the unit laws. For $(l, r) : (S \to MA, MA' \to S')$ we calculate:
+Graphically:
+\begin{center}
+\todo{todo}
+\end{center}
+
+For the unit laws, suppose we have $\langle l, r \rangle : (S, S') \hto (A, A')$ with representative $M$. We calculate:
 \begin{align*}
 \id_{A, A'} \circ \langle l, r\rangle 
-&= \langle \epsilon_A, \epsilon_{A'}^{-1} \rangle \circ \langle l, r\rangle \\
-&= \langle (M\epsilon_A) l, r (M\epsilon_{A'}^{-1})\rangle \\
-&= \langle (\lambda_M A) l, r (\lambda_M^{-1} A')\rangle \\
-&= \langle l, r (\lambda_M^{-1} A') (\lambda_M A')\rangle \\
+&= \langle \lambda^{-1}_A, \lambda_{A'} \rangle \circ \langle l, r\rangle \\
+&= \langle (M \otimes \lambda^{-1}_A) l, r (M\otimes  \lambda_{A'})\rangle \\
+&= \langle (\lambda^{-1}_M \otimes  A) l, r (\lambda_M \otimes A')\rangle \\
+&= \langle l, r (\lambda_M \otimes A') (\lambda^{-1}_M \otimes A')\rangle \\
 &= \langle l, r \rangle  \\
 \langle l, r \rangle \circ \id_{S, S'} 
-&= \langle l, r \rangle \circ \langle \epsilon_S, \epsilon_{S'}^{-1} \rangle  \\
-&= \langle (Il)\epsilon_S, \epsilon_{S'}^{-1} (Ir) \rangle \\
-&= \langle (\lambda_M S)l, r (\lambda_{S'}^{-1} S') \rangle \\
-&= \langle l, r (\lambda_{S'}^{-1} S')(\lambda_M S') \rangle \\
+&= \langle l, r \rangle \circ \langle \lambda^{-1}_S, \lambda_{S'}\rangle  \\
+&= \langle (I \otimes l)\lambda^{-1}_S, \lambda_{S'} (I \otimes r) \rangle \\
+&= \langle (\lambda^{-1}_M \otimes S)l, r (\lambda_{M} \otimes S') \rangle \\
+&= \langle l, r (\lambda_{M} \otimes S')(\lambda^{-1}_M \otimes S') \rangle \\
 &= \langle l, r \rangle
 \end{align*}
-Where in both cases we have used the coend relations to move $\lambda_M$ to the other side.
-\end{proof}
-
-In \cite[Section 6]{Doubles} a very similar category was considered.
-The \emph{double} $\Double_l \C$ of a monoidal category $(\C, \otimes, I)$ is \todo{the opposite category of} a special case of the above, where $\C$ is allowed to act on itself via left tensor.
-We will denote this case by $\PreOptic_\otimes$.
-
-\begin{proposition}
-For any $\C$ and $\M$, there is a functor $(-, -)_* : \C \times \C^\op \to \PreOptic_\M$, which is given on objects by $(S, S')_* = (S, S')$ and for a morphism $(f, g) : (S, S') \to (A, A')$ by $(f, g)_* = \langle \epsilon_A f, g \epsilon_{A'}^{-1} \rangle$.
-\end{proposition}
-\begin{proof}
-This preserves identities, as the identity on an object $(S, S')$ in $\PreOptic_\M$ is defined to be exactly $\langle \epsilon_S, \epsilon_{S'}^{-1} \rangle$.
+Where in both cases we have used the naturality of $\lambda$ and coend relations to move $\lambda^{-1}_M$ to the right-hand side of the coend. Graphically:
+\begin{center}
+\todo{todo}
+\end{center}
+
+%<---
+\end{proof}
+
+\begin{remark}
+Note that the definition of the $\Optic$ category involves a coend possibly indexed by a large category.
+To be maximally careful, we should only ever discuss $\Optic$ categories where we know that the coend exists by some other means, e.g., by exhibiting an isomorphism with some other set.
+For many, but not all, of the examples given later, we provide such an isomorphism.
+
+\todo{How does the doubles paper get away with it?}
+\end{remark}
+
+\begin{proposition}
+For any $\C$, there is a functor $(-, -)_* : \C \times \C^\op \to \Optic_\C$, which is given on objects by $(S, S')_* = (S, S')$ and for a morphism $(f, g) : (S, S') \to (A, A')$ by $(f, g)_* = \langle \lambda_A^{-1} f, g \lambda_{A'} \rangle$.
+\end{proposition}
+\begin{proof}
+This preserves identities, as the identity on an object $(S, S')$ in $\Optic_\M$ is defined to be exactly $\langle \lambda^{-1}_S, \lambda_{S'} \rangle$.
 
@@
 (f', g')_* \circ (f, g)_* 
-&= \langle \epsilon_B f', g' \epsilon_{B'}^{-1} \rangle \circ \langle \epsilon_A f, g \epsilon_{A'}^{-1} \rangle \\
-&= \langle (I(\epsilon_B f'))\epsilon_A f, g \epsilon_{A'}^{-1} (I(g' \epsilon_{B'}^{-1}))\rangle && \text{(By definition of $\circ$)}\\
-&= \langle (I\epsilon_B) (I f')\epsilon_A f, g \epsilon_{A'}^{-1} (I g')(I\epsilon_{B'}^{-1})\rangle && \text{(Functoriality of action of $I$)}\\
-&= \langle (I\epsilon_B) \epsilon_B f' f, g g' \epsilon_{B'}^{-1} (I\epsilon_{B'}^{-1})\rangle && \text{(Naturality of $\epsilon$)}\\
-&= \langle (\lambda_I B) \epsilon_B f' f, g g' \epsilon_{B'}^{-1} (\lambda_I^{-1}B')\rangle && \text{(Unitality of action)} \\
-&= \langle \epsilon_B f' f, g g' \epsilon_{B'}^{-1} (\lambda_I^{-1}B') (\lambda_I B') \rangle && \text{(Coend relation)}  \\
-&= \langle \epsilon_B f'f, g g' \epsilon_{B'}^{-1} \rangle \\
+&= \langle \lambda^{-1}_B f', g' \lambda_{B'} \rangle \circ \langle \lambda^{-1}_A f, g \lambda_{A'} \rangle \\
+&= \langle (I\otimes (\lambda^{-1}_B f'))\lambda^{-1}_A f, g \lambda_{A'} (I\otimes (g' \lambda_{B'}))\rangle && \text{(By definition of $\circ$)}\\
+&= \langle (I \otimes \lambda^{-1}_B) (I \otimes f')\lambda^{-1}_A f, g \lambda_{A'} (I \otimes g')(I\otimes \lambda_{B'})\rangle && \text{(Functoriality of $I \otimes -$)}\\
+&= \langle (I\otimes \lambda^{-1}_B) \lambda^{-1}_B f' f, g g' \lambda_{B'} (I\otimes \lambda_{B'})\rangle && \text{(Naturality of $\lambda$)}\\
+&= \langle (\lambda^{-1}_I \otimes B) \lambda^{-1}_B f' f, g g' \lambda_{B'} (\lambda_I \otimes B')\rangle && \text{(Unitality of action)} \\
+&= \langle \lambda^{-1}_B f' f, g g' \lambda_{B'} (\lambda_I \otimes B') (\lambda^{-1}_I \otimes B') \rangle && \text{(Coend relation)}  \\
+&= \langle \lambda^{-1}_B f'f, g g' \lambda_{B'} \rangle \\
 &= (f'f, gg')_*
 \end{align*}
-\end{proof}
-\todo{Is this functor monoidal?}
-
-\todo{Is this functor faithful? What if $I$ is terminal? No! Take $S = \emptyset$}
-
-\todo{This doesn't give us the structure of a `framing', we can only lift vertical arrows to horizontal arrows facing one direction.}
+Graphically, there is not much to do:
+\begin{center}
+\todo{todo}
+\end{center}
+\end{proof}
+
+%\todo{This doesn't give us the structure of a `framing', we can only lift vertical arrows to horizontal arrows facing one direction.}
 
 \begin{theorem}
-If $(\C, \otimes, I)$ is a symmetric monoidal category, then $\PreOptic_\otimes$ is also symmetric monoidal. \todo{braided?}
-\end{theorem}
-\begin{proof}
-On objects we define $(S, S') \otimes (T, T') := (S \otimes T, S' \otimes T')$. The unit is given by the object $(I, I)$. The action of $\otimes$ on morphisms is induced by
+$\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit is $(I, I)$, and with the action on morphisms induced by
 \begin{align*}
@@
 \end{align*}
-yielding a function $\PreOptic_\otimes((S, S'), (A, A')) \times \PreOptic_\otimes((T, T'), (B, B')) \to \PreOptic_\otimes((S \otimes T, S' \otimes T'), (A \otimes B, A' \otimes B'))$.
-
+\end{theorem}
+\begin{proof}
 Equationally, suppose we have representatives $(l, r) : (S \to M \otimes A, M \otimes A' \to S')$ and $(l', r') : (T \to N \otimes B, N \otimes B' \to T')$. Then:
@@
 
-Note that because $(S, S')_* = (S, S')$, required equations for $(-, -)_*$ to be a monoidal functor hold by definition (although we don't yet know that $\PreOptic_\otimes$ is monoidal).
-The pentagon and triangle axioms then hold in $\PreOptic_\otimes$, as they are the image of the same axioms in $\C \times \C^\op$ under $(-, -)_*$.
-The only remaining piece to verify is that these structure maps are natural in $\PreOptic_\otimes$.
+Note that because $(S, S')_* = (S, S')$, required equations for $(-, -)_*$ to be a monoidal functor hold by definition (although we don't yet know that $\Optic_\otimes$ is monoidal).
+The pentagon and triangle axioms then hold in $\Optic_\otimes$, as they are the image of the same axioms in $\C \times \C^\op$ under $(-, -)_*$.
+The only remaining piece to verify is that these structure maps are natural in $\Optic_\otimes$.
 
@@
 
-There is some further useful structure in $\PreOptic_\otimes$. The set of costates $(S, S') \hto (I, I)$ is isomorphic to $\C(S, S')$:
-\begin{align*}
-\PreOptic_\otimes((S, S'), (I, I)) 
+There is some further useful structure in $\Optic_\C$. 
+\begin{proposition}
+The set of costates $(S, S') \hto (I, I)$ is isomorphic to $\C(S, S')$.
+\end{proposition}
+\begin{proof}
+\begin{align*}
+\Optic_\otimes((S, S'), (I, I)) 
 &= \int^{M \in \C} \C(S, M \otimes I) \times \C(M \otimes I, S') \\
@@
 \end{align*}
-The identity morphism $\C(S, S)$ gives us a preoptic $\varepsilon : (S, S) \to (I, I)$ that we call the \emph{counit}.
-
-States are not as easy to describe in general.
+\end{proof}
+
+States are not as easy to describe in general:
 
@@
 \begin{proof}
-\begin{align*}
-\PreOptic_\otimes((I,I), (A,A')) 
+First, note that
+\begin{align*}
+\Optic_\otimes((I,I), (A,A')) 
 &= \int^{M \in \C} \C(I, M \otimes A) \times \C(M \otimes A', I) \\
-&\cong \int^{M \in \C} \C(I, M \otimes A)
+&\cong \int^{M \in \C} \C(I, M \otimes A).
 \end{align*}
@@
 
-\subsection{Optics}
+\todo{Entrywise Coproduct}
+
+\begin{proposition}
+A strong monoidal functor $F : \C \to \D$ induces a functor $\Optic(F) : \Optic_\C \to \Optic_\D$
+\end{proposition}
+\begin{proof}
+\todo{todo}
+\end{proof}
+
+\begin{proposition}
+These assignments assemble into a \todo{pseudo?}functor $\Optic : \SymmMonCat \to SymmMonCat$.
+\end{proposition}
+\begin{proof}
+\todo{todo}
+\end{proof}
+
+\subsection{Teleological Categories}
+
+As noted in \cite{CoherenceForLenses},
+
+\begin{definition}[{\cite[Definition 5.1]{CoherenceForLenses}}]
+A \emph{teleological category is} a symmetric monoidal category $(\C, \otimes, I)$, equipped with:
+\begin{itemize}
+\item A wide symmetric monoidal subcategory $\C_d$ of dualisable morphisms, with an involutive symmetric monoidal functor $(-)^* : \C_d^\op \to \C_d$
+\item A family of morphisms $\epsilon_X : X \otimes X^* \to I$, called \emph{counits}, natural with respect to the morphisms in $\C_d$,
+\end{itemize}
+such that the diagrams
+blah
+commute.
+\end{definition}
+
+In the case of optics, 
+The identity morphism $\C(S, S)$ gives us a preoptic $\varepsilon : (S, S) \to (I, I)$ that we call the \emph{counit}.
+
+\begin{proposition}
+With the above data, the category $\Optic_\C$ is a teleological category.
+\end{proposition}
+\begin{proof}
+\todo{todo}
+\end{proof}
+
+We can therefore
+
+As conjectured by Jules Hedges, the structure of a teleological category is precisely what is added by $\Optic$.
+\begin{theorem}
+$\Optic_\C$ is the free teleological category on a symmetric monoidal category $\C$.
+\end{theorem}
+\begin{proof}
+\todo{todo}
+\end{proof}
+
+\todo{Consequences: Inclusion $\C \to \Optic_\C$ is faithful/monoidal?}
+
+\subsection{Optics for a Monoidal Action}
+
+Let $\C$ be a category and $(\M, \otimes, I)$ a monoidal category that acts on $\C$.
+
+\section{Lawful Optics}
 In this section we will focus only on preoptics of the form $p : (S,S) \hto (A, A)$.
-In what follows, we abbreviate $\PreOptic_\M((S, S), (A, A))$ as $\PreOptic_\M(S, A)$ and $p : (S, S) \hto (A, A)$ as $p : S \hto A$.
+In what follows, we abbreviate $\Optic_\M((S, S), (A, A))$ as $\Optic_\M(S, A)$ and $p : (S, S) \hto (A, A)$ as $p : S \hto A$.
 
 For a fixed $M \in \M$, there is a map $\C(S, M A) \times \C(M A, S) \to \C(S, S)$ given by composition.
-This induces a map $outside : \PreOptic_\M(S, A) \to \C(S, S)$.
+This induces a map $outside : \Optic_\M(S, A) \to \C(S, S)$.
 By composition in the other direction we have a map $\C(S, M A) \times \C(M A, S) \to \C(M A, M A)$.
-Including this object $\C(M A, M A)$ into the coend $\int^{M \in \M} \C(M A, M A)$, we induce a map $inside : \PreOptic_\M(S, A) \to \int^{M \in \M} \C(M A, M A)$.
+Including this object $\C(M A, M A)$ into the coend $\int^{M \in \M} \C(M A, M A)$, we induce a map $inside : \Optic_\M(S, A) \to \int^{M \in \M} \C(M A, M A)$.
 \begin{definition}
@@
 \]
-where $S$ is some functor $\M^\op \times \M \to \E$.
+where $P$ is a functor $\M^\op \times \M \to \E$.
 
@@
 \begin{proposition}
-There is an subcategory $\Optic_\M$ of $\PreOptic_\M$ given by objects of the form $(X, X)$ and optics between them.
+There is an subcategory $\Lawful_\C$ of $\Optic_\C$ given by objects of the form $(X, X)$ and lawful optics between them.
 \end{proposition}
@@
 \begin{align*}
-\PreOptic_\times(S, A) &= \int^{M \in \M} \C(S, M \times A) \times \C(M \times A, S) \\
+\Optic_\times(S, A) &= \int^{M \in \M} \C(S, M \times A) \times \C(M \times A, S) \\
 &\cong \int^{M \in \M} \C(S, M) \times \C(S, A) \times \C(M \times A, S) && \text{(universal property of product)} \\
@@
 \label{prop-OpticImpliesLensLaws}
-Suppose $\langle l, r \rangle : S \hto A$ is a lens, i.e. that that $rl = \id_S$ and $\langle lr \rangle = \langle \phi \times A \rangle$ for some $\phi : M \to M$. Then $p$ obeys the three lens laws.
+Suppose $\langle l, r \rangle : S \hto A$ is a lens, i.e. that $rl = \id_S$ and $\langle lr \rangle = \langle \phi \times A \rangle$ for some $\phi : M \to M$. Then $p$ obeys the three lens laws.
 \end{proposition}
@@
 \]
-is a witness that $\langle \fput (i \times A), [j,\fget] \rangle = \langle \fput, [\id_S, \fget] \rangle$ as elements of $\PreOptic_\M(S, A)$.
+is a witness that $\langle \fput (i \times A), [j,\fget] \rangle = \langle \fput, [\id_S, \fget] \rangle$ as elements of $\Optic_\M(S, A)$.
 \end{proof}
@@
 \begin{align*}
-\PreOptic_\sqcup(S, A) &= \int^{M \in \M} \C(S, M \sqcup A) \times \C(M \sqcup A, S) \\
+\Optic_\sqcup(S, A) &= \int^{M \in \M} \C(S, M \sqcup A) \times \C(M \sqcup A, S) \\
 &\cong \int^{M \in \M} \C(S, M \sqcup A) \times \C(M, S) \times \C(A, S) && \text{(universal property of coproduct)} \\
@@
 
-\subsubsection{Traversals}
-\todo{Do it}
+\subsubsection{Affine Traversals}
 
@@
 
-\subsubsection{Affine Traversals}
+\subsubsection{Traversals}
+\todo{Do it}
 
@@
 \begin{definition}
-Suppose $\C$ is acted on by $(\M, \otimes, I)$ and let $P \in \Prof(\C, \C)$ be a profunctor. A \emph{Tambara module structure for $\M$} on $P$ is a natural family of maps:
+Suppose $\C$ is acted on by $(\M, \otimes, I)$ and let $P \in \Prof(\C, \C)$ be a profunctor. A \emph{Tambara module structure for $\M$} on $P$ is a family of maps:
 \begin{align*}
@@
 \end{align*}
-such that $\alpha_{A,B,I} = \id_{P(A,B)}$, and the following diagram commutes:
+natural in $A$ and $B$, and dinatural in $M$. Further, we must have that $\alpha_{A,B,I} = \id_{P(A,B)}$, and that the following diagram commutes:
 \[
@@
 \]
+for all $A, B \in \C$ and $N, M \in \M$.
 \end{definition}
@@
 \begin{proposition}
-The category $\PreOptic_\M$ is isomorphic to the full subcategory on objects of the form $E_A$ in the Kleisli category for the monad $U \Pastro_\M : \Prof(\C, \C) \to \Prof(\C, \C)$.
+The category $\Optic_\M$ is isomorphic to the full subcategory on objects of the form $E_A$ in the Kleisli category for the monad $U \Pastro_\M : \Prof(\C, \C) \to \Prof(\C, \C)$.
 \end{proposition}
@@
 \begin{align*}
-[\Tamb_\C(\M), \Set]((U-)(A,A),(U-)(S,S)) &\cong \PreOptic_\M(S, A)
+[\Tamb_\C(\M), \Set]((U-)(A,A),(U-)(S,S)) &\cong \Optic_\M(S, A)
 \end{align*}
@@
 \cong \;&\int^{M \in \M} \C(S, MA) \times \C(MA, S)  && \text{(by co-Yoneda twice)} \\
-= \;&\PreOptic_\M(S, A)
-\end{align*}
-\todo{This works for $\PreOptic_\M((S, S'), (A, A'))$ just fine, just define $E_{A,A'}$ in the obvious way.}
+= \;&\Optic_\M(S, A)
+\end{align*}
+\todo{This works for $\Optic_\M((S, S'), (A, A'))$ just fine, just define $E_{A,A'}$ in the obvious way.}
 
@@
 
-\subsection{Optics}
-
-The next question is: can we characterise the profunctor preoptics that actually correspond to the lawful optics?
-The plan is to chase through the above isomorphisms to see where the lawful optics end up.
+\subsection{Lawful Profunctor Optics}
+
+The next question is: can we characterise the profunctor optics that correspond to lawful optics? The plan is to chase through the above isomorphisms to see where the lawful optics end up.
 
@@
 \begin{proof}
-Let $\langle l, r \rangle$ be a representative for $p$ in $\PreOptic_\M(S,A)$ via the isomorphism of Proposition \ref{prop-profunctor-optics-are-optics}, so that
+Let $\langle l, r \rangle$ be a representative for $p$ in $\Optic_\M(S,A)$ via the isomorphism of Proposition \ref{prop-profunctor-optics-are-optics}, so that
 \begin{align*}

### 2018-03-02 paper.tex
Some attempts at diagrams

@@
 \usepackage{tikz-cd}
+\usetikzlibrary{positioning}
+\usetikzlibrary{fit}
 \usetikzlibrary{cd}
 \usetikzlibrary{arrows}
+
+\usepackage{adjustbox}
+\usepackage{etoolbox}
+\BeforeBeginEnvironment {tikzpicture}{\begin{adjustbox}{valign=m}}
+\AfterEndEnvironment {tikzpicture}{\end{adjustbox}}
 
@@
 
-\title{The Categorical Structure of Optics}
+\title{Categories of Optics}
 \author{Mitchell Riley}
@@
 If $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\langle l, r \rangle : (S, S') \hto (A, A')$ for the image of this pair in $\Optic_\C((S, S'), (A, A'))$, and say that $M$ is the complement for this representative.
+Optics will always be written with a crossed arrow $\hto$, to distinguish them from morphisms of $\C$.
 
 \begin{remark}
-Optics will always be written with a crossed arrow $\hto$, to distinguish them from morphisms of $\C$.
-\end{remark}
-
-Elements of $\Optic_\C((S, S'), (A, A'))$ have a suggestive interpretation as string diagrams with a ``hole'' missing. We draw the pair $\langle l, r \rangle$ as
+Elements of $\Optic_\C((S, S'), (A, A'))$ have an appealing interpretation as string diagrams with a ``hole'' missing. We draw the pair $\langle l, r \rangle$ as
 \begin{center}
@@
 \end{center}
-using the \todo{strange} convention of reading string diagrams from bottom to top.
+reading left to right, so the left half of the diagram represents $l$ and the right half $r$. The relation imposed by the coend takes the following form:
+\begin{center}
+\input{diagrams/coend-relation-left.tikz} \quad $=$ \quad \input{diagrams/coend-relation-right.tikz}
+\end{center}
+We will therefore omit the vertical cut point between $l$ and $r$ in subsequent diagrams; any choice yields a representative of same optic.
+\end{remark}
 
@@
 
-Graphically, this is placing the second optic into the hole of the first:
+Graphically, this is placing the second optic into the middle of the first:
 \begin{center}
@@
 \begin{proposition}
-For any $\C$, there is a functor $(-, -)_* : \C \times \C^\op \to \Optic_\C$, which is given on objects by $(S, S')_* = (S, S')$ and for a morphism $(f, g) : (S, S') \to (A, A')$ by $(f, g)_* = \langle \lambda_A^{-1} f, g \lambda_{A'} \rangle$.
+For any $\C$, there is a functor $\iota : \C \times \C^\op \to \Optic_\C$, which is given on objects by $\iota(S, S') = (S, S')$ and for a morphism $(f, g) : (S, S') \to (A, A')$ by $\iota(f, g) = \langle \lambda_A^{-1} f, g \lambda_{A'} \rangle$.
 \end{proposition}
@@
 \begin{align*}
-(f', g')_* \circ (f, g)_* 
+\iota(f', g') \circ \iota(f, g) 
 &= \langle \lambda^{-1}_B f', g' \lambda_{B'} \rangle \circ \langle \lambda^{-1}_A f, g \lambda_{A'} \rangle \\
@@
 &= \langle \lambda^{-1}_B f'f, g g' \lambda_{B'} \rangle \\
-&= (f'f, gg')_*
+&= \iota(f'f, gg')
 \end{align*}
@@
 \begin{theorem}
-$\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit is $(I, I)$, and with the action on morphisms induced by
+$\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit is $(I, I)$, and the action on morphisms induced by
 \begin{align*}
@@
 \end{align*}
-For future convenience, note that 
-\begin{align*}
-\langle l, r \rangle \otimes (T, T') &= \langle (M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T') \rangle \\
-&= \langle (\lambda^{-1}_M \otimes A \otimes T)(M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T')(\lambda_M \otimes A' \otimes T') \rangle \\
-&= \langle l \otimes T, r \otimes T' \rangle
-\end{align*}
-Now we check functoriality. Suppose we have:
-\begin{align*}
-\langle l_1, r_1 \rangle : (S_1, S_1') &\hto (S_2, S_2') \\
-\langle l_2, r_2 \rangle : (S_2, S_2') &\hto (S_3, S_3') \\
-\langle p_1, q_1 \rangle : (T_1, T_1') &\hto (T_2, T_2') \\
-\langle p_2, q_2 \rangle : (T_2, T_2') &\hto (T_3, T_3')
-\end{align*}
-with complements $M_1, M_2, N_1, N_2$ respectively. Then: \todo {(This is a mess. String diagram?)}
-\begin{align*}
-&(\langle l_2, r_2 \rangle \otimes \langle p_2, q_2 \rangle) \circ (\langle l_1, r_1 \rangle \otimes \langle p_1, q_1 \rangle) \\
-= \; &\langle (M_2 \otimes s_{S_3,N_2} \otimes T_3)(l_2 \otimes p_2), (r_2 \otimes q_2)(M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-&\circ \langle (M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), (r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2') \rangle \\
-= \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes N_1 \otimes l_2 \otimes p_2)(M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), \\
-&\;(r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2')(M_1 \otimes N_1 \otimes r_2 \otimes q_2)(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-= \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)(M_1 \otimes  l_2 \otimes N_1 \otimes p_2)(l_1 \otimes p_1), \\
-&\;(r_1 \otimes q_1)(M_1 \otimes r_2 \otimes N_1 \otimes q_2)(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-= \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1), \\
-&\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-= \; & \text{\todo{(Add a $s_{M_2, N_1}$ to either side of the coend, then appeal to coherence)}} \\
-= \; &\langle (M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S_3} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1) ,  \\
-&\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S'_3} \otimes T'_3) \rangle \\
-= \; &\langle (M_1 \otimes l_2)l_1, r_1(M_1 \otimes r_2) \rangle \otimes \langle (N_1 \otimes p_2)p_1, q_1(N_1 \otimes q_2) \rangle \\
-= \; &(\langle l_2, r_2 \rangle  \circ \langle l_1, r_1 \rangle) \otimes (\langle p_2, q_2 \rangle \circ \langle p_1, q_1 \rangle)
-\end{align*}
+This is functorial, as suggested by the equivalence of the following string diagrams:
+\todo{todo}
+%For future convenience, note that 
+%\begin{align*}
+%\langle l, r \rangle \otimes (T, T') &= \langle (M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T') \rangle \\
+%&= \langle (\lambda^{-1}_M \otimes A \otimes T)(M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T')(\lambda_M \otimes A' \otimes T') \rangle \\
+%&= \langle l \otimes T, r \otimes T' \rangle
+%\end{align*}
+%Now we check functoriality. Suppose we have:
+%\begin{align*}
+%\langle l_1, r_1 \rangle : (S_1, S_1') &\hto (S_2, S_2') \\
+%\langle l_2, r_2 \rangle : (S_2, S_2') &\hto (S_3, S_3') \\
+%\langle p_1, q_1 \rangle : (T_1, T_1') &\hto (T_2, T_2') \\
+%\langle p_2, q_2 \rangle : (T_2, T_2') &\hto (T_3, T_3')
+%\end{align*}
+%with complements $M_1, M_2, N_1, N_2$ respectively. Then: \todo {(This is a mess. String diagram?)}
+%\begin{align*}
+%&(\langle l_2, r_2 \rangle \otimes \langle p_2, q_2 \rangle) \circ (\langle l_1, r_1 \rangle \otimes \langle p_1, q_1 \rangle) \\
+%= \; &\langle (M_2 \otimes s_{S_3,N_2} \otimes T_3)(l_2 \otimes p_2), (r_2 \otimes q_2)(M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+%&\circ \langle (M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), (r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2') \rangle \\
+%= \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes N_1 \otimes l_2 \otimes p_2)(M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), \\
+%&\;(r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2')(M_1 \otimes N_1 \otimes r_2 \otimes q_2)(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+%= \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)(M_1 \otimes  l_2 \otimes N_1 \otimes p_2)(l_1 \otimes p_1), \\
+%&\;(r_1 \otimes q_1)(M_1 \otimes r_2 \otimes N_1 \otimes q_2)(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+%= \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1), \\
+%&\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+%= \; & \text{\todo{(Add a $s_{M_2, N_1}$ to either side of the coend, then appeal to coherence)}} \\
+%= \; &\langle (M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S_3} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1) ,  \\
+%&\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S'_3} \otimes T'_3) \rangle \\
+%= \; &\langle (M_1 \otimes l_2)l_1, r_1(M_1 \otimes r_2) \rangle \otimes \langle (N_1 \otimes p_2)p_1, q_1(N_1 \otimes q_2) \rangle \\
+%= \; &(\langle l_2, r_2 \rangle  \circ \langle l_1, r_1 \rangle) \otimes (\langle p_2, q_2 \rangle \circ \langle p_1, q_1 \rangle)
+%\end{align*}
 
@@
 \begin{align*}
-\alpha_{(R, R'), (S, S'), (T, T')} &:= (\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1})_* \\
-\lambda_{(S, S')} &:= (\lambda_{(S, S')}, \lambda_{(S, S')}^{-1})_* \\
-\rho_{(S, S')} &:= (\rho_{(S, S')}, \rho_{(S, S')}^{-1})_* \\
-s_{(S, S'), (T, T')} &:= (s_{S, T}, s_{T', S'})_*
-\end{align*}
-
-Note that because $(S, S')_* = (S, S')$, required equations for $(-, -)_*$ to be a monoidal functor hold by definition (although we don't yet know that $\Optic_\otimes$ is monoidal).
-The pentagon and triangle axioms then hold in $\Optic_\otimes$, as they are the image of the same axioms in $\C \times \C^\op$ under $(-, -)_*$.
-The only remaining piece to verify is that these structure maps are natural in $\Optic_\otimes$.
+\alpha_{(R, R'), (S, S'), (T, T')} &:= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1}) \\
+\lambda_{(S, S')} &:= \iota(\lambda_{(S, S')}, \lambda_{(S, S')}^{-1}) \\
+\rho_{(S, S')} &:= (\rho_{(S, S')}, \rho_{(S, S')}^{-1}) \\
+s_{(S, S'), (T, T')} &:= \iota(s_{S, T}, s_{T', S'})
+\end{align*}
+
+Note that because $\iota(S, S') = (S, S')$, required equations for $\iota$ to be a monoidal functor hold by definition (although we don't yet know that $\Optic_\otimes$ is monoidal).
+The pentagon and triangle axioms then hold in $\Optic_\otimes$, as they are the image of the same axioms in $\C \times \C^\op$ under $\iota$.
+The only remaining thing to verify is that these structure maps are natural in $\Optic_\otimes$.
 
@@
 &\alpha_{(R, R'), (S, S'), (T, T')} \circ (f \otimes (S, S')) \otimes (T, T') \\
-&= (\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1})_*  \circ (\langle l, r \rangle \otimes (S, S')) \otimes (T, T') \\
+&= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1})  \circ (\langle l, r \rangle \otimes (S, S')) \otimes (T, T') \\
 &= \langle\lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} \rangle  \circ \left\langle (l \otimes S) \otimes T, (r \otimes S') \otimes T' \right\rangle \\
@@
 &= \langle l \otimes (S \otimes T), r \otimes (S' \otimes T')\rangle \circ \left\langle \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')} \right\rangle \\
-&= \langle l, r \rangle \otimes ((S, S') \otimes (T, T')) \circ (\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1})_* \\
+&= \langle l, r \rangle \otimes ((S, S') \otimes (T, T')) \circ \iota(\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}) \\
 &= f \otimes ((S, S') \otimes (T, T')) \circ \alpha_{(Q, Q'), (S, S'), (T, T')} 
@@
 
+\begin{proposition}
+Any isomorphism $p : (S, S') \hto (A, A')$ in $\Optic_\C$ is of the form $\iota(f, g)$ for two isomorphisms $S \to A$ and $A' \to S'$ in $\C$.
+\end{proposition}
+\begin{proof}
+
+\end{proof}
+
 There is some further useful structure in $\Optic_\C$. 
 \begin{proposition}
+\label{prop-costates}
 The set of costates $(S, S') \hto (I, I)$ is isomorphic to $\C(S, S')$.
@@
 
-States are not as easy to describe in general:
+States are not as easy to describe in general, however:
 
@@
 
+\begin{proposition}
 \todo{Entrywise Coproduct}
+\end{proposition}
+
+\begin{remark}
+The motivating example here is that of coproducts distributing over the tensor product.
+\end{remark}
 
@@
 \begin{proof}
+On objects this is simply $\Optic(F)(S, S') = (FS, FS')$. The action on morphisms $\Optic_\C((S, S'), (A, A'))$ is induced by
+\begin{align*}
+&\C(S, M \otimes A) \times \C(M \otimes A', S) \\
+\to &\D(FS, F(M \otimes A)) \times \D(F(M \otimes A'), FS) \\
+\to &\D(FS, FM \otimes FA) \times \D(FM \otimes FA', FS) \\
+\to &\int^{N \in \D} \D(FS, N \otimes FA) \times \D(N \otimes FA', FS).
+\end{align*}
+where we have used the strong monoidal isomorphism in both directions.
+\todo{use equations instead}
+\todo{argue for functoriality}
+\end{proof}
+
+\begin{proposition}
+Together this operation defines a \todo{pseudo?}functor $\Optic : \SymmMonCat \to \SymmMonCat$.
+\end{proposition}
+\begin{proof}
 \todo{todo}
@@
 
-\begin{proposition}
-These assignments assemble into a \todo{pseudo?}functor $\Optic : \SymmMonCat \to SymmMonCat$.
-\end{proposition}
-\begin{proof}
-\todo{todo}
-\end{proof}
-
 \subsection{Teleological Categories}
 
-As noted in \cite{CoherenceForLenses},
+As noted in \cite{CoherenceForLenses}, \todo{the category of optics admits its own string diagram language}
 
@@
 \begin{itemize}
-\item A wide symmetric monoidal subcategory $\C_d$ of dualisable morphisms, with an involutive symmetric monoidal functor $(-)^* : \C_d^\op \to \C_d$
-\item A family of morphisms $\epsilon_X : X \otimes X^* \to I$, called \emph{counits}, natural with respect to the morphisms in $\C_d$,
+\item A wide symmetric monoidal subcategory $\C_d$ of dualisable morphisms, with an involutive strong symmetric monoidal functor $(-)^* : \C_d^\op \to \C_d$
+\item A symmetric monoidal extranatural family of morphisms $\varepsilon_X : X \otimes X^* \to I$, called \emph{counits}, natural with respect to the morphisms in $\C_d$.
 \end{itemize}
-such that the diagrams
-blah
-commute.
 \end{definition}
-
-In the case of optics, 
-The identity morphism $\C(S, S)$ gives us a preoptic $\varepsilon : (S, S) \to (I, I)$ that we call the \emph{counit}.
-
-\begin{proposition}
-With the above data, the category $\Optic_\C$ is a teleological category.
-\end{proposition}
-\begin{proof}
-\todo{todo}
-\end{proof}
-
-We can therefore
-
-As conjectured by Jules Hedges, the structure of a teleological category is precisely what is added by $\Optic$.
+\todo{The involution bit seems to be almost the same as asking for a symmetric monoidal dagger-category, that is stricter than this though}
+
+Unpacking the definition, $\varepsilon$ being a monoidal extranatural transformation amounts to the following diagrams in $\C$ commuting:
+\[
+\begin{tikzcd}
+X \otimes Y^* \ar[r, "f \otimes Y^*"]  \ar[d, "X \otimes f^*", swap] & Y \otimes Y^* \ar[d, "\varepsilon_Y"] \\
+X \otimes X^* \ar[r, "\varepsilon_X", swap] & I
+\end{tikzcd} \hspace{1cm}
+\begin{tikzcd}
+X^* \otimes X \ar[r, "\sigma"]  \ar[dr, "\varepsilon_{X^*}", swap] & X \otimes X^* \ar[d, "\varepsilon_X"] \\
+& I
+\end{tikzcd} \hspace{1cm}
+\begin{tikzcd}
+X \otimes Y \otimes X^* \otimes Y^* \ar[r, "X \otimes s \otimes X^*"]  \ar[dr, "\varepsilon_{X \otimes Y}", swap] & X \otimes X^* \otimes Y \otimes Y^* \ar[d, "\varepsilon_X \otimes \varepsilon_Y"] \\
+& I
+\end{tikzcd}
+\] 
+where $f : X \to Y$ is in $\C_d$. \todo{Is that last one actually something extra? It seems like the duality should also reverse the order of tensor, or something}
+
+\begin{proposition}
+$\Optic_\C$ forms a teleological category, with the following data:
+\begin{itemize}
+\item The dualisable morphisms are all morphisms of the form $\iota(f, g)$;
+\item The involution is given on objects by $(S, S')^* = (S', S)$, and on a morphism $\iota(f, g)$ by $\iota(g, f)$;
+\item The counit $\varepsilon_{(S, S')}$  is given by the image of the symmetry $s_{S \otimes S'}$ under the isomorphism of Proposition \ref{prop-costates}.
+\end{itemize}
+\end{proposition}
+\begin{proof}
+That morphisms of the form $\iota(f, g)$ constitute a category and that $\iota$ is a symmetric monoidal involution is clear.
+
+To check extranaturality, suppose we have a dualisable optic $\iota(f, g) : (X, X') \to (Y, Y')$, so $f : X \to Y$ and $g : Y' \to X'$.
+Extranaturality is witnessed by the equality of the string diagrams:
+\begin{center}
+\includegraphics[width=.4\textwidth]{diagrams/counit-extranaturality}
+\end{center}
+Symmetry:
+\begin{center}
+\includegraphics[width=.4\textwidth]{diagrams/counit-symmetry}
+\end{center}
+Monoidal:
+\begin{center}
+\includegraphics[width=.4\textwidth]{diagrams/counit-monoidal}
+\end{center}
+\end{proof}
+
+\todo{They stress about the empty set, does this matter here?}
+
+As conjectured by Jules Hedges, the structure of a teleological category is precisely what is added by forming the $\Optic$ category.
 \begin{theorem}
@@
 
-Let $\C$ be a category and $(\M, \otimes, I)$ a monoidal category that acts on $\C$.
+To capture the \texttt{Iso}s, \texttt{Traversal}s and \texttt{Setter}s of the Haskell \texttt{lens} library, we generalise to the case of a monoidal action of one category on another.
+
+\begin{definition}
+Let $\C$ be a category and $(\M, \otimes, I)$ a monoidal category.
+An \emph{action of $\M$ on $\C$} is a strong monoidal functor $a : \M \to [\C, \C]$.
+The action of an object $M \in \M$ on $A \in \C$ is written $MA$.
+\end{definition}
+
+Given such an action, we define 
+\begin{align*}
+\Optic_\M((S, S'), (A, A')) := \int^{M \in \C} \C(S, MA) \times \C(MA', S')
+\end{align*}
+
+\begin{proposition}
+We have a category $\Optic_\M$ and a functor $\iota : \C \times \C^\op \to \Optic_\M$. \qed
+\end{proposition}
+
+\subsection{Polymorphic Optics}
 
 \section{Lawful Optics}
+\todo{intro}
+
+\begin{remark}
 In this section we will focus only on preoptics of the form $p : (S,S) \hto (A, A)$.
-In what follows, we abbreviate $\Optic_\M((S, S), (A, A))$ as $\Optic_\M(S, A)$ and $p : (S, S) \hto (A, A)$ as $p : S \hto A$.
+We therefore abbreviate $\Optic_\M((S, S), (A, A))$ as $\Optic_\M(S, A)$ and $p : (S, S) \hto (A, A)$ as $p : S \hto A$.
+\end{remark}
 
@@
 \begin{proposition}
-\label{prop-onthenose}
-If $p : S \to A$ is an optic, then there exists a representative $p = \langle l, r \rangle$ such that $rl = \phi A$ on the nose for some $\phi : M \to M$.
-\end{proposition}
-\begin{proof}
-\todo{This is painful but seems important. There may be a more general principle at work here but I couldn't see it.}
-
-\todo{Put in an appendix?}
-
-There is a well known formula for the coend as the coequaliser in the diagram
-\[
-\begin{tikzcd}
-\coprod_{M \to N} P(N, M) \ar[r,shift left=.75ex]  \ar[r,shift right=.75ex] & \coprod_{M \in \M} P(M, M) \ar[r] & \int^{M \in \M} P(M, M)
-\end{tikzcd}
-\]
-where $P$ is a functor $\M^\op \times \M \to \E$.
-
-In our case $\E = \Set$, and unwinding the coequaliser this states that $\int^{M \in \M} \C(M A, M A)$ is a quotient of the set $\coprod_{M \in \M} \C(M A, M A)$.
-Two morphisms $f : M A \to M A$ and $g : N A \to N A$ are identified when there exists a $k : N A \to M A$ and natural transformation $\phi : M \to N$ such that the diagram
-\[
-\begin{tikzcd}
-M A \ar[r, "\phi_A"] \ar[d, "f", swap] & N A \ar[d, "g"] \ar[dl, "k"] \\
-M A \ar[r, "\phi_A", swap] & N A
-\end{tikzcd}
-\]
-commutes.
-This gives a binary relation $f \rightsquigarrow g$ that is not likely to be symmetric or transitive.
-The coend is obtained by identifying all morphisms related in this way, so in all, $\langle f \rangle = \langle g \rangle$ iff there exists a zigzag $f \leftrightsquigarrow u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n \leftrightsquigarrow g$ where the relation may apply in either direction.
-\todo{replace this with $f = u_1 \leftrightsquigarrow \dots u_n = g$ for clarity}
-
-If $f \rightsquigarrow g$ then $f^2 \rightsquigarrow g^2$: this is clear by stacking the above diagram, and then taking $k' = fk = kg$.
-This argument extends to show that $f^n \rightsquigarrow g^n$ for any $n$.
-
-Similarly unwinding the coequaliser for $\int^{M \in \M} \C(S, M A) \times \C(M A, S)$, two pairs $(l, r) : (S \to M A, MA \to S)$ and $(l', r') : (S \to NA, NA \to S)$ in $\coprod_{M \in \M} \C(S, M A) \times \C(M A, S)$ are identified when there exists a $\phi : M \to N$ such that
-\[
-\begin{tikzcd}
-M A \ar[r, "\phi_A"] \ar[d, "r", swap] & N A \ar[d, "r'"] \\
-S \ar[r, equal] \ar[d, "l", swap] & S \ar[d, "l'"]  \\
-MA \ar[r, "\phi_A"] & N A
-\end{tikzcd}
-\]
-commutes. \todo{put the $S$ on the outside?}
-
-We will now prove the result by induction.
-Because $inside(p) = \langle t \rangle$, there is a representative $\langle l, r \rangle$ so that $\langle lr \rangle = \langle t \rangle$.
-There therefore must exist a finite chain of relations $lr \leftrightsquigarrow u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n \leftrightsquigarrow t$.
-Supposing that the first relation faces rightwards, we have a diagram:
-\[
-\begin{tikzcd}
-M A \ar[r, "\phi_A"] \ar[d, "r", swap] & N A \ar[dd, "u_1"] \ar[ddl, "k"] \\
-S \ar[d,"l",swap] & \\
-M A \ar[r, "\phi_A", swap] & N A
-\end{tikzcd}
-\]
-Note that $r = rlr = rk\phi_A$. We therefore have the commutative diagram
-\[
-\begin{tikzcd}
-M A \ar[r, "\phi_A"] \ar[d, "r", swap] & N A \ar[d, "rk"] \\
-S \ar[r, equal] \ar[d, "l", swap] & S \ar[d, "\phi_Al"] \\
-MA \ar[r, "\phi_A", swap] & N A
-\end{tikzcd}
-\]
-where the composite of the morphisms on the right is $\phi_A l r k = \phi_A k \phi_A k = u_1^2$.
-Composing in the other direction we have $r k \phi_A l = rlrl = \id_S$.
-We have shown that whenever $rl = \id_S$ and $lr \rightsquigarrow u_1$, then there exist $l_1$ and $r_1$ so that $r_1l_1 = \id_S$, $l_1r_1 = u_1^2$ and $(l, r) \rightsquigarrow (l_1, r_1)$.
-A symmetric argument shows that if instead $lr \leftsquigarrow g$, there exist $l_1$ and $r_1$ so that $r_1l_1 = \id_S$, $l_1r_1 = u_1^2$ and $(l, r) \leftsquigarrow (l_1, r_1)$.
-
-We can now inductively apply the above argument to the chain $u_1^2 \leftrightsquigarrow \dots \leftrightsquigarrow u_n^2 \leftrightsquigarrow t^2 = t$, obtained by squaring each morphism in the original chain.
-We eventually obtain a chain $(l, r) \leftrightsquigarrow (l_1, r_1)\leftrightsquigarrow \dots \leftrightsquigarrow (l_n, r_n) \leftrightsquigarrow (l_t, r_t)$, where $r_tl_t = \id_S$ and $l_t r_t = t$.
-This pair $(l_t, r_t)$ is the required representative.
-\end{proof}
-
-The above argument has a similar form to some that appear in \cite{OnTheTrace}, which considered (among other things) coends of the form $\int^{c \in \C} \C(c, Fc)$ for an endofunctor $F : \C \to \C$.
-
-In view of this Proposition, whenever we posit a representative $\langle l, r \rangle$ of an optic, we may assume that $lr = \phi A$ on the nose, for some $\phi : M \to M$.
-
-\begin{proposition}
 There is an subcategory $\Lawful_\C$ of $\Optic_\C$ given by objects of the form $(X, X)$ and lawful optics between them.
@@
 \begin{proof}
-The identity preoptic $(\id_X, \id_X)_*$ is clearly an optic.
+The identity preoptic $\iota(\id_X, \id_X)$ is clearly an optic.
 
@@
 
+\begin{proposition}
+\label{prop-onthenose}
+If $p : S \to A$ is a lawful optic, then there exists a representative $p = \langle l, r \rangle$ such that $rl = \phi A$ on the nose for some $\phi : M \to M$.
+\end{proposition}
+\begin{proof}
+\todo{This is painful but seems important. There may be a more general principle at work here but I couldn't see it.}
+
+\todo{Put in an appendix?}
+
+There is a well known formula for the coend as the coequaliser in the diagram
+\[
+\begin{tikzcd}
+\coprod_{M \to N} P(N, M) \ar[r,shift left=.75ex]  \ar[r,shift right=.75ex] & \coprod_{M \in \M} P(M, M) \ar[r] & \int^{M \in \M} P(M, M)
+\end{tikzcd}
+\]
+where $P$ is a functor $\M^\op \times \M \to \E$.
+
+In our case $\E = \Set$, and unwinding the coequaliser this states that $\int^{M \in \M} \C(M A, M A)$ is a quotient of the set $\coprod_{M \in \M} \C(M A, M A)$.
+Two morphisms $f : M A \to M A$ and $g : N A \to N A$ are identified when there exists a $k : N A \to M A$ and natural transformation $\phi : M \to N$ such that the diagram
+\[
+\begin{tikzcd}
+M A \ar[r, "\phi_A"] \ar[d, "f", swap] & N A \ar[d, "g"] \ar[dl, "k"] \\
+M A \ar[r, "\phi_A", swap] & N A
+\end{tikzcd}
+\]
+commutes.
+This gives a binary relation $f \rightsquigarrow g$ that is not likely to be symmetric or transitive.
+The coend is obtained by identifying all morphisms related in this way, so in all, $\langle f \rangle = \langle g \rangle$ iff there exists a zigzag $f \leftrightsquigarrow u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n \leftrightsquigarrow g$ where the relation may apply in either direction.
+\todo{replace this with $f = u_1 \leftrightsquigarrow \dots u_n = g$ for clarity}
+
+If $f \rightsquigarrow g$ then $f^2 \rightsquigarrow g^2$: this is clear by stacking the above diagram, and then taking $k' = fk = kg$.
+This argument extends to show that $f^n \rightsquigarrow g^n$ for any $n$.
+
+Similarly unwinding the coequaliser for $\int^{M \in \M} \C(S, M A) \times \C(M A, S)$, two pairs $(l, r) : (S \to M A, MA \to S)$ and $(l', r') : (S \to NA, NA \to S)$ in $\coprod_{M \in \M} \C(S, M A) \times \C(M A, S)$ are identified when there exists a $\phi : M \to N$ such that
+\[
+\begin{tikzcd}
+M A \ar[r, "\phi_A"] \ar[d, "r", swap] & N A \ar[d, "r'"] \\
+S \ar[r, equal] \ar[d, "l", swap] & S \ar[d, "l'"]  \\
+MA \ar[r, "\phi_A"] & N A
+\end{tikzcd}
+\]
+commutes. \todo{put the $S$ on the outside?}
+
+We will now prove the result by induction.
+Because $inside(p) = \langle t \rangle$, there is a representative $\langle l, r \rangle$ so that $\langle lr \rangle = \langle t \rangle$.
+There therefore must exist a finite chain of relations $lr \leftrightsquigarrow u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n \leftrightsquigarrow t$.
+Supposing that the first relation faces rightwards, we have a diagram:
+\[
+\begin{tikzcd}
+M A \ar[r, "\phi_A"] \ar[d, "r", swap] & N A \ar[dd, "u_1"] \ar[ddl, "k"] \\
+S \ar[d,"l",swap] & \\
+M A \ar[r, "\phi_A", swap] & N A
+\end{tikzcd}
+\]
+Note that $r = rlr = rk\phi_A$. We therefore have the commutative diagram
+\[
+\begin{tikzcd}
+M A \ar[r, "\phi_A"] \ar[d, "r", swap] & N A \ar[d, "rk"] \\
+S \ar[r, equal] \ar[d, "l", swap] & S \ar[d, "\phi_Al"] \\
+MA \ar[r, "\phi_A", swap] & N A
+\end{tikzcd}
+\]
+where the composite of the morphisms on the right is $\phi_A l r k = \phi_A k \phi_A k = u_1^2$.
+Composing in the other direction we have $r k \phi_A l = rlrl = \id_S$.
+We have shown that whenever $rl = \id_S$ and $lr \rightsquigarrow u_1$, then there exist $l_1$ and $r_1$ so that $r_1l_1 = \id_S$, $l_1r_1 = u_1^2$ and $(l, r) \rightsquigarrow (l_1, r_1)$.
+A symmetric argument shows that if instead $lr \leftsquigarrow g$, there exist $l_1$ and $r_1$ so that $r_1l_1 = \id_S$, $l_1r_1 = u_1^2$ and $(l, r) \leftsquigarrow (l_1, r_1)$.
+
+We can now inductively apply the above argument to the chain $u_1^2 \leftrightsquigarrow \dots \leftrightsquigarrow u_n^2 \leftrightsquigarrow t^2 = t$, obtained by squaring each morphism in the original chain.
+We eventually obtain a chain $(l, r) \leftrightsquigarrow (l_1, r_1)\leftrightsquigarrow \dots \leftrightsquigarrow (l_n, r_n) \leftrightsquigarrow (l_t, r_t)$, where $r_tl_t = \id_S$ and $l_t r_t = t$.
+This pair $(l_t, r_t)$ is the required representative.
+\end{proof}
+
+The above argument has a similar form to some that appear in \cite{OnTheTrace}, which considered (among other things) coends of the form $\int^{c \in \C} \C(c, Fc)$ for an endofunctor $F : \C \to \C$.
+
+In view of this Proposition, whenever we posit a representative $\langle l, r \rangle$ of an optic, we may assume that $lr = \phi A$ on the nose, for some $\phi : M \to M$.
+
 \subsection{Examples}
@@
 Suppose $\C$ has finite products, and let $\C$ act on itself via the bifunctor $\times : \C \times \C \to \C$.
-The \emph{category of lenses} $\Lens$ is the category of optics with respect to this action: $\Lens = \Optic_\times$.
+The \emph{category of lenses} $\Lens$ is the category of optics with respect to this action: $\Lens = \Lawful_\times$.
 \end{definition}
@@
 
+\subsubsection{Isos}
+
 \subsubsection{Setters}
@@
 
-\subsection{Change of Action}
-
-\todo{TODO}
-
 \section{Profunctor Optics}

### 2018-03-02 paper.tex
Fix some old references to prethings

@@
 \begin{remark}
-In this section we will focus only on preoptics of the form $p : (S,S) \hto (A, A)$.
+In this section we will focus only on optics of the form $p : (S,S) \hto (A, A)$.
 We therefore abbreviate $\Optic_\M((S, S), (A, A))$ as $\Optic_\M(S, A)$ and $p : (S, S) \hto (A, A)$ as $p : S \hto A$.
@@
 \begin{definition}
-An preoptic $p : S \hto A$ is an \emph{optic} if $outside(p) = \id_S$, and $inside(p) = \langle t A \rangle$ for some $t : M \to M$ in $\M$.
+An optic $p : S \hto A$ is \emph{lawful} if $outside(p) = \id_S$, and $inside(p) = \langle t A \rangle$ for some $t : M \to M$ in $\M$.
 \end{definition}
@@
 \begin{proof}
-The identity preoptic $\iota(\id_X, \id_X)$ is clearly an optic.
-
-Suppose we have two optics $\langle l, r \rangle : R \hto S$ and $\langle l', r' \rangle : S \hto A$, where $l : R \to MS$ and $l' : S \to NA$, and such that $lr = \phi S$ and $l'r' = \psi A$.
-Then the composite $\langle (Ml')l, r (Mr')  \rangle$ is also an optic:
+The identity optic $\iota(\id_X, \id_X)$ is clearly lawful.
+
+Suppose we have two lawful optics $\langle l, r \rangle : R \hto S$ and $\langle l', r' \rangle : S \hto A$, where $l : R \to MS$ and $l' : S \to NA$, and such that $lr = \phi S$ and $l'r' = \psi A$.
+Then the composite $\langle (Ml')l, r (Mr')  \rangle$ is also a lawful optic:
 \begin{align*}
@@
 
-In view of this Proposition, whenever we posit a representative $\langle l, r \rangle$ of an optic, we may assume that $lr = \phi A$ on the nose, for some $\phi : M \to M$.
+In view of this Proposition, whenever we posit a representative $\langle l, r \rangle$ of an lawful optic, we may assume that $lr = \phi A$ on the nose, for some $\phi : M \to M$.
 
@@
 Suppose $\C$ has finite products, and let $\C$ act on itself via the bifunctor $\times : \C \times \C \to \C$.
-The \emph{category of lenses} $\Lens$ is the category of optics with respect to this action: $\Lens = \Lawful_\times$.
+The \emph{category of lenses} $\Lens$ is the category of lawful optics with respect to this action: $\Lens = \Lawful_\times$.
 \end{definition}
 
-As remarked in the introduction \todo{(todo: remark in the introduction)}, the preoptics for this action are exactly pairs of $\fget$ and $\fput$ functions.
+As remarked in the introduction \todo{(todo: remark in the introduction)}, the optics for this action are exactly pairs of $\fget$ and $\fput$ functions.
 \begin{align*}
@@
 
-This has been written out many times before in the case when $lr$ is the identity \cite{IsomorphismLensesPost} \todo{more}.
+This has been written out many times before in the case when $lr$ is the identity \cite{IsomorphismLensesPost}, we note here that the weaker condition is sufficient.
 
@@
 Suppose $\C$ has finite coproducts, and let $\C$ act on itself via the bifunctor $\sqcup : \C \times \C \to \C$.
-The \emph{category of prisms} is the category of optics with respect to this action: $\Prism = \Optic_\sqcup$.
+The \emph{category of prisms} is the category of lawful optics with respect to this action: $\Prism = \Lawful_\sqcup$.
 \end{definition}
 
-Just as prelenses correspond to a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$, prisms correspond to pairs of maps $\freview : A \to S$ and $\fmatching : S \to S \sqcup A$.
+Just as (possibly unlawful) lenses correspond to a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$, (unlawful) prisms correspond to pairs of maps $\freview : A \to S$ and $\fmatching : S \to S \sqcup A$.
 These names are taken from the Haskell \texttt{lens} library.
@@
 \end{align*}
-So, if we are given a pre-prism $\langle l, r \rangle : (S, S) \hto (A, A)$ then associated $\freview$ and $\fmatching$ morphisms are given by $\freview = r \inr$ and $\fmatching = (r\inl \sqcup A)l$
+So, if we are given a prism $\langle l, r \rangle : (S, S) \hto (A, A)$ then associated $\freview$ and $\fmatching$ morphisms are given by $\freview = r \inr$ and $\fmatching = (r\inl \sqcup A)l$
 
@@
 
-\subsection{Preoptics}
+\subsection{Optics}
 
@@
 
-We can now show that profunctor preoptics are precisely preoptics in the ordinary sense.
+We can now show that profunctor optics are precisely optics in the ordinary sense.
 
@@
 \begin{corollary}
-A profunctor preoptic is determined by its component at $\Pastro_\M E_A$, and furthermore, this component is determined by its value on $\langle \id_A, \id_A, \id_A, \id_A \rangle \in (U \Pastro_\M E_A)(A, A)$.
+A profunctor optic is determined by its component at $\Pastro_\M E_A$, and furthermore, this component is determined by its value on $\langle \id_A, \id_A, \id_A, \id_A \rangle \in (U \Pastro_\M E_A)(A, A)$.
 \end{corollary}
@@
 \begin{proposition}
-If $p : S \hto A$ is an optic then the associated natural transformation $(U-)(A,A) \to (U-)(S,S)$ is a lax monoidal. \todo{Rename the natural transformation $p$}
+If $p : S \hto A$ is a lawful optic then the associated natural transformation $(U-)(A,A) \to (U-)(S,S)$ is a lax monoidal. \todo{Rename the natural transformation $p$}
 \end{proposition}

### 2018-03-04 paper.tex
Some fixes

@@
 To be maximally careful, we should only ever discuss $\Optic$ categories where we know that the coend exists by some other means, e.g., by exhibiting an isomorphism with some other set.
-For many, but not all, of the examples given later, we provide such an isomorphism.
+For many---but not all---of the examples given later, we provide such an isomorphism.
 
@@
 \begin{proposition}
-For any $\C$, there is a functor $\iota : \C \times \C^\op \to \Optic_\C$, which is given on objects by $\iota(S, S') = (S, S')$ and for a morphism $(f, g) : (S, S') \to (A, A')$ by $\iota(f, g) = \langle \lambda_A^{-1} f, g \lambda_{A'} \rangle$.
+There is a functor $\iota : \C \times \C^\op \to \Optic_\C$, which is given on objects by $\iota(S, S') = (S, S')$ and for a morphism $(f, g) : (S, S') \to (A, A')$ by $\iota(f, g) = \langle \lambda_A^{-1} f, g \lambda_{A'} \rangle$.
 \end{proposition}
@@
 \end{proof}
+
+\begin{remark}
+This functor is not necessarily faithful, see Remark \ref{lens-iota-not-faithful}
+\end{remark}
 
@@
 \item The counit $\varepsilon_{(S, S')}$  is given by the image of the symmetry $s_{S \otimes S'}$ under the isomorphism of Proposition \ref{prop-costates}.
+\todo{It is a little annoying that a twist is necessary, but it has to go somewhere.
+The other option is in the definition of $\otimes$ but that seems worse.}
 \end{itemize}
@@
 \begin{proof}
-That morphisms of the form $\iota(f, g)$ constitute a category and that $\iota$ is a symmetric monoidal involution is clear.
+That morphisms of the form $\iota(f, g)$ constitute a category and that $\iota$ is a symmetric monoidal involution is clear. \todo{actually check monoidal part}
 
@@
 
+\begin{remark} \label{lens-iota-not-faithful}
+For the category of sets, the functor $\iota(-, -) : \Set \times \Set^\op \to \Optic_\times$ is not faithful.
+The problem is the empty set: the functor $0 \times (-)$ is not faithful.
+Any pair of maps $f : 0 \to A$, $g : A' \to S'$ yield equivalent optics $\iota(f, g)$, as the corresponding $\fget$ and $\fput$ functions must be the unique maps from $0$.
+
+\todo{Show that for the category of nonempty sets things .}
+\end{remark}
+
 \begin{proposition}
 \label{prop-OpticImpliesLensLaws}
-Suppose $\langle l, r \rangle : S \hto A$ is a lens, i.e. that $rl = \id_S$ and $\langle lr \rangle = \langle \phi \times A \rangle$ for some $\phi : M \to M$. Then $p$ obeys the three lens laws.
+Suppose $\langle l, r \rangle : S \hto A$ is a lawful lens in our sense, i.e.
+that $rl = \id_S$ and $\langle lr \rangle = \langle \phi \times A \rangle$ for some $\phi : M \to M$.
+Then $\fput$ and $\fget$ for this lens obey the three lens laws.
 \end{proposition}
@@
 \begin{proposition}
-Suppose there exists a map $x : 1 \to A$. Then if $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the three lens laws then the corresponding $p : S \hto A$ is a lens.
+Suppose there exists a map $x : 1 \to A$. Then if $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the three lens laws then the corresponding $p : S \hto A$ is a lawful lens.
 \end{proposition}
@@
 \begin{proposition}
-Suppose $\C$ has finite limits and that there is a morphism $x : 1 \to A$.
+Suppose $\C$ has pullbacks and that there is a morphism $x : 1 \to A$.
 If $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the three lens laws then there exists $C \in \C$ with $S \cong C \times A$.

### 2018-03-12 paper.tex
Small updates

@@
 \usetikzlibrary{arrows}
-
-\usepackage{adjustbox}
-\usepackage{etoolbox}
-\BeforeBeginEnvironment {tikzpicture}{\begin{adjustbox}{valign=m}}
-\AfterEndEnvironment {tikzpicture}{\end{adjustbox}}
+\input{tikzcurverel}
 
@@
 \newcommand{\N}{\mathscr{N}}
+\newcommand{\T}{\mathscr{T}}
 
@@
 \newcommand{\SymmMonCat}{\mathbf{SymmMonCat}}
+\newcommand{\Tele}{\mathbf{Tele}}
 
@@
 \begin{remark}
-\todo{I hope I can get away with this...} In what follows, we use the standard cheat of omitting associativity isomorphisms
+\todo{I hope I can get away with this...} In what follows, we use the standard cheat of omitting associativity isomorphisms.
 \end{remark}
 
+\begin{definition}
 Let $\C$ be a symmetric monoidal category, and suppose we have two pairs of objects $(S, S')$ and $(A, A')$. An \emph{optic} $p : (S, S') \hto (A, A')$ is an element of the set
@@
 \end{align*}
+\end{definition}
+
 If $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\langle l, r \rangle : (S, S') \hto (A, A')$ for the image of this pair in $\Optic_\C((S, S'), (A, A'))$, and say that $M$ is the complement for this representative.
@@
 \end{center}
-reading left to right, so the left half of the diagram represents $l$ and the right half $r$. The relation imposed by the coend takes the following form:
+reading left to right, so the left half of the diagram represents $l$ and the right half $r$. The relation imposed by the coend equates the following two diagrams:
 \begin{center}
-\input{diagrams/coend-relation-left.tikz} \quad $=$ \quad \input{diagrams/coend-relation-right.tikz}
+\input{diagrams/coend-relation-left.tikz} 
+\qquad
+\input{diagrams/coend-relation-right.tikz}
 \end{center}
@@
 \begin{remark}
-This functor is not necessarily faithful, see Remark \ref{lens-iota-not-faithful}
+This functor is not necessarily faithful, see Remark \ref{lens-iota-not-faithful}.
 \end{remark}
@@
 
+%\begin{theorem}
+%$\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit is $(I, I)$, and the action on morphisms induced by
+%\begin{align*}
+%&\C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(T, N \otimes B) \times \C(N \otimes B', T')\\
+%\to \quad&\C(S \otimes T, M \otimes A \otimes N \otimes B) \times \C(M \otimes A' \otimes N \otimes B', S' \otimes T') && \text{(action of $\otimes$ on morphisms in $\C$)}\\
+%\to \quad&\C(S \otimes T, M \otimes N \otimes A \otimes B) \times \C(M \otimes N \otimes A' \otimes B', S' \otimes T') && \text{($\otimes$ in $\C$ is symmetric)}\\
+%\to \quad&\int^{M \in \C} \C(S \otimes T, M \otimes A \otimes B) \times \C(M \otimes A' \otimes B', S' \otimes T') && \text{(inclusion into coend)}
+%\end{align*}
+%\end{theorem}
+%\begin{proof}
+%Equationally, suppose we have representatives $(l, r) : (S \to M \otimes A, M \otimes A' \to S')$ and $(l', r') : (T \to N \otimes B, N \otimes B' \to T')$. Then:
+%\begin{align*}
+%\langle l, r \rangle \otimes \langle l', r' \rangle &:= \langle (M \otimes s_{A,N} \otimes B)(l \otimes l'), (r \otimes r')(M \otimes s_{A',N} \otimes B') \rangle
+%\end{align*}
+%This is functorial, as suggested by the equivalence of the following string diagrams:
+%\todo{todo}
+%%For future convenience, note that 
+%%\begin{align*}
+%%\langle l, r \rangle \otimes (T, T') &= \langle (M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T') \rangle \\
+%%&= \langle (\lambda^{-1}_M \otimes A \otimes T)(M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T')(\lambda_M \otimes A' \otimes T') \rangle \\
+%%&= \langle l \otimes T, r \otimes T' \rangle
+%%\end{align*}
+%%Now we check functoriality. Suppose we have:
+%%\begin{align*}
+%%\langle l_1, r_1 \rangle : (S_1, S_1') &\hto (S_2, S_2') \\
+%%\langle l_2, r_2 \rangle : (S_2, S_2') &\hto (S_3, S_3') \\
+%%\langle p_1, q_1 \rangle : (T_1, T_1') &\hto (T_2, T_2') \\
+%%\langle p_2, q_2 \rangle : (T_2, T_2') &\hto (T_3, T_3')
+%%\end{align*}
+%%with complements $M_1, M_2, N_1, N_2$ respectively. Then: \todo {(This is a mess. String diagram?)}
+%%\begin{align*}
+%%&(\langle l_2, r_2 \rangle \otimes \langle p_2, q_2 \rangle) \circ (\langle l_1, r_1 \rangle \otimes \langle p_1, q_1 \rangle) \\
+%%= \; &\langle (M_2 \otimes s_{S_3,N_2} \otimes T_3)(l_2 \otimes p_2), (r_2 \otimes q_2)(M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+%%&\circ \langle (M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), (r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2') \rangle \\
+%%= \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes N_1 \otimes l_2 \otimes p_2)(M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), \\
+%%&\;(r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2')(M_1 \otimes N_1 \otimes r_2 \otimes q_2)(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+%%= \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)(M_1 \otimes  l_2 \otimes N_1 \otimes p_2)(l_1 \otimes p_1), \\
+%%&\;(r_1 \otimes q_1)(M_1 \otimes r_2 \otimes N_1 \otimes q_2)(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+%%= \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1), \\
+%%&\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+%%= \; & \text{\todo{(Add a $s_{M_2, N_1}$ to either side of the coend, then appeal to coherence)}} \\
+%%= \; &\langle (M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S_3} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1) ,  \\
+%%&\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S'_3} \otimes T'_3) \rangle \\
+%%= \; &\langle (M_1 \otimes l_2)l_1, r_1(M_1 \otimes r_2) \rangle \otimes \langle (N_1 \otimes p_2)p_1, q_1(N_1 \otimes q_2) \rangle \\
+%%= \; &(\langle l_2, r_2 \rangle  \circ \langle l_1, r_1 \rangle) \otimes (\langle p_2, q_2 \rangle \circ \langle p_1, q_1 \rangle)
+%%\end{align*}
+%
+%The structure morphisms are all lifted from the structure morphisms in $\C$:
+%\begin{align*}
+%\alpha_{(R, R'), (S, S'), (T, T')} &:= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1}) \\
+%\lambda_{(S, S')} &:= \iota(\lambda_{(S, S')}, \lambda_{(S, S')}^{-1}) \\
+%\rho_{(S, S')} &:= (\rho_{(S, S')}, \rho_{(S, S')}^{-1}) \\
+%s_{(S, S'), (T, T')} &:= \iota(s_{S, T}, s_{T', S'})
+%\end{align*}
+% 
+%Note that because $\iota(S, S') = (S, S')$, required equations for $\iota$ to be a monoidal functor hold by definition (although we don't yet know that $\Optic_\otimes$ is monoidal).
+The pentagon and triangle axioms then hold in $\Optic_\otimes$, as they are the image of the same axioms in $\C \times \C^\op$ under $\iota$.
+The only remaining thing to verify is that these structure maps are natural in $\Optic_\otimes$.
+%
+%Let us check that $\alpha_{(R, R'), (S, S'), (T, T')}$ is natural in $(R, R')$. Suppose $f : (Q, Q') \hto (R, R')$ has representative $(l, r) : (Q \to M \otimes R, M \otimes R' \to Q')$, then:
+%\begin{align*}
+%&\alpha_{(R, R'), (S, S'), (T, T')} \circ (f \otimes (S, S')) \otimes (T, T') \\
+%&= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1})  \circ (\langle l, r \rangle \otimes (S, S')) \otimes (T, T') \\
+%&= \langle\lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} \rangle  \circ \left\langle (l \otimes S) \otimes T, (r \otimes S') \otimes T' \right\rangle \\
+%&=\left\langle (M \otimes \lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T})((l \otimes S) \otimes T), ((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} ) \right\rangle \\
+%&=\left\langle (M \otimes \alpha_{R,S,T})((l \otimes S) \otimes T), ((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} )\right\rangle \\
+%&=\left\langle (l \otimes (S \otimes T))\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}(r \otimes (S' \otimes T')) \right\rangle \\
+%&= \langle (I \otimes l \otimes (S \otimes T)) \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}, (I \times r \otimes (S' \otimes T')) \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')}\rangle \\
+%&= \langle l \otimes (S \otimes T), r \otimes (S' \otimes T')\rangle \circ \left\langle \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')} \right\rangle \\
+%&= \langle l, r \rangle \otimes ((S, S') \otimes (T, T')) \circ \iota(\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}) \\
+%&= f \otimes ((S, S') \otimes (T, T')) \circ \alpha_{(Q, Q'), (S, S'), (T, T')} 
+%\end{align*}
+%\todo{There is some cheating going on here, composition actually adds an extra $\alpha$, but that wouldn't get in the way.}
+%\end{proof}
+
 \begin{theorem}
-$\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit is $(I, I)$, and the action on morphisms induced by
-\begin{align*}
-&\C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(T, N \otimes B) \times \C(N \otimes B', T')\\
-\to \quad&\C(S \otimes T, M \otimes A \otimes N \otimes B) \times \C(M \otimes A' \otimes N \otimes B', S' \otimes T') && \text{(action of $\otimes$ on morphisms in $\C$)}\\
-\to \quad&\C(S \otimes T, M \otimes N \otimes A \otimes B) \times \C(M \otimes N \otimes A' \otimes B', S' \otimes T') && \text{($\otimes$ in $\C$ is symmetric)}\\
-\to \quad&\int^{M \in \C} \C(S \otimes T, M \otimes A \otimes B) \times \C(M \otimes A' \otimes B', S' \otimes T') && \text{(inclusion into coend)}
-\end{align*}
+$\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, T' \otimes S')$, the unit is $(I, I)$, and the action on morphisms is given by:
+\begin{center}
+\input{diagrams/tensor-on-morphisms.tikz}
+\end{center}
 \end{theorem}
@@
 \begin{proposition}
-Any isomorphism $p : (S, S') \hto (A, A')$ in $\Optic_\C$ is of the form $\iota(f, g)$ for two isomorphisms $S \to A$ and $A' \to S'$ in $\C$.
-\end{proposition}
-\begin{proof}
-
-\end{proof}
+$\iota : \C \times \C^\op \to \Optic_\C$ is a strong monoidal functor. \qed
+\end{proposition}
+
+%\begin{proposition}
+%Any isomorphism $p : (S, S') \hto (A, A')$ in $\Optic_\C$ is of the form $\iota(f, g)$ for two isomorphisms $S \to A$ and $A' \to S'$ in $\C$.
+%\end{proposition}
+%\begin{proof}
+%\todo{This might not actually be true..}
+%\end{proof}
 
@@
 \begin{align*}
-\Optic_\otimes((S, S'), (I, I)) 
+\Optic_\C((S, S'), (I, I)) 
 &= \int^{M \in \C} \C(S, M \otimes I) \times \C(M \otimes I, S') \\
@@
 
+\todo{Is there a relationship between $\Optic_\C/(I, I)$ and $[2, \C]$?}
+
 States are not as easy to describe in general, however:
@@
 \begin{align*}
-\Optic_\otimes((I,I), (A,A')) 
+\Optic_\C((I,I), (A,A')) 
 &= \int^{M \in \C} \C(I, M \otimes A) \times \C(M \otimes A', I) \\
@@
 \begin{proposition}
-A strong monoidal functor $F : \C \to \D$ induces a functor $\Optic(F) : \Optic_\C \to \Optic_\D$
-\end{proposition}
-\begin{proof}
-On objects this is simply $\Optic(F)(S, S') = (FS, FS')$. The action on morphisms $\Optic_\C((S, S'), (A, A'))$ is induced by
-\begin{align*}
-&\C(S, M \otimes A) \times \C(M \otimes A', S) \\
-\to &\D(FS, F(M \otimes A)) \times \D(F(M \otimes A'), FS) \\
-\to &\D(FS, FM \otimes FA) \times \D(FM \otimes FA', FS) \\
-\to &\int^{N \in \D} \D(FS, N \otimes FA) \times \D(N \otimes FA', FS).
-\end{align*}
-where we have used the strong monoidal isomorphism in both directions.
-\todo{use equations instead}
-\todo{argue for functoriality}
+A monoidal functor $F : \C \to \D$ induces a  functor $\Optic(F) : \Optic_\C \to \Optic_\D$
+\end{proposition}
+\begin{proof}
+On objects this is simply $\Optic(F)(S, S') = (FS, FS')$. On a morphism $\langle l, r \rangle : (S, S') \to (A, A')$, we define
+\begin{align*}
+F\langle l, r \rangle := \langle \phi^{-1}_{M,A} (Fl), (Fr) \phi_{M,A'}\rangle
+\end{align*}
+where $\phi_{M,A} : FM \otimes FA \to F(M \otimes A)$ is the structure map of the monoidal functor.
+\todo{functoriality}
+\todo{monoidality}
 \end{proof}
@@
 \begin{itemize}
-\item A wide symmetric monoidal subcategory $\C_d$ of dualisable morphisms, with an involutive strong symmetric monoidal functor $(-)^* : \C_d^\op \to \C_d$
+\item A wide symmetric monoidal subcategory $\C_d$ of \emph{dualisable morphisms}, with an involutive strong symmetric monoidal functor $(-)^* : \C_d \to \overline{\C_d^\op}$, where---not finding a standard symbol for such a thing---we mean $\overline{\C_d^\op}$ to be the category with both the direction of the arrows \emph{and} the order of the tensor flipped: $(A \otimes B)^* = B^* \otimes A^*$.
 \item A symmetric monoidal extranatural family of morphisms $\varepsilon_X : X \otimes X^* \to I$, called \emph{counits}, natural with respect to the morphisms in $\C_d$.
@@
 \end{definition}
-\todo{The involution bit seems to be almost the same as asking for a symmetric monoidal dagger-category, that is stricter than this though}
-
-Unpacking the definition, $\varepsilon$ being a monoidal extranatural transformation amounts to the following diagrams in $\C$ commuting:
+Note that because $\C_d$ is symmetric monoidal and has the same collection of objects as $\C$, the symmetric monoidal structure of $\C$ must consist of dualisable maps.
+
+Unpacking the definition, $\varepsilon$ being a symmetric monoidal extranatural transformation amounts to the following diagrams in $\C$ commuting:
 \[
@@
 \begin{tikzcd}
-X \otimes Y \otimes X^* \otimes Y^* \ar[r, "X \otimes s \otimes X^*"]  \ar[dr, "\varepsilon_{X \otimes Y}", swap] & X \otimes X^* \otimes Y \otimes Y^* \ar[d, "\varepsilon_X \otimes \varepsilon_Y"] \\
+X \otimes Y \otimes Y^* \otimes X^* \ar[r, "X \otimes \varepsilon_Y \otimes X^*"]  \ar[dr, "\varepsilon_{X \otimes Y}", swap] & X \otimes X^* \ar[d, "\varepsilon_X"] \\
 & I
@@
 \] 
-where $f : X \to Y$ is in $\C_d$. \todo{Is that last one actually something extra? It seems like the duality should also reverse the order of tensor, or something}
-
-\begin{proposition}
-$\Optic_\C$ forms a teleological category, with the following data:
+where $f : X \to Y$ is in $\C_d$.
+
+\begin{example}
+Any compact closed category is a teleological category, where every morphism is dualisable and the unit morphisms have been forgotten.
+\end{example}
+
+\todo{\begin{example}
+The funny graph example from the coherence paper?
+\end{example}}
+
+\begin{definition}
+A \emph{teleological functor} $F : \C \to \D$ is a strong symmetric monoidal functor that restricts to a functor $F_d : \C_d \to \D_d$ on the dualisable subcategories, and such that $F(\varepsilon_X) = \varepsilon_{FX}$ \todo{up to the structure isomorphisms of $F$...}
+\end{definition}
+
+Together we have $\Tele$, the (1-)category of teleological categories and functors.
+There are evident functors $U : \Tele \to \SymmMonCat$ and $(-)_d : \Tele \to \SymmMonCat$, that take a teleological category to its underlying symmetric monoidal category and subcategory of dualisable morphisms respectively.
+
+\begin{proposition}
+$\Optic_\C$ forms a teleological category, where:
 \begin{itemize}
@@
 \item The involution is given on objects by $(S, S')^* = (S', S)$, and on a morphism $\iota(f, g)$ by $\iota(g, f)$;
-\item The counit $\varepsilon_{(S, S')}$  is given by the image of the symmetry $s_{S \otimes S'}$ under the isomorphism of Proposition \ref{prop-costates}.
-\todo{It is a little annoying that a twist is necessary, but it has to go somewhere.
-The other option is in the definition of $\otimes$ but that seems worse.}
+\item The counit $\varepsilon_{(S, S')}$  is given by the image of the symmetry $\id_{S \otimes S'}$ under the isomorphism of Proposition \ref{prop-costates}. 
 \end{itemize}
@@
 \begin{proof}
-That morphisms of the form $\iota(f, g)$ constitute a category and that $\iota$ is a symmetric monoidal involution is clear. \todo{actually check monoidal part}
+That morphisms of the form $\iota(f, g)$ constitute a category and that $(-)^*$ is a symmetric monoidal involution is clear. \todo{actually check monoidal part}
 
@@
 Extranaturality is witnessed by the equality of the string diagrams:
+\todo{TODO: the dual ordering has since been flipped:}
 \begin{center}
@@
 \end{center}
-\end{proof}
-
-\todo{They stress about the empty set, does this matter here?}
-
-As conjectured by Jules Hedges, the structure of a teleological category is precisely what is added by forming the $\Optic$ category.
+
+Note that the diagrams required to commute all terminate with the unit $I$, so in view of Proposition \ref{prop-costates} we should not be surprised that they correspond to equality of maps in $\C$.
+\end{proof}
+
+\todo{They stress about the empty set, have I avoided that issue?}
+
+\begin{proposition}
+$\Optic : \SymmMonCat \to \Tele$ is a functor.
+\end{proposition}
+\begin{proof}
+\todo{todo}
+\end{proof}
+
 \begin{theorem}
-$\Optic_\C$ is the free teleological category on a symmetric monoidal category $\C$.
+Suppose $\C$ is a symmetric monoidal category and $\T$ is a teleological category.
+For all monoidal functors $F : \C \to \T_d$, there exists a teleological functor $K : \Lens_\C \to \T$, unique up to isomorphism, such that $K\iota \cong F$.
+%$\Optic$ is left adjoint to $(-)_d$, so $\Optic_\C$ is the free teleological category on a category of dualisable morphisms $\C$.
 \end{theorem}
@@
 
-\todo{Consequences: Inclusion $\C \to \Optic_\C$ is faithful/monoidal?}
-
 \subsection{Optics for a Monoidal Action}
 
-To capture the \texttt{Iso}s, \texttt{Traversal}s and \texttt{Setter}s of the Haskell \texttt{lens} library, we generalise to the case of a monoidal action of one category on another.
+To capture the \texttt{Iso}s, \texttt{Traversal}s and \texttt{Setter}s of the Haskell \texttt{lens} library (see \ref{lawful-examples}), we generalise to the case of a monoidal action of one category on another.
 
@@
 
-\subsection{Polymorphic Optics}
+For the remainder of the paper we work in this slightly more general setting.
 
@@
 \subsection{Examples}
+\label{lawful-examples}
 
@@
 \begin{proof}
-By Proposition \ref{prop-onthenose}, we may assume that $lr = \phi \times A$ on the nose.
+By Proposition \ref{prop-onthenose}, we may assume that $lr = \phi \times A$.
 
@@
 
+\subsection{Polymorphic Optics}
+Haskell's optics \todo{find an older reference from DB theory?} allow \emph{polymorphic updates}, where the type of the codomain of the lens can be changed, causing a corresponding change in the domain.
+As an example, the lens into the first entry of a tuple has type \mbox{\texttt{first :: Lens (a, b) (a', b) a a'}}, then:
+\begin{center}
+\texttt{set first (1, 5) "hello" == ("hello", 5)}
+\end{center}
+Note that the type has been changed from $\texttt{(Int, Int)}$ to $\texttt{(String, Int)}$
+
+Polymorphic optics can be captured as follows.
+For any monoidal category $\C$, and any category $\D$, there is an action of $\C$ on the functor category $[\D, \C]$ which an object $C \in \C$ pointwise with a functor $F \in [\D, \C]$:
+\begin{align*}
+\C \times [\D, \C] &\to [\D, \C] \\
+C, F &\mapsto  C \otimes F(-)
+\end{align*}
+
+\todo{say more}
+
+\todo{What about the pointwise tensor of an entire functor?}
+
 %\subsection{Equivalence of Optics}
@@
 
-\section{Optic Families}
-
 \section{Indexed Optics}

### 2018-04-09 paper.tex
Progress with diagrams

@@
 \usetikzlibrary{arrows}
+\tikzset{ed/.style={auto,inner sep=2pt,font=\scriptsize}} %edges
+\tikzset{>=stealth'}
+\tikzset{vert/.style={draw,circle, minimum size=6mm, inner sep=0pt, fill=white}}
+\tikzset{vertbig/.style={draw,circle, minimum size=8mm, inner sep=0pt, fill=white}}
 \input{tikzcurverel}
@@
 \theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
+\newtheorem{theorem}{Theorem}[subsection]
 %\newtheorem{axiom}[theorem]{Axiom}
@@
 \newcommand{\Prism}{\mathbf{Prism}}
+\newcommand{\Setter}{\mathbf{Setter}}
 \newcommand{\Hask}{\mathbf{Hask}}
@@
 \end{align*}
-In other words, let $\langle l, r \rangle : (R, R') \hto (S, S')$ and $\langle l', r' \rangle : (S, S') \hto (A, A')$ with $M$ the complement for $\langle l, r \rangle$.
-The composite is then: $\langle l', r' \rangle \circ \langle l, r \rangle = \langle (M l')l, r(Mr')\rangle$.
+In other words, let $\langle l', r' \rangle : (R, R') \hto (S, S')$ and $\langle l, r \rangle : (S, S') \hto (A, A')$ with $M$ the complement for $\langle l', r' \rangle$.
+The composite is then: $\langle l, r \rangle \circ \langle l', r' \rangle = \langle (M l)l', r'(Mr)\rangle$.
 
@@
 \begin{center}
-\todo{todo}
+\input{diagrams/generic-optic-noline.tikz}
+\qquad\raisebox{1.5cm}{$\circ$}\qquad
+\input{diagrams/generic-optic2-noline.tikz} \\
+\raisebox{1.5cm}{$:=$}\qquad
+\input{diagrams/optic-composition.tikz}
 \end{center}
 
-The identity optic $(S, S') \hto (S, S')$ is given by $\langle \lambda^{-1}_S, \lambda_{S'} \rangle$, where $\lambda_S : I \otimes S \to S$ is the left unitor for $S$.
+The identity optic $(S, S') \hto (S, S')$ is given by $\langle \lambda^{-1}_S, \lambda_{S'} \rangle$, where $\lambda_S : I \otimes S \to S$ is the left unitor for $S$: 
+\begin{center}
+\input{diagrams/identity-optic-full.tikz}
+\end{center}
+This dashed line above the diagram represents the unit object. As is standard, we will elide the unit object and unitors in future diagrams. The diagram for the identity becomes simply:
+\begin{center}
+\input{diagrams/identity-optic.tikz}
+\end{center}
 
@@
 We check associativity of composition equationally.
-As in the definition of composition, the Fubini theorem allows us to choose representatives for all three optics simultaneously.
+As in the definition of composition, the Fubini theorem for coends allows us to choose representatives for all three optics simultaneously.
 Suppose we have representatives of three optics $\langle l_1, r_1\rangle : (R, R) \hto (S, S')$ and $\langle l_2, r_2 \rangle : (S, S') \hto (A, A')$ and $\langle l_3, r_3 \rangle : (A, A') \hto (B, B')$, that have complements $M$, $N$ and $P$ respectively.
@@
 \end{align*}
-Graphically:
-\begin{center}
-\todo{todo}
-\end{center}
 
@@
 \end{align*}
-Where in both cases we have used the naturality of $\lambda$ and coend relations to move $\lambda^{-1}_M$ to the right-hand side of the coend. Graphically:
-\begin{center}
-\todo{todo}
-\end{center}
-
-%<---
+Where in both cases we have used the naturality of $\lambda$ and coend relations to move $\lambda^{-1}_M$ to the right-hand side of the coend. 
 \end{proof}
@@
 \begin{proof}
+Graphically, this is:
+\begin{center}
+\input{diagrams/iota.tikz}
+\end{center}
+
 This preserves identities, as the identity on an object $(S, S')$ in $\Optic_\M$ is defined to be exactly $\langle \lambda^{-1}_S, \lambda_{S'} \rangle$.
@@
 \begin{center}
-\todo{todo}
+\input{diagrams/iota-functorial-left.tikz}
+\qquad \raisebox{0.3cm}{$=$} \qquad 
+\input{diagrams/iota-functorial-right.tikz}
 \end{center}
+
 \end{proof}
@@
 \begin{theorem}
-$\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, T' \otimes S')$, the unit is $(I, I)$, and the action on morphisms is given by:
+$\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit is $(I, I)$, and the action on morphisms is given by:
 \begin{center}
@@
 \begin{proof}
-Equationally, suppose we have representatives $(l, r) : (S \to M \otimes A, M \otimes A' \to S')$ and $(l', r') : (T \to N \otimes B, N \otimes B' \to T')$. Then:
+Equationally, suppose we have optics $S \hto A$ and $T \hto B$ with representatives:
+\begin{align*}
+(l, r) &: (S \to M \otimes A, M \otimes A' \to S') \\
+(l', r') &: (T \to N \otimes B, N \otimes B' \to T')
+\end{align*}
+Then:
 \begin{align*}
@@
 \lambda_{(S, S')} &:= \iota(\lambda_{(S, S')}, \lambda_{(S, S')}^{-1}) \\
-\rho_{(S, S')} &:= (\rho_{(S, S')}, \rho_{(S, S')}^{-1}) \\
+\rho_{(S, S')} &:= \iota(\rho_{(S, S')}, \rho_{(S, S')}^{-1}) \\
 s_{(S, S'), (T, T')} &:= \iota(s_{S, T}, s_{T', S'})
@@
 
-In the Haskell \texttt{lens} library, the action of the monoidal product on optics is denoted ``\texttt{alongside}'' for the product and ``\texttt{without}'' for the coproduct.
-
-\begin{proposition}
-$\iota : \C \times \C^\op \to \Optic_\C$ is a strong monoidal functor. \qed
+\begin{remark}
+In the Haskell \texttt{lens} library, the monoidal product on optics is denoted ``\texttt{alongside}'' for the product and ``\texttt{without}'' for the coproduct.
+\end{remark}
+
+\begin{proposition}
+If $\C$ is a strict symmetric monoidal category then $\Optic_\C$ is also strict.
+\end{proposition}
+\begin{proof}
+The structure maps of $\Optic_\C$ are given by $\iota$ applied to the structure maps of $\C$.
+If the latter are identities, then so are the former---the identity morphisms in $\Optic_\C$ are by definition $\iota(\id_S, \id_S')$.
+\end{proof}
+
+\begin{proposition}
+$\iota : \C \times \C^\op \to \Optic_\C$ is a strong monoidal functor. 
+\end{proposition}
+\begin{proposition}
+\todo{todo}
 \end{proposition}
@@
 
+In particular, for any $M \in \C$, the image of the identity yields an optic $c_M : (M, M) \hto (I, I)$, that we will call the connector.
+
 States are not as easy to describe in general, however:
@@
 \subsection{Teleological Categories}
-
-As noted in \cite{CoherenceForLenses}, \todo{the category of optics admits its own string diagram language}
+\label{teleological-categories}
+
+Categories of optics admit their own diagrammatic language, by virtue of them being \emph{teleological categories}.
+In fact, we show in Theorem \ref{optic-is-free-teleological-cat} that $\Optic_\C$ is the free teleological category on a collection of dualisable morphisms $\C$.
+
+In this section we assume that $\C$ is a \emph{strict} symmetric monoidal category.
 
@@
 \begin{itemize}
-\item A wide symmetric monoidal subcategory $\C_d$ of \emph{dualisable morphisms}, with an involutive strong symmetric monoidal functor $(-)^* : \C_d \to \overline{\C_d^\op}$, where---not finding a standard symbol for such a thing---we mean $\overline{\C_d^\op}$ to be the category with both the direction of the arrows \emph{and} the order of the tensor flipped: $(A \otimes B)^* = B^* \otimes A^*$.
-\item A symmetric monoidal extranatural family of morphisms $\varepsilon_X : X \otimes X^* \to I$, called \emph{counits}, natural with respect to the morphisms in $\C_d$.
-\end{itemize}
-\end{definition}
-Note that because $\C_d$ is symmetric monoidal and has the same collection of objects as $\C$, the symmetric monoidal structure of $\C$ must consist of dualisable maps.
-
-Unpacking the definition, $\varepsilon$ being a symmetric monoidal extranatural transformation amounts to the following diagrams in $\C$ commuting:
+\item A wide symmetric monoidal subcategory $\C_d$ of \emph{dualisable morphisms}, with an involutive strong symmetric monoidal functor $(-)^* : \C_d \to \C_d^\op$; and,
+\item A family of morphisms $\varepsilon_X : X \otimes X^* \to I$, called \emph{counits}, natural with respect to the morphisms in $\C_d$, such that
 \[
@@
 \begin{tikzcd}
-X^* \otimes X \ar[r, "\sigma"]  \ar[dr, "\varepsilon_{X^*}", swap] & X \otimes X^* \ar[d, "\varepsilon_X"] \\
+X^* \otimes X \ar[r, "s_{X^*, X}"]  \ar[dr, "\varepsilon_{X^*}", swap] & X \otimes X^* \ar[d, "\varepsilon_X"] \\
 & I
@@
 \begin{tikzcd}
-X \otimes Y \otimes Y^* \otimes X^* \ar[r, "X \otimes \varepsilon_Y \otimes X^*"]  \ar[dr, "\varepsilon_{X \otimes Y}", swap] & X \otimes X^* \ar[d, "\varepsilon_X"] \\
+X \otimes Y \otimes X^* \otimes Y^* \ar[r, "X \otimes s_{Y,X^*} \otimes X^*"]  \ar[dr, "\varepsilon_{X \otimes Y}", swap] & X \otimes X^* \otimes Y \otimes Y^* \ar[d, "\varepsilon_X \otimes \varepsilon_Y"] \\
 & I
@@
 \]
-where $f : X \to Y$ is in $\C_d$.
+commute for all $f : X \to Y$ is in $\C_d$.
+\end{itemize}
+\end{definition}
+Note that because $\C_d$ is symmetric monoidal and has the same collection of objects as $\C$, the symmetric monoidal structure of $\C$ must all be contained in $\C_d$.
 
 \begin{example}
-Any compact closed category is a teleological category, where every morphism is dualisable and the unit morphisms have been forgotten.
+Any symmetric monoidal category with terminal monoidal unit is trivially teleological, setting the dualisable morphisms to be only the structure maps of the monoidal category.
 \end{example}
@@
 \end{example}}
+
+\begin{remark}
+Compact closed categories very nearly form an example of teleological categories.
+In a compact closed category, there are canonical isomorphisms $(X \otimes Y)^* \cong Y^* \otimes X^*$.
+In a teleological category, however, duality does not reverse the order of the tensor.
+\todo{If $\C$ is strict though, does this matter?}
+\end{remark}
 
@@
 \item The involution is given on objects by $(S, S')^* = (S', S)$, and on a morphism $\iota(f, g)$ by $\iota(g, f)$;
-\item The counit $\varepsilon_{(S, S')}$  is given by the image of the symmetry $\id_{S \otimes S'}$ under the isomorphism of Proposition \ref{prop-costates}. 
+\item The counit $\varepsilon_{(S, S')}$  is given by the connector $c_{S \otimes S'}$.
 \end{itemize}
@@
 Extranaturality is witnessed by the equality of the string diagrams:
-\todo{TODO: the dual ordering has since been flipped:}
 \begin{center}
@@
 \begin{proof}
+We have to show that for a symmetric monoidal functor $F : \C \to \D$, the induced functor $\Optic_\C \to \Optic_\D$ is teleological.
+
 \todo{todo}
@@
 
+\begin{proposition}
+\label{prop-optic-decompose}
+Suppose $p : (S, S') \to (A, A')$ has representative $\langle l, r \rangle$. Then 
+\begin{align*}
+p = (\varepsilon_{(M, I)} \otimes (A, A'))\iota(l, r).
+\end{align*}
+\end{proposition}
+\begin{proof}
+\todo{by string diagram}
+\end{proof}
+
 \begin{theorem}
-Suppose $\C$ is a symmetric monoidal category and $\T$ is a teleological category.
-For all monoidal functors $F : \C \to \T_d$, there exists a teleological functor $K : \Lens_\C \to \T$, unique up to isomorphism, such that $K\iota \cong F$.
+\label{optic-is-free-teleological-cat}
+Suppose $\C$ is a \todo{strict} symmetric monoidal category and $\T$ is a teleological category.
+For all monoidal functors $F : \C \to \T_d$, there exists a teleological functor $K : \Lens_\C \to \T$, unique up to isomorphism, such that $Kj \cong F$.
 %$\Optic$ is left adjoint to $(-)_d$, so $\Optic_\C$ is the free teleological category on a category of dualisable morphisms $\C$.
@@
 \begin{proof}
- \todo{todo}
-\end{proof}
+\todo{This is the point at which I have run in to trouble: TODO}
+
+%On objects, define $K(S, S') = FS \otimes (FS')*$.
+Suppose $p : (S, S') \hto (A, A')$ is an optic with representative $\langle l, r \rangle$.
+By Proposition \ref{prop-optic-decompose} and the previous Lemma, $p$ may be decomposed as:
+%\begin{align*}
+%\langle l, r \rangle = (\varepsilon_{(M, I)}\iota(\rho_M^{-1}, \lambda_M) \otimes \id_{(A, A')})\iota(l, s_{M,A'}r)
+%\end{align*}
+%But now, in order for $K$ to be a teleological functor with $Kj \cong F$, each piece of this expression must be preserved by $K$, so we define:
+%\begin{align*}
+%K\langle l, r \rangle = (\varepsilon_{FM} \otimes \id_{FA \otimes FA'})(Fl \otimes s_{FM,FA'} (Fr)^* )
+%\end{align*}
+%
+%This is much easier to understand in the diagrammatic language for teleological categories: \todo{todo}
+%
+%We now have to check that this is well defined. \todo{todo}
+%
+%\todo{incomplete}
+\end{proof}
+
+\begin{remark}
+It is unclear whether an argument like this can work in the case $\C$ is \emph{not} strict. There are a number of issues:
+
+\begin{itemize}
+\item Given $f : S \to A$ and $g : A' \to S'$, the optic $j(f) \otimes j(g)^* : (S \otimes I, I \otimes S') \hto (A \otimes I, I \otimes A')$ is not equal to $\iota(f, g)$.
+It is also not in a form that can be composed with the unitors of $\Optic_\C$, as the $I$s are not all on the same side.
+\item \todo{wasn't there more?}
+\end{itemize}
+
+One possible workaround: We could extend the category of optics so it contains the image of $\C$ and its duals directly, without needing ghost morphisms $I \to I$ to face the other direction.
+So there are also objects $(S)$, and a morphism $(S) \hto (A)$ is either an $f : S \to A$ or the formal dual of a $g : A \to S$, and a morphism $(S) \hto (A, A')$ is an optic $(S, I) \hto (A, A')$.
+
+There are several cases involved when composing morphisms and tensoring objects, depending on which kinds of objects are involved.
+This is significantly fiddlier, but it should allow a version of Proposition \ref{prop-optic-decompose} to apply to any $\C$.
+\end{remark}
 
@@
 \begin{proposition}
-There is an subcategory $\Lawful_\C$ of $\Optic_\C$ given by objects of the form $(X, X)$ and lawful optics between them.
+There is an subcategory $\Lawful_\M$ of $\Optic_\M$ given by objects of the form $(X, X)$ and lawful optics between them.
 \end{proposition}
@@
 \begin{proof}
-\todo{This is painful but seems important. There may be a more general principle at work here but I couldn't see it.}
-
-\todo{Put in an appendix?}
+\todo{This is painful but seems important. There may be a more general principle at work here but I couldn't see it. Put in an appendix?}
 
@@
 
-\subsection{Examples}
+\section{Examples}
 \label{lawful-examples}
 
-\subsubsection{Lenses}
+\subsection{Lenses}
 
@@
 
-As remarked in the introduction \todo{(todo: remark in the introduction)}, the optics for this action are exactly pairs of $\fget$ and $\fput$ functions.
-\begin{align*}
-\Optic_\times(S, A) &= \int^{M \in \M} \C(S, M \times A) \times \C(M \times A, S) \\
-&\cong \int^{M \in \M} \C(S, M) \times \C(S, A) \times \C(M \times A, S) && \text{(universal property of product)} \\
-&\cong \C(S, A) \times \C(S \times A, S) && \text{(co-Yoneda)}
-\end{align*}
-
-Explicitly this isomorphism states that, given a prelens $\langle l, r \rangle : S \hto A$, the corresponding $\fget$ and $\fput$ functions are given by $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
+The optics for this action are exactly pairs of $\fget$ and $\fput$ functions.
+\begin{align*}
+\Optic_\times((S, S'), (A, A')) &= \int^{M \in \C} \C(S, M \times A) \times \C(M \times A', S') \\
+&\cong \int^{M \in \C} \C(S, M) \times \C(S, A) \times \C(M \times A', S') && \text{(universal property of product)} \\
+&\cong \C(S, A) \times \C(S \times A', S') && \text{(co-Yoneda)}
+\end{align*}
+
+Explicitly this isomorphism states that, given an (unlawful) lens $\langle l, r \rangle : (S, S') \hto (A, A')$, the corresponding $\fget$ and $\fput$ functions are given by $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
 In the other direction, given $\fget$ and $\fput$, the corresponding element in the coend has representative $\langle l, r \rangle$, where $l = [\id_s, \fget]$ and $r = \fput$.
@@
 Any pair of maps $f : 0 \to A$, $g : A' \to S'$ yield equivalent optics $\iota(f, g)$, as the corresponding $\fget$ and $\fput$ functions must be the unique maps from $0$.
-
-\todo{Show that for the category of nonempty sets things .}
 \end{remark}
+
+We now discuss lawful lenses.
 
@@
 
-This has been written out many times before in the case when $lr$ is the identity \cite{IsomorphismLensesPost}, we note here that the weaker condition is sufficient.
+This is well known in the case $lr$ is the identity \cite{IsomorphismLensesPost}, we note here that the weaker condition is sufficient.
 
@@
 
-\subsubsection{Prisms}
+\subsection{Non-Cartesian Lenses}
+If $\C$ is closed monoidal, we can use a similar trick to eliminate the coend in the definition of an optic:
+
+\begin{align*}
+\Optic_\otimes((S, S'), (A, A')) &= \int^{M \in \C} \C(S, M \otimes A) \times \C(M \otimes A', S') \\
+&\cong \int^{M \in \C} \C(\homC(S,A), M) \times \C(M \otimes A', S') \\
+&\cong \C(\homC(S, A) \otimes A', S')
+\end{align*}
+where $\homC(S, A)$ denotes the internal hom.
+
+\todo{laws?}
+\todo{The use of lenses in a type system with linear types seems worth exploring!}
+
+\subsection{Prisms}
 Prisms are dual to lenses:
@@
 \begin{align*}
-\Optic_\sqcup(S, A) &= \int^{M \in \M} \C(S, M \sqcup A) \times \C(M \sqcup A, S) \\
-&\cong \int^{M \in \M} \C(S, M \sqcup A) \times \C(M, S) \times \C(A, S) && \text{(universal property of coproduct)} \\
-&\cong \C(S, S \sqcup A) \times \C(A, S) && \text{(co-Yoneda)}
-\end{align*}
-So, if we are given a prism $\langle l, r \rangle : (S, S) \hto (A, A)$ then associated $\freview$ and $\fmatching$ morphisms are given by $\freview = r \inr$ and $\fmatching = (r\inl \sqcup A)l$
-
-The laws for prisms are the obvious duals to the lens laws. 
+\Optic_\sqcup((S, S'), (A, A')) &= \int^{M \in \C} \C(S, M \sqcup A) \times \C(M \sqcup A', S') \\
+&\cong \int^{M \in \C} \C(S, M \sqcup A) \times \C(M, S') \times \C(A, S') && \text{(universal property of coproduct)} \\
+&\cong \C(S, S' \sqcup A) \times \C(A', S') && \text{(co-Yoneda)}
+\end{align*}
+So, if we are given a prism $\langle l, r \rangle : (S, S') \hto (A, A')$ then associated $\freview$ and $\fmatching$ morphisms are given by $\freview = r \inr$ and $\fmatching = (r\inl \sqcup A)l$
+
+Restricting to prisms of the form $(S, S) \hto (A, A)$, the laws for prisms are the obvious duals to the lens laws: 
 \begin{align*}
@@
 The key is that in $\Set$, for any map $f : X \to Y$, the set $Y$ is equal to the union of $\im f$ and its complement.
-The first law implies that $\freview$ is injective, so $S \cong C \sqcup A$ for some complement $C$ \todo{name this map and use it properly}.
+The first law implies that $\freview$ is injective, so $S \cong C \sqcup A$ for some complement $C$.
 Identifying $A$ with its image in $S$, the second law implies that if $a\in A \subset S$ then $\fmatching(a) = \inr(a)$ and if $c\in C \subset S$ then $\fmatching(c) = \inl(c)$.
-The third law then follows easily by checking both cases.
+The third law then follows by checking both cases.
 \end{proof}
@@
 
-\subsubsection{Affine Traversals}
-
-\subsubsection{Isos}
-
-\subsubsection{Setters}
+\subsection{Affine Traversals}
+
+\subsection{Isos}
+
+\subsection{Setters}
 
@@
 \begin{definition}
-\todo{Again I am not fussing with associators/unitors, this is probably bad.
-Also this definition should work fine of we instead use an action of some $\M$ on $\C$.} Suppose $(\C, \otimes, I)$ is a monoidal category.
+\todo{This definition should work fine if we instead use an action of some $\M$ on $\C$, but I don't think that ever comes up?} Suppose $(\C, \otimes, I)$ is a monoidal category.
 A \emph{(left) strength} for an endofunctor $F : \C \to \C$ is a natural transformation
@@
 \begin{tikzcd}
-A \otimes B \otimes F C \ar[r, "A \otimes \theta_{B,C}"] \ar[d, "\theta_{A \otimes B, C}" left]  & A \otimes F(B\otimes C) \ar[d, "\theta_{A, B\otimes C}" right] \\
-F(A \otimes B \otimes C) \ar[r, equals]& F(A \otimes B \otimes C)
+1 \otimes F A \ar[r, "\theta_{1,A}"] \ar[d, "\cong" left]  & F(1 \otimes A) \ar[d, "\cong" right] \\
+F A \ar[r, equals] & F A
 \end{tikzcd}
@@
 \begin{tikzcd}
-1 \otimes F A \ar[r, "s_{1,A}"] \ar[d, "\cong" left]  & F(1 \otimes A) \ar[d, "\cong" right] \\
-F A \ar[r, equals] & F A
+(A \otimes B) \otimes F C \ar[rr, "\theta_{A \otimes B, C}"] \ar[d, "\alpha_{A,B,FC}" left]  && F((A \otimes B) \otimes C) \ar[d, "F\alpha_{A,B,FC}" right] \\
+A \otimes (B \otimes F C) \ar[r, "A \otimes \theta_{B,C}" below] & A \otimes F(B \otimes C) \ar[r, "\theta_{A, B\otimes C}" below] & F(A \otimes (B \otimes C))
 \end{tikzcd}
@@
 \begin{tikzcd}
-A \otimes F B \ar[r, "\theta_{A,B}"] \ar[d, "A \otimes \tau_B" left]  & G(A \otimes B) \ar[d, "\tau_{A \otimes B}" right] \\
+A \otimes F B \ar[r, "\theta_{A,B}"] \ar[d, "A \otimes \tau_B" left]  & F(A \otimes B) \ar[d, "\tau_{A \otimes B}" right] \\
 A \otimes G B \ar[r, "\theta'_{A, B}"]& G(A \otimes B)
@@
 
-Every endofunctor on $(\Set, \times, 1)$ has a unique strength, so this concept is invisible for Haskell functors.
+In what follows, we will exploit the convenient $\lambda$-calculus syntax for morphisms in a cartesian closed category. \todo{ref}
+
+\begin{example}
+An example, which we will use immediately, is the functor $FX = C \times \homC(D, X)$ in any cartesian closed category $\C$, and with any pair of objects $C$ and $D$. The strength is given by:
+\begin{align*}
+A \times FB = A \times C \times \homC(D, B) &\to C \times \homC(D, A \times B) = F(A \times B)\\
+(a, c, f) &\mapsto (c, \lambda d. (a, fd))
+\end{align*}
+\end{example}
+
+\begin{example}
+\emph{Any} functor $\Set \to \Set$ has a unique strength with respect to the cartesian product, so this concept is invisible for Haskell \texttt{Functor}s. \todo{ref}
+\end{example}
 
@@
 \begin{proof}
-Given a $f \in \C(A, FB)$, let $\eta$ be the natural transformation with components
-\begin{align*}
-A \times \homC(B, C) \xrightarrow{f \times \id} FB \times \homC(B, C) \xrightarrow{\theta_{\homC(B, C), B}}  F(B \times \homC(B, C)) \xrightarrow{F\epsilon} FC
-\end{align*}
-where $\theta$ is the strength for $F$ and $\epsilon$ is the evaluation map.
-
-Conversely, given an $\eta : A \times \homC(B, -) \to F$, the component at $B$ is a function $g : A \times \homC(B, B) \to FB$; we recover $f : A \to FB$ as $f = g (\id_A, \const_{\id_B})$.
-
-\todo{These are inverses.}
-\end{proof}
-
-This is a generalisation of \cite[Proposition 2.2]{SecondOrderFunctionals}
-
-\todo{unfinished}
-
-\subsubsection{Traversals}
+Given a $f \in \C(A, FB)$, let $\Phi(f)$ be the natural transformation with components
+\begin{align*}
+A \times \homC(B, C) &\to FC \\
+(a, g) &\mapsto F(\lambda x. \lambda h. h x)\theta_{\homC(B, C), B}(fa, g)
+\end{align*}
+%\begin{align*}
+%A \times \homC(B, C) \xrightarrow{f \times \id} FB \times \homC(B, C) \xrightarrow{\theta_{\homC(B, C), B}}  F(B \times \homC(B, C)) \xrightarrow{F\epsilon} FC
+%\end{align*}
+where $\theta$ is the strength for $F$.
+\todo{Check this is a strong natural transformation}
+
+Conversely, given an $\eta : A \times \homC(B, -) \Rightarrow F$, the component at $B$ is a function $\eta_B : A \times \homC(B, B) \to FB$; we define
+\begin{align*}
+A &\to FB \\
+a &\mapsto \eta_B(a, \lambda b. b)
+\end{align*}
+%$\Psi(\eta) : A \to FB$ to be $A \xrightarrow{A \times \const_{\id_B}} A \times \homC(B, B) \xrightarrow{\eta_B} FB$.
+
+\todo{out of date:}
+Checking these are inverse:
+\begin{align*}
+\Phi(\Psi(\eta))_C &= \Phi(\eta_B(A\times\const_{\id_B}))_C \\
+&= (F\epsilon) \theta_{\homC(B, C), B} \left( \eta_B(A\times\const_{\id_B}) \times \id_{\homC(B, C)} \right)
+\end{align*}
+\todo{todo, using the strength for $A \times \homC(B, -)$?}
+\end{proof}
+
+This is a generalisation of \cite[Proposition 2.2]{SecondOrderFunctionals}, isolating the properties of $\Set$ that were used.
+
+Now, we can construct setters.
+
+\begin{definition}
+Supposed $\C$ is cartesian closed, and let $\Strong(\C)$ act on $\C$ by evaluation. The \emph{category of setters} $\Setter_\C$ is the category of lawful optics for this action.
+\end{definition}
+
+Due to the above lemma, we can eliminate the coend from this definition:
+\begin{align*}
+\Setter_\C(S, A) &= \int^{F \in \Strong(\C)} \C(S, FA) \times \C(FA, S) \\
+&\cong \int^{F \in \Strong(\C)} \Strong_\C(\times)(S \times \homC(A, -), F)  \times \C(FA, S) \\
+&\cong \C(S \times \homC(A, A), S) \\
+&\cong \C(\homC(A, A), \homC(S,S))
+\end{align*}
+
+\todo{laws}
+
+\todo{This previous section might also work just with monoidal closed?}
+
+\subsection{Traversals}
 \todo{Do it}
@@
 \subsection{Polymorphic Optics}
-Haskell's optics \todo{find an older reference from DB theory?} allow \emph{polymorphic updates}, where the type of the codomain of the lens can be changed, causing a corresponding change in the domain.
-As an example, the lens into the first entry of a tuple has type \mbox{\texttt{first :: Lens (a, b) (a', b) a a'}}, then:
+Haskell's optics \todo{find an older reference from DB theory?} allow \emph{polymorphic updates}, where the type of the codomain of the lens can be changed by an update, causing a corresponding change in the type of the domain.
+As an example, the lens into the first entry of a tuple has type
+\begin{center}
+\texttt{first :: Lens (a, b) (a', b) a a'}, 
+\end{center}
+then:
 \begin{center}
@@
 
-Polymorphic optics can be captured as follows.
-For any monoidal category $\C$, and any category $\D$, there is an action of $\C$ on the functor category $[\D, \C]$ which an object $C \in \C$ pointwise with a functor $F \in [\D, \C]$:
-\begin{align*}
-\C \times [\D, \C] &\to [\D, \C] \\
-C, F &\mapsto  C \otimes F(-)
-\end{align*}
-
-\todo{say more}
+Polymorphic optics can be captured by the coend formalism as follows. Any action of a monoidal category $\M \times \C \to \C$ can be extended to act pointwise on a functor category:
+\begin{align*}
+\M \times [\D, \C] &\to [\D, \C] \\
+(M, F) &\mapsto  M \cdot (F-)
+\end{align*}
+
+So in the above example, we would take $F = \mathtt{Int} \times -$ and $G$ to be the identity functor.
+
+Given such a polymorphic optic in $[\D, \C]$, we can always `monomorphise' to obtain an ordinary optic in $\C$.
+\begin{proposition}
+There is a functor 
+\begin{align*}
+\mathsf{mono} : \D \times \Optic_{[\D, \C]} \to \Optic_\C
+\end{align*}
+that sends an object $D \in \D$ and optic $\langle l, r \rangle : F \hto G$ in $\Optic_{[\D, \C]}$ to the optic $\langle l_D, r_D \rangle : FD \hto GD$ in $\Optic_\C$.
+\end{proposition}
+\begin{proof}
+\todo{todo}
+\end{proof}
+
+Lawful optics in $\Optic_{[\D, \C]}$ are sent to lawful optics in $\Optic_\C$,  so we may restrict the domain to obtain a functor:
+\begin{align*}
+\mathsf{mono} : \D \times \Lawful_{[\D, \C]} \to \Lawful_\C
+\end{align*}
+
+\todo{more to say?}
 
@@
 \section{Profunctor Optics}
+
+\subsection{Tambara Modules}
 Let $I = \C(-,{=}) : \C \hto \C$ be the identity profunctor and $\odot$ be profunctor composition, written in diagrammatic order.
@@
 
-\section{Lenses in Linear Types?}
-
-\section{A Double-Categorical Perspective?}
-
-Dual pairs for the functors $(- \times A) : \M \to \C$ give a monoid in $PProf$.
-
 \section{Conclusion}

### 2018-04-09 tikzcurverel.tex
Progress with diagrams

%%% Add relative endpoints to curved 'to'

%% Due to limitations of TikZ, one cannot write '(a) to +(1,0)'.  The
%% target coordinate of a 'to' path must begin with a parenthesis.  In
%% this file we redefine the 'curve to' path to add options which
%% treat the target coordinate in a relative way.

%% With the option 'rel', the target coordinate is treated as if it
%% had a '+' in front of it, and similarly for 'rrel' and ++.  Note
%% that this can be misleading when reading the TikZ code if one is
%% unaware of its meaning, since we don't actually WRITE the + or ++
%% so the coordinate looks as if it were absolute.

%% The option 'abs' switches back to treating the target as absolute.

%% Ironically, these options DO NOT (yet) work together with the
%% 'relative' option (which calculates ANGLES relative to the line
%% from the source to the target coordinate).

\makeatletter

%%% Options to select relative endpoints
\newif\iftikz@to@relp
\tikz@to@relpfalse
\newif\iftikz@to@relpp
\tikz@to@relppfalse
\tikzoption{abs}[]{\tikz@to@relpfalse\tikz@to@relppfalse}
\tikzoption{rel}[]{\tikz@to@relptrue\tikz@to@relppfalse}
\tikzoption{rrel}[]{\tikz@to@relpfalse\tikz@to@relpptrue}

\tikzstyle{every curve to}=          []
\tikzstyle{curve to}=                [to path=\tikz@to@curve@path]

\tikzoption{bend angle}{\def\tikz@to@bend{#1}}

\tikzoption{bend left}[]{%
  \def\pgf@temp{#1}%
  \ifx\pgf@temp\pgfutil@empty%
  \else%
    \def\tikz@to@bend{#1}%
  \fi%
  \let\tikz@to@out=\tikz@to@bend%
  \c@pgf@counta=180\relax%
  \advance\c@pgf@counta by-\tikz@to@out\relax%
  \edef\tikz@to@in{\the\c@pgf@counta}%
  \tikz@to@switch@on%
  \tikz@to@relativetrue%
}

\tikzoption{bend right}[]{%
  \def\pgf@temp{#1}%
  \ifx\pgf@temp\pgfutil@empty%
  \else%
    \def\tikz@to@bend{#1}%
  \fi%
  % Now, negate
  \c@pgf@counta=\tikz@to@bend\relax%
  \c@pgf@counta=-\c@pgf@counta\relax%
  \edef\tikz@to@out{\the\c@pgf@counta}%
  \c@pgf@counta=180\relax%
  \advance\c@pgf@counta by-\tikz@to@out\relax%
  \edef\tikz@to@in{\the\c@pgf@counta}%
  \tikz@to@switch@on%
  \tikz@to@relativetrue%
}

\tikzoption{relative}[true]{\csname tikz@to@relative#1\endcsname}
\newif\iftikz@to@relative
\tikz@to@relativefalse

\tikzoption{in}{\def\tikz@to@in{#1}\tikz@to@switch@on}
\tikzoption{out}{\def\tikz@to@out{#1}\tikz@to@switch@on}

\tikzoption{in looseness}{\tikz@to@set@in@looseness{#1}}
\tikzoption{out looseness}{\tikz@to@set@out@looseness{#1}}
\tikzoption{looseness}{\tikz@to@set@in@looseness{#1}\tikz@to@set@out@looseness{#1}}

\tikzoption{in control}{\tikz@to@set@in@control{#1}}
\tikzoption{out control}{\tikz@to@set@out@control{#1}}
\tikzoption{controls}{\tikz@to@parse@controls#1\pgf@stop}

\tikzoption{in min distance}{\tikz@to@set@distances{#1}{}{}{}}
\tikzoption{in max distance}{\tikz@to@set@distances{}{#1}{}{}}
\tikzoption{in distance}{\tikz@to@set@distances{#1}{#1}{}{}}
\tikzoption{out min distance}{\tikz@to@set@distances{}{}{#1}{}}
\tikzoption{out max distance}{\tikz@to@set@distances{}{}{}{#1}}
\tikzoption{out distance}{\tikz@to@set@distances{}{}{#1}{#1}}
\tikzoption{min distance}{\tikz@to@set@distances{#1}{}{#1}{}}
\tikzoption{max distance}{\tikz@to@set@distances{}{#1}{}{#1}}
\tikzoption{distance}{\tikz@to@set@distances{#1}{#1}{#1}{#1}}

\def\tikz@to@set@distances#1#2#3#4{%
  \tikz@to@setifnotempy{#1}{\tikz@to@in@min}{\let\tikz@to@end@compute=\tikz@to@end@compute@looseness}%
  \tikz@to@setifnotempy{#2}{\tikz@to@in@max}{\let\tikz@to@end@compute=\tikz@to@end@compute@looseness}%
  \tikz@to@setifnotempy{#3}{\tikz@to@out@min}{\let\tikz@to@start@compute=\tikz@to@start@compute@looseness}%
  \tikz@to@setifnotempy{#4}{\tikz@to@out@max}{\let\tikz@to@start@compute=\tikz@to@start@compute@looseness}%
  \tikz@to@switch@on%
}

\def\tikz@to@setifnotempy#1#2#3{%
  \def\pgf@temp{#1}%
  \ifx\pgf@temp\pgfutil@empty\else\def#2{#1}#3\fi%
}

\def\tikz@to@set@in@looseness#1{%
  \def\tikz@to@in@looseness{#1}%
  \let\tikz@to@end@compute=\tikz@to@end@compute@looseness%
  \tikz@to@switch@on%
}
\def\tikz@to@set@out@looseness#1{%
  \def\tikz@to@out@looseness{#1}%
  \let\tikz@to@start@compute=\tikz@to@start@compute@looseness%
  \tikz@to@switch@on%
}

\def\tikz@to@parse@controls#1and#2\pgf@stop{\tikz@to@set@in@control{#2}\tikz@to@set@out@control{#1}}

\def\tikz@to@set@in@control#1{%
  \def\tikz@to@in@control{#1}%
  \let\tikz@to@end@compute=\tikz@to@end@compute@control%
  \tikz@to@switch@on%
}
\def\tikz@to@set@out@control#1{%
  \def\tikz@to@out@control{#1}%
  \let\tikz@to@start@compute=\tikz@to@start@compute@control%
  \tikz@to@switch@on%
}

\def\tikz@to@bend{30}

\def\tikz@to@out{45}
\def\tikz@to@in{135}

\def\tikz@to@out@looseness{1}
\def\tikz@to@in@looseness{1}

\def\tikz@to@in@min{0pt}
\def\tikz@to@in@max{10000pt}
\def\tikz@to@out@min{0pt}
\def\tikz@to@out@max{10000pt}

\def\tikz@to@switch@on{\let\tikz@to@path=\tikz@to@curve@path}

\def\tikz@to@curve@path{%
  [every curve to]
  \pgfextra{\iftikz@to@relative\tikz@to@compute@relative\else\tikz@to@compute\fi}
  \tikz@computed@path
  \tikztonodes%
  \pgfextra{\tikz@to@relpfalse\tikz@to@relppfalse}%
}

\def\tikz@to@modify#1#2{%
  \pgfutil@ifundefined{pgf@sh@ns@#1}
  {}%
  {\edef#1{#1.#2}}
}%

\def\tikz@to@compute{%
  \let\tikz@tofrom=\tikztostart%
  \let\tikz@toto=\tikztotarget%
  \tikz@to@modify\tikz@tofrom\tikz@to@out%
  \tikz@to@modify\tikz@toto\tikz@to@in%
  \ifx\tikz@to@start@compute\tikz@to@start@compute@looseness%
    \tikz@to@compute@distance%
  \else%
    \ifx\tikz@from@start@compute\tikz@to@start@compute@looseness%  
      \tikz@to@compute@distance%
    \fi%
  \fi%
  \tikz@to@start@compute%
  \tikz@to@end@compute%
  \iftikz@to@relp
    \edef\tikz@computed@path{.. controls \tikz@computed@start and \tikz@computed@end .. +(\tikz@toto)}
  \else
    \iftikz@to@relpp  
      \edef\tikz@computed@path{.. controls \tikz@computed@start and \tikz@computed@end .. ++(\tikz@toto)}
    \else
      \edef\tikz@computed@path{.. controls \tikz@computed@start and \tikz@computed@end .. (\tikz@toto)}
    \fi
  \fi
}

\def\tikz@to@compute@distance{\tikz@scan@one@point\tikz@@to@compute@distance(\tikz@tofrom)}
\def\tikz@@to@compute@distance#1{%
  \def\tikz@first@point{#1}%
  \iftikz@to@relp%
    \tikz@scan@one@point\tikz@@@to@compute@distance([shift={(\tikz@toto)}]\tikz@tofrom)%
  \else%
    \iftikz@to@relpp%
      \tikz@scan@one@point\tikz@@@to@compute@distance([shift={(\tikz@toto)}]\tikz@tofrom)%
    \else%
      \tikz@scan@one@point\tikz@@@to@compute@distance(\tikz@toto)%
    \fi%
  \fi}
\def\tikz@@@to@compute@distance#1{%
  \def\tikz@second@point{#1}%
  \tikz@to@compute@distance@main%
}
\def\tikz@to@compute@distance@main{%
  \pgf@process{\pgfpointdiff{\tikz@first@point}{\tikz@second@point}}%
  \ifdim\pgf@x<0pt\pgf@xa=-\pgf@x\else\pgf@xa=\pgf@x\fi%
  \ifdim\pgf@y<0pt\pgf@ya=-\pgf@y\else\pgf@ya=\pgf@y\fi%
  % 
  % Calculate length of second to first vector:
  % 
  \pgf@process{\pgfpointnormalised{\pgfqpoint{\pgf@xa}{\pgf@ya}}}%
  \ifdim\pgf@x>\pgf@y%
    \c@pgf@counta=\pgf@x%
    \ifnum\c@pgf@counta=0\relax%
    \else%
      \divide\c@pgf@counta by 255\relax%
      \pgf@xa=16\pgf@xa\relax%
      \divide\pgf@xa by\c@pgf@counta%
      \pgf@xa=16\pgf@xa\relax%
    \fi%
  \else%
    \c@pgf@counta=\pgf@y%
    \ifnum\c@pgf@counta=0\relax%
    \else%
      \divide\c@pgf@counta by 255\relax%
      \pgf@ya=16\pgf@ya\relax%
      \divide\pgf@ya by\c@pgf@counta%
      \pgf@xa=16\pgf@ya\relax%
    \fi%
  \fi%
  \pgf@x=0.3915\pgf@xa%
  \pgf@xa=\tikz@to@out@looseness\pgf@x%
  \pgf@xb=\tikz@to@in@looseness\pgf@x%
  % Adjust as necessary
  \pgfmathsetlength{\pgf@ya}{\tikz@to@out@min}
  \ifdim\pgf@xa<\pgf@ya%
    \pgf@xa=\pgf@ya%
  \fi%
  \pgfmathsetlength{\pgf@ya}{\tikz@to@out@max}
  \ifdim\pgf@xa>\pgf@ya%
    \pgf@xa=\pgf@ya%
  \fi%
  \pgfmathsetlength{\pgf@ya}{\tikz@to@in@min}
  \ifdim\pgf@xb<\pgf@ya%
    \pgf@xb=\pgf@ya%
  \fi%
  \pgfmathsetlength{\pgf@ya}{\tikz@to@in@max}
  \ifdim\pgf@xb>\pgf@ya%
    \pgf@xb=\pgf@ya%
  \fi%
}

\def\tikz@to@start@compute@looseness{%
  % Here, we can use the old version, since the source coordinate is
  % correct as-is.  Moreover, we need to, since using a relative first
  % control point doesn't work when the start coordinate is itself +
  % relative (it computes the control point relative to the previous
  % "current point").
  \edef\tikz@computed@start{([shift=(\tikz@to@out:\the\pgf@xa)]\tikz@tofrom)}%
%  \edef\tikz@computed@start{+(\tikz@to@out:\the\pgf@xa)}%
}
\def\tikz@to@end@compute@looseness{%
  % Here, we need to use a different version, since the target
  % coordinate is not necessarily being interpreted literally.
  % Fortunately, we are lucky and relative second control points seem
  % to always work.
  \edef\tikz@computed@end{+(\tikz@to@in:\the\pgf@xb)}%
%  \edef\tikz@computed@end{([shift=(\tikz@to@in:\the\pgf@xb)]\tikz@toto)}%
}
\def\tikz@to@start@compute@control{%
  \let\tikz@computed@start=\tikz@to@out@control%
}
\def\tikz@to@end@compute@control{%
  \let\tikz@computed@end=\tikz@to@in@control%
}

\let\tikz@to@start@compute=\tikz@to@start@compute@looseness%
\let\tikz@to@end@compute=\tikz@to@end@compute@looseness%

% Relative curves

\def\tikz@to@compute@relative{%
  \tikz@scan@one@point\tikz@@to@compute@relative(\tikztostart)%
}
\def\tikz@@to@compute@relative#1{%
  \def\tikz@tofrom{#1}%
  \tikz@scan@one@point\tikz@@@to@compute@relative(\tikztotarget)%
}
\def\tikz@@@to@compute@relative#1{%
  \def\tikz@toto{#1}%
  \begingroup
    % 
    % Adjust start and target so that they lie on the border in the
    % rotated coordinate system.
    %  
    \pgfutil@ifundefined{pgf@sh@ns@\tikztostart}
    {%
      \let\tikz@first@point=\tikz@tofrom%
      \let\tikz@tostart@tikz=\pgfutil@empty
    }%
    {%
      % Start computation of new start.
      {%
        \tikz@tofrom%
        \pgf@xc=\pgf@x%
        \pgf@yc=\pgf@y%
        {%
          \pgftransformreset%
          \pgftransformshift{\pgfqpoint{\pgf@xc}{\pgf@yc}}%
          \pgftransformrotate{\tikz@to@out}%
          \pgftransformshift{\pgfqpoint{-\pgf@xc}{-\pgf@yc}}%
          \pgf@process{\pgfpointtransformed{\tikz@toto}}%
        }%
        \pgf@xc=\pgf@x%
        \pgf@yc=\pgf@y%
        \pgfpointshapeborder{\tikztostart}{\pgfqpoint{\pgf@xc}{\pgf@yc}}%
        \xdef\tikz@tofrom@smuggle{\noexpand\pgfqpoint{\the\pgf@x}{\the\pgf@y}}
      }%
      \let\tikz@first@point=\tikz@tofrom@smuggle%
      \tikz@first@point%
      \edef\tikz@tostart@tikz{(\the\pgf@x,\the\pgf@y)}%
    }%
    \pgfutil@ifundefined{pgf@sh@ns@\tikztotarget}
    {%
      \let\tikz@second@point=\tikz@toto%
    }%
    {%
      % Start computation of new target.
      {%
        \tikz@toto%
        \pgf@xc=\pgf@x%
        \pgf@yc=\pgf@y%
        {%
          \pgftransformreset%
          \pgftransformshift{\pgfqpoint{\pgf@xc}{\pgf@yc}}%
          \pgftransformrotate{180}%
          \pgftransformrotate{\tikz@to@in}%
          \pgftransformshift{\pgfqpoint{-\pgf@xc}{-\pgf@yc}}%
          \pgf@process{\pgfpointtransformed{\tikz@tofrom}}%
        }%
        \pgf@xc=\pgf@x%
        \pgf@yc=\pgf@y%
        \pgfpointshapeborder{\tikztotarget}{\pgfqpoint{\pgf@xc}{\pgf@yc}}%
        \xdef\tikz@toto@smuggle{\noexpand\pgfqpoint{\the\pgf@x}{\the\pgf@y}}
      }%
      \let\tikz@second@point=\tikz@toto@smuggle%
    }%
    \tikz@second@point%
    \edef\tikz@totarget@tikz{(\the\pgf@x,\the\pgf@y)}%
    %
    % Compute distances
    %
    \tikz@to@compute@distance@main%
    \edef\tikz@to@first@distance{\the\pgf@xa}%
    \edef\tikz@to@second@distance{\the\pgf@xb}%
    %
    % Next step: Establish a transformed coordinate system so that the (modified)
    % start is at the origin and the (modified) target is at (1,0)
    %
    \pgftransformreset%
    \pgf@process{\tikz@first@point}%
    \pgf@xa=\pgf@x%
    \pgf@ya=\pgf@y%
    \pgf@process{\tikz@second@point}%
    \advance\pgf@x by-\pgf@xa%
    \advance\pgf@y by-\pgf@ya%
    \pgfpointnormalised{}%
    \pgf@xc=\pgf@x%
    \pgf@yc=\pgf@y%
    \pgf@xb=-\pgf@x%
    \pgf@yb=-\pgf@y%
    %
    % Now compute the control points.
    %
    {%
      \pgftransformshift{\tikz@first@point}%
      \pgftransformcm{\pgf@sys@tonumber\pgf@xc}{\pgf@sys@tonumber\pgf@yc}{\pgf@sys@tonumber\pgf@yb}{\pgf@sys@tonumber\pgf@xc}%
                      {\pgfpointorigin}%
      \pgf@process{\pgfpointtransformed{\pgfpointpolar{\tikz@to@out}{\tikz@to@first@distance}}}%
      \xdef\tikz@computed@start{(\the\pgf@x,\the\pgf@y)}%
    }
    {%
      \pgftransformshift{\tikz@second@point}%
      \pgftransformcm{\pgf@sys@tonumber\pgf@xc}{\pgf@sys@tonumber\pgf@yc}{\pgf@sys@tonumber\pgf@yb}{\pgf@sys@tonumber\pgf@xc}%
                      {\pgfpointorigin}%
      \pgf@process{\pgfpointtransformed{\pgfpointpolar{\tikz@to@in}{\tikz@to@second@distance}}}%
      \xdef\tikz@computed@end{(\the\pgf@x,\the\pgf@y)}%
    }
    \xdef\tikz@computed@path{
      \tikz@tostart@tikz
      .. controls \tikz@computed@start and \tikz@computed@end ..
      \tikz@totarget@tikz}%
  \endgroup
}

### 2018-04-10 paper.tex
Tensor is functorial string diagrams

@@
 \documentclass[11pt,a4paper]{article}
+\usepackage{authblk}
 %\usepackage[utf8]{inputenc}
@@
 \usetikzlibrary{arrows}
+\usetikzlibrary{calc}
 \tikzset{ed/.style={auto,inner sep=2pt,font=\scriptsize}} %edges
@@
 \author{Mitchell Riley}
+\affil{Wesleyan University \\ \texttt{mvriley@wesleyan.edu}}
 \begin{document}
@@
 \section{Introduction}
-
-\todo{TODO: Might have to adjust the entire thing because the action of $\M$ on $\C$ is not strictly monoidal.
-On the other hand, through the entire Pastro/Street paper pretends associativity/etc is strict, so maybe who cares?
-What we really want is just a (non-strict) monoidal functor $\M \to [\C, \C]$ from some $\M$.
-I may also want to put $\otimes$ and $\cdot$ everywhere instead of just writing $MA$ and $NMA$.}
 
@@
 This category was first defined in \cite[Section 6]{Doubles} to investigate the relationship between Tambara modules and the center of a monoidal category.
-There it is called the \emph{double} $\Double_l \C$ of a monoidal category, and our definition is identical, other than flipping the direction of the arrows to match the existing literature on lenses.
+There it is called the \emph{double} $\Double_l \C$ of a monoidal category, and our definition is identical, other than flipping the direction of the morphisms to match the existing work on lenses.
 
@@
 \end{remark}
+
+The remainder of this section comprises some useful observations that were not made in \cite{Doubles}.
 
@@
 \begin{theorem}
-$\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit is $(I, I)$, and the action on morphisms is given by:
+$\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit object is $(I, I)$, and the action on a pair of morphisms $\langle l, r \rangle : S \hto A$ and $\langle l', r' \rangle : T \hto B$ is given by:
 \begin{center}
@@
 \begin{proof}
-Equationally, suppose we have optics $S \hto A$ and $T \hto B$ with representatives:
-\begin{align*}
-(l, r) &: (S \to M \otimes A, M \otimes A' \to S') \\
-(l', r') &: (T \to N \otimes B, N \otimes B' \to T')
-\end{align*}
-Then:
+Equationally, suppose the two optics have complements $M$ and $N$ respectively. Then:
 \begin{align*}
@@
 \end{align*}
-This is functorial, as suggested by the equivalence of the following string diagrams:
-\todo{todo}
+This is well-defined, as the calculus of string diagrams allows us to combine the coend relation on each optic to establish the coend relation for the compound diagram. \todo{draw this?}
+
+Let us check functoriality of $\otimes$. Suppose we have optics:
+\begin{align*}
+\langle l_1, r_1 \rangle : (S_1, S_1') &\hto (S_2, S_2') \\
+\langle l_2, r_2 \rangle : (S_2, S_2') &\hto (S_3, S_3') \\
+\langle p_1, q_1 \rangle : (T_1, T_1') &\hto (T_2, T_2') \\
+\langle p_2, q_2 \rangle : (T_2, T_2') &\hto (T_3, T_3')
+\end{align*}
+The string diagram for $(\langle l_2, r_2 \rangle \circ \langle l_1, r_1 \rangle) \otimes (\langle p_2, q_2 \rangle \circ \langle p_1, q_1 \rangle)$ is:
+\begin{center}
+\input{diagrams/tensor-functorial-left.tikz}
+\end{center}
+And for $(\langle l_2, r_2 \rangle \otimes \langle p_2, q_2 \rangle) \circ (\langle l_1, r_1 \rangle \otimes \langle p_1, q_1 \rangle)$ is:
+\begin{center}
+\input{diagrams/tensor-functorial-right.tikz}
+\end{center}
+These two diagrams are equivalent.
+We can use the naturality of the symmetry morphism to push $l_2$ and $r_2$ through to be next to $l_1$ and $r_1$ respectively.
+This creates two extra twists that can be cancelled in the center of the diagram.
+
+%%%% Note: The following is the above argument written equationally:
 %For future convenience, note that 
@@
 
-The structure morphisms are all lifted from the structure morphisms in $\C$:
+The structure morphisms are all lifted from the structure morphisms in $\C \times \C^\op$:
 \begin{align*}
 \alpha_{(R, R'), (S, S'), (T, T')} &:= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1}) \\
-\lambda_{(S, S')} &:= \iota(\lambda_{(S, S')}, \lambda_{(S, S')}^{-1}) \\
-\rho_{(S, S')} &:= \iota(\rho_{(S, S')}, \rho_{(S, S')}^{-1}) \\
+\lambda_{(S, S')} &:= \iota(\lambda_{S}, \lambda_{S'}^{-1}) \\
+\rho_{(S, S')} &:= \iota(\rho_{S}, \rho_{S'}^{-1}) \\
 s_{(S, S'), (T, T')} &:= \iota(s_{S, T}, s_{T', S'})
@@
 \todo{There is some cheating going on here, composition actually adds an extra $\alpha$, but that wouldn't get in the way.}
+
+\todo{convert this to a string diagram}
 \end{proof}

### 2018-04-18 paper.tex
More diagrams

@@
 \newcommand{\Prof}{\mathbf{Prof}}
+\newcommand{\Core}{\mathbf{Core}}
 \newcommand{\MonCat}{\mathbf{MonCat}}
@@
 
+\newcommand{\switched}{\mathbin{\tilde{\otimes}}}
+
 \newcommand{\id}{\mathrm{id}}
@@
 }
+If $\E$ is cocomplete, there is a formula for the coend as the coequaliser in the diagram
+\[
+\begin{tikzcd}
+\coprod_{M \to N} P(N, M) \ar[r,shift left=.75ex]  \ar[r,shift right=.75ex] & \coprod_{M \in \M} P(M, M) \ar[r] & \int^{M \in \M} P(M, M)
+\end{tikzcd}
+\]
+where $P$ is a functor $\M^\op \times \M \to \E$.
 
@@
 This category was first defined in \cite[Section 6]{Doubles} to investigate the relationship between Tambara modules and the center of a monoidal category.
-There it is called the \emph{double} $\Double_l \C$ of a monoidal category, and our definition is identical, other than flipping the direction of the morphisms to match the existing work on lenses.
+There it is called the \emph{double} $\Double_l \C$ of a monoidal category, and our definition is identical, other than flipping the direction of the morphisms to match the existing work on lenses, and restricting our attention to the unenriched case.
 
@@
 Optics will always be written with a crossed arrow $\hto$, to distinguish them from morphisms of $\C$.
+
+\begin{example}
+For any three objects $M, A, A' \in \C$, there is the \emph{tautological} optic \[t_{M,A} : (M \otimes A, M \otimes A') \hto (A, A')\] which is given by $\langle \id_{M \otimes A}, \id_{M \otimes A'} \rangle$.
+\end{example}
 
@@
 Note that the definition of the $\Optic$ category involves a coend possibly indexed by a large category.
-To be maximally careful, we should only ever discuss $\Optic$ categories where we know that the coend exists by some other means, e.g., by exhibiting an isomorphism with some other set.
+To be careful, we should only ever discuss $\Optic$ categories where we know that the coend exists by some other means, e.g., by exhibiting an isomorphism with some other set.
 For many---but not all---of the examples given later, we provide such an isomorphism.
@@
 \end{proposition}
-\begin{proposition}
+\begin{proof}
 \todo{todo}
-\end{proposition}
+\end{proof}
 
@@
 
-In particular, for any $M \in \C$, the image of the identity yields an optic $c_M : (M, M) \hto (I, I)$, that we will call the connector.
-
-States are not as easy to describe in general, however:
+In particular, for any $S \in \C$, the image of the identity yields an optic $c_S : (S, S) \hto (I, I)$, that we will call the connector:
+\begin{center}
+\input{diagrams/connector-full.tikz}
+\end{center}
+Or, again omitting the unitors:
+\begin{center}
+\input{diagrams/connector.tikz}
+\end{center}
 
@@
 \begin{proposition}
-Together this operation defines a \todo{pseudo?}functor $\Optic : \SymmMonCat \to \SymmMonCat$.
+\label{prop-optic-functor}
+Collectively this operation defines a \todo{pseudo?}functor \[\Optic : \SymmMonCat \to \SymmMonCat.\]
 \end{proposition}
@@
 
-Categories of optics admit their own diagrammatic language, by virtue of them being \emph{teleological categories}.
+Categories of optics admit their own diagrammatic language, by virtue of being \emph{teleological categories}, monoidal categories with counits.
 In fact, we show in Theorem \ref{optic-is-free-teleological-cat} that $\Optic_\C$ is the free teleological category on a collection of dualisable morphisms $\C$.
@@
 In this section we assume that $\C$ is a \emph{strict} symmetric monoidal category.
+It will be convenient to equip $\Optic_\C$ with a slightly different symmetric monoidal structure: \todo{And the universal property given in this section is an argument for this being the ``morally correct'' tensor}
+
+\begin{definition}
+The \emph{switched} monoidal product on $\Optic_\C$ is given on objects by 
+\begin{align*}
+(S, S') \switched (T, T') := (S \otimes T, T' \otimes S')
+\end{align*}
+And on morphisms $\langle l, r \rangle : S \hto A$ and $\langle l', r' \rangle : T \hto B$ by:
+\begin{center}
+\input{diagrams/switched-tensor-on-morphisms.tikz}
+\end{center}
+\end{definition}
+
+\begin{proposition}
+$\Optic_\C$ equipped with the switched tensor is monoidally equivalent to it equipped with the unswitched tensor.
+\end{proposition}
+\begin{proof}
+\todo{todo, I hope this is true?}
+\end{proof}
 
@@
 \begin{itemize}
-\item A wide symmetric monoidal subcategory $\C_d$ of \emph{dualisable morphisms}, with an involutive strong symmetric monoidal functor $(-)^* : \C_d \to \C_d^\op$; and,
-\item A family of morphisms $\varepsilon_X : X \otimes X^* \to I$, called \emph{counits}, natural with respect to the morphisms in $\C_d$, such that
+\item A wide symmetric monoidal subcategory $\C_d$ of \emph{dualisable morphisms}, with an involutive strong symmetric monoidal functor $(-)^* : \C_d \to \overline{\C_d^\op}$, where---not finding a standard symbol for such a thing---we mean $\overline{\C_d^\op}$ to be the category with both the direction of the arrows \emph{and} the order of the tensor flipped: $(A \otimes B)^* = B^* \otimes A^*$.
+\todo{Do we want this to be strict?}
+\item A symmetric monoidal extranatural family of morphisms $\varepsilon_X : X \otimes X^* \to I$, called \emph{counits}, natural with respect to the morphisms in $\C_d$.
+\end{itemize}
+\end{definition}
+Unpacking the definition, $\varepsilon$ being a symmetric monoidal extranatural transformation amounts to the following diagrams in $\C$ commuting:
 \[
@@
 \begin{tikzcd}
-X^* \otimes X \ar[r, "s_{X^*, X}"]  \ar[dr, "\varepsilon_{X^*}", swap] & X \otimes X^* \ar[d, "\varepsilon_X"] \\
+X^* \otimes X \ar[r, "\sigma"]  \ar[dr, "\varepsilon_{X^*}", swap] & X \otimes X^* \ar[d, "\varepsilon_X"] \\
 & I
@@
 \begin{tikzcd}
-X \otimes Y \otimes X^* \otimes Y^* \ar[r, "X \otimes s_{Y,X^*} \otimes X^*"]  \ar[dr, "\varepsilon_{X \otimes Y}", swap] & X \otimes X^* \otimes Y \otimes Y^* \ar[d, "\varepsilon_X \otimes \varepsilon_Y"] \\
+X \otimes Y \otimes Y^* \otimes X^* \ar[r, "X \otimes \varepsilon_Y \otimes X^*"]  \ar[dr, "\varepsilon_{X \otimes Y}", swap] & X \otimes X^* \ar[d, "\varepsilon_X"] \\
 & I
@@
 \] 
-commute for all $f : X \to Y$ is in $\C_d$.
-\end{itemize}
-\end{definition}
-Note that because $\C_d$ is symmetric monoidal and has the same collection of objects as $\C$, the symmetric monoidal structure of $\C$ must all be contained in $\C_d$.
+where $f : X \to Y$ is in $\C_d$.
+
+%%%% The following is a version with duality given by reflection.
+%\begin{definition}[{\cite[Definition 5.1]{CoherenceForLenses}}]
+%A \emph{teleological category is} a symmetric monoidal category $(\C, \otimes, I)$, equipped with:
+%\begin{itemize}
+%\item A wide symmetric monoidal subcategory $\C_d$ of \emph{dualisable morphisms}, with an involutive strong symmetric monoidal functor $(-)^* : \C_d \to \C_d^\op$; and,
+%\item A family of morphisms $\varepsilon_X : X \otimes X^* \to I$, called \emph{counits}, natural with respect to the morphisms in $\C_d$, such that
+%\[
+%\begin{tikzcd}
+%X \otimes Y^* \ar[r, "f \otimes Y^*"]  \ar[d, "X \otimes f^*", swap] & Y \otimes Y^* \ar[d, "\varepsilon_Y"] \\
+%X \otimes X^* \ar[r, "\varepsilon_X", swap] & I
+%\end{tikzcd} \hspace{1cm}
+%\begin{tikzcd}
+%X^* \otimes X \ar[r, "s_{X^*, X}"]  \ar[dr, "\varepsilon_{X^*}", swap] & X \otimes X^* \ar[d, "\varepsilon_X"] \\
+%& I
+%\end{tikzcd}
+%\]
+%\[
+%\begin{tikzcd}
+%X \otimes Y \otimes X^* \otimes Y^* \ar[r, "X \otimes s_{Y,X^*} \otimes X^*"]  \ar[dr, "\varepsilon_{X \otimes Y}", swap] & X \otimes X^* \otimes Y \otimes Y^* \ar[d, "\varepsilon_X \otimes \varepsilon_Y"] \\
+%& I
+%\end{tikzcd}
+%\]
+%commute for all $f : X \to Y$ is in $\C_d$.
+%\end{itemize}
+%\end{definition}
+
+%\begin{remark}
+%Compact closed categories very nearly form examples of teleological categories.
+In a compact closed category, there are canonical isomorphisms $(X \otimes Y)^* \cong Y^* \otimes X^*$.
+In a teleological category, however, duality does not reverse the order of the tensor.
+\todo{If $\C$ is strict, as it is here, does this matter?}
+%\end{remark}
+
+Note that because $\C_d$ is symmetric monoidal and has the same collection of objects as $\C$, the symmetric monoidal structure morphisms of $\C$ must all be in $\C_d$.
 
 \begin{example}
-Any symmetric monoidal category with terminal monoidal unit is trivially teleological, setting the dualisable morphisms to be only the structure maps of the monoidal category.
+Any symmetric monoidal category with terminal monoidal unit is trivially teleological, setting the dualisable morphisms to be the structure maps of the monoidal category.
+\end{example}
+
+\begin{example}
+Any compact closed category is a teleological category, where every morphism is dualisable and the unit morphisms have been forgotten.
 \end{example}
@@
 
-\begin{remark}
-Compact closed categories very nearly form an example of teleological categories.
-In a compact closed category, there are canonical isomorphisms $(X \otimes Y)^* \cong Y^* \otimes X^*$.
-In a teleological category, however, duality does not reverse the order of the tensor.
-\todo{If $\C$ is strict though, does this matter?}
-\end{remark}
-
 \begin{definition}
@@
 
-Together we have $\Tele$, the (1-)category of teleological categories and functors.
+Together we have $\Tele$, the subcategory of $\SymmMonCat$ given by teleological categories and teleological functors.
 There are evident functors $U : \Tele \to \SymmMonCat$ and $(-)_d : \Tele \to \SymmMonCat$, that take a teleological category to its underlying symmetric monoidal category and subcategory of dualisable morphisms respectively.
@@
 \item The dualisable morphisms are all morphisms of the form $\iota(f, g)$;
-\item The involution is given on objects by $(S, S')^* = (S', S)$, and on a morphism $\iota(f, g)$ by $\iota(g, f)$;
-\item The counit $\varepsilon_{(S, S')}$  is given by the connector $c_{S \otimes S'}$.
+\item The involution is given on objects by $(S, S')^* := (S', S)$, and on a morphisms by \[\iota(f, g)^* := \iota(g, f);\]
+\item The counit $\varepsilon_{(S, S')} : (S, S') \switched (S, S')^* = (S \otimes S', S \otimes S') \to (I, I)$ is given by the connector: \[\varepsilon_{(S, S')} := c_{S \otimes S'}.\]
 \end{itemize}
@@
 \begin{proof}
-That morphisms of the form $\iota(f, g)$ constitute a category and that $(-)^*$ is a symmetric monoidal involution is clear. \todo{actually check monoidal part}
-
-To check extranaturality, suppose we have a dualisable optic $\iota(f, g) : (X, X') \to (Y, Y')$, so $f : X \to Y$ and $g : Y' \to X'$.
+That morphisms of the form $\iota(f, g)$ constitute a category and that $(-)^*$ is a symmetric monoidal involution is clear: we have
+\begin{align*}
+\left( (S, S') \switched (T, T') \right)^* 
+&= \left( S \otimes T, T' \otimes S' \right)^* \\
+&= \left(T' \otimes S', S \otimes T  \right) \\
+&= (T', T) \otimes (S', S) \\
+&= (T, T')^* \otimes (S, S')^*
+\end{align*}
+
+To check extranaturality of $\varepsilon$, suppose we have a dualisable optic $\iota(f, g) : (S, S') \hto (T, T')$, so $f : S \to T$ and $g : T' \to S'$.
 Extranaturality is witnessed by the equality of the string diagrams:
 \begin{center}
-\includegraphics[width=.4\textwidth]{diagrams/counit-extranaturality}
+\input{diagrams/counit-extranatural-left.tikz}
+\qquad \raisebox{1.5cm}{$=$} \qquad 
+\input{diagrams/counit-extranatural-right.tikz}
 \end{center}
@@
 \end{center}
-Monoidal:
+Monoidality:
 \begin{center}
@@
 
-\todo{They stress about the empty set, have I avoided that issue?}
-
-\begin{proposition}
-$\Optic : \SymmMonCat \to \Tele$ is a functor.
-\end{proposition}
-\begin{proof}
-We have to show that for a symmetric monoidal functor $F : \C \to \D$, the induced functor $\Optic_\C \to \Optic_\D$ is teleological.
+%\todo{They stress about the empty set, have I avoided that issue?}
+
+\begin{proposition}
+The functor $\Optic : \SymmMonCat \to \SymmMonCat$ of Proposition \ref{prop-optic-functor} has its image in the subcategory $\Tele$.
+\end{proposition}
+\begin{proof}
+We must show that for a symmetric monoidal functor $F : \C \to \D$, the induced functor $\Optic_\C \to \Optic_\D$ is teleological.
 
@@
 
+%\begin{proposition}
+%Suppose $\langle l, r \rangle : (S, S') \hto (A, A')$ has complement $M$. Then 
+%\begin{align*}
+%\langle l, r \rangle = (\varepsilon_{(M, I)} \otimes (A, A'))\iota(l, r).
+%\end{align*}
+%\end{proposition}
+%\begin{proof}
+%First note that because $\C$ is strict monoidal, the counit $\varepsilon_{(M, I)} : (M \otimes I, M \otimes I) = (M, M) \hto (I, I)$ is equal to the connector $c_M : (M, M) \hto (I, I)$.
+%
+%The claim then holds, as any optic 
+%\begin{center}
+%\input{diagrams/generic-optic-noline.tikz}
+%\end{center}
+%is equal to the composite
+%\begin{center}
+%\input{diagrams/optic-decomposed.tikz}
+%\end{center}
+%where we have drawn the normally invisible strings corresponding to the unit $I$.
+%\end{proof}
+
 \begin{proposition}
 \label{prop-optic-decompose}
-Suppose $p : (S, S') \to (A, A')$ has representative $\langle l, r \rangle$. Then 
-\begin{align*}
-p = (\varepsilon_{(M, I)} \otimes (A, A'))\iota(l, r).
-\end{align*}
-\end{proposition}
-\begin{proof}
-\todo{by string diagram}
+Suppose $\langle l, r \rangle : (S, S') \hto (A, A')$ has complement $M$. Then 
+\begin{align*}
+\langle l, r \rangle = (\varepsilon_{(M, I)} \otimes (A, A'))(j(l) \otimes j(r)^*)
+\end{align*}
+where $j : \C \to \Optic_\C$ is the functor $j(A) := \iota(A, I)$.
+\end{proposition}
+\begin{proof}
+First note that because $\C$ is strict monoidal, the counit $\varepsilon_{(M, I)} : (M \otimes I, M \otimes I) = (M, M) \hto (I, I)$ is equal to the connector $c_M : (M, M) \hto (I, I)$.
+\todo{todo}
 \end{proof}
@@
 \label{optic-is-free-teleological-cat}
-Suppose $\C$ is a \todo{strict} symmetric monoidal category and $\T$ is a teleological category.
-For all monoidal functors $F : \C \to \T_d$, there exists a teleological functor $K : \Lens_\C \to \T$, unique up to isomorphism, such that $Kj \cong F$.
+Suppose $\C$ is a strict symmetric monoidal category and $\T$ is a teleological category.
+For all monoidal functors $F : \C \to \T_d$, there exists a teleological functor $K : \Optic_\C \to \T$, unique up to isomorphism, such that $Kj \cong F$.
 %$\Optic$ is left adjoint to $(-)_d$, so $\Optic_\C$ is the free teleological category on a category of dualisable morphisms $\C$.
@@
 \begin{proof}
-\todo{This is the point at which I have run in to trouble: TODO}
-
-%On objects, define $K(S, S') = FS \otimes (FS')*$.
-Suppose $p : (S, S') \hto (A, A')$ is an optic with representative $\langle l, r \rangle$.
-By Proposition \ref{prop-optic-decompose} and the previous Lemma, $p$ may be decomposed as:
-%\begin{align*}
-%\langle l, r \rangle = (\varepsilon_{(M, I)}\iota(\rho_M^{-1}, \lambda_M) \otimes \id_{(A, A')})\iota(l, s_{M,A'}r)
-%\end{align*}
-%But now, in order for $K$ to be a teleological functor with $Kj \cong F$, each piece of this expression must be preserved by $K$, so we define:
-%\begin{align*}
-%K\langle l, r \rangle = (\varepsilon_{FM} \otimes \id_{FA \otimes FA'})(Fl \otimes s_{FM,FA'} (Fr)^* )
-%\end{align*}
+On objects, define $K(S, S') = FS \otimes (FS')^*$. Suppose $\langle l, r \rangle : (S, S') \hto (A, A')$ is an optic. By the previous Proposition,
+\begin{align*}
+\langle l, r \rangle = (\varepsilon_{(M, I)} \otimes (A, A'))(j(l) \otimes j(r)^*)
+\end{align*}
+But now, in order for $K$ to be a teleological functor with $Kj \cong F$, each piece of this expression must be preserved by $K$, so we are forced to define:
+\begin{align*}
+K\langle l, r \rangle = (\varepsilon_{FM} \otimes FA \otimes (FA')^*)(Fl \otimes (Fr)^* )
+\end{align*}
 %
@@
 %We now have to check that this is well defined. \todo{todo}
-%
-%\todo{incomplete}
+
+\todo{incomplete}
 \end{proof}
@@
 \item Given $f : S \to A$ and $g : A' \to S'$, the optic $j(f) \otimes j(g)^* : (S \otimes I, I \otimes S') \hto (A \otimes I, I \otimes A')$ is not equal to $\iota(f, g)$.
-It is also not in a form that can be composed with the unitors of $\Optic_\C$, as the $I$s are not all on the same side.
+It is also not in a form that can be composed with the unitors of $\Optic_\C$, as the $I$s are not on the same side in either the domain or codomain.
 \item \todo{wasn't there more?}
@@
 \begin{definition}
-An optic $p : S \hto A$ is \emph{lawful} if $outside(p) = \id_S$, and $inside(p) = \langle t A \rangle$ for some $t : M \to M$ in $\M$.
+An optic $p : S \hto A$ is \emph{lawful} if $outside(p) = \id_S$, and $inside(p) = \langle \phi A \rangle$ for some $\phi : M \to M$ in $\M$.
 \end{definition}
@@
 \begin{proof}
-\todo{This is painful but seems important. There may be a more general principle at work here but I couldn't see it. Put in an appendix?}
-
-There is a well known formula for the coend as the coequaliser in the diagram
-\[
-\begin{tikzcd}
-\coprod_{M \to N} P(N, M) \ar[r,shift left=.75ex]  \ar[r,shift right=.75ex] & \coprod_{M \in \M} P(M, M) \ar[r] & \int^{M \in \M} P(M, M)
-\end{tikzcd}
-\]
-where $P$ is a functor $\M^\op \times \M \to \E$.
-
-In our case $\E = \Set$, and unwinding the coequaliser this states that $\int^{M \in \M} \C(M A, M A)$ is a quotient of the set $\coprod_{M \in \M} \C(M A, M A)$.
-Two morphisms $f : M A \to M A$ and $g : N A \to N A$ are identified when there exists a $k : N A \to M A$ and natural transformation $\phi : M \to N$ such that the diagram
+The coend relation in $\int^{M \in \M} \C(M A, M A)$ states that two morphisms $f : M A \to M A$ and $g : N A \to N A$ are identified when there exists a $k : N A \to M A$ and morphism $\phi : M \to N$ such that
 \[
@@
 commutes.
-This gives a binary relation $f \rightsquigarrow g$ that is not likely to be symmetric or transitive.
-The coend is obtained by identifying all morphisms related in this way, so in all, $\langle f \rangle = \langle g \rangle$ iff there exists a zigzag $f \leftrightsquigarrow u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n \leftrightsquigarrow g$ where the relation may apply in either direction.
-\todo{replace this with $f = u_1 \leftrightsquigarrow \dots u_n = g$ for clarity}
-
-If $f \rightsquigarrow g$ then $f^2 \rightsquigarrow g^2$: this is clear by stacking the above diagram, and then taking $k' = fk = kg$.
-This argument extends to show that $f^n \rightsquigarrow g^n$ for any $n$.
-
-Similarly unwinding the coequaliser for $\int^{M \in \M} \C(S, M A) \times \C(M A, S)$, two pairs $(l, r) : (S \to M A, MA \to S)$ and $(l', r') : (S \to NA, NA \to S)$ in $\coprod_{M \in \M} \C(S, M A) \times \C(M A, S)$ are identified when there exists a $\phi : M \to N$ such that
+This gives a binary relation $f \rightsquigarrow g$ that is not likely to be symmetric or transitive in general.
+The coend is obtained by identifying all morphisms related in this way, $\langle f \rangle = \langle g \rangle$ iff there exists a zigzag $f = u_1 \leftrightsquigarrow u_2 \leftrightsquigarrow \dots  \leftrightsquigarrow u_{n-1} \leftrightsquigarrow u_n = g$ where the relation may apply in either direction.
+
+Note that if $f \rightsquigarrow g$ then $ff \rightsquigarrow gg$: this is clear by stacking the above diagram, and then taking $k' = fk = kg$.
+This argument can be repeated to show that $f^n \rightsquigarrow g^n$ for any $n$.
+
+Similarly two representatives $\langle l, r \rangle : S \hto A$ and $\langle l', r' \rangle : S \hto A$ with complements $M$ and $N$ respectively are identified when there exists a $\phi : M \to N$ such that
 \[
@@
 \]
-commutes. \todo{put the $S$ on the outside?}
-
-We will now prove the result by induction.
-Because $inside(p) = \langle t \rangle$, there is a representative $\langle l, r \rangle$ so that $\langle lr \rangle = \langle t \rangle$.
-There therefore must exist a finite chain of relations $lr \leftrightsquigarrow u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n \leftrightsquigarrow t$.
+commutes.
+
+Now suppose $p = \langle l, r \rangle : S \hto A$ is a lawful optic, so $rl = \id_S$ and $\langle lr \rangle = \langle \psi A\rangle$.
+There therefore must exist a finite chain of relations $lr = u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n = \psi A$.
 Supposing that the first relation faces rightwards, we have a diagram:
@@
 \begin{tikzcd}
-M A \ar[r, "\phi_A"] \ar[d, "r", swap] & N A \ar[dd, "u_1"] \ar[ddl, "k"] \\
+M A \ar[r, "\phi_A"] \ar[d, "r", swap] & N A \ar[dd, "u_2"] \ar[ddl, "k"] \\
 S \ar[d,"l",swap] & \\
@@
 \]
-where the composite of the morphisms on the right is $\phi_A l r k = \phi_A k \phi_A k = u_1^2$.
-Composing in the other direction we have $r k \phi_A l = rlrl = \id_S$.
-We have shown that whenever $rl = \id_S$ and $lr \rightsquigarrow u_1$, then there exist $l_1$ and $r_1$ so that $r_1l_1 = \id_S$, $l_1r_1 = u_1^2$ and $(l, r) \rightsquigarrow (l_1, r_1)$.
-A symmetric argument shows that if instead $lr \leftsquigarrow g$, there exist $l_1$ and $r_1$ so that $r_1l_1 = \id_S$, $l_1r_1 = u_1^2$ and $(l, r) \leftsquigarrow (l_1, r_1)$.
-
-We can now inductively apply the above argument to the chain $u_1^2 \leftrightsquigarrow \dots \leftrightsquigarrow u_n^2 \leftrightsquigarrow t^2 = t$, obtained by squaring each morphism in the original chain.
-We eventually obtain a chain $(l, r) \leftrightsquigarrow (l_1, r_1)\leftrightsquigarrow \dots \leftrightsquigarrow (l_n, r_n) \leftrightsquigarrow (l_t, r_t)$, where $r_tl_t = \id_S$ and $l_t r_t = t$.
-This pair $(l_t, r_t)$ is the required representative.
+Define $l' = \phi_A l$ and $r' = rk$. The above diagram is a witness that $\langle l, r \rangle = \langle l', r' \rangle$ as an optic $S \hto A$.
+
+The composite $l'r'$ is:
+\begin{align*}
+l'r' &= \phi_A l r k \\
+&= \phi_A k \phi_A k \\
+&= u_2^2
+\end{align*}
+
+A symmetric argument shows that if instead the relation faces leftward, so $lr \leftsquigarrow g$, there exists $l'$ and $r'$ so that $\langle l, r \rangle = \langle l', r' \rangle$ and $l'r' = u_2^2$.
+
+We can now inductively apply the above argument to the shorter chain \[l'r' = u_1^2 \leftrightsquigarrow \dots \leftrightsquigarrow u_n^2 \leftrightsquigarrow (\psi A)^2 = \psi^2 A,\] obtained by squaring each morphism in the original chain, until we are left with a representative $\langle l^*, r^* \rangle$ such that $l^*r^* = \psi^N A$, for some $N>0$.
+This pair $\langle l^*, r^* \rangle$ is the required representative.
 \end{proof}
@@
 Any pair of maps $f : 0 \to A$, $g : A' \to S'$ yield equivalent optics $\iota(f, g)$, as the corresponding $\fget$ and $\fput$ functions must be the unique maps from $0$.
+\end{remark}
+
+\begin{remark}
+In the case that $\C$ is cartesian closed, $\Optic_\times$ is monoidal closed via the astonishing formula
+\begin{align*}
+[(S, S'), (A, A')] := (\homC(S, A) \times \homC(S \times A', S'), \, S \times A')
+\end{align*}
+where $\homC(-, -)$ denotes the internal hom. For a proof see \cite[Section 1.2]{DialecticaCategories}. This cannot be extended to non-cartesian closed categories, the isomorphism 
+\begin{align*}
+\Optic_\times((S, S') \otimes (T, T'), (A, A')) \cong \Optic_\times((S, S'),  [(T, T'), (A, A')])
+\end{align*}
+uses the diagonal maps of $\C$ in an essential way.
 \end{remark}
@@
 \Optic_\otimes((S, S'), (A, A')) &= \int^{M \in \C} \C(S, M \otimes A) \times \C(M \otimes A', S') \\
-&\cong \int^{M \in \C} \C(\homC(S,A), M) \times \C(M \otimes A', S') \\
-&\cong \C(\homC(S, A) \otimes A', S')
-\end{align*}
-where $\homC(S, A)$ denotes the internal hom.
+&\cong \int^{M \in \C} \C(S, M \otimes A) \times \C(M, \homC(A',S')) \\
+&\cong \C(S, \homC(A',S') \otimes A)
+\end{align*}
+where $\homC(S, A)$ denotes the internal hom. If $\C$ is cartesian, this is of course isomorphic to the pair of maps discussed in the previous section.
 
@@
 
+For any category $\C$, there is a unique action of the terminal category $1$ on $\C$ that fixes every object.
+
+\begin{proposition}
+The category of optics for this action is isomorphic to $\C \times \C^\op$.
+\end{proposition}
+\begin{proof}
+\begin{align*}
+\Optic_1((S, S'), (A, A')) &= \int^{M \in 1} \C(S, MA) \times \C(MA', S') \\
+&\cong \C(S, \star \cdot A) \times \C(\star \cdot A', S') \\
+&\cong \C(S, A) \times \C(A', S')
+\end{align*}
+where $\star$ denotes the object of $1$.
+\end{proof}
+
+\begin{proposition}
+The category of \emph{lawful} optics for this action is isomorphic to $\Core(\C)$, the subcategory of isomorphisms in $\C$.
+\end{proposition}
+\begin{proof}
+Given any lawful $\langle l, r \rangle : S \hto A$, we know that $rl = \id_S$, and $lr = \phi \cdot A$ where $\phi : \star \to \star$ in $1$.
+But $\phi$ must be $\id_\star$, so $lr = \id_A$, and $r = l^{-1}$.
+\end{proof}
+
 \subsection{Setters}
@@
 
-\todo{Taken from http://cs.ioc.ee/~tarmo/ssgep15/ssgep-1a.pdf}
-\begin{definition}
-\todo{This definition should work fine if we instead use an action of some $\M$ on $\C$, but I don't think that ever comes up?} Suppose $(\C, \otimes, I)$ is a monoidal category.
-A \emph{(left) strength} for an endofunctor $F : \C \to \C$ is a natural transformation
+%\todo{Taken from http://cs.ioc.ee/~tarmo/ssgep15/ssgep-1a.pdf}
+\begin{definition}[\cite{StrongFunctors}]
+Suppose $(\C, \otimes, I)$ is a monoidal category. A \emph{(left) strength} for an endofunctor $F : \C \to \C$ is a natural transformation
 \begin{align*}
@@
 
+\subsection{``Achromatic'' Lenses}
+
 \subsection{Polymorphic Optics}
@@
 \end{center}
-Note that the type has been changed from $\texttt{(Int, Int)}$ to $\texttt{(String, Int)}$
+Note that the type has been changed from $\texttt{(Int, Int)}$ to $\texttt{(String, Int)}$.
 
@@
 \begin{proof}
-This follows abstractly as a left adjoint of a strong monoidal functor \cite{Kelly1974}.
+This follows abstractly as the left adjoint of a strong monoidal functor \cite{Kelly1974}.
 \end{proof}
@@
 \begin{proposition}
-If $p : S \hto A$ is a lawful optic then the associated natural transformation $(U-)(A,A) \to (U-)(S,S)$ is a lax monoidal. \todo{Rename the natural transformation $p$}
+If $p : S \hto A$ is a lawful optic then the associated natural transformation $\tilde{p} : (U-)(A,A) \to (U-)(S,S)$ is a lax monoidal.
 \end{proposition}
@@
 \begin{align*}
-p_P = (UP)(l,r) \alpha_{A,A,M}
+\tilde{p}_P = (UP)(l,r) \alpha_{A,A,M}
 \end{align*}
@@
 
-To show $p$ is monoidal, we must show that both
+To show $\tilde{p}$ is monoidal, we must show that both
 \[
 \begin{tikzcd}
-UP(A,A) \times UQ(A,A) \ar[r, "p_P \times p_Q"] \ar[d, swap] & UP(S, S) \times UQ(S, S)  \ar[d] \\
-U(P \odot Q)(A,A)  \ar[r, "p_{P \odot Q}", swap] & U(P \odot Q)(S,S)
+UP(A,A) \times UQ(A,A) \ar[r, "\tilde{p}_P \times \tilde{p}_Q"] \ar[d, swap] & UP(S, S) \times UQ(S, S)  \ar[d] \\
+U(P \odot Q)(A,A)  \ar[r, "\tilde{p}_{P \odot Q}", swap] & U(P \odot Q)(S,S)
 \end{tikzcd}
@@
 1 \ar[d] \ar[dr] & \\
-UI(A,A)  \ar[r, "p_I", swap] & UI(S,S)
+UI(A,A)  \ar[r, "\tilde{p}_I", swap] & UI(S,S)
 \end{tikzcd}
@@
 \begin{align*}
-\langle (p_P \times p_Q)(x, y) \rangle &= \langle (UP)(l,r) \alpha_{A,A,M} x,  (UQ)(l,r) \beta_{A,A,M} y\rangle \\
+\langle (\tilde{p}_P \times \tilde{p}_Q)(x, y) \rangle &= \langle (UP)(l,r) \alpha_{A,A,M} x,  (UQ)(l,r) \beta_{A,A,M} y\rangle \\
 &= \langle (UP)(l,lr) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(by the coend relations)} \\
@@
 &= (U(P \odot Q))(l,r) (\alpha_{A,A,M} \odot \beta_{A,A,M}) \langle x, y \rangle && \text{(by definition of $\alpha \odot \beta$)} \\
-&= p_{P \odot Q} \langle x, y \rangle
+&= \tilde{p}_{P \odot Q} \langle x, y \rangle
 \end{align*}
@@
 \begin{align*}
-p_I(\id_A) = (UI)(l,r) (M \id_A) = r \id_{MA} l = rl = \id_S
+\tilde{p}_I(\id_A) = (UI)(l,r) (M \id_A) = r \id_{MA} l = rl = \id_S
 \end{align*}
@@
 \begin{proposition}
-Let $\C = \Set$ and suppose $p : S \hto A$ is a pre-lens such that the associated natural transformation $p : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal. Then $p$ is a lens.
+Let $\C = \Set$ and suppose $p : S \hto A$ is a lens such that the associated natural transformation $p : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal. Then $p$ is lawful.
 \end{proposition}

### 2018-05-04 paper.tex
Counit symmetry
Extra tikz code not necessary
Progress

@@
 \usetikzlibrary{calc}
+\usetikzlibrary{decorations.markings}
 \tikzset{ed/.style={auto,inner sep=2pt,font=\scriptsize}} %edges
@@
 \tikzset{vertbig/.style={draw,circle, minimum size=8mm, inner sep=0pt, fill=white}}
-\input{tikzcurverel}
+\tikzset{->-/.style={decoration={
+  markings,
+  mark=at position #1 with {\arrow{>}}},postaction={decorate}}}
 
@@
 
-\subsection{Notation}
-\todo{I am open to changing any/all of these}
-\begin{itemize}
-\item Given $f : A \to B$ and $g : A \to C$, I write $[f, g] : A \to B \times C$ and $!_A : A \to 1$.
-\item Given $f : A \to B$ and $g : C \to D$, I write $f \times g : A \times C \to B \times D$.
-\item Given a $x \in P(C, C)$, I write $\langle x \rangle \in \int^C P(C, C)$ for its image, and $\copr_C : P(C,C) \to \int^C P(C, C)$
-\item For a monoidal category, the structure maps are $\alpha$, $\lambda$ and $\rho$. A symmetry is $s$.
-\end{itemize}
-
 \todo{
@@
 
-\todo{ Notation: For a monoidal category, the structure maps are $\alpha$, $\lambda$ and $\rho$, symmetry is $s$.
-For an action of $(\M, \otimes, I)$ on $\C$ we have two structure maps that are isomorphisms: $\epsilon_A : A \to IA$ and $\mu_{M,N,A} = MNA \to (M \otimes N)A$.
-}
-
 We begin by constructing the category of optics in a symmetric monoidal category $\C$.
@@
 \begin{remark}
-\todo{I hope I can get away with this...} In what follows, we use the standard cheat of omitting associativity isomorphisms.
+In what follows, we use the standard cheat of omitting associativity isomorphisms.
 \end{remark}
@@
 
-If $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\langle l, r \rangle : (S, S') \hto (A, A')$ for the image of this pair in $\Optic_\C((S, S'), (A, A'))$, and say that $M$ is the complement for this representative.
+Because this coend takes place in $\Set$, we can describe the set $\Optic_\C((S, S'), (A, A'))$ explicitly.
+It is the set of pairs $(l, r)$, where $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, quotiented by the relation
+\begin{align*}
+((f \otimes A) l, r) \sim (l, r (f \otimes A'))
+\end{align*}
+where $l : S \to M \otimes A$, $r : N \otimes A' \to S'$ and $f : M \to N$.
+
+If $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\langle l, r \rangle : (S, S') \hto (A, A')$ for the image of this pair in $\Optic_\C((S, S'), (A, A'))$, and say that $M$ is the complement for the representative.
 Optics will always be written with a crossed arrow $\hto$, to distinguish them from morphisms of $\C$.
@@
 
-Graphically, this is placing the second optic into the middle of the first:
+Graphically, this is placing the first optic into the hole of the second:
 \begin{center}
@@
 \end{center}
-This dashed line above the diagram represents the unit object. As is standard, we will elide the unit object and unitors in future diagrams. The diagram for the identity becomes simply:
+This dashed line above the diagram represents the unit object.
+As is standard, we will elide the unit object and unitors in future diagrams unless they are necessary.
+The diagram for the identity becomes simply:
 \begin{center}
@@
 
-Categories of optics admit their own diagrammatic language, by virtue of being \emph{teleological categories}, monoidal categories with counits.
-In fact, we show in Theorem \ref{optic-is-free-teleological-cat} that $\Optic_\C$ is the free teleological category on a collection of dualisable morphisms $\C$.
-
-In this section we assume that $\C$ is a \emph{strict} symmetric monoidal category.
+In this section we establish a universal property of the $\Optic$ construction.
+The idea is that every optic $\langle l, r\rangle : (S, S') \hto (A, A')$ consists of a morphism $S \to M \otimes A$ and the `formal dual' of a morphism $M \otimes A' \to S'$, composed with a `formal counit' that traces out the object $M$:
+\begin{center}
+\input{diagrams/generic-optic-folded.tikz}
+\end{center}
+
+We assume temporarily that $\C$ is a \emph{strict} symmetric monoidal category.
 It will be convenient to equip $\Optic_\C$ with a slightly different symmetric monoidal structure: \todo{And the universal property given in this section is an argument for this being the ``morally correct'' tensor}
@@
 \begin{proposition}
-$\Optic_\C$ equipped with the switched tensor is monoidally equivalent to it equipped with the unswitched tensor.
-\end{proposition}
-\begin{proof}
-\todo{todo, I hope this is true?}
-\end{proof}
-
-\begin{definition}[{\cite[Definition 5.1]{CoherenceForLenses}}]
+$(\Optic_\C, \switched, (I, I))$ is a symmetric monoidal category that is monoidally equivalent to $\Optic_\C$ with the unswitched tensor.
+\end{proposition}
+\begin{proof}
+The proof that $(\Optic_\C, \switched, (I, I))$ is symmetric monoidal is nearly identical to that for the unswitched tensor.
+Note that due to the switching, the structure morphisms are slightly different:
+\begin{align*}
+\alpha_{(R, R'), (S, S'), (T, T')} &:= \iota(\alpha_{R,S,T}, \alpha_{T',S',R'}^{-1}) \\
+\lambda_{(S, S')} &:= \iota(\lambda_{S}, \rho_{S'}^{-1}) \\
+\rho_{(S, S')} &:= \iota(\rho_{S}, \lambda_{S'}^{-1}) \\
+s_{(S, S'), (T, T')} &:= \iota(s_{S, T}, s_{S', T'})
+\end{align*}
+
+The categories are monoidally equivalent via the identity functor $I : (\Optic_\C, \switched, (I, I)) \to (\Optic_\C, \otimes, (I, I))$, where the structure isomorphisms are given by
+\begin{align*}
+\iota(\id_{S \otimes S'}, s_{T, T'}) : I(S, S') \otimes I(T, T') \to I((S, S') \switched (T, T'))
+\end{align*}
+
+\end{proof}
+
+\begin{remark}
+Just as in the unswitched case, if $\C$ is a strict monoidal category than so is $(\Optic_\C, \switched, (I, I))$.
+\end{remark}
+
+\begin{definition}[Compare {\cite[Definition 5.1]{CoherenceForLenses}}]
 A \emph{teleological category is} a symmetric monoidal category $(\C, \otimes, I)$, equipped with:
@@
 &= \left(T' \otimes S', S \otimes T  \right) \\
-&= (T', T) \otimes (S', S) \\
-&= (T, T')^* \otimes (S, S')^*
+&= (T', T) \switched (S', S) \\
+&= (T, T')^* \switched (S, S')^*
 \end{align*}
@@
 \begin{center}
-\includegraphics[width=.4\textwidth]{diagrams/counit-symmetry}
-\end{center}
-Monoidality:
-\begin{center}
-\includegraphics[width=.4\textwidth]{diagrams/counit-monoidal}
-\end{center}
+\input{diagrams/counit-symmetry-left.tikz}
+\qquad \raisebox{1.5cm}{$=$} \qquad 
+\input{diagrams/counit-symmetry-right.tikz}
+\end{center}
+Monoidality: \todo{there is basically nothing to do in the graphical calculus}
 
@@
 \begin{proof}
-We must show that for a symmetric monoidal functor $F : \C \to \D$, the induced functor $\Optic_\C \to \Optic_\D$ is teleological.
-
-\todo{todo}
+We must show that for a symmetric monoidal functor $F : \C \to \D$, the induced functor $F : \Optic_\C \to \Optic_\D$ is teleological.
+
+First, $F$ preserves the dualisable morphisms. If $\iota(f, g) : (S, S') \hto (A, A')$,
+\begin{align*}
+F\iota(f, g) 
+&= F(\langle \lambda_A^{-1} f, g \lambda_{A'} \rangle) \\
+&= \langle \phi^{-1}_{I,A} (F(\lambda_A^{-1} f)), (F(g \lambda_{A'})) \phi_{I,A'}\rangle \\
+&= \langle \phi^{-1}_{I,A} (F\lambda_A^{-1}) (Ff), (Fg)(F \lambda_{A'}) \phi_{I,A'}\rangle \\
+&= \langle (\phi^{-1}_I \otimes FA) \phi^{-1}_{I,A} (F\lambda_A^{-1}) (Ff), (Fg)(F \lambda_{A'}) \phi_{I,A'} (\phi_I \otimes FA) \rangle \\
+&= \langle \lambda_{FA}^{-1} (Ff), (Fg)\lambda_{FA'} \rangle \\
+&= \iota(Ff, Fg)
+\end{align*}
+
+And it also preserves the counits:
+\begin{align*}
+F(\varepsilon_{(S, S')})
+&= F(c_{S \otimes S'}) \\
+&= F(\langle \rho_S^{-1}, \rho_{S'} \rangle) \\
+&= \langle \phi^{-1}_{S,I} (F \rho_S^{-1}), (F \rho_{S'}) \phi_{S',I}\rangle \\
+&= \langle (FS \otimes \phi_I^{-1}) \phi^{-1}_{S,I} (F \rho_S^{-1}), (F \rho_{S'}) \phi_{S',I} (FS \otimes \phi_I)\rangle \\
+&= \langle \rho_{FS}^{-1}, \rho_{FS'} \rangle \\
+&= \varepsilon_{(FS, FS')}
+\end{align*}
+
+\todo{This works fine when $\C$ is not strict}
 \end{proof}
@@
 \begin{align*}
-\langle l, r \rangle = (\varepsilon_{(M, I)} \otimes (A, A'))(j(l) \otimes j(r)^*)
+\langle l, r \rangle = ((A, I) \switched \varepsilon_{(M, I)} \switched (I, A'))(j(s_{M,A}l) \switched j(rs_{A',M})^*)
 \end{align*}
 where $j : \C \to \Optic_\C$ is the functor $j(A) := \iota(A, I)$.
+\todo{The symmetries could have been avoided in the above expression if the Optic category had been defined with the tensor in the opposite order!}
 \end{proposition}
@@
 First note that because $\C$ is strict monoidal, the counit $\varepsilon_{(M, I)} : (M \otimes I, M \otimes I) = (M, M) \hto (I, I)$ is equal to the connector $c_M : (M, M) \hto (I, I)$.
-\todo{todo}
+
+Then, up to strictness of the monoidal unit, we are composing the two optics
+\begin{center}
+\input{diagrams/optic-decomposed-outer.tikz}
+\end{center}
+and
+\begin{center}
+\input{diagrams/optic-decomposed-inner.tikz}
+\end{center}
+so the two pairs of twists cancel, and we are left exactly with the diagram for $\langle l, r \rangle$.
 \end{proof}
@@
 Suppose $\C$ is a strict symmetric monoidal category and $\T$ is a teleological category.
-For all monoidal functors $F : \C \to \T_d$, there exists a teleological functor $K : \Optic_\C \to \T$, unique up to isomorphism, such that $Kj \cong F$.
+For all symmetric monoidal functors $F : \C \to \T_d$, there exists a teleological functor $K : \Optic_\C \to \T$, unique up to isomorphism, such that $Kj \cong F$.
 %$\Optic$ is left adjoint to $(-)_d$, so $\Optic_\C$ is the free teleological category on a category of dualisable morphisms $\C$.
@@
 \begin{align*}
-\langle l, r \rangle = (\varepsilon_{(M, I)} \otimes (A, A'))(j(l) \otimes j(r)^*)
+\langle l, r \rangle = ((A, I) \switched \varepsilon_{(M, I)} \switched (I, A'))(j(s_{M,A}l) \switched j(rs_{M,A'})^*)
 \end{align*}
@@
 \begin{align*}
-K\langle l, r \rangle = (\varepsilon_{FM} \otimes FA \otimes (FA')^*)(Fl \otimes (Fr)^* )
-\end{align*}
-%
-%This is much easier to understand in the diagrammatic language for teleological categories: \todo{todo}
-%
-%We now have to check that this is well defined. \todo{todo}
-
-\todo{incomplete}
+K\langle l, r \rangle = (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F(s_{M,A}l) \otimes (F(rs_{A', M}))^* )
+\end{align*}
+
+We must show that this is well defined. Suppose we have two lenses related by the coend relation:
+\begin{align*}
+\langle (f \otimes A) l, r \rangle = \langle l, r (f \otimes A') \rangle
+\end{align*}
+Then: \todo{do as string diagram}
+\begin{align*}
+K\langle (f \otimes A) l, r \rangle 
+&= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F(s_{M,A}(f \otimes A)l) \otimes (F(rs_{A',M}))^* ) \\
+&= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F((A \otimes f)s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
+%&= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(FA \otimes Ff \otimes FM \otimes FA')(F(s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
+&= (FA \otimes (\varepsilon_{FM} (Ff \otimes FM)) \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
+&= (FA \otimes (\varepsilon_{FN} (FN \otimes (Ff)^*)) \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
+&= (FA \otimes \varepsilon_{FN} \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(rs_{A',M}(A' \otimes f)))^* ) \\
+&= (FA \otimes \varepsilon_{FN} \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(r(f \otimes A')s_{A',N}))^* ) \\
+&= K\langle  l, r (f \otimes A') \rangle 
+\end{align*}
+\todo{functoriality} \todo{monoidal} \todo{preserves dualisable morphisms} \todo{preserves counit}
 \end{proof}
@@
 \end{proposition}
-
-\subsection{Affine Traversals}
 
@@
 
+\subsection{Affine Traversals}
+
+Also folklore are \emph{affine traversals}, which allow access to a target that may or may not be present.
+These are described at \cite{AffineTraversalPost}, and it is hypothesised that they correspond to pairs of maps $\C(S, A \sqcup S') \times \C(S\times A', S')$.
+This is not precisely correct, but very close:
+
+Suppose $\C$ is cartesian closed, and has binary coproducts. Then let $\mathsf{Aff}$ be the category $\C \times \C$, equipped with the monoidal structure
+\begin{align*}
+(P', Q') \otimes (P, Q) &= (P' \sqcup (Q' \times P) , Q' \times Q)
+\end{align*}
+\todo{check $\mathsf{Aff}$ is actually a monoidal category...}
+
+Define a monoidal action $\mathsf{Aff} \to [\C, \C]$ where $(P, Q)$ acts on $A$ by
+\begin{align*}
+(P, Q) \cdot A = P \sqcup (Q \times A)
+\end{align*}
+so that as expected,
+\begin{align*}
+(P', Q') \cdot (P, Q) \cdot A 
+&= (P', Q') \cdot  (P \sqcup (Q \times A)) \\
+&= P' \sqcup (Q' \times (P \sqcup (Q \times A))) \\
+&\cong P' \sqcup (Q' \times P) \sqcup (Q' \times Q \times A) \\
+&= (P' \sqcup (Q' \times P) , Q' \times Q) \cdot A \\
+&= ((P', Q') \otimes (P, Q)) \cdot A
+\end{align*}
+
+\todo{This feels similar to taking some sort of `compositum' of the two actions $\times$ and $\sqcup$, both embed in this category.
+Marco suggests taking the pushout of the projections into the pullback, calculated in the 2-cat of monoidal categories.}
+
+Now the set of optics $(S, S') \hto (A, A')$ is:
+\begin{align*}
+\Optic_{\mathsf{Aff}}((S, S'), (A, A')) 
+&= \int^{M \in \mathsf{Aff}} \C(S, M \cdot A) \times \C(M \cdot A', S') \\
+&\cong \int^{P,Q \in \C} \C(S, (P,Q) \cdot A) \times \C((P,Q) \cdot A', S') \\
+&= \int^{P,Q \in \C} \C(S, P \sqcup (Q \times A)) \times \C(P \sqcup (Q \times A'), S') \\
+&\cong \int^{P,Q \in \C} \C(S, P \sqcup (Q \times A)) \times \C(P,S') \times \C(Q \times A', S') \\
+&\cong \int^{Q \in \C} \C(S, S' \sqcup (Q \times A)) \times \C(Q \times A', S') \\
+&\cong \int^{Q \in \C} \C(S, S' \sqcup (Q \times A)) \times \C(Q, \homC(A', S')) \\
+&\cong \C(S, S' \sqcup (\homC(A', S') \times A))
+\end{align*}
+
+This set includes into $\C(S, A \sqcup S') \times \C(S\times A', S')$, but the two are not equal---in other words---there are fewer affine traversals than expected.
+
+\todo{Give an example of two elements of the set that correspond to the same affine traversal}
+
+\todo{For \emph{lawful} affine traversals, there may not be a difference}
+
+\begin{remark}
+For this argument to work, it is important that the morphisms in $\mathsf{Aff}$ are just those in $\C \times \C$, even though there are likely to be more natural transformations between the corresponding functors $P \sqcup (Q \times -)$ and $P' \sqcup (Q' \times -)$.
+\end{remark}
+
 \subsection{Traversals}
@@
 
-So in the above example, we would take $F = \mathtt{Int} \times -$ and $G$ to be the identity functor.
+So in the above example, we have the product $\times$ acting pointwise on the functor category $\Set \to \Set$.
+Our example \texttt{first} is then an optic $F \hto G$, where $F = (-) \times \mathtt{Int}$ and $G$ is the identity functor.
 
@@
 \todo{What about the pointwise tensor of an entire functor?}
+
+\subsection{Indexed Optics}
+\todo{
+This possibly looks like
+\begin{align*}
+\int^{M \in \M} \C(S, M(IA)) \times \C(M A', S')
+\end{align*}
+with another monoidal action $I$. The $I$ would need to distribute over $M$ in some way. ``Coindexed'' optics seem to have 
+\begin{align*}
+\int^{M \in \M} \C(S, J(MA)) \times \C(M A', S')
+\end{align*}
+which is why they pass information `in the other direction' but still transform covariantly.
+}
 
@@
 
-\section{Indexed Optics}
-\todo{
-This possibly looks like
-\begin{align*}
-\int^{M \in \M} \C(S, M(IA)) \times \C(M A', S')
-\end{align*}
-with another monoidal action $I$. The $I$ would need to distribute over $M$ in some way. ``Coindexed'' optics seem to have 
-\begin{align*}
-\int^{M \in \M} \C(S, J(MA)) \times \C(M A', S')
-\end{align*}
-which is why they pass information `in the other direction' but still transform covariantly.
-}
-
 \section{Merely Well-Behaved Optics}
@@
 \begin{example}
-A minimal example of a prelens that obeys $\fget\fput$ and $\fput\fget$ but not $\fput\fput$ is the following. Let $p : \{A,B,C\} \hto \{X, Y\}$ be the prelens with
+A minimal example of a lens that obeys $\fget\fput$ and $\fput\fget$ but not $\fput\fput$ is the following. Let $p : \{A,B,C\} \hto \{X, Y\}$ be the lens with
 \begin{align*}

### 2018-05-14 paper.tex
check inverses in Setter

@@
 
-\todo{Past work:
-\begin{itemize}
-\item The Haskell lens people: edwardk, shachaf, xplat, roconnor... (TODO: find out who these people are)
-\item The Doubles paper
-\item Bartosz's blog post which was written about the same time I started this. (Only tensor-like optics, no discussion of laws, confusion about enrichment(?))
-\item The profunctor optics paper out of Oxford. (No generality, nothing categorical, no discussion of laws)
-\end{itemize}
-}
-
-\todo{Contributions:
-\begin{itemize}
-\item ...
-\end{itemize}
-}
-
-\todo{Introduction should include:
-\begin{itemize}
-\item Previous attempts to generalise optics
-\item Some remark about how it's hard to isolate exactly what $\Set$-like properties are being used
-\end{itemize}
-}
+%\todo{Past work:
+%\begin{itemize}
+%\item The Haskell lens people: edwardk, shachaf, xplat, roconnor... (TODO: find out who these people are)
+%\item The Doubles paper
+%\item Bartosz's blog post which was written about the same time I started this. (Only tensor-like optics, no discussion of laws, confusion about enrichment(?))
+%\item The profunctor optics paper out of Oxford. (No generality, nothing categorical, no discussion of laws)
+%\end{itemize}
+%}
+%
+%\todo{Contributions:
+%\begin{itemize}
+%\item ...
+%\end{itemize}
+%}
+%
+%\todo{Introduction should include:
+%\begin{itemize}
+%\item Previous attempts to generalise optics
+%\item Some remark about how it's hard to isolate exactly what $\Set$-like properties are being used
+%\end{itemize}
+%}
 A lens from $S$ to $A$ is a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$ that typically obeys three laws (whose names are in diagrammatic order):
@@
 As is standard, we will elide the unit object and unitors in future diagrams unless they are necessary.
-The diagram for the identity becomes simply:
+The diagram for the identity becomes:
 \begin{center}
@@
 \end{align*}
-Where in both cases we have used the naturality of $\lambda$ and coend relations to move $\lambda^{-1}_M$ to the right-hand side of the coend. 
+Where in both cases we have used the naturality of $\lambda$ and coend relations to move $\lambda^{-1}_M$ to the right-hand side of the coend, where it may be cancelled.
 \end{proof}
@@
 \label{prop-optic-functor}
-Collectively this operation defines a \todo{pseudo?}functor \[\Optic : \SymmMonCat \to \SymmMonCat.\]
-\end{proposition}
-\begin{proof}
-\todo{todo}
-\end{proof}
+Collectively this operation defines a \todo{pseudo?}functor \[\Optic : \SymmMonCat \to \SymmMonCat.\] \qed
+\end{proposition}
 
@@
 \end{align*}
-Then: \todo{do as string diagram}
+Then: \todo{maybe do as string diagram}
 \begin{align*}
@@
 \end{proof}
-
-\begin{remark}
-It is unclear whether an argument like this can work in the case $\C$ is \emph{not} strict. There are a number of issues:
-
-\begin{itemize}
-\item Given $f : S \to A$ and $g : A' \to S'$, the optic $j(f) \otimes j(g)^* : (S \otimes I, I \otimes S') \hto (A \otimes I, I \otimes A')$ is not equal to $\iota(f, g)$.
-It is also not in a form that can be composed with the unitors of $\Optic_\C$, as the $I$s are not on the same side in either the domain or codomain.
-\item \todo{wasn't there more?}
-\end{itemize}
-
-One possible workaround: We could extend the category of optics so it contains the image of $\C$ and its duals directly, without needing ghost morphisms $I \to I$ to face the other direction.
-So there are also objects $(S)$, and a morphism $(S) \hto (A)$ is either an $f : S \to A$ or the formal dual of a $g : A \to S$, and a morphism $(S) \hto (A, A')$ is an optic $(S, I) \hto (A, A')$.
-
-There are several cases involved when composing morphisms and tensoring objects, depending on which kinds of objects are involved.
-This is significantly fiddlier, but it should allow a version of Proposition \ref{prop-optic-decompose} to apply to any $\C$.
-\end{remark}
 
@@
 
+\todo{As we get higher up in the hierarchy, the `ad-hoc' laws get closer to being the same as the coend laws}
+
 \subsection{Lenses}
@@
 \begin{definition}[\cite{StrongFunctors}]
-Suppose $(\C, \otimes, I)$ is a monoidal category. A \emph{(left) strength} for an endofunctor $F : \C \to \C$ is a natural transformation
+Suppose $(\C, \otimes, I)$ is a monoidal category.  A \emph{(left) strong functor} is a functor $F : \C \to \C$ equipped with a natural transformation
 \begin{align*}
@@
 \]
-commute.
-A \emph{strong functor} is a functor equipped with a strength.
-A \emph{strong natural transformation} $\tau : (F,\theta) \to (G,\theta')$ is a natural transformation that respects the strength:
+commute. A \emph{strong natural transformation} $\tau : (F,\theta) \to (G,\theta')$ is a natural transformation that respects the strength:
 \[
@@
 
-In what follows, we will exploit the convenient $\lambda$-calculus syntax for morphisms in a cartesian closed category. \todo{ref}
+In what follows, we will exploit the convenient $\lambda$-calculus syntax for morphisms in a cartesian closed category. \todo{ref} \todo{this sudden change in notation is a bit confusing}
 
 \begin{example}
-An example, which we will use immediately, is the functor $FX = C \times \homC(D, X)$ in any cartesian closed category $\C$, and with any pair of objects $C$ and $D$. The strength is given by:
-\begin{align*}
-A \times FB = A \times C \times \homC(D, B) &\to C \times \homC(D, A \times B) = F(A \times B)\\
-(a, c, f) &\mapsto (c, \lambda d. (a, fd))
+An example, which we will use immediately, is the functor $FX = A \times \homC(B, X)$ in any cartesian closed category $\C$, and with any pair of objects $A$ and $B$.
+The strength $s_{C,D}$ is given by:
+\begin{align*}
+C \times FD = C \times A \times \homC(B, D) &\to A \times \homC(B, C \times D) = F(C \times D)\\
+(c, a, f) &\mapsto (a, \lambda d. (c, fd))
 \end{align*}
@@
 \begin{proof}
-Given a $f \in \C(A, FB)$, let $\Phi(f)$ be the natural transformation with components
+We construct the isomorphism $\Phi: C(A, FB) \cong \Strong_\C(\times)(A \times \homC(B, -), F)$ and its inverse $\Psi$.
+Given a $f \in \C(A, FB)$, let $\Phi(f)$ be the natural transformation such that the component at $C$ is the composite 
+\begin{align*}
+A \times \homC(B, C) \to FB \times \homC(B, C) \to F(B \times \homC(B, C)) \to FC
+\end{align*}
+I.e.,
 \begin{align*}
 A \times \homC(B, C) &\to FC \\
-(a, g) &\mapsto F(\lambda x. \lambda h. h x)\theta_{\homC(B, C), B}(fa, g)
+(a, g) &\mapsto F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(g, f a))
 \end{align*}
@@
 
-Conversely, given an $\eta : A \times \homC(B, -) \Rightarrow F$, the component at $B$ is a function $\eta_B : A \times \homC(B, B) \to FB$; we define
-\begin{align*}
-A &\to FB \\
-a &\mapsto \eta_B(a, \lambda b. b)
-\end{align*}
+Conversely, given a strong natural transformation $\eta : A \times \homC(B, -) \Rightarrow F$, the component at $B$ is a function $\eta_B : A \times \homC(B, B) \to FB$; we define $\Psi(\eta) : A \to FB$ by $\Psi(\eta)(a) = \eta_B(a, \id_B)$
+
 %$\Psi(\eta) : A \to FB$ to be $A \xrightarrow{A \times \const_{\id_B}} A \times \homC(B, B) \xrightarrow{\eta_B} FB$.
 
-\todo{out of date:}
-Checking these are inverse:
-\begin{align*}
-\Phi(\Psi(\eta))_C &= \Phi(\eta_B(A\times\const_{\id_B}))_C \\
-&= (F\epsilon) \theta_{\homC(B, C), B} \left( \eta_B(A\times\const_{\id_B}) \times \id_{\homC(B, C)} \right)
-\end{align*}
-\todo{todo, using the strength for $A \times \homC(B, -)$?}
-\end{proof}
-
-This is a generalisation of \cite[Proposition 2.2]{SecondOrderFunctionals}, isolating the properties of $\Set$ that were used.
-
-Now, we can construct setters.
+Now, verifying these are inverse:
+\begin{align*}
+\Phi(\Psi(\eta))_C (a,g)
+&= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(g, \Psi(\eta)(a))) \\
+&= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(g, \eta_B(a, \id_B))) \\
+&= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(\id, \eta_B)(g, (a, \id_B))) \\
+&= F(\lambda x. \lambda h. h x)(\eta_{\homC(B, C) \times B} s_{\homC(B, C), B}(g, a, \id_B)) && \text{($\theta$ is a strong transformation)}\\
+&= F(\lambda x. \lambda h. h x)(\eta_{\homC(B, C) \times B} (a, \lambda d. (g, \id_B d)) ) && \text{(definition of $s$)}\\
+&= F(\lambda x. \lambda h. h x)(\eta_{\homC(B, C) \times B} (a, \lambda d. (g, d)) ) \\
+&= \eta_{C}(\lambda (a, f). (a, \lambda b. \mathsf{fst}(f b)\mathsf{snd}(f b)) (a, \lambda d. (g, d)) && \text{(naturality of $\eta$)}\\
+&= \eta_{C}(a, \lambda b. g b) \\
+&= \eta_{C}(a, g)
+\end{align*}
+And in the other direction:
+\begin{align*}
+\Psi(\Phi(f))(a) 
+&= \Phi(f)_B(a, \id_B) \\
+&= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, B), B}(\id_B, f a))\\
+&= F(\lambda x. \lambda h. h x)(F(\lambda b. (\id_B, b)))\theta_{1, B}(f a) && \text{(naturality of $\theta$)}\\
+&= F(\lambda b. \id_B b)\theta_{1, B}(f a)\\
+&= \theta_{1, B}(f a) && \text{(strength of $\theta$)}\\
+&= f a
+\end{align*}
+\end{proof}
+
+This is a generalisation of \cite[Proposition 2.2]{SecondOrderFunctionals}, isolating the properties of $\Set$ that are used. We can now construct setters:
 
 \begin{definition}
-Supposed $\C$ is cartesian closed, and let $\Strong(\C)$ act on $\C$ by evaluation. The \emph{category of setters} $\Setter_\C$ is the category of lawful optics for this action.
+Supposed $\C$ is cartesian closed and let $\Strong(\C)$ act on $\C$ by evaluation. The \emph{category of setters} $\Setter_\C$ is the category of optics for this action.
 \end{definition}
 
-Due to the above lemma, we can eliminate the coend from this definition:
-\begin{align*}
-\Setter_\C(S, A) &= \int^{F \in \Strong(\C)} \C(S, FA) \times \C(FA, S) \\
-&\cong \int^{F \in \Strong(\C)} \Strong_\C(\times)(S \times \homC(A, -), F)  \times \C(FA, S) \\
-&\cong \C(S \times \homC(A, A), S) \\
-&\cong \C(\homC(A, A), \homC(S,S))
+Due to the above lemma, we can eliminate the coend from the definition:
+\begin{align*}
+\Setter_\C((S, S'), (A, A')) &= \int^{F \in \Strong(\C)} \C(S, FA) \times \C(FA', S') \\
+&\cong \int^{F \in \Strong(\C)} \Strong_\C(\times)(S \times \homC(A, -), F)  \times \C(FA', S') \\
+&\cong \C(S \times \homC(A, A'), S') \\
+&\cong \C(\homC(A, A'), \homC(S,S'))
 \end{align*}
@@
 
-This set includes into $\C(S, A \sqcup S') \times \C(S\times A', S')$, but the two are not equal---in other words---there are fewer affine traversals than expected.
+This set includes into $\C(S, A \sqcup S') \times \C(S\times A', S')$, but the two are not equal. In other words, there are fewer affine traversals than expected.
 
@@
 \begin{remark}
-For this argument to work, it is important that the morphisms in $\mathsf{Aff}$ are just those in $\C \times \C$, even though there are likely to be more natural transformations between the corresponding functors $P \sqcup (Q \times -)$ and $P' \sqcup (Q' \times -)$.
+For this argument to work, it is important that the morphisms in $\mathsf{Aff}$ are just those in $\C \times \C$, even though there are likely to be more natural transformations between the functors $P \sqcup (Q \times -)$ and $P' \sqcup (Q' \times -)$.
 \end{remark}
@@
 \subsection{Traversals}
-\todo{Do it}
+\todo{todo}
 
 \subsection{``Achromatic'' Lenses}
+\todo{http://oleg.fi/gists/posts/2018-03-28-achromatic-lens.html}
 
@@
 \begin{definition}
-There is a category $\Tamb_\C(\M)$ of Tambara modules and natural transformations that respect the extra structure, in the sense that for any $l : P \to Q$, the diagram
+There is a category $\Tamb(\M)$ of Tambara modules and natural transformations that respect the extra structure, in the sense that for any $l : P \to Q$, the diagram
 \[
@@
 This category is monoidal with respect to $\odot$ as given above, and the monoidal unit is given by $I$.
-There is an evident forgetful functor $U : \Tamb_\C(\M) \to \Prof(\C, \C)$ that is strong monoidal.
+There is an evident forgetful functor $U : \Tamb(\M) \to \Prof(\C, \C)$ that is strong monoidal.
 This forgetful functor has both a left and right adjoint; particularly important for us is the left adjoint:
@@
 \begin{definition}
-Let $\Pastro_\M : \Prof(\C, \C) \to \Tamb_\C(\M)$ be the functor \todo{change notation? drop $\C$ if we use the same one the whole time?}
+Let $\Pastro_\M : \Prof(\C, \C) \to \Tamb(\M)$ be the functor:
 \begin{align*}
@@
 \begin{proposition}
-$\Pastro_\M : \Prof(\C, \C) \to \Tamb_\C(\M)$ is left adjoint to $U : \Tamb_\C(\M) \to \Prof(\C, \C)$.
+$\Pastro_\M : \Prof(\C, \C) \to \Tamb(\M)$ is left adjoint to $U : \Tamb(\M) \to \Prof(\C, \C)$.
 \end{proposition}
@@
 
-\begin{proposition}
-The category $\Optic_\M$ is isomorphic to the full subcategory on objects of the form $E_A$ in the Kleisli category for the monad $U \Pastro_\M : \Prof(\C, \C) \to \Prof(\C, \C)$.
-\end{proposition}
-\begin{proof}
-\todo{Is there a point to proving this?}
-\end{proof}
+%\begin{proposition}
+%The category $\Optic_\M$ is isomorphic to the full subcategory on objects of the form $E_A$ in the Kleisli category for the monad $U \Pastro_\M : \Prof(\C, \C) \to \Prof(\C, \C)$.
+%\end{proposition}
+%\begin{proof}
+%\todo{Is there a point to proving this?}
+%\end{proof}
 
 Given a profunctor, or indeed a Tambara module, we can evaluate it at any two objects of $\C$.
-This process is functorial in the choice of Tambara module, giving a functor $(U-)(A,A) : \Tamb_\C(\M) \to \Set$.
+This process is functorial in the choice of Tambara module, giving a functor $(U-)(A,A) : \Tamb(\M) \to \Set$.
 
@@
 \label{lemma-rep}
-The functor $(U-)(A,A) : \Tamb_\C(\M) \to \Set$ is representable: there is a natural isomorphism
-$(U-)(A,A) \cong \Tamb_\C(\M)(\Pastro_\M E_A, -)$
+The functor $(U-)(A,A) : \Tamb(\M) \to \Set$ is representable: there is a natural isomorphism
+$(U-)(A,A) \cong \Tamb(\M)(\Pastro_\M E_A, -)$
 \end{lemma}
@@
 \cong \;&\Prof(E_A, U-) && \text{(natural transformations as ends)} \\
-\cong \;&\Tamb_\C(\M)(\Pastro_\M E_A, -) && \text{(by adjointness)} 
+\cong \;&\Tamb(\M)(\Pastro_\M E_A, -) && \text{(by adjointness)} 
 \end{align*}
@@
 \begin{align*}
-[\Tamb_\C(\M), \Set]((U-)(A,A),(U-)(S,S)) &\cong \Optic_\M(S, A)
+[\Tamb(\M), \Set]((U-)(A,A),(U-)(S,S)) &\cong \Optic_\M(S, A)
 \end{align*}
@@
 \begin{align*}
-&[\Tamb_\C(\M), \Set]((U-)(A,A),(U-)(S,S)) \\
-\cong \;&[\Tamb_\C(\M), \Set](\Tamb_\C(\M)(\Pastro_\M E_A, -), (U-)(S,S))  && \text{(by Lemma \ref{lemma-rep})}\\
+&[\Tamb(\M), \Set]((U-)(A,A),(U-)(S,S)) \\
+\cong \;&[\Tamb(\M), \Set](\Tamb(\M)(\Pastro_\M E_A, -), (U-)(S,S))  && \text{(by Lemma \ref{lemma-rep})}\\
 \cong \;&(U\Pastro_\M E_A)(S,S)  && \text{(by Yoneda)} \\
@@
 
-Therefore the functor $\Tamb_\C(\M)(\Pastro_\M E_A, -)$ is canonically lax monoidal, and so the isomorphic functor $(U-)(A,A)$ is also.
+Therefore the functor $\Tamb(\M)(\Pastro_\M E_A, -)$ is canonically lax monoidal, and so the isomorphic functor $(U-)(A,A)$ is also.
 
@@
 
-\todo{I don't see why the converse should be true in general, but it seems to be true in specific situations:}
+\todo{The converse is true in specific situations:}
 
@@
 
-\todo{
-\section{Degenerate Optics}
-The Haskell lens library has some other `optics' that aren't proper optics, but still integrate nicely with the rest of the ecosystem, e.g.
-Getters, Reviews and Folds.
-I am starting to doubt those fit into this framework though.}
-
-\section{Merely Well-Behaved Optics}
+\todo{Here are some thoughts:}
+\begin{theorem}
+If $t : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal, then $\hat{t} : S \hto A$ is a lawful optic.
+\end{theorem}
+\begin{proof}
+The natural transformation $t$ is characterised by its component at $\Pastro_\M E_A$, so I expect the result to follow from the lax monoidalness of $t$ with $P = Q = \Pastro_\M E_A$.
+
+The triangle diagram gives immediately that $rl = \id_S$. The square diagram says that
+\begin{align*}
+\langle l, lr, r \rangle = \langle l, \id_{MA}, r \rangle
+\end{align*}
+as elements of 
+\begin{align*}
+\int^{M,N\in \M} \C(S, MA) \times \C(MA, NA) \times \C(NA, S)
+\end{align*}
+And the goal is to somehow prove that $\langle lr \rangle = \psi A$ for some $\psi : M \to M$.
+Presumably a proof would work by induction on the chain of coend relations, but I don't see how to make progress.
+\end{proof}
+
+\section{Misc}
+\subsection{Degenerate Optics}
+The Haskell lens library has some other `optics' that aren't really optics, but still integrate nicely with the rest of the ecosystem, e.g. Getters, Reviews and Folds.
+
+Getters $(S, S') \hto (A, A')$ are supposed to correspond to morphisms $S \to A$.
+These cannot fit nicely into the coend formalism, as there is always the function $\mathsf{outside} : \Optic_\M((S, S), (A, A')) \to \C(S, S')$.
+
+There are some ways to jam it in though, in the specific case of $(S, S) \to (A, A')$, if we set $\M$ to be the category of copointed functors $\C \to \C$.
+Here copointed means the slice category $[\C, \C] / \id_\C$.
+
+Then I claim that 
+\begin{align*}
+\int^{F \in \mathsf{Copointed}} \C(S, FA) \times \C(FA, S) \cong \C(S, A) \times \C(S, S)
+\end{align*}
+So that the set of `lawful' getters is exactly $\C(S, A)$.
+
+\subsection{Merely Well-Behaved Optics}
 \todo{
@@
 
-\section{The Challenge of Effectful Optics}
+\subsection{Effectful Optics}
 
@@
 
+\subsection{Optics Into Stacks of Functors and Monad Transformers}
+
 \section{Conclusion}

### 2018-05-19 paper.tex
Commit things before rekerjiggering

@@
 \begin{itemize}
-\item ``$\fput\fget$'': $\fget \; \fput = \pi_2$ as maps $S \times A \to A$, so that any update to $A$ should be \todo{represented faithfully in $S$},
+\item ``$\fput\fget$'': $\fget \; \fput = \pi_2$ as maps $S \times A \to A$, so that any update to $A$ should be represented faithfully in $S$;
 \item ``$\fget\fput$'': $\fput [\id_S, \fget] = \id_S$ as maps $S \to S$, so that if $A$ is not changed then $S$ should not change; and,
@@
 
+The general pattern is, once we choose a particular monoidal action $\M \to [\C, \C]$, we can find an isomorphism between the set of optics $(S, S') \hto (A, A')$ and a set that is easier to describe.
+The goal is then to find necessary and sufficient conditions on this second set for the corresponding element of the coend to be a lawful optic.
+
 \todo{As we get higher up in the hierarchy, the `ad-hoc' laws get closer to being the same as the coend laws}
@@
 
-In favourable conditions, we can upgrade this result to show that the existence of a lens $S \hto A$ implies that $S \cong M \times A$ for some $M$.
+In favourable conditions, we can upgrade this result to show that the existence of a lens $S \hto A$ implies that $S \cong C \times A$ for some $C$.
 This is a generalised from the argument given in \cite[Corollary 13]{AlgebrasAndUpdateStrategies} for $\Set$.
@@
 
+\todo{There may be something generalisable here with ``monoidal factorisation systems''}
+
 \subsection{Non-Cartesian Lenses}
@@
 \end{align*}
-where $\homC(S, A)$ denotes the internal hom. If $\C$ is cartesian, this is of course isomorphic to the pair of maps discussed in the previous section.
+where $\homC(A', S')$ denotes the internal hom. If $\C$ is cartesian, this is of course isomorphic to the pair of maps discussed in the previous section.
 
@@
 \todo{The use of lenses in a type system with linear types seems worth exploring!}
+
+\subsection{``Achromatic'' Lenses}
+\todo{http://oleg.fi/gists/posts/2018-03-28-achromatic-lens.html}
+
+Suppose $\C$ is cartesian closed and has finite coproducts. Then $\C$ acts on itself via $M \cdot A = (M \sqcup 1) \times A$.
+\begin{align*}
+\Optic((S, S'), (A, A')) 
+&= \int^{M \in \C} \C(S, M \cdot A) \times \C(M \cdot A', S') \\
+&= \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C((M \sqcup 1) \times A', S') \\
+&= \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C((M \times A') \sqcup A', S') \\
+&= \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C(M \times A', S') \times \C(A', S') \\
+&= \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C(M, \homC(A', S')) \times \C(A', S') \\
+&= \C(S, (\homC(A', S') \sqcup 1) \times A) \times \C(A', S') \\
+&= \C(S, \homC(A', S') \sqcup 1) \times \C(S, A) \times \C(A', S') \\
+\end{align*}
+
+\todo{Equivalently(?), let $\M$ be the category of pointed sets}
 
@@
 
-\subsection{``Achromatic'' Lenses}
-\todo{http://oleg.fi/gists/posts/2018-03-28-achromatic-lens.html}
-
 \subsection{Polymorphic Optics}
@@
 
+For $p : S \hto A$, let $\tilde{p} : (U-)(A,A) \Rightarrow (U-)(S,S)$ denote the corresponding natural transformation under this isomorphism, and for $t : (U-)(A,A) \Rightarrow (U-)(S,S)$, let $\hat{t} : S \hto A$ be the corresponding optic.
+
 \begin{corollary}
@@
 This is the content of the first two isomorphisms above.
-
+\todo{fix notation in the following}
 Explicitly, let $p_{\Pastro_\M E_A}(\langle \id_A, \id_A, \id_A, \id_A \rangle) = \langle l, \id_A, \id_A, r \rangle$, where $l : S \to M A$ and $r : M A \to S$.
@@
 \begin{proposition}
-If $p : S \hto A$ is a lawful optic then the associated natural transformation $\tilde{p} : (U-)(A,A) \to (U-)(S,S)$ is a lax monoidal.
+If $p : S \hto A$ is a lawful optic then the associated natural transformation $\tilde{p} : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal.
 \end{proposition}

### 2018-05-19 src/Affine.hs
Commit some haskell tests

@@ -1,0 +1,48 @@
+{-# LANGUAGE TupleSections #-}
+import Control.Lens
+import Data.Bifunctor
+import Data.Profunctor
+import Data.Profunctor.Strong
+
+data Kiosk a b s t = Kiosk (s -> Either t a) (s -> b -> t)
+-- (s -> Either t a) (s -> b -> t)
+-- s -> (Either t a, b -> t)
+-- s -> Either (t, b -> t) (a, b -> t)
+
+sellKiosk :: Kiosk a b a b
+sellKiosk = Kiosk Right (\_ -> id)
+
+instance Profunctor (Kiosk u v) where
+    dimap f g (Kiosk getter setter) = Kiosk
+        (\a -> first g $ getter (f a))
+        (\a v -> g (setter (f a) v))
+
+instance Strong (Kiosk u v) where
+    first' (Kiosk getter setter) = Kiosk
+        (\(a, c) -> first (,c) $ getter a)
+        (\(a, c) v -> (setter a v, c))
+
+instance Choice (Kiosk u v) where
+    right' (Kiosk getter setter) = Kiosk
+        (\eca -> assoc (second getter eca))
+        (\eca v -> second (`setter` v) eca)
+      where
+        assoc :: Either a (Either b c) -> Either (Either a b) c
+        assoc (Left a)          = Left (Left a)
+        assoc (Right (Left b))  = Left (Right b)
+        assoc (Right (Right c)) = Right c
+
+data Beh a b s t = Beh (s -> Either t (b -> t, a))
+
+one :: Beh a b s t -> Kiosk a b s t
+one (Beh f) = Kiosk getter setter
+  where getter s = second snd (f s)
+        setter s b = case f s of
+          Left t -> t
+          Right (g, _) -> g b
+
+
+two :: Kiosk a b s t -> Beh a b s t
+two (Kiosk getter setter) = Beh $ \s -> case getter s of
+  Left t -> Left t
+  Right a -> Right ((setter s), a)

### 2018-05-19 src/MonTest.hs

@@ -40,7 +40,6 @@ _1 (Carrier f g) = Carrier (assoc . f) (g . unassoc)
   where assoc   ((x, y), z) = (x, (y, z))
         unassoc (x, (y, z)) = ((x, y), z)
 
-
 -- TODO: This might require a Kleisli strength on m so that we have a
 -- well behaved "preproduct" on the Kleisli category
 

### 2018-05-19 src/Phantom.hs

@@ -1,0 +1,77 @@
+{-# LANGUAGE RankNTypes #-}
+{-# LANGUAGE GADTs #-}
+module Phantom where
+
+import Control.Applicative
+import Data.Functor.Identity
+import Data.Profunctor
+import Data.Coerce
+
+class Functor f => Pointed f where
+  point :: a -> f a
+
+instance Pointed (Either a) where point = Right
+
+class Functor f => Copointed f where
+  copoint :: f a -> a
+
+instance Copointed ((,) a) where copoint = snd
+instance Copointed Identity where copoint = runIdentity
+
+class Profunctor p => StrongPointed p where
+  enpointen :: Pointed f => p a b -> p (f a) (f b)
+
+instance StrongPointed (->) where
+  enpointen = fmap
+
+class Profunctor p => StrongCopointed p where
+  encopointen :: Copointed f => p a b -> p (f a) (f b)
+
+instance StrongCopointed (->) where
+  encopointen = fmap
+
+--------------------------------------------------------------------------------
+
+data Getter r a b = Getter { runGetter :: a -> Const r b }
+
+instance Profunctor (Getter r) where
+  dimap f g (Getter p) = Getter $ fmap g . p . f
+
+instance StrongCopointed (Getter r) where
+  encopointen (Getter p) = Getter $ coerce . p . copoint
+
+(^.) :: s -> (Getter a a a -> Getter a s s) -> a
+s ^. l = getConst $ runGetter (l (Getter Const)) s
+
+--------------------------------------------------------------------------------
+
+data Direct s a where
+  Direct :: Copointed f => (s -> f a) -> (f a -> s) -> Direct s a
+
+toDirect :: (s -> a) -> (s -> s) -> Direct s a
+toDirect f g = Direct (\s -> (g s, f s)) fst
+
+fromDirect :: Direct s a -> (s -> a, s -> s)
+fromDirect (Direct l r) = (copoint . l, r . l)
+
+-- toDirect $ fromDirect (Direct l r)
+-- toDirect (copoint . l, r . l)
+-- Direct (\s -> ((r . l) s, (copoint . l) s)) fst
+-- Direct (\p -> (p, copoint p)) . l) (r . fst)
+-- ...
+
+-- fromDirect $ toDirect f g
+-- fromDirect $ Direct (\s -> (g s, f s)) fst
+-- (copoint . (\s -> (g s, f s)), g)
+-- (f, g)
+
[…]

### 2018-05-19 src/ProfLaws.hs

@@ -1,0 +1,48 @@
+{-# LANGUAGE GADTs #-}
+{-# LANGUAGE RankNTypes #-}
+module ProfLaws where
+
+data HalfGuy s a where
+  HalfGuy :: (s -> (m, a)) -> ((m, a) -> s) -> HalfGuy s a
+
+data BigGuy s a where
+  BigGuy :: (s -> (m, a)) -> ((m, a) -> (n, a)) -> ((n, a) -> s) -> BigGuy s a
+
+flatten :: BigGuy s a -> (s -> a, s -> a -> a, s -> a -> a -> s)
+flatten (BigGuy l c r) = (o, p, q)
+  where o s = snd (l s)
+        p s a = snd (c (fst (l s), a))
+        q s a1 a2 = r (fst (c (fst (l s), a1)), a2)
+
+
+iflatten :: BigGuy s a -> (s -> a, s -> a -> a, s -> a -> a -> s)
+iflatten (BigGuy l c r) = (\s -> snd (l s), \s a -> snd (c (fst (l s), a)), \s a1 a2 -> r (fst (c (fst (l s), a1)), a2))
+
+-- or:
+
+-- For a lens,
+get = undefined
+put = undefined
+-- l = \s' -> (s', get s')
+-- r = \(s', a') -> put s' a'
+-- rl = (\(s', a') -> (put s' a', get (put s' a')))
+
+-- This is <l, id, r>
+-- iflatten (BigGuy (\s' -> (s', get s')) id (\(s', a') -> put s' a'))
+d1 = (\s -> snd ((\s' -> (s', get s')) s),
+      \s a -> snd (id (fst ((\s' -> (s', get s')) s), a)),
+      \s a1 a2 -> (\(s', a') -> put s' a') (fst (id (fst ((\s' -> (s', get s')) s), a1)), a2))
+
+d2 = (\s -> get s,
+      \s a -> a,
+      \s a1 a2 -> put s a2)
+
+-- This is <l, rl, r>
+
+e1 = (\s -> snd ((\s' -> (s', get s')) s),
+      \s a -> snd ((\(s', a') -> (put s' a', get (put s' a'))) (fst ((\s' -> (s', get s')) s), a)),
+      \s a1 a2 -> (\(s', a') -> put s' a') (fst ((\(s', a') -> (put s' a', get (put s' a'))) (fst ((\s' -> (s', get s')) s), a1)), a2))
+
+e2 = (\s -> get s,
[…]

### 2018-06-08 paper.tex
Start reworking examples

@@
 \newcommand{\fmatching}{\textsc{Matching}}
+\newcommand{\funzip}{\textsc{Unzip}}
+
+\newcommand{\inside}{\mathsf{inside}}
+\newcommand{\outside}{\mathsf{outside}}
+\newcommand{\once}{\mathsf{once}}
+\newcommand{\twice}{\mathsf{twice}}
 
@@
 
-%\todo{Past work:
-%\begin{itemize}
-%\item The Haskell lens people: edwardk, shachaf, xplat, roconnor... (TODO: find out who these people are)
-%\item The Doubles paper
-%\item Bartosz's blog post which was written about the same time I started this. (Only tensor-like optics, no discussion of laws, confusion about enrichment(?))
-%\item The profunctor optics paper out of Oxford. (No generality, nothing categorical, no discussion of laws)
-%\end{itemize}
-%}
-%
-%\todo{Contributions:
-%\begin{itemize}
-%\item ...
-%\end{itemize}
-%}
-%
-%\todo{Introduction should include:
-%\begin{itemize}
-%\item Previous attempts to generalise optics
-%\item Some remark about how it's hard to isolate exactly what $\Set$-like properties are being used
-%\end{itemize}
-%}
+\todo{Past work:
+\begin{itemize}
+\item The Haskell lens people: edwardk, shachaf, xplat, roconnor... (TODO: find out who these people are)
+\item The Doubles paper
+\item Bartosz's blog post which was written about the same time I started this. (Only tensor-like optics, no discussion of laws, confusion about enrichment(?))
+\item The profunctor optics paper out of Oxford. (No generality, nothing categorical, no discussion of laws)
+\item Very old Dialectica category stuff
+\end{itemize}
+}
+
+\todo{Contributions:
+\begin{itemize}
+\item A definition of optics general enough to encompass lenses, setters, traversals, and others?
+\item A universal property satisfied by the category of optics in the monoidal case
+\item A satisfying categorical description of lens laws
+\item An attempt to isolate exactly what $\Set$-like properties are being used in various places
+\item A couple of new avenues for generalising optics
+\end{itemize}
+}
+
 A lens from $S$ to $A$ is a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$ that typically obeys three laws (whose names are in diagrammatic order):
@@
 \item ``$\fget\fput$'': $\fput [\id_S, \fget] = \id_S$ as maps $S \to S$, so that if $A$ is not changed then $S$ should not change; and,
-\item ``$\fput\fput$'': $\fput (\fput \times \id_A) = \fput \, \pi_{1, 3}$ as maps $S \times A \times A \to S$, so any update to $A$ completely overwrites previous updates.
+\item ``$\fput\fput$'': $\fput (\fput \times A) = \fput \, \pi_{1, 3}$ as maps $S \times A \times A \to S$, so any update to $A$ completely overwrites previous updates.
 \end{itemize}
@@
 \begin{proposition}
-A monoidal functor $F : \C \to \D$ induces a  functor $\Optic(F) : \Optic_\C \to \Optic_\D$
+\label{prop-change-of-action-monoidal}
+A monoidal functor $F : \C \to \D$ induces a functor $\Optic(F) : \Optic_\C \to \Optic_\D$.
 \end{proposition}
@@
 \begin{definition}
-A \emph{teleological functor} $F : \C \to \D$ is a strong symmetric monoidal functor that restricts to a functor $F_d : \C_d \to \D_d$ on the dualisable subcategories, and such that $F(\varepsilon_X) = \varepsilon_{FX}$ \todo{up to the structure isomorphisms of $F$...}
+A \emph{teleological functor} $F : \C \to \D$ is a symmetric monoidal functor that restricts to a functor $F_d : \C_d \to \D_d$ on the dualisable subcategories, and such that $F(\varepsilon_X) = \varepsilon_{FX}$ \todo{up to the structure isomorphisms of $F$...}
 \end{definition}
@@
 
+\begin{proposition}
+\label{prop-change-of-action}
+Suppose $\C$ and $\D$ are categories acted on by $\M$ and $\mathcal{N}$ respectively.
+If $F : \C \to \D$ is a functor that commutes with the actions, then there is an induced functor $\Optic(F) : \Optic_\M \to \Optic_\N$.
+\end{proposition}
+\begin{proof}
+Analogous to Proposition \ref{prop-change-of-action-monoidal}
+\end{proof}
+
 For the remainder of the paper we work in this slightly more general setting.
@@
 \todo{intro}
+\todo{Here I am using ; to mean composition in diagrammatic order, I need to make a final decision on which to use}
 
@@
 In this section we will focus only on optics of the form $p : (S,S) \hto (A, A)$.
-We therefore abbreviate $\Optic_\M((S, S), (A, A))$ as $\Optic_\M(S, A)$ and $p : (S, S) \hto (A, A)$ as $p : S \hto A$.
+For brevity we will write $\Optic_\M((S, S), (A, A))$ as $\Optic_\M(S, A)$ and $p : (S, S) \hto (A, A)$ as $p : S \hto A$.
 \end{remark}
 
+\todo{In this section I am using semicolon to mean composition in diagrammatic order. Should I also switch the comma in $\langle l, r \rangle$ to be a $\mid$?}
+
 For a fixed $M \in \M$, there is a map $\C(S, M A) \times \C(M A, S) \to \C(S, S)$ given by composition.
-This induces a map $outside : \Optic_\M(S, A) \to \C(S, S)$.
-By composition in the other direction we have a map $\C(S, M A) \times \C(M A, S) \to \C(M A, M A)$.
-Including this object $\C(M A, M A)$ into the coend $\int^{M \in \M} \C(M A, M A)$, we induce a map $inside : \Optic_\M(S, A) \to \int^{M \in \M} \C(M A, M A)$.
+This induces a map $\outside : \Optic_\M(S, A) \to \C(S, S)$, given equationally by $\outside(\langle l, r \rangle) = l ; r$
+
+There are also maps two maps 
+\begin{align*}
+\once, \twice : \Optic_\M(S, A) \to \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S)
+\end{align*}
+defined by 
+\begin{align*}
+\once(\langle l, r \rangle) &= \langle l, \id_{MA}, r \rangle \\
+\twice(\langle l, r \rangle) &= \langle l, r;l, r \rangle
+\end{align*}
+
 \begin{definition}
-An optic $p : S \hto A$ is \emph{lawful} if $outside(p) = \id_S$, and $inside(p) = \langle \phi A \rangle$ for some $\phi : M \to M$ in $\M$.
+An optic $p : S \hto A$ is \emph{lawful} if 
+\begin{align*}
+\outside(p) &= \id_S \\
+\once(p) &= \twice(p)
+\end{align*}
 \end{definition}
 
-\begin{proposition}
-There is an subcategory $\Lawful_\M$ of $\Optic_\M$ given by objects of the form $(X, X)$ and lawful optics between them.
-\end{proposition}
-\begin{proof}
-The identity optic $\iota(\id_X, \id_X)$ is clearly lawful.
-
-Suppose we have two lawful optics $\langle l, r \rangle : R \hto S$ and $\langle l', r' \rangle : S \hto A$, where $l : R \to MS$ and $l' : S \to NA$, and such that $lr = \phi S$ and $l'r' = \psi A$.
-Then the composite $\langle (Ml')l, r (Mr')  \rangle$ is also a lawful optic:
-\begin{align*}
-r (Mr')(Ml')l &= r M(r'l') l = rl = \id_S
+We will see that in all the standard examples of optics, this specialises to the expected laws for that type of optic.
+
+\begin{proposition}
+There is an subcategory $\Lawful_\M$ of $\Optic_\M$ given by objects of the form $(S, S)$ and lawful optics between them.
+\end{proposition}
+\begin{proof}
+The identity optic $\iota(\id_S, \id_S)$ is lawful: 
+\begin{align*}
+\outside(\langle \lambda^{-1}_S, \lambda_{S} \rangle) &= \lambda_{S} \lambda^{-1}_S = \id_S \\
 \intertext{and}
-(Ml')l r (Mr') &= (Ml')(\phi S)(Mr') \\ 
-&= (\phi NA) M(l')M(r') \\ 
-&= (\phi NA) M(l'r') \\
-&= (\phi NA) M(\psi A) \\
-&= \phi(\psi A)
-\end{align*}
-by the naturality of the action of $\M$.
-\end{proof}
+\once(\langle \lambda^{-1}_S, \lambda_{S} \rangle) 
+&= \langle \lambda^{-1}_S, \id_{IA}, \lambda_{S} \rangle \\
+&= \langle \lambda^{-1}_S, \lambda_{S};\lambda^{-1}_S , \lambda_{S} \rangle \\
+&= \twice(\langle \lambda^{-1}_S, \lambda_{S} \rangle)
+\end{align*}
+
+Suppose we have two lawful optics $\langle l, r \rangle : R \hto S$ and $\langle l', r' \rangle : S \hto A$, where $l : R \to MS$ and $l' : S \to NA$.
+We must show that $\langle (Ml')l, r (Mr')  \rangle$ is also a lawful optic.
+The first equation is straightforward:
+\begin{align*}
+\outside(\langle l; (Ml'),(Mr') ; r   \rangle) 
+&= l ; Ml' ; Mr' ; r \\
+&= l ; M(l'r') ; r \\
+&= l ; M\id_{NA} ; r \\
+&= l ; r \\
+&= \id_{MNA}
+\end{align*}
+
+For the second, we must show
+\[ \langle l;(Ml'), (Mr'); r;l;(Ml') , (Mr') ; r  \rangle = \langle l;(Ml'), \id_{MNA} , (Mr') ; r  \rangle. \]
+
+We do this by showing that, in some sense, the expressions in the above equation respect the coend relations defining the codomains of $\once(\langle l, r \rangle)$ and $\once(\langle l', r' \rangle)$.
+
+So consider the generating relation $\langle l;\phi_S, c, r \rangle = \langle l, \phi_S ; c, r \rangle$ in \[\int^{M_1, M_2 \in \M} \C(R, M_1 S) \times \C(M_1 S, M_2 S) \times \C(M_2 S, R).\]
+This implies that 
+\begin{align*}
+\langle l;\phi_S;(Ml'), (Mr'); c ;(Ml') , (Mr') ; r \rangle 
+&= \langle l;(Ml');\phi_{NA}, (Mr'); c ;(Ml') , (Mr') ; r \rangle && \text{(functoriality)} \\
+&= \langle l;(Ml'), \phi_{NA};(Mr'); c ;(Ml') , (Mr') ; r \rangle && \text{(coend relation)} \\
+&= \langle l;(Ml'), (Mr');\phi_{S}; c ;(Ml') , (Mr') ; r \rangle && \text{(functoriality)}
+\end{align*}
+And similarly for the other generating relation, $\langle l, c;\phi_S, r \rangle = \langle l,  c, \phi_S; r \rangle$.
+
+Therefore, the chain of relations proving $\langle l, r;l, r \rangle = \langle l, \id_{MA}, r \rangle$ can be replicated to show
+\begin{align*}
+\langle l;(Ml'), (Mr');r;l;(Ml') , (Mr') ; r \rangle &= \langle l;(Ml'), (Mr');\id_{MA};(Ml') , (Mr') ; r \rangle,
+\end{align*}
+which is equal to $\langle l;(Ml'), M(r'l'), (Mr') ; r \rangle$.
+
+Similarly, a generating relation $\langle l';\psi_A, c', r' \rangle = \langle l', \psi_A ; c', r' \rangle$ in \[\int^{N_1, N_2 \in \M} \C(S, N_1 A) \times \C(N_1 A, N_2 A) \times \C(M_2 A, S)\]
+implies that
+\begin{align*}
+\langle l;M(l';\psi_A), Mc', (Mr') ; r \rangle 
+&= \langle l;Ml';M\psi_A, Mc', (Mr') ; r \rangle \\
+&= \langle l;Ml', M\psi_A ; Mc', (Mr') ; r \rangle \\
+&= \langle l;Ml', M(\psi_A;c'), (Mr') ; r \rangle 
+\end{align*}
+So again we can replicate the chain of relations proving $\langle l', r';l', r' \rangle = \langle l', \id_{MA}, r' \rangle$ to show that
+\[\langle l;(Ml'), M(r'l'), (Mr') ; r \rangle = \langle l;(Ml'), \id_{MNA}, (Mr') ; r \rangle \]
+
+We conclude that composition preserves lawfulness, so $\Lawful_\M$ is indeed a subcategory of $\Optic_\M$.
+
+\todo{There is probably a more conceptual way to do this}
+\end{proof}
+
+The requirement that $\once(p) = \twice(p)$ is mysterious, but there are sufficient conditions that are easier to verify.
+
+\begin{proposition}
+Let $\langle l, r \rangle : S \hto A$ be an optic. If $l;r = \id_S$ and $r;l = \phi A$ for some $\phi : M \to M$ in $\M$, then $\langle l, r \rangle$ is a lawful optic.
+\end{proposition}
+\begin{proof}
+The $\outside(\langle l, r \rangle) = l;r = \id_S$ is exactly the first condition. And for the second, we verify:
+\begin{align*}
+\twice(\langle l, r \rangle) 
+&= \langle l, r;l, r \rangle \\
+&= \langle l, \phi A, r \rangle && \text{($r;l = \phi A$)}\\
+&= \langle l (\phi A), \id_{MA}, r \rangle && \text{(coend relation)} \\
+&= \langle l;r;l, \id_{MA}, r \rangle && \text{($r;l = \phi A$ again)}\\
+&= \langle l, \id_{MA}, r \rangle  && \text{($l;r = \id_S$)}\\
+&= \once(\langle l, r \rangle) 
+\end{align*}
+\end{proof}
+
+\begin{remark}
+Even if $r;l = \phi A$ for some $\phi$, the same is not necessarily true of any other representative of the same optic.
+\end{remark}
+
+Let $\inside : \Optic_\M(S, A) \to \int^{M \in \M} \C(M A, M A)$ be the map induced by $\inside(\langle l, r \rangle) = \langle r ; l \rangle$.
+We might ask that instead of requiring $r;l = \phi A$ exactly, we have $\langle r ; l \rangle = \langle \phi A \rangle$ in $\int^{M \in \M} \C(M A, M A)$2  .
+In fact, this is equivalent:
 
@@
 \label{prop-onthenose}
-If $p : S \to A$ is a lawful optic, then there exists a representative $p = \langle l, r \rangle$ such that $rl = \phi A$ on the nose for some $\phi : M \to M$.
-\end{proposition}
-\begin{proof}
+Suppose $p : S \hto A$ satisfies $\outside(p) = \id_S$ and $\inside(p) = \langle \phi A \rangle$.
+Then there exists a representative $\langle l, r \rangle$ such that $l ; r = \psi A$ on the nose for some (possibly different) $\psi : M \to M$.
+\end{proposition}
+\begin{proof}
+\todo{Go through this proof for formatting again.}
+
 The coend relation in $\int^{M \in \M} \C(M A, M A)$ states that two morphisms $f : M A \to M A$ and $g : N A \to N A$ are identified when there exists a $k : N A \to M A$ and morphism $\phi : M \to N$ such that
@@
 
-In view of this Proposition, whenever we posit a representative $\langle l, r \rangle$ of an lawful optic, we may assume that $lr = \phi A$ on the nose, for some $\phi : M \to M$.
+Finally, lawfulness is preserved by the change-of-action functors of Proposition \ref{prop-change-of-action}.
+
+\begin{proposition}
+If $F : \C \to \D$ is a functor that commutes with the monoidal actions on $\C$ and $\D$, then $\Optic(F) : \Optic_\M \to \Optic_\N$ restricts to a functor $\Lawful_\M \to \Lawful_\N$.
+\end{proposition}
+\begin{proof}
+\todo{this should be in here}
+\end{proof}
 
@@
 
-The general pattern is, once we choose a particular monoidal action $\M \to [\C, \C]$, we can find an isomorphism between the set of optics $(S, S') \hto (A, A')$ and a set that is easier to describe.
-The goal is then to find necessary and sufficient conditions on this second set for the corresponding element of the coend to be a lawful optic.
+The general pattern is as follows.
+Once we choose a particular monoidal action $\M \to [\C, \C]$, we find an isomorphism between the set of optics $(S, S') \hto (A, A')$ and a set $\mathbb{O}((S, S'), (A, A'))$ that is easier to describe.
+Ideally, we then find a similar description $\mathbb{D}(S, A)$ for the set \[ \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S)\] appearing in the definition of a lawful optic.
+We can then ``read off'' what conditions on an element of $\mathbb{O}((S, S), (A, A))$ are needed to ensure that the corresponding element of $\Optic_\M(S, A)$ is lawful.
 
@@
 
-The optics for this action are exactly pairs of $\fget$ and $\fput$ functions.
+The optics for this action correspond exactly to pairs of $\fget$ and $\fput$ functions.
 \begin{align*}
@@
 &\cong \int^{M \in \C} \C(S, M) \times \C(S, A) \times \C(M \times A', S') && \text{(universal property of product)} \\
-&\cong \C(S, A) \times \C(S \times A', S') && \text{(co-Yoneda)}
-\end{align*}
-
-Explicitly this isomorphism states that, given an (unlawful) lens $\langle l, r \rangle : (S, S') \hto (A, A')$, the corresponding $\fget$ and $\fput$ functions are given by $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
-In the other direction, given $\fget$ and $\fput$, the corresponding element in the coend has representative $\langle l, r \rangle$, where $l = [\id_s, \fget]$ and $r = \fput$.
-Note that even if the $\fget$ and $\fput$ correspond to a law-abiding lens, this particular representative will not be an isomorphism.
+&\cong \C(S, A) \times \C(S \times A', S') && \text{(co-Yoneda)} \\
+&=: \mathbb{O}((S, S'), (A, A'))
+\end{align*}
+
+Explicitly this isomorphism states that, given an optic $\langle l, r \rangle : (S, S') \hto (A, A')$, the corresponding element of $\mathbb{O}((S, S'), (A, A'))$ is the pair $(\fget, \fput)$, where $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
+In the other direction, given $(\fget, \fput)$, the corresponding optic has representative $\langle [\id_S, \fget],  \fput \rangle$.
 
@@
 \label{prop-OpticImpliesLensLaws}
-Suppose $\langle l, r \rangle : S \hto A$ is a lawful lens in our sense, i.e.
-that $rl = \id_S$ and $\langle lr \rangle = \langle \phi \times A \rangle$ for some $\phi : M \to M$.
-Then $\fput$ and $\fget$ for this lens obey the three lens laws.
-\end{proposition}
-\begin{proof}
-By Proposition \ref{prop-onthenose}, we may assume that $lr = \phi \times A$.
-
-Let $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$. Verification of the laws is straightforward:
-\begin{align*}
-\fget \; \fput 
-&= \pi_2 l r (\pi_1 l \times A) \\
-&= \pi_2 (t \times A) (\pi_1 l \times A) \\
-&= \pi_2 (t \pi_1 l \times A) \\
-&= \pi_2 \\
-\fput [\id_S, \fget] 
-&= r (\pi_1 l \times A) [\id_S, \pi_2 l] \\
-&= r [\pi_1 l, \pi_2 l] \\
-&= rl \\
-&= \id_S \\
-\fput (\fput \times A) 
-&= r (\pi_1 l \times A) (r (\pi_1 l \times A) \times A) \\
-&= r (\pi_1 l  r (\pi_1 l \times A) \times A) \\
-&= r (\pi_1 (t\pi_1 l \times A) \times A) \\
-&= r (t\pi_1 l \times A) \pi_{1,3} \\
-&= r lr(\pi_1 l \times A) \pi_{1,3} \\
-&= r(\pi_1 l \times A) \pi_{1,3} \\
-&= \fput \, \pi_{1, 3}
-\end{align*}
-\end{proof}
-
-This is well known in the case $lr$ is the identity \cite{IsomorphismLensesPost}, we note here that the weaker condition is sufficient.
-
-\begin{proposition}
-Suppose there exists a map $x : 1 \to A$. Then if $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the three lens laws then the corresponding $p : S \hto A$ is a lawful lens.
-\end{proposition}
-\begin{proof}
-Recall that the corresponding optic $p : S \hto A$ has as a representative $\langle [\id_s, \fget], \fput \rangle$.
-
-Let $\fput_x : S \to S$ be the composite $S \to S \times 1 \xrightarrow{x} S \times A \xrightarrow{\fput} S$. The commutative diagram
-\[
-\begin{tikzcd}
-S \times A \ar[r, "\fput_x \times A "] \ar[d, "lr", swap] & S \times A \ar[d, "\fput_x \times A"] \ar[dl, "lr"] \\
-S \times A \ar[r, "\fput_x \times A", swap] & S \times A
-\end{tikzcd}
-\]
-is a witness that $\langle lr \rangle = \langle \fput_x \times A \rangle$ in $\int^{M \in \M} \C(M A, M A)$.
-\todo{Is there some property of $\times$ used here we can abstract? Having a map $1 \to A$ guarantees that $- \times A$ is faithful, is this the trick?}
-\end{proof}
+A lens $p : S \hto A$ is a lawful lens in our sense, i.e.
+that $\outside(p) = \id_S$ and $\once(p) = \twice(p)$, if and only if the corresponding $\fput$ and $\fget$ for this lens obey the three lens laws.
+\end{proposition}
+\begin{proof}
+We begin by giving
+\[ \int^{M_1, M_2 \in \C} \C(S, M_1 \times A) \times \C(M_1 \times A, M_2 \times A) \times \C(M_2 \times A, S)\]
+the same treatment as $\Optic_\times(S, A)$. By the same sorts of arguments as above \todo{is this worth writing out?}, this is isomorphic to
+\[\mathbb{D}(S, A) := \C(S, A) \times \C(S \times A, A) \times \C(S \times A \times A, S)\]
+with the isomorphism given by 
+\begin{align*}
+\Phi(\langle l, c, r \rangle) = (&\pi_2 l, \\
+&\pi_2 c (\pi_1 l \times A), \\
+&r(\pi_1 c (\pi_1 l \times A) \times A))
+\end{align*}
+Now suppose we are given a lens $(\fget, \fput)$, which in coend form is $\langle [\id_S, \fget],  \fput \rangle$. Evaluating $\outside$ on this gives:
+\begin{align*}
+\outside(\langle [\id_S, \fget],  \fput \rangle) = \fput [\id_S, \fget]
+\end{align*}
+so requiring $\outside(p) = \id_S$ is precisely the $\fget\fput$ law.
+
+We now have to slog through evaluating $\Phi(\once(p))$ and $\Phi(\twice(p))$.
+\begin{alignat*}{3}
+\Phi(\once(\langle [\id_S, \fget],  \fput \rangle)) &= 
+\Phi(&&\langle [\id_S, \fget], \id_{S \times A}, \fput \rangle) \\
+&= (&&\pi_2 [\id_S, \fget], \\
+&&&\pi_2 \id_{S \times A} (\pi_1 [\id_S, \fget] \times A), \\
+&&& \fput (\pi_1 \id_{S \times A} (\pi_1 [\id_S, \fget] \times A) \times A) \quad) \\
+%
+&= (&&\fget, \\
+&&& \pi_2, \\
+&&& \fput \pi_{1,3} \quad) \\
+%%%%
+%%%%
+\Phi(\twice(\langle [\id_S, \fget],  \fput \rangle)) &= 
+\Phi(&&\langle [\id_S, \fget], [\id_S, \fget]\fput, \fput \rangle) \\
+&= (&&\pi_2 [\id_S, \fget], \\
+&&&\pi_2 [\id_S, \fget]\fput (\pi_1 [\id_S, \fget] \times A), \\
+&&& \fput (\pi_1 [\id_S, \fget]\fput (\pi_1 [\id_S, \fget] \times A) \times A)) \quad) \\
+%
+&= (&&\fget, \\
+&&& \fget \; \fput (\id_S \times A), \\
+&&& \fput (\fput (\id_S \times A) \times A) \quad) \\
+%
+&= (&&\fget, \\
+&&& \fget \; \fput, \\
+&&& \fput (\fput \times A) \quad)
+\end{alignat*}
+So $\Phi(\once(p))$ being equal to $\Phi(\twice(p))$ is exactly equivalent to the $\fput\fget$ and $\fput\fput$ laws holding.
+\end{proof}
+
+\todo{This last proposition should probably be deleted now}
 
@@
 
-\subsection{Non-Cartesian Lenses}
-If $\C$ is closed monoidal, we can use a similar trick to eliminate the coend in the definition of an optic:
+\subsection{Linear Lenses}
+\newcommand{\ev}{\mathsf{ev}}
+\newcommand{\coev}{\mathsf{coev}}
+
+If $\C$ is closed monoidal, we can use a similar trick to eliminate the coends.
 
@@
 &\cong \int^{M \in \C} \C(S, M \otimes A) \times \C(M, \homC(A',S')) \\
-&\cong \C(S, \homC(A',S') \otimes A)
+&\cong \C(S, \homC(A',S') \otimes A) \\
+&=: \mathbb{O}((S, S'), (A, A'))
 \end{align*}
@@
 
-\todo{laws?}
-\todo{The use of lenses in a type system with linear types seems worth exploring!}
+For an optic, the corresponding element of $\mathbb{O}((S, S'), (A, A'))$ will be called $\funzip$.
+The above isomorphism sends $\funzip$ to the element $\langle \funzip , \ev_{A', S'} \rangle$, where $\ev_{A', S'} : \homC(A',S') \otimes A' \to S'$ is the evaluation map.
+In the other direction, given $\langle l, r \rangle$ we have $\funzip = (\tilde r \otimes A)l$ where $\tilde r : M \to \homC(A', S')$ denotes the transpose of $r$.
+
+We cannot possibly use the three $\fput$/$\fget$ style lens laws in this setting as we lack projections, but using the same techniques as for cartesian lenses above we can devise some new ones:
+
+\begin{proposition}
+A linear lens $p : S \hto A$ is lawful iff the following two laws for $\funzip$ hold:
+\begin{align*}
+\ev_{A, S} \; \funzip &= \id_S && \textsc{(Rezip)} \\
+(\coev_{\homC(A, S), A} \otimes A)\funzip &= ((\funzip \circ -) \otimes A)\funzip && \textsc{(ZipZip)} 
+\end{align*}
+where \[ \funzip \circ - : \homC(A, S) \to \homC(A, \homC(A, S) \otimes A) \] denotes the internal composition. \todo{I obviously need better names for the laws}
+\end{proposition}
+\begin{proof}
+We have an isomorphism:
+\begin{align*}
+& \int^{M_1, M_2 \in \C} \C(S, M_1 \otimes A) \times \C(M_1 \otimes A, M_2 \otimes A) \times \C(M_2 \otimes A, S) \\
+&\cong \int^{M_1, M_2 \in \C} \C(S, M_1 \otimes A) \times \C(M_1, \homC(A, M_2 \otimes A)) \times \C(M_2, \homC(A, S)) \\
+&\cong \int^{M_1 \in \C} \C(S, M_1 \otimes A) \times \C(M_1, \homC(A, \homC(A, S) \otimes A)) \\
+&\cong \C(S, \homC(A, \homC(A, S) \otimes A) \otimes A)
+\end{align*}
+which evaluated on an element $\langle l, c, r \rangle$ is given by
+\begin{align*}
+\Phi(\langle l, c, r \rangle) &= (\widetilde{(\tilde{r} \otimes A)c} \otimes A)l
+\end{align*}
+Now suppose we are given an optic $p$ with corresponding element of $\mathbb{O}(S, A)$ is $\funzip$.
+Then $\outside(\langle \funzip , \ev_{A, S} \rangle) = \ev_{A, S} \; \funzip$, giving the first law.
+
+Now we evaluate $\Phi(\once(p))$ and $\Phi(\twice(p))$.
+\begin{align*}
+\Phi(\once(\langle \funzip , \ev_{A, S} \rangle)) 
+&= \Phi(\langle \funzip , \id_{\homC(A,S) \otimes A}, \ev_{A, S} \rangle) \\
+&= (\widetilde{(\tilde{\ev_{A, S}} \otimes A)\id_{\homC(A,S) \otimes A}} \otimes A)\funzip \\
+&= (\coev_{\homC(A, S), A} \otimes A)\funzip \\
+\Phi(\twice(\langle \funzip , \ev_{A, S} \rangle)) 
+&= \Phi(\langle \funzip , \funzip \; \ev_{A, S}, \ev_{A, S} \rangle) \\
+&= (\widetilde{(\tilde{\ev_{A, S}} \otimes A)(\funzip \; \ev_{A, S})} \otimes A)\funzip \\
+&= (\widetilde{(\funzip \; \ev_{A, S})} \otimes A)\funzip \\
+&= ((\funzip \circ -) \otimes A)\funzip
+\end{align*}
+\todo{Fix those overtildes}
+So indeed the optic is lawful iff $(\coev_{\homC(A, S), A} \otimes A)\funzip = ((\funzip \circ -) \otimes A)\funzip$.
+\end{proof}
+
+\todo{The use of lenses in a language with linear types seems worth exploring!}
 
@@
 &= \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C((M \sqcup 1) \times A', S') \\
-&= \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C((M \times A') \sqcup A', S') \\
-&= \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C(M \times A', S') \times \C(A', S') \\
-&= \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C(M, \homC(A', S')) \times \C(A', S') \\
-&= \C(S, (\homC(A', S') \sqcup 1) \times A) \times \C(A', S') \\
-&= \C(S, \homC(A', S') \sqcup 1) \times \C(S, A) \times \C(A', S') \\
-\end{align*}
-
-\todo{Equivalently(?), let $\M$ be the category of pointed sets}
+&\cong \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C((M \times A') \sqcup A', S') \\
+&\cong \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C(M \times A', S') \times \C(A', S') \\
+&\cong \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C(M, \homC(A', S')) \times \C(A', S') \\
+&\cong \C(S, (\homC(A', S') \sqcup 1) \times A) \times \C(A', S') \\
+&\cong \C(S, \homC(A', S') \sqcup 1) \times \C(S, A) \times \C(A', S') \\
+\end{align*}
+
+\begin{remark}
+Equivalently, we could let $\M$ be the category of pointed objects of $\C$ and pointed maps between them.
+\end{remark}
+
+\todo{Is it worth working the laws out?}
 
@@
 
-Just as (possibly unlawful) lenses correspond to a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$, (unlawful) prisms correspond to pairs of maps $\freview : A \to S$ and $\fmatching : S \to S \sqcup A$.
+Just as optics for $\times$ correspond to a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$, optics for $\sqcup$ correspond to pairs of maps $\freview : A \to S$ and $\fmatching : S \to S \sqcup A$.
 These names are taken from the Haskell \texttt{lens} library.
@@
 \end{align*}
-So, if we are given a prism $\langle l, r \rangle : (S, S') \hto (A, A')$ then associated $\freview$ and $\fmatching$ morphisms are given by $\freview = r \inr$ and $\fmatching = (r\inl \sqcup A)l$
-
-Restricting to prisms of the form $(S, S) \hto (A, A)$, the laws for prisms are the obvious duals to the lens laws: 
+If we are given a prism $\langle l, r \rangle : (S, S') \hto (A, A')$ then associated $\freview$ and $\fmatching$ morphisms are given by $\freview = r \inr$ and $\fmatching = (r\inl \sqcup A)l$
+
+The laws for prisms are the obvious duals to the lens laws: 
 \begin{align*}
@@
 
-In the \texttt{lens} library documentation the third law is missing, due to the following:
+In the \texttt{lens} library documentation the third law is missing, on account of following:
 
@@
 Identifying $A$ with its image in $S$, the second law implies that if $a\in A \subset S$ then $\fmatching(a) = \inr(a)$ and if $c\in C \subset S$ then $\fmatching(c) = \inl(c)$.
-The third law then follows by checking both cases.
-\end{proof}
-
-The following is then the dual of Proposition \ref{prop-OpticImpliesLensLaws}.
+The third law can then be verified pointwise by checking both cases $a\in A \subset S$ and $c\in C \subset S$ separately.
+\end{proof}
+
+The following is then exactly the dual of Proposition \ref{prop-OpticImpliesLensLaws}.
 \begin{proposition}
@@
 \end{align*}
-where $\star$ denotes the object of $1$.
-\end{proof}
-
-\begin{proposition}
-The category of \emph{lawful} optics for this action is isomorphic to $\Core(\C)$, the subcategory of isomorphisms in $\C$.
-\end{proposition}
-\begin{proof}
-Given any lawful $\langle l, r \rangle : S \hto A$, we know that $rl = \id_S$, and $lr = \phi \cdot A$ where $\phi : \star \to \star$ in $1$.
-But $\phi$ must be $\id_\star$, so $lr = \id_A$, and $r = l^{-1}$.
+where $\star$ denotes the object of $1$. Composition in $\Optic_1((S, S'), (A, A'))$ does indeed correspond to composition in $\C \times \C^\op$.
+\end{proof}
+
+\begin{proposition}
+An iso $\langle l, r \rangle$ is lawful iff (as expected) $l$ and $r$ are mutual inverses.
+\end{proposition}
+\begin{proof}
+\[ \int^{M_1, M_2 \in \M} \C(S, M_1 \otimes A) \times \C(M_1 \otimes A, M_2 \otimes A) \times \C(M_2 \otimes A, S) \]
+specialises in this case to just
+\[ \C(S, A) \times \C(A, A) \times \C(A, S) \]
+The condition $\outside(\langle l, r \rangle) = \id_S$ is the claim that $rl = \id_S$, and $\once(\langle l, r \rangle) = (l, \id_A, r)$ is equal to $\twice(\langle l, r \rangle) = (l, lr, r)$ iff $lr = \id_A$.s
 \end{proof}
@@
 
-To define setters we must first recall the notion of a strong functor.
-
-%\todo{Taken from http://cs.ioc.ee/~tarmo/ssgep15/ssgep-1a.pdf}
+To define setters we must recall the notion of a strong functor.
+
 \begin{definition}[\cite{StrongFunctors}]
@@
 
-Also folklore are \emph{affine traversals}, which allow access to a target that may or may not be present.
-These are described at \cite{AffineTraversalPost}, and it is hypothesised that they correspond to pairs of maps $\C(S, A \sqcup S') \times \C(S\times A', S')$.
+A folklore variant of a prism is the \emph{affine traversal}, which allows access to a target that may or may not be present.
+These are described in \cite{AffineTraversalPost}, and are there hypothesised to correspond to pairs of maps $\C(S, A \sqcup S') \times \C(S\times A', S')$.
 This is not precisely correct, but very close:
@@
 \end{align*}
+
+\begin{remark}
+It is important here that the morphisms in $\mathsf{Aff}$ are only those that arise from pairs of morphisms $P \to P'$ and $Q \to Q'$, although in principle there are other natural transformations between the corresponding functors $(P, Q) \cdot -$ and $(P', Q') \cdot -$.
+\end{remark}
 
@@
 \todo{For \emph{lawful} affine traversals, there may not be a difference}
-
-\begin{remark}
-For this argument to work, it is important that the morphisms in $\mathsf{Aff}$ are just those in $\C \times \C$, even though there are likely to be more natural transformations between the functors $P \sqcup (Q \times -)$ and $P' \sqcup (Q' \times -)$.
-\end{remark}
 
@@
 \subsection{Optics}
+\todo{Figure out the most sensible order to prove these things in}
 
@@
 \end{definition}
-
-%\begin{proposition}
-%The category $\Optic_\M$ is isomorphic to the full subcategory on objects of the form $E_A$ in the Kleisli category for the monad $U \Pastro_\M : \Prof(\C, \C) \to \Prof(\C, \C)$.
-%\end{proposition}
-%\begin{proof}
-%\todo{Is there a point to proving this?}
-%\end{proof}
 
@@
 
-\begin{proposition}
+\begin{proposition}[Profunctor Optics are Optics]
 \label{prop-profunctor-optics-are-optics}
@@
 
+There is yet another isomorphic description of optics: \todo{Reference proof in PS}
+
+\begin{proposition}
+$\Optic_\M(S, A)$ is isomorphic to $\Prof(E_S, U \Phi_\M E_A)$. \todo{Equivalently to $\Tamb(\M)(\Phi_\M E_S, \Phi_\M E_A)$ by adjointness}
+\end{proposition}
+\begin{proof}
+\begin{align*}
+&\Prof(E_S, U \Phi_\M E_A) \\
+\cong\;&\int_{X,Y \in \C} \Set(E_S(X,Y), (U \Phi_\M E_A)(X,Y)) \\
+= \;&\int_{X,Y \in \C} \Set(\C(X,A) \times \C(A,Y), (U \Phi_\M E_A)(X,Y)) \\
+\cong \;& (U \Phi_\M E_A)(S,S) \\
+= \;&\int^{M \in \M} \C(S, MA) \times \C(MA, S) \\
+= \;&\Optic_\M(S, A)
+\end{align*}
+\end{proof}
+
+\todo{This gives one direction for generalising optics: are there other easy to describe comonoid objects in $\Prof$?}
+
 \subsection{Lawful Profunctor Optics}
@@
 
+\begin{theorem}
+An optic $p : S \hto A$ is lawful iff the corresponding natural transformation $E_S \Rightarrow U \Phi_\M E_A$ is a comonoid morphism.
+\end{theorem}
+\begin{proof}
+
+\end{proof}
+
 \begin{lemma}
@@
 Therefore the functor $\Tamb(\M)(\Pastro_\M E_A, -)$ is canonically lax monoidal, and so the isomorphic functor $(U-)(A,A)$ is also.
+
+\todo{Once this is proven, is the remainder of the section for free?}
 
@@
 
-\todo{The converse is true in specific situations:}
-
-\begin{proposition}
-Let $\C = \Set$ and suppose $p : S \hto A$ is a lens such that the associated natural transformation $p : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal. Then $p$ is lawful.
-\end{proposition}
-\begin{proof}
-\todo{Show that it satisfies the getput, putget and putput laws. This strategy works only with $\times$ and in $\Set$.}
-\end{proof}
+%\begin{proposition}
+%Let $\C = \Set$ and suppose $p : S \hto A$ is a lens such that the associated natural transformation $p : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal. Then $p$ is lawful.
+%\end{proposition}
+%\begin{proof}
+%\todo{Show that it satisfies the getput, putget and putput laws. This strategy works only with $\times$ and in $\Set$.}
+%\end{proof}
 
 \todo{Here are some thoughts:}
+The converse is more difficult, and unfortunately requires another fiddly proof by induction on the coend relation.
+The idea is that any profunctor optic is characterised by its component at $\Pastro_\M E_A$, so the result should follow from the commutativity of the square for lax monoidality when $P = Q = \Pastro_\M E_A$.
+
+For the remainder of the section, fix a lax monoidal natural transformation $t : (U-)(A,A) \to (U-)(S,S)$ and suppose $\hat{t} = \langle l, r \rangle$ for $l : S \to MA$ and $r : MA \to S$.
+Commutativity of the triangle implies immediately that $rl = \id_S$.
+
+Unwinding definitions, commutativity of the square states that
+\begin{align*}
+\langle l, lr, r \rangle = \langle l, \id_{MA}, r \rangle
+\end{align*}
+as elements of 
+\begin{align*}
+\int^{M,N\in \M} \C(S, MA) \times \C(MA, NA) \times \C(NA, S)
+\end{align*}
+Our goal is to show that this implies $\langle lr \rangle = \langle \phi A \rangle$ for some $\phi : M \to M$ in $\M$.
+
+\todo{describe the coend relation on this set}
+
+\newcommand{\rightrightsquigarrow}{\mathrel{\substack{\textstyle\rightsquigarrow\\[-0.6ex]
+                      \textstyle\rightsquigarrow}}}
+\newcommand{\leftleftsquigarrow}{\mathrel{\substack{\textstyle\leftsquigarrow\\[-0.6ex]
+                      \textstyle\leftsquigarrow}}}
+
+\begin{align*}
+&\int^{N,M} \C(S, M \times A) \times \C(M \times A, N \times A) \times \C(N \times A, S) \\
+&= \int^{N,M} \C(S, M) \times \C(S, A) \times \C(M \times A, N \times A) \times \C(N \times A, S) \\
+&= \int^{N} \C(S, A) \times \C(S \times A, N \times A) \times \C(N \times A, S) \\
+&= \int^{N} \C(S, A) \times \C(S \times A, N) \times \C(S \times A, A) \times \C(N \times A, S) \\
+&= \C(S, A) \times \C(S \times A, A) \times \C(S \times A \times A, S) \\
+\end{align*}
+Here $\langle l, c, r \rangle$ is sent to $(l \pi_2, (l \pi_1, \id_A) c \pi_2, ((l \pi_1, \id_A) c, \id_A) r)$
+
+\todo{Do this for the linear lens too}
 \begin{theorem}
@@
 \begin{proof}
-The natural transformation $t$ is characterised by its component at $\Pastro_\M E_A$, so I expect the result to follow from the lax monoidalness of $t$ with $P = Q = \Pastro_\M E_A$.
-
-The triangle diagram gives immediately that $rl = \id_S$. The square diagram says that
-\begin{align*}
-\langle l, lr, r \rangle = \langle l, \id_{MA}, r \rangle
-\end{align*}
-as elements of 
-\begin{align*}
-\int^{M,N\in \M} \C(S, MA) \times \C(MA, NA) \times \C(NA, S)
-\end{align*}
-And the goal is to somehow prove that $\langle lr \rangle = \psi A$ for some $\psi : M \to M$.
-Presumably a proof would work by induction on the chain of coend relations, but I don't see how to make progress.
+
 \end{proof}
@@
 Getters $(S, S') \hto (A, A')$ are supposed to correspond to morphisms $S \to A$.
-These cannot fit nicely into the coend formalism, as there is always the function $\mathsf{outside} : \Optic_\M((S, S), (A, A')) \to \C(S, S')$.
+These cannot fit nicely into the coend formalism, as there is always the function $\outside : \Optic_\M((S, S), (A, A')) \to \C(S, S')$.
 
@@
 
+\todo{Go back and fix all the $\langle \rangle$s to use $\mid$.}
+
 \bibliographystyle{alpha}

### 2018-06-08 paper.tex
Long missing proof of adjointness

@@
 
+\todo{Do laws? For \emph{lawful} affine traversals, there may not be a difference}
+
 \todo{Give an example of two elements of the set that correspond to the same affine traversal}
-
-\todo{For \emph{lawful} affine traversals, there may not be a difference}
 
@@
 \end{center}
-then:
+\todo{Why is the spacing strange above?} then:
 \begin{center}
@@
 Let $I = \C(-,{=}) : \C \hto \C$ be the identity profunctor and $\odot$ be profunctor composition, written in diagrammatic order.
-The following section generalises definitions that first appeared in \cite{Doubles}.
+The following section generalises definitions that first appeared in \cite[Section 3]{Doubles} for monoidal categories to the more general case of a monoidal action.
+
 \begin{definition}
@@
 
-Note that the hom profunctor $I := \C(-, =) : \C^\op \times \C \to \Set$ has a canonical Tambara module structure for any $\M$, given by functoriality.
+Note that the identity profunctor $I$ has a canonical Tambara module structure for any $\M$ given by functoriality.
 
@@
 \begin{definition}
-There is a category $\Tamb(\M)$ of Tambara modules and natural transformations that respect the extra structure, in the sense that for any $l : P \to Q$, the diagram
+There is a category $\Tamb(\M)$ of Tambara modules and natural transformations that respect the extra structure, in the sense that for any $l : P \hto Q$, the diagram
 \[
@@
 
-This category is monoidal with respect to $\odot$ as given above, and the monoidal unit is given by $I$.
+This category is monoidal with respect to $\odot$ as given above with monoidal unit $I$.
 There is an evident forgetful functor $U : \Tamb(\M) \to \Prof(\C, \C)$ that is strong monoidal.
-This forgetful functor has both a left and right adjoint; particularly important for us is the left adjoint:
-
-\begin{definition}
+This forgetful functor has both a left and right adjoint; important for us is the left adjoint:
+
+\begin{definition}[{\cite[Section 5]{Doubles}}]
 Let $\Pastro_\M : \Prof(\C, \C) \to \Tamb(\M)$ be the functor:
@@
 \begin{align*}
-\mathrm{Pastro}_\C(\M)(P)(A,B) := \int^{M \in \M} \int^{C,D \in \C} \C(A, MC) \times P(C,D) \times  \C(MD, B)
-\end{align*}
-The module structure $\alpha_{A,B,M} : \Pastro_\M(P)(A,B) \to \Pastro_\M(P)(MA, MB)
-$ is given by map induced by 
-\begin{align*}
-&\int^{C,D \in \C} \C(A, NC) \times P(C,D) \times  \C(ND, B) \\
-\xrightarrow{\text{functoriality}} \quad& \int^{C,D \in \C} \C(MA, MNC) \times P(C,D) \times  \C(MND, MB) \\
+\Pastro_\M(P)(A,B) := \int^{M \in \M} \int^{C,D \in \C} \C(A, MC) \times P(C,D) \times  \C(MD, B)
+\end{align*}
+The module structure $\alpha_{A,B,M} : \Pastro_\M P(A,B) \to \Pastro_\M P (MA, MB)
+$ is induced by the maps
+\begin{align*}
+&\C(A, NC) \times P(C,D) \times  \C(ND, B) \\
+\xrightarrow{\text{functoriality}} \quad& \C(MA, MNC) \times P(C,D) \times  \C(MND, MB) \\
 \xrightarrow{\copr_{MN}} \quad&\int^{N \in \M} \int^{C,D \in \C} \C(MA, NC) \times P(C,D) \times  \C(ND, MB) \\
-= \quad&\Pastro_\M(P)(MA, MB)
-\end{align*}
-for all $N \in \M$.
+= \quad&\Pastro_\M P (MA, MB)
+\end{align*}
+for all $C, D \in \C$ and $N \in \M$. Equationally, this is $\alpha_{A,B,M}(\langle l, p, r \rangle) = \langle Ml, p, Mr \rangle$.
 \end{definition}
@@
 \begin{proof}
-\todo{Could crunch through this manually, may be a neat way to do it using techniques from P/S}
+For any $P \in \Prof(\C, \C)$, there is a map $\eta : P \hto U \Phi_\M P$, given by $\eta(p) = \langle \id_A, p, \id_B \rangle$.
+
+Suppose we have an element $\langle l, p, r \rangle \in \Pastro_\M P(A,B)$. Then one can check that this element is equal to 
+\begin{align*}
+\langle l, p, r \rangle = \Pastro_\M P(l, r) \alpha_{A, B, M} \; \eta(p)
+\end{align*}
+where $\alpha_{A, B, M}$ is the module structure map for $\Pastro_\M P$.
+
+Now suppose $T \in \Tamb(\M)$ is a Tambara module with structure map $\beta$.
+We would like to show that for any map $f : P \hto UT$, there exists a unique $\hat f : \Phi_\M P \hto T$ so that $f$ factors as \[P \xrightarrow{\eta} U \Phi_\M P \xrightarrow{U\hat f} UT \].
+
+The data of such a map $\hat f : \Phi_\M P \hto T$ is a natural transformation between the underlying profunctors.
+For the factorisation property to hold, we must have that $\hat{f}\eta(p) = f(p)$ for any $p \in P(A,B)$, but then the action on the remainder of $\Phi_\M P(A, B)$ is fixed:
+\begin{align*}
+\hat{f}(\langle l, p, r) \rangle &= \hat{f}(\Pastro_\M P(l, r) \alpha_{A, B, M} \; \eta(p)) \\
+&=T(l, r) \; \beta_{A, B, N} \; f(p)
+\end{align*}
+This establishes uniqueness. It remains to show that $\hat{f}$ so defined is actually a Tambara module morphism, but this is easy:
+\begin{align*}
+\hat{f}\alpha_{A,B,N}(\langle l, p, r \rangle)
+&= \hat{f}(\langle Nl, p, Nr \rangle) \\
+&= T(Nl, Nr) \; \beta_{A, B, NM} \; f(p) \\
+&= T(Nl, Nr) \; \beta_{A, B, NM} \; f(p) \\
+&= T(Nl, Nr) \beta_{MA,MB,N} \; \beta_{A, B, M} \; f(p) \\
+&= \beta_{A,B,N} T(l, r) \; \beta_{A, B, M} \; f(p) \\
+&= \beta_{A,B,N} \hat{f} (\langle l, p, r \rangle)
+\end{align*}
 \end{proof}
@@
 \begin{proof}
-This follows abstractly as the left adjoint of a strong monoidal functor \cite{Kelly1974}.
+This follows from abstract nonsense as the left adjoint of a strong monoidal functor \cite{Kelly1974}.
 \end{proof}

### 2018-06-09 paper.tex
Some typos/corrections

@@
 \usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
+\usepackage{minted}
 
@@
 \begin{remark}
-Note that the definition of the $\Optic$ category involves a coend possibly indexed by a large category.
-To be careful, we should only ever discuss $\Optic$ categories where we know that the coend exists by some other means, e.g., by exhibiting an isomorphism with some other set.
+Note that the homsets of $\Optic_\C$ are given by a coend indexed by a possibly large category, so their existence is not guaranteed by the cocompleteness of $\Set$.
+We should be careful to only discuss $\Optic$ categories where we know that the coends exist by some other means, e.g., by exhibiting an isomorphism with some other set.
 For many---but not all---of the examples given later, we provide such an isomorphism.
@@
 This preserves identities, as the identity on an object $(S, S')$ in $\Optic_\M$ is defined to be exactly $\langle \lambda^{-1}_S, \lambda_{S'} \rangle$.
-
-To check functoriality, suppose we have $(f, g) : (S, S') \to (A, A')$ and $(f', g') : (A, A') \to (B, B')$ in $\C \times \C^\op$. Then:
+To check functoriality, suppose we have $(f, g) : (S, S') \to (A, A')$ and $(f', g') : (A, A') \to (B, B')$ in $\C \times \C^\op$.
+Then:
 \begin{align*}
@@
 \begin{proposition}
-$\iota : \C \times \C^\op \to \Optic_\C$ is a strong monoidal functor. 
-\end{proposition}
-\begin{proof}
-\todo{todo}
+$\iota : \C \times \C^\op \to \Optic_\C$ is a monoidal functor. 
+\end{proposition}
+\begin{proof}
+This is clear, as the structure morphisms in $\Optic_\C$ are exactly the structure morphisms in $\C \times \C^\op$ under $\iota$.
 \end{proof}
@@
 
-\begin{proposition}
-\todo{Entrywise Coproduct}
-\end{proposition}
-
-\begin{remark}
-The motivating example here is that of coproducts distributing over the tensor product.
-\end{remark}
+%\begin{proposition}
+%\todo{Entrywise Coproduct}
+%\end{proposition}
+%
+%\begin{remark}
+%The motivating example here is that of coproducts distributing over the tensor product.
+%\end{remark}
 
@@
 \label{prop-optic-functor}
-Collectively this operation defines a \todo{pseudo?}functor \[\Optic : \SymmMonCat \to \SymmMonCat.\] \qed
-\end{proposition}
+Collectively this operation defines a 2-functor \[\Optic : \SymmMonCat \to \SymmMonCat.\] \qed
+\end{proposition}
+\todo{Haven't actually checked natural transformations}
+\todo{Also we run into the large coend issue again, it's probably not well defined on every symm mon cat.}
 
@@
 We assume temporarily that $\C$ is a \emph{strict} symmetric monoidal category.
-It will be convenient to equip $\Optic_\C$ with a slightly different symmetric monoidal structure: \todo{And the universal property given in this section is an argument for this being the ``morally correct'' tensor}
+It will be convenient to equip $\Optic_\C$ with a slightly different symmetric monoidal structure.
+The universal property for $\Optic_\C$ given in this section is an argument for this being the ``morally correct'' tensor, although it does seem a little strange.
 
@@
 
+\begin{remark}
+Jeremy Gibbons notes (originally in the case of ordinary lenses) that the first law is equivalent to requiring that $p$ composed with the connector $c_A$ is equal to the connector $c_S$.
+This is an appealing description from a string diagram standpoint, but I do not know if there is a similar description for the second law.
+\todo{Something to do with embedding $\Optic_\C$ into a compact closed category then using the unit to compose the lenses vertically?
+Should I draw a picture of this?}
+\end{remark}
+
 \begin{proposition}
@@
 Let $\inside : \Optic_\M(S, A) \to \int^{M \in \M} \C(M A, M A)$ be the map induced by $\inside(\langle l, r \rangle) = \langle r ; l \rangle$.
-We might ask that instead of requiring $r;l = \phi A$ exactly, we have $\langle r ; l \rangle = \langle \phi A \rangle$ in $\int^{M \in \M} \C(M A, M A)$2  .
+We might ask that instead of requiring $r;l = \phi A$ exactly, we have $\langle r ; l \rangle = \langle \phi A \rangle$ in $\int^{M \in \M} \C(M A, M A)$.
 In fact, this is equivalent:
@@
 \end{alignat*}
-So $\Phi(\once(p))$ being equal to $\Phi(\twice(p))$ is exactly equivalent to the $\fput\fget$ and $\fput\fput$ laws holding.
+So checking componentwise, $\Phi(\once(p))$ being equal to $\Phi(\twice(p))$ is exactly equivalent to the $\fput\fget$ and $\fput\fput$ laws holding.
 \end{proof}
@@
 \begin{proposition}
-When $\C = \Set$\todo{, and probably more generally,} the third law is implied by the other two.
+When $\C = \Set$, the third law is implied by the other two.
 \end{proposition}
@@
 \[ \C(S, A) \times \C(A, A) \times \C(A, S) \]
-The condition $\outside(\langle l, r \rangle) = \id_S$ is the claim that $rl = \id_S$, and $\once(\langle l, r \rangle) = (l, \id_A, r)$ is equal to $\twice(\langle l, r \rangle) = (l, lr, r)$ iff $lr = \id_A$.s
+The condition $\outside(\langle l, r \rangle) = \id_S$ is the claim that $rl = \id_S$, and $\once(\langle l, r \rangle) = (l, \id_A, r)$ is equal to $\twice(\langle l, r \rangle) = (l, lr, r)$ iff $lr = \id_A$.
 \end{proof}
@@
 As an example, the lens into the first entry of a tuple has type
-\begin{center}
-\texttt{first :: Lens (a, b) (a', b) a a'},
-\end{center}
-\todo{Why is the spacing strange above?} then:
-\begin{center}
-\texttt{set first (1, 5) "hello" == ("hello", 5)}
-\end{center}
+\begin{minted}{haskell}
+first :: Lens (a, b) (a', b) a a'
+\end{minted}
+then:
+\begin{minted}{haskell}
+set first (1, 5) "hello" == ("hello", 5)
+\end{minted}
 Note that the type has been changed from $\texttt{(Int, Int)}$ to $\texttt{(String, Int)}$.
@@
 \subsection{Optics}
-\todo{Figure out the most sensible order to prove these things in}
-
 \begin{definition}
@@
 \end{align*}
-\todo{This works for $\Optic_\M((S, S'), (A, A'))$ just fine, just define $E_{A,A'}$ in the obvious way.}
-
-\todo{Flip the order of the isomorphisms top to bottom?}
-\end{proof}
-
-For $p : S \hto A$, let $\tilde{p} : (U-)(A,A) \Rightarrow (U-)(S,S)$ denote the corresponding natural transformation under this isomorphism, and for $t : (U-)(A,A) \Rightarrow (U-)(S,S)$, let $\hat{t} : S \hto A$ be the corresponding optic.
+\end{proof}
+
+The same proof works in the more general case of $\Optic_\M((S, S'), (A,A'))$, defining $E_{A, A'}$ to be $\C(-, A) \times \C(A', {=})$.
+
+For $p : S \hto A$, let $\tilde{p} : (U-)(A,A) \rightarrow (U-)(S,S)$ denote the corresponding natural transformation under this isomorphism, and for $t : (U-)(A,A) \rightarrow (U-)(S,S)$, let $\hat{t} : S \hto A$ be the corresponding optic.
 
 \begin{corollary}
-A profunctor optic is determined by its component at $\Pastro_\M E_A$, and furthermore, this component is determined by its value on $\langle \id_A, \id_A, \id_A, \id_A \rangle \in (U \Pastro_\M E_A)(A, A)$.
+A profunctor optic $p$ is determined by its component at $\Pastro_\M E_A$, and furthermore, this component is determined by its value on $\langle \id_A, \id_A, \id_A, \id_A \rangle \in (U \Pastro_\M E_A)(A, A)$.
 \end{corollary}
@@
 This is the content of the first two isomorphisms above.
-\todo{fix notation in the following}
-Explicitly, let $p_{\Pastro_\M E_A}(\langle \id_A, \id_A, \id_A, \id_A \rangle) = \langle l, \id_A, \id_A, r \rangle$, where $l : S \to M A$ and $r : M A \to S$.
-Then the component of $p$ at any other Tambara module $P$ is given by
+Explicitly, suppose $\hat{p} = \langle l, r \rangle$ with $l : S \to MA$ and $r : MA \to S$.
+Then for any Tambara module $P$, the component of $p$ at $P$ is
 \begin{align*}
@@
 \end{align*}
-where $\alpha$ is the module structure for $P$.
-\end{proof}
-
-There is yet another isomorphic description of optics: \todo{Reference proof in PS}
-
-\begin{proposition}
-$\Optic_\M(S, A)$ is isomorphic to $\Prof(E_S, U \Phi_\M E_A)$. \todo{Equivalently to $\Tamb(\M)(\Phi_\M E_S, \Phi_\M E_A)$ by adjointness}
+where $\alpha$ is the module structure for $P$. In particular, 
+\[
+p_{\Pastro_\M E_A}(\langle \id_A, \id_A, \id_A, \id_A \rangle) = \langle l, \id_A, \id_A, r \rangle
+\]
+\end{proof}
+
+There is yet another isomorphic description of optics, which may be an unexplored avenue for generalisation.
+
+\begin{proposition}
+$\Optic_\M(S, A)$ is isomorphic to $\Prof(E_S, U \Phi_\M E_A)$.
 \end{proposition}
@@
 
-\todo{This gives one direction for generalising optics: are there other easy to describe comonoid objects in $\Prof$?}
-
 \subsection{Lawful Profunctor Optics}
 
-The next question is: can we characterise the profunctor optics that correspond to lawful optics? The plan is to chase through the above isomorphisms to see where the lawful optics end up.
-
-The exchange profunctor has a canonical comonoid structure. The comultiplication $\Delta : E_A \to E_A \odot E_A$ is given by the composite
-\begin{align*}
-&E_A(X,Y) \\
-= \quad& \C(X, A) \times \C(A, Y) \\
-\xrightarrow{[\pi_1, \const_{\id_A}, \const_{\id_A}, \pi_2]} \quad& \C(X, A) \times \C(A, A) \times \C(A, A) \times \C(A, Y) \\
-\xrightarrow{\copr_A} \quad& \int^{C \in \C} \C(X, A) \times \C(A, C) \times \C(C, A) \times \C(A, Y) \\
-= \quad& \int^{C \in \C} E_A(X,C) \times E_A(C,Y) \\
-= \quad&  (E_A \odot E_A)(X,Y)
-\end{align*}
-and the counit $\varepsilon : E_A \to I$ simply composes the two morphisms. Because $\Pastro_\M$ is oplax monoidal, the Tambara module $\Pastro_\M E_A$ has an induced comonoid structure.
+The next goal is to characterise the profunctor optics that correspond to lawful optics.
+
+The exchange profunctor has a canonical comonoid structure, where the comultiplication $\Delta : E_A \to E_A \odot E_A$ and counit $\varepsilon : E_A(X, Y) \to \C(X, Y)$ are given by
+\begin{align*}
+\Delta((f, g)) &= \langle f, \id_A, \id_A, g \rangle \\
+\varepsilon((f, g)) &= gf
+\end{align*}
+Because $\Pastro_\M$ is oplax monoidal, the profunctor $U\Pastro_\M E_A$ has an induced comonoid structure, given by
+\begin{align*}
+\Delta(\langle l, r \rangle) &= \langle l, lr, r \rangle \\
+\varepsilon(\langle l, r \rangle) &= rl
+\end{align*}
+
+Comparing these definitions with the definition of a lawful optic, we have immediately:
+
+\begin{proposition}
+An optic $p : S \hto A$ is lawful iff the corresponding natural transformation $E_S \rightarrow U \Phi_\M E_A$ is a comonoid morphism. \qed
+\end{proposition}
+
+All that is needed to complete the connection with profunctor optics is the following standard result in category theory.
+
+\begin{lemma}
+For an object $X$ in a monoidal category $(\C, \otimes, I)$, a comonoid structure $(X,\Delta,\varepsilon)$ is equivalent to a lax monoidal structure on $\C(X, -)$.
+Further, comonoid morphisms $(X_1,\Delta_1,\varepsilon_1) \to (X_2,\Delta_2,\varepsilon_2)$ are equivalent to monoidal natural transformations $\C(X, -) \to \C(Y, -)$.
+\end{lemma}
+\begin{proof}
+For a comonoid $(X,\Delta,\varepsilon)$, define a lax monoidal structure 
+\begin{align*}
+\phi &: 1 \to \C(X, I) \\
+\phi_{A, B} &: \C(X, A) \times \C(X, B) \to \C(X, A \otimes B) 
+\end{align*}
+by $\phi = \varepsilon$ and $\phi_{A, B}(f, g) = (f \otimes g) \Delta$.
+
+From such a lax monoidal structure, we recover the comonoid maps by $\varepsilon = \phi$ and $\Delta = \phi_{X, X}(\id_X, \id_X)$.
+
+\todo{check equations, and the rest}
+\end{proof}
 
 \begin{theorem}
-An optic $p : S \hto A$ is lawful iff the corresponding natural transformation $E_S \Rightarrow U \Phi_\M E_A$ is a comonoid morphism.
+$p : S \hto A$ is a lawful optic iff the associated natural transformation $\tilde{p} : (U-)(A,A) \to (U-)(S,S)$ is monoidal with respect to the canonical lax monoidal structures on $(U-)(A,A)$ and $(U-)(S,S)$.
 \end{theorem}
 \begin{proof}
-
-\end{proof}
-
-\begin{lemma}
-For an object $X$ in a monoidal category $\C$, a comonoid structure $(X,\Delta,\varepsilon)$ is equivalent to a lax monoidal structure on $\C(X, -)$.
-\end{lemma}
-\begin{proof}
-\todo{not hard}
-\end{proof}
-
-Therefore the functor $\Tamb(\M)(\Pastro_\M E_A, -)$ is canonically lax monoidal, and so the isomorphic functor $(U-)(A,A)$ is also.
-
-\todo{Once this is proven, is the remainder of the section for free?}
-
-\begin{proposition}
-If $p : S \hto A$ is a lawful optic then the associated natural transformation $\tilde{p} : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal.
-\end{proposition}
-\begin{proof}
-Let $\langle l, r \rangle$ be a representative for $p$ in $\Optic_\M(S,A)$ via the isomorphism of Proposition \ref{prop-profunctor-optics-are-optics}, so that
-\begin{align*}
-\tilde{p}_P = (UP)(l,r) \alpha_{A,A,M}
-\end{align*}
-on each Tambara module $P$.
-
-To show $\tilde{p}$ is monoidal, we must show that both
-\[
-\begin{tikzcd}
-UP(A,A) \times UQ(A,A) \ar[r, "\tilde{p}_P \times \tilde{p}_Q"] \ar[d, swap] & UP(S, S) \times UQ(S, S)  \ar[d] \\
-U(P \odot Q)(A,A)  \ar[r, "\tilde{p}_{P \odot Q}", swap] & U(P \odot Q)(S,S)
-\end{tikzcd}
-\]
-and
-\[
-\begin{tikzcd}
-1 \ar[d] \ar[dr] & \\
-UI(A,A)  \ar[r, "\tilde{p}_I", swap] & UI(S,S)
-\end{tikzcd}
-\]
-commute. For the first we have
-\begin{align*}
-\langle (\tilde{p}_P \times \tilde{p}_Q)(x, y) \rangle &= \langle (UP)(l,r) \alpha_{A,A,M} x,  (UQ)(l,r) \beta_{A,A,M} y\rangle \\
-&= \langle (UP)(l,lr) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(by the coend relations)} \\
-&= \langle (UP)(l,\phi A) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $lr = \phi A$)} \\
-&= \langle (UP)((\phi A)l,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(by the coend relations again)} \\
-&= \langle (UP)(lrl,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $lr = \phi A$ again)} \\
-&= \langle (UP)(l,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $rl = \id_S$)} \\
-&= (U(P \odot Q))(l,r) \langle \alpha_{A,A,M} x, \beta_{A,A,M} y \rangle && \text{(by definition of $P \odot Q$)} \\
-&= (U(P \odot Q))(l,r) (\alpha_{A,A,M} \odot \beta_{A,A,M}) \langle x, y \rangle && \text{(by definition of $\alpha \odot \beta$)} \\
-&= \tilde{p}_{P \odot Q} \langle x, y \rangle
-\end{align*}
-And for the second:
-\begin{align*}
-\tilde{p}_I(\id_A) = (UI)(l,r) (M \id_A) = r \id_{MA} l = rl = \id_S
-\end{align*}
-as required.
-\end{proof}
+$p : S \hto A$ is lawful iff $E_S \rightarrow U \Phi_\M E_A$ is a comonoid morphism, iff $\Phi_\M E_S \rightarrow \Phi_\M E_A$ is a comonoid morphism by adjointness. Now apply the previous lemma.
+\end{proof}
+
+\begin{remark}
+For Haskell's profunctor lenses, these laws take the form:
+\begin{minted}{haskell}
+l :: Tambara m p => p a a -> p s s
+
+l id == id
+l (Procompose p q) == Procompose (l p) (l q)
+\end{minted}
+\end{remark}
 
 %\begin{proposition}
-%Let $\C = \Set$ and suppose $p : S \hto A$ is a lens such that the associated natural transformation $p : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal. Then $p$ is lawful.
+%If $p : S \hto A$ is a lawful optic then the associated natural transformation $\tilde{p} : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal.
 %\end{proposition}
 %\begin{proof}
-%\todo{Show that it satisfies the getput, putget and putput laws. This strategy works only with $\times$ and in $\Set$.}
+%Let $\langle l, r \rangle$ be a representative for $p$ in $\Optic_\M(S,A)$ via the isomorphism of Proposition \ref{prop-profunctor-optics-are-optics}, so that
+%\begin{align*}
+%\tilde{p}_P = (UP)(l,r) \alpha_{A,A,M}
+%\end{align*}
+%on each Tambara module $P$.
+%
+%To show $\tilde{p}$ is monoidal, we must show that both
+%\[
+%\begin{tikzcd}
+%UP(A,A) \times UQ(A,A) \ar[r, "\tilde{p}_P \times \tilde{p}_Q"] \ar[d, swap] & UP(S, S) \times UQ(S, S)  \ar[d] \\
+%U(P \odot Q)(A,A)  \ar[r, "\tilde{p}_{P \odot Q}", swap] & U(P \odot Q)(S,S)
+%\end{tikzcd}
+%\]
+%and
+%\[
+%\begin{tikzcd}
+%1 \ar[d] \ar[dr] & \\
+%UI(A,A)  \ar[r, "\tilde{p}_I", swap] & UI(S,S)
+%\end{tikzcd}
+%\]
+%commute. For the first we have
+%\begin{align*}
+%\langle (\tilde{p}_P \times \tilde{p}_Q)(x, y) \rangle &= \langle (UP)(l,r) \alpha_{A,A,M} x,  (UQ)(l,r) \beta_{A,A,M} y\rangle \\
+%&= \langle (UP)(l,lr) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(by the coend relations)} \\
+%&= \langle (UP)(l,\phi A) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $lr = \phi A$)} \\
+%&= \langle (UP)((\phi A)l,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(by the coend relations again)} \\
+%&= \langle (UP)(lrl,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $lr = \phi A$ again)} \\
+%&= \langle (UP)(l,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $rl = \id_S$)} \\
+%&= (U(P \odot Q))(l,r) \langle \alpha_{A,A,M} x, \beta_{A,A,M} y \rangle && \text{(by definition of $P \odot Q$)} \\
+%&= (U(P \odot Q))(l,r) (\alpha_{A,A,M} \odot \beta_{A,A,M}) \langle x, y \rangle && \text{(by definition of $\alpha \odot \beta$)} \\
+%&= \tilde{p}_{P \odot Q} \langle x, y \rangle
+%\end{align*}
+%And for the second:
+%\begin{align*}
+%\tilde{p}_I(\id_A) = (UI)(l,r) (M \id_A) = r \id_{MA} l = rl = \id_S
+%\end{align*}
+%as required.
 %\end{proof}
-
-\todo{Here are some thoughts:}
-The converse is more difficult, and unfortunately requires another fiddly proof by induction on the coend relation.
+%
+%%\begin{proposition}
+%%Let $\C = \Set$ and suppose $p : S \hto A$ is a lens such that the associated natural transformation $p : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal. Then $p$ is lawful.
+%%\end{proposition}
+%%\begin{proof}
+%%\todo{Show that it satisfies the getput, putget and putput laws. This strategy works only with $\times$ and in $\Set$.}
+%%\end{proof}
+%
+%\todo{Here are some thoughts:}
+%The converse is more difficult, and unfortunately requires another fiddly proof by induction on the coend relation.
 The idea is that any profunctor optic is characterised by its component at $\Pastro_\M E_A$, so the result should follow from the commutativity of the square for lax monoidality when $P = Q = \Pastro_\M E_A$.
-
-For the remainder of the section, fix a lax monoidal natural transformation $t : (U-)(A,A) \to (U-)(S,S)$ and suppose $\hat{t} = \langle l, r \rangle$ for $l : S \to MA$ and $r : MA \to S$.
+%
+%For the remainder of the section, fix a lax monoidal natural transformation $t : (U-)(A,A) \to (U-)(S,S)$ and suppose $\hat{t} = \langle l, r \rangle$ for $l : S \to MA$ and $r : MA \to S$.
 Commutativity of the triangle implies immediately that $rl = \id_S$.
-
-Unwinding definitions, commutativity of the square states that
-\begin{align*}
-\langle l, lr, r \rangle = \langle l, \id_{MA}, r \rangle
-\end{align*}
-as elements of 
-\begin{align*}
-\int^{M,N\in \M} \C(S, MA) \times \C(MA, NA) \times \C(NA, S)
-\end{align*}
-Our goal is to show that this implies $\langle lr \rangle = \langle \phi A \rangle$ for some $\phi : M \to M$ in $\M$.
-
-\todo{describe the coend relation on this set}
-
-\newcommand{\rightrightsquigarrow}{\mathrel{\substack{\textstyle\rightsquigarrow\\[-0.6ex]
-                      \textstyle\rightsquigarrow}}}
-\newcommand{\leftleftsquigarrow}{\mathrel{\substack{\textstyle\leftsquigarrow\\[-0.6ex]
-                      \textstyle\leftsquigarrow}}}
-
-\begin{align*}
-&\int^{N,M} \C(S, M \times A) \times \C(M \times A, N \times A) \times \C(N \times A, S) \\
-&= \int^{N,M} \C(S, M) \times \C(S, A) \times \C(M \times A, N \times A) \times \C(N \times A, S) \\
-&= \int^{N} \C(S, A) \times \C(S \times A, N \times A) \times \C(N \times A, S) \\
-&= \int^{N} \C(S, A) \times \C(S \times A, N) \times \C(S \times A, A) \times \C(N \times A, S) \\
-&= \C(S, A) \times \C(S \times A, A) \times \C(S \times A \times A, S) \\
-\end{align*}
-Here $\langle l, c, r \rangle$ is sent to $(l \pi_2, (l \pi_1, \id_A) c \pi_2, ((l \pi_1, \id_A) c, \id_A) r)$
-
-\todo{Do this for the linear lens too}
-\begin{theorem}
-If $t : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal, then $\hat{t} : S \hto A$ is a lawful optic.
-\end{theorem}
-\begin{proof}
-
-\end{proof}
+%
+%Unwinding definitions, commutativity of the square states that
+%\begin{align*}
+%\langle l, lr, r \rangle = \langle l, \id_{MA}, r \rangle
+%\end{align*}
+%as elements of 
+%\begin{align*}
+%\int^{M,N\in \M} \C(S, MA) \times \C(MA, NA) \times \C(NA, S)
+%\end{align*}
+%Our goal is to show that this implies $\langle lr \rangle = \langle \phi A \rangle$ for some $\phi : M \to M$ in $\M$.
+%
+%\todo{describe the coend relation on this set}
+%
+%\newcommand{\rightrightsquigarrow}{\mathrel{\substack{\textstyle\rightsquigarrow\\[-0.6ex]
+%                      \textstyle\rightsquigarrow}}}
+%\newcommand{\leftleftsquigarrow}{\mathrel{\substack{\textstyle\leftsquigarrow\\[-0.6ex]
+%                      \textstyle\leftsquigarrow}}}
+%
+%\begin{align*}
+%&\int^{N,M} \C(S, M \times A) \times \C(M \times A, N \times A) \times \C(N \times A, S) \\
+%&= \int^{N,M} \C(S, M) \times \C(S, A) \times \C(M \times A, N \times A) \times \C(N \times A, S) \\
+%&= \int^{N} \C(S, A) \times \C(S \times A, N \times A) \times \C(N \times A, S) \\
+%&= \int^{N} \C(S, A) \times \C(S \times A, N) \times \C(S \times A, A) \times \C(N \times A, S) \\
+%&= \C(S, A) \times \C(S \times A, A) \times \C(S \times A \times A, S) \\
+%\end{align*}
+%Here $\langle l, c, r \rangle$ is sent to $(l \pi_2, (l \pi_1, \id_A) c \pi_2, ((l \pi_1, \id_A) c, \id_A) r)$
+%
+%\todo{Do this for the linear lens too}
+%\begin{theorem}
+%If $t : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal, then $\hat{t} : S \hto A$ is a lawful optic.
+%\end{theorem}
+%\begin{proof}
+%
+%\end{proof}
 

### 2018-06-11 paper.tex
More work

@@
 \section{Optics}
+\label{sec-optics}
 
@@
 
+\begin{proposition}
+If $F : \C \to \D$ is a functor that commutes with the monoidal actions on $\C$ and $\D$, then $\Optic(F) : \Optic_\M \to \Optic_\N$ restricts to a functor $\Lawful_\M \to \Lawful_\N$.
+\end{proposition}
+\begin{proof}
+If $p = \langle l, r \rangle$ is lawful, 
+\end{proof}
+
 The requirement that $\once(p) = \twice(p)$ is mysterious, but there are sufficient conditions that are easier to verify.
@@
 Finally, lawfulness is preserved by the change-of-action functors of Proposition \ref{prop-change-of-action}.
-
-\begin{proposition}
-If $F : \C \to \D$ is a functor that commutes with the monoidal actions on $\C$ and $\D$, then $\Optic(F) : \Optic_\M \to \Optic_\N$ restricts to a functor $\Lawful_\M \to \Lawful_\N$.
-\end{proposition}
-\begin{proof}
-\todo{this should be in here}
-\end{proof}
 
@@
 
+\subsection{Monad Transformer Optics}
+
+\todo{todo}
+
+There is also an analogous notion of optics of composites of functors.
+
 \subsection{Indexed Optics}
@@
 \section{Profunctor Optics}
+The Haskell \texttt{lens} library implements optics using what is known as the \emph{profunctor encoding}. Lenses are defined as follows:
+
+\begin{minted}{haskell}
+class Profunctor p => Strong p where
+  second' :: p a b -> p (c, a) (c, b)
+
+type Lens s a = forall p. Strong p => p a a -> p s s
+\end{minted}
+
+The precise connection between this encoding and the previous one was investigated independently in \cite{ProfunctorOpticsPost}.
+In this section, we extend these ideas to the case of a monoidal action and include an analysis of lawful optics in this setting.
 
@@
 \begin{definition}
-Suppose $\C$ is acted on by $(\M, \otimes, I)$ and let $P \in \Prof(\C, \C)$ be a profunctor. A \emph{Tambara module structure for $\M$} on $P$ is a family of maps:
+Suppose a category $\C$ is acted on by $(\M, \otimes, I)$ and let $P \in \Prof(\C, \C)$ be a profunctor. A \emph{Tambara module structure for $\M$} on $P$ is a family of maps:
 \begin{align*}
@@
 This category is monoidal with respect to $\odot$ as given above with monoidal unit $I$.
-There is an evident forgetful functor $U : \Tamb(\M) \to \Prof(\C, \C)$ that is strong monoidal.
-This forgetful functor has both a left and right adjoint; important for us is the left adjoint:
+
+\begin{remark}
+In the code, the \mintinline{haskell}{Strong} typeclass corresponds to supplying the structure map $\alpha$ for a profunctor \texttt{p}.
+Parametricity guarantees a form of (di)naturality for $M$, $A$ and $B$, but as with any definition in Haskell, the equations required of a Tambara module must be checked externally.
+\end{remark}
+
+There is an evident forgetful functor $U : \Tamb(\M) \to \Prof(\C, \C)$ that is strong monoidal. This forgetful functor has both a left and right adjoint; important for us is the left adjoint:
 
@@
 &= T(Nl, Nr) \; \beta_{A, B, NM} \; f(p) \\
-&= T(Nl, Nr) \; \beta_{A, B, NM} \; f(p) \\
 &= T(Nl, Nr) \beta_{MA,MB,N} \; \beta_{A, B, M} \; f(p) \\
@@
 \begin{proof}
-This follows from abstract nonsense as the left adjoint of a strong monoidal functor \cite{Kelly1974}.
+This follows from abstract nonsense as the left adjoint of a strong monoidal functor, see \cite{Kelly1974}.
 \end{proof}
@@
 \end{align*}
-\end{proof}
-
 The same proof works in the more general case of $\Optic_\M((S, S'), (A,A'))$, defining $E_{A, A'}$ to be $\C(-, A) \times \C(A', {=})$.
+\end{proof}
+
+\begin{remark}
+This proposition justifies the profunctor encoding
+\begin{minted}{haskell}
+type Lens s a = forall p. Strong p => p a a -> p s s
+\end{minted}
+using parametricity as a proxy for naturality.
+\end{remark}
 
@@
 
+Free copointed on $F$ is exactly $F \times \id_\C$
+The functor $\mathsf{Copointed} \to [\C, \C]$ has a right adjoint given by $F \mapsto F \times \id_\C$. Copointed map $F \to G \times \id_\C$ is the same as an uncopointed map $F \to G$
+
+For $l, r : \C(S, FA) \times \C(FA, S)$, the map $r$ is equal to
+\[
+FA \xrightarrow{[\id_{FA}, \mathsf{copoint}]} FA \times A \xrightarrow{\pi_1} FA \to S
+\]
+But that first map is the component at $A$ of a copointed natural transformation (the unit of the adjunction). So $l, r$ is equal to
+\begin{align*}
+S \to FA \xrightarrow{[\id_{FA}, \mathsf{copoint}]} FA \times A\\
+FA \times A \xrightarrow{\pi_1} FA \to S
+\end{align*}
+
 \subsection{Merely Well-Behaved Optics}
@@
 
-\subsection{Optics Into Stacks of Functors and Monad Transformers}
-
 \section{Conclusion}

### 2018-06-11 paper.tex
Reindent everything

@@
 \usepackage{authblk}
-%\usepackage[utf8]{inputenc}
+% \usepackage[utf8]{inputenc}
 \usepackage{amsthm}
@@
 \usepackage{mathtools}
-%\usepackage{stmaryrd}
-%\usepackage{tensor}
+% \usepackage{stmaryrd}
+% \usepackage{tensor}
 \usepackage[mathscr]{eucal}
 \usepackage{url}
-%\usepackage{marvosym}
+% \usepackage{marvosym}
 \usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
@@
 \newtheorem{theorem}{Theorem}[subsection]
-%\newtheorem{axiom}[theorem]{Axiom}
+% \newtheorem{axiom}[theorem]{Axiom}
 \newtheorem*{theoremstar}{Theorem}
-%\newtheorem{fact}[theorem]{Fact}
+% \newtheorem{fact}[theorem]{Fact}
 \newtheorem{proposition}[theorem]{Proposition}
@@
 \newtheorem{definition}[theorem]{Definition}
-%\newtheorem{convention}[theorem]{Convention}
-%\newtheorem{construction}[theorem]{Construction}
+% \newtheorem{convention}[theorem]{Convention}
+% \newtheorem{construction}[theorem]{Construction}
 \newtheorem{example}[theorem]{Example}
-%\newtheorem{examples}[theorem]{Examples}
-%\newtheorem{notation}[theorem]{Notation}
+% \newtheorem{examples}[theorem]{Examples}
+% \newtheorem{notation}[theorem]{Notation}
 \newtheorem{remark}[theorem]{Remark}
-%\newtheorem{idea}[theorem]{Idea}
-%\newtheorem{question}[theorem]{Question}
+% \newtheorem{idea}[theorem]{Idea}
+% \newtheorem{question}[theorem]{Question}
 
@@
 \newcommand{\Pastro}{\Phi}
-%\newcommand{\Pastro}{\mathrm{Pastro}}
+% \newcommand{\Pastro}{\mathrm{Pastro}}
 \newcommand{\Double}{\mathcal{D}}
@@
 \newif\ifhideproofs
-%\hideproofstrue %uncomment to hide proofs
+% \hideproofstrue %uncomment to hide proofs
 \ifhideproofs
@@
 
-If $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\langle l, r \rangle : (S, S') \hto (A, A')$ for the image of this pair in $\Optic_\C((S, S'), (A, A'))$, and say that $M$ is the complement for the representative.
+If $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\langle l \mid r \rangle : (S, S') \hto (A, A')$ for the image of this pair in $\Optic_\C((S, S'), (A, A'))$, and say that $M$ is the complement for the representative.
 Optics will always be written with a crossed arrow $\hto$, to distinguish them from morphisms of $\C$.
@@
 \begin{example}
-For any three objects $M, A, A' \in \C$, there is the \emph{tautological} optic \[t_{M,A} : (M \otimes A, M \otimes A') \hto (A, A')\] which is given by $\langle \id_{M \otimes A}, \id_{M \otimes A'} \rangle$.
+  For any three objects $M, A, A' \in \C$, there is the \emph{tautological} optic \[t_{M,A} : (M \otimes A, M \otimes A') \hto (A, A')\] which is given by $\langle \id_{M \otimes A}\mid \id_{M \otimes A'} \rangle$.
 \end{example}
@@
 \begin{remark}
-Elements of $\Optic_\C((S, S'), (A, A'))$ have an appealing interpretation as string diagrams with a ``hole'' missing. We draw the pair $\langle l, r \rangle$ as
+  Elements of $\Optic_\C((S, S'), (A, A'))$ have an appealing
+  interpretation as string diagrams with a ``hole'' missing. We draw the
+  pair $\langle l \mid r \rangle$ as
   \begin{center}
@@
 \end{align*}
-The product in $\Set$ preserves colimits, so in particular coends. Using this fact, and the Fubini theorem for coends \cite[Remark 1.9]{CoendCofriend}, the domain is isomorphic to
+The product in $\Set$ preserves colimits, so in particular coends. Using this fact, and the Fubini theorem for coends~\cite[Remark 1.9]{CoendCofriend}, the domain is isomorphic to
 \begin{align*}
@@
 \begin{proof}
-In \cite[Section 6]{Doubles} this is proven abstractly, by exhibiting this category as the Kleisli category for a monad in the bicategory $\Prof$. Here we prove the properties directly.
+  In~\cite[Section 6]{Doubles} this is proven abstractly, by exhibiting this category as the Kleisli category for a monad in the bicategory $\Prof$. Here we prove the properties directly.
 
@@
     &= \langle (M \otimes ((N \otimes l_3)l_2))l_1, r_1(M \otimes (r_2(N \otimes r_3))) \rangle \\
-&= \langle (M \otimes N \otimes l_3)(M \otimes l_2)l_1, r_1(M \otimes r_2)(M \otimes N \otimes r_3)) \rangle \\
+    &= \langle (M \otimes N \otimes l_3)(M \otimes l_2)l_1, r_1(M \otimes r_2)(M \otimes N \otimes r_3) \rangle \\
     &= \langle l_3, r_3 \rangle \circ (\langle (M \otimes l_2)l_1, r_1(M \otimes r_2) \rangle) \\
@@
 
-The remainder of this section comprises some useful observations that were not made in \cite{Doubles}.
+The remainder of this section comprises some useful observations that were not made in~\cite{Doubles}.
 
@@
 \begin{remark}
-This functor is not necessarily faithful, see Remark \ref{lens-iota-not-faithful}.
+  This functor is not necessarily faithful, see Remark~\ref{lens-iota-not-faithful}.
 \end{remark}
 
-%\todo{This doesn't give us the structure of a `framing', we can only lift vertical arrows to horizontal arrows facing one direction.}
-
-%\begin{theorem}
-%$\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit is $(I, I)$, and the action on morphisms induced by
-%\begin{align*}
-%&\C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(T, N \otimes B) \times \C(N \otimes B', T')\\
-%\to \quad&\C(S \otimes T, M \otimes A \otimes N \otimes B) \times \C(M \otimes A' \otimes N \otimes B', S' \otimes T') && \text{(action of $\otimes$ on morphisms in $\C$)}\\
-%\to \quad&\C(S \otimes T, M \otimes N \otimes A \otimes B) \times \C(M \otimes N \otimes A' \otimes B', S' \otimes T') && \text{($\otimes$ in $\C$ is symmetric)}\\
-%\to \quad&\int^{M \in \C} \C(S \otimes T, M \otimes A \otimes B) \times \C(M \otimes A' \otimes B', S' \otimes T') && \text{(inclusion into coend)}
-%\end{align*}
-%\end{theorem}
-%\begin{proof}
-%Equationally, suppose we have representatives $(l, r) : (S \to M \otimes A, M \otimes A' \to S')$ and $(l', r') : (T \to N \otimes B, N \otimes B' \to T')$. Then:
-%\begin{align*}
-%\langle l, r \rangle \otimes \langle l', r' \rangle &:= \langle (M \otimes s_{A,N} \otimes B)(l \otimes l'), (r \otimes r')(M \otimes s_{A',N} \otimes B') \rangle
-%\end{align*}
-%This is functorial, as suggested by the equivalence of the following string diagrams:
-%\todo{todo}
-%%For future convenience, note that 
-%%\begin{align*}
-%%\langle l, r \rangle \otimes (T, T') &= \langle (M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T') \rangle \\
-%%&= \langle (\lambda^{-1}_M \otimes A \otimes T)(M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T')(\lambda_M \otimes A' \otimes T') \rangle \\
-%%&= \langle l \otimes T, r \otimes T' \rangle
-%%\end{align*}
-%%Now we check functoriality. Suppose we have:
-%%\begin{align*}
-%%\langle l_1, r_1 \rangle : (S_1, S_1') &\hto (S_2, S_2') \\
-%%\langle l_2, r_2 \rangle : (S_2, S_2') &\hto (S_3, S_3') \\
-%%\langle p_1, q_1 \rangle : (T_1, T_1') &\hto (T_2, T_2') \\
-%%\langle p_2, q_2 \rangle : (T_2, T_2') &\hto (T_3, T_3')
-%%\end{align*}
-%%with complements $M_1, M_2, N_1, N_2$ respectively. Then: \todo {(This is a mess. String diagram?)}
-%%\begin{align*}
-%%&(\langle l_2, r_2 \rangle \otimes \langle p_2, q_2 \rangle) \circ (\langle l_1, r_1 \rangle \otimes \langle p_1, q_1 \rangle) \\
-%%= \; &\langle (M_2 \otimes s_{S_3,N_2} \otimes T_3)(l_2 \otimes p_2), (r_2 \otimes q_2)(M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-%%&\circ \langle (M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), (r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2') \rangle \\
-%%= \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes N_1 \otimes l_2 \otimes p_2)(M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), \\
-%%&\;(r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2')(M_1 \otimes N_1 \otimes r_2 \otimes q_2)(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-%%= \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)(M_1 \otimes  l_2 \otimes N_1 \otimes p_2)(l_1 \otimes p_1), \\
-%%&\;(r_1 \otimes q_1)(M_1 \otimes r_2 \otimes N_1 \otimes q_2)(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-%%= \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1), \\
-%%&\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-%%= \; & \text{\todo{(Add a $s_{M_2, N_1}$ to either side of the coend, then appeal to coherence)}} \\
-%%= \; &\langle (M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S_3} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1) ,  \\
-%%&\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S'_3} \otimes T'_3) \rangle \\
-%%= \; &\langle (M_1 \otimes l_2)l_1, r_1(M_1 \otimes r_2) \rangle \otimes \langle (N_1 \otimes p_2)p_1, q_1(N_1 \otimes q_2) \rangle \\
-%%= \; &(\langle l_2, r_2 \rangle  \circ \langle l_1, r_1 \rangle) \otimes (\langle p_2, q_2 \rangle \circ \langle p_1, q_1 \rangle)
-%%\end{align*}
-%
-%The structure morphisms are all lifted from the structure morphisms in $\C$:
-%\begin{align*}
-%\alpha_{(R, R'), (S, S'), (T, T')} &:= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1}) \\
-%\lambda_{(S, S')} &:= \iota(\lambda_{(S, S')}, \lambda_{(S, S')}^{-1}) \\
-%\rho_{(S, S')} &:= (\rho_{(S, S')}, \rho_{(S, S')}^{-1}) \\
-%s_{(S, S'), (T, T')} &:= \iota(s_{S, T}, s_{T', S'})
-%\end{align*}
-% 
-%Note that because $\iota(S, S') = (S, S')$, required equations for $\iota$ to be a monoidal functor hold by definition (although we don't yet know that $\Optic_\otimes$ is monoidal).
+% \todo{This doesn't give us the structure of a `framing', we can only lift vertical arrows to horizontal arrows facing one direction.}
+
+% \begin{theorem}
+%   $\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit is $(I, I)$, and the action on morphisms induced by
+%   \begin{align*}
+      %       &\C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(T, N \otimes B) \times \C(N \otimes B', T')\\
+      %       \to \quad&\C(S \otimes T, M \otimes A \otimes N \otimes B) \times \C(M \otimes A' \otimes N \otimes B', S' \otimes T') && \text{(action of $\otimes$ on morphisms in $\C$)}\\
+      %       \to \quad&\C(S \otimes T, M \otimes N \otimes A \otimes B) \times \C(M \otimes N \otimes A' \otimes B', S' \otimes T') && \text{($\otimes$ in $\C$ is symmetric)}\\
+      %       \to \quad&\int^{M \in \C} \C(S \otimes T, M \otimes A \otimes B) \times \C(M \otimes A' \otimes B', S' \otimes T') && \text{(inclusion into coend)}
+                                                                                                                                    %     \end{align*}
+                                                                                                                                    %                                                                                                                                     \end{theorem}
+                                                                                                                                    %                                                                                                                                     \begin{proof}
+                                                                                                                                    %                                                                                                                                     Equationally, suppose we have representatives $(l, r) : (S \to M \otimes A, M \otimes A' \to S')$ and $(l', r') : (T \to N \otimes B, N \otimes B' \to T')$.
+Then:
+                                                                                                                                    %                                                                                                                                     \begin{align*}
+                                                                                                                                    %                                                                                                                                     \langle l, r \rangle \otimes \langle l', r' \rangle &:= \langle (M \otimes s_{A,N} \otimes B)(l \otimes l'), (r \otimes r')(M \otimes s_{A',N} \otimes B') \rangle
+                                                                                                                                                                                                                                                                                                                                %     \end{align*}
+                                                                                                                                                                                                                                                                                                                                %                                                                                                                                                                                                                                                                                                                                 This is functorial, as suggested by the equivalence of the following string diagrams:
+                                                                                                                                                                                                                                                                                                                                %                                                                                                                                                                                                                                                                                                                                 \todo{todo}
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                 For future convenience, note that
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                 \begin{align*}
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   \langle l, r \rangle \otimes (T, T') &= \langle (M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T') \rangle \\
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   &= \langle (\lambda^{-1}_M \otimes A \otimes T)(M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T')(\lambda_M \otimes A' \otimes T') \rangle \\
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   &= \langle l \otimes T, r \otimes T' \rangle
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                 \end{align*}
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                 Now we check functoriality.
+Suppose we have:
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                 \begin{align*}
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   \langle l_1, r_1 \rangle : (S_1, S_1') &\hto (S_2, S_2') \\
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   \langle l_2, r_2 \rangle : (S_2, S_2') &\hto (S_3, S_3') \\
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   \langle p_1, q_1 \rangle : (T_1, T_1') &\hto (T_2, T_2') \\
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   \langle p_2, q_2 \rangle : (T_2, T_2') &\hto (T_3, T_3')
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                 \end{align*}
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                 with complements $M_1, M_2, N_1, N_2$ respectively.
+Then: \todo {(This is a mess.
+String diagram?)}
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                 \begin{align*}
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   &(\langle l_2, r_2 \rangle \otimes \langle p_2, q_2 \rangle) \circ (\langle l_1, r_1 \rangle \otimes \langle p_1, q_1 \rangle) \\
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   = \; &\langle (M_2 \otimes s_{S_3,N_2} \otimes T_3)(l_2 \otimes p_2), (r_2 \otimes q_2)(M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   &\circ \langle (M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), (r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2') \rangle \\
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   = \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes N_1 \otimes l_2 \otimes p_2)(M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), \\
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   &\;(r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2')(M_1 \otimes N_1 \otimes r_2 \otimes q_2)(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   = \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)(M_1 \otimes  l_2 \otimes N_1 \otimes p_2)(l_1 \otimes p_1), \\
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   &\;(r_1 \otimes q_1)(M_1 \otimes r_2 \otimes N_1 \otimes q_2)(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   = \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1), \\
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   &\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   = \; & \text{\todo{(Add a $s_{M_2, N_1}$ to either side of the coend, then appeal to coherence)}} \\
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   = \; &\langle (M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S_3} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1) ,  \\
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   &\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S'_3} \otimes T'_3) \rangle \\
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   = \; &\langle (M_1 \otimes l_2)l_1, r_1(M_1 \otimes r_2) \rangle \otimes \langle (N_1 \otimes p_2)p_1, q_1(N_1 \otimes q_2) \rangle \\
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                   = \; &(\langle l_2, r_2 \rangle  \circ \langle l_1, r_1 \rangle) \otimes (\langle p_2, q_2 \rangle \circ \langle p_1, q_1 \rangle)
+                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                 \end{align*}
+                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            %
+                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            %                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             The structure morphisms are all lifted from the structure morphisms in $\C$:
+                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            %                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             \begin{align*}
+                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            %                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             \alpha_{(R, R'), (S, S'), (T, T')} &:= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1}) \\
+      %       \lambda_{(S, S')} &:= \iota(\lambda_{(S, S')}, \lambda_{(S, S')}^{-1}) \\
+      %       \rho_{(S, S')} &:= (\rho_{(S, S')}, \rho_{(S, S')}^{-1}) \\
+      %       s_{(S, S'), (T, T')} &:= \iota(s_{S, T}, s_{T', S'})
+                                     %     \end{align*}
+                                     %
+                                     %                                      Note that because $\iota(S, S') = (S, S')$, required equations for $\iota$ to be a monoidal functor hold by definition (although we don't yet know that $\Optic_\otimes$ is monoidal).
 The pentagon and triangle axioms then hold in $\Optic_\otimes$, as they are the image of the same axioms in $\C \times \C^\op$ under $\iota$.
@@
                                      %
-%Let us check that $\alpha_{(R, R'), (S, S'), (T, T')}$ is natural in $(R, R')$. Suppose $f : (Q, Q') \hto (R, R')$ has representative $(l, r) : (Q \to M \otimes R, M \otimes R' \to Q')$, then:
-%\begin{align*}
-%&\alpha_{(R, R'), (S, S'), (T, T')} \circ (f \otimes (S, S')) \otimes (T, T') \\
-%&= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1})  \circ (\langle l, r \rangle \otimes (S, S')) \otimes (T, T') \\
-%&= \langle\lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} \rangle  \circ \left\langle (l \otimes S) \otimes T, (r \otimes S') \otimes T' \right\rangle \\
-%&=\left\langle (M \otimes \lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T})((l \otimes S) \otimes T), ((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} ) \right\rangle \\
-%&=\left\langle (M \otimes \alpha_{R,S,T})((l \otimes S) \otimes T), ((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} )\right\rangle \\
-%&=\left\langle (l \otimes (S \otimes T))\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}(r \otimes (S' \otimes T')) \right\rangle \\
-%&= \langle (I \otimes l \otimes (S \otimes T)) \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}, (I \times r \otimes (S' \otimes T')) \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')}\rangle \\
-%&= \langle l \otimes (S \otimes T), r \otimes (S' \otimes T')\rangle \circ \left\langle \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')} \right\rangle \\
-%&= \langle l, r \rangle \otimes ((S, S') \otimes (T, T')) \circ \iota(\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}) \\
-%&= f \otimes ((S, S') \otimes (T, T')) \circ \alpha_{(Q, Q'), (S, S'), (T, T')} 
-%\end{align*}
-%\todo{There is some cheating going on here, composition actually adds an extra $\alpha$, but that wouldn't get in the way.}
-%\end{proof}
+                                     %                                      Let us check that $\alpha_{(R, R'), (S, S'), (T, T')}$ is natural in $(R, R')$.
+Suppose $f : (Q, Q') \hto (R, R')$ has representative $(l, r) : (Q \to M \otimes R, M \otimes R' \to Q')$, then:
+                                     %                                      \begin{align*}
+                                     %                        &\alpha_{(R, R'), (S, S'), (T, T')} \circ (f \otimes (S, S')) \otimes (T, T') \\
+      %               &= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1})  \circ (\langle l, r \rangle \otimes (S, S')) \otimes (T, T') \\
+      %               &= \langle\lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} \rangle  \circ \left\langle (l \otimes S) \otimes T, (r \otimes S') \otimes T' \right\rangle \\
+      %               &=\left\langle (M \otimes \lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T})((l \otimes S) \otimes T), ((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} ) \right\rangle \\
+      %               &=\left\langle (M \otimes \alpha_{R,S,T})((l \otimes S) \otimes T), ((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} )\right\rangle \\
+      %               &=\left\langle (l \otimes (S \otimes T))\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}(r \otimes (S' \otimes T')) \right\rangle \\
+      %               &= \langle (I \otimes l \otimes (S \otimes T)) \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}, (I \times r \otimes (S' \otimes T')) \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')}\rangle \\
+      %               &= \langle l \otimes (S \otimes T), r \otimes (S' \otimes T')\rangle \circ \left\langle \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')} \right\rangle \\
+      %               &= \langle l, r \rangle \otimes ((S, S') \otimes (T, T')) \circ \iota(\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}) \\
+      %               &= f \otimes ((S, S') \otimes (T, T')) \circ \alpha_{(Q, Q'), (S, S'), (T, T')}
+                        %     \end{align*}
+                        %                         \todo{There is some cheating going on here, composition actually adds an extra $\alpha$, but that wouldn't get in the way.}
+                        %                         \end{proof}
 
@@
   %%%% Note: The following is the above argument written equationally:
-%For future convenience, note that 
-%\begin{align*}
-%\langle l, r \rangle \otimes (T, T') &= \langle (M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T') \rangle \\
-%&= \langle (\lambda^{-1}_M \otimes A \otimes T)(M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T')(\lambda_M \otimes A' \otimes T') \rangle \\
-%&= \langle l \otimes T, r \otimes T' \rangle
-%\end{align*}
-%Now we check functoriality. Suppose we have:
-%\begin{align*}
-%\langle l_1, r_1 \rangle : (S_1, S_1') &\hto (S_2, S_2') \\
-%\langle l_2, r_2 \rangle : (S_2, S_2') &\hto (S_3, S_3') \\
-%\langle p_1, q_1 \rangle : (T_1, T_1') &\hto (T_2, T_2') \\
-%\langle p_2, q_2 \rangle : (T_2, T_2') &\hto (T_3, T_3')
-%\end{align*}
-%with complements $M_1, M_2, N_1, N_2$ respectively. Then: \todo {(This is a mess. String diagram?)}
-%\begin{align*}
-%&(\langle l_2, r_2 \rangle \otimes \langle p_2, q_2 \rangle) \circ (\langle l_1, r_1 \rangle \otimes \langle p_1, q_1 \rangle) \\
-%= \; &\langle (M_2 \otimes s_{S_3,N_2} \otimes T_3)(l_2 \otimes p_2), (r_2 \otimes q_2)(M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-%&\circ \langle (M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), (r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2') \rangle \\
-%= \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes N_1 \otimes l_2 \otimes p_2)(M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), \\
-%&\;(r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2')(M_1 \otimes N_1 \otimes r_2 \otimes q_2)(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-%= \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)(M_1 \otimes  l_2 \otimes N_1 \otimes p_2)(l_1 \otimes p_1), \\
-%&\;(r_1 \otimes q_1)(M_1 \otimes r_2 \otimes N_1 \otimes q_2)(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-%= \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1), \\
-%&\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-%= \; & \text{\todo{(Add a $s_{M_2, N_1}$ to either side of the coend, then appeal to coherence)}} \\
-%= \; &\langle (M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S_3} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1) ,  \\
-%&\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S'_3} \otimes T'_3) \rangle \\
-%= \; &\langle (M_1 \otimes l_2)l_1, r_1(M_1 \otimes r_2) \rangle \otimes \langle (N_1 \otimes p_2)p_1, q_1(N_1 \otimes q_2) \rangle \\
-%= \; &(\langle l_2, r_2 \rangle  \circ \langle l_1, r_1 \rangle) \otimes (\langle p_2, q_2 \rangle \circ \langle p_1, q_1 \rangle)
-%\end{align*}
+                                             %                                              For future convenience, note that
+                                             %                                              \begin{align*}
+                                             %                                              \langle l, r \rangle \otimes (T, T') &= \langle (M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T') \rangle \\
+      %               &= \langle (\lambda^{-1}_M \otimes A \otimes T)(M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T')(\lambda_M \otimes A' \otimes T') \rangle \\
+      %               &= \langle l \otimes T, r \otimes T' \rangle
+                        %     \end{align*}
+                        %                         Now we check functoriality. Suppose we have:
+                        %                         \begin{align*}
+                        %                         \langle l_1, r_1 \rangle : (S_1, S_1') &\hto (S_2, S_2') \\
+      %       \langle l_2, r_2 \rangle : (S_2, S_2') &\hto (S_3, S_3') \\
+      %       \langle p_1, q_1 \rangle : (T_1, T_1') &\hto (T_2, T_2') \\
+      %       \langle p_2, q_2 \rangle : (T_2, T_2') &\hto (T_3, T_3')
+                                                       %     \end{align*}
+                                                       %                                                        with complements $M_1, M_2, N_1, N_2$ respectively.
+Then: \todo {(This is a mess.
+String diagram?)}
+                                                       %                                                        \begin{align*}
+                                                       %                        &(\langle l_2, r_2 \rangle \otimes \langle p_2, q_2 \rangle) \circ (\langle l_1, r_1 \rangle \otimes \langle p_1, q_1 \rangle) \\
+      %       = \; &\langle (M_2 \otimes s_{S_3,N_2} \otimes T_3)(l_2 \otimes p_2), (r_2 \otimes q_2)(M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+      %               &\circ \langle (M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), (r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2') \rangle \\
+      %       = \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes N_1 \otimes l_2 \otimes p_2)(M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), \\
+      %               &\;(r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2')(M_1 \otimes N_1 \otimes r_2 \otimes q_2)(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+      %       = \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)(M_1 \otimes  l_2 \otimes N_1 \otimes p_2)(l_1 \otimes p_1), \\
+      %               &\;(r_1 \otimes q_1)(M_1 \otimes r_2 \otimes N_1 \otimes q_2)(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+      %       = \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1), \\
+      %               &\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+      %       = \; & \text{\todo{(Add a $s_{M_2, N_1}$ to either side of the coend, then appeal to coherence)}} \\
+      %       = \; &\langle (M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S_3} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1) ,  \\
+      %               &\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S'_3} \otimes T'_3) \rangle \\
+      %       = \; &\langle (M_1 \otimes l_2)l_1, r_1(M_1 \otimes r_2) \rangle \otimes \langle (N_1 \otimes p_2)p_1, q_1(N_1 \otimes q_2) \rangle \\
+      %       = \; &(\langle l_2, r_2 \rangle  \circ \langle l_1, r_1 \rangle) \otimes (\langle p_2, q_2 \rangle \circ \langle p_1, q_1 \rangle)
+                     %     \end{align*}
 
@@
 
-%\begin{proposition}
-%Any isomorphism $p : (S, S') \hto (A, A')$ in $\Optic_\C$ is of the form $\iota(f, g)$ for two isomorphisms $S \to A$ and $A' \to S'$ in $\C$.
-%\end{proposition}
-%\begin{proof}
-%\todo{This might not actually be true..}
-%\end{proof}
+      %       \begin{proposition}
+      %       Any isomorphism $p : (S, S') \hto (A, A')$ in $\Optic_\C$ is of the form $\iota(f, g)$ for two isomorphisms $S \to A$ and $A' \to S'$ in $\C$.
+      %       \end{proposition}
+      %       \begin{proof}
+      %       \todo{This might not actually be true..}
+      %       \end{proof}
 
@@
 
-%\begin{proposition}
-%\todo{Entrywise Coproduct}
-%\end{proposition}
-%
-%\begin{remark}
-%The motivating example here is that of coproducts distributing over the tensor product.
-%\end{remark}
-
-\begin{proposition}
-\label{prop-change-of-action-monoidal}
+      %       \begin{proposition}
+      %       \todo{Entrywise Coproduct}
+      %       \end{proposition}
+      %
+      %       \begin{remark}
+      %       The motivating example here is that of coproducts distributing over the tensor product.
+      %       \end{remark}
+
+\begin{proposition}\label{prop-change-of-action-monoidal}
   A monoidal functor $F : \C \to \D$ induces a functor $\Optic(F) : \Optic_\C \to \Optic_\D$.
@@
 
-\begin{proposition}
-\label{prop-optic-functor}
+\begin{proposition}\label{prop-optic-functor}
   Collectively this operation defines a 2-functor \[\Optic : \SymmMonCat \to \SymmMonCat.\] \qed
@@
   \begin{itemize}
-\item A wide symmetric monoidal subcategory $\C_d$ of \emph{dualisable morphisms}, with an involutive strong symmetric monoidal functor $(-)^* : \C_d \to \overline{\C_d^\op}$, where---not finding a standard symbol for such a thing---we mean $\overline{\C_d^\op}$ to be the category with both the direction of the arrows \emph{and} the order of the tensor flipped: $(A \otimes B)^* = B^* \otimes A^*$.
+  \item A wide symmetric monoidal subcategory $\C_d$ of \emph{dualisable morphisms}, with an involutive strong symmetric monoidal functor ${(-)}^* : \C_d \to \overline{\C_d^\op}$, where---not finding a standard symbol for such a thing---we mean $\overline{\C_d^\op}$ to be the category with both the direction of the arrows \emph{and} the order of the tensor flipped: ${(A \otimes B)}^* = B^* \otimes A^*$.
 \todo{Do we want this to be strict?}
@@
 %%%% The following is a version with duality given by reflection.
-%\begin{definition}[{\cite[Definition 5.1]{CoherenceForLenses}}]
-%A \emph{teleological category is} a symmetric monoidal category $(\C, \otimes, I)$, equipped with:
-%\begin{itemize}
-%\item A wide symmetric monoidal subcategory $\C_d$ of \emph{dualisable morphisms}, with an involutive strong symmetric monoidal functor $(-)^* : \C_d \to \C_d^\op$; and,
-%\item A family of morphisms $\varepsilon_X : X \otimes X^* \to I$, called \emph{counits}, natural with respect to the morphisms in $\C_d$, such that
-%\[
-%\begin{tikzcd}
-%X \otimes Y^* \ar[r, "f \otimes Y^*"]  \ar[d, "X \otimes f^*", swap] & Y \otimes Y^* \ar[d, "\varepsilon_Y"] \\
-%X \otimes X^* \ar[r, "\varepsilon_X", swap] & I
-%\end{tikzcd} \hspace{1cm}
-%\begin{tikzcd}
-%X^* \otimes X \ar[r, "s_{X^*, X}"]  \ar[dr, "\varepsilon_{X^*}", swap] & X \otimes X^* \ar[d, "\varepsilon_X"] \\
-%& I
-%\end{tikzcd}
-%\]
-%\[
-%\begin{tikzcd}
-%X \otimes Y \otimes X^* \otimes Y^* \ar[r, "X \otimes s_{Y,X^*} \otimes X^*"]  \ar[dr, "\varepsilon_{X \otimes Y}", swap] & X \otimes X^* \otimes Y \otimes Y^* \ar[d, "\varepsilon_X \otimes \varepsilon_Y"] \\
-%& I
-%\end{tikzcd}
-%\]
-%commute for all $f : X \to Y$ is in $\C_d$.
-%\end{itemize}
-%\end{definition}
-
-%\begin{remark}
-%Compact closed categories very nearly form examples of teleological categories.
+      %       \begin{definition}[{\cite[Definition 5.1]{CoherenceForLenses}}]
+      %       A \emph{teleological category is} a symmetric monoidal category $(\C, \otimes, I)$, equipped with:
+      %       \begin{itemize}
+      %       \item A wide symmetric monoidal subcategory $\C_d$ of \emph{dualisable morphisms}, with an involutive strong symmetric monoidal functor $(-)^* : \C_d \to \C_d^\op$; and,
+      %       \item A family of morphisms $\varepsilon_X : X \otimes X^* \to I$, called \emph{counits}, natural with respect to the morphisms in $\C_d$, such that
+      %       \[
+      %       \begin{tikzcd}
+      %       X \otimes Y^* \ar[r, "f \otimes Y^*"]  \ar[d, "X \otimes f^*", swap] & Y \otimes Y^* \ar[d, "\varepsilon_Y"] \\
+      %       X \otimes X^* \ar[r, "\varepsilon_X", swap] & I
+                                                            %                                                             \end{tikzcd} \hspace{1cm}
+                                                            %                                                             \begin{tikzcd}
+                                                            %                                                             X^* \otimes X \ar[r, "s_{X^*, X}"]  \ar[dr, "\varepsilon_{X^*}", swap] & X \otimes X^* \ar[d, "\varepsilon_X"] \\
+      %               & I
+                        %                         \end{tikzcd}
+                        %                         \]
+                        %                         \[
+                        %                         \begin{tikzcd}
+                        %                         X \otimes Y \otimes X^* \otimes Y^* \ar[r, "X \otimes s_{Y,X^*} \otimes X^*"]  \ar[dr, "\varepsilon_{X \otimes Y}", swap] & X \otimes X^* \otimes Y \otimes Y^* \ar[d, "\varepsilon_X \otimes \varepsilon_Y"] \\
+      %               & I
+                        %                         \end{tikzcd}
+                        %                         \]
+                        %                         commute for all $f : X \to Y$ is in $\C_d$.
+                        %                         \end{itemize}
+                        %                         \end{definition}
+
+                        %                         \begin{remark}
+                        %                         Compact closed categories very nearly form examples of teleological categories.
 In a compact closed category, there are canonical isomorphisms $(X \otimes Y)^* \cong Y^* \otimes X^*$.
@@
 \todo{If $\C$ is strict, as it is here, does this matter?}
-%\end{remark}
+                        %                         \end{remark}
 
@@
 \begin{definition}
-A \emph{teleological functor} $F : \C \to \D$ is a symmetric monoidal functor that restricts to a functor $F_d : \C_d \to \D_d$ on the dualisable subcategories, and such that $F(\varepsilon_X) = \varepsilon_{FX}$ \todo{up to the structure isomorphisms of $F$...}
+  A \emph{teleological functor} $F : \C \to \D$ is a symmetric monoidal functor that restricts to a functor $F_d : \C_d \to \D_d$ on the dualisable subcategories, and such that $F(\varepsilon_X) = \varepsilon_{FX}$ \todo{up to the structure isomorphisms of $F$}
 \end{definition}
@@
 Together we have $\Tele$, the subcategory of $\SymmMonCat$ given by teleological categories and teleological functors.
-There are evident functors $U : \Tele \to \SymmMonCat$ and $(-)_d : \Tele \to \SymmMonCat$, that take a teleological category to its underlying symmetric monoidal category and subcategory of dualisable morphisms respectively.
+There are evident functors $U : \Tele \to \SymmMonCat$ and ${(-)}_d : \Tele \to \SymmMonCat$, that take a teleological category to its underlying symmetric monoidal category and subcategory of dualisable morphisms respectively.
 
@@
   \item The dualisable morphisms are all morphisms of the form $\iota(f, g)$;
-\item The involution is given on objects by $(S, S')^* := (S', S)$, and on a morphisms by \[\iota(f, g)^* := \iota(g, f);\]
-\item The counit $\varepsilon_{(S, S')} : (S, S') \switched (S, S')^* = (S \otimes S', S \otimes S') \to (I, I)$ is given by the connector: \[\varepsilon_{(S, S')} := c_{S \otimes S'}.\]
+  \item The involution is given on objects by ${(S, S')}^* := (S', S)$, and on morphisms by \[\iota{(f, g)}^* := \iota(g, f);\]
+  \item The counit $\varepsilon_{(S, S')} : (S, S') \switched {(S, S')}^* = (S \otimes S', S \otimes S') \to (I, I)$ is given by the connector: \[\varepsilon_{(S, S')} := c_{S \otimes S'}.\]
   \end{itemize}
@@
 \begin{proof}
-That morphisms of the form $\iota(f, g)$ constitute a category and that $(-)^*$ is a symmetric monoidal involution is clear: we have
+  That morphisms of the form $\iota(f, g)$ constitute a category and that ${(-)}^*$ is a symmetric monoidal involution is clear: we have
   \begin{align*}
@@
 
-Note that the diagrams required to commute all terminate with the unit $I$, so in view of Proposition \ref{prop-costates} we should not be surprised that they correspond to equality of maps in $\C$.
-\end{proof}
-
-%\todo{They stress about the empty set, have I avoided that issue?}
+  Note that the diagrams required to commute all terminate with the unit $I$, so in view of Proposition~\ref{prop-costates} we should not be surprised that they correspond to equality of maps in $\C$.
+\end{proof}
+
+      %       \todo{They stress about the empty set, have I avoided that issue?}
 
 \begin{proposition}
-The functor $\Optic : \SymmMonCat \to \SymmMonCat$ of Proposition \ref{prop-optic-functor} has its image in the subcategory $\Tele$.
+  The functor $\Optic : \SymmMonCat \to \SymmMonCat$ of Proposition~\ref{prop-optic-functor} has its image in the subcategory $\Tele$.
 \end{proposition}
@@
 
-%\begin{proposition}
-%Suppose $\langle l, r \rangle : (S, S') \hto (A, A')$ has complement $M$. Then 
-%\begin{align*}
-%\langle l, r \rangle = (\varepsilon_{(M, I)} \otimes (A, A'))\iota(l, r).
-%\end{align*}
-%\end{proposition}
-%\begin{proof}
-%First note that because $\C$ is strict monoidal, the counit $\varepsilon_{(M, I)} : (M \otimes I, M \otimes I) = (M, M) \hto (I, I)$ is equal to the connector $c_M : (M, M) \hto (I, I)$.
-%
-%The claim then holds, as any optic 
-%\begin{center}
-%\input{diagrams/generic-optic-noline.tikz}
-%\end{center}
-%is equal to the composite
-%\begin{center}
-%\input{diagrams/optic-decomposed.tikz}
-%\end{center}
-%where we have drawn the normally invisible strings corresponding to the unit $I$.
-%\end{proof}
-
-\begin{proposition}
-\label{prop-optic-decompose}
+      %       \begin{proposition}
+      %       Suppose $\langle l, r \rangle : (S, S') \hto (A, A')$ has complement $M$. Then
+      %       \begin{align*}
+      %       \langle l, r \rangle = (\varepsilon_{(M, I)} \otimes (A, A'))\iota(l, r).
+      %     \end{align*}
+      %       \end{proposition}
+      %       \begin{proof}
+      %       First note that because $\C$ is strict monoidal, the counit $\varepsilon_{(M, I)} : (M \otimes I, M \otimes I) = (M, M) \hto (I, I)$ is equal to the connector $c_M : (M, M) \hto (I, I)$.
+      %
+      %       The claim then holds, as any optic
+      %       \begin{center}
+      %       \input{diagrams/generic-optic-noline.tikz}
+      %       \end{center}
+      %       is equal to the composite
+      %       \begin{center}
+      %       \input{diagrams/optic-decomposed.tikz}
+      %       \end{center}
+      %       where we have drawn the normally invisible strings corresponding to the unit $I$.
+      %       \end{proof}
+
+\begin{proposition}\label{prop-optic-decompose}
   Suppose $\langle l, r \rangle : (S, S') \hto (A, A')$ has complement $M$. Then
@@
 For all symmetric monoidal functors $F : \C \to \T_d$, there exists a teleological functor $K : \Optic_\C \to \T$, unique up to isomorphism, such that $Kj \cong F$.
-%$\Optic$ is left adjoint to $(-)_d$, so $\Optic_\C$ is the free teleological category on a category of dualisable morphisms $\C$.
+      %       $\Optic$ is left adjoint to $(-)_d$, so $\Optic_\C$ is the free teleological category on a category of dualisable morphisms $\C$.
 \end{theorem}
@@
     &= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F((A \otimes f)s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
-%&= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(FA \otimes Ff \otimes FM \otimes FA')(F(s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
+      %               &= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(FA \otimes Ff \otimes FM \otimes FA')(F(s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
     &= (FA \otimes (\varepsilon_{FM} (Ff \otimes FM)) \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
@@
 
-To capture the \texttt{Iso}s, \texttt{Traversal}s and \texttt{Setter}s of the Haskell \texttt{lens} library (see \ref{lawful-examples}), we generalise to the case of a monoidal action of one category on another.
+To capture the \texttt{Iso}s, \texttt{Traversal}s and \texttt{Setter}s of the Haskell \texttt{lens} library (see~\ref{lawful-examples}), we generalise to the case of a monoidal action of one category on another.
 
@@
 
-\begin{proposition}
-\label{prop-change-of-action}
+\begin{proposition}\label{prop-change-of-action}
   Suppose $\C$ and $\D$ are categories acted on by $\M$ and $\mathcal{N}$ respectively.
@@
 \begin{proof}
-Analogous to Proposition \ref{prop-change-of-action-monoidal}
+  Analogous to Proposition~\ref{prop-change-of-action-monoidal}
 \end{proof}
@@
 
-\begin{proposition}
-\label{prop-onthenose}
+\begin{proposition}\label{prop-onthenose}
   Suppose $p : S \hto A$ satisfies $\outside(p) = \id_S$ and $\inside(p) = \langle \phi A \rangle$.
@@
 
-\begin{remark} \label{lens-iota-not-faithful}
+\begin{remark}\label{lens-iota-not-faithful}
   For the category of sets, the functor $\iota(-, -) : \Set \times \Set^\op \to \Optic_\times$ is not faithful.
@@
   \end{align*}
-where $\homC(-, -)$ denotes the internal hom. For a proof see \cite[Section 1.2]{DialecticaCategories}. This cannot be extended to non-cartesian closed categories, the isomorphism 
+  where $\homC(-, -)$ denotes the internal hom. For a proof see~\cite[Section 1.2]{DialecticaCategories}. This cannot be extended to non-cartesian closed categories, the isomorphism
   \begin{align*}
@@
 
-\begin{proposition}
-\label{prop-OpticImpliesLensLaws}
-A lens $p : S \hto A$ is a lawful lens in our sense, i.e.
-that $\outside(p) = \id_S$ and $\once(p) = \twice(p)$, if and only if the corresponding $\fput$ and $\fget$ for this lens obey the three lens laws.
+\begin{proposition}\label{prop-OpticImpliesLensLaws}
+  A lens $p : S \hto A$ is a lawful lens in our sense, i.e.\ that $\outside(p) = \id_S$ and $\once(p) = \twice(p)$, if and only if the corresponding $\fput$ and $\fget$ for this lens obey the three lens laws.
 \end{proposition}
@@
 In favourable conditions, we can upgrade this result to show that the existence of a lens $S \hto A$ implies that $S \cong C \times A$ for some $C$.
-This is a generalised from the argument given in \cite[Corollary 13]{AlgebrasAndUpdateStrategies} for $\Set$.
+This is a generalised from the argument given in~\cite[Corollary 13]{AlgebrasAndUpdateStrategies} for $\Set$.
 
@@
 
-The following is then exactly the dual of Proposition \ref{prop-OpticImpliesLensLaws}.
-\begin{proposition}
-\label{prop-OpticImpliesPrismLaws}
+The following is then exactly the dual of Proposition~\ref{prop-OpticImpliesLensLaws}.
+\begin{proposition}\label{prop-OpticImpliesPrismLaws}
   If $p : S \hto A$ is a prism then the associated $\fmatching$ and $\freview$ functions satisfy the three prism laws. \qed
@@
   \end{align*}
-%\begin{align*}
-%A \times \homC(B, C) \xrightarrow{f \times \id} FB \times \homC(B, C) \xrightarrow{\theta_{\homC(B, C), B}}  F(B \times \homC(B, C)) \xrightarrow{F\epsilon} FC
-%\end{align*}
+             %              \begin{align*}
+             %              A \times \homC(B, C) \xrightarrow{f \times \id} FB \times \homC(B, C) \xrightarrow{\theta_{\homC(B, C), B}}  F(B \times \homC(B, C)) \xrightarrow{F\epsilon} FC
+             %     \end{align*}
   where $\theta$ is the strength for $F$.
@@
 
-%$\Psi(\eta) : A \to FB$ to be $A \xrightarrow{A \times \const_{\id_B}} A \times \homC(B, B) \xrightarrow{\eta_B} FB$.
+             %              $\Psi(\eta) : A \to FB$ to be $A \xrightarrow{A \times \const_{\id_B}} A \times \homC(B, B) \xrightarrow{\eta_B} FB$.
 
@@
 
-This is a generalisation of \cite[Proposition 2.2]{SecondOrderFunctionals}, isolating the properties of $\Set$ that are used. We can now construct setters:
+This is a generalisation of~\cite[Proposition 2.2]{SecondOrderFunctionals}, isolating the properties of $\Set$ that are used. We can now construct setters:
 
@@
 A folklore variant of a prism is the \emph{affine traversal}, which allows access to a target that may or may not be present.
-These are described in \cite{AffineTraversalPost}, and are there hypothesised to correspond to pairs of maps $\C(S, A \sqcup S') \times \C(S\times A', S')$.
+These are described in~\cite{AffineTraversalPost}, and are there hypothesised to correspond to pairs of maps $\C(S, A \sqcup S') \times \C(S\times A', S')$.
 This is not precisely correct, but very close:
@@
 \end{align*}
-\todo{check $\mathsf{Aff}$ is actually a monoidal category...}
+\todo{check $\mathsf{Aff}$ is actually a monoidal category}
 
@@
 
-%\subsection{Equivalence of Optics}
-%
-%One issue with the definition of optic given in the last section is that it could be difficult to determine when two optics $\langle l, r \rangle, \langle l', r' \rangle : S \hto A$ are equal.
+           %            \subsection{Equivalence of Optics}
+           %
+           %            One issue with the definition of optic given in the last section is that it could be difficult to determine when two optics $\langle l, r \rangle, \langle l', r' \rangle : S \hto A$ are equal.
 For some choices of $\M$, however, we can reduce a zigzag of relations to a single one.
            %
-%\todo{This may work in general with some huge number of conditions: something like $-A$ reflects monomorphisms and preserves binary coproducts, all subobjects in $\M$ have complements.}
-%
-%\begin{proposition}
-%Suppose all epimorphisms split in $\C$, and that $- \times A : \C \to \C$ reflects epis.
+           %            \todo{This may work in general with some huge number of conditions: something like $-A$ reflects monomorphisms and preserves binary coproducts, all subobjects in $\M$ have complements.}
+           %
+           %            \begin{proposition}
+           %            Suppose all epimorphisms split in $\C$, and that $- \times A : \C \to \C$ reflects epis.
 Then two lenses $\langle l, r \rangle$ and $\langle l', r' \rangle :  S \hto A$ with complements $M$ and $N$ respectively are equal iff there exists an morphism $\phi : M \to N$ such that $(\phi \times A)l = l'$ and $r = r' (\phi \times A)$.
-%\end{proposition}
-%\begin{proof}
-%The backward direction is clear: the morphism $\phi$ is a witness that $\langle l, r \rangle \rightsquigarrow \langle l', r' \rangle$, so the two optics are equal.
-%
-%%note that $p$ and $q$ must have identical $\fget$ and $\fput$ functions:
-%%\begin{align*}
-%%\fget &= \pi_2 l = \pi_2 l' \\
-%%\fput &= r (\pi_1 l \times A) = r' (\pi_1 l' \times A)
-%%\end{align*}
-%For the forward direction, note that the map $(\pi_1 l \times A)$ is a retraction: it has the section $(r, \pi_2)$:
-%\begin{align*}
-%(\pi_1 l \times A)(r, \pi_2) = (\pi_1 l r, \pi_2) = (\pi_1, \pi_2) = \id_{S \times A}
-%\end{align*}
-%Now by assumption, $\pi_1 l : S \to M$ is an epi, so has a retraction $f : M \to S$. The claim is that $\phi = \pi_1 l' f$ is the required morphism $M \to N$.
-%
-%The situation is summarised in the following diagram, which other than the dashed line, we know commutes.
-%\[
-%\begin{tikzcd}
-%M \times A \ar[r, "{f \times A}", dashed, bend left = 50] \ar[d, "r", swap] & S \times A \ar[d, "\fput"] \ar[r, "{\pi_1 l' \times A}"] \ar[l, "{\pi_1 l \times A}", swap] & N \times A \ar[d, "r'"] \\
-%S \ar[r, equal] \ar[d, "l", swap] & S \ar[d, "{[\id_S, \fget]}"] \ar[r, equal] & S \ar[d, "l'"] \\
-%M \times A & S \times A \ar[r] \ar[l] & N \times A
-%\end{tikzcd}
-%\]
-%We can now calculate:
-%\begin{align*}
-%r = r(\pi_1 l f \times A) = \fput (f \times A) = r' (\pi_1 l' f \times A) = r'(\phi \times A)
-%\end{align*}
-%as required. The equation relating $l$ and $l'$ follows immediately as they are the inverses of $r$ and $r'$.
-%\end{proof}
-%
-%The conditions of the above Proposition hold in $\Set$, so long as $A$ is not empty.
+           %            \end{proposition}
+           %            \begin{proof}
+           %            The backward direction is clear: the morphism $\phi$ is a witness that $\langle l, r \rangle \rightsquigarrow \langle l', r' \rangle$, so the two optics are equal.
+           %
+           %%            note that $p$ and $q$ must have identical $\fget$ and $\fput$ functions:
+           %%            \begin{align*}
+           %%              \fget &= \pi_2 l = \pi_2 l' \\
+           %%              \fput &= r (\pi_1 l \times A) = r' (\pi_1 l' \times A)
+           %%            \end{align*}
+                                   %                                    For the forward direction, note that the map $(\pi_1 l \times A)$ is a retraction: it has the section $(r, \pi_2)$:
+                                   %                                    \begin{align*}
+                                   %                                    (\pi_1 l \times A)(r, \pi_2) = (\pi_1 l r, \pi_2) = (\pi_1, \pi_2) = \id_{S \times A}
+                                   %     \end{align*}
+                                   %                                    Now by assumption, $\pi_1 l : S \to M$ is an epi, so has a retraction $f : M \to S$.
+The claim is that $\phi = \pi_1 l' f$ is the required morphism $M \to N$.
+                                   %
+                                   %                                    The situation is summarised in the following diagram, which other than the dashed line, we know commutes.
+                                   %                                    \[
+                                   %                                    \begin{tikzcd}
+                                   %                                    M \times A \ar[r, "{f \times A}", dashed, bend left = 50] \ar[d, "r", swap] & S \times A \ar[d, "\fput"] \ar[r, "{\pi_1 l' \times A}"] \ar[l, "{\pi_1 l \times A}", swap] & N \times A \ar[d, "r'"] \\
+      %       S \ar[r, equal] \ar[d, "l", swap] & S \ar[d, "{[\id_S, \fget]}"] \ar[r, equal] & S \ar[d, "l'"] \\
+      %       M \times A & S \times A \ar[r] \ar[l] & N \times A
+                                                      %                                                       \end{tikzcd}
+                                                      %                                                       \]
+                                                      %                                                       We can now calculate:
+                                                      %                                                       \begin{align*}
+                                                      %                                                       r = r(\pi_1 l f \times A) = \fput (f \times A) = r' (\pi_1 l' f \times A) = r'(\phi \times A)
+                                                      %     \end{align*}
+                                                      %                                                       as required.
+The equation relating $l$ and $l'$ follows immediately as they are the inverses of $r$ and $r'$.
+                                                      %                                                       \end{proof}
+                                                      %
+                                                      %                                                       The conditions of the above Proposition hold in $\Set$, so long as $A$ is not empty.
 
                                                       %                                                       Old attempt:
-%\begin{definition}
-%A functor $F : \C \to \D$ satisfies the \emph{splitting morphism condition} (SM) if, for every $f : A \to B$ in $\C$ such that $Ff$ is a split monomorphism, there exists a $g : B \to A$ such that $F(gf) = \id_{FA}$.
-%
-%Similarly, $F$ satisfies the \emph{splitting epimorphism condition} (SE) if for every $f : A \to B$ in $\C$ such that $Ff$ is a split epimorphism, there exists a $g : B \to A$ such that $F(fg) = \id_{FB}$.
-%\end{definition}
-%
-%These definitions are identical to ones given in a (as far as I can tell totally unrelated) paper on triangulated categories \cite{ObjectiveTriangleFunctors}.
+                                                      %                                                       \begin{definition}
+                                                      %                                                       A functor $F : \C \to \D$ satisfies the \emph{splitting morphism condition} (SM) if, for every $f : A \to B$ in $\C$ such that $Ff$ is a split monomorphism, there exists a $g : B \to A$ such that $F(gf) = \id_{FA}$.
+                                                      %
+                                                      %                                                       Similarly, $F$ satisfies the \emph{splitting epimorphism condition} (SE) if for every $f : A \to B$ in $\C$ such that $Ff$ is a split epimorphism, there exists a $g : B \to A$ such that $F(fg) = \id_{FB}$.
+                                                      %                                                       \end{definition}
+                                                      %
+                                                      %                                                       These definitions are identical to ones given in a (as far as I can tell totally unrelated) paper on triangulated categories \cite{ObjectiveTriangleFunctors}.
 The conditions are not too difficult to satisfy:
                                                       %
-%\begin{proposition}[\todo{cite}]
-%If $F$ is full then it satisfies (SM) and (SE).
-%\end{proposition}
-%\begin{proof}
-%
-%\end{proof}
-%
-%\begin{proposition}[\todo{cite}]
-%If $F$ is faithful then it satisfies (SM) and (SE).
-%\end{proposition}
-%\begin{proof}
-%
-%\end{proof}
-%
-%\begin{theorem}
-%Suppose we have two optics $\langle l, r \rangle$ and $\langle l', r' \rangle \in \Optic_\M(S, A)$ with complements $M$ and $N$ respectively, and suppose $\M$ has the property that the ``evaluation-at-$A$'' functor $(-A) : \M \to \C$ satisfies (SM) and (SE).
+                                                      %                                                       \begin{proposition}[\todo{cite}]
+                                                      %                                                       If $F$ is full then it satisfies (SM) and (SE).
+                                                      %                                                       \end{proposition}
+                                                      %                                                       \begin{proof}
+                                                      %
+                                                      %                                                       \end{proof}
+                                                      %
+                                                      %                                                       \begin{proposition}[\todo{cite}]
+                                                      %                                                       If $F$ is faithful then it satisfies (SM) and (SE).
+                                                      %                                                       \end{proposition}
+                                                      %                                                       \begin{proof}
+                                                      %
+                                                      %                                                       \end{proof}
+                                                      %
+                                                      %                                                       \begin{theorem}
+                                                      %                                                       Suppose we have two optics $\langle l, r \rangle$ and $\langle l', r' \rangle \in \Optic_\M(S, A)$ with complements $M$ and $N$ respectively, and suppose $\M$ has the property that the ``evaluation-at-$A$'' functor $(-A) : \M \to \C$ satisfies (SM) and (SE).
 Then the two optics are equal iff there exists an morphism $\phi : M \to N$ such that $\phi_A l = l'$ and $r = r' \phi_A$.
-%\end{theorem}
-%\begin{proof}
-%The backward direction is clear: the morphism $\phi$ is a witness that $\langle l, r \rangle \rightsquigarrow \langle l', r' \rangle$, so the two optics are equal.
-%
-%For the forward direction, as in Proposition \ref{prop-onthenose} we induct on a zigzag \[(l, r) = (l_1, r_1) \leftrightsquigarrow \dots \leftrightsquigarrow (l_n, r_n) = (l', r'),\] where each pair $(l_i, r_i)$ has complement $M_i$.
+                                                      %                                                       \end{theorem}
+                                                      %                                                       \begin{proof}
+                                                      %                                                       The backward direction is clear: the morphism $\phi$ is a witness that $\langle l, r \rangle \rightsquigarrow \langle l', r' \rangle$, so the two optics are equal.
+                                                      %
+                                                      %                                                       For the forward direction, as in Proposition \ref{prop-onthenose} we induct on a zigzag \[(l, r) = (l_1, r_1) \leftrightsquigarrow \dots \leftrightsquigarrow (l_n, r_n) = (l', r'),\] where each pair $(l_i, r_i)$ has complement $M_i$.
 As a base case, we can take the identity $\id_M : M \to M = M_1$.
@@
                                                       %
-%If $(l_{i-1}, r_{i-1}) \rightsquigarrow (l_i, r_i)$, then by definition we have a $\psi : M_{i-1}\to M_i$ that satisfies the equations $\psi_A l_{i-1} = l_i$ and $r_{i-1} = r_i \psi_A$.
+                                                      %                                                       If $(l_{i-1}, r_{i-1}) \rightsquigarrow (l_i, r_i)$, then by definition we have a $\psi : M_{i-1}\to M_i$ that satisfies the equations $\psi_A l_{i-1} = l_i$ and $r_{i-1} = r_i \psi_A$.
 Therefore the composite $\psi\phi$ satisfies $(\psi\phi)_A l = \psi_A l_{i-1} = l_i$ and $r = r_{i-1} \phi_A = r_i (\psi \phi)_A$, so $\psi\phi : M \to M_i$ is the required morphism.
                                                       %
-%If instead $(l_{i-1}, r_{i-1}) \leftsquigarrow (l_i, r_i)$, we have a morphism in the opposite direction $\psi : M_i \to M_{i-1}$, with $\psi_A l_i = l_{i-1}$ and $r_i = r_{i-1} \psi_A$, as shown in the following commutative diagram
-%\[
-%\begin{tikzcd}
-%M A \ar[r, "\phi_A"] \ar[d, "r", swap] & M_{i-1} A \ar[d, "r_{i-1}"] & M_i A \ar[l, "\psi_A", swap] \ar[d, "r_i"]\\
-%S \ar[r, equal] \ar[d, "l", swap] & S \ar[r, equal] \ar[d, "l_{i-1}"] & S \ar[d, "l_i"] \\
-%M A \ar[r, "\phi_A", swap] & M_{i-1} A & M_i A \ar[l, "\psi_A"]
-%\end{tikzcd}
-%\]
-%To construct a morphism $M \to M_i$ we have to perform a slightly awkward switchback maneuver. First note that $\phi_A$ is a split monomorphism, as $(l r_{i-1}) \phi_A = lr = \id_{MA}$.
-%
-%By condition (SM), therefore, there is a morphism $\gamma : M_{i-1} \to M$ such that $\gamma_A \phi_A = \id_{MA}$. But now, the composite $\gamma_A \psi_A : M_i \to M$ is a split epimorphism:
-%\begin{align*}
-%(\gamma_A \psi_A)(l_i r) = \gamma_A l_{i-1} r = \gamma_A \phi_A l r = \gamma_A \phi_A = \id_{MA}
-%\end{align*}
-%and by condition (SE), there is a morphism $\theta : M \to M_i$ with $\gamma_A \psi_A \theta_A = \id_{MA}$.
+                                                      %                                                       If instead $(l_{i-1}, r_{i-1}) \leftsquigarrow (l_i, r_i)$, we have a morphism in the opposite direction $\psi : M_i \to M_{i-1}$, with $\psi_A l_i = l_{i-1}$ and $r_i = r_{i-1} \psi_A$, as shown in the following commutative diagram
+                                                      %                                                       \[
+                                                      %                                                       \begin{tikzcd}
+                                                      %                                                       M A \ar[r, "\phi_A"] \ar[d, "r", swap] & M_{i-1} A \ar[d, "r_{i-1}"] & M_i A \ar[l, "\psi_A", swap] \ar[d, "r_i"]\\
+      %       S \ar[r, equal] \ar[d, "l", swap] & S \ar[r, equal] \ar[d, "l_{i-1}"] & S \ar[d, "l_i"] \\
+      %       M A \ar[r, "\phi_A", swap] & M_{i-1} A & M_i A \ar[l, "\psi_A"]
+                                                       %                                                        \end{tikzcd}
+                                                       %                                                        \]
+                                                       %                                                        To construct a morphism $M \to M_i$ we have to perform a slightly awkward switchback maneuver.
+First note that $\phi_A$ is a split monomorphism, as $(l r_{i-1}) \phi_A = lr = \id_{MA}$.
+                                                       %
+                                                       %                                                        By condition (SM), therefore, there is a morphism $\gamma : M_{i-1} \to M$ such that $\gamma_A \phi_A = \id_{MA}$.
+But now, the composite $\gamma_A \psi_A : M_i \to M$ is a split epimorphism:
+                                                       %                                                        \begin{align*}
+                                                       %                                                        (\gamma_A \psi_A)(l_i r) = \gamma_A l_{i-1} r = \gamma_A \phi_A l r = \gamma_A \phi_A = \id_{MA}
+                                                       %     \end{align*}
+                                                       %                                                        and by condition (SE), there is a morphism $\theta : M \to M_i$ with $\gamma_A \psi_A \theta_A = \id_{MA}$.
 It remains to show that $\theta_A l = l_i$ and $r = r_i \theta_A$.
 First some intermediate steps:
-%\begin{align*}
-%r \gamma_A = r_{i-1} l_{i-1} r \gamma_A = r_{i-1} \phi_A l r \gamma_A = r_{i-1} \phi_A \gamma_A = 
-%\end{align*}
-%So finally:
-%\begin{align*}
-%r &= r \gamma_A \psi_A \theta_A	
-%\end{align*}
-%\todo{picture}
-%\end{proof}
+                                                       %                                                        \begin{align*}
+                                                       %                                                        r \gamma_A = r_{i-1} l_{i-1} r \gamma_A = r_{i-1} \phi_A l r \gamma_A = r_{i-1} \phi_A \gamma_A =
+                                                       %     \end{align*}
+                                                       %                                                        So finally:
+                                                       %                                                        \begin{align*}
+                                                       %                                                        r &= r \gamma_A \psi_A \theta_A
+                                                                                                                    %     \end{align*}
+                                                                                                                    %                                                                                                                     \todo{picture}
+                                                                                                                    %                                                                                                                     \end{proof}
 
@@
 
-The precise connection between this encoding and the previous one was investigated independently in \cite{ProfunctorOpticsPost}.
+The precise connection between this encoding and the previous one was investigated independently in~\cite{ProfunctorOpticsPost}.
 In this section, we extend these ideas to the case of a monoidal action and include an analysis of lawful optics in this setting.
@@
 Let $I = \C(-,{=}) : \C \hto \C$ be the identity profunctor and $\odot$ be profunctor composition, written in diagrammatic order.
-The following section generalises definitions that first appeared in \cite[Section 3]{Doubles} for monoidal categories to the more general case of a monoidal action.
+The following section generalises definitions that first appeared in~\cite[Section 3]{Doubles} for monoidal categories to the more general case of a monoidal action.
 
@@
   Now suppose $T \in \Tamb(\M)$ is a Tambara module with structure map $\beta$.
-We would like to show that for any map $f : P \hto UT$, there exists a unique $\hat f : \Phi_\M P \hto T$ so that $f$ factors as \[P \xrightarrow{\eta} U \Phi_\M P \xrightarrow{U\hat f} UT \].
+We would like to show that for any map $f : P \hto UT$, there exists a unique $\hat f : \Phi_\M P \hto T$ so that $f$ factors as \[P \xrightarrow{\eta} U \Phi_\M P \xrightarrow{U\hat f} UT.
+\]
 
@@
 
-\begin{lemma}
-\label{lemma-rep}
+\begin{lemma}\label{lemma-rep}
   The functor $(U-)(A,A) : \Tamb(\M) \to \Set$ is representable: there is a natural isomorphism
@@
 
-\begin{proposition}[Profunctor Optics are Optics]
-\label{prop-profunctor-optics-are-optics}
+\begin{proposition}[Profunctor Optics are Optics]\label{prop-profunctor-optics-are-optics}
   \begin{align*}
@@
 
-%\begin{proposition}
-%If $p : S \hto A$ is a lawful optic then the associated natural transformation $\tilde{p} : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal.
-%\end{proposition}
-%\begin{proof}
-%Let $\langle l, r \rangle$ be a representative for $p$ in $\Optic_\M(S,A)$ via the isomorphism of Proposition \ref{prop-profunctor-optics-are-optics}, so that
-%\begin{align*}
-%\tilde{p}_P = (UP)(l,r) \alpha_{A,A,M}
-%\end{align*}
-%on each Tambara module $P$.
-%
-%To show $\tilde{p}$ is monoidal, we must show that both
-%\[
-%\begin{tikzcd}
-%UP(A,A) \times UQ(A,A) \ar[r, "\tilde{p}_P \times \tilde{p}_Q"] \ar[d, swap] & UP(S, S) \times UQ(S, S)  \ar[d] \\
-%U(P \odot Q)(A,A)  \ar[r, "\tilde{p}_{P \odot Q}", swap] & U(P \odot Q)(S,S)
-%\end{tikzcd}
-%\]
-%and
-%\[
-%\begin{tikzcd}
-%1 \ar[d] \ar[dr] & \\
-%UI(A,A)  \ar[r, "\tilde{p}_I", swap] & UI(S,S)
-%\end{tikzcd}
-%\]
-%commute. For the first we have
-%\begin{align*}
-%\langle (\tilde{p}_P \times \tilde{p}_Q)(x, y) \rangle &= \langle (UP)(l,r) \alpha_{A,A,M} x,  (UQ)(l,r) \beta_{A,A,M} y\rangle \\
-%&= \langle (UP)(l,lr) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(by the coend relations)} \\
-%&= \langle (UP)(l,\phi A) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $lr = \phi A$)} \\
-%&= \langle (UP)((\phi A)l,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(by the coend relations again)} \\
-%&= \langle (UP)(lrl,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $lr = \phi A$ again)} \\
-%&= \langle (UP)(l,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $rl = \id_S$)} \\
-%&= (U(P \odot Q))(l,r) \langle \alpha_{A,A,M} x, \beta_{A,A,M} y \rangle && \text{(by definition of $P \odot Q$)} \\
-%&= (U(P \odot Q))(l,r) (\alpha_{A,A,M} \odot \beta_{A,A,M}) \langle x, y \rangle && \text{(by definition of $\alpha \odot \beta$)} \\
-%&= \tilde{p}_{P \odot Q} \langle x, y \rangle
-%\end{align*}
-%And for the second:
-%\begin{align*}
-%\tilde{p}_I(\id_A) = (UI)(l,r) (M \id_A) = r \id_{MA} l = rl = \id_S
-%\end{align*}
-%as required.
-%\end{proof}
-%
-%%\begin{proposition}
-%%Let $\C = \Set$ and suppose $p : S \hto A$ is a lens such that the associated natural transformation $p : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal. Then $p$ is lawful.
-%%\end{proposition}
-%%\begin{proof}
-%%\todo{Show that it satisfies the getput, putget and putput laws. This strategy works only with $\times$ and in $\Set$.}
-%%\end{proof}
-%
-%\todo{Here are some thoughts:}
-%The converse is more difficult, and unfortunately requires another fiddly proof by induction on the coend relation.
+                  %                   \begin{proposition}
+                  %                   If $p : S \hto A$ is a lawful optic then the associated natural transformation $\tilde{p} : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal.
+                  %                   \end{proposition}
+                  %                   \begin{proof}
+                  %                   Let $\langle l, r \rangle$ be a representative for $p$ in $\Optic_\M(S,A)$ via the isomorphism of Proposition \ref{prop-profunctor-optics-are-optics}, so that
+                  %                   \begin{align*}
+                  %                   \tilde{p}_P = (UP)(l,r) \alpha_{A,A,M}
+                  %     \end{align*}
+                  %                   on each Tambara module $P$.
+                  %
+                  %                   To show $\tilde{p}$ is monoidal, we must show that both
+                  %                   \[
+                  %                   \begin{tikzcd}
+                  %                   UP(A,A) \times UQ(A,A) \ar[r, "\tilde{p}_P \times \tilde{p}_Q"] \ar[d, swap] & UP(S, S) \times UQ(S, S)  \ar[d] \\
+      %       U(P \odot Q)(A,A)  \ar[r, "\tilde{p}_{P \odot Q}", swap] & U(P \odot Q)(S,S)
+                                                                         %                                                                          \end{tikzcd}
+                                                                         %                                                                          \]
+                                                                         %                                                                          and
+                                                                         %                                                                          \[
+                                                                         %                                                                          \begin{tikzcd}
+                                                                         %                                                                          1 \ar[d] \ar[dr] & \\
+      %       UI(A,A)  \ar[r, "\tilde{p}_I", swap] & UI(S,S)
+                                                     %                                                      \end{tikzcd}
+                                                     %                                                      \]
+                                                     %                                                      commute. For the first we have
+                                                     %                                                      \begin{align*}
+                                                     %                                                      \langle (\tilde{p}_P \times \tilde{p}_Q)(x, y) \rangle &= \langle (UP)(l,r) \alpha_{A,A,M} x,  (UQ)(l,r) \beta_{A,A,M} y\rangle \\
+      %               &= \langle (UP)(l,lr) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(by the coend relations)} \\
+      %               &= \langle (UP)(l,\phi A) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $lr = \phi A$)} \\
+      %               &= \langle (UP)((\phi A)l,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(by the coend relations again)} \\
+      %               &= \langle (UP)(lrl,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $lr = \phi A$ again)} \\
+      %               &= \langle (UP)(l,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $rl = \id_S$)} \\
+      %               &= (U(P \odot Q))(l,r) \langle \alpha_{A,A,M} x, \beta_{A,A,M} y \rangle && \text{(by definition of $P \odot Q$)} \\
+      %               &= (U(P \odot Q))(l,r) (\alpha_{A,A,M} \odot \beta_{A,A,M}) \langle x, y \rangle && \text{(by definition of $\alpha \odot \beta$)} \\
+      %               &= \tilde{p}_{P \odot Q} \langle x, y \rangle
+                        %     \end{align*}
+                        %                         And for the second:
+                        %                         \begin{align*}
+                        %                         \tilde{p}_I(\id_A) = (UI)(l,r) (M \id_A) = r \id_{MA} l = rl = \id_S
+                        %     \end{align*}
+                        %                         as required.
+                        %                         \end{proof}
+                        %
+                        %%                         \begin{proposition}
+                        %%                           Let $\C = \Set$ and suppose $p : S \hto A$ is a lens such that the associated natural transformation $p : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal.
+Then $p$ is lawful.
+                        %%                         \end{proposition}
+                        %%                         \begin{proof}
+                        %%                           \todo{Show that it satisfies the getput, putget and putput laws. This strategy works only with $\times$ and in $\Set$.}
+                        %%                         \end{proof}
+                        %
+                        %                         \todo{Here are some thoughts:}
+                        %                         The converse is more difficult, and unfortunately requires another fiddly proof by induction on the coend relation.
 The idea is that any profunctor optic is characterised by its component at $\Pastro_\M E_A$, so the result should follow from the commutativity of the square for lax monoidality when $P = Q = \Pastro_\M E_A$.
                         %
-%For the remainder of the section, fix a lax monoidal natural transformation $t : (U-)(A,A) \to (U-)(S,S)$ and suppose $\hat{t} = \langle l, r \rangle$ for $l : S \to MA$ and $r : MA \to S$.
+                        %                         For the remainder of the section, fix a lax monoidal natural transformation $t : (U-)(A,A) \to (U-)(S,S)$ and suppose $\hat{t} = \langle l, r \rangle$ for $l : S \to MA$ and $r : MA \to S$.
 Commutativity of the triangle implies immediately that $rl = \id_S$.
                         %
-%Unwinding definitions, commutativity of the square states that
-%\begin{align*}
-%\langle l, lr, r \rangle = \langle l, \id_{MA}, r \rangle
-%\end{align*}
-%as elements of 
-%\begin{align*}
-%\int^{M,N\in \M} \C(S, MA) \times \C(MA, NA) \times \C(NA, S)
-%\end{align*}
-%Our goal is to show that this implies $\langle lr \rangle = \langle \phi A \rangle$ for some $\phi : M \to M$ in $\M$.
-%
-%\todo{describe the coend relation on this set}
-%
-%\newcommand{\rightrightsquigarrow}{\mathrel{\substack{\textstyle\rightsquigarrow\\[-0.6ex]
+                        %                         Unwinding definitions, commutativity of the square states that
+                        %                         \begin{align*}
+                        %                         \langle l, lr, r \rangle = \langle l, \id_{MA}, r \rangle
+                        %     \end{align*}
+                        %                         as elements of
+                        %                         \begin{align*}
+                        %                         \int^{M,N\in \M} \C(S, MA) \times \C(MA, NA) \times \C(NA, S)
+                        %     \end{align*}
+                        %                         Our goal is to show that this implies $\langle lr \rangle = \langle \phi A \rangle$ for some $\phi : M \to M$ in $\M$.
+                        %
+                        %                         \todo{describe the coend relation on this set}
+                        %
+                        %                         \newcommand{\rightrightsquigarrow}{\mathrel{\substack{\textstyle\rightsquigarrow\\[-0.6ex]
       %       \textstyle\rightsquigarrow}}}
-%\newcommand{\leftleftsquigarrow}{\mathrel{\substack{\textstyle\leftsquigarrow\\[-0.6ex]
+      %       \newcommand{\leftleftsquigarrow}{\mathrel{\substack{\textstyle\leftsquigarrow\\[-0.6ex]
       %       \textstyle\leftsquigarrow}}}
       %
-%\begin{align*}
-%&\int^{N,M} \C(S, M \times A) \times \C(M \times A, N \times A) \times \C(N \times A, S) \\
-%&= \int^{N,M} \C(S, M) \times \C(S, A) \times \C(M \times A, N \times A) \times \C(N \times A, S) \\
-%&= \int^{N} \C(S, A) \times \C(S \times A, N \times A) \times \C(N \times A, S) \\
-%&= \int^{N} \C(S, A) \times \C(S \times A, N) \times \C(S \times A, A) \times \C(N \times A, S) \\
-%&= \C(S, A) \times \C(S \times A, A) \times \C(S \times A \times A, S) \\
-%\end{align*}
-%Here $\langle l, c, r \rangle$ is sent to $(l \pi_2, (l \pi_1, \id_A) c \pi_2, ((l \pi_1, \id_A) c, \id_A) r)$
-%
-%\todo{Do this for the linear lens too}
-%\begin{theorem}
-%If $t : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal, then $\hat{t} : S \hto A$ is a lawful optic.
-%\end{theorem}
-%\begin{proof}
-%
-%\end{proof}
+      %       \begin{align*}
+      %               &\int^{N,M} \C(S, M \times A) \times \C(M \times A, N \times A) \times \C(N \times A, S) \\
+      %               &= \int^{N,M} \C(S, M) \times \C(S, A) \times \C(M \times A, N \times A) \times \C(N \times A, S) \\
+      %               &= \int^{N} \C(S, A) \times \C(S \times A, N \times A) \times \C(N \times A, S) \\
+      %               &= \int^{N} \C(S, A) \times \C(S \times A, N) \times \C(S \times A, A) \times \C(N \times A, S) \\
+      %               &= \C(S, A) \times \C(S \times A, A) \times \C(S \times A \times A, S) \\
+      %     \end{align*}
+      %       Here $\langle l, c, r \rangle$ is sent to $(l \pi_2, (l \pi_1, \id_A) c \pi_2, ((l \pi_1, \id_A) c, \id_A) r)$
+      %
+      %       \todo{Do this for the linear lens too}
+      %       \begin{theorem}
+      %       If $t : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal, then $\hat{t} : S \hto A$ is a lawful optic.
+      %       \end{theorem}
+      %       \begin{proof}
+      %
+      %       \end{proof}
 
@@
 \begin{example}
-The following example is taken from \cite{AClearPictureOfLensLaws}. The ``change counter'' lens $\bN \times A \hto A$ for a set $A$ has $\fput$ and $\fget$ given by:
+  The following example is taken from~\cite{AClearPictureOfLensLaws}. The ``change counter'' lens $\bN \times A \hto A$ for a set $A$ has $\fput$ and $\fget$ given by:
   \begin{align*}
@@
 
-Many attempts \cite{ReflectionsOnMonadicLenses} \todo{more} to define effectful lenses have wrapped the result of one or both of $\fget$ and $\fput$ with a monad.
+Many attempts~\cite{ReflectionsOnMonadicLenses} \todo{more} to define effectful lenses have wrapped the result of one or both of $\fget$ and $\fput$ with a monad.
 This approach is a little ad-hoc; it is not obvious what the laws ought to be and there is no clear generalisation to other varieties of optic.

### 2018-06-11 paper.tex
Get commented out bits under control
Long and tedious conversion from commas to mids

@@
 
+\newcommand{\rep}[2]{{\ensuremath \langle #1 \mid #2 \rangle}}
+\newcommand{\repthree}[3]{{\ensuremath \langle #1 \mid #2 \mid #3 \rangle}}
+\newcommand{\repfour}[4]{{\ensuremath \langle #1 \mid #2 \mid #3 \mid #4 \rangle}}
+
 \newcommand{\fget}{\textsc{Get}}
@@
 
-If $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\langle l \mid r \rangle : (S, S') \hto (A, A')$ for the image of this pair in $\Optic_\C((S, S'), (A, A'))$, and say that $M$ is the complement for the representative.
+If $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\rep{l}{r} : (S, S') \hto (A, A')$ for the image of this pair in $\Optic_\C((S, S'), (A, A'))$, and say that $M$ is the complement for the representative.
 Optics will always be written with a crossed arrow $\hto$, to distinguish them from morphisms of $\C$.
@@
 \begin{example}
-  For any three objects $M, A, A' \in \C$, there is the \emph{tautological} optic \[t_{M,A} : (M \otimes A, M \otimes A') \hto (A, A')\] which is given by $\langle \id_{M \otimes A}\mid \id_{M \otimes A'} \rangle$.
+  For any three objects $M, A, A' \in \C$, there is the \emph{tautological} optic \[t_{M,A} : (M \otimes A, M \otimes A') \hto (A, A')\] which is given by $\rep{\id_{M \otimes A}}{\id_{M \otimes A}}$.
 \end{example}
@@
   interpretation as string diagrams with a ``hole'' missing. We draw the
-  pair $\langle l \mid r \rangle$ as
+  pair $\rep{l}{r}$ as
   \begin{center}
@@
 \end{align*}
-In other words, let $\langle l', r' \rangle : (R, R') \hto (S, S')$ and $\langle l, r \rangle : (S, S') \hto (A, A')$ with $M$ the complement for $\langle l', r' \rangle$.
-The composite is then: $\langle l, r \rangle \circ \langle l', r' \rangle = \langle (M l)l', r'(Mr)\rangle$.
+In other words, let $\rep{l'}{r'} : (R, R') \hto (S, S')$ and $\rep{l}{r} : (S, S') \hto (A, A')$ with $M$ the complement for $\rep{l'}{r'}$.
+The composite is then: $\rep{l}{r} \circ \rep{l'}{r'} = \rep{(M l)l'}{r'(Mr)}$.
 
@@
 
-The identity optic $(S, S') \hto (S, S')$ is given by $\langle \lambda^{-1}_S, \lambda_{S'} \rangle$, where $\lambda_S : I \otimes S \to S$ is the left unitor for $S$:
+The identity optic $(S, S') \hto (S, S')$ is given by $\rep{\lambda^{-1}_S}{\lambda_{S'}}$, where $\lambda_S : I \otimes S \to S$ is the left unitor for $S$:
 \begin{center}
@@
 As in the definition of composition, the Fubini theorem for coends allows us to choose representatives for all three optics simultaneously.
-Suppose we have representatives of three optics $\langle l_1, r_1\rangle : (R, R) \hto (S, S')$ and $\langle l_2, r_2 \rangle : (S, S') \hto (A, A')$ and $\langle l_3, r_3 \rangle : (A, A') \hto (B, B')$, that have complements $M$, $N$ and $P$ respectively.
+Suppose we have representatives of three optics $\rep{l_1}{r_1} : (R, R) \hto (S, S')$, $\rep{l_2}{r_2} : (S, S') \hto (A, A')$ and $\rep{l_3}{r_3} : (A, A') \hto (B, B')$, that have complements $M$, $N$ and $P$ respectively.
 Then:
   \begin{align*}
-    (\langle l_3, r_3 \rangle \circ \langle l_2, r_2 \rangle) \circ \langle l_1, r_1 \rangle
-    &= \langle (N \otimes l_3)l_2, r_2(N \otimes r_3) \rangle \circ \langle l_1, r_1 \rangle \\
-    &= \langle (M \otimes ((N \otimes l_3)l_2))l_1, r_1(M \otimes (r_2(N \otimes r_3))) \rangle \\
-    &= \langle (M \otimes N \otimes l_3)(M \otimes l_2)l_1, r_1(M \otimes r_2)(M \otimes N \otimes r_3) \rangle \\
-    &= \langle l_3, r_3 \rangle \circ (\langle (M \otimes l_2)l_1, r_1(M \otimes r_2) \rangle) \\
-    &= \langle l_3, r_3 \rangle \circ (\langle l_2, r_2 \rangle \circ \langle l_1, r_1 \rangle)
-  \end{align*}
-
-  For the unit laws, suppose we have $\langle l, r \rangle : (S, S') \hto (A, A')$ with representative $M$. We calculate:
-  \begin{align*}
-    \id_{A, A'} \circ \langle l, r\rangle
-    &= \langle \lambda^{-1}_A, \lambda_{A'} \rangle \circ \langle l, r\rangle \\
-    &= \langle (M \otimes \lambda^{-1}_A) l, r (M\otimes  \lambda_{A'})\rangle \\
-    &= \langle (\lambda^{-1}_M \otimes  A) l, r (\lambda_M \otimes A')\rangle \\
-    &= \langle l, r (\lambda_M \otimes A') (\lambda^{-1}_M \otimes A')\rangle \\
-    &= \langle l, r \rangle  \\
-    \langle l, r \rangle \circ \id_{S, S'}
-    &= \langle l, r \rangle \circ \langle \lambda^{-1}_S, \lambda_{S'}\rangle  \\
-    &= \langle (I \otimes l)\lambda^{-1}_S, \lambda_{S'} (I \otimes r) \rangle \\
-    &= \langle (\lambda^{-1}_M \otimes S)l, r (\lambda_{M} \otimes S') \rangle \\
-    &= \langle l, r (\lambda_{M} \otimes S')(\lambda^{-1}_M \otimes S') \rangle \\
-    &= \langle l, r \rangle
+    (\rep{l_3}{r_3} \circ \rep{l_2, r_2}) \circ \rep{l_1}{r_1}
+    &= \rep{(N \otimes l_3)l_2}{r_2(N \otimes r_3)} \circ \rep{l_1}{r_1} \\
+    &= \rep{(M \otimes ((N \otimes l_3)l_2))l_1}{r_1(M \otimes (r_2(N \otimes r_3)))} \\
+    &= \rep{(M \otimes N \otimes l_3)(M \otimes l_2)l_1}{r_1(M \otimes r_2)(M \otimes N \otimes r_3)} \\
+    &= \rep{l_3}{r_3} \circ (\rep{(M \otimes l_2)l_1}{r_1(M \otimes r_2)}) \\
+    &= \rep{l_3}{r_3} \circ (\rep{l_2}{r_2} \circ \rep{l_1}{r_1})
+  \end{align*}
+
+  For the unit laws, suppose we have $\rep{l}{r} : (S, S') \hto (A, A')$ with representative $M$. We calculate:
+  \begin{align*}
+    \id_{A, A'} \circ \rep{l}{r}
+    &= \rep{\lambda^{-1}_A}{\lambda_{A'}} \circ \rep{l}{r} \\
+    &= \rep{(M \otimes \lambda^{-1}_A) l}{r (M\otimes  \lambda_{A'}} \\
+    &= \rep{(\lambda^{-1}_M \otimes  A) l}{r (\lambda_M \otimes A'} \\
+    &= \rep{l}{r (\lambda_M \otimes A') (\lambda^{-1}_M \otimes A')} \\
+    &= \rep{l}{r} \\
+    \rep{l}{r} \circ \id_{S, S'}
+    &= \rep{l}{r} \circ \rep{\lambda^{-1}_S}{\lambda_{S'}}  \\
+    &= \rep{(I \otimes l)\lambda^{-1}_S}{\lambda_{S'} (I \otimes r)} \\
+    &= \rep{(\lambda^{-1}_M \otimes S)l}{r (\lambda_{M} \otimes S')} \\
+    &= \rep{l}{r (\lambda_{M} \otimes S')(\lambda^{-1}_M \otimes S')} \\
+    &= \rep{l}{r}
   \end{align*}
@@
 \begin{proposition}
-  There is a functor $\iota : \C \times \C^\op \to \Optic_\C$, which is given on objects by $\iota(S, S') = (S, S')$ and for a morphism $(f, g) : (S, S') \to (A, A')$ by $\iota(f, g) = \langle \lambda_A^{-1} f, g \lambda_{A'} \rangle$.
+  There is a functor $\iota : \C \times \C^\op \to \Optic_\C$, which is given on objects by $\iota(S, S') = (S, S')$ and for a morphism $(f, g) : (S, S') \to (A, A')$ by $\iota(f, g) = \rep{ \lambda_A^{-1} f}{ g \lambda_{A'}}$.
 \end{proposition}
@@
 
-  This preserves identities, as the identity on an object $(S, S')$ in $\Optic_\M$ is defined to be exactly $\langle \lambda^{-1}_S, \lambda_{S'} \rangle$.
+  This preserves identities, as the identity on an object $(S, S')$ in $\Optic_\M$ is defined to be exactly $\rep{ \lambda^{-1}_S}{ \lambda_{S'}}$.
 To check functoriality, suppose we have $(f, g) : (S, S') \to (A, A')$ and $(f', g') : (A, A') \to (B, B')$ in $\C \times \C^\op$.
@@
     \iota(f', g') \circ \iota(f, g)
-    &= \langle \lambda^{-1}_B f', g' \lambda_{B'} \rangle \circ \langle \lambda^{-1}_A f, g \lambda_{A'} \rangle \\
-    &= \langle (I\otimes (\lambda^{-1}_B f'))\lambda^{-1}_A f, g \lambda_{A'} (I\otimes (g' \lambda_{B'}))\rangle && \text{(By definition of $\circ$)}\\
-    &= \langle (I \otimes \lambda^{-1}_B) (I \otimes f')\lambda^{-1}_A f, g \lambda_{A'} (I \otimes g')(I\otimes \lambda_{B'})\rangle && \text{(Functoriality of $I \otimes -$)}\\
-    &= \langle (I\otimes \lambda^{-1}_B) \lambda^{-1}_B f' f, g g' \lambda_{B'} (I\otimes \lambda_{B'})\rangle && \text{(Naturality of $\lambda$)}\\
-    &= \langle (\lambda^{-1}_I \otimes B) \lambda^{-1}_B f' f, g g' \lambda_{B'} (\lambda_I \otimes B')\rangle && \text{(Unitality of action)} \\
-    &= \langle \lambda^{-1}_B f' f, g g' \lambda_{B'} (\lambda_I \otimes B') (\lambda^{-1}_I \otimes B') \rangle && \text{(Coend relation)}  \\
-    &= \langle \lambda^{-1}_B f'f, g g' \lambda_{B'} \rangle \\
+    &= \rep{ \lambda^{-1}_B f'}{ g' \lambda_{B'}} \circ \rep{ \lambda^{-1}_A f}{ g \lambda_{A'}} \\
+    &= \rep{ (I\otimes (\lambda^{-1}_B f'))\lambda^{-1}_A f}{ g \lambda_{A'} (I\otimes (g' \lambda_{B'})} && \text{(By definition of $\circ$)}\\
+    &= \rep{ (I \otimes \lambda^{-1}_B) (I \otimes f')\lambda^{-1}_A f}{ g \lambda_{A'} (I \otimes g')(I\otimes \lambda_{B'}} && \text{(Functoriality of $I \otimes -$)}\\
+    &= \rep{ (I\otimes \lambda^{-1}_B) \lambda^{-1}_B f' f}{ g g' \lambda_{B'} (I\otimes \lambda_{B'}} && \text{(Naturality of $\lambda$)}\\
+    &= \rep{ (\lambda^{-1}_I \otimes B) \lambda^{-1}_B f' f}{ g g' \lambda_{B'} (\lambda_I \otimes B'} && \text{(Unitality of action)} \\
+    &= \rep{ \lambda^{-1}_B f' f}{ g g' \lambda_{B'} (\lambda_I \otimes B') (\lambda^{-1}_I \otimes B')} && \text{(Coend relation)}  \\
+    &= \rep{ \lambda^{-1}_B f'f}{ g g' \lambda_{B'}} \\
     &= \iota(f'f, gg')
@@
 % \begin{proof}
-                                                                                                                                    %                                                                                                                                     Equationally, suppose we have representatives $(l, r) : (S \to M \otimes A, M \otimes A' \to S')$ and $(l', r') : (T \to N \otimes B, N \otimes B' \to T')$.
-Then:
+%   Equationally, suppose we have representatives $(l, r) : (S \to M \otimes A, M \otimes A' \to S')$ and $(l', r') : (T \to N \otimes B, N \otimes B' \to T')$. Then:
 %   \begin{align*}
@@
 %%   \end{align*}
-                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                 Now we check functoriality.
-Suppose we have:
+%%   Now we check functoriality. Suppose we have:
 %%   \begin{align*}
@@
 %%   \end{align*}
-                                                                                                                                                                                                                                                                                                                                %%                                                                                                                                                                                                                                                                                                                                 with complements $M_1, M_2, N_1, N_2$ respectively.
-Then: \todo {(This is a mess.
-String diagram?)}
+%%   with complements $M_1, M_2, N_1, N_2$ respectively. Then: \todo {(This is a mess. String diagram?)}
 %%   \begin{align*}
@@
 %
-                                     %                                      Let us check that $\alpha_{(R, R'), (S, S'), (T, T')}$ is natural in $(R, R')$.
-Suppose $f : (Q, Q') \hto (R, R')$ has representative $(l, r) : (Q \to M \otimes R, M \otimes R' \to Q')$, then:
+%   Let us check that $\alpha_{(R, R'), (S, S'), (T, T')}$ is natural in $(R, R')$. Suppose $f : (Q, Q') \hto (R, R')$ has representative $(l, r) : (Q \to M \otimes R, M \otimes R' \to Q')$, then:
 %   \begin{align*}
@@
 \begin{theorem}
-  $\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit object is $(I, I)$, and the action on a pair of morphisms $\langle l, r \rangle : S \hto A$ and $\langle l', r' \rangle : T \hto B$ is given by:
+  $\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit object is $(I, I)$, and the action on a pair of morphisms $\rep{ l}{ r} : S \hto A$ and $\rep{ l'}{ r'} : T \hto B$ is given by:
   \begin{center}
@@
   \begin{align*}
-    \langle l, r \rangle \otimes \langle l', r' \rangle &:= \langle (M \otimes s_{A,N} \otimes B)(l \otimes l'), (r \otimes r')(M \otimes s_{A',N} \otimes B') \rangle
+    \rep{ l}{ r} \otimes \rep{ l'}{ r'} &:= \rep{(M \otimes s_{A,N} \otimes B)(l \otimes l')}{(r \otimes r')(M \otimes s_{A',N} \otimes B')}
   \end{align*}
@@
   \begin{align*}
-    \langle l_1, r_1 \rangle : (S_1, S_1') &\hto (S_2, S_2') \\
-    \langle l_2, r_2 \rangle : (S_2, S_2') &\hto (S_3, S_3') \\
-    \langle p_1, q_1 \rangle : (T_1, T_1') &\hto (T_2, T_2') \\
-    \langle p_2, q_2 \rangle : (T_2, T_2') &\hto (T_3, T_3')
-  \end{align*}
-  The string diagram for $(\langle l_2, r_2 \rangle \circ \langle l_1, r_1 \rangle) \otimes (\langle p_2, q_2 \rangle \circ \langle p_1, q_1 \rangle)$ is:
+    \rep{ l_1}{ r_1} : (S_1, S_1') &\hto (S_2, S_2') \\
+    \rep{ l_2}{ r_2} : (S_2, S_2') &\hto (S_3, S_3') \\
+    \rep{ p_1}{ q_1} : (T_1, T_1') &\hto (T_2, T_2') \\
+    \rep{ p_2}{ q_2} : (T_2, T_2') &\hto (T_3, T_3')
+  \end{align*}
+  The string diagram for $(\rep{ l_2}{ r_2} \circ \rep{ l_1}{ r_1}) \otimes (\rep{ p_2}{ q_2} \circ \rep{ p_1}{ q_1})$ is:
   \begin{center}
@@
   \end{center}
-  And for $(\langle l_2, r_2 \rangle \otimes \langle p_2, q_2 \rangle) \circ (\langle l_1, r_1 \rangle \otimes \langle p_1, q_1 \rangle)$ is:
+  And for $(\rep{ l_2}{ r_2} \otimes \rep{ p_2}{ q_2}) \circ (\rep{ l_1}{ r_1} \otimes \rep{ p_1}{ q_1})$ is:
   \begin{center}
@@
   % \end{align*}
-                                                       %                                                        with complements $M_1, M_2, N_1, N_2$ respectively.
-Then: \todo {(This is a mess.
-String diagram?)}
+  % with complements $M_1, M_2, N_1, N_2$ respectively. Then: \todo {(This is a mess. String diagram?)}
   % \begin{align*}
@@
     &\alpha_{(R, R'), (S, S'), (T, T')} \circ (f \otimes (S, S')) \otimes (T, T') \\
-    &= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1})  \circ (\langle l, r \rangle \otimes (S, S')) \otimes (T, T') \\
-    &= \langle\lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} \rangle  \circ \left\langle (l \otimes S) \otimes T, (r \otimes S') \otimes T' \right\rangle \\
-    &=\left\langle (M \otimes \lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T})((l \otimes S) \otimes T), ((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} ) \right\rangle \\
-    &=\left\langle (M \otimes \alpha_{R,S,T})((l \otimes S) \otimes T), ((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} )\right\rangle \\
-    &=\left\langle (l \otimes (S \otimes T))\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}(r \otimes (S' \otimes T')) \right\rangle \\
-    &= \langle (I \otimes l \otimes (S \otimes T)) \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}, (I \times r \otimes (S' \otimes T')) \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')}\rangle \\
-    &= \langle l \otimes (S \otimes T), r \otimes (S' \otimes T')\rangle \circ \left\langle \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')} \right\rangle \\
-    &= \langle l, r \rangle \otimes ((S, S') \otimes (T, T')) \circ \iota(\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}) \\
+    &= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1})  \circ (\rep{ l}{ r} \otimes (S, S')) \otimes (T, T') \\
+    &= \rep{\lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T}}{\alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'}}  \circ \rep{(l \otimes S) \otimes T}{ (r \otimes S') \otimes T'} \\
+    &= \rep{(M \otimes \lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T})((l \otimes S) \otimes T)}{((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} )} \\
+    &=\rep{(M \otimes \alpha_{R,S,T})((l \otimes S) \otimes T)}{((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} )} \\
+    &= \rep{(l \otimes (S \otimes T))\alpha_{Q,S,T}}{\alpha_{Q',S',T'}^{-1}(r \otimes (S' \otimes T'))} \\
+    &= \rep{(I \otimes l \otimes (S \otimes T)) \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}}{(I \times r \otimes (S' \otimes T')) \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')}} \\
+    &= \rep{l \otimes (S \otimes T)}{r \otimes (S' \otimes T')} \circ \rep{\lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}}{\alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')} } \\
+    &= \rep{ l}{ r} \otimes ((S, S') \otimes (T, T')) \circ \iota(\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}) \\
     &= f \otimes ((S, S') \otimes (T, T')) \circ \alpha_{(Q, Q'), (S, S'), (T, T')}
@@
 There is some further useful structure in $\Optic_\C$.
-\begin{proposition}
-\label{prop-costates}
+\begin{proposition}\label{prop-costates}
   The set of costates $(S, S') \hto (I, I)$ is isomorphic to $\C(S, S')$.
@@
 \begin{proof}
-  On objects this is simply $\Optic(F)(S, S') = (FS, FS')$. On a morphism $\langle l, r \rangle : (S, S') \to (A, A')$, we define
-  \begin{align*}
-    F\langle l, r \rangle := \langle \phi^{-1}_{M,A} (Fl), (Fr) \phi_{M,A'}\rangle
+  On objects this is simply $\Optic(F)(S, S') = (FS, FS')$. On a morphism $\rep{ l}{ r} : (S, S') \to (A, A')$, we define
+  \begin{align*}
+    F\rep{ l}{ r} := \rep{\phi^{-1}_{M,A} (Fl)}{(Fr) \phi_{M,A'}}
   \end{align*}
@@
 In this section we establish a universal property of the $\Optic$ construction.
-The idea is that every optic $\langle l, r\rangle : (S, S') \hto (A, A')$ consists of a morphism $S \to M \otimes A$ and the `formal dual' of a morphism $M \otimes A' \to S'$, composed with a `formal counit' that traces out the object $M$:
+The idea is that every optic $\rep{ l}{ r} : (S, S') \hto (A, A')$ consists of a morphism $S \to M \otimes A$ and the `formal dual' of a morphism $M \otimes A' \to S'$, composed with a `formal counit' that traces out the object $M$:
 \begin{center}
@@
   \end{align*}
-  And on morphisms $\langle l, r \rangle : S \hto A$ and $\langle l', r' \rangle : T \hto B$ by:
+  And on morphisms $\rep{ l}{ r} : S \hto A$ and $\rep{ l'}{ r'} : T \hto B$ by:
   \begin{center}
@@
     F\iota(f, g)
-    &= F(\langle \lambda_A^{-1} f, g \lambda_{A'} \rangle) \\
-    &= \langle \phi^{-1}_{I,A} (F(\lambda_A^{-1} f)), (F(g \lambda_{A'})) \phi_{I,A'}\rangle \\
-    &= \langle \phi^{-1}_{I,A} (F\lambda_A^{-1}) (Ff), (Fg)(F \lambda_{A'}) \phi_{I,A'}\rangle \\
-    &= \langle (\phi^{-1}_I \otimes FA) \phi^{-1}_{I,A} (F\lambda_A^{-1}) (Ff), (Fg)(F \lambda_{A'}) \phi_{I,A'} (\phi_I \otimes FA) \rangle \\
-    &= \langle \lambda_{FA}^{-1} (Ff), (Fg)\lambda_{FA'} \rangle \\
+    &= F(\rep{ \lambda_A^{-1} f}{ g \lambda_{A'}}) \\
+    &= \rep{\phi^{-1}_{I,A} (F(\lambda_A^{-1} f))}{(F(g \lambda_{A'})) \phi_{I,A'}} \\
+    &= \rep{ \phi^{-1}_{I,A} (F\lambda_A^{-1}) (Ff)}{(Fg)(F \lambda_{A'}) \phi_{I,A'}} \\
+    &= \rep{ (\phi^{-1}_I \otimes FA) \phi^{-1}_{I,A} (F\lambda_A^{-1}) (Ff)}{(Fg)(F \lambda_{A'}) \phi_{I,A'} (\phi_I \otimes FA)} \\
+    &= \rep{ \lambda_{FA}^{-1} (Ff)}{ (Fg)\lambda_{FA'}} \\
     &= \iota(Ff, Fg)
@@
     &= F(c_{S \otimes S'}) \\
-    &= F(\langle \rho_S^{-1}, \rho_{S'} \rangle) \\
-    &= \langle \phi^{-1}_{S,I} (F \rho_S^{-1}), (F \rho_{S'}) \phi_{S',I}\rangle \\
-    &= \langle (FS \otimes \phi_I^{-1}) \phi^{-1}_{S,I} (F \rho_S^{-1}), (F \rho_{S'}) \phi_{S',I} (FS \otimes \phi_I)\rangle \\
-    &= \langle \rho_{FS}^{-1}, \rho_{FS'} \rangle \\
+    &= F(\rep{ \rho_S^{-1}}{ \rho_{S'}}) \\
+    &= \rep{\phi^{-1}_{S,I} (F \rho_S^{-1})}{(F \rho_{S'}) \phi_{S',I}} \\
+    &= \rep{ (FS \otimes \phi_I^{-1}) \phi^{-1}_{S,I} (F \rho_S^{-1})}{ (F \rho_{S'}) \phi_{S',I} (FS \otimes \phi_I)} \\
+    &= \rep{ \rho_{FS}^{-1}}{ \rho_{FS'} } \\
     &= \varepsilon_{(FS, FS')}
@@
 \begin{proposition}\label{prop-optic-decompose}
-  Suppose $\langle l, r \rangle : (S, S') \hto (A, A')$ has complement $M$. Then
-  \begin{align*}
-    \langle l, r \rangle = ((A, I) \switched \varepsilon_{(M, I)} \switched (I, A'))(j(s_{M,A}l) \switched j(rs_{A',M})^*)
+  Suppose $\rep{ l}{ r} : (S, S') \hto (A, A')$ has complement $M$. Then
+  \begin{align*}
+    \rep{ l}{ r} = ((A, I) \switched \varepsilon_{(M, I)} \switched (I, A'))(j(s_{M,A}l) \switched j(rs_{A',M})^*)
   \end{align*}
@@
   \end{center}
-  so the two pairs of twists cancel, and we are left exactly with the diagram for $\langle l, r \rangle$.
+  so the two pairs of twists cancel, and we are left exactly with the diagram for $\rep{ l}{ r}$.
 \end{proof}
@@
 \begin{proof}
-  On objects, define $K(S, S') = FS \otimes (FS')^*$. Suppose $\langle l, r \rangle : (S, S') \hto (A, A')$ is an optic. By the previous Proposition,
-  \begin{align*}
-    \langle l, r \rangle = ((A, I) \switched \varepsilon_{(M, I)} \switched (I, A'))(j(s_{M,A}l) \switched j(rs_{M,A'})^*)
+  On objects, define $K(S, S') = FS \otimes (FS')^*$. Suppose $\rep{ l}{ r} : (S, S') \hto (A, A')$ is an optic. By the previous Proposition,
+  \begin{align*}
+    \rep{ l}{ r} = ((A, I) \switched \varepsilon_{(M, I)} \switched (I, A'))(j(s_{M,A}l) \switched j(rs_{M,A'})^*)
   \end{align*}
@@
   \begin{align*}
-    K\langle l, r \rangle = (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F(s_{M,A}l) \otimes (F(rs_{A', M}))^* )
+    K\rep{ l}{ r} = (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F(s_{M,A}l) \otimes (F(rs_{A', M}))^* )
   \end{align*}
@@
   \begin{align*}
-    \langle (f \otimes A) l, r \rangle = \langle l, r (f \otimes A') \rangle
+    \rep{ (f \otimes A) l}{ r} = \rep{ l}{ r (f \otimes A')}
   \end{align*}
@@
   \begin{align*}
-    K\langle (f \otimes A) l, r \rangle
+    K\rep{ (f \otimes A) l}{ r}
     &= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F(s_{M,A}(f \otimes A)l) \otimes (F(rs_{A',M}))^* ) \\
@@
     &= (FA \otimes \varepsilon_{FN} \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(r(f \otimes A')s_{A',N}))^* ) \\
-    &= K\langle  l, r (f \otimes A') \rangle
+    &= K\rep{  l}{ r (f \otimes A')}
   \end{align*}
@@
 
-\todo{In this section I am using semicolon to mean composition in diagrammatic order. Should I also switch the comma in $\langle l, r \rangle$ to be a $\mid$?}
+\todo{In this section I am using semicolon to mean composition in diagrammatic order. Should I also switch the comma in $\rep{ l}{ r}$ to be a $\mid$?}
 
 For a fixed $M \in \M$, there is a map $\C(S, M A) \times \C(M A, S) \to \C(S, S)$ given by composition.
-This induces a map $\outside : \Optic_\M(S, A) \to \C(S, S)$, given equationally by $\outside(\langle l, r \rangle) = l ; r$
+This induces a map $\outside : \Optic_\M(S, A) \to \C(S, S)$, given equationally by $\outside(\rep{ l}{ r}) = l ; r$
 
@@
 \begin{align*}
-  \once(\langle l, r \rangle) &= \langle l, \id_{MA}, r \rangle \\
-  \twice(\langle l, r \rangle) &= \langle l, r;l, r \rangle
+  \once(\rep{ l}{ r}) &= \repthree{ l}{ \id_{MA}}{ r} \\
+  \twice(\rep{ l}{ r} \rangle) &= \repthree{l}{r;l}{r}
 \end{align*}
@@
   \begin{align*}
-    \outside(\langle \lambda^{-1}_S, \lambda_{S} \rangle) &= \lambda_{S} \lambda^{-1}_S = \id_S \\
+    \outside(\rep{ \lambda^{-1}_S}{ \lambda_{S}}) &= \lambda_{S} \lambda^{-1}_S = \id_S \\
     \intertext{and}
-    \once(\langle \lambda^{-1}_S, \lambda_{S} \rangle)
-                                                          &= \langle \lambda^{-1}_S, \id_{IA}, \lambda_{S} \rangle \\
-                                                          &= \langle \lambda^{-1}_S, \lambda_{S};\lambda^{-1}_S , \lambda_{S} \rangle \\
-                                                          &= \twice(\langle \lambda^{-1}_S, \lambda_{S} \rangle)
-  \end{align*}
-
-  Suppose we have two lawful optics $\langle l, r \rangle : R \hto S$ and $\langle l', r' \rangle : S \hto A$, where $l : R \to MS$ and $l' : S \to NA$.
-We must show that $\langle (Ml')l, r (Mr')  \rangle$ is also a lawful optic.
+    \once(\rep{ \lambda^{-1}_S}{ \lambda_{S}})
+                                                          &= \repthree{\lambda^{-1}_S}{\id_{IA}}{\lambda_{S}} \\
+                                                          &= \repthree{\lambda^{-1}_S}{\lambda_{S};\lambda^{-1}_S}{\lambda_{S}} \\
+                                                          &= \twice(\rep{ \lambda^{-1}_S}{ \lambda_{S}})
+  \end{align*}
+
+  Suppose we have two lawful optics $\rep{ l}{ r} : R \hto S$ and $\rep{ l'}{ r'} : S \hto A$, where $l : R \to MS$ and $l' : S \to NA$.
+We must show that $\rep{ (Ml')l}{ r (Mr') }$ is also a lawful optic.
 The first equation is straightforward:
   \begin{align*}
-    \outside(\langle l; (Ml'),(Mr') ; r   \rangle)
+    \outside(\rep{ l; (Ml')}{(Mr') ; r  })
     &= l ; Ml' ; Mr' ; r \\
@@
   For the second, we must show
-  \[ \langle l;(Ml'), (Mr'); r;l;(Ml') , (Mr') ; r  \rangle = \langle l;(Ml'), \id_{MNA} , (Mr') ; r  \rangle. \]
-
-  We do this by showing that, in some sense, the expressions in the above equation respect the coend relations defining the codomains of $\once(\langle l, r \rangle)$ and $\once(\langle l', r' \rangle)$.
-
-  So consider the generating relation $\langle l;\phi_S, c, r \rangle = \langle l, \phi_S ; c, r \rangle$ in \[\int^{M_1, M_2 \in \M} \C(R, M_1 S) \times \C(M_1 S, M_2 S) \times \C(M_2 S, R).\]
+  \[ \repthree{ l;(Ml')}{ (Mr'); r;l;(Ml')}{(Mr') ; r } = \rep{ l;(Ml')}{ \id_{MNA}}{ (Mr') ; r }. \]
+
+  We do this by showing that, in some sense, the expressions in the above equation respect the coend relations defining the codomains of $\once(\rep{ l}{ r})$ and $\once(\rep{ l'}{ r'})$.
+
+  So consider the generating relation $\repthree{ l;\phi_S}{ c}{r} = \rep{ l}{ \phi_S ; c}{r}$ in \[\int^{M_1, M_2 \in \M} \C(R, M_1 S) \times \C(M_1 S, M_2 S) \times \C(M_2 S, R).\]
   This implies that
   \begin{align*}
-    \langle l;\phi_S;(Ml'), (Mr'); c ;(Ml') , (Mr') ; r \rangle
-    &= \langle l;(Ml');\phi_{NA}, (Mr'); c ;(Ml') , (Mr') ; r \rangle && \text{(functoriality)} \\
-    &= \langle l;(Ml'), \phi_{NA};(Mr'); c ;(Ml') , (Mr') ; r \rangle && \text{(coend relation)} \\
-    &= \langle l;(Ml'), (Mr');\phi_{S}; c ;(Ml') , (Mr') ; r \rangle && \text{(functoriality)}
-  \end{align*}
-  And similarly for the other generating relation, $\langle l, c;\phi_S, r \rangle = \langle l,  c, \phi_S; r \rangle$.
-
-  Therefore, the chain of relations proving $\langle l, r;l, r \rangle = \langle l, \id_{MA}, r \rangle$ can be replicated to show
-  \begin{align*}
-    \langle l;(Ml'), (Mr');r;l;(Ml') , (Mr') ; r \rangle &= \langle l;(Ml'), (Mr');\id_{MA};(Ml') , (Mr') ; r \rangle,
-  \end{align*}
-  which is equal to $\langle l;(Ml'), M(r'l'), (Mr') ; r \rangle$.
-
-  Similarly, a generating relation $\langle l';\psi_A, c', r' \rangle = \langle l', \psi_A ; c', r' \rangle$ in \[\int^{N_1, N_2 \in \M} \C(S, N_1 A) \times \C(N_1 A, N_2 A) \times \C(M_2 A, S)\]
+    \rep{ l;\phi_S;(Ml')}{ (Mr'); c ;(Ml')}{(Mr') ; r}
+    &= \rep{ l;(Ml');\phi_{NA}}{ (Mr'); c ;(Ml')}{(Mr') ; r} && \text{(functoriality)} \\
+    &= \rep{ l;(Ml')}{ \phi_{NA};(Mr'); c ;(Ml')}{(Mr') ; r} && \text{(coend relation)} \\
+    &= \rep{ l;(Ml')}{ (Mr');\phi_{S}; c ;(Ml')}{(Mr') ; r} && \text{(functoriality)}
+  \end{align*}
+  And similarly for the other generating relation, $\rep{l}{ c;\phi_S}{r } = \rep{l}{c}{\phi_S; r }$.
+
+  Therefore, the chain of relations proving $\rep{l}{ r;l}{r } = \rep{l}{ \id_{MA}}{ r }$ can be replicated to show
+  \begin{align*}
+    \rep{l;(Ml')}{ (Mr');r;l;(Ml')}{(Mr') ; r } &= \rep{l;(Ml')}{ (Mr');\id_{MA};(Ml')}{ (Mr') ; r },
+  \end{align*}
+  which is equal to $\rep{l;(Ml')}{ M(r'l')}{ (Mr') ; r }$.
+
+  Similarly, a generating relation $\rep{l';\psi_A}{ c'}{ r' } = \rep{l'}{ \psi_A ; c'}{ r' }$ in \[\int^{N_1, N_2 \in \M} \C(S, N_1 A) \times \C(N_1 A, N_2 A) \times \C(M_2 A, S)\]
   implies that
   \begin{align*}
-    \langle l;M(l';\psi_A), Mc', (Mr') ; r \rangle
-    &= \langle l;Ml';M\psi_A, Mc', (Mr') ; r \rangle \\
-    &= \langle l;Ml', M\psi_A ; Mc', (Mr') ; r \rangle \\
-    &= \langle l;Ml', M(\psi_A;c'), (Mr') ; r \rangle
-  \end{align*}
-  So again we can replicate the chain of relations proving $\langle l', r';l', r' \rangle = \langle l', \id_{MA}, r' \rangle$ to show that
-  \[\langle l;(Ml'), M(r'l'), (Mr') ; r \rangle = \langle l;(Ml'), \id_{MNA}, (Mr') ; r \rangle \]
+    \rep{l;M(l';\psi_A)}{ Mc'}{ (Mr') ; r }
+    &= \rep{l;Ml';M\psi_A}{ Mc'}{ (Mr') ; r } \\
+    &= \rep{l;Ml'}{ M\psi_A ; Mc'}{ (Mr') ; r } \\
+    &= \rep{l;Ml'}{ M(\psi_A;c')}{ (Mr') ; r }
+  \end{align*}
+  So again we can replicate the chain of relations proving $\rep{l'}{ r';l'}{ r' } = \rep{l'}{ \id_{MA}}{ r' }$ to show that
+  \[\rep{l;(Ml')}{ M(r'l')}{ (Mr') ; r } = \rep{l;(Ml')}{ \id_{MNA}}{ (Mr') ; r } \]
 
@@
 \begin{proof}
-  If $p = \langle l, r \rangle$ is lawful,
+  If $p = \rep{l}{ r }$ is lawful, \todo{todo}
 \end{proof}
@@
 \begin{proposition}
-  Let $\langle l, r \rangle : S \hto A$ be an optic. If $l;r = \id_S$ and $r;l = \phi A$ for some $\phi : M \to M$ in $\M$, then $\langle l, r \rangle$ is a lawful optic.
-\end{proposition}
-\begin{proof}
-  The $\outside(\langle l, r \rangle) = l;r = \id_S$ is exactly the first condition. And for the second, we verify:
-  \begin{align*}
-    \twice(\langle l, r \rangle)
-    &= \langle l, r;l, r \rangle \\
-    &= \langle l, \phi A, r \rangle && \text{($r;l = \phi A$)}\\
-    &= \langle l (\phi A), \id_{MA}, r \rangle && \text{(coend relation)} \\
-    &= \langle l;r;l, \id_{MA}, r \rangle && \text{($r;l = \phi A$ again)}\\
-    &= \langle l, \id_{MA}, r \rangle  && \text{($l;r = \id_S$)}\\
-    &= \once(\langle l, r \rangle)
+  Let $\rep{l}{ r } : S \hto A$ be an optic. If $l;r = \id_S$ and $r;l = \phi A$ for some $\phi : M \to M$ in $\M$, then $\rep{l}{ r }$ is lawful.
+\end{proposition}
+\begin{proof}
+  The $\outside(\rep{l}{ r }) = l;r = \id_S$ is exactly the first condition. And for the second, we verify:
+  \begin{align*}
+    \twice(\rep{l}{ r })
+    &= \rep{l}{ r;l}{ r } \\
+    &= \rep{l}{ \phi A}{ r } && \text{($r;l = \phi A$)}\\
+    &= \rep{l (\phi A)}{ \id_{MA}}{ r } && \text{(coend relation)} \\
+    &= \rep{l;r;l}{ \id_{MA}}{ r } && \text{($r;l = \phi A$ again)}\\
+    &= \rep{l}{ \id_{MA}}{ r }  && \text{($l;r = \id_S$)}\\
+    &= \once(\rep{l}{ r })
   \end{align*}
@@
 
-Let $\inside : \Optic_\M(S, A) \to \int^{M \in \M} \C(M A, M A)$ be the map induced by $\inside(\langle l, r \rangle) = \langle r ; l \rangle$.
+Let $\inside : \Optic_\M(S, A) \to \int^{M \in \M} \C(M A, M A)$ be the map induced by $\inside(\rep{l}{ r }) = \langle r ; l \rangle$.
 We might ask that instead of requiring $r;l = \phi A$ exactly, we have $\langle r ; l \rangle = \langle \phi A \rangle$ in $\int^{M \in \M} \C(M A, M A)$.
@@
   Suppose $p : S \hto A$ satisfies $\outside(p) = \id_S$ and $\inside(p) = \langle \phi A \rangle$.
-Then there exists a representative $\langle l, r \rangle$ such that $l ; r = \psi A$ on the nose for some (possibly different) $\psi : M \to M$.
+Then there exists a representative $\rep{l}{ r }$ such that $l ; r = \psi A$ on the nose for some (possibly different) $\psi : M \to M$.
 \end{proposition}
@@
 
-  Similarly two representatives $\langle l, r \rangle : S \hto A$ and $\langle l', r' \rangle : S \hto A$ with complements $M$ and $N$ respectively are identified when there exists a $\phi : M \to N$ such that
+  Similarly two representatives $\rep{l}{ r } : S \hto A$ and $\rep{l'}{ r' } : S \hto A$ with complements $M$ and $N$ respectively are identified when there exists a $\phi : M \to N$ such that
   \[
@@
 
-  Now suppose $p = \langle l, r \rangle : S \hto A$ is a lawful optic, so $rl = \id_S$ and $\langle lr \rangle = \langle \psi A\rangle$.
+  Now suppose $p = \rep{l}{ r } : S \hto A$ is a lawful optic, so $rl = \id_S$ and $\langle lr \rangle = \langle \psi A\rangle$.
 There therefore must exist a finite chain of relations $lr = u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n = \psi A$.
@@
   \]
-  Define $l' = \phi_A l$ and $r' = rk$. The above diagram is a witness that $\langle l, r \rangle = \langle l', r' \rangle$ as an optic $S \hto A$.
+  Define $l' = \phi_A l$ and $r' = rk$. The above diagram is a witness that $\rep{l}{ r } = \rep{l'}{ r' }$ as an optic $S \hto A$.
 
@@
 
-  A symmetric argument shows that if instead the relation faces leftward, so $lr \leftsquigarrow g$, there exists $l'$ and $r'$ so that $\langle l, r \rangle = \langle l', r' \rangle$ and $l'r' = u_2^2$.
-
-  We can now inductively apply the above argument to the shorter chain \[l'r' = u_1^2 \leftrightsquigarrow \dots \leftrightsquigarrow u_n^2 \leftrightsquigarrow (\psi A)^2 = \psi^2 A,\] obtained by squaring each morphism in the original chain, until we are left with a representative $\langle l^*, r^* \rangle$ such that $l^*r^* = \psi^N A$, for some $N>0$.
-This pair $\langle l^*, r^* \rangle$ is the required representative.
+  A symmetric argument shows that if instead the relation faces leftward, so $lr \leftsquigarrow g$, there exists $l'$ and $r'$ so that $\rep{l}{ r } = \rep{l'}{ r' }$ and $l'r' = u_2^2$.
+
+  We can now inductively apply the above argument to the shorter chain \[l'r' = u_1^2 \leftrightsquigarrow \dots \leftrightsquigarrow u_n^2 \leftrightsquigarrow (\psi A)^2 = \psi^2 A,\] obtained by squaring each morphism in the original chain, until we are left with a representative $\rep{l^*}{ r^* }$ such that $l^*r^* = \psi^N A$, for some $N>0$.
+This pair $\rep{l^*}{ r^* }$ is the required representative.
 \end{proof}
@@
 
-Explicitly this isomorphism states that, given an optic $\langle l, r \rangle : (S, S') \hto (A, A')$, the corresponding element of $\mathbb{O}((S, S'), (A, A'))$ is the pair $(\fget, \fput)$, where $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
-In the other direction, given $(\fget, \fput)$, the corresponding optic has representative $\langle [\id_S, \fget],  \fput \rangle$.
+Explicitly this isomorphism states that, given an optic $\rep{l}{ r } : (S, S') \hto (A, A')$, the corresponding element of $\mathbb{O}((S, S'), (A, A'))$ is the pair $(\fget, \fput)$, where $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
+In the other direction, given $(\fget, \fput)$, the corresponding optic has representative $\rep{[\id_S, \fget]}{\fput}$.
 
@@
   \begin{align*}
-    \Phi(\langle l, c, r \rangle) = (&\pi_2 l, \\
+    \Phi(\repthree{l}{ c}{ r }) = (&\pi_2 l, \\
                                    &\pi_2 c (\pi_1 l \times A), \\
@@
   \end{align*}
-  Now suppose we are given a lens $(\fget, \fput)$, which in coend form is $\langle [\id_S, \fget],  \fput \rangle$. Evaluating $\outside$ on this gives:
-  \begin{align*}
-    \outside(\langle [\id_S, \fget],  \fput \rangle) = \fput [\id_S, \fget]
+  Now suppose we are given a lens $(\fget, \fput)$, which in coend form is $\rep{[\id_S, \fget]}{\fput}$. Evaluating $\outside$ on this gives:
+  \begin{align*}
+    \outside(\rep{[\id_S, \fget]}{\fput}) = \fput [\id_S, \fget]
   \end{align*}
@@
   \begin{alignat*}{3}
-    \Phi(\once(\langle [\id_S, \fget],  \fput \rangle)) &=
-    \Phi(&&\langle [\id_S, \fget], \id_{S \times A}, \fput \rangle) \\
+    \Phi(\once(\rep{[\id_S, \fget]}{ \fput})) &=
+    \Phi(&&\repthree{[\id_S, \fget]}{\id_{S \times A}}{\fput}) \\
     &= (&&\pi_2 [\id_S, \fget], \\
@@
     %%%%
-    \Phi(\twice(\langle [\id_S, \fget],  \fput \rangle)) &=
-    \Phi(&&\langle [\id_S, \fget], [\id_S, \fget]\fput, \fput \rangle) \\
+    \Phi(\twice(\rep{[\id_S, \fget]}{ \fput})) &=
+    \Phi(&&\repthree{[\id_S, \fget]}{[\id_S, \fget]\fput}{\fput}) \\
     &= (&&\pi_2 [\id_S, \fget], \\
@@
   \]
-  is a witness that $\langle \fput (i \times A), [j,\fget] \rangle = \langle \fput, [\id_S, \fget] \rangle$ as elements of $\Optic_\M(S, A)$.
+  is a witness that $\rep{\fput (i \times A)}{ [j,\fget] } = \rep{\fput}{ [\id_S, \fget] }$ as elements of $\Optic_\M(S, A)$.
 \end{proof}
@@
 For an optic, the corresponding element of $\mathbb{O}((S, S'), (A, A'))$ will be called $\funzip$.
-The above isomorphism sends $\funzip$ to the element $\langle \funzip , \ev_{A', S'} \rangle$, where $\ev_{A', S'} : \homC(A',S') \otimes A' \to S'$ is the evaluation map.
-In the other direction, given $\langle l, r \rangle$ we have $\funzip = (\tilde r \otimes A)l$ where $\tilde r : M \to \homC(A', S')$ denotes the transpose of $r$.
+The above isomorphism sends $\funzip$ to the element $\rep{\funzip }{ \ev_{A', S'} }$, where $\ev_{A', S'} : \homC(A',S') \otimes A' \to S'$ is the evaluation map.
+In the other direction, given $\rep{l}{ r }$ we have $\funzip = (\tilde r \otimes A)l$ where $\tilde r : M \to \homC(A', S')$ denotes the transpose of $r$.
 
@@
   \end{align*}
-  which evaluated on an element $\langle l, c, r \rangle$ is given by
-  \begin{align*}
-    \Phi(\langle l, c, r \rangle) &= (\widetilde{(\tilde{r} \otimes A)c} \otimes A)l
-  \end{align*}
-  Now suppose we are given an optic $p$ with corresponding element of $\mathbb{O}(S, A)$ is $\funzip$.
-Then $\outside(\langle \funzip , \ev_{A, S} \rangle) = \ev_{A, S} \; \funzip$, giving the first law.
+  which evaluated on an element $\repthree{l}{ c}{r }$ is given by
+  \begin{align*}
+    \Phi(\repthree{l}{ c}{r}) &= (\widetilde{(\tilde{r} \otimes A)c} \otimes A)l
+  \end{align*}
+  Now suppose we are given an optic $p$ with corresponding element of $\mathbb{O}(S, A)$ is $\funzip$. Then $\outside(\rep{\funzip }{ \ev_{A, S} }) = \ev_{A, S} \; \funzip$, giving the first law.
 
@@
   \begin{align*}
-    \Phi(\once(\langle \funzip , \ev_{A, S} \rangle))
-    &= \Phi(\langle \funzip , \id_{\homC(A,S) \otimes A}, \ev_{A, S} \rangle) \\
+    \Phi(\once(\rep{\funzip }{ \ev_{A, S} }))
+    &= \Phi(\repthree{\funzip }{ \id_{\homC(A,S) \otimes A}}{\ev_{A, S} }) \\
     &= (\widetilde{(\tilde{\ev_{A, S}} \otimes A)\id_{\homC(A,S) \otimes A}} \otimes A)\funzip \\
     &= (\coev_{\homC(A, S), A} \otimes A)\funzip \\
-    \Phi(\twice(\langle \funzip , \ev_{A, S} \rangle))
-    &= \Phi(\langle \funzip , \funzip \; \ev_{A, S}, \ev_{A, S} \rangle) \\
+    \Phi(\twice(\rep{\funzip }{ \ev_{A, S} }))
+    &= \Phi(\repthree{\funzip }{ \funzip \; \ev_{A, S}}{ \ev_{A, S} }) \\
     &= (\widetilde{(\tilde{\ev_{A, S}} \otimes A)(\funzip \; \ev_{A, S})} \otimes A)\funzip \\
@@
 \end{align*}
-If we are given a prism $\langle l, r \rangle : (S, S') \hto (A, A')$ then associated $\freview$ and $\fmatching$ morphisms are given by $\freview = r \inr$ and $\fmatching = (r\inl \sqcup A)l$
+If we are given a prism $\rep{l}{ r } : (S, S') \hto (A, A')$ then associated $\freview$ and $\fmatching$ morphisms are given by $\freview = r \inr$ and $\fmatching = (r\inl \sqcup A)l$
 
@@
 \begin{proposition}
-  An iso $\langle l, r \rangle$ is lawful iff (as expected) $l$ and $r$ are mutual inverses.
+  An iso $\rep{l}{ r }$ is lawful iff (as expected) $l$ and $r$ are mutual inverses.
 \end{proposition}
@@
   \[ \C(S, A) \times \C(A, A) \times \C(A, S) \]
-  The condition $\outside(\langle l, r \rangle) = \id_S$ is the claim that $rl = \id_S$, and $\once(\langle l, r \rangle) = (l, \id_A, r)$ is equal to $\twice(\langle l, r \rangle) = (l, lr, r)$ iff $lr = \id_A$.
+  The condition $\outside(\rep{l}{ r }) = \id_S$ is the claim that $rl = \id_S$, and $\once(\rep{l}{ r }) = (l, \id_A, r)$ is equal to $\twice(\rep{l}{ r }) = (l, lr, r)$ iff $lr = \id_A$.
 \end{proof}
@@
   \end{align*}
-  that sends an object $D \in \D$ and optic $\langle l, r \rangle : F \hto G$ in $\Optic_{[\D, \C]}$ to the optic $\langle l_D, r_D \rangle : FD \hto GD$ in $\Optic_\C$.
+  that sends an object $D \in \D$ and optic $\rep{l}{ r } : F \hto G$ in $\Optic_{[\D, \C]}$ to the optic $\rep{l_D}{ r_D } : FD \hto GD$ in $\Optic_\C$.
 \end{proposition}
@@
 %
-           %            One issue with the definition of optic given in the last section is that it could be difficult to determine when two optics $\langle l, r \rangle, \langle l', r' \rangle : S \hto A$ are equal.
-For some choices of $\M$, however, we can reduce a zigzag of relations to a single one.
+% One issue with the definition of optic given in the last section is that it could be difficult to determine when two optics $\rep{l}{ r }, \langle l', r' \rangle : S \hto A$
+are equal. For some choices of $\M$, however, we can reduce a zigzag of relations to a single one.
 %
@@
 %   \end{align*}
-                                   %                                    Now by assumption, $\pi_1 l : S \to M$ is an epi, so has a retraction $f : M \to S$.
-The claim is that $\phi = \pi_1 l' f$ is the required morphism $M \to N$.
+%   Now by assumption, $\pi_1 l : S \to M$ is an epi, so has a retraction $f : M \to S$. The claim is that $\phi = \pi_1 l' f$ is the required morphism $M \to N$.
 %
@@
 %   \end{align*}
-                                                      %                                                       as required.
-The equation relating $l$ and $l'$ follows immediately as they are the inverses of $r$ and $r'$.
+%   as required. The equation relating $l$ and $l'$ follows immediately as they are the inverses of $r$ and $r'$.
 % \end{proof}
@@
 %   \]
-                                                       %                                                        To construct a morphism $M \to M_i$ we have to perform a slightly awkward switchback maneuver.
-First note that $\phi_A$ is a split monomorphism, as $(l r_{i-1}) \phi_A = lr = \id_{MA}$.
-                                                       %
-                                                       %                                                        By condition (SM), therefore, there is a morphism $\gamma : M_{i-1} \to M$ such that $\gamma_A \phi_A = \id_{MA}$.
-But now, the composite $\gamma_A \psi_A : M_i \to M$ is a split epimorphism:
+%   To construct a morphism $M \to M_i$ we have to perform a slightly awkward switchback maneuver. First note that $\phi_A$ is a split monomorphism, as $(l r_{i-1}) \phi_A = lr = \id_{MA}$.
+%
+%   By condition (SM), therefore, there is a morphism $\gamma : M_{i-1} \to M$ such that $\gamma_A \phi_A = \id_{MA}$. But now, the composite $\gamma_A \psi_A : M_i \to M$ is a split epimorphism:
 %   \begin{align*}
@@
   \end{align*}
-  for all $C, D \in \C$ and $N \in \M$. Equationally, this is $\alpha_{A,B,M}(\langle l, p, r \rangle) = \langle Ml, p, Mr \rangle$.
+  for all $C, D \in \C$ and $N \in \M$. Equationally, this is $\alpha_{A,B,M}(\repthree{l}{ p}{ r} ) = \rep{Ml}{ p}{ Mr} $.
 \end{definition}
@@
 \begin{proof}
-  For any $P \in \Prof(\C, \C)$, there is a map $\eta : P \hto U \Phi_\M P$, given by $\eta(p) = \langle \id_A, p, \id_B \rangle$.
-
-  Suppose we have an element $\langle l, p, r \rangle \in \Pastro_\M P(A,B)$. Then one can check that this element is equal to
-  \begin{align*}
-    \langle l, p, r \rangle = \Pastro_\M P(l, r) \alpha_{A, B, M} \; \eta(p)
+  For any $P \in \Prof(\C, \C)$, there is a map $\eta : P \hto U \Phi_\M P$, given by $\eta(p) = \repthree{\id_A}{ p}{\id_B }$.
+
+  Suppose we have an element $\rep{l}{ p}{r} \in \Pastro_\M P(A,B)$. Then one can check that this element is equal to
+  \begin{align*}
+    \repthree{l}{ p}{r } = \Pastro_\M P(l, r) \alpha_{A, B, M} \; \eta(p)
   \end{align*}
@@
   \begin{align*}
-    \hat{f}(\langle l, p, r) \rangle &= \hat{f}(\Pastro_\M P(l, r) \alpha_{A, B, M} \; \eta(p)) \\
+    \hat{f}(\rep{l}{ p}{r }) &= \hat{f}(\Pastro_\M P(l, r) \alpha_{A, B, M} \; \eta(p)) \\
                                      &=T(l, r) \; \beta_{A, B, N} \; f(p)
@@
   \begin{align*}
-    \hat{f}\alpha_{A,B,N}(\langle l, p, r \rangle)
-    &= \hat{f}(\langle Nl, p, Nr \rangle) \\
+    \hat{f}\alpha_{A,B,N}(\rep{l}{ p}{r })
+    &= \hat{f}(\rep{Nl}{ p}{ Nr }) \\
     &= T(Nl, Nr) \; \beta_{A, B, NM} \; f(p) \\
@@
     &= \beta_{A,B,N} T(l, r) \; \beta_{A, B, M} \; f(p) \\
-    &= \beta_{A,B,N} \hat{f} (\langle l, p, r \rangle)
+    &= \beta_{A,B,N} \hat{f} (\rep{l}{ p}{r })
   \end{align*}
@@
 \begin{corollary}
-  A profunctor optic $p$ is determined by its component at $\Pastro_\M E_A$, and furthermore, this component is determined by its value on $\langle \id_A, \id_A, \id_A, \id_A \rangle \in (U \Pastro_\M E_A)(A, A)$.
+  A profunctor optic $p$ is determined by its component at $\Pastro_\M E_A$, and furthermore, this component is determined by its value on $\repfour{\id_A}{ \id_A}{\id_A}{\id_A } \in (U \Pastro_\M E_A)(A, A)$.
 \end{corollary}
@@
   This is the content of the first two isomorphisms above.
-Explicitly, suppose $\hat{p} = \langle l, r \rangle$ with $l : S \to MA$ and $r : MA \to S$.
+Explicitly, suppose $\hat{p} = \rep{l}{ r }$ with $l : S \to MA$ and $r : MA \to S$.
 Then for any Tambara module $P$, the component of $p$ at $P$ is
@@
   \[
-    p_{\Pastro_\M E_A}(\langle \id_A, \id_A, \id_A, \id_A \rangle) = \langle l, \id_A, \id_A, r \rangle
+    p_{\Pastro_\M E_A}(\repfour{\id_A}{ \id_A}{ \id_A}{\id_A }) = \repfour{l}{ \id_A}{\id_A}{ r }
   \]
@@
 \begin{align*}
-  \Delta((f, g)) &= \langle f, \id_A, \id_A, g \rangle \\
+  \Delta((f, g)) &= \repfour{f}{ \id_A}{\id_A}{ g}  \\
   \varepsilon((f, g)) &= gf
@@
 \begin{align*}
-  \Delta(\langle l, r \rangle) &= \langle l, lr, r \rangle \\
-  \varepsilon(\langle l, r \rangle) &= rl
+  \Delta(\rep{l}{ r }) &= \repthree{l}{lr}{r } \\
+  \varepsilon(\rep{l}{ r }) &= rl
 \end{align*}
@@
 %% \begin{proposition}
-                        %%                           Let $\C = \Set$ and suppose $p : S \hto A$ is a lens such that the associated natural transformation $p : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal.
-Then $p$ is lawful.
+%%   Let $\C = \Set$ and suppose $p : S \hto A$ is a lens such that the associated natural transformation $p : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal. Then $p$ is lawful.
 %% \end{proposition}
@@
 
-Prelenses that satisfy the first two laws correspond to pairs $\langle l, r \rangle$ such that $rl = \id_S$ and $\pi_2lr = \pi_2$.
+Prelenses that satisfy the first two laws correspond to pairs $\rep{l}{ r }$ such that $rl = \id_S$ and $\pi_2lr = \pi_2$.
 \todo{prove?} This condition seems unavoidably tied to the product structure on $\C$; it is not clear whether this weakened notion of lens can be generalised to other optics.
@@
 
-\todo{Go back and fix all the $\langle \rangle$s to use $\mid$.}
-
 \bibliographystyle{alpha}

### 2018-06-12 paper.tex
Fill in some little bits

@@
 
+\newcommand{\lenslib}{\texttt{lens}}
+
 \newcommand{\Pastro}{\Phi}
@@
 
-\newcommand{\rep}[2]{{\ensuremath \langle #1 \mid #2 \rangle}}
+\newcommand{\rep}[2]{{\ensuremath \left\langle #1 \mid #2 \right\rangle}}
 \newcommand{\repthree}[3]{{\ensuremath \langle #1 \mid #2 \mid #3 \rangle}}
@@
 
-Graphically, this is placing the first optic into the hole of the second:
+Graphically, this is substituting the first optic for the hole of the second:
 \begin{center}
@@
 This dashed line above the diagram represents the unit object.
-As is standard, we will elide the unit object and unitors in future diagrams unless they are necessary.
-The diagram for the identity becomes:
+It is common in string diagrams to omit unitors and the unit object unless they are necessary to make sense of the diagram.
+In this case, we would draw:
 \begin{center}
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop-optic-is-cat}
   The above data form a category $\Optic_\C$.
@@
 \begin{proposition}
-  There is a functor $\iota : \C \times \C^\op \to \Optic_\C$, which is given on objects by $\iota(S, S') = (S, S')$ and for a morphism $(f, g) : (S, S') \to (A, A')$ by $\iota(f, g) = \rep{ \lambda_A^{-1} f}{ g \lambda_{A'}}$.
+  There is a functor $\iota : \C \times \C^\op \to \Optic_\C$, which is given on objects by $\iota(S, S') = (S, S')$ and for a morphism $(f, g) : (S, S') \to (A, A')$ by $\iota(f, g) = \rep{\lambda_A^{-1} f}{g \lambda_{A'}}$.
 \end{proposition}
@@
 
-  This preserves identities, as the identity on an object $(S, S')$ in $\Optic_\M$ is defined to be exactly $\rep{ \lambda^{-1}_S}{ \lambda_{S'}}$.
+  This preserves identities, as the identity on an object $(S, S')$ in $\Optic_\M$ is defined to be exactly $\rep{\lambda^{-1}_S}{\lambda_{S'}}$.
 To check functoriality, suppose we have $(f, g) : (S, S') \to (A, A')$ and $(f', g') : (A, A') \to (B, B')$ in $\C \times \C^\op$.
@@
     \iota(f', g') \circ \iota(f, g)
-    &= \rep{ \lambda^{-1}_B f'}{ g' \lambda_{B'}} \circ \rep{ \lambda^{-1}_A f}{ g \lambda_{A'}} \\
-    &= \rep{ (I\otimes (\lambda^{-1}_B f'))\lambda^{-1}_A f}{ g \lambda_{A'} (I\otimes (g' \lambda_{B'})} && \text{(By definition of $\circ$)}\\
-    &= \rep{ (I \otimes \lambda^{-1}_B) (I \otimes f')\lambda^{-1}_A f}{ g \lambda_{A'} (I \otimes g')(I\otimes \lambda_{B'}} && \text{(Functoriality of $I \otimes -$)}\\
-    &= \rep{ (I\otimes \lambda^{-1}_B) \lambda^{-1}_B f' f}{ g g' \lambda_{B'} (I\otimes \lambda_{B'}} && \text{(Naturality of $\lambda$)}\\
-    &= \rep{ (\lambda^{-1}_I \otimes B) \lambda^{-1}_B f' f}{ g g' \lambda_{B'} (\lambda_I \otimes B'} && \text{(Unitality of action)} \\
-    &= \rep{ \lambda^{-1}_B f' f}{ g g' \lambda_{B'} (\lambda_I \otimes B') (\lambda^{-1}_I \otimes B')} && \text{(Coend relation)}  \\
-    &= \rep{ \lambda^{-1}_B f'f}{ g g' \lambda_{B'}} \\
+    &= \rep{\lambda^{-1}_B f'}{g' \lambda_{B'}} \circ \rep{\lambda^{-1}_A f}{g \lambda_{A'}} \\
+    &= \rep{(I\otimes (\lambda^{-1}_B f'))\lambda^{-1}_A f}{g \lambda_{A'} (I\otimes (g' \lambda_{B'})} && \text{(By definition of $\circ$)}\\
+    &= \rep{(I \otimes \lambda^{-1}_B) (I \otimes f')\lambda^{-1}_A f}{g \lambda_{A'} (I \otimes g')(I\otimes \lambda_{B'}} && \text{(Functoriality of $I \otimes -$)}\\
+    &= \rep{(I\otimes \lambda^{-1}_B) \lambda^{-1}_B f' f}{g g' \lambda_{B'} (I\otimes \lambda_{B'}} && \text{(Naturality of $\lambda$)}\\
+    &= \rep{(\lambda^{-1}_I \otimes B) \lambda^{-1}_B f' f}{g g' \lambda_{B'} (\lambda_I \otimes B'} && \text{(Unitality of action)} \\
+    &= \rep{\lambda^{-1}_B f' f}{g g' \lambda_{B'} (\lambda_I \otimes B') (\lambda^{-1}_I \otimes B')} && \text{(Coend relation)}  \\
+    &= \rep{\lambda^{-1}_B f'f}{g g' \lambda_{B'}} \\
     &= \iota(f'f, gg')
@@
 \begin{theorem}
-  $\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit object is $(I, I)$, and the action on a pair of morphisms $\rep{ l}{ r} : S \hto A$ and $\rep{ l'}{ r'} : T \hto B$ is given by:
+  $\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit object is $(I, I)$, and the action on a pair of morphisms $\rep{l}{r} : S \hto A$ and $\rep{l'}{r'} : T \hto B$ is given by:
   \begin{center}
@@
 \begin{proof}
-  Equationally, suppose the two optics have complements $M$ and $N$ respectively. Then:
-  \begin{align*}
-    \rep{ l}{ r} \otimes \rep{ l'}{ r'} &:= \rep{(M \otimes s_{A,N} \otimes B)(l \otimes l')}{(r \otimes r')(M \otimes s_{A',N} \otimes B')}
+  Suppose the two optics have complements $M$ and $N$ respectively. Written equationally, their tensor is:
+  \begin{align*}
+    \rep{l}{r} \otimes \rep{l'}{r'} &:= \rep{(M \otimes s_{A,N} \otimes B)(l \otimes l')}{(r \otimes r')(M \otimes s_{A',N} \otimes B')}
   \end{align*}
@@
   \begin{align*}
-    \rep{ l_1}{ r_1} : (S_1, S_1') &\hto (S_2, S_2') \\
-    \rep{ l_2}{ r_2} : (S_2, S_2') &\hto (S_3, S_3') \\
-    \rep{ p_1}{ q_1} : (T_1, T_1') &\hto (T_2, T_2') \\
-    \rep{ p_2}{ q_2} : (T_2, T_2') &\hto (T_3, T_3')
-  \end{align*}
-  The string diagram for $(\rep{ l_2}{ r_2} \circ \rep{ l_1}{ r_1}) \otimes (\rep{ p_2}{ q_2} \circ \rep{ p_1}{ q_1})$ is:
+    \rep{l_1}{r_1} : (S_1, S_1') &\hto (S_2, S_2') \\
+    \rep{l_2}{r_2} : (S_2, S_2') &\hto (S_3, S_3') \\
+    \rep{p_1}{q_1} : (T_1, T_1') &\hto (T_2, T_2') \\
+    \rep{p_2}{q_2} : (T_2, T_2') &\hto (T_3, T_3')
+  \end{align*}
+  The string diagram for $(\rep{l_2}{r_2} \circ \rep{l_1}{r_1}) \otimes (\rep{p_2}{q_2} \circ \rep{p_1}{q_1})$ is:
   \begin{center}
@@
   \end{center}
-  And for $(\rep{ l_2}{ r_2} \otimes \rep{ p_2}{ q_2}) \circ (\rep{ l_1}{ r_1} \otimes \rep{ p_1}{ q_1})$ is:
+  And for $(\rep{l_2}{r_2} \otimes \rep{p_2}{q_2}) \circ (\rep{l_1}{r_1} \otimes \rep{p_1}{q_1})$ is:
   \begin{center}
@@
   \end{center}
-  These two diagrams are equivalent.
-We can use the naturality of the symmetry morphism to push $l_2$ and $r_2$ through to be next to $l_1$ and $r_1$ respectively.
-This creates two extra twists that can be cancelled in the center of the diagram.
+  These two diagrams are equivalen: We can use the naturality of the symmetry morphism to push $l_2$ and $r_2$ past the crossing to be next to $l_1$ and $r_1$ respectively.
+This creates two extra twists that can be cancelled in the center of the diagram (implicitly using the coend relation).
 
@@
   Note that because $\iota(S, S') = (S, S')$, required equations for $\iota$ to be a monoidal functor hold by definition (although we don't yet know that $\Optic_\otimes$ is monoidal).
-The pentagon and triangle axioms then hold in $\Optic_\otimes$, as they are the image of the same axioms in $\C \times \C^\op$ under $\iota$.
+The pentagon and triangle equations then hold in $\Optic_\otimes$, as they are the image of the same axioms in $\C \times \C^\op$ under $\iota$.
 The only remaining thing to verify is that these structure maps are natural in $\Optic_\otimes$.
 
-  Let us check that $\alpha_{(R, R'), (S, S'), (T, T')}$ is natural in $(R, R')$. Suppose $f : (Q, Q') \hto (R, R')$ has representative $(l, r) : (Q \to M \otimes R, M \otimes R' \to Q')$, then:
+  Let us check that $\alpha_{(R, R'), (S, S'), (T, T')}$ is natural in $(R, R')$. Suppose $\rep{l}{r} : (Q, Q') \hto (R, R')$ is an optic with complement $M$.
   \begin{align*}
     &\alpha_{(R, R'), (S, S'), (T, T')} \circ (f \otimes (S, S')) \otimes (T, T') \\
-    &= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1})  \circ (\rep{ l}{ r} \otimes (S, S')) \otimes (T, T') \\
-    &= \rep{\lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T}}{\alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'}}  \circ \rep{(l \otimes S) \otimes T}{ (r \otimes S') \otimes T'} \\
+    &= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1})  \circ (\rep{l}{r} \otimes (S, S')) \otimes (T, T') \\
+    &= \rep{\lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T}}{\alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'}}  \circ \rep{(l \otimes S) \otimes T}{(r \otimes S') \otimes T'} \\
     &= \rep{(M \otimes \lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T})((l \otimes S) \otimes T)}{((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} )} \\
@@
     &= \rep{l \otimes (S \otimes T)}{r \otimes (S' \otimes T')} \circ \rep{\lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}}{\alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')} } \\
-    &= \rep{ l}{ r} \otimes ((S, S') \otimes (T, T')) \circ \iota(\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}) \\
+    &= \rep{l}{r} \otimes ((S, S') \otimes (T, T')) \circ \iota(\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}) \\
     &= f \otimes ((S, S') \otimes (T, T')) \circ \alpha_{(Q, Q'), (S, S'), (T, T')}
   \end{align*}
-  \todo{There is some cheating going on here, composition actually adds an extra $\alpha$, but that wouldn't get in the way.}
-
-  \todo{convert this to a string diagram}
+
+Naturality in the other variables is similar, as is the naturality of the unitors.
+  \todo{convert this to a string diagram?}
 \end{proof}
@@
 \begin{remark}
-  In the Haskell \texttt{lens} library, the monoidal product on optics is denoted ``\texttt{alongside}'' for the product and ``\texttt{without}'' for the coproduct.
+  In the Haskell \lenslib{} library, the monoidal product on optics is denoted ``\texttt{alongside}'' for the product and ``\texttt{without}'' for the coproduct.
 \end{remark}
@@
 \begin{proposition}
-  $\iota : \C \times \C^\op \to \Optic_\C$ is a monoidal functor.
+  $\iota : \C \times \C^\op \to \Optic_\C$ is a strict monoidal functor.
 \end{proposition}
@@
 
-In particular, for any $S \in \C$, the image of the identity yields an optic $c_S : (S, S) \hto (I, I)$, that we will call the connector:
+In particular, for any $S \in \C$, the identity $\id_S$ yields an optic $c_S = \rep{\rho_S^{-1}}{\rho_S} : (S, S) \hto (I, I)$, that we will call the connector:
 \begin{center}
@@
 \begin{proof}
-  On objects this is simply $\Optic(F)(S, S') = (FS, FS')$. On a morphism $\rep{ l}{ r} : (S, S') \to (A, A')$, we define
-  \begin{align*}
-    F\rep{ l}{ r} := \rep{\phi^{-1}_{M,A} (Fl)}{(Fr) \phi_{M,A'}}
+  On objects this is simply $\Optic(F)(S, S') = (FS, FS')$. On a morphism $\rep{l}{r} : (S, S') \to (A, A')$, we define
+  \begin{align*}
+    \Optic(F)\rep{l}{r} := \rep{\phi^{-1}_{M,A} (Fl)}{(Fr) \phi_{M,A'}}
   \end{align*}
@@
 \todo{Haven't actually checked natural transformations}
-\todo{Also we run into the large coend issue again, it's probably not well defined on every symm mon cat.}
+\todo{Also we run into the large coend issue again, it's not defined on every symm mon cat.}
 
@@
 In this section we establish a universal property of the $\Optic$ construction.
-The idea is that every optic $\rep{ l}{ r} : (S, S') \hto (A, A')$ consists of a morphism $S \to M \otimes A$ and the `formal dual' of a morphism $M \otimes A' \to S'$, composed with a `formal counit' that traces out the object $M$:
+The idea is that every optic $\rep{l}{r} : (S, S') \hto (A, A')$ consists of a morphism $S \to M \otimes A$ and the `formal dual' of a morphism $M \otimes A' \to S'$, composed with a `formal counit' that traces out the object $M$:
 \begin{center}
@@
 
-We assume temporarily that $\C$ is a \emph{strict} symmetric monoidal category.
+We assume in this section that $\C$ is a \emph{strict} symmetric monoidal category.
 It will be convenient to equip $\Optic_\C$ with a slightly different symmetric monoidal structure.
@@
   \end{align*}
-  And on morphisms $\rep{ l}{ r} : S \hto A$ and $\rep{ l'}{ r'} : T \hto B$ by:
+  And on morphisms $\rep{l}{r} : S \hto A$ and $\rep{l'}{r'} : T \hto B$ by:
   \begin{center}
@@
 
-  The categories are monoidally equivalent via the identity functor $I : (\Optic_\C, \switched, (I, I)) \to (\Optic_\C, \otimes, (I, I))$, where the structure isomorphisms are given by
+  The categories are monoidally equivalent via the identity functor \[I : (\Optic_\C, \switched, (I, I)) \to (\Optic_\C, \otimes, (I, I)),\] where the structure isomorphisms are given by
   \begin{align*}
@@
 
-Note that because $\C_d$ is symmetric monoidal and has the same collection of objects as $\C$, the symmetric monoidal structure morphisms of $\C$ must all be in $\C_d$.
+Note that because $\C_d$ is symmetric monoidal and has the same collection of objects as $\C$, the symmetric monoidal structure morphisms of $\C$ must be contained in $\C_d$.
 
@@
 
-\todo{\begin{example}
-    The funny graph example from the coherence paper?
-  \end{example}}
+\begin{example}
+  \todo{The funny graph example from the coherence paper?}
+\end{example}
 
@@
 
-  Note that the diagrams required to commute all terminate with the unit $I$, so in view of Proposition~\ref{prop-costates} we should not be surprised that they correspond to equality of maps in $\C$.
+  Note that the diagrams that are required to commute in the definition of teleological category all terminate with the unit $I$, so in view of Proposition~\ref{prop-costates} we should not be surprised that they correspond to equality of maps in $\C$.
 \end{proof}
@@
     F\iota(f, g)
-    &= F(\rep{ \lambda_A^{-1} f}{ g \lambda_{A'}}) \\
+    &= F(\rep{\lambda_A^{-1} f}{g \lambda_{A'}}) \\
     &= \rep{\phi^{-1}_{I,A} (F(\lambda_A^{-1} f))}{(F(g \lambda_{A'})) \phi_{I,A'}} \\
-    &= \rep{ \phi^{-1}_{I,A} (F\lambda_A^{-1}) (Ff)}{(Fg)(F \lambda_{A'}) \phi_{I,A'}} \\
-    &= \rep{ (\phi^{-1}_I \otimes FA) \phi^{-1}_{I,A} (F\lambda_A^{-1}) (Ff)}{(Fg)(F \lambda_{A'}) \phi_{I,A'} (\phi_I \otimes FA)} \\
-    &= \rep{ \lambda_{FA}^{-1} (Ff)}{ (Fg)\lambda_{FA'}} \\
+    &= \rep{\phi^{-1}_{I,A} (F\lambda_A^{-1}) (Ff)}{(Fg)(F \lambda_{A'}) \phi_{I,A'}} \\
+    &= \rep{(\phi^{-1}_I \otimes FA) \phi^{-1}_{I,A} (F\lambda_A^{-1}) (Ff)}{(Fg)(F \lambda_{A'}) \phi_{I,A'} (\phi_I \otimes FA)} \\
+    &= \rep{\lambda_{FA}^{-1} (Ff)}{(Fg)\lambda_{FA'}} \\
     &= \iota(Ff, Fg)
@@
     &= F(c_{S \otimes S'}) \\
-    &= F(\rep{ \rho_S^{-1}}{ \rho_{S'}}) \\
+    &= F(\rep{\rho_S^{-1}}{\rho_{S'}}) \\
     &= \rep{\phi^{-1}_{S,I} (F \rho_S^{-1})}{(F \rho_{S'}) \phi_{S',I}} \\
-    &= \rep{ (FS \otimes \phi_I^{-1}) \phi^{-1}_{S,I} (F \rho_S^{-1})}{ (F \rho_{S'}) \phi_{S',I} (FS \otimes \phi_I)} \\
-    &= \rep{ \rho_{FS}^{-1}}{ \rho_{FS'} } \\
+    &= \rep{(FS \otimes \phi_I^{-1}) \phi^{-1}_{S,I} (F \rho_S^{-1})}{(F \rho_{S'}) \phi_{S',I} (FS \otimes \phi_I)} \\
+    &= \rep{\rho_{FS}^{-1}}{\rho_{FS'} } \\
     &= \varepsilon_{(FS, FS')}
@@
 
+To establish the universal property of $\Optic_\M$, we will
+
 \begin{proposition}\label{prop-optic-decompose}
-  Suppose $\rep{ l}{ r} : (S, S') \hto (A, A')$ has complement $M$. Then
-  \begin{align*}
-    \rep{ l}{ r} = ((A, I) \switched \varepsilon_{(M, I)} \switched (I, A'))(j(s_{M,A}l) \switched j(rs_{A',M})^*)
+  Suppose $\rep{l}{r} : (S, S') \hto (A, A')$ has complement $M$. Then
+  \begin{align*}
+    \rep{l}{r} = ((A, I) \switched \varepsilon_{(M, I)} \switched (I, A'))(j(s_{M,A}l) \switched j(rs_{A',M})^*)
   \end{align*}
   where $j : \C \to \Optic_\C$ is the functor $j(A) := \iota(A, I)$.
-  \todo{The symmetries could have been avoided in the above expression if the Optic category had been defined with the tensor in the opposite order!}
-\end{proposition}
+\end{proposition}
+The symmetries in the above expression could have been avoided if $\Optic$ had been defined as $\int^{M \in \C} \C(S, A \otimes M) \times \C(A' \otimes M, S')$, but it is too late to change the convention now!
 \begin{proof}
@@
   \end{center}
-  so the two pairs of twists cancel, and we are left exactly with the diagram for $\rep{ l}{ r}$.
+  so the two pairs of twists cancel, and we are left exactly with the diagram for $\rep{l}{r}$.
 \end{proof}
@@
 For all symmetric monoidal functors $F : \C \to \T_d$, there exists a teleological functor $K : \Optic_\C \to \T$, unique up to isomorphism, such that $Kj \cong F$.
-  % $\Optic$ is left adjoint to $(-)_d$, so $\Optic_\C$ is the free teleological category on a category of dualisable morphisms $\C$.
 \end{theorem}
 \begin{proof}
-  On objects, define $K(S, S') = FS \otimes (FS')^*$. Suppose $\rep{ l}{ r} : (S, S') \hto (A, A')$ is an optic. By the previous Proposition,
-  \begin{align*}
-    \rep{ l}{ r} = ((A, I) \switched \varepsilon_{(M, I)} \switched (I, A'))(j(s_{M,A}l) \switched j(rs_{M,A'})^*)
-  \end{align*}
-  But now, in order for $K$ to be a teleological functor with $Kj \cong F$, each piece of this expression must be preserved by $K$, so we are forced to define:
-  \begin{align*}
-    K\rep{ l}{ r} = (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F(s_{M,A}l) \otimes (F(rs_{A', M}))^* )
-  \end{align*}
-
-  We must show that this is well defined. Suppose we have two lenses related by the coend relation:
-  \begin{align*}
-    \rep{ (f \otimes A) l}{ r} = \rep{ l}{ r (f \otimes A')}
+  We begin by constructing $K$. On objects, define $K(S, S') = FS \otimes (FS')^*$. Suppose $\rep{l}{r} : (S, S') \hto (A, A')$ is an optic. By the previous Proposition,
+  \begin{align*}
+    \rep{l}{r} = ((A, I) \switched \varepsilon_{(M, I)} \switched (I, A'))(j(s_{M,A}l) \switched j(rs_{M,A'})^*)
+  \end{align*}
+  Which suggests defining
+  \begin{align*}
+    K\rep{l}{r} = (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F(s_{M,A}l) \otimes (F(rs_{A', M}))^* )
+  \end{align*}
+
+  We must show that this is well defined. Suppose we have two optics related by the coend relation:
+  \begin{align*}
+    \rep{(f \otimes A) l}{r} = \rep{l}{r (f \otimes A')}
   \end{align*}
@@
   \begin{align*}
-    K\rep{ (f \otimes A) l}{ r}
+    K\rep{(f \otimes A) l}{r}
     &= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F(s_{M,A}(f \otimes A)l) \otimes (F(rs_{A',M}))^* ) \\
@@
     &= (FA \otimes \varepsilon_{FN} \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(r(f \otimes A')s_{A',N}))^* ) \\
-    &= K\rep{  l}{ r (f \otimes A')}
+    &= K\rep{ l}{r (f \otimes A')}
   \end{align*}
   \todo{functoriality} \todo{monoidal} \todo{preserves dualisable morphisms} \todo{preserves counit}
+  \todo{uniqueness} 
+\end{proof}
+
+\begin{theorem}
+$\Optic : \SymmMonCat \to \Tele$ is left biadjoint to the underlying dualisable morphisms functor ${(-)}_d : \Tele \to \SymmMonCat$
+\end{theorem}
+\begin{proof}
+\todo{figure out exactly what else needs proving}
 \end{proof}
@@
 
-To capture the \texttt{Iso}s, \texttt{Traversal}s and \texttt{Setter}s of the Haskell \texttt{lens} library (see~\ref{lawful-examples}), we generalise to the case of a monoidal action of one category on another.
+To capture the \texttt{Iso}s, \texttt{Traversal}s and \texttt{Setter}s of the Haskell \lenslib{} library (see~\ref{lawful-examples}), we generalise to the case of a monoidal action of one category on another.
 
@@
 
+The following are analogous to Propositions~\ref{prop-optic-is-cat} and \ref{prop-change-of-action-monoidal}.
+
 \begin{proposition}
@@
   Suppose $\C$ and $\D$ are categories acted on by $\M$ and $\mathcal{N}$ respectively.
-If $F : \C \to \D$ is a functor that commutes with the actions, then there is an induced functor $\Optic(F) : \Optic_\M \to \Optic_\N$.
-\end{proposition}
-\begin{proof}
-  Analogous to Proposition~\ref{prop-change-of-action-monoidal}
-\end{proof}
-
-For the remainder of the paper we work in this slightly more general setting.
+Let $F : \C \to \D$ be a functor that commutes with the actions, in the sense that there exist natural isomorphisms
+  \begin{align*}
+  \phi &: F(IA) \to I(FA) \\
+  \phi_{M,A} &: (FM)(FA) \to F(MA)
+  \end{align*}
+satisfying conditions analogous to those for a monoidal functor.
+
+Then there is an induced functor $\Optic(F) : \Optic_\M \to \Optic_\N$. \qed
+\end{proposition}
+
+For the remainder of the paper we work in this more general setting.
 
@@
 \todo{intro}
-\todo{Here I am using ; to mean composition in diagrammatic order, I need to make a final decision on which to use}
+
+In this section I use $;$ to denote composition of $\C$ in diagrammatic order.
+The reason for this is that the coend relation can be applied simply by shifting the position of $\mid$ in a representative:
+\begin{align*}
+\rep{l;\phi A}{r} = \rep{l}{\phi A;r}
+\end{align*}
+
+\todo{Should I switch everything else to use diagrammatic order?}
 
@@
 
-\todo{In this section I am using semicolon to mean composition in diagrammatic order. Should I also switch the comma in $\rep{ l}{ r}$ to be a $\mid$?}
-
 For a fixed $M \in \M$, there is a map $\C(S, M A) \times \C(M A, S) \to \C(S, S)$ given by composition.
-This induces a map $\outside : \Optic_\M(S, A) \to \C(S, S)$, given equationally by $\outside(\rep{ l}{ r}) = l ; r$
+This induces a map $\outside : \Optic_\M(S, A) \to \C(S, S)$, given equationally by $\outside(\rep{l}{r}) = l ; r$
 
@@
 \begin{align*}
-  \once(\rep{ l}{ r}) &= \repthree{ l}{ \id_{MA}}{ r} \\
-  \twice(\rep{ l}{ r} \rangle) &= \repthree{l}{r;l}{r}
+  \once(\rep{l}{r}) &= \repthree{ l}{\id_{MA}}{r} \\
+  \twice(\rep{l}{r} \rangle) &= \repthree{l}{r;l}{r}
 \end{align*}
@@
   \begin{align*}
-    \outside(\rep{ \lambda^{-1}_S}{ \lambda_{S}}) &= \lambda_{S} \lambda^{-1}_S = \id_S \\
+    \outside(\rep{\lambda^{-1}_S}{\lambda_{S}}) &= \lambda_{S} \lambda^{-1}_S = \id_S \\
     \intertext{and}
-    \once(\rep{ \lambda^{-1}_S}{ \lambda_{S}})
+    \once(\rep{\lambda^{-1}_S}{\lambda_{S}})
                                                           &= \repthree{\lambda^{-1}_S}{\id_{IA}}{\lambda_{S}} \\
                                                           &= \repthree{\lambda^{-1}_S}{\lambda_{S};\lambda^{-1}_S}{\lambda_{S}} \\
-                                                          &= \twice(\rep{ \lambda^{-1}_S}{ \lambda_{S}})
-  \end{align*}
-
-  Suppose we have two lawful optics $\rep{ l}{ r} : R \hto S$ and $\rep{ l'}{ r'} : S \hto A$, where $l : R \to MS$ and $l' : S \to NA$.
-We must show that $\rep{ (Ml')l}{ r (Mr') }$ is also a lawful optic.
+                                                          &= \twice(\rep{\lambda^{-1}_S}{\lambda_{S}})
+  \end{align*}
+
+  Suppose we have two lawful optics $\rep{l}{r} : R \hto S$ and $\rep{l'}{r'} : S \hto A$, where $l : R \to MS$ and $l' : S \to NA$.
+We must show that $\rep{(Ml')l}{r (Mr') }$ is also a lawful optic.
 The first equation is straightforward:
   \begin{align*}
-    \outside(\rep{ l; (Ml')}{(Mr') ; r  })
+    \outside(\rep{l; (Ml')}{(Mr') ; r  })
     &= l ; Ml' ; Mr' ; r \\
@@
     &= l ; r \\
-    &= \id_{MNA}
+    &= \id_S
   \end{align*}
@@
   For the second, we must show
-  \[ \repthree{ l;(Ml')}{ (Mr'); r;l;(Ml')}{(Mr') ; r } = \rep{ l;(Ml')}{ \id_{MNA}}{ (Mr') ; r }. \]
-
-  We do this by showing that, in some sense, the expressions in the above equation respect the coend relations defining the codomains of $\once(\rep{ l}{ r})$ and $\once(\rep{ l'}{ r'})$.
-
-  So consider the generating relation $\repthree{ l;\phi_S}{ c}{r} = \rep{ l}{ \phi_S ; c}{r}$ in \[\int^{M_1, M_2 \in \M} \C(R, M_1 S) \times \C(M_1 S, M_2 S) \times \C(M_2 S, R).\]
+  \[ \repthree{ l;(Ml')}{(Mr'); r;l;(Ml')}{(Mr') ; r } = \rep{l;(Ml')}{\id_{MNA}}{(Mr') ; r }. \]
+
+  We do this by showing that, in some sense, the expressions in the above equation respect the coend relations defining the codomains of $\once(\rep{l}{r})$ and $\once(\rep{l'}{r'})$.
+
+  So consider the generating relation $\repthree{ l;\phi_S}{c}{r} = \repthree{l}{\phi_S ; c}{r}$ in \[\int^{M_1, M_2 \in \M} \C(R, M_1 S) \times \C(M_1 S, M_2 S) \times \C(M_2 S, R).\]
   This implies that
   \begin{align*}
-    \rep{ l;\phi_S;(Ml')}{ (Mr'); c ;(Ml')}{(Mr') ; r}
-    &= \rep{ l;(Ml');\phi_{NA}}{ (Mr'); c ;(Ml')}{(Mr') ; r} && \text{(functoriality)} \\
-    &= \rep{ l;(Ml')}{ \phi_{NA};(Mr'); c ;(Ml')}{(Mr') ; r} && \text{(coend relation)} \\
-    &= \rep{ l;(Ml')}{ (Mr');\phi_{S}; c ;(Ml')}{(Mr') ; r} && \text{(functoriality)}
-  \end{align*}
-  And similarly for the other generating relation, $\rep{l}{ c;\phi_S}{r } = \rep{l}{c}{\phi_S; r }$.
-
-  Therefore, the chain of relations proving $\rep{l}{ r;l}{r } = \rep{l}{ \id_{MA}}{ r }$ can be replicated to show
-  \begin{align*}
-    \rep{l;(Ml')}{ (Mr');r;l;(Ml')}{(Mr') ; r } &= \rep{l;(Ml')}{ (Mr');\id_{MA};(Ml')}{ (Mr') ; r },
-  \end{align*}
-  which is equal to $\rep{l;(Ml')}{ M(r'l')}{ (Mr') ; r }$.
-
-  Similarly, a generating relation $\rep{l';\psi_A}{ c'}{ r' } = \rep{l'}{ \psi_A ; c'}{ r' }$ in \[\int^{N_1, N_2 \in \M} \C(S, N_1 A) \times \C(N_1 A, N_2 A) \times \C(M_2 A, S)\]
+    \repthree{l;\phi_S;(Ml')}{(Mr'); c ;(Ml')}{(Mr') ; r}
+    &= \repthree{l;(Ml');\phi_{NA}}{(Mr'); c ;(Ml')}{(Mr') ; r} && \text{(functoriality)} \\
+    &= \repthree{l;(Ml')}{\phi_{NA};(Mr'); c ;(Ml')}{(Mr') ; r} && \text{(coend relation)} \\
+    &= \repthree{l;(Ml')}{(Mr');\phi_{S}; c ;(Ml')}{(Mr') ; r} && \text{(functoriality)}
+  \end{align*}
+  And similarly for the other generating relation, $\repthree{l}{c;\phi_S}{r } = \repthree{l}{c}{\phi_S; r }$.
+
+  Therefore, the chain of relations proving $\repthree{l}{r;l}{r } = \repthree{l}{\id_{MA}}{r }$ can be replicated to show
+  \begin{align*}
+    \repthree{l;(Ml')}{(Mr');r;l;(Ml')}{(Mr') ; r } &= \repthree{l;(Ml')}{(Mr');\id_{MA};(Ml')}{(Mr') ; r },
+  \end{align*}
+  which is equal to $\repthree{l;(Ml')}{M(r'l')}{(Mr') ; r }$.
+
+  Similarly, a generating relation $\repthree{l';\psi_A}{c'}{r' } = \repthree{l'}{\psi_A ; c'}{r' }$ in \[\int^{N_1, N_2 \in \M} \C(S, N_1 A) \times \C(N_1 A, N_2 A) \times \C(M_2 A, S)\]
   implies that
   \begin{align*}
-    \rep{l;M(l';\psi_A)}{ Mc'}{ (Mr') ; r }
-    &= \rep{l;Ml';M\psi_A}{ Mc'}{ (Mr') ; r } \\
-    &= \rep{l;Ml'}{ M\psi_A ; Mc'}{ (Mr') ; r } \\
-    &= \rep{l;Ml'}{ M(\psi_A;c')}{ (Mr') ; r }
-  \end{align*}
-  So again we can replicate the chain of relations proving $\rep{l'}{ r';l'}{ r' } = \rep{l'}{ \id_{MA}}{ r' }$ to show that
-  \[\rep{l;(Ml')}{ M(r'l')}{ (Mr') ; r } = \rep{l;(Ml')}{ \id_{MNA}}{ (Mr') ; r } \]
+    \repthree{l;M(l';\psi_A)}{Mc'}{(Mr') ; r }
+    &= \repthree{l;Ml';M\psi_A}{Mc'}{(Mr') ; r } \\
+    &= \repthree{l;Ml'}{M\psi_A ; Mc'}{(Mr') ; r } \\
+    &= \repthree{l;Ml'}{M(\psi_A;c')}{(Mr') ; r }
+  \end{align*}
+  So again we can replicate the chain of relations proving $\repthree{l'}{r';l'}{r' } = \repthree{l'}{\id_{MA}}{r' }$ to show that
+  \[\repthree{l;(Ml')}{M(r'l')}{(Mr') ; r } = \repthree{l;(Ml')}{\id_{MNA}}{(Mr') ; r } \]
 
   We conclude that composition preserves lawfulness, so $\Lawful_\M$ is indeed a subcategory of $\Optic_\M$.
-
-  \todo{There is probably a more conceptual way to do this}
 \end{proof}
@@
 \begin{proof}
-  If $p = \rep{l}{ r }$ is lawful, \todo{todo}
+  If $p = \rep{l}{r}$ is lawful, then verifying the first equation is easy:
+  \begin{align*}
+  \once(\Optic(F)(\rep{l}{r})) 
+  &= \once(\rep{(Fl);\phi^{-1}_{M,A} }{\phi_{M,A'};(Fr) }) \\
+  &= (Fl);\phi^{-1}_{M,A};\phi_{M,A'};(Fr)\\
+  &= (Fl);(Fr)\\
+  &= \id_{FS}
+  \end{align*}
+  where $\phi_{M,A'} : (FM)(FA) \to F(MA)$ is the structure map for $F$ commuting with the actions.
+
+  For the second equation, consider a generating relation $\repthree{l;\psi A}{c}{r} = \repthree{l}{\psi A ; c}{r}$. We can use the naturality of $\phi$ to show
+  \begin{align*}
+  \repthree{F(l;\psi A);\phi^{-1}_{M,A}}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} 
+  &= \repthree{F(l);F(\psi A);\phi^{-1}_{M,A}}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
+  &= \repthree{F(l);\phi^{-1}_{M',A};(F\psi) A}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
+  &= \repthree{F(l);\phi^{-1}_{M',A}}{(F\psi) A;\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
+  &= \repthree{F(l);\phi^{-1}_{M',A}}{\phi_{M,A};F(\psi A);Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
+  &= \repthree{F(l);\phi^{-1}_{M',A}}{\phi_{M,A};F(\psi A;c);\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
+  \end{align*}
+  Similarly, 
+  \begin{align*}
+    \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};F(\psi_A;r)} 
+    &= \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};F(c;\psi A);\phi^{-1}_{N,A}}{\phi_{N,A};Fr} 
+  \end{align*}
+
+  If $\rep{l}{r}$ is lawful, we can therefore replicate the chain of relations proving $\twice(\rep{l}{r}) = \once(\rep{l}{r})$ to show:
+  \begin{align*}
+  \twice(\Optic(F)(\rep{l}{r})) 
+  &= \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};F(r;l);\phi^{-1}_{M,A}}{\phi_{M,A};Fr}  \\
+  &= \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};F(\id_MA);\phi^{-1}_{M,A}}{\phi_{M,A};Fr}  \\
+  &= \repthree{Fl;\phi^{-1}_{M,A}}{\id_{(FM)A}}{\phi_{M,A};Fr}  \\
+  &= \once(\Optic(F)(\rep{l}{r})) 
+  \end{align*}
+
+  \todo{There is probably a more conceptual way to do this}
 \end{proof}
@@
 \begin{proposition}
-  Let $\rep{l}{ r } : S \hto A$ be an optic. If $l;r = \id_S$ and $r;l = \phi A$ for some $\phi : M \to M$ in $\M$, then $\rep{l}{ r }$ is lawful.
-\end{proposition}
-\begin{proof}
-  The $\outside(\rep{l}{ r }) = l;r = \id_S$ is exactly the first condition. And for the second, we verify:
-  \begin{align*}
-    \twice(\rep{l}{ r })
-    &= \rep{l}{ r;l}{ r } \\
-    &= \rep{l}{ \phi A}{ r } && \text{($r;l = \phi A$)}\\
-    &= \rep{l (\phi A)}{ \id_{MA}}{ r } && \text{(coend relation)} \\
-    &= \rep{l;r;l}{ \id_{MA}}{ r } && \text{($r;l = \phi A$ again)}\\
-    &= \rep{l}{ \id_{MA}}{ r }  && \text{($l;r = \id_S$)}\\
-    &= \once(\rep{l}{ r })
+  Let $\rep{l}{r } : S \hto A$ be an optic. If $l;r = \id_S$ and $r;l = \phi A$ for some $\phi : M \to M$ in $\M$, then $\rep{l}{r }$ is lawful.
+\end{proposition}
+\begin{proof}
+  The $\outside(\rep{l}{r }) = l;r = \id_S$ is exactly the first condition. And for the second, we verify:
+  \begin{align*}
+    \twice(\rep{l}{r })
+    &= \repthree{l}{r;l}{r } \\
+    &= \repthree{l}{\phi A}{r } && \text{($r;l = \phi A$)}\\
+    &= \repthree{l (\phi A)}{\id_{MA}}{r } && \text{(coend relation)} \\
+    &= \repthree{l;r;l}{\id_{MA}}{r } && \text{($r;l = \phi A$ again)}\\
+    &= \repthree{l}{\id_{MA}}{r }  && \text{($l;r = \id_S$)}\\
+    &= \once(\rep{l}{r })
   \end{align*}
@@
 
-Let $\inside : \Optic_\M(S, A) \to \int^{M \in \M} \C(M A, M A)$ be the map induced by $\inside(\rep{l}{ r }) = \langle r ; l \rangle$.
+Let $\inside : \Optic_\M(S, A) \to \int^{M \in \M} \C(M A, M A)$ be the map induced by $\inside(\rep{l}{r }) = \langle r ; l \rangle$.
 We might ask that instead of requiring $r;l = \phi A$ exactly, we have $\langle r ; l \rangle = \langle \phi A \rangle$ in $\int^{M \in \M} \C(M A, M A)$.
@@
   Suppose $p : S \hto A$ satisfies $\outside(p) = \id_S$ and $\inside(p) = \langle \phi A \rangle$.
-Then there exists a representative $\rep{l}{ r }$ such that $l ; r = \psi A$ on the nose for some (possibly different) $\psi : M \to M$.
-\end{proposition}
-\begin{proof}
-  \todo{Go through this proof for formatting again.}
-
-  The coend relation in $\int^{M \in \M} \C(M A, M A)$ states that two morphisms $f : M A \to M A$ and $g : N A \to N A$ are identified when there exists a $k : N A \to M A$ and morphism $\phi : M \to N$ such that
-  \[
-    \begin{tikzcd}
-      M A \ar[r, "\phi_A"] \ar[d, "f", swap] & N A \ar[d, "g"] \ar[dl, "k"] \\
-      M A \ar[r, "\phi_A", swap] & N A
-    \end{tikzcd}
-  \]
-  commutes.
-This gives a binary relation $f \rightsquigarrow g$ that is not likely to be symmetric or transitive in general.
-The coend is obtained by identifying all morphisms related in this way, $\langle f \rangle = \langle g \rangle$ iff there exists a zigzag $f = u_1 \leftrightsquigarrow u_2 \leftrightsquigarrow \dots  \leftrightsquigarrow u_{n-1} \leftrightsquigarrow u_n = g$ where the relation may apply in either direction.
-
-  Note that if $f \rightsquigarrow g$ then $ff \rightsquigarrow gg$: this is clear by stacking the above diagram, and then taking $k' = fk = kg$.
-This argument can be repeated to show that $f^n \rightsquigarrow g^n$ for any $n$.
-
-  Similarly two representatives $\rep{l}{ r } : S \hto A$ and $\rep{l'}{ r' } : S \hto A$ with complements $M$ and $N$ respectively are identified when there exists a $\phi : M \to N$ such that
-  \[
-    \begin{tikzcd}
-      M A \ar[r, "\phi_A"] \ar[d, "r", swap] & N A \ar[d, "r'"] \\
-      S \ar[r, equal] \ar[d, "l", swap] & S \ar[d, "l'"]  \\
-      MA \ar[r, "\phi_A"] & N A
-    \end{tikzcd}
-  \]
-  commutes.
-
-  Now suppose $p = \rep{l}{ r } : S \hto A$ is a lawful optic, so $rl = \id_S$ and $\langle lr \rangle = \langle \psi A\rangle$.
-There therefore must exist a finite chain of relations $lr = u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n = \psi A$.
-  Supposing that the first relation faces rightwards, we have a diagram:
-  \[
-    \begin{tikzcd}
-      M A \ar[r, "\phi_A"] \ar[d, "r", swap] & N A \ar[dd, "u_2"] \ar[ddl, "k"] \\
-      S \ar[d,"l",swap] & \\
-      M A \ar[r, "\phi_A", swap] & N A
-    \end{tikzcd}
-  \]
-  Note that $r = rlr = rk\phi_A$. We therefore have the commutative diagram
-  \[
-    \begin{tikzcd}
-      M A \ar[r, "\phi_A"] \ar[d, "r", swap] & N A \ar[d, "rk"] \\
-      S \ar[r, equal] \ar[d, "l", swap] & S \ar[d, "\phi_Al"] \\
-      MA \ar[r, "\phi_A", swap] & N A
-    \end{tikzcd}
-  \]
-  Define $l' = \phi_A l$ and $r' = rk$. The above diagram is a witness that $\rep{l}{ r } = \rep{l'}{ r' }$ as an optic $S \hto A$.
-
-  The composite $l'r'$ is:
-  \begin{align*}
-    l'r' &= \phi_A l r k \\
-         &= \phi_A k \phi_A k \\
-         &= u_2^2
-  \end{align*}
-
-  A symmetric argument shows that if instead the relation faces leftward, so $lr \leftsquigarrow g$, there exists $l'$ and $r'$ so that $\rep{l}{ r } = \rep{l'}{ r' }$ and $l'r' = u_2^2$.
-
-  We can now inductively apply the above argument to the shorter chain \[l'r' = u_1^2 \leftrightsquigarrow \dots \leftrightsquigarrow u_n^2 \leftrightsquigarrow (\psi A)^2 = \psi^2 A,\] obtained by squaring each morphism in the original chain, until we are left with a representative $\rep{l^*}{ r^* }$ such that $l^*r^* = \psi^N A$, for some $N>0$.
-This pair $\rep{l^*}{ r^* }$ is the required representative.
+Then there exists a representative $\rep{l}{r }$ such that $l ; r = \psi A$ on the nose for some (possibly different) $\psi : M \to M$.
+\end{proposition}
+\begin{proof}
+  The generating relation for $\int^{M \in \M} \C(M A, M A)$ is 
+  \[ \langle f \phi_A \rangle = \langle \phi_A f \rangle \] 
+  whenever $f : N A \to M A$ and $\phi : M \to N$. This relation $f \phi_A \rightsquigarrow \phi_A f$ is not likely to be symmetric or transitive in general.
+
+  Note that if $f \phi_A \rightsquigarrow \phi_A f$ then $f \phi_A f \phi_A \rightsquigarrow \phi_A f \phi_A f$. More generally, if $f \rightsquigarrow g$ then $f^n \rightsquigarrow g^n$ for any $n$.
+
+  Now let $\rep{l}{r}$ be a representative for $p$, so $rl = \id_S$ and $\langle lr \rangle = \langle \psi A\rangle$.
+There therefore exists a finite chain of relations $lr = u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n = \psi A$.
+
+Suppose the first relation faces rightward, so there exists a $k$ and $\phi$ with $r;l = \phi_A;k$ and $u_2 = k;\phi_A$. Define $l' = l;\phi_A$ and $r' = k;r$. Then:
+\begin{align*}
+\rep{l'}{r'} 
+&= \rep{l ; \phi_A}{k ; r} \\
+&= \rep{l}{\phi_A ; k ; r} \\
+&= \rep{l}{r ; l; r} \\
+&= \rep{l}{r}
+\end{align*}
+This new representative satisfies
+\begin{align*}
+l';r' &= l;\phi_A;k;r = l;r;l;r = \id_S \\
+r';l' &= k;r;l;\phi_A = k;\phi_A;k;\phi_A = u_2^2
+\end{align*}
+
+  A symmetric argument shows that if instead the relation faces leftward, so $lr \leftsquigarrow u_2$, there again exists $l'$ and $r'$ so that $\rep{l}{r} = \rep{l'}{r'}$, and both $l';r' = \id_S$ and $r';l' = u_2^2$.
+
+  We can now inductively apply the above argument to the shorter chain \[l'r' = u_1^2 \leftrightsquigarrow \dots \leftrightsquigarrow u_n^2 \leftrightsquigarrow (\psi A)^2 = \psi^2 A,\] obtained by squaring each morphism in the original chain, until we are left with a representative $\rep{l^*}{r^*}$ such that $r^*;l^* = \psi^N_A$, for some $N>0$.
+This pair $\rep{l^*}{r^* }$ is the required representative.
 \end{proof}
@@
 The above argument has a similar form to some that appear in \cite{OnTheTrace}, which considered (among other things) coends of the form $\int^{c \in \C} \C(c, Fc)$ for an endofunctor $F : \C \to \C$.
-
-Finally, lawfulness is preserved by the change-of-action functors of Proposition \ref{prop-change-of-action}.
 
@@
 
-Explicitly this isomorphism states that, given an optic $\rep{l}{ r } : (S, S') \hto (A, A')$, the corresponding element of $\mathbb{O}((S, S'), (A, A'))$ is the pair $(\fget, \fput)$, where $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
+Explicitly this isomorphism states that, given an optic $\rep{l}{r } : (S, S') \hto (A, A')$, the corresponding element of $\mathbb{O}((S, S'), (A, A'))$ is the pair $(\fget, \fput)$, where $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
 In the other direction, given $(\fget, \fput)$, the corresponding optic has representative $\rep{[\id_S, \fget]}{\fput}$.
@@
   \begin{align*}
-    \Phi(\repthree{l}{ c}{ r }) = (&\pi_2 l, \\
+    \Phi(\repthree{l}{c}{r }) = (&\pi_2 l, \\
                                    &\pi_2 c (\pi_1 l \times A), \\
@@
   \begin{alignat*}{3}
-    \Phi(\once(\rep{[\id_S, \fget]}{ \fput})) &=
+    \Phi(\once(\rep{[\id_S, \fget]}{\fput})) &=
     \Phi(&&\repthree{[\id_S, \fget]}{\id_{S \times A}}{\fput}) \\
@@
     %%%%
-    \Phi(\twice(\rep{[\id_S, \fget]}{ \fput})) &=
+    \Phi(\twice(\rep{[\id_S, \fget]}{\fput})) &=
     \Phi(&&\repthree{[\id_S, \fget]}{[\id_S, \fget]\fput}{\fput}) \\
@@
   \]
-  is a witness that $\rep{\fput (i \times A)}{ [j,\fget] } = \rep{\fput}{ [\id_S, \fget] }$ as elements of $\Optic_\M(S, A)$.
+  is a witness that $\rep{\fput (i \times A)}{[j,\fget] } = \rep{\fput}{[\id_S, \fget] }$ as elements of $\Optic_\M(S, A)$.
 \end{proof}
@@
 For an optic, the corresponding element of $\mathbb{O}((S, S'), (A, A'))$ will be called $\funzip$.
-The above isomorphism sends $\funzip$ to the element $\rep{\funzip }{ \ev_{A', S'} }$, where $\ev_{A', S'} : \homC(A',S') \otimes A' \to S'$ is the evaluation map.
-In the other direction, given $\rep{l}{ r }$ we have $\funzip = (\tilde r \otimes A)l$ where $\tilde r : M \to \homC(A', S')$ denotes the transpose of $r$.
+The above isomorphism sends $\funzip$ to the element $\rep{\funzip }{\ev_{A', S'} }$, where $\ev_{A', S'} : \homC(A',S') \otimes A' \to S'$ is the evaluation map.
+In the other direction, given $\rep{l}{r }$ we have $\funzip = (\tilde r \otimes A)l$ where $\tilde r : M \to \homC(A', S')$ denotes the transpose of $r$.
 
@@
   \end{align*}
-  which evaluated on an element $\repthree{l}{ c}{r }$ is given by
-  \begin{align*}
-    \Phi(\repthree{l}{ c}{r}) &= (\widetilde{(\tilde{r} \otimes A)c} \otimes A)l
-  \end{align*}
-  Now suppose we are given an optic $p$ with corresponding element of $\mathbb{O}(S, A)$ is $\funzip$. Then $\outside(\rep{\funzip }{ \ev_{A, S} }) = \ev_{A, S} \; \funzip$, giving the first law.
+  which evaluated on an element $\repthree{l}{c}{r }$ is given by
+  \begin{align*}
+    \Phi(\repthree{l}{c}{r}) &= (\widetilde{(\tilde{r} \otimes A)c} \otimes A)l
+  \end{align*}
+  Now suppose we are given an optic $p$ with corresponding element of $\mathbb{O}(S, A)$ is $\funzip$. Then \[\outside(\rep{\funzip }{\ev_{A, S} }) = \ev_{A, S} \; \funzip,\] giving the first law.
 
@@
   \begin{align*}
-    \Phi(\once(\rep{\funzip }{ \ev_{A, S} }))
-    &= \Phi(\repthree{\funzip }{ \id_{\homC(A,S) \otimes A}}{\ev_{A, S} }) \\
+    \Phi(\once(\rep{\funzip }{\ev_{A, S} }))
+    &= \Phi(\repthree{\funzip }{\id_{\homC(A,S) \otimes A}}{\ev_{A, S} }) \\
     &= (\widetilde{(\tilde{\ev_{A, S}} \otimes A)\id_{\homC(A,S) \otimes A}} \otimes A)\funzip \\
     &= (\coev_{\homC(A, S), A} \otimes A)\funzip \\
-    \Phi(\twice(\rep{\funzip }{ \ev_{A, S} }))
-    &= \Phi(\repthree{\funzip }{ \funzip \; \ev_{A, S}}{ \ev_{A, S} }) \\
+    \Phi(\twice(\rep{\funzip }{\ev_{A, S} }))
+    &= \Phi(\repthree{\funzip }{\funzip \; \ev_{A, S}}{\ev_{A, S} }) \\
     &= (\widetilde{(\tilde{\ev_{A, S}} \otimes A)(\funzip \; \ev_{A, S})} \otimes A)\funzip \\
@@
 \end{proof}
-
-\todo{The use of lenses in a language with linear types seems worth exploring!}
 
@@
 Just as optics for $\times$ correspond to a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$, optics for $\sqcup$ correspond to pairs of maps $\freview : A \to S$ and $\fmatching : S \to S \sqcup A$.
-These names are taken from the Haskell \texttt{lens} library.
+These names are taken from the Haskell \lenslib{} library.
 \begin{align*}
@@
 \end{align*}
-If we are given a prism $\rep{l}{ r } : (S, S') \hto (A, A')$ then associated $\freview$ and $\fmatching$ morphisms are given by $\freview = r \inr$ and $\fmatching = (r\inl \sqcup A)l$
+If we are given a prism $\rep{l}{r } : (S, S') \hto (A, A')$ then associated $\freview$ and $\fmatching$ morphisms are given by $\freview = r \inr$ and $\fmatching = (r\inl \sqcup A)l$
 
@@
 
-In the \texttt{lens} library documentation the third law is missing, on account of following:
+In the \lenslib{} library documentation the third law is missing, on account of following:
 
@@
 \begin{proposition}
-  An iso $\rep{l}{ r }$ is lawful iff (as expected) $l$ and $r$ are mutual inverses.
+  An iso $\rep{l}{r }$ is lawful iff (as expected) $l$ and $r$ are mutual inverses.
 \end{proposition}
@@
   \[ \C(S, A) \times \C(A, A) \times \C(A, S) \]
-  The condition $\outside(\rep{l}{ r }) = \id_S$ is the claim that $rl = \id_S$, and $\once(\rep{l}{ r }) = (l, \id_A, r)$ is equal to $\twice(\rep{l}{ r }) = (l, lr, r)$ iff $lr = \id_A$.
+  The condition $\outside(\rep{l}{r }) = \id_S$ is the claim that $rl = \id_S$, and $\once(\rep{l}{r }) = (l, \id_A, r)$ is equal to $\twice(\rep{l}{r }) = (l, lr, r)$ iff $lr = \id_A$.
 \end{proof}
@@
   \end{align*}
-  that sends an object $D \in \D$ and optic $\rep{l}{ r } : F \hto G$ in $\Optic_{[\D, \C]}$ to the optic $\rep{l_D}{ r_D } : FD \hto GD$ in $\Optic_\C$.
+  that sends an object $D \in \D$ and optic $\rep{l}{r } : F \hto G$ in $\Optic_{[\D, \C]}$ to the optic $\rep{l_D}{r_D } : FD \hto GD$ in $\Optic_\C$.
 \end{proposition}
@@
 %
-% One issue with the definition of optic given in the last section is that it could be difficult to determine when two optics $\rep{l}{ r }, \langle l', r' \rangle : S \hto A$
+% One issue with the definition of optic given in the last section is that it could be difficult to determine when two optics $\rep{l}{r }, \langle l', r' \rangle : S \hto A$
 are equal. For some choices of $\M$, however, we can reduce a zigzag of relations to a single one.
@@
 \section{Profunctor Optics}
-The Haskell \texttt{lens} library implements optics using what is known as the \emph{profunctor encoding}. Lenses are defined as follows:
+The Haskell \lenslib{} library implements optics using what is known as the \emph{profunctor encoding}. Lenses are defined as follows:
 
@@
   \end{align*}
-  for all $C, D \in \C$ and $N \in \M$. Equationally, this is $\alpha_{A,B,M}(\repthree{l}{ p}{ r} ) = \rep{Ml}{ p}{ Mr} $.
+  for all $C, D \in \C$ and $N \in \M$. Equationally, this is $\alpha_{A,B,M}(\repthree{l}{p}{r} ) = \rep{Ml}{p}{Mr} $.
 \end{definition}
@@
 \begin{proof}
-  For any $P \in \Prof(\C, \C)$, there is a map $\eta : P \hto U \Phi_\M P$, given by $\eta(p) = \repthree{\id_A}{ p}{\id_B }$.
-
-  Suppose we have an element $\rep{l}{ p}{r} \in \Pastro_\M P(A,B)$. Then one can check that this element is equal to
-  \begin{align*}
-    \repthree{l}{ p}{r } = \Pastro_\M P(l, r) \alpha_{A, B, M} \; \eta(p)
+  For any $P \in \Prof(\C, \C)$, there is a map $\eta : P \hto U \Phi_\M P$, given by $\eta(p) = \repthree{\id_A}{p}{\id_B }$.
+
+  Suppose we have an element $\rep{l}{p}{r} \in \Pastro_\M P(A,B)$. Then one can check that this element is equal to
+  \begin{align*}
+    \repthree{l}{p}{r } = \Pastro_\M P(l, r) \alpha_{A, B, M} \; \eta(p)
   \end{align*}
@@
   \begin{align*}
-    \hat{f}(\rep{l}{ p}{r }) &= \hat{f}(\Pastro_\M P(l, r) \alpha_{A, B, M} \; \eta(p)) \\
+    \hat{f}(\rep{l}{p}{r }) &= \hat{f}(\Pastro_\M P(l, r) \alpha_{A, B, M} \; \eta(p)) \\
                                      &=T(l, r) \; \beta_{A, B, N} \; f(p)
@@
   \begin{align*}
-    \hat{f}\alpha_{A,B,N}(\rep{l}{ p}{r })
-    &= \hat{f}(\rep{Nl}{ p}{ Nr }) \\
+    \hat{f}\alpha_{A,B,N}(\rep{l}{p}{r })
+    &= \hat{f}(\rep{Nl}{p}{Nr }) \\
     &= T(Nl, Nr) \; \beta_{A, B, NM} \; f(p) \\
@@
     &= \beta_{A,B,N} T(l, r) \; \beta_{A, B, M} \; f(p) \\
-    &= \beta_{A,B,N} \hat{f} (\rep{l}{ p}{r })
+    &= \beta_{A,B,N} \hat{f} (\rep{l}{p}{r })
   \end{align*}
@@
 \begin{corollary}
-  A profunctor optic $p$ is determined by its component at $\Pastro_\M E_A$, and furthermore, this component is determined by its value on $\repfour{\id_A}{ \id_A}{\id_A}{\id_A } \in (U \Pastro_\M E_A)(A, A)$.
+  A profunctor optic $p$ is determined by its component at $\Pastro_\M E_A$, and furthermore, this component is determined by its value on $\repfour{\id_A}{\id_A}{\id_A}{\id_A } \in (U \Pastro_\M E_A)(A, A)$.
 \end{corollary}
@@
   This is the content of the first two isomorphisms above.
-Explicitly, suppose $\hat{p} = \rep{l}{ r }$ with $l : S \to MA$ and $r : MA \to S$.
+Explicitly, suppose $\hat{p} = \rep{l}{r }$ with $l : S \to MA$ and $r : MA \to S$.
 Then for any Tambara module $P$, the component of $p$ at $P$ is
@@
   \[
-    p_{\Pastro_\M E_A}(\repfour{\id_A}{ \id_A}{ \id_A}{\id_A }) = \repfour{l}{ \id_A}{\id_A}{ r }
+    p_{\Pastro_\M E_A}(\repfour{\id_A}{\id_A}{\id_A}{\id_A }) = \repfour{l}{\id_A}{\id_A}{r }
   \]
@@
 \begin{align*}
-  \Delta((f, g)) &= \repfour{f}{ \id_A}{\id_A}{ g}  \\
+  \Delta((f, g)) &= \repfour{f}{\id_A}{\id_A}{g}  \\
   \varepsilon((f, g)) &= gf
@@
 \begin{align*}
-  \Delta(\rep{l}{ r }) &= \repthree{l}{lr}{r } \\
-  \varepsilon(\rep{l}{ r }) &= rl
+  \Delta(\rep{l}{r }) &= \repthree{l}{lr}{r } \\
+  \varepsilon(\rep{l}{r }) &= rl
 \end{align*}
@@
 
-Prelenses that satisfy the first two laws correspond to pairs $\rep{l}{ r }$ such that $rl = \id_S$ and $\pi_2lr = \pi_2$.
+Prelenses that satisfy the first two laws correspond to pairs $\rep{l}{r }$ such that $rl = \id_S$ and $\pi_2lr = \pi_2$.
 \todo{prove?} This condition seems unavoidably tied to the product structure on $\C$; it is not clear whether this weakened notion of lens can be generalised to other optics.
@@
 
+\todo{Figure out the right numbering style}
+
 \bibliographystyle{alpha}

### 2018-06-13 paper.tex
More fiddling

@@
 \newcommand{\funzip}{\textsc{Unzip}}
+\newcommand{\fover}{\textsc{Over}}
 
@@
 \newcommand{\twice}{\mathsf{twice}}
+
+% Credit: Sam Buss
+\newbox\gnBoxA
+\newdimen\gnCornerHgt
+\setbox\gnBoxA=\hbox{$\ulcorner$}
+\global\gnCornerHgt=\ht\gnBoxA
+\newdimen\gnArgHgt
+\def\nameof #1{%
+    \setbox\gnBoxA=\hbox{$#1$}%
+    \gnArgHgt=\ht\gnBoxA%
+    \ifnum     \gnArgHgt<\gnCornerHgt \gnArgHgt=0pt%
+    \else \advance \gnArgHgt by -\gnCornerHgt%
+    \fi \raise\gnArgHgt\hbox{$\ulcorner$} \box\gnBoxA %
+    \raise\gnArgHgt\hbox{$\urcorner$}}
 
@@
   \item A definition of optics general enough to encompass lenses, setters, traversals, and others?
+  \item A definition of lawful optic that specialises in the correct way and allows us to easily derive ad-hoc laws for new kids of optic
   \item A universal property satisfied by the category of optics in the monoidal case
@@
   \item An attempt to isolate exactly what $\Set$-like properties are being used in various places
-  \item A couple of new avenues for generalising optics
+  \item New avenues for generalising optics
   \end{itemize}
@@
 This category was first defined in \cite[Section 6]{Doubles} to investigate the relationship between Tambara modules and the center of a monoidal category.
-There it is called the \emph{double} $\Double_l \C$ of a monoidal category, and our definition is identical, other than flipping the direction of the morphisms to match the existing work on lenses, and restricting our attention to the unenriched case.
+There it is called the \emph{double} of a monoidal category, and our definition is identical, other than flipping the direction of the morphisms to match the existing work on lenses and restricting our attention to the unenriched case.
 
@@
 
-For a fixed $M \in \M$, there is a map $\C(S, M A) \times \C(M A, S) \to \C(S, S)$ given by composition.
-This induces a map $\outside : \Optic_\M(S, A) \to \C(S, S)$, given equationally by $\outside(\rep{l}{r}) = l ; r$
-
-There are also maps two maps
-\begin{align*}
-  \once, \twice : \Optic_\M(S, A) \to \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S)
-\end{align*}
-defined by
-\begin{align*}
-  \once(\rep{l}{r}) &= \repthree{ l}{\id_{MA}}{r} \\
-  \twice(\rep{l}{r} \rangle) &= \repthree{l}{r;l}{r}
+Using the universal property of the coend, we define three maps:
+\begin{align*}
+  \outside &: \Optic_\M(S, A) \to \C(S, S) \\
+  \once, \twice &: \Optic_\M(S, A) \to \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S)
+\end{align*}
+by
+\begin{align*}
+  \outside(\rep{l}{r}) &= l;r \\
+  \once(\rep{l}{r}) &= \repthree{l}{\id_{MA}}{r} \\
+  \twice(\rep{l}{r}) &= \repthree{l}{r;l}{r}
 \end{align*}
@@
 
-We will see that in all the standard examples of optics, this specialises to the expected laws for that type of optic.
+We will see that in all the common examples of optics, this specialises to the expected laws for that variant of optic.
+
+\begin{remark}
+The above definition of lawful does not match neatly with the constant complement idea, which might instead require that $r;l = \id_{MA}$ for some $M$.
+I argue that $\once(p) = \twice(p)$ is the correct condition for a few reasons.
+
+The main reason is that it corresponds precisely to the ad-hoc lens laws with no additional requirements, whereas finding a complement for a lens requires further conditions on the category $\C$.
+
+Secondly, even if $r;l = \id_{MA}$ holds for a particular representative $\langle l, r \rangle$, the same is not likely to be true for a different representative.
+
+Finally, we will later see an interpretation of optics as morphisms between certain comonoid objects. Lawfulness corresponds exactly to a morphism being a comonoid morphism.
+\end{remark}
 
@@
   For the second, we must show
-  \[ \repthree{ l;(Ml')}{(Mr'); r;l;(Ml')}{(Mr') ; r } = \rep{l;(Ml')}{\id_{MNA}}{(Mr') ; r }. \]
+  \[ \repthree{ l;(Ml')}{(Mr'); r;l;(Ml')}{(Mr') ; r } = \repthree{l;(Ml')}{\id_{MNA}}{(Mr') ; r }. \]
 
@@
 Once we choose a particular monoidal action $\M \to [\C, \C]$, we find an isomorphism between the set of optics $(S, S') \hto (A, A')$ and a set $\mathbb{O}((S, S'), (A, A'))$ that is easier to describe.
-Ideally, we then find a similar description $\mathbb{D}(S, A)$ for the set \[ \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S)\] appearing in the definition of a lawful optic.
+Ideally, we then also find a simplified description $\mathbb{D}(S, A)$ for the set \[ \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S)\] appearing in the definition of a lawful optic.
 We can then ``read off'' what conditions on an element of $\mathbb{O}((S, S), (A, A))$ are needed to ensure that the corresponding element of $\Optic_\M(S, A)$ is lawful.
-
-\todo{As we get higher up in the hierarchy, the `ad-hoc' laws get closer to being the same as the coend laws}
+With no offence intended, we will call these more specific conditions the `ad-hoc' laws.
+
+\todo{There is a common pattern in some of these examples, where the evaluation-at-$A$ functor $-A : \M \to \C$ has a left or right adjoint. Is it worth abstracting this out?}
 
@@
 
-\todo{This last proposition should probably be deleted now}
-
-In favourable conditions, we can upgrade this result to show that the existence of a lens $S \hto A$ implies that $S \cong C \times A$ for some $C$.
+If we ask more of our category $\C$, we can upgrade this result to show that a lens $S \hto A$ implies the existence of a complement $\C$ with $S \cong C \times A$.
 This is a generalised from the argument given in~\cite[Corollary 13]{AlgebrasAndUpdateStrategies} for $\Set$.
@@
 \todo{There may be something generalisable here with ``monoidal factorisation systems''}
-
-\subsection{Linear Lenses}
-\newcommand{\ev}{\mathsf{ev}}
-\newcommand{\coev}{\mathsf{coev}}
-
-If $\C$ is closed monoidal, we can use a similar trick to eliminate the coends.
-
-\begin{align*}
-  \Optic_\otimes((S, S'), (A, A')) &= \int^{M \in \C} \C(S, M \otimes A) \times \C(M \otimes A', S') \\
-                                   &\cong \int^{M \in \C} \C(S, M \otimes A) \times \C(M, \homC(A',S')) \\
-                                   &\cong \C(S, \homC(A',S') \otimes A) \\
-                                   &=: \mathbb{O}((S, S'), (A, A'))
-\end{align*}
-where $\homC(A', S')$ denotes the internal hom. If $\C$ is cartesian, this is of course isomorphic to the pair of maps discussed in the previous section.
-
-For an optic, the corresponding element of $\mathbb{O}((S, S'), (A, A'))$ will be called $\funzip$.
-The above isomorphism sends $\funzip$ to the element $\rep{\funzip }{\ev_{A', S'} }$, where $\ev_{A', S'} : \homC(A',S') \otimes A' \to S'$ is the evaluation map.
-In the other direction, given $\rep{l}{r }$ we have $\funzip = (\tilde r \otimes A)l$ where $\tilde r : M \to \homC(A', S')$ denotes the transpose of $r$.
-
-We cannot possibly use the three $\fput$/$\fget$ style lens laws in this setting as we lack projections, but using the same techniques as for cartesian lenses above we can devise some new ones:
-
-\begin{proposition}
-  A linear lens $p : S \hto A$ is lawful iff the following two laws for $\funzip$ hold:
-  \begin{align*}
-    \ev_{A, S} \; \funzip &= \id_S && \textsc{(Rezip)} \\
-    (\coev_{\homC(A, S), A} \otimes A)\funzip &= ((\funzip \circ -) \otimes A)\funzip && \textsc{(ZipZip)}
-  \end{align*}
-  where \[ \funzip \circ - : \homC(A, S) \to \homC(A, \homC(A, S) \otimes A) \] denotes the internal composition. \todo{I obviously need better names for the laws}
-\end{proposition}
-\begin{proof}
-  We have an isomorphism:
-  \begin{align*}
-    & \int^{M_1, M_2 \in \C} \C(S, M_1 \otimes A) \times \C(M_1 \otimes A, M_2 \otimes A) \times \C(M_2 \otimes A, S) \\
-    &\cong \int^{M_1, M_2 \in \C} \C(S, M_1 \otimes A) \times \C(M_1, \homC(A, M_2 \otimes A)) \times \C(M_2, \homC(A, S)) \\
-    &\cong \int^{M_1 \in \C} \C(S, M_1 \otimes A) \times \C(M_1, \homC(A, \homC(A, S) \otimes A)) \\
-    &\cong \C(S, \homC(A, \homC(A, S) \otimes A) \otimes A)
-  \end{align*}
-  which evaluated on an element $\repthree{l}{c}{r }$ is given by
-  \begin{align*}
-    \Phi(\repthree{l}{c}{r}) &= (\widetilde{(\tilde{r} \otimes A)c} \otimes A)l
-  \end{align*}
-  Now suppose we are given an optic $p$ with corresponding element of $\mathbb{O}(S, A)$ is $\funzip$. Then \[\outside(\rep{\funzip }{\ev_{A, S} }) = \ev_{A, S} \; \funzip,\] giving the first law.
-
-  Now we evaluate $\Phi(\once(p))$ and $\Phi(\twice(p))$.
-  \begin{align*}
-    \Phi(\once(\rep{\funzip }{\ev_{A, S} }))
-    &= \Phi(\repthree{\funzip }{\id_{\homC(A,S) \otimes A}}{\ev_{A, S} }) \\
-    &= (\widetilde{(\tilde{\ev_{A, S}} \otimes A)\id_{\homC(A,S) \otimes A}} \otimes A)\funzip \\
-    &= (\coev_{\homC(A, S), A} \otimes A)\funzip \\
-    \Phi(\twice(\rep{\funzip }{\ev_{A, S} }))
-    &= \Phi(\repthree{\funzip }{\funzip \; \ev_{A, S}}{\ev_{A, S} }) \\
-    &= (\widetilde{(\tilde{\ev_{A, S}} \otimes A)(\funzip \; \ev_{A, S})} \otimes A)\funzip \\
-    &= (\widetilde{(\funzip \; \ev_{A, S})} \otimes A)\funzip \\
-    &= ((\funzip \circ -) \otimes A)\funzip
-  \end{align*}
-  \todo{Fix those overtildes}
-  So indeed the optic is lawful iff $(\coev_{\homC(A, S), A} \otimes A)\funzip = ((\funzip \circ -) \otimes A)\funzip$.
-\end{proof}
-
-\subsection{``Achromatic'' Lenses}
-\todo{http://oleg.fi/gists/posts/2018-03-28-achromatic-lens.html}
-
-Suppose $\C$ is cartesian closed and has finite coproducts. Then $\C$ acts on itself via $M \cdot A = (M \sqcup 1) \times A$.
-\begin{align*}
-  \Optic((S, S'), (A, A'))
-  &= \int^{M \in \C} \C(S, M \cdot A) \times \C(M \cdot A', S') \\
-  &= \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C((M \sqcup 1) \times A', S') \\
-  &\cong \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C((M \times A') \sqcup A', S') \\
-  &\cong \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C(M \times A', S') \times \C(A', S') \\
-  &\cong \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C(M, \homC(A', S')) \times \C(A', S') \\
-  &\cong \C(S, (\homC(A', S') \sqcup 1) \times A) \times \C(A', S') \\
-  &\cong \C(S, \homC(A', S') \sqcup 1) \times \C(S, A) \times \C(A', S') \\
-\end{align*}
-
-\begin{remark}
-  Equivalently, we could let $\M$ be the category of pointed objects of $\C$ and pointed maps between them.
-\end{remark}
-
-\todo{Is it worth working the laws out?}
 
@@
   Suppose $\C$ is cartesian closed and $F : \C \to \C$ is strong with respect to $\times$. Then for any objects $A, B \in \C$, \[\C(A, FB) \cong \Strong_\C(\times)(A \times \homC(B, -), F)\]
+naturally in $A$ and $F$. In other words, the functor $(A \mapsto A \times \homC(B, -)) : \C \to \Strong_\C$ is left adjoint to the evaluation-at-$B$ functor $-B : \Strong_\C \to \C$.
 \end{lemma}
 \begin{proof}
-  We construct the isomorphism $\Phi: C(A, FB) \cong \Strong_\C(\times)(A \times \homC(B, -), F)$ and its inverse $\Psi$.
-  Given a $f \in \C(A, FB)$, let $\Phi(f)$ be the natural transformation such that the component at $C$ is the composite
+  We construct the isomorphism $P : C(A, FB) \cong \Strong_\C(\times)(A \times \homC(B, -), F)$ and its inverse $Q$.
+  Given a $f \in \C(A, FB)$, let $P(f)$ be the natural transformation such that the component at $C$ is the composite
   \begin{align*}
@@
 
-  Conversely, given a strong natural transformation $\eta : A \times \homC(B, -) \Rightarrow F$, the component at $B$ is a function $\eta_B : A \times \homC(B, B) \to FB$; we define $\Psi(\eta) : A \to FB$ by $\Psi(\eta)(a) = \eta_B(a, \id_B)$
+  Conversely, given a strong natural transformation $\eta : A \times \homC(B, -) \Rightarrow F$, the component at $B$ is a function $\eta_B : A \times \homC(B, B) \to FB$; we define $Q(\eta) : A \to FB$ by $Q(\eta)(a) = \eta_B(a, \id_B)$
 
@@
   \begin{align*}
-    \Phi(\Psi(\eta))_C (a,g)
+    P(Q(\eta))_C (a,g)
     &= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(g, \Psi(\eta)(a))) \\
@@
   \begin{align*}
-    \Psi(\Phi(f))(a)
-    &= \Phi(f)_B(a, \id_B) \\
+    Q(P(f))(a)
+    &= P(f)_B(a, \id_B) \\
     &= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, B), B}(\id_B, f a))\\
@@
   \end{align*}
-\end{proof}
-
-This is a generalisation of~\cite[Proposition 2.2]{SecondOrderFunctionals}, isolating the properties of $\Set$ that are used. We can now construct setters:
+\todo{Naturality}
+\end{proof}
+
+This is a generalisation of~\cite[Proposition 2.2]{SecondOrderFunctionals}, isolating the properties of $\Set$ that are used. We can finally construct setters:
 
@@
 \end{align*}
-
-\todo{laws}
-
-\todo{This previous section might also work just with monoidal closed?}
+In the Haskell \lenslib{} library, the map $\homC(A, A) \to \homC(S,S)$ corresponding to a setter is called $\fover$: we think of a setter as allowing us to apply a function $A \to A$ over some parts of $S$.
+
+The laws for setters are a kind of `functoriality':
+
+\begin{proposition}
+A setter $p : S \hto A$ is lawful iff 
+\begin{align*}
+\fover \; \nameof{\id_A} &= \nameof{\id_S} \\
+({-} \circ =)(\fover \times \fover) &= \fover ({-} \circ =)
+\end{align*}
+where  $\circ$ denotes internal composition and $\nameof{\id_A} : 1 \to \homC(A, A)$ is the `name of' $\id_A$, and similarly for $\id_S$.
+\end{proposition}
+\begin{proof}
+We have a chain of isomorphisms
+\begin{align*}
+&\int^{M_1, M_2 \in \Strong_\C} \C(S, M_1 A) \times \C(M_1 A, M_2  A) \times \C(M_2 A, S) \\
+&\cong \int^{M_1, M_2 \in \Strong_\C} \Strong_\C(S \times \homC(A, -), M_1) \times \Strong_\C(M_1 A \times \homC(A, -), M_2) \times \C(M_2 A, S) \\
+&\cong \int^{M_2 \in \Strong_\C} \Strong_\C(S \times \homC(A, A) \times \homC(A, -), M_2) \times \C(M_2 A, S) \\
+&\cong \C(S \times \homC(A, A) \times \homC(A, A), S) \\
+&\cong \C(\homC(A, A) \times \homC(A, A), \homC(S,S))
+\end{align*}
+\todo{Worth writing out the rest?}
+\end{proof}
+
+\todo{This previous section might also work just with monoidal closed? I don't see where cartesianness was used.}
+
+\subsection{Linear Lenses}
+\newcommand{\ev}{\mathsf{ev}}
+\newcommand{\coev}{\mathsf{coev}}
+
+If $\C$ is closed monoidal, we can use a similar trick to eliminate the coends.
+
+\begin{align*}
+  \Optic_\otimes((S, S'), (A, A')) &= \int^{M \in \C} \C(S, M \otimes A) \times \C(M \otimes A', S') \\
+                                   &\cong \int^{M \in \C} \C(S, M \otimes A) \times \C(M, \homC(A',S')) \\
+                                   &\cong \C(S, \homC(A',S') \otimes A) \\
+                                   &=: \mathbb{O}((S, S'), (A, A'))
+\end{align*}
+where $\homC(A', S')$ denotes the internal hom. If $\C$ is cartesian, this is of course isomorphic to the pair of maps discussed in the previous section.
+
+For an optic, the corresponding element of $\mathbb{O}((S, S'), (A, A'))$ will be called $\funzip$.
+The above isomorphism sends $\funzip$ to the element $\rep{\funzip }{\ev_{A', S'}}$, where $\ev_{A', S'} : \homC(A',S') \otimes A' \to S'$ is the evaluation map.
+In the other direction, given $\rep{l}{r }$ we have $\funzip = (\tilde r \otimes A)l$ where $\tilde r : M \to \homC(A', S')$ denotes the transpose of $r$.
+
+We cannot possibly use the three $\fput$/$\fget$ style lens laws in this setting as we lack projections, but using the same techniques as for cartesian lenses above we can devise some new ones:
+
+\begin{proposition}
+  A linear lens $p : S \hto A$ is lawful iff the following two laws for $\funzip$ hold:
+  \begin{align*}
+    \ev_{A, S} \; \funzip &= \id_S && \textsc{(Rezip)} \\
+    (\coev_{\homC(A, S), A} \otimes A)\funzip &= ((\funzip \circ -) \otimes A)\funzip && \textsc{(ZipZip)}
+  \end{align*}
+  where \[ \funzip \circ - : \homC(A, S) \to \homC(A, \homC(A, S) \otimes A) \] denotes internal composition and \[\coev_{\homC(A, S), A} : \homC(A, S) \to \homC(A, \homC(A, S) \otimes A)\] is coevaluation.
+  \todo{I obviously need better names for the laws}
+\end{proposition}
+\begin{proof}
+  We have an isomorphism:
+  \begin{align*}
+    & \int^{M_1, M_2 \in \C} \C(S, M_1 \otimes A) \times \C(M_1 \otimes A, M_2 \otimes A) \times \C(M_2 \otimes A, S) \\
+    &\cong \int^{M_1, M_2 \in \C} \C(S, M_1 \otimes A) \times \C(M_1, \homC(A, M_2 \otimes A)) \times \C(M_2, \homC(A, S)) \\
+    &\cong \int^{M_1 \in \C} \C(S, M_1 \otimes A) \times \C(M_1, \homC(A, \homC(A, S) \otimes A)) \\
+    &\cong \C(S, \homC(A, \homC(A, S) \otimes A) \otimes A)
+  \end{align*}
+  which evaluated on an element $\repthree{l}{c}{r }$ is given by
+  \begin{align*}
+    \Phi(\repthree{l}{c}{r}) &= (\widetilde{(\tilde{r} \otimes A)c} \otimes A)l
+  \end{align*}
+  Now suppose we are given an optic $p$ with corresponding element of $\mathbb{O}(S, A)$ is $\funzip$. Then \[\outside(\rep{\funzip }{\ev_{A, S} }) = \ev_{A, S} \; \funzip,\] giving the first law.
+
+  Now we evaluate $\Phi(\once(p))$ and $\Phi(\twice(p))$.
+  \begin{align*}
+    \Phi(\once(\rep{\funzip }{\ev_{A, S} }))
+    &= \Phi(\repthree{\funzip }{\id_{\homC(A,S) \otimes A}}{\ev_{A, S} }) \\
+    &= (\widetilde{(\tilde{\ev_{A, S}} \otimes A)\id_{\homC(A,S) \otimes A}} \otimes A)\funzip \\
+    &= (\widetilde{(\id_{\homC(A, S)} \otimes A)} \otimes A)\funzip \\
+    &= (\coev_{\homC(A, S), A} \otimes A)\funzip \\
+    \Phi(\twice(\rep{\funzip }{\ev_{A, S} }))
+    &= \Phi(\repthree{\funzip }{\funzip \; \ev_{A, S}}{\ev_{A, S} }) \\
+    &= (\widetilde{(\tilde{\ev_{A, S}} \otimes A)(\funzip \; \ev_{A, S})} \otimes A)\funzip \\
+    &= (\widetilde{(\funzip \; \ev_{A, S})} \otimes A)\funzip \\
+    &= ((\funzip \circ -) \otimes A)\funzip
+  \end{align*}
+  \todo{Fix those overtildes}
+  So indeed the optic is lawful iff $\ev_{A, S} \; \funzip = \id_S$ and $(\coev_{\homC(A, S), A} \otimes A)\funzip = ((\funzip \circ -) \otimes A)\funzip$.
+\end{proof}
+
+\subsection{``Achromatic'' Lenses}
+\todo{http://oleg.fi/gists/posts/2018-03-28-achromatic-lens.html}
+
+Suppose $\C$ is cartesian closed and has finite coproducts. Then $\C$ acts on itself via $M \cdot A = (M \sqcup 1) \times A$.
+\begin{align*}
+  \Optic((S, S'), (A, A'))
+  &= \int^{M \in \C} \C(S, M \cdot A) \times \C(M \cdot A', S') \\
+  &= \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C((M \sqcup 1) \times A', S') \\
+  &\cong \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C((M \times A') \sqcup A', S') \\
+  &\cong \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C(M \times A', S') \times \C(A', S') \\
+  &\cong \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C(M, \homC(A', S')) \times \C(A', S') \\
+  &\cong \C(S, (\homC(A', S') \sqcup 1) \times A) \times \C(A', S') \\
+  &\cong \C(S, \homC(A', S') \sqcup 1) \times \C(S, A) \times \C(A', S')
+\end{align*}
+
+\begin{remark}
+  Equivalently, we could let $\M$ be the category of pointed objects of $\C$ and pointed maps between them.
+\end{remark}
+
+\todo{Worth writing out?}
 
@@
 A folklore variant of a prism is the \emph{affine traversal}, which allows access to a target that may or may not be present.
-These are described in~\cite{AffineTraversalPost}, and are there hypothesised to correspond to pairs of maps $\C(S, A \sqcup S') \times \C(S\times A', S')$.
+These are described in~\cite{AffineTraversalPost}, and it is suggested they correspond to pairs of maps $\C(S, A \sqcup S') \times \C(S\times A', S')$.
 This is not precisely correct, but very close:
@@
 
-This set includes into $\C(S, A \sqcup S') \times \C(S\times A', S')$, but the two are not equal. In other words, there are fewer affine traversals than expected.
+This set includes into $\C(S, A \sqcup S') \times \C(S\times A', S')$, but the two are not equal.
 
@@
   \end{align*}
-  that sends an object $D \in \D$ and optic $\rep{l}{r } : F \hto G$ in $\Optic_{[\D, \C]}$ to the optic $\rep{l_D}{r_D } : FD \hto GD$ in $\Optic_\C$.
+  that sends an object $D \in \D$ and optic $\rep{l}{r } : F \hto G$ in $\Optic_{[\D, \C]}$ to the optic $\rep{l_D}{r_D } : FD \hto GD$ in $\Optic_\C$. Further, this preserves lawfulness.
 \end{proposition}
@@
 \end{proof}
-
-Lawful optics in $\Optic_{[\D, \C]}$ are sent to lawful optics in $\Optic_\C$,  so we may restrict the domain to obtain a functor:
-\begin{align*}
-  \mathsf{mono} : \D \times \Lawful_{[\D, \C]} \to \Lawful_\C
-\end{align*}
-
-\todo{more to say?}
 
@@
 
+\todo{Maybe some of the long equational manipulations could be done by commutative diagram, using a pair of dashes to signal the start and end value?}
+
 \bibliographystyle{alpha}

### 2018-06-18 paper.tex
Work on Traversals section

@@
 \newcommand{\Cat}{\mathbf{Cat}}
+%\newcommand{\Hask}{\mathbf{Hask}}
 \newcommand{\Prof}{\mathbf{Prof}}
@@
 \newcommand{\Tele}{\mathbf{Tele}}
+\newcommand{\Tamb}{\mathbf{Tamb}}
+
+\newcommand{\Endo}{\mathbf{Endo}}
+\newcommand{\Strong}{\mathbf{Strong}}
+\newcommand{\Point}{\mathbf{Point}}
+\newcommand{\CoPoint}{\mathbf{CoPoint}}
+\newcommand{\Traversable}{\mathbf{Traversable}}
 
@@
 \newcommand{\Lawful}{\mathbf{Lawful}}
-\newcommand{\SemiOptic}{\mathbf{SemiOptic}}
+%\newcommand{\SemiOptic}{\mathbf{SemiOptic}}
 \newcommand{\Lens}{\mathbf{Lens}}
@@
 \newcommand{\Setter}{\mathbf{Setter}}
-\newcommand{\Hask}{\mathbf{Hask}}
-\newcommand{\Endo}{\mathbf{Endo}}
-\newcommand{\Strong}{\mathbf{Strong}}
-\newcommand{\Tamb}{\mathbf{Tamb}}
-\newcommand{\Point}{\mathbf{Point}}
-\newcommand{\CoPoint}{\mathbf{CoPoint}}
-\newcommand{\Traversable}{\mathbf{Traversable}}
+\newcommand{\Traversal}{\mathbf{Traversal}}
 
@@
 There therefore exists a finite chain of relations $lr = u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n = \psi A$.
-
-Suppose the first relation faces rightward, so there exists a $k$ and $\phi$ with $r;l = \phi_A;k$ and $u_2 = k;\phi_A$. Define $l' = l;\phi_A$ and $r' = k;r$. Then:
+Suppose the first relation faces rightward, so there exists a $k$ and $\phi$ with $r;l = \phi_A;k$ and $u_2 = k;\phi_A$.
+Define $l' = l;\phi_A$ and $r' = k;r$.
+Then:
 \begin{align*}
@@
 Once we choose a particular monoidal action $\M \to [\C, \C]$, we find an isomorphism between the set of optics $(S, S') \hto (A, A')$ and a set $\mathbb{O}((S, S'), (A, A'))$ that is easier to describe.
+We follow \cite{ProfunctorOptics} (and others) in calling elements of $\mathbb{O}$ \emph{concrete optics}.
+There is no canonical choice for this set; our primary goal is to find a way to eliminate the coend so that we no longer have to deal with equivalence classes of morphisms.
+
 Ideally, we then also find a simplified description $\mathbb{D}(S, A)$ for the set \[ \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S)\] appearing in the definition of a lawful optic.
-We can then ``read off'' what conditions on an element of $\mathbb{O}((S, S), (A, A))$ are needed to ensure that the corresponding element of $\Optic_\M(S, A)$ is lawful.
-With no offence intended, we will call these more specific conditions the `ad-hoc' laws.
+We can then ``read off'' what conditions on are needed on a concrete optic to ensure that the corresponding element of $\Optic_\M(S, A)$ is lawful.
+With no offence intended, we will call these more conditions the `ad-hoc' laws.
 
 \todo{There is a common pattern in some of these examples, where the evaluation-at-$A$ functor $-A : \M \to \C$ has a left or right adjoint. Is it worth abstracting this out?}
+
+We begin with the most common kinds of optic before moving to more exotic possibilities.
 
@@
   Suppose $\C$ has finite products, and let $\C$ act on itself via the bifunctor $\times : \C \times \C \to \C$.
-The \emph{category of lenses} $\Lens$ is the category of lawful optics with respect to this action: $\Lens = \Lawful_\times$.
+The \emph{category of lenses} $\Lens$ is the category of lawful optics with respect to this action.
 \end{definition}
@@
 If we ask more of our category $\C$, we can upgrade this result to show that a lens $S \hto A$ implies the existence of a complement $\C$ with $S \cong C \times A$.
-This is a generalised from the argument given in~\cite[Corollary 13]{AlgebrasAndUpdateStrategies} for $\Set$.
-
-\begin{proposition}
+This doesn't appear to follow purely from the ad-hoc lens laws---an argument using a definition of lawfulness based on constant complements.
+
+\begin{proposition}[{Generalisation of \cite[Corollary 13]{AlgebrasAndUpdateStrategies}}]
   Suppose $\C$ has pullbacks and that there is a morphism $x : 1 \to A$.
@@
   Suppose $\C$ has finite coproducts, and let $\C$ act on itself via the bifunctor $\sqcup : \C \times \C \to \C$.
-The \emph{category of prisms} is the category of lawful optics with respect to this action: $\Prism = \Lawful_\sqcup$.
+The \emph{category of prisms} is the category of lawful optics with respect to $\sqcup$.
 \end{definition}
@@
 \begin{definition}
-  Supposed $\C$ is cartesian closed and let $\Strong(\C)$ act on $\C$ by evaluation. The \emph{category of setters} $\Setter_\C$ is the category of optics for this action.
+  Supposed $\C$ is cartesian closed and let $\Strong(\C)$ act on $\C$ by evaluation. The \emph{category of setters} $\Setter_\C$ is the category of lawful optics for this action.
 \end{definition}
@@
 \todo{This previous section might also work just with monoidal closed? I don't see where cartesianness was used.}
+
+\subsection{Traversals}
+Let $\C = \Set$. \todo{define applicative/traversable functors}
+
+\begin{definition}
+The category $\Traversal_\C$ of traversals in $\C$ is the category of lawful optics for the action of $\Traversable_\C$ on $\C$ given by evaluation.
+\end{definition}
+
+(Yes, the names $\Traversal$ vs\@. $\Traversable$ are confusing.)
+
+It is known that traversable functors correspond to coalgebras for a particular parameterised comonad.
+See~\cite{AlgebrasForParameterisedMonads} for the relevant definitions of parameterised monads and algebras.
+
+\begin{proposition}[{\cite[Theorem 4.10, Proposition 5.4]{SecondOrderFunctionals}}]
+Traversable structures on a functor $T : \Set \to \Set$ correspond to parameterised coalgebra structures
+\begin{align*}
+t_{A, B} : TA \to UR^*_{A, B}(T B)
+\end{align*} 
+where $UR^*_{X,Y}$ is the parameterised comonad
+\begin{align*}
+UR^*_{X, Y} Z = \Sigma_{n\in \bN} X^n \times \homC(Y^n,Z)
+\end{align*}
+Moreover, this correspondence forms an isomorphism of categories between $\Traversable$ and the Eilenberg-Moore category of coalgebras for $UR^*_{-, -}$, which we denote $\C_T$.
+\end{proposition}
+
+\begin{remark}
+In~\cite[Section 2.3]{ProfunctorOptics}, it is claimed that a traversal $S \hto A$ exhibits an isomorphism \[S \cong \Sigma_n A^n \times \homC(A^n,S).\] This appears to be a misreading of~\cite[Proposition 5.4]{SecondOrderFunctionals}.
+\end{remark}
+
+The language of coalgebras now allows us to characterise traversals.
+
+\begin{lemma}
+  For any objects $A, B \in \Set$ and traversable functor $F$, \[\C(FA, B) \cong \Traversable(F, \Sigma_n (-)^n \times \homC(A^n,B))\]
+naturally in $B$ and $F$.
+In other words, the functor \[(B \mapsto \Sigma_n (-)^n \times \homC(A^n,B)) : \C \to \Traversable\] is right adjoint to the evaluation-at-$A$ functor $-A : \Traversable \to \C$.
+\end{lemma}
+\begin{proof}
+By~\cite[Proposition 6]{AlgebrasForParameterisedMonads}, there is a parameterised adjunction $L_T \dashv R_T$, where
+\begin{align*}
+L_T : \C^\op \times \C_T &\to \C \\
+(X, (F, f)) &\mapsto FX \\
+R_T : \C \times \C &\to \C_T \\
+(Y, Z) &\mapsto (UR^*_{-, Y} Z, \varepsilon) \\
+\end{align*}
+where $\varepsilon$ is the counit of $UR^*_{-, -}$. Evaluating these with the fixed parameter $A$, we get an ordinary adjunction 
+\begin{align*}
+L_T(A) : \C_T &\to \C \\
+(F, f) &\mapsto FA \\
+R_T(A) : \C &\to \C_T \\
+Z &\mapsto (UR^*_{-, A} Z, \varepsilon) \\
+\end{align*}
+But this is exactly the adjunction we were trying to show.
+\end{proof}
+
+We then reach the same characterisation of traversals as~\cite{ProfunctorOptics}:
+\begin{align*}
+\Optic_\Traversable((S, S'), (A, A')) &= \int^{F \in \Traversable} \C(S, F A) \times \C(F A', S') \\
+&\cong \int^{F \in \Traversable} \C(S, F A) \times \Traversable(F, \Sigma_n (-)^n \times \homC(A'^n,S')) \\
+&\cong \C(S, \Sigma_n A^n \times \homC(A'^n,S')) \\
+&=: \mathbb{O}((S, S'), (A, A'))
+\end{align*}
+
+\todo{laws}
+
+\begin{remark}
+\todo{todo?} A careful analysis would be needed to describe traversals in some other category, in particular, the description of $UR^*$ does not make sense if $\C$ is not locally cartesian closed.
+\end{remark}
+
+\begin{remark}
+Traversable functors can be described as a particular class of polynomial functors known as finitary containers. There may be something generalisable here with other classes of polynomial functors.
+\end{remark}
 
@@
 A folklore variant of a prism is the \emph{affine traversal}, which allows access to a target that may or may not be present.
-These are described in~\cite{AffineTraversalPost}, and it is suggested they correspond to pairs of maps $\C(S, A \sqcup S') \times \C(S\times A', S')$.
-This is not precisely correct, but very close:
 
@@
 \begin{remark}
-  It is important here that the morphisms in $\mathsf{Aff}$ are only those that arise from pairs of morphisms $P \to P'$ and $Q \to Q'$, although in principle there are other natural transformations between the corresponding functors $(P, Q) \cdot -$ and $(P', Q') \cdot -$.
+  It is important here that the morphisms in $\mathsf{Aff}$ are only those that arise from pairs of morphisms $P \to P'$ and $Q \to Q'$, although in principle there may be other natural transformations between the corresponding functors $(P, Q) \cdot -$ and $(P', Q') \cdot -$.
 \end{remark}
@@
 
-This set includes into $\C(S, A \sqcup S') \times \C(S\times A', S')$, but the two are not equal.
+We note that this contradicts the folklore description of affine traversals as pairs of maps $\C(S, A \sqcup S') \times \C(S\times A', S')$, see~\cite{AffineTraversalPost}.
+That set is in fact ``too large'': the provided map $S \times A' \to S$ must be defined even on elements of $S$ whose image under the first map $S \to A \sqcup S'$ lies in the right-hand component, which is not the case in our description.
 
@@
 \todo{Give an example of two elements of the set that correspond to the same affine traversal}
-
-\subsection{Traversals}
-\todo{todo}
 

### 2018-06-18 paper.tex
bib fixes and some other quibbles

@@
 
-\todo{Past work:
-  \begin{itemize}
-  \item The Haskell lens people: edwardk, shachaf, xplat, roconnor... (TODO: find out who these people are)
-  \item The Doubles paper
-  \item Bartosz's blog post which was written about the same time I started this. (Only tensor-like optics, no discussion of laws, confusion about enrichment(?))
-  \item The profunctor optics paper out of Oxford. (No generality, nothing categorical, no discussion of laws)
-  \item Very old Dialectica category stuff
-  \end{itemize}
-}
-
-\todo{Contributions:
-  \begin{itemize}
-  \item A definition of optics general enough to encompass lenses, setters, traversals, and others?
-  \item A definition of lawful optic that specialises in the correct way and allows us to easily derive ad-hoc laws for new kids of optic
-  \item A universal property satisfied by the category of optics in the monoidal case
-  \item A satisfying categorical description of lens laws
-  \item An attempt to isolate exactly what $\Set$-like properties are being used in various places
-  \item New avenues for generalising optics
-  \end{itemize}
-}
-
-A lens from $S$ to $A$ is a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$ that typically obeys three laws (whose names are in diagrammatic order):
+%\todo{Past work:
+%  \begin{itemize}
+%  \item The Haskell lens people: edwardk, shachaf (Shachaf Ben-Kiki), xplat, roconnor... (TODO: find out who these people are)
+%  \item The Doubles paper
+%  \item Bartosz's blog post which was written about the same time I started this. (Only tensor-like optics, no discussion of laws, confusion about enrichment(?))
+%  \item The profunctor optics paper out of Oxford. (No generality, nothing categorical, no discussion of laws)
+%  \item Very old Dialectica category stuff
+%  \end{itemize}
+%}
+
+In their most concrete form, a lens from $S$ to $A$ is a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$.
+Typically we want our lenses to obey the following laws (whose names should be considered in diagrammatic order):
 \begin{itemize}
@@
 \end{itemize}
-
-\todo{talk about ``constant complement'' idea}
-
-\todo{
+In some of the literature, lenses obeying these conditions are called \emph{very well-behaved}. Since this is the only set of conditions we are interested in, we will call such lenses \emph{lawful}.
+
+Lenses were discovered to be just one of a heirarchy of data accessors, including prisms, setters, traversals, and more.
+Each has a concrete description as a collection of certain maps, with attendant laws that make them well behaved.
+These are all implemented in the Haskell \lenslib{} library: see \cite{LensLibrary}.
+
+\todo{Contributions:
+  \begin{itemize}
+  \item A definition of optics general enough to encompass lenses, setters, traversals, and others
+  \item A definition of lawfulness that specialises in the correct way in all examples and allows us to easily derive ad-hoc laws for new kids of optic
+  \item A universal property satisfied by the category of optics in the monoidal case
+  \item A satisfying categorical description of lens laws as the homomorphism condition on a morphism between certain comonoids
+  \item An attempt to isolate exactly what $\Set$-like properties are being used in various places
+  \item New avenues for generalising optics
+  \end{itemize}
+}
+
 \subsection{(Co)ends and (Co)Yoneda}
-}
-If $\E$ is cocomplete, there is a formula for the coend as the coequaliser in the diagram
+
+In this paper we will make frequent use of the (co)end calculus. For a comprehensive introduction to ends and coends, see~\cite{CoendCofriend}. The most important results for us are:
+
+\begin{lemma}\label{lemma:calculate-coend}
+If $\E$ is cocomplete, the coend of $P : \M^\op \times \M \to \E$ can be calculated as the coequaliser in the diagram
 \[
   \begin{tikzcd}
-    \coprod_{M \to N} P(N, M) \ar[r,shift left=.75ex]  \ar[r,shift right=.75ex] & \coprod_{M \in \M} P(M, M) \ar[r] & \int^{M \in \M} P(M, M)
+    \displaystyle \coprod_{M \to N} P(N, M) \ar[r,shift left=.75ex]  \ar[r,shift right=.75ex] & \displaystyle\coprod_{M \in \M} P(M, M) \ar[r] & \displaystyle\int^{M \in \M} P(M, M)
   \end{tikzcd}
 \]
-where $P$ is a functor $\M^\op \times \M \to \E$.
+\qed
+\end{lemma}
+
+\begin{lemma}[Ninja Yoneda Lemma/Yoneda Reduction]
+For every functor $K : \C^\op \to \Set$ and $H : \C \to \Set$, we have the following natural isomorphisms:
+\begin{align*}
+K &\cong \int^c Kc \times \C(-,c) &
+K &\cong \int_c (Kc)^{\C(c,-)} \\
+H &\cong \int^c Hc \times \C(c,-)  &
+H &\cong \int_c (Hc)^{\C(-,c)}
+\end{align*}
+where the components of the isomorphisms at $X$ on the left are given by inclusion with the identity morphism $\C(X, X)$, and on the right projection onto the identity morphism.
+\qed
+\end{lemma}
+
+\begin{theorem}[Fubini Theorem]
+For a functor $F : \C^\op \times \C \times \D^\op \times \D \to \E$, there are canonical isomorphisms
+\begin{align*}
+\int^c \int^d F(c, c, d, d) \cong \int^{(c, d)} F(c, c, d, d) \cong \int^d \int^c F(c, c, d, d)
+\end{align*}
+\end{theorem}
+
+\todo{more?}
 
@@
 
-We begin by constructing the category of optics in a symmetric monoidal category $\C$.
-This category was first defined in \cite[Section 6]{Doubles} to investigate the relationship between Tambara modules and the center of a monoidal category.
-There it is called the \emph{double} of a monoidal category, and our definition is identical, other than flipping the direction of the morphisms to match the existing work on lenses and restricting our attention to the unenriched case.
+We begin by defining the category of optics in a symmetric monoidal category $\C$.
+This category was first defined in \cite[Section 6]{Doubles} as the `double' of a monoidal category.
+There it was used for an entirely different purpose---to investigate the relationship between Tambara modules and the `center' of a monoidal category.
+Our definition is identical, other than flipping the direction of the morphisms to match the existing work on lenses, and restricting our attention to the unenriched setting.
+
+This section contains no discussion of laws. The optic category is  generalising the pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$, with no additional conditions imposed.
 
 \begin{remark}
-  In what follows, we use the standard cheat of omitting associativity isomorphisms.
+  To avoid getting lost in the notation we will use the standard cheat of omitting associativity morphisms and trust that the dedicated reader could insert them everywhere they are needed.
 \end{remark}
@@
 
-Because this coend takes place in $\Set$, we can describe the set $\Optic_\C((S, S'), (A, A'))$ explicitly.
+Because this coend takes place in $\Set$, we can use Lemma \ref{lemma:calculate-coend} to describe the set $\Optic_\C((S, S'), (A, A'))$ explicitly.
 It is the set of pairs $(l, r)$, where $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, quotiented by the relation
@@
 \end{align*}
-where $l : S \to M \otimes A$, $r : N \otimes A' \to S'$ and $f : M \to N$.
-
-If $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\rep{l}{r} : (S, S') \hto (A, A')$ for the image of this pair in $\Optic_\C((S, S'), (A, A'))$, and say that $M$ is the complement for the representative.
+for any $l : S \to M \otimes A$, $r : N \otimes A' \to S'$ and $f : M \to N$.
+
+For a pair of maps $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\rep{l}{r} : (S, S') \hto (A, A')$ for their image in $\Optic_\C((S, S'), (A, A'))$, and say that $M$ is the complement for this representative.
 Optics will always be written with a crossed arrow $\hto$, to distinguish them from morphisms of $\C$.
@@
 \end{align*}
-The product in $\Set$ preserves colimits, so in particular coends. Using this fact, and the Fubini theorem for coends~\cite[Remark 1.9]{CoendCofriend}, the domain is isomorphic to
+The product in $\Set$ preserves colimits, so in particular coends. Using this fact and the Fubini theorem for coends, the domain is isomorphic to
 \begin{align*}
@@
 \begin{remark}
-  Note that the homsets of $\Optic_\C$ are given by a coend indexed by a possibly large category, so their existence is not guaranteed by the cocompleteness of $\Set$.
+  Note that the hom-sets of $\Optic_\C$ are given by a coend indexed by a possibly large category, so their existence is not guaranteed by the cocompleteness of $\Set$.
 We should be careful to only discuss $\Optic$ categories where we know that the coends exist by some other means, e.g., by exhibiting an isomorphism with some other set.
-For many---but not all---of the examples given later, we provide such an isomorphism.
-
-  \todo{How does the doubles paper get away with it?}
+For all of the examples given later, we provide such an isomorphism.
 \end{remark}
@@
 
-To capture the \texttt{Iso}s, \texttt{Traversal}s and \texttt{Setter}s of the Haskell \lenslib{} library (see~\ref{lawful-examples}), we generalise to the case of a monoidal action of one category on another.
+To capture more of the optic variants available in the Haskell \lenslib{} library, we generalise to the case of a monoidal action of one category on another.
 
@@
   Let $\C$ be a category and $(\M, \otimes, I)$ a monoidal category.
-An \emph{action of $\M$ on $\C$} is a strong monoidal functor $a : \M \to [\C, \C]$.
+An \emph{action of $\M$ on $\C$} is a monoidal functor $a : \M \to [\C, \C]$.
 The action of an object $M \in \M$ on $A \in \C$ is written $MA$.

### 2018-06-19 paper.tex
More intro, add a couple of diagrams

@@
 
+\usepackage[hidelinks]{hyperref} % Should be imported LAST
+
 \theoremstyle{plain}
@@
 \newcommand{\switched}{\mathbin{\tilde{\otimes}}}
+
+\newcommand{\conc}{\mathbb{C}}
+\newcommand{\conctwice}{\mathbb{C}^2}
 
@@
 
-In their most concrete form, a lens from $S$ to $A$ is a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$.
-Typically we want our lenses to obey the following laws (whose names should be considered in diagrammatic order):
+In their most concrete form, a \emph{lens} from $S$ to $A$ is a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$.
+From an engineering standpoint, such a lens allows us to ``zoom in'' to a small part $A$ of a larger $S$, manipulate it in some way, then ``zoom back out'' and have our changes in $A$ represented in $S$.
+
+Typically we want our lenses to obey the following laws (that are named in view of composition in diagrammatic order!): 
 \begin{itemize}
@@
 
-Lenses were discovered to be just one of a heirarchy of data accessors, including prisms, setters, traversals, and more.
-Each has a concrete description as a collection of certain maps, with attendant laws that make them well behaved.
-These are all implemented in the Haskell \lenslib{} library: see \cite{LensLibrary}.
+Lenses were discovered to be just one of a hierarchy of data accessors, including prisms, setters, traversals, and more, collectively called \emph{optics}.
+Each has a concrete description as a collection of certain maps, with attendant laws that make them (very) well behaved.
+We begin in Section~\ref{sec:optics} by defining the \emph{category of optics} in a sufficiently general way to encompass almost all the optic variants in use in the wild.
+Section~\ref{sec:lawful-optics} defines the equivalent of the lens laws for a general category of optics.
+Then in Section~\ref{sec:examples} we see how the general definitions specialise to the optic variants we know and love.
+
+The widely used Haskell \lenslib{} library contains implementations of all these optic variants: see \cite{LensLibrary}.
+There, optics are written in a form known as the \emph{profunctor encoding}, which at first glance is completely different to that given here in Section \ref{sec:optics}.
+As this note was being written, Bartosz Milewski~\cite{ProfunctorOpticsPost} independently described the relationship between some forms of optic and their profunctor encoding.
+In Section~\ref{sec:profunctor-optics} we extend this to more of the optic hierarchy and translate the lens laws into the profunctor setting.
+
+More recently, concrete lenses have found use in compositional game theory \cite{CompositionalGameTheory}.
+The $\fget$ function is thought of as mapping observations on the state of play to choices of what move to make.
+The $\fput$ function computes the utility of the moves that the players make.
+There is interest in generalising this to a probabilistic setting, but it is not clear what the right replacement for concrete lenses is.
+
+Much of what is known about lenses and their variants is folklore, and careful verification of some of their categorical properties has been lacking.
+The aim of the present paper is to fill this gap, with the hope that a better understanding of the general properties of these categories will make it easier to generalise to new and exotic settings.
+This is particularly important with the advent of linear types in Haskell, which enables a new branch of the lens family tree, and with the new applications in game theory.
 
@@
   \item A satisfying categorical description of lens laws as the homomorphism condition on a morphism between certain comonoids
-  \item An attempt to isolate exactly what $\Set$-like properties are being used in various places
-  \item New avenues for generalising optics
+  \item An attempt to isolate what $\Set$-like properties are being used in various places
   \end{itemize}
@@
 
-\subsection{(Co)ends and (Co)Yoneda}
+\subsection{(Co)ends and Yoneda Reduction}
 
@@
 
-\begin{lemma}\label{lemma:calculate-coend}
+\begin{lemma}[Coend as coequaliser]\label{lemma:calculate-coend}
 If $\E$ is cocomplete, the coend of $P : \M^\op \times \M \to \E$ can be calculated as the coequaliser in the diagram
@@
 \begin{align*}
-K &\cong \int^c Kc \times \C(-,c) &
-K &\cong \int_c (Kc)^{\C(c,-)} \\
-H &\cong \int^c Hc \times \C(c,-)  &
-H &\cong \int_c (Hc)^{\C(-,c)}
-\end{align*}
-where the components of the isomorphisms at $X$ on the left are given by inclusion with the identity morphism $\C(X, X)$, and on the right projection onto the identity morphism.
+K &\cong \int^C KC \times \C(-,C) &
+K &\cong \int_C (KC)^{\C(C,-)} \\
+H &\cong \int^C HC \times \C(C,-)  &
+H &\cong \int_C (HC)^{\C(-,C)}
+\end{align*}
+where the components of the isomorphisms at $X$ are given by inclusion with the identity morphism $\C(X, X)$ on the left, and projection onto the identity morphism on the right.
 \qed
@@
 \begin{align*}
-\int^c \int^d F(c, c, d, d) \cong \int^{(c, d)} F(c, c, d, d) \cong \int^d \int^c F(c, c, d, d)
+\int^C \int^D F(C,C,D,D) \cong \int^{(C,D)} F(C,C,D,D) \cong \int^D \int^C F(C,C,D,D)
 \end{align*}
@@
 
-\section{Optics}
-\label{sec-optics}
+\section{Optics}\label{sec:optics}
 
@@
   \begin{align*}
-    \Optic_\C((S, S'), (A, A')) := \int^{M \in \C} \C(S, M \otimes A) \times \C(M \otimes A', S')
+    \Optic_\otimes((S, S'), (A, A')) := \int^{M \in \C} \C(S, M \otimes A) \times \C(M \otimes A', S')
   \end{align*}
@@
 
-Because this coend takes place in $\Set$, we can use Lemma \ref{lemma:calculate-coend} to describe the set $\Optic_\C((S, S'), (A, A'))$ explicitly.
+Because this coend takes place in $\Set$, we can use Lemma \ref{lemma:calculate-coend} to describe the set $\Optic_\otimes((S, S'), (A, A'))$ explicitly.
 It is the set of pairs $(l, r)$, where $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, quotiented by the relation
@@
 
-For a pair of maps $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\rep{l}{r} : (S, S') \hto (A, A')$ for their image in $\Optic_\C((S, S'), (A, A'))$, and say that $M$ is the complement for this representative.
+For a pair of maps $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\rep{l}{r} : (S, S') \hto (A, A')$ for their image in $\Optic_\otimes((S, S'), (A, A'))$, and say that $M$ is the complement for this representative.
 Optics will always be written with a crossed arrow $\hto$, to distinguish them from morphisms of $\C$.
@@
 \begin{remark}
-  Elements of $\Optic_\C((S, S'), (A, A'))$ have an appealing
+  Elements of $\Optic_\otimes((S, S'), (A, A'))$ have an appealing
   interpretation as string diagrams with a ``hole'' missing. We draw the
@@
 \begin{proposition}\label{prop-optic-is-cat}
-  The above data form a category $\Optic_\C$.
+  The above data form a category $\Optic_\otimes$.
 \end{proposition}
@@
 \begin{remark}
-  Note that the hom-sets of $\Optic_\C$ are given by a coend indexed by a possibly large category, so their existence is not guaranteed by the cocompleteness of $\Set$.
+  Note that the hom-sets of $\Optic_\otimes$ are given by a coend indexed by a possibly large category, so their existence is not guaranteed by the cocompleteness of $\Set$.
 We should be careful to only discuss $\Optic$ categories where we know that the coends exist by some other means, e.g., by exhibiting an isomorphism with some other set.
@@
 \begin{proposition}
-  There is a functor $\iota : \C \times \C^\op \to \Optic_\C$, which is given on objects by $\iota(S, S') = (S, S')$ and for a morphism $(f, g) : (S, S') \to (A, A')$ by $\iota(f, g) = \rep{\lambda_A^{-1} f}{g \lambda_{A'}}$.
+  There is a functor $\iota : \C \times \C^\op \to \Optic_\otimes$, which is given on objects by $\iota(S, S') = (S, S')$ and for a morphism $(f, g) : (S, S') \to (A, A')$ by $\iota(f, g) = \rep{\lambda_A^{-1} f}{g \lambda_{A'}}$.
 \end{proposition}
@@
 
-  This preserves identities, as the identity on an object $(S, S')$ in $\Optic_\M$ is defined to be exactly $\rep{\lambda^{-1}_S}{\lambda_{S'}}$.
+  This preserves identities, as the identity on an object $(S, S')$ in $\Optic_\otimes$ is defined to be exactly $\rep{\lambda^{-1}_S}{\lambda_{S'}}$.
 To check functoriality, suppose we have $(f, g) : (S, S') \to (A, A')$ and $(f', g') : (A, A') \to (B, B')$ in $\C \times \C^\op$.
@@
 % \begin{theorem}
-%   $\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit is $(I, I)$, and the action on morphisms induced by
+%   $\Optic_\otimes$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit is $(I, I)$, and the action on morphisms induced by
 %   \begin{align*}
@@
 \begin{theorem}
-  $\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit object is $(I, I)$, and the action on a pair of morphisms $\rep{l}{r} : S \hto A$ and $\rep{l'}{r'} : T \hto B$ is given by:
+  $\Optic_\otimes$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit object is $(I, I)$, and the action on a pair of morphisms $\rep{l}{r} : S \hto A$ and $\rep{l'}{r'} : T \hto B$ is given by:
   \begin{center}
@@
 \begin{proposition}
-  If $\C$ is a strict symmetric monoidal category then $\Optic_\C$ is also strict.
-\end{proposition}
-\begin{proof}
-  The structure maps of $\Optic_\C$ are given by $\iota$ applied to the structure maps of $\C$.
-If the latter are identities, then so are the former---the identity morphisms in $\Optic_\C$ are by definition $\iota(\id_S, \id_S')$.
+  If $\C$ is a strict symmetric monoidal category then $\Optic_\otimes$ is also strict.
+\end{proposition}
+\begin{proof}
+  The structure maps of $\Optic_\otimes$ are given by $\iota$ applied to the structure maps of $\C$.
+If the latter are identities, then so are the former---the identity morphisms in $\Optic_\otimes$ are by definition $\iota(\id_S, \id_S')$.
 \end{proof}
@@
 \begin{proposition}
-  $\iota : \C \times \C^\op \to \Optic_\C$ is a strict monoidal functor.
-\end{proposition}
-\begin{proof}
-  This is clear, as the structure morphisms in $\Optic_\C$ are exactly the structure morphisms in $\C \times \C^\op$ under $\iota$.
+  $\iota : \C \times \C^\op \to \Optic_\otimes$ is a strict monoidal functor.
+\end{proposition}
+\begin{proof}
+  This is clear, as the structure morphisms in $\Optic_\otimes$ are exactly the structure morphisms in $\C \times \C^\op$ under $\iota$.
 \end{proof}
@@
 % \begin{proposition}
-%   Any isomorphism $p : (S, S') \hto (A, A')$ in $\Optic_\C$ is of the form $\iota(f, g)$ for two isomorphisms $S \to A$ and $A' \to S'$ in $\C$.
+%   Any isomorphism $p : (S, S') \hto (A, A')$ in $\Optic_\otimes$ is of the form $\iota(f, g)$ for two isomorphisms $S \to A$ and $A' \to S'$ in $\C$.
 % \end{proposition}
@@
 
-There is some further useful structure in $\Optic_\C$.
+There is some further useful structure in $\Optic_\otimes$.
 \begin{proposition}\label{prop-costates}
@@
   \begin{align*}
-    \Optic_\C((S, S'), (I, I))
+    \Optic_\otimes((S, S'), (I, I))
     &= \int^{M \in \C} \C(S, M \otimes I) \times \C(M \otimes I, S') \\
@@
 
-\todo{Is there a relationship between $\Optic_\C/(I, I)$ and $[2, \C]$?}
+\todo{Is there a relationship between $\Optic_\otimes/(I, I)$ and $[2, \C]$?}
 
@@
   \begin{align*}
-    \Optic_\C((I,I), (A,A'))
+    \Optic_\otimes((I,I), (A,A'))
     &= \int^{M \in \C} \C(I, M \otimes A) \times \C(M \otimes A', I) \\
@@
 \begin{proposition}\label{prop-change-of-action-monoidal}
-  A monoidal functor $F : \C \to \D$ induces a functor $\Optic(F) : \Optic_\C \to \Optic_\D$.
+  A monoidal functor $F : \C \to \D$ induces a functor $\Optic(F) : \Optic_\otimes \to \Optic_\D$.
 \end{proposition}
@@
 
-We assume in this section that $\C$ is a \emph{strict} symmetric monoidal category.
-It will be convenient to equip $\Optic_\C$ with a slightly different symmetric monoidal structure.
-The universal property for $\Optic_\C$ given in this section is an argument for this being the ``morally correct'' tensor, although it does seem a little strange.
+We assume in this section that $\C$ is a \emph{strict} symmetric monoidal category. It will be convenient to equip $\Optic_\otimes$ with a slightly different symmetric monoidal structure.
 
 \begin{definition}
-  The \emph{switched} monoidal product on $\Optic_\C$ is given on objects by
+  The \emph{switched} monoidal product on $\Optic_\otimes$ is given on objects by
   \begin{align*}
@@
 
+The universal property for $\Optic_\otimes$ given in this section is an argument for this being the ``morally correct'' tensor, although it does seem a little strange.
+When we later discuss lawful optics, we must use the unswitched tensor to maintain the invariant that a objects are of the form $(X, X)$.
+
 \begin{proposition}
-  $(\Optic_\C, \switched, (I, I))$ is a symmetric monoidal category that is monoidally equivalent to $\Optic_\C$ with the unswitched tensor.
-\end{proposition}
-\begin{proof}
-  The proof that $(\Optic_\C, \switched, (I, I))$ is symmetric monoidal is nearly identical to that for the unswitched tensor.
+  $(\Optic_\otimes, \switched, (I, I))$ is a symmetric monoidal category that is monoidally equivalent to $\Optic_\otimes$ with the unswitched tensor.
+\end{proposition}
+\begin{proof}
+  The proof that $(\Optic_\otimes, \switched, (I, I))$ is symmetric monoidal is nearly identical to that for the unswitched tensor.
 Note that due to the switching, the structure morphisms are slightly different:
@@
 
-  The categories are monoidally equivalent via the identity functor \[I : (\Optic_\C, \switched, (I, I)) \to (\Optic_\C, \otimes, (I, I)),\] where the structure isomorphisms are given by
+  The categories are monoidally equivalent via the identity functor \[I : (\Optic_\otimes, \switched, (I, I)) \to (\Optic_\otimes, \otimes, (I, I)),\] where the structure isomorphisms making this functor monoidal are given by
   \begin{align*}
@@
 \begin{remark}
-  Just as in the unswitched case, if $\C$ is a strict monoidal category than so is $(\Optic_\C, \switched, (I, I))$.
+  Just as in the unswitched case, if $\C$ is a strict monoidal category than so is $(\Optic_\otimes, \switched, (I, I))$.
 \end{remark}
@@
 \begin{proposition}
-  $\Optic_\C$ forms a teleological category, where:
+  $\Optic_\otimes$ forms a teleological category, where:
   \begin{itemize}
@@
 \begin{proof}
-  We must show that for a symmetric monoidal functor $F : \C \to \D$, the induced functor $F : \Optic_\C \to \Optic_\D$ is teleological.
+  We must show that for a symmetric monoidal functor $F : \C \to \D$, the induced functor $F : \Optic_\otimes \to \Optic_\D$ is teleological.
 
@@
 
-To establish the universal property of $\Optic_\M$, we will
+To establish the universal property of $\Optic_\otimes$, we will
 
@@
   \end{align*}
-  where $j : \C \to \Optic_\C$ is the functor $j(A) := \iota(A, I)$.
+  where $j : \C \to \Optic_\otimes$ is the functor $j(A) := \iota(A, I)$.
 \end{proposition}
@@
   Suppose $\C$ is a strict symmetric monoidal category and $\T$ is a teleological category.
-For all symmetric monoidal functors $F : \C \to \T_d$, there exists a teleological functor $K : \Optic_\C \to \T$, unique up to isomorphism, such that $Kj \cong F$.
+For all symmetric monoidal functors $F : \C \to \T_d$, there exists a teleological functor $K : \Optic_\otimes \to \T$, unique up to isomorphism, such that $Kj \cong F$.
 \end{theorem}
@@
   \end{align*}
+  The diagram for $K\rep{l}{r}$ in $\T$ is as follows:
+  \begin{center}
+    \input{diagrams/k-generic-optic.tikz}
+  \end{center}
 
@@
   \end{align*}
-  Then: \todo{maybe do as string diagram}
-  \begin{align*}
-    K\rep{(f \otimes A) l}{r}
-    &= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F(s_{M,A}(f \otimes A)l) \otimes (F(rs_{A',M}))^* ) \\
-    &= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F((A \otimes f)s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
-    % &= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(FA \otimes Ff \otimes FM \otimes FA')(F(s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
-    &= (FA \otimes (\varepsilon_{FM} (Ff \otimes FM)) \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
-    &= (FA \otimes (\varepsilon_{FN} (FN \otimes (Ff)^*)) \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
-    &= (FA \otimes \varepsilon_{FN} \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(rs_{A',M}(A' \otimes f)))^* ) \\
-    &= (FA \otimes \varepsilon_{FN} \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(r(f \otimes A')s_{A',N}))^* ) \\
-    &= K\rep{ l}{r (f \otimes A')}
-  \end{align*}
-  \todo{functoriality} \todo{monoidal} \todo{preserves dualisable morphisms} \todo{preserves counit}
+  Then well definedness is shown by the equivalence of the diagrams
+  \begin{center}
+    \input{diagrams/k-well-defined-left.tikz}
+    \qquad \raisebox{1.5cm}{$=$} \qquad
+    \input{diagrams/k-well-defined-right.tikz}
+  \end{center}
+  using naturality of the symmetry and extranaturality of the counit.
+%\todo{maybe do as string diagram}
+%  \begin{align*}
+%    K\rep{(f \otimes A) l}{r}
+%    &= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F(s_{M,A}(f \otimes A)l) \otimes (F(rs_{A',M}))^* ) \\
+%    &= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F((A \otimes f)s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
+%    % &= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(FA \otimes Ff \otimes FM \otimes FA')(F(s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
+%    &= (FA \otimes (\varepsilon_{FM} (Ff \otimes FM)) \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
+%    &= (FA \otimes (\varepsilon_{FN} (FN \otimes (Ff)^*)) \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
+%    &= (FA \otimes \varepsilon_{FN} \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(rs_{A',M}(A' \otimes f)))^* ) \\
+%    &= (FA \otimes \varepsilon_{FN} \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(r(f \otimes A')s_{A',N}))^* ) \\
+%    &= K\rep{ l}{r (f \otimes A')}
+%  \end{align*}
+  \todo{todo: functoriality, monoidality, preserves dualisable morphisms, preserves counit}
+
   \todo{uniqueness} 
@@
 
-\section{Lawful Optics}
+\section{Lawful Optics}\label{sec:lawful-optics}
 \todo{intro}
@@
 This is an appealing description from a string diagram standpoint, but I do not know if there is a similar description for the second law.
-\todo{Something to do with embedding $\Optic_\C$ into a compact closed category then using the unit to compose the lenses vertically?
+\todo{Something to do with embedding $\Optic_\otimes$ into a compact closed category then using the unit to compose the lenses vertically?
 Should I draw a picture of this?}
@@
   We conclude that composition preserves lawfulness, so $\Lawful_\M$ is indeed a subcategory of $\Optic_\M$.
+\end{proof}
+
+\begin{proposition}
+  In the case that $\C$ is symmetric monoidal and $\M = \C$ acts by left-tensor, then $\Lawful_\otimes$ is symmetric monoidal with the unswitched tensor.
+\end{proposition}
+\begin{proof}
+\todo{todo}
 \end{proof}
@@
 
-The above argument has a similar form to some that appear in \cite{OnTheTrace}, which considered (among other things) coends of the form $\int^{c \in \C} \C(c, Fc)$ for an endofunctor $F : \C \to \C$.
-
-\section{Examples}
-\label{lawful-examples}
+The above argument has a similar form to those that appear in \cite{OnTheTrace}, which considered (among other things) coends of the form $\int^{c \in \C} \C(c, Fc)$ for an endofunctor $F : \C \to \C$.
+
+\section{Examples}\label{sec:examples}
 
 The general pattern is as follows.
-Once we choose a particular monoidal action $\M \to [\C, \C]$, we find an isomorphism between the set of optics $(S, S') \hto (A, A')$ and a set $\mathbb{O}((S, S'), (A, A'))$ that is easier to describe.
-We follow \cite{ProfunctorOptics} (and others) in calling elements of $\mathbb{O}$ \emph{concrete optics}.
+Once we choose a particular monoidal action $\M \to [\C, \C]$, we find an isomorphism between the set of optics $(S, S') \hto (A, A')$ and a set $\conc((S, S'), (A, A'))$ that is easier to describe.
+We follow \cite{ProfunctorOptics} (and others) in calling elements of $\conc$ \emph{concrete optics}.
 There is no canonical choice for this set; our primary goal is to find a way to eliminate the coend so that we no longer have to deal with equivalence classes of morphisms.
 
-Ideally, we then also find a simplified description $\mathbb{D}(S, A)$ for the set \[ \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S)\] appearing in the definition of a lawful optic.
+Ideally, we then also find a simplified description $\conctwice(S, A)$ for the set \[ \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S)\] appearing in the definition of a lawful optic.
 We can then ``read off'' what conditions on are needed on a concrete optic to ensure that the corresponding element of $\Optic_\M(S, A)$ is lawful.
@@
                                   &\cong \int^{M \in \C} \C(S, M) \times \C(S, A) \times \C(M \times A', S') && \text{(universal property of product)} \\
-                                  &\cong \C(S, A) \times \C(S \times A', S') && \text{(co-Yoneda)} \\
-                                  &=: \mathbb{O}((S, S'), (A, A'))
-\end{align*}
-
-Explicitly this isomorphism states that, given an optic $\rep{l}{r } : (S, S') \hto (A, A')$, the corresponding element of $\mathbb{O}((S, S'), (A, A'))$ is the pair $(\fget, \fput)$, where $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
+                                  &\cong \C(S, A) \times \C(S \times A', S') && \text{(Yoneda reduction)}
+\end{align*}
+
+This last set is the set of concrete lenses $\conc_\times((S, S'), (A, A'))$.
+Explicitly this isomorphism states that, given an optic $\rep{l}{r } : (S, S') \hto (A, A')$, the corresponding element of $\conc_\times((S, S'), (A, A'))$ is the pair $(\fget, \fput)$, where $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
 In the other direction, given $(\fget, \fput)$, the corresponding optic has representative $\rep{[\id_S, \fget]}{\fput}$.
@@
   the same treatment as $\Optic_\times(S, A)$. By the same sorts of arguments as above \todo{is this worth writing out?}, this is isomorphic to
-  \[\mathbb{D}(S, A) := \C(S, A) \times \C(S \times A, A) \times \C(S \times A \times A, S)\]
+  \[\conctwice_\times(S, A) := \C(S, A) \times \C(S \times A, A) \times \C(S \times A \times A, S)\]
   with the isomorphism given by
@@
 
+\begin{remark}
+Much of the work on bidirectional transformations \cite{CombinatorsForBidirectionalTreeTransformations} considers lenses that are only `well-behaved', not `very well-behaved': they obey the $\fput\fget$ and $\fget\fput$ laws but not the $\fput\fput$ law.
+
+For example, the ``change counter'' lens $\bN \times A \hto A$ from~\cite{AClearPictureOfLensLaws} has $\fput$ and $\fget$ given by:
+  \begin{align*}
+    \fget(n, a) &= a \\
+    \fput((n, a), a') &= \begin{cases}
+      (n, a) & \text{if } a = a' \\
+      (n+1, a') & \text{otherwise}
+    \end{cases}
+  \end{align*}
+  This example is typical of (merely) well-behaved lenses: there is metadata stored alongside the target of a lens that mutates as the lens is used.
+
+Lenses that satisfy the first two laws correspond to pairs $\rep{l}{r}$ such that $rl = \id_S$ and $\pi_2lr = \pi_2$.
+This condition seems unavoidably tied to the product structure on $\C$; there is no obvious way generalise this to other optics variants.
+\end{remark}
+
+%\begin{example}
+%  A minimal example of a lens that obeys $\fget\fput$ and $\fput\fget$ but not $\fput\fput$ is the following. Let $p : \{A,B,C\} \hto \{X, Y\}$ be the lens with
+%  \begin{align*}
+%    \fget : \{A,B,C\} &\to \{X, Y\} \\
+%    A &\mapsto X \\
+%    B &\mapsto X \\
+%    C &\mapsto Y
+%  \end{align*}
+%  \begin{align*}
+%    \fput : \{A,B,C\} \times \{X, Y\} &\to \{A,B,C\} \\
+%    (A,X) &\mapsto A \\
+%    (B,X) &\mapsto B \\
+%    (C,X) &\mapsto B \\
+%    (A,Y) &\mapsto C \\
+%    (B,Y) &\mapsto C \\
+%    (C,Y) &\mapsto C
+%  \end{align*}
+%\end{example}
+
 \subsection{Prisms}
@@
                                   &\cong \int^{M \in \C} \C(S, M \sqcup A) \times \C(M, S') \times \C(A, S') && \text{(universal property of coproduct)} \\
-                                  &\cong \C(S, S' \sqcup A) \times \C(A', S') && \text{(co-Yoneda)}
+                                  &\cong \C(S, S' \sqcup A) \times \C(A', S') && \text{(Yoneda reduction)}
 \end{align*}
@@
 \begin{example}
-  \emph{Any} functor $\Set \to \Set$ has a unique strength with respect to the cartesian product, so this concept is invisible for Haskell \texttt{Functor}s. \todo{ref}
+  \emph{Any} functor $\Set \to \Set$ has a unique strength with respect to the cartesian product, so this concept is invisible for Haskell \texttt{Functor}s. 
 \end{example}
@@
 
+Experts will recognise $UR^*_{-, -}$ as the free applicative functor \cite{FreeApplicativeFunctors} on the functor $R_{X,Y} Z = X \times Y \to Z$.
+
 \begin{remark}
@@
 R_T : \C \times \C &\to \C_T \\
-(Y, Z) &\mapsto (UR^*_{-, Y} Z, \varepsilon) \\
+(Y, Z) &\mapsto (UR^*_{-, Y} Z, \varepsilon)
 \end{align*}
@@
 R_T(A) : \C &\to \C_T \\
-Z &\mapsto (UR^*_{-, A} Z, \varepsilon) \\
+Z &\mapsto (UR^*_{-, A} Z, \varepsilon)
 \end{align*}
@@
 &\cong \int^{F \in \Traversable} \C(S, F A) \times \Traversable(F, \Sigma_n (-)^n \times \homC(A'^n,S')) \\
-&\cong \C(S, \Sigma_n A^n \times \homC(A'^n,S')) \\
-&=: \mathbb{O}((S, S'), (A, A'))
+&\cong \C(S, \Sigma_n A^n \times \homC(A'^n,S'))
 \end{align*}
@@
 
-If $\C$ is closed monoidal, we can use a similar trick to eliminate the coends.
+If $\C$ is closed monoidal, but not necessarily cartesian, we can use the tensor-hom adjunction to eliminate the coend:
 
@@
                                    &\cong \C(S, \homC(A',S') \otimes A) \\
-                                   &=: \mathbb{O}((S, S'), (A, A'))
 \end{align*}
@@
 
-For an optic, the corresponding element of $\mathbb{O}((S, S'), (A, A'))$ will be called $\funzip$.
+For an optic, the corresponding element of $\conc_\otimes((S, S'), (A, A'))$ will be called $\funzip$.
 The above isomorphism sends $\funzip$ to the element $\rep{\funzip }{\ev_{A', S'}}$, where $\ev_{A', S'} : \homC(A',S') \otimes A' \to S'$ is the evaluation map.
@@
   \end{align*}
-  Now suppose we are given an optic $p$ with corresponding element of $\mathbb{O}(S, A)$ is $\funzip$. Then \[\outside(\rep{\funzip }{\ev_{A, S} }) = \ev_{A, S} \; \funzip,\] giving the first law.
+  Now suppose we are given an optic $p$ with corresponding element of $\conc_\otimes(S, A)$ is $\funzip$. Then \[\outside(\rep{\funzip }{\ev_{A, S} }) = \ev_{A, S} \; \funzip,\] giving the first law.
 
@@
   \begin{align*}
-    \mathsf{mono} : \D \times \Optic_{[\D, \C]} \to \Optic_\C
-  \end{align*}
-  that sends an object $D \in \D$ and optic $\rep{l}{r } : F \hto G$ in $\Optic_{[\D, \C]}$ to the optic $\rep{l_D}{r_D } : FD \hto GD$ in $\Optic_\C$. Further, this preserves lawfulness.
+    \mathsf{mono} : \D \times \Optic_{[\D, \C]} \to \Optic_\otimes
+  \end{align*}
+  that sends an object $D \in \D$ and optic $\rep{l}{r } : F \hto G$ in $\Optic_{[\D, \C]}$ to the optic $\rep{l_D}{r_D } : FD \hto GD$ in $\Optic_\otimes$. Further, this preserves lawfulness.
 \end{proposition}
@@
 There is also an analogous notion of optics of composites of functors.
+
+\subsection{Effectful Optics}
+\todo{todo}
+Many attempts~\cite{ReflectionsOnMonadicLenses} \todo{more refs} to define effectful lenses have wrapped the result of one or both of $\fget$ and $\fput$ with a monad.
+There are disadvantages to this approach: it is not obvious what the laws ought to be and there is no clear generalisation to other varieties of optic.
+The definition of optic given in Section~\ref{sec:optics} suggests we instead set $\C$ to be the Kleisli category of some effectful monad.
+
+\subsection{Degenerate Optics}
+\todo{This doesn't work yet:}
+
+The Haskell lens library has some other `optics' that aren't really optics, but still integrate nicely with the rest of the ecosystem, e.g. Getters, Reviews and Folds.
+
+Getters $(S, S') \hto (A, A')$ are supposed to correspond to morphisms $S \to A$.
+These cannot fit nicely into the coend formalism, as there is always the function $\outside : \Optic_\M((S, S), (A, A')) \to \C(S, S')$.
+
+There are some ways to jam it in though, in the specific case of $(S, S) \to (A, A')$, if we set $\M$ to be the category of copointed functors $\C \to \C$.
+Here copointed means the slice category $[\C, \C] / \id_\C$.
+
+Then I claim that
+\begin{align*}
+  \int^{F \in \mathsf{Copointed}} \C(S, FA) \times \C(FA, S) \cong \C(S, A) \times \C(S, S)
+\end{align*}
+So that the set of `lawful' getters is exactly $\C(S, A)$.
+
+Free copointed on $F$ is exactly $F \times \id_\C$
+The functor $\mathsf{Copointed} \to [\C, \C]$ has a right adjoint given by $F \mapsto F \times \id_\C$. Copointed map $F \to G \times \id_\C$ is the same as an uncopointed map $F \to G$
+
+For $l, r : \C(S, FA) \times \C(FA, S)$, the map $r$ is equal to
+\[
+  FA \xrightarrow{[\id_{FA}, \mathsf{copoint}]} FA \times A \xrightarrow{\pi_1} FA \to S
+\]
+But that first map is the component at $A$ of a copointed natural transformation (the unit of the adjunction). So $l, r$ is equal to
+\begin{align*}
+  S \to FA \xrightarrow{[\id_{FA}, \mathsf{copoint}]} FA \times A\\
+  FA \times A \xrightarrow{\pi_1} FA \to S
+\end{align*}
 
@@
 
-\section{Profunctor Optics}
+\section{Profunctor Optics}\label{sec:profunctor-optics}
 The Haskell \lenslib{} library implements optics using what is known as the \emph{profunctor encoding}. Lenses are defined as follows:
@@
 
-The precise connection between this encoding and the previous one was investigated independently in~\cite{ProfunctorOpticsPost}.
-In this section, we extend these ideas to the case of a monoidal action and include an analysis of lawful optics in this setting.
+\todo{explain why this encoding is used}
 
@@
     &(U-)(A,A) \\
-    \cong \;&\int_{X,Y \in \C} \Set(\C(X,A) \times \C(A,Y), (U-)(X,Y)) && \text{(by Yoneda (un)reduction twice)} \\
+    \cong \;&\int_{X,Y \in \C} \Set(\C(X,A) \times \C(A,Y), (U-)(X,Y)) && \text{(by Yoneda reduction twice)} \\
     =\;&\int_{X,Y \in \C} \Set(E_A(X,Y), (U-)(X,Y)) && \text{(by definition)}\\
@@
     = \;&\int^{M \in \M} \int^{C,D \in \C} \C(S, MC) \times \C(C,A) \times \C(A,D) \times \C(MD,S) \\
-    \cong \;&\int^{M \in \M} \C(S, MA) \times \C(MA, S)  && \text{(by co-Yoneda twice)} \\
+    \cong \;&\int^{M \in \M} \C(S, MA) \times \C(MA, S)  && \text{(by Yoneda reduction twice)} \\
     = \;&\Optic_\M(S, A)
@@
 
-\section{Misc}
-\subsection{Degenerate Optics}
-The Haskell lens library has some other `optics' that aren't really optics, but still integrate nicely with the rest of the ecosystem, e.g. Getters, Reviews and Folds.
-
-Getters $(S, S') \hto (A, A')$ are supposed to correspond to morphisms $S \to A$.
-These cannot fit nicely into the coend formalism, as there is always the function $\outside : \Optic_\M((S, S), (A, A')) \to \C(S, S')$.
-
-There are some ways to jam it in though, in the specific case of $(S, S) \to (A, A')$, if we set $\M$ to be the category of copointed functors $\C \to \C$.
-Here copointed means the slice category $[\C, \C] / \id_\C$.
-
-Then I claim that
-\begin{align*}
-  \int^{F \in \mathsf{Copointed}} \C(S, FA) \times \C(FA, S) \cong \C(S, A) \times \C(S, S)
-\end{align*}
-So that the set of `lawful' getters is exactly $\C(S, A)$.
-
-Free copointed on $F$ is exactly $F \times \id_\C$
-The functor $\mathsf{Copointed} \to [\C, \C]$ has a right adjoint given by $F \mapsto F \times \id_\C$. Copointed map $F \to G \times \id_\C$ is the same as an uncopointed map $F \to G$
-
-For $l, r : \C(S, FA) \times \C(FA, S)$, the map $r$ is equal to
-\[
-  FA \xrightarrow{[\id_{FA}, \mathsf{copoint}]} FA \times A \xrightarrow{\pi_1} FA \to S
-\]
-But that first map is the component at $A$ of a copointed natural transformation (the unit of the adjunction). So $l, r$ is equal to
-\begin{align*}
-  S \to FA \xrightarrow{[\id_{FA}, \mathsf{copoint}]} FA \times A\\
-  FA \times A \xrightarrow{\pi_1} FA \to S
-\end{align*}
-
-\subsection{Merely Well-Behaved Optics}
-\todo{
-  The lenses that the UPenn crew look at are less restricted. They obey the $\fput\fget$ and $\fget\fput$ laws but not the $\fput\fput$ law.
-}
-
-\begin{example}
-  The following example is taken from~\cite{AClearPictureOfLensLaws}. The ``change counter'' lens $\bN \times A \hto A$ for a set $A$ has $\fput$ and $\fget$ given by:
-  \begin{align*}
-    \fget(n, a) &= a \\
-    \fput((n, a), a') &= \begin{cases}
-      (n, a) & \text{if } a = a' \\
-      (n+1, a') & \text{otherwise}
-    \end{cases}
-  \end{align*}
-  This example is typical of (merely) well-behaved lenses: there is metadata carried along with the target of a lens that mutates as the lens is used.
-\end{example}
-
-\begin{example}
-  A minimal example of a lens that obeys $\fget\fput$ and $\fput\fget$ but not $\fput\fput$ is the following. Let $p : \{A,B,C\} \hto \{X, Y\}$ be the lens with
-  \begin{align*}
-    \fget : \{A,B,C\} &\to \{X, Y\} \\
-    A &\mapsto X \\
-    B &\mapsto X \\
-    C &\mapsto Y
-  \end{align*}
-  \begin{align*}
-    \fput : \{A,B,C\} \times \{X, Y\} &\to \{A,B,C\} \\
-    (A,X) &\mapsto A \\
-    (B,X) &\mapsto B \\
-    (C,X) &\mapsto B \\
-    (A,Y) &\mapsto C \\
-    (B,Y) &\mapsto C \\
-    (C,Y) &\mapsto C
-  \end{align*}
-\end{example}
-
-Prelenses that satisfy the first two laws correspond to pairs $\rep{l}{r }$ such that $rl = \id_S$ and $\pi_2lr = \pi_2$.
-\todo{prove?} This condition seems unavoidably tied to the product structure on $\C$; it is not clear whether this weakened notion of lens can be generalised to other optics.
-
-\subsection{Effectful Optics}
-
-Many attempts~\cite{ReflectionsOnMonadicLenses} \todo{more} to define effectful lenses have wrapped the result of one or both of $\fget$ and $\fput$ with a monad.
-This approach is a little ad-hoc; it is not obvious what the laws ought to be and there is no clear generalisation to other varieties of optic.
-The definition of optic given here suggests we instead set $\C$ to be the Kleisli category for some monad $T$.
+\subsection{The van Laarhoven Encoding}
+\todo{todo}
 
@@
 
-\todo{Figure out the right numbering style}
-
-\todo{Maybe some of the long equational manipulations could be done by commutative diagram, using a pair of dashes to signal the start and end value?}
+\todo{Figure out the right section numbering style}
+
+\todo{Maybe some of the long equational manipulations could be done by commutative diagram, using a pair of dashed lines to signal the start and end value?}
 

### 2018-06-22 paper.tex
Some thoughts on effectful optics

@@
 
+\newcommand{\mget}{\textsc{MGet}}
+\newcommand{\mput}{\textsc{MPut}}
+\newcommand{\munzip}{\textsc{Munzip}}
+
 \newcommand{\inside}{\mathsf{inside}}
@@
   \item A definition of optics general enough to encompass lenses, setters, traversals, and others
-  \item A definition of lawfulness that specialises in the correct way in all examples and allows us to easily derive ad-hoc laws for new kids of optic
+  \item A definition of lawfulness that specialises in the correct way in all examples and allows us to easily derive concrete laws for new kids of optic
   \item A universal property satisfied by the category of optics in the monoidal case
@@
 In other words, let $\rep{l'}{r'} : (R, R') \hto (S, S')$ and $\rep{l}{r} : (S, S') \hto (A, A')$ with $M$ the complement for $\rep{l'}{r'}$.
-The composite is then: $\rep{l}{r} \circ \rep{l'}{r'} = \rep{(M l)l'}{r'(Mr)}$.
+The composite is then: $\rep{l}{r} \circ \rep{l'}{r'} = \rep{(M \otimes l)l'}{r'(M \otimes r)}$.
 
@@
 \begin{proof}
-  In~\cite[Section 6]{Doubles} this is proven abstractly, by exhibiting this category as the Kleisli category for a monad in the bicategory $\Prof$. Here we prove the properties directly.
+  In~\cite[Section 6]{Doubles} this is proven abstractly, by exhibiting this category as the Kleisli category for a monad in the bicategory $\Prof$. Here we prove the conditions directly.
 
   We check associativity of composition equationally.
-As in the definition of composition, the Fubini theorem for coends allows us to choose representatives for all three optics simultaneously.
 Suppose we have representatives of three optics $\rep{l_1}{r_1} : (R, R) \hto (S, S')$, $\rep{l_2}{r_2} : (S, S') \hto (A, A')$ and $\rep{l_3}{r_3} : (A, A') \hto (B, B')$, that have complements $M$, $N$ and $P$ respectively.
+As in the definition of composition, the Fubini theorem for coends allows us to choose these representatives simultaneously.
 Then:
   \begin{align*}
-    (\rep{l_3}{r_3} \circ \rep{l_2, r_2}) \circ \rep{l_1}{r_1}
+    (\rep{l_3}{r_3} \circ \rep{l_2}{r_2}) \circ \rep{l_1}{r_1}
     &= \rep{(N \otimes l_3)l_2}{r_2(N \otimes r_3)} \circ \rep{l_1}{r_1} \\
@@
   \end{align*}
-  Where in both cases we have used the naturality of $\lambda$ and coend relations to move $\lambda^{-1}_M$ to the right-hand side of the coend, where it may be cancelled.
+  In both cases we have used the naturality of $\lambda$ and the coend relations to move $\lambda^{-1}_M$ to the right-hand side, where it may be cancelled.
 \end{proof}
@@
 An \emph{action of $\M$ on $\C$} is a monoidal functor $a : \M \to [\C, \C]$.
-The action of an object $M \in \M$ on $A \in \C$ is written $MA$.
+For two objects $M \in \M$ and $A \in \C$, the action $a(M)(A)$ is abbreviated $MA$.
 \end{definition}
@@
 
-The main reason is that it corresponds precisely to the ad-hoc lens laws with no additional requirements, whereas finding a complement for a lens requires further conditions on the category $\C$.
+The main reason is that it corresponds precisely to the concrete lens laws with no additional requirements, whereas finding a complement for a lens requires further conditions on the category $\C$.
 
@@
 We can then ``read off'' what conditions on are needed on a concrete optic to ensure that the corresponding element of $\Optic_\M(S, A)$ is lawful.
-With no offence intended, we will call these more conditions the `ad-hoc' laws.
+We will call these conditions the \emph{concrete} laws.
+
+It is worth emphasising that once a monoidal action has been chosen and a concrete description of the corresponding optics found, no further work is needed to show that the result forms a category of optics, with a subcategory of lawful optics.
+This is especially useful when devising new optic variants, as we do later.
+
+We begin with the most common kinds of optic before moving to more exotic possibilities.
 
 \todo{There is a common pattern in some of these examples, where the evaluation-at-$A$ functor $-A : \M \to \C$ has a left or right adjoint. Is it worth abstracting this out?}
-
-We begin with the most common kinds of optic before moving to more exotic possibilities.
 
@@
 \begin{proposition}\label{prop-OpticImpliesLensLaws}
-  A lens $p : S \hto A$ is a lawful lens in our sense, i.e.\ that $\outside(p) = \id_S$ and $\once(p) = \twice(p)$, if and only if the corresponding $\fput$ and $\fget$ for this lens obey the three lens laws.
+  A concrete lens given by $\fget$ and $fput$ is lawful (in our sense) if and it obeys the three lens laws.
 \end{proposition}
@@
 If we ask more of our category $\C$, we can upgrade this result to show that a lens $S \hto A$ implies the existence of a complement $\C$ with $S \cong C \times A$.
-This doesn't appear to follow purely from the ad-hoc lens laws---an argument using a definition of lawfulness based on constant complements.
+This doesn't appear to follow purely from the concrete lens laws---an argument that a definition of lawfulness based on constant complements is not the correct generalisation.
 
@@
   Suppose $\C$ has pullbacks and that there is a morphism $x : 1 \to A$.
-If $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the three lens laws then there exists $C \in \C$ with $S \cong C \times A$.
+If $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the concrete lens laws then there exists $C \in \C$ with $S \cong C \times A$.
 \end{proposition}
@@
 
-The laws for prisms are the obvious duals to the lens laws:
+The concrete laws for prisms are the obvious duals to the lens laws:
 \begin{align*}
@@
 \begin{proposition}\label{prop-OpticImpliesPrismLaws}
-  If $p : S \hto A$ is a prism then the associated $\fmatching$ and $\freview$ functions satisfy the three prism laws. \qed
+  If $p : S \hto A$ is a prism then the associated $\fmatching$ and $\freview$ functions satisfy the concrete prism laws. \qed
 \end{proposition}
@@
 \begin{proposition}
-  An iso $\rep{l}{r }$ is lawful iff (as expected) $l$ and $r$ are mutual inverses.
+  An iso $\rep{l}{r}$ is lawful iff (as expected) $l$ and $r$ are mutual inverses.
 \end{proposition}
@@
 
-\subsection{Setters}
+\subsection{Setters}\label{sec:setters}
 
@@
 
-\begin{definition}[\cite{StrongFunctors}]
+\begin{definition}[\cite{StrongFunctors}]\label{def:strong-functor}
   Suppose $(\C, \otimes, I)$ is a monoidal category.  A \emph{(left) strong functor} is a functor $F : \C \to \C$ equipped with a natural transformation
@@
   \end{align*}
-  such that both
+  such that the strength commutes with the unitor:
   \[
     \begin{tikzcd}
-      1 \otimes F A \ar[r, "\theta_{1,A}"] \ar[d, "\cong" left]  & F(1 \otimes A) \ar[d, "\cong" right] \\
+      I \otimes F A \ar[r, "\theta_{1,A}"] \ar[d, "\cong" left]  & F(I \otimes A) \ar[d, "\cong" right] \\
       F A \ar[r, equals] & F A
@@
   \]
-  and
+  and with associativity:
   \[
@@
   \]
-  commute. A \emph{strong natural transformation} $\tau : (F,\theta) \to (G,\theta')$ is a natural transformation that respects the strength:
+  A \emph{strong natural transformation} $\tau : (F,\theta) \to (G,\theta')$ is a natural transformation that respects the strength:
   \[
@@
 \end{align*}
-where  $\circ$ denotes internal composition and $\nameof{\id_A} : 1 \to \homC(A, A)$ is the `name of' $\id_A$, and similarly for $\id_S$.
+where  $\circ$ denotes internal composition and $\nameof{\id_X} : 1 \to \homC(X, X)$ denotes the `name of' $\id_X$.
 \end{proposition}
@@
 
-Experts will recognise $UR^*_{-, -}$ as the free applicative functor \cite{FreeApplicativeFunctors} on the functor $R_{X,Y} Z = X \times Y \to Z$.
+% Experts will recognise $UR^*_{-, -}$ as the free applicative functor \cite{FreeApplicativeFunctors} on the functor $R_{X,Y} Z = X \times Y \to Z$.
 
@@
 
-\subsection{Linear Lenses}
+\subsection{Linear Lenses}\label{sec:linear-lenses}
 \newcommand{\ev}{\mathsf{ev}}
@@
                                    &\cong \int^{M \in \C} \C(S, M \otimes A) \times \C(M, \homC(A',S')) \\
-                                   &\cong \C(S, \homC(A',S') \otimes A) \\
+                                   &\cong \C(S, \homC(A',S') \otimes A)
 \end{align*}
@@
 
-For an optic, the corresponding element of $\conc_\otimes((S, S'), (A, A'))$ will be called $\funzip$.
-The above isomorphism sends $\funzip$ to the element $\rep{\funzip }{\ev_{A', S'}}$, where $\ev_{A', S'} : \homC(A',S') \otimes A' \to S'$ is the evaluation map.
-In the other direction, given $\rep{l}{r }$ we have $\funzip = (\tilde r \otimes A)l$ where $\tilde r : M \to \homC(A', S')$ denotes the transpose of $r$.
+A concrete linear lens is therefore a map $\funzip : S \to \homC(A',S') \otimes A$.
+The above isomorphism sends $\funzip$ to the element $\rep{\funzip}{\ev_{A', S'}}$, where $\ev_{A', S'} : \homC(A',S') \otimes A' \to S'$ is the evaluation map.
+In the other direction, given $\rep{l}{r}$ we have $\funzip = (\tilde r \otimes A)l$ where $\tilde r : M \to \homC(A', S')$ denotes the transpose of $r$.
 
@@
 
-\begin{proposition}
-  A linear lens $p : S \hto A$ is lawful iff the following two laws for $\funzip$ hold:
+\begin{proposition}\label{prop:concrete-linear-lawful}
+  A linear lens $p : S \hto A$ is lawful iff the following two concrete laws for $\funzip$ hold:
   \begin{align*}
@@
 \end{minted}
-Note that the type has been changed from $\texttt{(Int, Int)}$ to $\texttt{(String, Int)}$.
+Note that the type has been changed from \mintinline{haskell}{(Int, Int)} to \mintinline{haskell}{(String, Int)}.
 
@@
   \end{align*}
-  that sends an object $D \in \D$ and optic $\rep{l}{r } : F \hto G$ in $\Optic_{[\D, \C]}$ to the optic $\rep{l_D}{r_D } : FD \hto GD$ in $\Optic_\otimes$. Further, this preserves lawfulness.
+  that sends an object $D \in \D$ and optic $\rep{l}{r } : F \hto G$ in $\Optic_{[\D, \C]}$ to the optic $\rep{l_D}{r_D } : FD \hto GD$ in $\Optic_\otimes$. This functor preserves lawfulness.
 \end{proposition}
@@
 \subsection{Effectful Optics}
-\todo{todo}
-Many attempts~\cite{ReflectionsOnMonadicLenses} \todo{more refs} to define effectful lenses have wrapped the result of one or both of $\fget$ and $\fput$ with a monad.
-There are disadvantages to this approach: it is not obvious what the laws ought to be and there is no clear generalisation to other varieties of optic.
-The definition of optic given in Section~\ref{sec:optics} suggests we instead set $\C$ to be the Kleisli category of some effectful monad.
+\newcommand{\monact}{\ltimes}
+
+Many proposed definitions of effectful lenses~\cite{ReflectionsOnMonadicLenses} have modified one or both of $\fget$ and $\fput$ to produce results wrapped in a monadic action.
+There are disadvantages to this approach: it is not obvious what the laws ought to be and there is no clear generalisation to other optic variants.
+The general definition of optic given in Section~\ref{sec:optics} suggests we instead work with the Kleisli category $\C_T$ of some effectful monad $T : \C \to \C$.
+
+\todo{define Kleisli category?} For a morphism $f : X \to Y$ in $\C_T$, we write $\underline{f} : X \to TY$ for its underlying morphism in $\C$.
+
+This presents its own set of difficulties.
+Kleisli categories are only monoidal when the monad in question is \emph{commutative}~\cite{PremonoidalCategories}, which rules out many monads of interest.
+A premonoidal structure is not sufficient: composition of optics would in that case not be well defined.
+
+But this does not preclude the existence of monoidal actions on $\C_T$. In fact, there is a common monoidal action that has long been used under a different guise:
+
+\begin{definition}[{\cite{NotionsOfComputationAndMonads}}]
+A \emph{strong monad} $T : \C \to \C$ on a monoidal category $(\C, \otimes, I)$ is a monad that is strong as a functor (Definition~\ref{def:strong-functor}), and such that the strength commutes with the unit and multiplication:
+\[
+  \begin{tikzcd}
+    A \otimes B \ar[d, swap, "A \times \eta_B"] \ar[dr, "\eta_{A \times B}"] & \\
+    A \otimes TB \ar[r, swap, "\theta_{A, B}"] & T(A \otimes B) 
+  \end{tikzcd} \hspace{1cm}
+  \begin{tikzcd}
+    A \otimes T^2 B \ar[r, "\theta_{A, TB}"] \ar[d, swap, "A \otimes \mu_B"] & T(A \otimes TB) \ar[r, "T\theta_{A, B}"] & T^2(A \otimes B) \ar[d, "\mu_{A \otimes B}"] \\
+    A \otimes TB \ar[rr, swap, "\theta_{A, B}"] & & T(A \times B)
+  \end{tikzcd}
+\]
+\end{definition}
+
+\begin{proposition}
+If $T : \C \to \C$ is a strong monad then $\C$ acts on $\C_T$ by $X \cdot Y \mapsto X \otimes Y$.
+\end{proposition}
+
+The crucial difference between this and a monoidal structure on $\C_T$ is that we only demand $X$ be functorial with respect to \emph{pure functions} in $\C$, whereas $Y$ must be functorial with respect to \emph{computations} in $\C_T$.
+We will write this action as $X \monact Y$ to highlight the different roles played by $X$ and $Y$.
+
+\begin{proof}
+Suppose $T$ is a strong monad with strength $\theta_{A, B} : A \otimes T B \to T(A \otimes B)$.
+For $A \in \C$, we have a functor $A \otimes - : \C_T \to \C_T$.
+On a morphism $f : X \to Y$ in $\C_T$, we define $A \otimes f : A \otimes X \to A \otimes Y$ to be the composite
+\begin{align*}
+A \otimes X \xrightarrow{A \otimes \underline{f}} A \otimes TY \xrightarrow{\theta_{A, Y}} T(A \otimes Y)
+\end{align*}
+Functoriality follows from the requirement that $\theta$ commute with the unit and multiplication of $T$. \todo{Draw this out?}
+
+Our goal is to show that $A \mapsto A \otimes -$ is a monoidal functor $a : \C \to [\C_T, \C_T]$.
+A morphism $f : A \to B$ in $\C$ induces a natural transformation $A \otimes - \to B \otimes -$ with components $A \otimes X \to T(B \otimes X)$ given by composing $A \otimes X \to B \otimes X$ with the unit of the monad.
+This transformation is natural by \todo{todo}.
+
+Finally, the functor $a$ is monoidal, with the structure maps given by the associativity and unit maps of $\C$. \todo{this uses that the strength commutes with unitors and associativity}
+\end{proof}
+
+Suppose $\C$ is a monoidal closed category and $T : \C \to \C$ is a strong monad. We can find a concrete description of the optics for the action $\monact$, using the same method as for linear lenses.
+
+\begin{align*}
+\Optic((S, S'), (A, A'))
+&= \int^{M \in \C} \C_T(S, M \monact A) \times \C_T(M \monact A', S') \\
+&= \int^{M \in \C} \C_T(S, M \monact A) \times \C(M \times A', T S') \\
+&\cong \int^{M \in \C} \C_T(S, M \monact A) \times \C(M, \homC(A', T S')) \\
+&\cong \C_T(S, \homC(A', T S') \monact A) \\
+&\cong \C(S, T(\homC(A', T S') \times A))
+\end{align*}
+
+Concrete effectful lenses therefore consist of a single morphism $\munzip : S \to T(\homC(A', T S') \times A)$.
+
+\begin{proposition}
+\todo{this is sketchy}
+A concrete effectful lens is lawful iff
+  \begin{align*}
+    \mu_S T(\ev_{A, TS}) \; \munzip &= \eta_S \\
+    T(\coev_{\homC(A, TS), A} \otimes A)\munzip &= T((T\munzip \circ -) \otimes A)\munzip 
+  \end{align*}
+\end{proposition}
+  Or, if you prefer do-notation:
+\begin{minted}{haskell}
+do (c, a) <- munzip s
+   c a
+== return s
+
+do (c, a) <- munzip s
+   let f a' = do
+     s' <- c a'
+     munzip s'
+   return (f, a)
+==
+do (c, a) <- munzip s
+   let f a' = (c, a')
+   return (f, a)
+\end{minted}
+\begin{proof}
+This is exactly analogous to Proposition \ref{prop:concrete-linear-lawful} for linear lenses, with the unit and multiplication of the monad inserted in the appropriate places.
+%\begin{align*}
+%&\int^{M, N \in \C} \C_T(S, M \monact A) \times \C_T(M \monact A, N \monact A) \times \C_T(N \monact A, S) \\
+%&\cong \int^{M, N \in \C} \C_T(S, M \monact A) \times \C_T(M \monact A, N \monact A) \times \C(N, \homC(A, TS)) \\
+%&\cong \int^{M \in \C} \C_T(S, M \monact A) \times \C_T(M \monact A, \homC(A, TS) \monact A)\\
+%&\cong \int^{M \in \C} \C_T(S, M \monact A) \times \C(M \times A, T(\homC(A, TS) \times A))\\
+%&\cong \int^{M \in \C} \C_T(S, M \monact A) \times \C(M, \homC(A, T(\homC(A, TS) \monact A)))\\
+%&\cong \C_T(S, \homC(A, T(\homC(A, TS) \times A)) \times A) \\
+%&\cong \C(S, T(\homC(A, T(\homC(A, TS) \times A)) \times A))
+%\end{align*}
+\end{proof}
+
+We can say more once we make a specific choice of strong monad.
+
+%\subsubsection{Partial Lenses}
+%
+%\begin{definition}
+%The \emph{partiality} or \emph{maybe monad} is defined by
+%\begin{align*}
+%P X = X \sqcup 1
+%\end{align*}
+%\todo{todo: define its unit, multiplication and strength}
+%\end{definition}
+
+\subsubsection{Stateful Lenses}
+
+\begin{definition}
+The \emph{state monad} is defined by
+\begin{align*}
+T_Q X = \homC(Q, X \times Q)
+\end{align*}
+where $Q$ is the set of states.
+\todo{todo: define its unit, multiplication and strength}
+\end{definition}
+
+We can find a concrete description of optics for the action $\monact : \C \times \C_{T_Q} \to \C_{T_Q}$:
+\begin{align*}
+\Optic((S, S'), (A, A'))
+&= \int^{M \in \C} \C_{T_Q}(S, M \monact A) \times \C_{T_Q}(M \monact A', S') \\
+&= \int^{M \in \C} \C(S, \homC(Q, M \times A \times Q)) \times \C_{T_Q}(M \monact A', S') \\
+&\cong \int^{M \in \C} \C(S \times Q, M \times A\times Q) \times \C_{T_Q}(M \monact A', S') \\
+&\cong \int^{M \in \C} \C(S \times Q, M) \times \C(S \times Q, A\times Q) \times \C_{T_Q}(M \monact A', S') \\
+&\cong \C(S \times Q, A \times Q) \times \C_{T_Q}((S \times Q) \monact A', S') \\
+&\cong \C_{T_Q}(S, A) \times \C_{T_Q}(S \times Q \times A', S')
+\end{align*}
+By analogy with ordinary lenses, let us call these maps $\mget$ and $\mput$.
+
+\todo{Explain how composition works in code?}
+
+\begin{proposition}
+\todo{Translate this from code}
+A stateful lens given by 
+\begin{minted}{haskell}
+mget :: s -> State q a 
+mput :: s -> q -> a -> State q s
+\end{minted}
+is lawful iff:
+\begin{minted}{haskell}
+do
+  q <- getState
+  a <- mget s
+  mput s q a
+==
+return s
+
+do s' <- mput s q a
+   mget s'
+== 
+return a
+
+let (s', q') = runState (mput s q1 a1) q2
+in mput s' q' a2
+==
+mput s q1 a2
+\end{minted}
+\end{proposition}
+We may as well also name these the $\fget\fput$, $\fput\fget$ and $\fput\fput$ laws.
+\begin{proof}
+%We similarly calculate
+%\begin{align*}
+%&\int^{M, N \in \C} \C_{T_Q}(S, M \monact A) \times \C_{T_Q}(M \monact A, N \monact A) \times \C_{T_Q}(N \monact A, S) \\
+%&\cong \int^{M, N \in \C} \C(S, \homC(Q, M \times A \times Q)) \times \C(M \times A, \homC(Q, N \times A \times Q)) \times \C_{T_Q}(N \monact A, S) \\
+%&\cong \int^{M, N \in \C} \C(S \times Q, M \times A \times Q) \times \C(M \times A \times Q, N \times A \times Q) \times \C_{T_Q}(N \monact A, S) \\
+%&\cong \int^{M, N \in \C} \C(S \times Q, M) \times \C(S \times Q,  A \times Q) \times \C(M \times A \times Q, N \times A \times Q) \times \C_{T_Q}(N \monact A, S) \\
+%&\cong \int^{N \in \C} \C_{T_Q}(S, A) \times \C(S \times Q \times A \times Q, N \times A \times Q) \times \C_{T_Q}(N \monact A, S) \\
+%&\cong \int^{N \in \C} \C_{T_Q}(S, A) \times \C(S \times Q \times A \times Q, N) \times \C(S \times Q \times A \times Q, A \times Q) \times \C_{T_Q}(N \monact A, S) \\
+%&\cong \C_{T_Q}(S, A)\times \C_{T_Q}((S \times Q) \monact A, A) \times \C_{T_Q}((S \times Q \times A \times Q) \monact A, S)
+%\end{align*}
+\todo{This is a mess}
+\end{proof}
+
+\begin{remark}
+Of course, having theoretical justification does not mean that this kind of effectful lens useful!
+It is hard to get intuition for the meaning of the laws.
+The $\fget\fput$ law appear easier to satisfy than the $\mathsf{MGetPut_0}$ law of \cite{ReflectionsOnMonadicLenses}, as $\mput$ is given access to the original state.
+On the other hand, our $\fput\fget$ law seems difficult to satisfy: it must hold no matter what auxiliary state is provided.
+\end{remark}
+
+\todo{Try out some examples given in other papers?}
 
@@
 \begin{definition}
-  There is a category $\Tamb(\M)$ of Tambara modules and natural transformations that respect the extra structure, in the sense that for any $l : P \hto Q$, the diagram
+  There is a category $\Tamb(\M)$ of Tambara modules and natural transformations that respect the module structure, in the sense that for any $l : P \to Q$, the diagram
   \[
@@
 \end{proof}
+
+\begin{remark}
+  The right adjoint to $U$ is described in \cite{NotionsOfComputationAsMonoids}, and was used to investigate Haskell's \mintinline{haskell}{Arrow} typeclass.
+\end{remark}
 

### 2018-06-22 src/Comonoidal.hs

@@ -1,0 +1,24 @@
+{-# LANGUAGE FlexibleInstances #-}
+module Comonoidal where
+
+import Control.Comonad
+import Data.Profunctor
+import Data.Profunctor.Composition
+
+class Comonoidal p where
+  comult :: p a b -> Procompose p p a b
+  counit :: p a b -> (a -> b)
+
+
+data Exchange a b s t = Exchange (s -> a) (b -> t)
+
+instance Profunctor (Exchange a b) where
+  dimap f g (Exchange l r) = Exchange (l . f) (g . r)
+
+instance Comonoidal (Exchange x x) where
+  comult (Exchange l r) = Procompose (Exchange id r) (Exchange l id)
+  counit (Exchange l r) = r . l
+
+instance Comonad m => Comonoidal (Star m) where
+  comult (Star f) = Procompose (Star f) (Star _)
+  counit (Star f) = extract . f

### 2018-06-22 src/FunList.hs

@@ -1,0 +1,23 @@
+data FunList a b t = Done t | More a (FunList a b (b -> t))
+
+instance Functor (FunList a b) where
+  fmap f (Done t) = Done (f t)
+  fmap f (More x l) = More x (fmap (f .) l)
+instance Applicative (FunList a b) where
+  pure = Done
+  (Done f) <*> l' = fmap f l'
+  (More x l) <*> l' = More x (fmap flip l <*> l')
+
+data Flipped b t a = Flipped { unflipped :: FunList a b t}
+
+instance Functor (Flipped b t) where
+  fmap f (Flipped (Done t)) = Flipped (Done t)
+  fmap f (Flipped (More a fl)) = Flipped (More (f a) (unflipped $ fmap f (Flipped fl)))
+
+instance Foldable (Flipped b t) where
+  foldMap f (Flipped (Done t)) = mempty
+  foldMap f (Flipped (More a fl)) = f a `mappend` foldMap f (Flipped fl)
+
+instance Traversable (Flipped b t) where
+  traverse f (Flipped (Done t)) = pure (Flipped (Done t))
+  traverse f (Flipped (More a fl)) = ((Flipped .) . More) <$> (f a) <*> (unflipped <$> traverse f (Flipped fl))

### 2018-06-22 src/Indexed.hs

@@ -1,0 +1,15 @@
+{-# LANGUAGE RankNTypes #-}
+module Indexed where
+
+import Control.Monad.Indexed
+
+data Underlying m a = Underlying { getUnderlying :: forall i. m i i a }
+
+instance IxFunctor m => Functor (Underlying m) where
+  fmap f (Underlying g) = Underlying (imap f g)
+
+instance IxApplicative m => Applicative (Underlying m) where
+
+instance IxMonad m => Monad (Underlying m) where
+  return a = Underlying (ireturn a)
+  (Underlying ma) >>= f = Underlying (ibind (getUnderlying . f) ma)

### 2018-06-22 src/Monadic.hs

@@ -1,0 +1,27 @@
+{-# LANGUAGE GADTs #-}
+{-# LANGUAGE RankNTypes #-}
+{-# LANGUAGE ScopedTypeVariables #-}
+module Monadic where
+
+import Control.Monad (liftM, ap, (>=>))
+
+data Monadic t s a where
+  Monadic :: (s -> t (m, a)) -> ((m, a) -> t s) -> Monadic t s a
+
+data Concrete t s a where
+  Concrete :: (s -> t (a -> t s, a)) -> Concrete t s a
+
+to :: Monad t => Monadic t s a -> Concrete t s a
+to (Monadic l r) = Concrete $ \s -> do
+  (m, a) <- l s
+  let f a' = r (m, a')
+  return (f, a)
+
+fro :: Monad t => Concrete t s a -> Monadic t s a
+fro (Concrete f) = Monadic f (\(i, a) -> i a)
+
+data Twice t s a where
+  Twice :: (s -> t (m, a)) -> ((m, a) -> t (n, a)) -> ((n, a) -> t s) -> Twice t s a
+
+-- data ConcreteTwice q s a where
+--   ConcreteTwice ::

### 2018-06-22 src/Phantom.hs

@@ -65,7 +65,7 @@ fromDirect (Direct l r) = (copoint . l, r . l)
 -- (copoint . (\s -> (g s, f s)), g)
 -- (f, g)
 
-rt (Direct l r) = Direct (\s -> (s, copoint (l s))) fst
+rt (Direct l r) = Direct ((\p -> (p, copoint p)) . l) (r . fst)
 
 to :: (s -> a) -> (forall p. StrongCopointed p => p a a -> p s s)
 to l = dimap diag fst . encopointen . lmap l

### 2018-06-22 src/Stateful.hs

@@ -1,0 +1,124 @@
+{-# LANGUAGE GADTs #-}
+{-# LANGUAGE RankNTypes #-}
+{-# LANGUAGE ScopedTypeVariables #-}
+module Stateful where
+
+import Control.Monad (liftM, ap, (>=>))
+
+data State q a = State { runState :: q -> (a, q) }
+
+getState :: State q q
+getState = State $ \q -> (q, q)
+
+putState :: q -> State q ()
+putState q = State $ \_ -> ((), q)
+
+secretly :: State q a -> State q a
+secretly act = do
+  q <- getState
+  a <- act
+  putState q
+  return a
+
+instance Functor (State q) where
+  fmap = liftM
+
+instance Applicative (State q) where
+  pure = return
+  (<*>) = ap
+
+instance Monad (State q) where
+  return a = State (\q -> (a, q))
+  act >>= k = State $ \st ->
+                        let (x, st') = runState act st
+                        in runState (k x) st'
+
+data Stateful q s a where
+  Stateful :: (s -> State q (m, a)) -> ((m, a) -> State q s) -> Stateful q s a
+
+data Concrete q s a where
+  Concrete :: (s -> State q a) -> (s -> q -> a -> State q s) -> Concrete q s a
+
+to :: Stateful q s a -> Concrete q s a
+to (Stateful l r) = Concrete mget mput
+  where mget = fmap snd . l
+        mput s q a = let ((m, _), _) = runState (l s) q
+                     in r (m, a)
+
+fro :: forall q s a. Concrete q s a -> Stateful q s a
+fro (Concrete mget mput) = Stateful l r
+  where l :: s -> State q ((s, q), a)
+        l s = do
+          q <- getState
+          a <- mget s
+          return ((s, q), a)
+        -- l s = State $ \q -> let (a, q') = (runState $ mget s) q
+        --                     in (((s, q), a), q')
+        r :: ((s, q), a) -> State q s
+        r ((s, q), a) = mput s q a
+
+data Twice q s a where
+  Twice :: (s -> State q (m, a)) -> ((m, a) -> State q (n, a)) -> ((n, a) -> State q s) -> Twice q s a
+
+data ConcreteTwice q s a where
+  ConcreteTwice :: (s -> State q a) -> (s -> q -> a -> State q a) -> (s -> q -> a -> q -> a -> State q s) -> ConcreteTwice q s a
+
[…]

### 2018-06-22 paper.tex
Work on filling in the teleological section

@@
 \newcommand{\freview}{\textsc{Review}}
+\newcommand{\fcreate}{\textsc{Create}}
 \newcommand{\fmatching}{\textsc{Matching}}
@@
 
-\subsection{Teleological Categories}
-\label{teleological-categories}
+\subsection{Teleological Categories}\label{sec:teleological-categories}
+\todo{I think there are strictness issues in this section, but the idea is correct}
 
@@
   \begin{itemize}
-  \item A wide symmetric monoidal subcategory $\C_d$ of \emph{dualisable morphisms}, with an involutive strong symmetric monoidal functor ${(-)}^* : \C_d \to \overline{\C_d^\op}$, where---not finding a standard symbol for such a thing---we mean $\overline{\C_d^\op}$ to be the category with both the direction of the arrows \emph{and} the order of the tensor flipped: ${(A \otimes B)}^* = B^* \otimes A^*$.
-\todo{Do we want this to be strict?}
+  \item A symmetric monoidal subcategory $\C_d$ of \emph{dualisable morphisms} containing all the objects of $\C$, with an involutive symmetric monoidal functor ${(-)}^* : \C_d \to \overline{\C_d^\op}$, where---not finding a standard symbol for such a thing---we mean $\overline{\C_d^\op}$ to be the category with both the direction of the arrows \emph{and} the order of the tensor flipped: ${(A \otimes B)}^* \cong B^* \otimes A^*$.
+Note that there is therefore a canonical isomorphism $\phi : I \cong I^*$
   \item A symmetric monoidal extranatural family of morphisms $\varepsilon_X : X \otimes X^* \to I$, called \emph{counits}, natural with respect to the morphisms in $\C_d$.
@@
     & I
+  \end{tikzcd}\]
+\[
+  \begin{tikzcd}
+    X \otimes Y \otimes Y^* \otimes X^* \ar[r, "X \otimes \varepsilon_Y \otimes X^*"]  \ar[dr, "\varepsilon_{X \otimes Y}", swap] & X \otimes X^* \ar[d, "\varepsilon_X"] \\
+    & I
   \end{tikzcd} \hspace{1cm}
   \begin{tikzcd}
-    X \otimes Y \otimes Y^* \otimes X^* \ar[r, "X \otimes \varepsilon_Y \otimes X^*"]  \ar[dr, "\varepsilon_{X \otimes Y}", swap] & X \otimes X^* \ar[d, "\varepsilon_X"] \\
+    I \otimes I^* \ar[r,"I \otimes \phi"] \ar[dr, swap, "\varepsilon_I"] & I \ar[d, equal] \\
     & I
@@
 
-\begin{example}
-  \todo{The funny graph example from the coherence paper?}
-\end{example}
+%\begin{example}
+%  \todo{The funny graph example from the coherence paper?}
+%\end{example}
+
+%There are few surprises in the following definitions.
 
 \begin{definition}
-  A \emph{teleological functor} $F : \C \to \D$ is a symmetric monoidal functor that restricts to a functor $F_d : \C_d \to \D_d$ on the dualisable subcategories, and such that $F(\varepsilon_X) = \varepsilon_{FX}$ \todo{up to the structure isomorphisms of $F$}
+  A \emph{teleological functor} $F : \C \to \D$ is a symmetric monoidal functor that restricts to a functor $F_d : \C_d \to \D_d$ on the dualisable subcategories, commutes with the duality and such that the counits are preserved:
+  \[
+   \begin{tikzcd}
+    F(X \otimes X^*) \ar[r, "\cong"]  \ar[d, "F\varepsilon_X", swap] & FX \otimes FX^* \ar[d, "\varepsilon_{FX}"] \\
+    FI \ar[r, "\cong", swap] & I
+  \end{tikzcd}
+  \]
 \end{definition}
+
+%\begin{definition}
+%  A \emph{teleological natural transformation} $\alpha : F \Rightarrow G$ is a monoidal natural transformation that is additionally compatible with the dualisation:
+%  \[
+%  \begin{tikzcd}
+%    (FX)^* \ar[r, "\cong"]  \ar[d, "(\alpha_X)^*", swap] & F(X^*) \ar[d, "\alpha_{X^*}"] \\
+%    (GX)^* \ar[r, "\cong", swap] & G(X^*)
+%  \end{tikzcd}
+%  \]
+%  whenever $\alpha_X$ is dualisable. \todo{Does adding this condition make sense?}
+%\end{definition}
 
@@
 There are evident functors $U : \Tele \to \SymmMonCat$ and ${(-)}_d : \Tele \to \SymmMonCat$, that take a teleological category to its underlying symmetric monoidal category and subcategory of dualisable morphisms respectively.
+
+The definition of teleological category suggests a string diagram calculus similar to that for compact closed categories, but where only counits exist, and only morphisms known to be dualisable may be passed around a counit by extranaturality.
+We have of course not proven that such a calculus is sound for teleological categories, but we trust that a sceptical reader could verify our arguments equationally.
 
@@
 
-  \todo{This works fine when $\C$ is not strict}
+%  \todo{This works fine when $\C$ is not strict}
 \end{proof}
@@
   Suppose $\C$ is a strict symmetric monoidal category and $\T$ is a teleological category.
-For all symmetric monoidal functors $F : \C \to \T_d$, there exists a teleological functor $K : \Optic_\otimes \to \T$, unique up to isomorphism, such that $Kj \cong F$.
+For all symmetric monoidal functors $F : \C \to \T_d$, there exists a teleological functor $K : \Optic_\otimes \to \T$, unique up to teleological natural isomorphism with the property $Kj \cong F$.
 \end{theorem}
 \begin{proof}
-  We begin by constructing $K$. On objects, define $K(S, S') = FS \otimes (FS')^*$. Suppose $\rep{l}{r} : (S, S') \hto (A, A')$ is an optic. By the previous Proposition,
-  \begin{align*}
-    \rep{l}{r} = ((A, I) \switched \varepsilon_{(M, I)} \switched (I, A'))(j(s_{M,A}l) \switched j(rs_{M,A'})^*)
-  \end{align*}
-  Which suggests defining
+  We begin by constructing $K$.
+Note that any $(S, S')$ in $\Optic_\otimes$ can be written as $j(S) \switched j(S')^*$, so on objects define $K(S, S') = FS \otimes (FS')^*$.
+Suppose $\rep{l}{r} : (S, S') \hto (A, A')$ is an optic.
+By the previous Proposition,
+  \begin{align*}
+    \rep{l}{r} = ((A, I) \switched \varepsilon_{(M, I)} \switched (I, A'))(j(s_{M,A}l) \switched j(rs_{A', M})^*)
+  \end{align*}
+  So up to isomorphism we are forced to define
   \begin{align*}
@@
 
-  We must show that this is well defined. Suppose we have two optics related by the coend relation:
-  \begin{align*}
-    \rep{(f \otimes A) l}{r} = \rep{l}{r (f \otimes A')}
-  \end{align*}
-  Then well definedness is shown by the equivalence of the diagrams
-  \begin{center}
-    \input{diagrams/k-well-defined-left.tikz}
-    \qquad \raisebox{1.5cm}{$=$} \qquad
-    \input{diagrams/k-well-defined-right.tikz}
-  \end{center}
-  using naturality of the symmetry and extranaturality of the counit.
-%\todo{maybe do as string diagram}
 %  \begin{align*}
@@
 %  \end{align*}
-  \todo{todo: functoriality, monoidality, preserves dualisable morphisms, preserves counit}
-
-  \todo{uniqueness} 
+
+There are now a lot of things to check. 
+\begin{itemize}
+\item Well-definedness: Suppose we have two optics related by the coend relation:
+  \begin{align*}
+    \rep{(f \otimes A) l}{r} = \rep{l}{r (f \otimes A')}
+  \end{align*}
+  Then well-definedness is shown by the equivalence of diagrams
+  \begin{center}
+    \input{diagrams/k-well-defined-left.tikz}
+    \qquad \raisebox{1.5cm}{$=$} \qquad
+    \input{diagrams/k-well-defined-right.tikz}
+  \end{center}
+  using naturality of the symmetry and extranaturality of the counit.
+\item Functoriality: We have an equivalence of diagrams
+  \begin{center}
+    \input{diagrams/k-functorial-left.tikz}
+    \quad \raisebox{1.5cm}{$=$} \quad
+    \input{diagrams/k-functorial-right.tikz}
+  \end{center}
+using naturality of the symmetry, and monoidality of the counit.
+\item Preservation of duals:
+\begin{align*}
+K((S, S')^*) 
+= K(S', S) 
+= FS' \otimes (FS)^*
+\cong (FS \otimes (FS')^*)^*
+= (K(S, S'))^*
+\end{align*}
+\item Monoidality: We have the isomorphism
+\begin{align*}
+K((S, S') \switched (T, T')) 
+&= K(S \otimes T, T' \otimes S) \\
+&= F(S \otimes T) \otimes F(T' \otimes S')^* \\
+&\cong FS \otimes FT \otimes (FS')^* \otimes (FT')^* \\
+&\cong FS \otimes (FS')^* \otimes FT \otimes (FT')^* \\
+&= K(S, S') \otimes K(T, T')
+\end{align*}
+using the symmetry of $\T$, and
+\begin{align*}
+K(I, I) 
+&= FI \otimes (FI)^* \\
+&\cong I \otimes I^* \\
+&\cong I
+\end{align*}
+That these obey the required coherences is straightforward. More difficult is showing that the first isomorphism is natural in $(S, S')$ and $(T, T')$: \todo{todo}
+\item Preservation of dualisable morphisms:  For a morphism $\iota(f, g)$:
+\begin{align*}
+K(\iota(f, g))
+    &= K(\rep{\lambda_A^{-1} f}{g \lambda_{A'}}) \\
+    &= (FA \otimes \varepsilon_{FI} \otimes (FA')^*)(F(s_{I,A}\lambda_A^{-1} f) \otimes (F(g \lambda_{A'}s_{A', I}))^* ) \\
+    &= (FA \otimes (FA')^*)(Ff \otimes (Fg)^* ) \\
+    &= Ff \otimes (Fg)^*
+\end{align*}
+and this is dualisable, as dualisability is preserved by taking the monoidal product and duals.
+\item Preservation of counits: 
+\begin{align*}
+K(\varepsilon_{(S, S')}) 
+&= K(c_{S \otimes S'}) \\
+&= K(\rep{\rho_{S \otimes S'}^{-1}}{\rho_{S \otimes S'}}) \\
+&= (FI \otimes \varepsilon_{F(S \otimes S')} \otimes (FI)^*)(F(s_{S \otimes S',I}\rho_{S \otimes S'}^{-1}) \otimes (F(\rho_{S \otimes S'} s_{I, S \otimes S'}))^* ) \\
+&= (\varepsilon_{F(S \otimes S')})(F(S \otimes S') \otimes F(S \otimes S')^* ) \\
+&= \varepsilon_{F(S \otimes S')}
+\end{align*}
+by strictness of the monoidal unit.
+\todo{Show this is actually the morphism we want}
+\end{itemize}
 \end{proof}
@@
 For two objects $M \in \M$ and $A \in \C$, the action $a(M)(A)$ is abbreviated $MA$.
+The tensor product in $\M$ will also be written as juxtaposition, so $(NM)A \cong N(MA)$.
 \end{definition}
@@
 \begin{align*}
-  \Optic_\M((S, S'), (A, A')) := \int^{M \in \C} \C(S, MA) \times \C(MA', S')
+  \Optic_\M((S, S'), (A, A')) := \int^{M \in \M} \C(S, MA) \times \C(MA', S')
 \end{align*}
@@
   \begin{align*}
-  \once(\Optic(F)(\rep{l}{r})) 
-  &= \once(\rep{(Fl);\phi^{-1}_{M,A} }{\phi_{M,A'};(Fr) }) \\
+  \outside(\Optic(F)(\rep{l}{r})) 
+  &= \outside(\rep{(Fl);\phi^{-1}_{M,A} }{\phi_{M,A'};(Fr) }) \\
   &= (Fl);\phi^{-1}_{M,A};\phi_{M,A'};(Fr)\\
@@
 
-It is worth emphasising that once a monoidal action has been chosen and a concrete description of the corresponding optics found, no further work is needed to show that the result forms a category of optics, with a subcategory of lawful optics.
+It is worth emphasising that once a monoidal action has been chosen and a concrete description of the corresponding optics found, no further work is needed to show that the result forms a category of optics with a subcategory of lawful optics.
 This is especially useful when devising new optic variants, as we do later.
@@
 
-\todo{There may be something generalisable here with ``monoidal factorisation systems''}
+%\todo{There may be something generalisable here with ``monoidal factorisation systems''}
 
@@
 \begin{remark}
-\todo{todo?} A careful analysis would be needed to describe traversals in some other category, in particular, the description of $UR^*$ does not make sense if $\C$ is not locally cartesian closed.
+A careful analysis would be needed to describe traversals in some other category, in particular, the description of $UR^*$ does not make sense if $\C$ is not locally cartesian closed.
 \end{remark}
@@
 \begin{remark}
-Traversable functors can be described as a particular class of polynomial functors known as finitary containers. There may be something generalisable here with other classes of polynomial functors.
+Traversable functors can be described as a particular class of polynomial functors known as finitary containers. It may be possible to generalise this to other classes of polynomial functors.
 \end{remark}
@@
 \end{proof}
-
-\subsection{``Achromatic'' Lenses}
-\todo{http://oleg.fi/gists/posts/2018-03-28-achromatic-lens.html}
-
-Suppose $\C$ is cartesian closed and has finite coproducts. Then $\C$ acts on itself via $M \cdot A = (M \sqcup 1) \times A$.
-\begin{align*}
-  \Optic((S, S'), (A, A'))
-  &= \int^{M \in \C} \C(S, M \cdot A) \times \C(M \cdot A', S') \\
-  &= \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C((M \sqcup 1) \times A', S') \\
-  &\cong \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C((M \times A') \sqcup A', S') \\
-  &\cong \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C(M \times A', S') \times \C(A', S') \\
-  &\cong \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C(M, \homC(A', S')) \times \C(A', S') \\
-  &\cong \C(S, (\homC(A', S') \sqcup 1) \times A) \times \C(A', S') \\
-  &\cong \C(S, \homC(A', S') \sqcup 1) \times \C(S, A) \times \C(A', S')
-\end{align*}
-
-\begin{remark}
-  Equivalently, we could let $\M$ be the category of pointed objects of $\C$ and pointed maps between them.
-\end{remark}
-
-\todo{Worth writing out?}
-
-\subsection{Affine Traversals}
-
-A folklore variant of a prism is the \emph{affine traversal}, which allows access to a target that may or may not be present.
-
-Suppose $\C$ is cartesian closed, and has binary coproducts. Then let $\mathsf{Aff}$ be the category $\C \times \C$, equipped with the monoidal structure
-\begin{align*}
-  (P', Q') \otimes (P, Q) &= (P' \sqcup (Q' \times P) , Q' \times Q)
-\end{align*}
-\todo{check $\mathsf{Aff}$ is actually a monoidal category}
-
-Define a monoidal action $\mathsf{Aff} \to [\C, \C]$ where $(P, Q)$ acts on $A$ by
-\begin{align*}
-  (P, Q) \cdot A = P \sqcup (Q \times A)
-\end{align*}
-so that as expected,
-\begin{align*}
-  (P', Q') \cdot (P, Q) \cdot A
-  &= (P', Q') \cdot  (P \sqcup (Q \times A)) \\
-  &= P' \sqcup (Q' \times (P \sqcup (Q \times A))) \\
-  &\cong P' \sqcup (Q' \times P) \sqcup (Q' \times Q \times A) \\
-  &= (P' \sqcup (Q' \times P) , Q' \times Q) \cdot A \\
-  &= ((P', Q') \otimes (P, Q)) \cdot A
-\end{align*}
-
-\begin{remark}
-  It is important here that the morphisms in $\mathsf{Aff}$ are only those that arise from pairs of morphisms $P \to P'$ and $Q \to Q'$, although in principle there may be other natural transformations between the corresponding functors $(P, Q) \cdot -$ and $(P', Q') \cdot -$.
-\end{remark}
-
-\todo{This feels similar to taking some sort of `compositum' of the two actions $\times$ and $\sqcup$, both embed in this category.
-Marco suggests taking the pushout of the projections into the pullback, calculated in the 2-cat of monoidal categories.}
-
-Now the set of optics $(S, S') \hto (A, A')$ is:
-\begin{align*}
-  \Optic_{\mathsf{Aff}}((S, S'), (A, A'))
-  &= \int^{M \in \mathsf{Aff}} \C(S, M \cdot A) \times \C(M \cdot A', S') \\
-  &\cong \int^{P,Q \in \C} \C(S, (P,Q) \cdot A) \times \C((P,Q) \cdot A', S') \\
-  &= \int^{P,Q \in \C} \C(S, P \sqcup (Q \times A)) \times \C(P \sqcup (Q \times A'), S') \\
-  &\cong \int^{P,Q \in \C} \C(S, P \sqcup (Q \times A)) \times \C(P,S') \times \C(Q \times A', S') \\
-  &\cong \int^{Q \in \C} \C(S, S' \sqcup (Q \times A)) \times \C(Q \times A', S') \\
-  &\cong \int^{Q \in \C} \C(S, S' \sqcup (Q \times A)) \times \C(Q, \homC(A', S')) \\
-  &\cong \C(S, S' \sqcup (\homC(A', S') \times A))
-\end{align*}
-
-We note that this contradicts the folklore description of affine traversals as pairs of maps $\C(S, A \sqcup S') \times \C(S\times A', S')$, see~\cite{AffineTraversalPost}.
-That set is in fact ``too large'': the provided map $S \times A' \to S$ must be defined even on elements of $S$ whose image under the first map $S \to A \sqcup S'$ lies in the right-hand component, which is not the case in our description.
-
-\todo{Do laws? For \emph{lawful} affine traversals, there may not be a difference}
-
-\todo{Give an example of two elements of the set that correspond to the same affine traversal}
 
@@
 
-Our goal is to show that $A \mapsto A \otimes -$ is a monoidal functor $a : \C \to [\C_T, \C_T]$.
+Our goal is to show that the assignment $A \mapsto A \otimes -$ extends to a monoidal functor $a : \C \to [\C_T, \C_T]$.
 A morphism $f : A \to B$ in $\C$ induces a natural transformation $A \otimes - \to B \otimes -$ with components $A \otimes X \to T(B \otimes X)$ given by composing $A \otimes X \to B \otimes X$ with the unit of the monad.
@@
 &= \int^{M \in \C} \C_T(S, M \monact A) \times \C_T(M \monact A', S') \\
-&= \int^{M \in \C} \C_T(S, M \monact A) \times \C(M \times A', T S') \\
+&= \int^{M \in \C} \C_T(S, M \monact A) \times \C(M \otimes A', T S') \\
 &\cong \int^{M \in \C} \C_T(S, M \monact A) \times \C(M, \homC(A', T S')) \\
 &\cong \C_T(S, \homC(A', T S') \monact A) \\
-&\cong \C(S, T(\homC(A', T S') \times A))
-\end{align*}
-
-Concrete effectful lenses therefore consist of a single morphism $\munzip : S \to T(\homC(A', T S') \times A)$.
+&\cong \C(S, T(\homC(A', T S') \otimes A))
+\end{align*}
+
+Concrete effectful lenses therefore consist of a single morphism $\munzip : S \to T(\homC(A', T S') \otimes A)$.
+The category $\C$ includes into $\C_T$ in a way that preserves the action of $\C$, so there is an induced inclusion $\Optic_\otimes \to \Optic_\monact$.
 
 \begin{proposition}
-\todo{this is sketchy}
 A concrete effectful lens is lawful iff
@@
     \mu_S T(\ev_{A, TS}) \; \munzip &= \eta_S \\
-    T(\coev_{\homC(A, TS), A} \otimes A)\munzip &= T((T\munzip \circ -) \otimes A)\munzip 
-  \end{align*}
+    T(\eta_{\homC(A, TS) \otimes A)}\coev_{\homC(A, TS), A} \otimes A)\munzip &= T((\munzip \circ_T -) \otimes A)\munzip 
+  \end{align*}
+  where \[ \munzip \circ_T - : \homC(A, TS) \to \homC(A, T(\homC(A, TS) \otimes A)) \] denotes internal Kleisli composition and \[\coev_{\homC(A, TS), A} : \homC(A, TS) \to \homC(A, \homC(A, TS) \otimes A) \] is coevaluation.
 \end{proposition}
@@
    c a
-== return s
+== 
+return s
 
@@
 
-We can say more once we make a specific choice of strong monad.
+If we choose a specific monad, we can hope to simplify the description of concrete effectful lenses and their laws.
 
@@
 
-We can find a concrete description of optics for the action $\monact : \C \times \C_{T_Q} \to \C_{T_Q}$:
+Working in a cartesian closed category, we can find a concrete description of optics for the action $\monact : \C \times \C_{T_Q} \to \C_{T_Q}$ that is closer to that for ordinary lenses.
 \begin{align*}
@@
 \todo{Try out some examples given in other papers?}
+
+\subsection{Further Examples}
+\todo{I probably don't have the standing to get away with saying} The dedicated reader may enjoy re-deriving the concrete representation and laws for the following optic varieties:
+
+\begin{itemize}
+\item \emph{``Achromatic'' Lenses} \cite[Section 5.2]{ProfunctorOpticsThesis} are lenses that also admit an operation $\fcreate : A \to S$.
+These are optics for the action of $\C$ on itself by $M \cdot A = (M \sqcup 1) \times A$, or equivalently, of the category of pointed objects of $\C$ on $\C$ by cartesian product.
+Concrete achromatic lenses $S \hto A$ are elements of the set \[\C(S, \homC(A', S') \sqcup 1) \times \C(S, A) \times \C(A', S').\]
+%\begin{align*}
+%  \Optic((S, S'), (A, A'))
+%  &= \int^{M \in \C} \C(S, M \cdot A) \times \C(M \cdot A', S') \\
+%  &= \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C((M \sqcup 1) \times A', S') \\
+%  &\cong \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C((M \times A') \sqcup A', S') \\
+%  &\cong \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C(M \times A', S') \times \C(A', S') \\
+%  &\cong \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C(M, \homC(A', S')) \times \C(A', S') \\
+%  &\cong \C(S, (\homC(A', S') \sqcup 1) \times A) \times \C(A', S') \\
+%  &\cong \C(S, \homC(A', S') \sqcup 1) \times \C(S, A) \times \C(A', S')
+%\end{align*}
+\item \emph{Affine Traversals} \cite{AffineTraversalPost} allow access to a target that may or may not be present.
+Suppose $\C$ is cartesian closed and has binary coproducts.
+Let $\mathsf{Aff}$ be the category $\C \times \C$, equipped with the monoidal structure
+\begin{align*}
+  (P', Q') \otimes (P, Q) &= (P' \sqcup (Q' \times P) , Q' \times Q)
+\end{align*}
+The category $\mathsf{Aff}$ acts on $\C$ by $(P, Q) \cdot A = P \sqcup (Q \times A)$. A concrete representation of the optics for this action is \[\C(S, S' \sqcup (\homC(A', S') \times A)).\]
+
+Affine traversals are described in the folklore as pairs of maps $\C(S, A \sqcup S') \times \C(S\times A', S')$.
+Such a pair does determine an affine traversal, but in fact gives more information than is necessary: the right-hand map need not be defined at all $S$.
+
+%\begin{align*}
+%  (P', Q') \cdot (P, Q) \cdot A
+%  &= (P', Q') \cdot  (P \sqcup (Q \times A)) \\
+%  &= P' \sqcup (Q' \times (P \sqcup (Q \times A))) \\
+%  &\cong P' \sqcup (Q' \times P) \sqcup (Q' \times Q \times A) \\
+%  &= (P' \sqcup (Q' \times P) , Q' \times Q) \cdot A \\
+%  &= ((P', Q') \otimes (P, Q)) \cdot A
+%\end{align*}
+%\begin{remark}
+%  It is important here that the morphisms in $\mathsf{Aff}$ are only those that arise from pairs of morphisms $P \to P'$ and $Q \to Q'$, although in principle there may be other natural transformations between the corresponding functors $(P, Q) \cdot -$ and $(P', Q') \cdot -$.
+%\end{remark}
+%\todo{This feels similar to taking some sort of `compositum' of the two actions $\times$ and $\sqcup$, both embed in this category.
+Marco suggests taking the pushout of the projections into the pullback, calculated in the 2-cat of monoidal categories.}
+%Now the set of optics $(S, S') \hto (A, A')$ is:
+%\begin{align*}
+%  \Optic_{\mathsf{Aff}}((S, S'), (A, A'))
+%  &= \int^{M \in \mathsf{Aff}} \C(S, M \cdot A) \times \C(M \cdot A', S') \\
+%  &\cong \int^{P,Q \in \C} \C(S, (P,Q) \cdot A) \times \C((P,Q) \cdot A', S') \\
+%  &= \int^{P,Q \in \C} \C(S, P \sqcup (Q \times A)) \times \C(P \sqcup (Q \times A'), S') \\
+%  &\cong \int^{P,Q \in \C} \C(S, P \sqcup (Q \times A)) \times \C(P,S') \times \C(Q \times A', S') \\
+%  &\cong \int^{Q \in \C} \C(S, S' \sqcup (Q \times A)) \times \C(Q \times A', S') \\
+%  &\cong \int^{Q \in \C} \C(S, S' \sqcup (Q \times A)) \times \C(Q, \homC(A', S')) \\
+%  &\cong \C(S, S' \sqcup (\homC(A', S') \times A))
+%\end{align*}
+\end{itemize}
 
@@
   \end{align*}
-  natural in $A$ and $B$, and dinatural in $M$. Further, we must have that $\alpha_{A,B,I} = \id_{P(A,B)}$, and that the following diagram commutes:
+  natural in $A$ and $B$, and dinatural in $M$, and such that $\alpha_{A,B,I} = \id_{P(A,B)}$, and $\alpha$ commutes with the tensor of $\M$:
   \[
     \begin{tikzcd}
-      P(A,B) \ar[r, "\alpha_{A,B,M}"] \ar[dr, "\alpha_{A, B, N \otimes M}" below left] & P(MA, MB) \ar[d, "\alpha_{MA, MB, N}" right] \\
+      P(A,B) \ar[r, "\alpha_{A,B,M}"] \ar[dr, "\alpha_{A, B, NM}" below left] & P(MA, MB) \ar[d, "\alpha_{MA, MB, N}" right] \\
       & P(NMA, NMB)
@@
   \end{align*}
-  for all $C, D \in \C$ and $N \in \M$. Equationally, this is $\alpha_{A,B,M}(\repthree{l}{p}{r} ) = \rep{Ml}{p}{Mr} $.
+  for all $C, D \in \C$ and $N \in \M$. Equationally, this is $\alpha_{A,B,M}(\repthree{l}{p}{r} ) = \repthree{Ml}{p}{Mr} $.
 \end{definition}
@@
 
-  Suppose we have an element $\rep{l}{p}{r} \in \Pastro_\M P(A,B)$. Then one can check that this element is equal to
+  Suppose we have an element $\repthree{l}{p}{r} \in \Pastro_\M P(A,B)$. Then one can check that this element is equal to
   \begin{align*}
@@
   \begin{align*}
-    \hat{f}(\rep{l}{p}{r }) &= \hat{f}(\Pastro_\M P(l, r) \alpha_{A, B, M} \; \eta(p)) \\
+    \hat{f}(\repthree{l}{p}{r}) &= \hat{f}(\Pastro_\M P(l, r) \alpha_{A, B, M} \; \eta(p)) \\
                                      &=T(l, r) \; \beta_{A, B, N} \; f(p)
@@
   \begin{align*}
-    \hat{f}\alpha_{A,B,N}(\rep{l}{p}{r })
-    &= \hat{f}(\rep{Nl}{p}{Nr }) \\
-    &= T(Nl, Nr) \; \beta_{A, B, NM} \; f(p) \\
-    &= T(Nl, Nr) \beta_{MA,MB,N} \; \beta_{A, B, M} \; f(p) \\
-    &= \beta_{A,B,N} T(l, r) \; \beta_{A, B, M} \; f(p) \\
-    &= \beta_{A,B,N} \hat{f} (\rep{l}{p}{r })
+    \hat{f}\alpha_{A,B,N}(\repthree{l}{p}{r })
+    &= \hat{f}(\repthree{Nl}{p}{Nr }) && \text{(definition of $\alpha$)}\\
+    &= T(Nl, Nr) \; \beta_{A, B, NM} \; f(p) && \text{(definition of $\hat{f}$)}\\
+    &= T(Nl, Nr) \beta_{MA,MB,N} \; \beta_{A, B, M} \; f(p) && \text{($\beta$ commutes with tensor in $\M$)} \\
+    &= \beta_{A,B,N} T(l, r) \; \beta_{A, B, M} \; f(p) && \text{(naturality of $\beta$)} \\
+    &= \beta_{A,B,N} \hat{f} (\repthree{l}{p}{r}) && \text{(definition of $\hat{f}$)}
   \end{align*}
@@
 \begin{remark}
-  The right adjoint to $U$ is described in \cite{NotionsOfComputationAsMonoids}, and was used to investigate Haskell's \mintinline{haskell}{Arrow} typeclass.
+  The right adjoint to $U$ is described in \cite{NotionsOfComputationAsMonoids} to investigate Haskell's \mintinline{haskell}{Arrow} typeclass.
 \end{remark}

### 2018-06-25 paper.tex
Fix a couple of bugs

@@
 
-In their most concrete form, a \emph{lens} from $S$ to $A$ is a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$.
-From an engineering standpoint, such a lens allows us to ``zoom in'' to a small part $A$ of a larger $S$, manipulate it in some way, then ``zoom back out'' and have our changes in $A$ represented in $S$.
-
-Typically we want our lenses to obey the following laws (that are named in view of composition in diagrammatic order!): 
+In its most concrete form, a \emph{lens} from $S$ to $A$ is a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$.
+From a software engineering standpoint, such a lens allows us to ``zoom in'' on $S$ to focus on a small part $A$, manipulate $A$ in some way, then ``zoom out'' and have our changes reflected $S$.
+
+We consider a lens well-behaved if it obeys the following laws: 
 \begin{itemize}
@@
 \end{itemize}
-In some of the literature, lenses obeying these conditions are called \emph{very well-behaved}. Since this is the only set of conditions we are interested in, we will call such lenses \emph{lawful}.
+We will call such lenses \emph{lawful}. (The names of the laws make more sense when the equations are written with composition in diagrammatic order!)
 
 Lenses were discovered to be just one of a hierarchy of data accessors, including prisms, setters, traversals, and more, collectively called \emph{optics}.
-Each has a concrete description as a collection of certain maps, with attendant laws that make them (very) well behaved.
+Each optic variant has a concrete description as a certain collection of maps, with attendant laws under which we consider them well-behaved.
 We begin in Section~\ref{sec:optics} by defining the \emph{category of optics} in a sufficiently general way to encompass almost all the optic variants in use in the wild.
-Section~\ref{sec:lawful-optics} defines the equivalent of the lens laws for a general category of optics.
-Then in Section~\ref{sec:examples} we see how the general definitions specialise to the optic variants we know and love.
+Section~\ref{sec:lawful-optics} defines the equivalent of the lens laws for a generic category of optics.
+Then in Section~\ref{sec:examples} we see how the generic definitions specialise to the optic variants we know and love.
 
 The widely used Haskell \lenslib{} library contains implementations of all these optic variants: see \cite{LensLibrary}.
-There, optics are written in a form known as the \emph{profunctor encoding}, which at first glance is completely different to that given here in Section \ref{sec:optics}.
+There, optics are written in a form known as the \emph{profunctor encoding}, which at first glance is completely different to that given in Section~\ref{sec:optics}.
 As this note was being written, Bartosz Milewski~\cite{ProfunctorOpticsPost} independently described the relationship between some forms of optic and their profunctor encoding.
@@
 Much of what is known about lenses and their variants is folklore, and careful verification of some of their categorical properties has been lacking.
-The aim of the present paper is to fill this gap, with the hope that a better understanding of the general properties of these categories will make it easier to generalise to new and exotic settings.
-This is particularly important with the advent of linear types in Haskell, which enables a new branch of the lens family tree, and with the new applications in game theory.
+The aim of the present paper is to fill this gap, with the hope that a better understanding of the general structure of these categories will make it easier to generalise to new and exotic settings.
+This is particularly important with the advent of linear types in Haskell, which enables a new branch of the lens family tree, and with the new applications to game theory.
 
@@
   \item A satisfying categorical description of lens laws as the homomorphism condition on a morphism between certain comonoids
-  \item An attempt to isolate what $\Set$-like properties are being used in various places
+  \item An attempt to isolate what $\Set$-like properties are being used in some places
   \end{itemize}
@@
 
-      %       \begin{proposition}
-      %       \todo{Entrywise Coproduct}
-      %       \end{proposition}
-      %
-      %       \begin{remark}
-      %       The motivating example here is that of coproducts distributing over the tensor product.
-      %       \end{remark}
-
-\begin{proposition}\label{prop-change-of-action-monoidal}
+\begin{proposition}\label{prop:change-of-action-monoidal}
   A monoidal functor $F : \C \to \D$ induces a functor $\Optic(F) : \Optic_\otimes \to \Optic_\D$.
@@
 
-The following are analogous to Propositions~\ref{prop-optic-is-cat} and \ref{prop-change-of-action-monoidal}.
+The following are analogous to Propositions~\ref{prop-optic-is-cat} and \ref{prop:change-of-action-monoidal}.
 
@@
 
-\begin{proposition}\label{prop-change-of-action}
+\begin{proposition}\label{prop:change-of-action}
   Suppose $\C$ and $\D$ are categories acted on by $\M$ and $\mathcal{N}$ respectively.
-Let $F : \C \to \D$ be a functor that commutes with the actions, in the sense that there exist natural isomorphisms
-  \begin{align*}
-  \phi &: F(IA) \to I(FA) \\
-  \phi_{M,A} &: (FM)(FA) \to F(MA)
+Let $F_1 : \M \to N$ be a monoidal functor and $F_2 : \C \to \D$ be a functor that commutes with the actions, in the sense that there exist natural isomorphisms
+  \begin{align*}
+  \phi &: F_2(I A) \to F_1(I)(F_2A) \\
+  \phi_{M,A} &: F_2(MA) \to (F_1 M)(F_2 A) 
   \end{align*}
@@
 For the remainder of the paper we work in this more general setting.
+
+      %       \begin{proposition}
+      %       \todo{Entrywise Coproduct}
+      %       \end{proposition}
+      %
+      %       \begin{remark}
+      %       The motivating example here is that of coproducts distributing over the tensor product.
+      %       \end{remark}
 
@@
 
-\begin{proposition}
+\begin{proposition} \todo{This is broken, is supposed to use $F_1$ and $F_2$.}
   If $F : \C \to \D$ is a functor that commutes with the monoidal actions on $\C$ and $\D$, then $\Optic(F) : \Optic_\M \to \Optic_\N$ restricts to a functor $\Lawful_\M \to \Lawful_\N$.
@@
   \end{alignat*}
-  So checking componentwise, $\Phi(\once(p))$ being equal to $\Phi(\twice(p))$ is exactly equivalent to the $\fput\fget$ and $\fput\fput$ laws holding.
+  So looking componentwise, $\Phi(\once(p))$ being equal to $\Phi(\twice(p))$ is exactly equivalent to the $\fput\fget$ and $\fput\fput$ laws holding.
 \end{proof}
@@
 The category $\Traversal_\C$ of traversals in $\C$ is the category of lawful optics for the action of $\Traversable_\C$ on $\C$ given by evaluation.
+(Yes, the names $\Traversal$ vs\@.
+$\Traversable$ are confusing.)
 \end{definition}
-
-(Yes, the names $\Traversal$ vs\@. $\Traversable$ are confusing.)
 
@@
 \end{align*}
-Moreover, this correspondence forms an isomorphism of categories between $\Traversable$ and the Eilenberg-Moore category of coalgebras for $UR^*_{-, -}$, which we denote $\C_T$.
+Moreover, this correspondence forms an isomorphism of categories between $\Traversable$ and the Eilenberg-Moore category of coalgebras for $UR^*_{-, -}$, which we denote $\C_T$. \qed
 \end{proposition}
@@
 \subsection{Polymorphic Optics}
-Haskell's optics \todo{find an older reference from DB theory?} allow \emph{polymorphic updates}, where the type of the codomain of the lens can be changed by an update, causing a corresponding change in the type of the domain.
-As an example, the lens into the first entry of a tuple has type
-\begin{minted}{haskell}
-first :: Lens (a, b) (a', b) a a'
-\end{minted}
-then:
+Haskell's optics \todo{has this appeared in DB theory?} allow \emph{polymorphic updates}, where the type of the codomain of the lens can be changed by an update, causing a corresponding change in the type of the domain.
+As an example, we permitted to use a lens into the \mintinline{haskell}{first} entry of a tuple in the following way:
 \begin{minted}{haskell}
@@
 
-Polymorphic optics can be captured by the coend formalism as follows. Any action of a monoidal category $\M \times \C \to \C$ can be extended to act pointwise on a functor category:
+Polymorphic optics can be captured by the coend formalism as follows. Any action of a monoidal category $\M \times \C \to \C$ can be extended to act objectwise on a functor category:
 \begin{align*}
@@
 So in the above example, we have the product $\times$ acting pointwise on the functor category $\Set \to \Set$.
-Our example \texttt{first} is then an optic $F \hto G$, where $F = (-) \times \mathtt{Int}$ and $G$ is the identity functor.
+Our example \mintinline{haskell}{first} is then an optic $F \hto G$, where $F = (-) \times \mintinline{haskell}{Int}$ and $G$ is the identity functor.
 
@@
   \begin{align*}
-    \mathsf{mono} : \D \times \Optic_{[\D, \C]} \to \Optic_\otimes
-  \end{align*}
-  that sends an object $D \in \D$ and optic $\rep{l}{r } : F \hto G$ in $\Optic_{[\D, \C]}$ to the optic $\rep{l_D}{r_D } : FD \hto GD$ in $\Optic_\otimes$. This functor preserves lawfulness.
-\end{proposition}
-\begin{proof}
+    \mathsf{mono} : \D \times \D^\op \times \Optic_{[\D, \C]} \to \Optic_\otimes
+  \end{align*}
+  that sends an object $(D, D') \in \D \times \D^\op$ and optic $\rep{l}{r} : (F, F') \hto (G, G')$ in $\Optic_{[\D, \C]}$ to the optic $\rep{l_D}{r_{D'}} : (FD, F'D') \hto (GD, G'D')$ in $\Optic_\M$.
+For fixed $(D, D) \in \D \times \D^\op$, this functor preserves lawfulness.
+\end{proposition}
+\begin{proof}
+  On an object $(D, D') \in \D \times \D^\op$, this is essentially the same as Proposition~\ref{prop:change-of-action} but with different functors on each side of the lens: the evaluation-at-$D$ functor $[\D, \C] \to \C$ on the left and evaluation-at-$D'$ on the right.
+  Given a morphism $(f, g) : (D_1, D'_1) \to (D_2, D'_2) \in \D \times \D^\op$ and an object $(F, F') \in \Optic_{[\D, \C]}$, there is an induced lens $\iota(Ff, F'g) : (FD_1, F'D'_1) \hto (FD_2, F'D'_2)$.
+Bifunctoriality of $\mathsf{mono}$ is ensured by the naturality of $l$ and $r$ in the morphisms of $\Optic_{[\D, \C]}$.
+\end{proof}
+
+\todo{What about the pointwise tensor of an entire functor?}
+
+\subsection{Monad Transformer Optics}
+
 \todo{todo}
-\end{proof}
-
-\todo{What about the pointwise tensor of an entire functor?}
-
-\subsection{Monad Transformer Optics}
-
-\todo{todo}
-
-There is also an analogous notion of optics of composites of functors.
+
+%There is also an analogous notion of optics of composites of functors.
 
@@
 There are disadvantages to this approach: it is not obvious what the laws ought to be and there is no clear generalisation to other optic variants.
-The general definition of optic given in Section~\ref{sec:optics} suggests we instead work with the Kleisli category $\C_T$ of some effectful monad $T : \C \to \C$.
-
-\todo{define Kleisli category?} For a morphism $f : X \to Y$ in $\C_T$, we write $\underline{f} : X \to TY$ for its underlying morphism in $\C$.
-
-This presents its own set of difficulties.
-Kleisli categories are only monoidal when the monad in question is \emph{commutative}~\cite{PremonoidalCategories}, which rules out many monads of interest.
-A premonoidal structure is not sufficient: composition of optics would in that case not be well defined.
-
-But this does not preclude the existence of monoidal actions on $\C_T$. In fact, there is a common monoidal action that has long been used under a different guise:
+The general definition of optic given in Section~\ref{sec:optics} suggests we instead work with the Kleisli category $\C_T$ of some monad $(T, \eta, \mu) : \C \to \C$.
+
+\begin{definition}
+The Kleisli category $\C_T$ of a monad $T$ has the same objects as $\C$, with morphisms $X \to Y$ given by morphisms $X \to TY$.
+Identities are given by the unit of $T$, and the composite of two morphisms $f : X \to Y$ and $g : Y \to Z$ in $\C_T$ is given by
+\begin{align*}
+X \xrightarrow{f} TY \xrightarrow{Tg} TTZ \xrightarrow{\mu_Z} TZ
+\end{align*}
+
+For $f : X \to Y$ in $\C_T$, we write $\underline{f} : X \to TY$ for its underlying morphism in $\C$.
+\end{definition}
+
+Working in a Kleisli category presents its own set of difficulties.
+The product in $\C$ is a monoidal product in a $\C_T$ only when the monad in question is \emph{commutative}, which rules out many monads of interest.
+A premonoidal structure~\cite{PremonoidalCategories} is not sufficient: composition of optics would in that case not be well defined.
+
+But this does not preclude the existence of monoidal actions on $\C_T$. In fact, there is a monoidal action that has long been used under a different guise:
 

### 2018-06-26 paper.tex
State of play before I try and redo setters

@@
 \usepackage{minted}
+\usepackage{cite}
 
@@
 \newcommand{\Traversal}{\mathbf{Traversal}}
+\newcommand{\Getter}{\mathbf{Getter}}
+\newcommand{\Review}{\mathbf{Review}}
 
@@
 
-%\todo{Past work:
-%  \begin{itemize}
-%  \item The Haskell lens people: edwardk, shachaf (Shachaf Ben-Kiki), xplat, roconnor... (TODO: find out who these people are)
-%  \item The Doubles paper
-%  \item Bartosz's blog post which was written about the same time I started this. (Only tensor-like optics, no discussion of laws, confusion about enrichment(?))
-%  \item The profunctor optics paper out of Oxford. (No generality, nothing categorical, no discussion of laws)
-%  \item Very old Dialectica category stuff
-%  \end{itemize}
-%}
-
 In its most concrete form, a \emph{lens} from $S$ to $A$ is a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$.
@@
 Section~\ref{sec:lawful-optics} defines the equivalent of the lens laws for a generic category of optics.
-Then in Section~\ref{sec:examples} we see how the generic definitions specialise to the optic variants we know and love.
+Then in Section~\ref{sec:examples} we see that these generic definitions specialise correctly to all the basic varieties of optic, including giving the correct laws.
 
@@
 As this note was being written, Bartosz Milewski~\cite{ProfunctorOpticsPost} independently described the relationship between some forms of optic and their profunctor encoding.
-In Section~\ref{sec:profunctor-optics} we extend this to more of the optic hierarchy and translate the lens laws into the profunctor setting.
+In Section~\ref{sec:profunctor-optics} we extend this to more of the optic hierarchy and translate the laws into the profunctor setting.
 
@@
   \begin{itemize}
-  \item A definition of optics general enough to encompass lenses, setters, traversals, and others
-  \item A definition of lawfulness that specialises in the correct way in all examples and allows us to easily derive concrete laws for new kids of optic
+  \item A definition of optics that uses the monoidal action of one category of another. This general enough to encompass lenses, setters, traversals, and more exotic things.
+  \item A definition of lawfulness that specialises in the correct way in and allows us to easily derive concrete laws for new kids of optic.
+Importantly, in the general case this definition is less strict than the `constant complement' definition.
   \item A universal property satisfied by the category of optics in the monoidal case
-  \item A satisfying categorical description of lens laws as the homomorphism condition on a morphism between certain comonoids
+  \item A categorical description of optic laws as the homomorphism condition on a morphism between certain comonoids
   \item An attempt to isolate what $\Set$-like properties are being used in some places
@@
 }
+
+%\todo{Past work:
+%  \begin{itemize}
+%  \item The Haskell lens people: edwardk, shachaf, xplat, roconnor...
+%  \item The Doubles paper
+%  \item Bartosz's blog post which was written about the same time I started this. (Only tensor-like optics, no discussion of laws, confusion about enrichment(?))
+%  \item The profunctor optics paper out of Oxford. (No generality, nothing categorical, no discussion of laws)
+%  \item Very old Dialectica category stuff
+%  \end{itemize}
+%}
 
@@
 
-For a pair of maps $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\rep{l}{r} : (S, S') \hto (A, A')$ for their image in $\Optic_\otimes((S, S'), (A, A'))$, and say that $M$ is the complement for this representative.
+For a pair of maps $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\rep{l}{r} : (S, S') \hto (A, A')$ for their image in $\Optic_\otimes((S, S'), (A, A'))$, and say that $M$ is the residual for this representative.
 Optics will always be written with a crossed arrow $\hto$, to distinguish them from morphisms of $\C$.
@@
 \end{align*}
-In other words, let $\rep{l'}{r'} : (R, R') \hto (S, S')$ and $\rep{l}{r} : (S, S') \hto (A, A')$ with $M$ the complement for $\rep{l'}{r'}$.
+In other words, let $\rep{l'}{r'} : (R, R') \hto (S, S')$ and $\rep{l}{r} : (S, S') \hto (A, A')$ with $M$ the residual for $\rep{l'}{r'}$.
 The composite is then: $\rep{l}{r} \circ \rep{l'}{r'} = \rep{(M \otimes l)l'}{r'(M \otimes r)}$.
@@
   We check associativity of composition equationally.
-Suppose we have representatives of three optics $\rep{l_1}{r_1} : (R, R) \hto (S, S')$, $\rep{l_2}{r_2} : (S, S') \hto (A, A')$ and $\rep{l_3}{r_3} : (A, A') \hto (B, B')$, that have complements $M$, $N$ and $P$ respectively.
+Suppose we have representatives of three optics $\rep{l_1}{r_1} : (R, R) \hto (S, S')$, $\rep{l_2}{r_2} : (S, S') \hto (A, A')$ and $\rep{l_3}{r_3} : (A, A') \hto (B, B')$, that have residuals $M$, $N$ and $P$ respectively.
 As in the definition of composition, the Fubini theorem for coends allows us to choose these representatives simultaneously.
@@
 %%   \end{align*}
-%%   with complements $M_1, M_2, N_1, N_2$ respectively. Then: \todo {(This is a mess. String diagram?)}
+%%   with residuals $M_1, M_2, N_1, N_2$ respectively. Then: \todo {(This is a mess. String diagram?)}
 %%   \begin{align*}
@@
 \begin{proof}
-  Suppose the two optics have complements $M$ and $N$ respectively. Written equationally, their tensor is:
+  Suppose the two optics have residuals $M$ and $N$ respectively. Written equationally, their tensor is:
   \begin{align*}
@@
   % \end{align*}
-  % with complements $M_1, M_2, N_1, N_2$ respectively. Then: \todo {(This is a mess. String diagram?)}
+  % with residuals $M_1, M_2, N_1, N_2$ respectively. Then: \todo {(This is a mess. String diagram?)}
   % \begin{align*}
@@
 
-  Let us check that $\alpha_{(R, R'), (S, S'), (T, T')}$ is natural in $(R, R')$. Suppose $\rep{l}{r} : (Q, Q') \hto (R, R')$ is an optic with complement $M$.
+  Let us check that $\alpha_{(R, R'), (S, S'), (T, T')}$ is natural in $(R, R')$. Suppose $\rep{l}{r} : (Q, Q') \hto (R, R')$ is an optic with residual $M$.
   \begin{align*}
@@
 
-  The categories are monoidally equivalent via the identity functor \[I : (\Optic_\otimes, \switched, (I, I)) \to (\Optic_\otimes, \otimes, (I, I)),\] where the structure isomorphisms making this functor monoidal are given by
-  \begin{align*}
-    \iota(\id_{S \otimes S'}, s_{T, T'}) : I(S, S') \otimes I(T, T') \to I((S, S') \switched (T, T'))
+  The categories are monoidally equivalent via the identity functor \[\id : (\Optic_\otimes, \switched, (I, I)) \to (\Optic_\otimes, \otimes, (I, I)),\] where the structure isomorphisms making this functor monoidal are given by
+  \begin{align*}
+    \iota(\id_{S \otimes S'}, s_{T, T'}) : \id(S, S') \otimes \id(T, T') \to \id((S, S') \switched (T, T'))
   \end{align*}
@@
       %       \begin{proposition}
-      %       Suppose $\langle l, r \rangle : (S, S') \hto (A, A')$ has complement $M$. Then
+      %       Suppose $\langle l, r \rangle : (S, S') \hto (A, A')$ has residual $M$. Then
       %       \begin{align*}
@@
 \begin{proposition}\label{prop-optic-decompose}
-  Suppose $\rep{l}{r} : (S, S') \hto (A, A')$ has complement $M$. Then
+  Suppose $\rep{l}{r} : (S, S') \hto (A, A')$ has residual $M$. Then
   \begin{align*}
@@
 
+\begin{definition}
+Given two categories equipped with monoidal actions $(\M, \C)$ and $(\N, D)$, a \emph{morphism of actions} is a monoidal functor $F^\bullet : \M \to N$ and a functor $F : \C \to \D$ that commutes with the actions, in the sense that there exist natural isomorphisms
+  \begin{align*}
+  \phi &: F(I A) \to (F^\bullet I)(F_2A) \\
+  \phi_{M,A} &: F(MA) \to (F^\bullet M)(F A) 
+  \end{align*}
+satisfying conditions analogous to those for a monoidal functor.
+\end{definition}
+
 \begin{proposition}\label{prop:change-of-action}
-  Suppose $\C$ and $\D$ are categories acted on by $\M$ and $\mathcal{N}$ respectively.
-Let $F_1 : \M \to N$ be a monoidal functor and $F_2 : \C \to \D$ be a functor that commutes with the actions, in the sense that there exist natural isomorphisms
-  \begin{align*}
-  \phi &: F_2(I A) \to F_1(I)(F_2A) \\
-  \phi_{M,A} &: F_2(MA) \to (F_1 M)(F_2 A) 
-  \end{align*}
-satisfying conditions analogous to those for a monoidal functor.
-
-Then there is an induced functor $\Optic(F) : \Optic_\M \to \Optic_\N$. \qed
+If $F : (\M, \C) \to (\N, D)$, is a morphism of actions, there is an induced functor $\Optic(F) : \Optic_\M \to \Optic_\N$. \qed
 \end{proposition}
@@
 \end{proposition}
+This would of course make no sense with the switched tensor, as the tensor of two objects would no longer be of the form $(X, X)$.
 \begin{proof}
@@
 
-\begin{proposition} \todo{This is broken, is supposed to use $F_1$ and $F_2$.}
-  If $F : \C \to \D$ is a functor that commutes with the monoidal actions on $\C$ and $\D$, then $\Optic(F) : \Optic_\M \to \Optic_\N$ restricts to a functor $\Lawful_\M \to \Lawful_\N$.
+\begin{proposition}
+  Suppose $F : (\M, \C) \to (\N, \D)$ is a morphism of actions. Then $\Optic(F) : \Optic_\M \to \Optic_\N$ restricts to a functor $\Lawful_\M \to \Lawful_\N$.
 \end{proposition}
@@
   &= (Fl);\phi^{-1}_{M,A};\phi_{M,A'};(Fr)\\
-  &= (Fl);(Fr)\\
+  &= (Fl);(F_2r)\\
   &= \id_{FS}
   \end{align*}
-  where $\phi_{M,A'} : (FM)(FA) \to F(MA)$ is the structure map for $F$ commuting with the actions.
+  where $\phi_{M,A'} : (F^\bullet M)(FA) \to F(MA)$ is the structure map for $F$ commuting with the actions.
 
@@
   \repthree{F(l;\psi A);\phi^{-1}_{M,A}}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} 
-  &= \repthree{F(l);F(\psi A);\phi^{-1}_{M,A}}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
-  &= \repthree{F(l);\phi^{-1}_{M',A};(F\psi) A}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
-  &= \repthree{F(l);\phi^{-1}_{M',A}}{(F\psi) A;\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
-  &= \repthree{F(l);\phi^{-1}_{M',A}}{\phi_{M,A};F(\psi A);Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
-  &= \repthree{F(l);\phi^{-1}_{M',A}}{\phi_{M,A};F(\psi A;c);\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
+  &= \repthree{Fl;F(\psi A);\phi^{-1}_{M,A}}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
+  &= \repthree{Fl;\phi^{-1}_{M',A};(F^\bullet \psi) A}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
+  &= \repthree{Fl;\phi^{-1}_{M',A}}{(F^\bullet \psi) A;\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
+  &= \repthree{Fl;\phi^{-1}_{M',A}}{\phi_{M',A};F(\psi A);Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
+  &= \repthree{Fl;\phi^{-1}_{M',A}}{\phi_{M',A};F(\psi A;c);\phi^{-1}_{N,A}}{\phi_{N,A};Fr}
   \end{align*}
@@
   &= \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};F(r;l);\phi^{-1}_{M,A}}{\phi_{M,A};Fr}  \\
-  &= \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};F(\id_MA);\phi^{-1}_{M,A}}{\phi_{M,A};Fr}  \\
-  &= \repthree{Fl;\phi^{-1}_{M,A}}{\id_{(FM)A}}{\phi_{M,A};Fr}  \\
+  &= \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};F(\id_{MA});\phi^{-1}_{M,A}}{\phi_{M,A};Fr}  \\
+  &= \repthree{Fl;\phi^{-1}_{M,A}}{\id_{(F^\bullet M)(FA)}}{\phi_{M,A};Fr}  \\
   &= \once(\Optic(F)(\rep{l}{r})) 
@@
 \begin{proposition}\label{prop-OpticImpliesLensLaws}
-  A concrete lens given by $\fget$ and $fput$ is lawful (in our sense) if and it obeys the three lens laws.
+  A concrete lens given by $\fget$ and $\fput$ is lawful (in our sense) if and it obeys the three lens laws.
 \end{proposition}
@@
 \begin{proof}
-  \[ \int^{M_1, M_2 \in \M} \C(S, M_1 \otimes A) \times \C(M_1 \otimes A, M_2 \otimes A) \times \C(M_2 \otimes A, S) \]
+  \[ \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S) \]
   specialises in this case to just
@@
 \subsection{Setters}\label{sec:setters}
+
+\todo{TODO: do this again using power and copower}
 
@@
 
+\todo{remainder of the proof is not very interesting}
+
       %       $\Psi(\eta) : A \to FB$ to be $A \xrightarrow{A \times \const_{\id_B}} A \times \homC(B, B) \xrightarrow{\eta_B} FB$.
 
-  Now, verifying these are inverse:
-  \begin{align*}
-    P(Q(\eta))_C (a,g)
-    &= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(g, \Psi(\eta)(a))) \\
-    &= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(g, \eta_B(a, \id_B))) \\
-    &= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(\id, \eta_B)(g, (a, \id_B))) \\
-    &= F(\lambda x. \lambda h. h x)(\eta_{\homC(B, C) \times B} s_{\homC(B, C), B}(g, a, \id_B)) && \text{($\theta$ is a strong transformation)}\\
-    &= F(\lambda x. \lambda h. h x)(\eta_{\homC(B, C) \times B} (a, \lambda d. (g, \id_B d)) ) && \text{(definition of $s$)}\\
-    &= F(\lambda x. \lambda h. h x)(\eta_{\homC(B, C) \times B} (a, \lambda d. (g, d)) ) \\
-    &= \eta_{C}(\lambda (a, f). (a, \lambda b. \mathsf{fst}(f b)\mathsf{snd}(f b)) (a, \lambda d. (g, d)) && \text{(naturality of $\eta$)}\\
-    &= \eta_{C}(a, \lambda b. g b) \\
-    &= \eta_{C}(a, g)
-  \end{align*}
-  And in the other direction:
-  \begin{align*}
-    Q(P(f))(a)
-    &= P(f)_B(a, \id_B) \\
-    &= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, B), B}(\id_B, f a))\\
-    &= F(\lambda x. \lambda h. h x)(F(\lambda b. (\id_B, b)))\theta_{1, B}(f a) && \text{(naturality of $\theta$)}\\
-    &= F(\lambda b. \id_B b)\theta_{1, B}(f a)\\
-    &= \theta_{1, B}(f a) && \text{(strength of $\theta$)}\\
-    &= f a
-  \end{align*}
-\todo{Naturality}
+%  Now, verifying these are inverse:
+%  \begin{align*}
+%    P(Q(\eta))_C (a,g)
+%    &= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(g, \Psi(\eta)(a))) \\
+%    &= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(g, \eta_B(a, \id_B))) \\
+%    &= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(\id, \eta_B)(g, (a, \id_B))) \\
+%    &= F(\lambda x. \lambda h. h x)(\eta_{\homC(B, C) \times B} s_{\homC(B, C), B}(g, a, \id_B)) && \text{($\theta$ is a strong transformation)}\\
+%    &= F(\lambda x. \lambda h. h x)(\eta_{\homC(B, C) \times B} (a, \lambda d. (g, \id_B d)) ) && \text{(definition of $s$)}\\
+%    &= F(\lambda x. \lambda h. h x)(\eta_{\homC(B, C) \times B} (a, \lambda d. (g, d)) ) \\
+%    &= \eta_{C}(\lambda (a, f). (a, \lambda b. \mathsf{fst}(f b)\mathsf{snd}(f b)) (a, \lambda d. (g, d)) && \text{(naturality of $\eta$)}\\
+%    &= \eta_{C}(a, \lambda b. g b) \\
+%    &= \eta_{C}(a, g)
+%  \end{align*}
+%  And in the other direction:
+%  \begin{align*}
+%    Q(P(f))(a)
+%    &= P(f)_B(a, \id_B) \\
+%    &= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, B), B}(\id_B, f a))\\
+%    &= F(\lambda x. \lambda h. h x)(F(\lambda b. (\id_B, b)))\theta_{1, B}(f a) && \text{(naturality of $\theta$)}\\
+%    &= F(\lambda b. \id_B b)\theta_{1, B}(f a)\\
+%    &= \theta_{1, B}(f a) && \text{(strength of $\theta$)}\\
+%    &= f a
+%  \end{align*}
+%\todo{Naturality}
 \end{proof}
@@
   On an object $(D, D') \in \D \times \D^\op$, this is essentially the same as Proposition~\ref{prop:change-of-action} but with different functors on each side of the lens: the evaluation-at-$D$ functor $[\D, \C] \to \C$ on the left and evaluation-at-$D'$ on the right.
+
   Given a morphism $(f, g) : (D_1, D'_1) \to (D_2, D'_2) \in \D \times \D^\op$ and an object $(F, F') \in \Optic_{[\D, \C]}$, there is an induced lens $\iota(Ff, F'g) : (FD_1, F'D'_1) \hto (FD_2, F'D'_2)$.
-Bifunctoriality of $\mathsf{mono}$ is ensured by the naturality of $l$ and $r$ in the morphisms of $\Optic_{[\D, \C]}$.
+Bifunctoriality of $\mathsf{mono}$ is ensured by the naturality of each $l$ and $r$ in the morphisms of $\Optic_{[\D, \C]}$.
 \end{proof}
@@
 \todo{What about the pointwise tensor of an entire functor?}
-
-\subsection{Monad Transformer Optics}
-
-\todo{todo}
-
-%There is also an analogous notion of optics of composites of functors.
 
@@
 \begin{remark}
-Of course, having theoretical justification does not mean that this kind of effectful lens useful!
+Of course, this notion of effectful lens may not be useful!
 It is hard to get intuition for the meaning of the laws.
-The $\fget\fput$ law appear easier to satisfy than the $\mathsf{MGetPut_0}$ law of \cite{ReflectionsOnMonadicLenses}, as $\mput$ is given access to the original state.
+The $\fget\fput$ law here appears easier to satisfy than the $\mathsf{MGetPut_0}$ law of \cite{ReflectionsOnMonadicLenses}, as $\mput$ is given access to the original state.
 On the other hand, our $\fput\fget$ law seems difficult to satisfy: it must hold no matter what auxiliary state is provided.
@@
 %\end{align*}
+
+\item \emph{Functor Optics} \todo{todo}
+
+\item \todo{This is speculative...} \emph{Monad Transformer Optics} \cite{MonadTransformerLensesTalk} were considered by Edward Kmett  as a method for embedding pieces of a monad transformer stack into the whole.
+There is some debate about the correct categorical description of monad transformers~\cite{MonadTransformersAsMonoidTransformers, CalculatingMonadTransformersCategoryTheory}, so we do not attempt to say anything precise, but the perspective given here could help in a couple of ways.
+
+Kmett considers optics for the operation of composing two monad transformers.
+The primary test-case was to embed \mintinline{haskell}{ReaderT} actions into \mintinline{haskell}{StateT} actions, but from the constant-complement perspective, this is impossible: \mintinline{haskell}{StateT} does not factor as the composite of \mintinline{haskell}{ReaderT} with some other monad transformer.
+In this setting the constant-complement laws may be asking too much, the optic laws in this paper may give the correct notion of lawfulness for monad transformers.
+
+Also, instead of considering optics within a category of monad transformers, we could instead look at optics for the action of monad transformers on monads.
+One can indeed define an optic $\mintinline{haskell}{State} \hto \mintinline{haskell}{Reader}$ that uses residual $\mintinline{haskell}{StateT}$.
+Whether this is lawful or useful is not clear!
+
+\item \emph{Degenerate Optics} include the \mintinline{haskell}{Getter}s and \mintinline{haskell}{Review}s of the Haskell library, where an optic $(S, S') \hto (A, A')$ corresponds simply to a morphism $S \to A$ or $A' \to S'$ respectively.
+These do fit into the coend formalism, with a slight modification.
+
+If we have a monoidal category $\M$ that acts on two different categories $\C_1$ and $\C_2$, we may well form the `optic' category:
+\begin{align*}
+  \Optic_\M((S, S'), (A, A')) := \int^{M \in \M} \C_1(S, MA) \times \C_2(MA', S')
+\end{align*}
+We lose, of course, the ability to talk about lawful optics.
+To encode \mintinline{haskell}{Getter}s or \mintinline{haskell}{Review}s, we then set $\C_2$ or $\C_1$ to be the codiscrete category $\C_\mathsf{codisc}$ with the same set of objects as $\C$, so that all homsets are the one element set.
+In this way we indeed get categories $\Getter$ and $\Review$ that are isomorphic to $\C$ and $\C^\op$.
+The functor $\C \to \C_\mathsf{codisc}$ induces functors $\Lens \to \Getter$ and $\Prism \to \Review$.
+
+\todo{We actually haven't talked about profunctors yet, where should this go?} There is a corresponding notion of Tambara module for a profunctor between two different categories.
+A profunctor $P : \C^\op \times \C_\mathsf{codisc}$ essentially ignores its covariant argument; this explains the appearance of a \mintinline{haskell}{RightPhantom} typeclass or equivalent in many profunctor optic libraries.
 \end{itemize}
 
-\subsection{Degenerate Optics}
-\todo{This doesn't work yet:}
-
-The Haskell lens library has some other `optics' that aren't really optics, but still integrate nicely with the rest of the ecosystem, e.g. Getters, Reviews and Folds.
-
-Getters $(S, S') \hto (A, A')$ are supposed to correspond to morphisms $S \to A$.
-These cannot fit nicely into the coend formalism, as there is always the function $\outside : \Optic_\M((S, S), (A, A')) \to \C(S, S')$.
-
-There are some ways to jam it in though, in the specific case of $(S, S) \to (A, A')$, if we set $\M$ to be the category of copointed functors $\C \to \C$.
-Here copointed means the slice category $[\C, \C] / \id_\C$.
-
-Then I claim that
-\begin{align*}
-  \int^{F \in \mathsf{Copointed}} \C(S, FA) \times \C(FA, S) \cong \C(S, A) \times \C(S, S)
-\end{align*}
-So that the set of `lawful' getters is exactly $\C(S, A)$.
-
-Free copointed on $F$ is exactly $F \times \id_\C$
-The functor $\mathsf{Copointed} \to [\C, \C]$ has a right adjoint given by $F \mapsto F \times \id_\C$. Copointed map $F \to G \times \id_\C$ is the same as an uncopointed map $F \to G$
-
-For $l, r : \C(S, FA) \times \C(FA, S)$, the map $r$ is equal to
-\[
-  FA \xrightarrow{[\id_{FA}, \mathsf{copoint}]} FA \times A \xrightarrow{\pi_1} FA \to S
-\]
-But that first map is the component at $A$ of a copointed natural transformation (the unit of the adjunction). So $l, r$ is equal to
-\begin{align*}
-  S \to FA \xrightarrow{[\id_{FA}, \mathsf{copoint}]} FA \times A\\
-  FA \times A \xrightarrow{\pi_1} FA \to S
-\end{align*}
-
-\subsection{Indexed Optics}
-\todo{
-  This possibly looks like
-  \begin{align*}
-    \int^{M \in \M} \C(S, M(IA)) \times \C(M A', S')
-  \end{align*}
-  with another monoidal action $I$. The $I$ would need to distribute over $M$ in some way. ``Coindexed'' optics seem to have
-  \begin{align*}
-    \int^{M \in \M} \C(S, J(MA)) \times \C(M A', S')
-  \end{align*}
-  which is why they pass information `in the other direction' but still transform covariantly.
-}
+%\subsection{Indexed Optics}
+%\todo{
+%  This possibly looks like
+%  \begin{align*}
+%    \int^{M \in \M} \C(S, M(IA)) \times \C(M A', S')
+%  \end{align*}
+%  with another monoidal action $I$. The $I$ would need to distribute over $M$ in some way. ``Coindexed'' optics seem to have
+%  \begin{align*}
+%    \int^{M \in \M} \C(S, J(MA)) \times \C(M A', S')
+%  \end{align*}
+%  which is why they pass information `in the other direction' but still transform covariantly.
+%}
 
@@
 % One issue with the definition of optic given in the last section is that it could be difficult to determine when two optics $\rep{l}{r }, \langle l', r' \rangle : S \hto A$
-are equal. For some choices of $\M$, however, we can reduce a zigzag of relations to a single one.
+% are equal. For some choices of $\M$, however, we can reduce a zigzag of relations to a single one.
 %
@@
 %   Suppose all epimorphisms split in $\C$, and that $- \times A : \C \to \C$ reflects epis.
-Then two lenses $\langle l, r \rangle$ and $\langle l', r' \rangle :  S \hto A$ with complements $M$ and $N$ respectively are equal iff there exists an morphism $\phi : M \to N$ such that $(\phi \times A)l = l'$ and $r = r' (\phi \times A)$.
+Then two lenses $\langle l, r \rangle$ and $\langle l', r' \rangle :  S \hto A$ with residuals $M$ and $N$ respectively are equal iff there exists an morphism $\phi : M \to N$ such that $(\phi \times A)l = l'$ and $r = r' (\phi \times A)$.
 % \end{proposition}
@@
 % \begin{theorem}
-%   Suppose we have two optics $\langle l, r \rangle$ and $\langle l', r' \rangle \in \Optic_\M(S, A)$ with complements $M$ and $N$ respectively, and suppose $\M$ has the property that the ``evaluation-at-$A$'' functor $(-A) : \M \to \C$ satisfies (SM) and (SE).
+%   Suppose we have two optics $\langle l, r \rangle$ and $\langle l', r' \rangle \in \Optic_\M(S, A)$ with residuals $M$ and $N$ respectively, and suppose $\M$ has the property that the ``evaluation-at-$A$'' functor $(-A) : \M \to \C$ satisfies (SM) and (SE).
 Then the two optics are equal iff there exists an morphism $\phi : M \to N$ such that $\phi_A l = l'$ and $r = r' \phi_A$.
@@
 %
-%   For the forward direction, as in Proposition \ref{prop-onthenose} we induct on a zigzag \[(l, r) = (l_1, r_1) \leftrightsquigarrow \dots \leftrightsquigarrow (l_n, r_n) = (l', r'),\] where each pair $(l_i, r_i)$ has complement $M_i$.
+%   For the forward direction, as in Proposition \ref{prop-onthenose} we induct on a zigzag \[(l, r) = (l_1, r_1) \leftrightsquigarrow \dots \leftrightsquigarrow (l_n, r_n) = (l', r'),\] where each pair $(l_i, r_i)$ has residual $M_i$.
 As a base case, we can take the identity $\id_M : M \to M = M_1$.
@@
   In the code, the \mintinline{haskell}{Strong} typeclass corresponds to supplying the structure map $\alpha$ for a profunctor \texttt{p}.
-Parametricity guarantees a form of (di)naturality for $M$, $A$ and $B$, but as with any definition in Haskell, the equations required of a Tambara module must be checked externally.
+Parametricity guarantees a form of (di)naturality for $M$, $A$ and $B$, but as with any definition in Haskell, the equations required of a Tambara module must be checked by hand.
 \end{remark}
@@
 
+\section{Mixed Optics}
+\todo{This hopefully will handle degenerate optics and indexed optics}
+
 \section{Conclusion}

### 2018-06-26 paper.tex
Redo setters

@@
 
-\todo{TODO: do this again using power and copower}
-
-To define setters we must recall the notion of a strong functor.
-
-\begin{definition}[\cite{StrongFunctors}]\label{def:strong-functor}
-  Suppose $(\C, \otimes, I)$ is a monoidal category.  A \emph{(left) strong functor} is a functor $F : \C \to \C$ equipped with a natural transformation
-  \begin{align*}
-    \theta_{A,B} : A \otimes F B \to F(A \otimes B)
-  \end{align*}
-  such that the strength commutes with the unitor:
-  \[
-    \begin{tikzcd}
-      I \otimes F A \ar[r, "\theta_{1,A}"] \ar[d, "\cong" left]  & F(I \otimes A) \ar[d, "\cong" right] \\
-      F A \ar[r, equals] & F A
-    \end{tikzcd}
-  \]
-  and with associativity:
-  \[
-    \begin{tikzcd}
-      (A \otimes B) \otimes F C \ar[rr, "\theta_{A \otimes B, C}"] \ar[d, "\alpha_{A,B,FC}" left]  && F((A \otimes B) \otimes C) \ar[d, "F\alpha_{A,B,FC}" right] \\
-      A \otimes (B \otimes F C) \ar[r, "A \otimes \theta_{B,C}" below] & A \otimes F(B \otimes C) \ar[r, "\theta_{A, B\otimes C}" below] & F(A \otimes (B \otimes C))
-    \end{tikzcd}
-  \]
-  A \emph{strong natural transformation} $\tau : (F,\theta) \to (G,\theta')$ is a natural transformation that respects the strength:
-  \[
-    \begin{tikzcd}
-      A \otimes F B \ar[r, "\theta_{A,B}"] \ar[d, "A \otimes \tau_B" left]  & F(A \otimes B) \ar[d, "\tau_{A \otimes B}" right] \\
-      A \otimes G B \ar[r, "\theta'_{A, B}"]& G(A \otimes B)
-    \end{tikzcd}
-  \]
-
-  There is an evident category $\Strong(\C)$ of strong endofunctors and strong natural transformations, and a forgetful functor $U : \Strong(\C) \to [\C, \C]$.
+\begin{definition}
+  The \emph{category of setters} $\Setter_\C$ is the category of lawful optics for the action of $[\C, \C]$ on $\C$ by evaluation.
 \end{definition}
 
-In what follows, we will exploit the convenient $\lambda$-calculus syntax for morphisms in a cartesian closed category. \todo{ref} \todo{this sudden change in notation is a bit confusing}
-
-\begin{example}
-  An example, which we will use immediately, is the functor $FX = A \times \homC(B, X)$ in any cartesian closed category $\C$, and with any pair of objects $A$ and $B$.
-The strength $s_{C,D}$ is given by:
-  \begin{align*}
-    C \times FD = C \times A \times \homC(B, D) &\to A \times \homC(B, C \times D) = F(C \times D)\\
-    (c, a, f) &\mapsto (a, \lambda d. (c, fd))
-  \end{align*}
-\end{example}
-
-\begin{example}
-  \emph{Any} functor $\Set \to \Set$ has a unique strength with respect to the cartesian product, so this concept is invisible for Haskell \texttt{Functor}s. 
-\end{example}
-
-\begin{lemma}
-  Suppose $\C$ is cartesian closed and $F : \C \to \C$ is strong with respect to $\times$. Then for any objects $A, B \in \C$, \[\C(A, FB) \cong \Strong_\C(\times)(A \times \homC(B, -), F)\]
-naturally in $A$ and $F$. In other words, the functor $(A \mapsto A \times \homC(B, -)) : \C \to \Strong_\C$ is left adjoint to the evaluation-at-$B$ functor $-B : \Strong_\C \to \C$.
-\end{lemma}
-\begin{proof}
-  We construct the isomorphism $P : C(A, FB) \cong \Strong_\C(\times)(A \times \homC(B, -), F)$ and its inverse $Q$.
-  Given a $f \in \C(A, FB)$, let $P(f)$ be the natural transformation such that the component at $C$ is the composite
-  \begin{align*}
-    A \times \homC(B, C) \to FB \times \homC(B, C) \to F(B \times \homC(B, C)) \to FC
-  \end{align*}
-  I.e.,
-  \begin{align*}
-    A \times \homC(B, C) &\to FC \\
-    (a, g) &\mapsto F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(g, f a))
-  \end{align*}
-  % \begin{align*}
-      %       A \times \homC(B, C) \xrightarrow{f \times \id} FB \times \homC(B, C) \xrightarrow{\theta_{\homC(B, C), B}}  F(B \times \homC(B, C)) \xrightarrow{F\epsilon} FC
-      %     \end{align*}
-  where $\theta$ is the strength for $F$.
-  \todo{Check this is a strong natural transformation}
-
-  Conversely, given a strong natural transformation $\eta : A \times \homC(B, -) \Rightarrow F$, the component at $B$ is a function $\eta_B : A \times \homC(B, B) \to FB$; we define $Q(\eta) : A \to FB$ by $Q(\eta)(a) = \eta_B(a, \id_B)$
-
-\todo{remainder of the proof is not very interesting}
-
-      %       $\Psi(\eta) : A \to FB$ to be $A \xrightarrow{A \times \const_{\id_B}} A \times \homC(B, B) \xrightarrow{\eta_B} FB$.
-
-%  Now, verifying these are inverse:
-%  \begin{align*}
-%    P(Q(\eta))_C (a,g)
-%    &= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(g, \Psi(\eta)(a))) \\
-%    &= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(g, \eta_B(a, \id_B))) \\
-%    &= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(\id, \eta_B)(g, (a, \id_B))) \\
-%    &= F(\lambda x. \lambda h. h x)(\eta_{\homC(B, C) \times B} s_{\homC(B, C), B}(g, a, \id_B)) && \text{($\theta$ is a strong transformation)}\\
-%    &= F(\lambda x. \lambda h. h x)(\eta_{\homC(B, C) \times B} (a, \lambda d. (g, \id_B d)) ) && \text{(definition of $s$)}\\
-%    &= F(\lambda x. \lambda h. h x)(\eta_{\homC(B, C) \times B} (a, \lambda d. (g, d)) ) \\
-%    &= \eta_{C}(\lambda (a, f). (a, \lambda b. \mathsf{fst}(f b)\mathsf{snd}(f b)) (a, \lambda d. (g, d)) && \text{(naturality of $\eta$)}\\
-%    &= \eta_{C}(a, \lambda b. g b) \\
-%    &= \eta_{C}(a, g)
-%  \end{align*}
-%  And in the other direction:
-%  \begin{align*}
-%    Q(P(f))(a)
-%    &= P(f)_B(a, \id_B) \\
-%    &= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, B), B}(\id_B, f a))\\
-%    &= F(\lambda x. \lambda h. h x)(F(\lambda b. (\id_B, b)))\theta_{1, B}(f a) && \text{(naturality of $\theta$)}\\
-%    &= F(\lambda b. \id_B b)\theta_{1, B}(f a)\\
-%    &= \theta_{1, B}(f a) && \text{(strength of $\theta$)}\\
-%    &= f a
-%  \end{align*}
-%\todo{Naturality}
-\end{proof}
-
-This is a generalisation of~\cite[Proposition 2.2]{SecondOrderFunctionals}, isolating the properties of $\Set$ that are used. We can finally construct setters:
-
-\begin{definition}
-  Supposed $\C$ is cartesian closed and let $\Strong(\C)$ act on $\C$ by evaluation. The \emph{category of setters} $\Setter_\C$ is the category of lawful optics for this action.
-\end{definition}
-
-Due to the above lemma, we can eliminate the coend from the definition:
-\begin{align*}
-  \Setter_\C((S, S'), (A, A')) &= \int^{F \in \Strong(\C)} \C(S, FA) \times \C(FA', S') \\
-                               &\cong \int^{F \in \Strong(\C)} \Strong_\C(\times)(S \times \homC(A, -), F)  \times \C(FA', S') \\
-                               &\cong \C(S \times \homC(A, A'), S') \\
-                               &\cong \C(\homC(A, A'), \homC(S,S'))
-\end{align*}
-In the Haskell \lenslib{} library, the map $\homC(A, A) \to \homC(S,S)$ corresponding to a setter is called $\fover$: we think of a setter as allowing us to apply a function $A \to A$ over some parts of $S$.
-
-The laws for setters are a kind of `functoriality':
+To devise the concrete form of a setter, we use the following proposition.
+This is a generalisation of~\cite[Proposition 2.2]{SecondOrderFunctionals}, and helps to explain why the store comonad is so important.
+
+\begin{proposition}
+If $\C$ is cotensored over $\Set$ then the evaluation-at-$A$ functor $-A : [\C, \C] \to \C$ has a right adjoint given by $S \mapsto S^{\C(-, A)}$.
+
+If $\C$ is tensored over $\Set$ then $-A : [\C, \C] \to \C$ has a left adjoint given by $S \mapsto \C(A, -) \cdot S$.
+\end{proposition}
+\begin{proof}
+For the first, we have
+\begin{align*}
+\C(FA, S) 
+&\cong \int_X \Set(\C(X, A), \C(FX, S)) \\
+&\cong \int_X \C(FX, S^{\C(X, A)}) \\
+&\cong [\C, \C](F, S^{\C(-, A)})
+\end{align*}
+and for the second,
+\begin{align*}
+\C(S, FA) 
+&\cong \int_X \Set(\C(A, X), \C(S, FX)) \\
+&\cong \int_X \C(\C(A, X) \cdot S, FX) \\
+&\cong [\C, \C](\C(A, -) \cdot S, F)
+\end{align*}
+\end{proof}
+
+We can use either of the above adjunctions to describe setters concretely:
+\begin{align*}
+  \Setter_\C((S, S'), (A, A')) &= \int^{F \in [\C, \C]} \C(S, FA) \times \C(FA', S') \\
+                               &\cong \int^{F \in [\C, \C]} [\C, \C](\C(A, -) \cdot S, F) \times \C(FA', S') \\
+                               &\cong \C(\C(A, A') \cdot S, S') \\
+                               &\cong \Set(\C(A, A'), \C(S, S'))
+\end{align*}
+
+\begin{remark}
+This characterisation of setters is maybe a little odd, in that we have ended up with a function of $\Set$s, rather than a description internal to $\C$.
+If we modify our definition of $\Setter$ slightly, we can get such an internal characterisation.
+
+Suppose $\C$ is cartesian closed and let $\Strong_\C$ be the category of \emph{strong functors}\cite{StrongFunctors} on $\C$.
+Then, again, $\Strong_\C$ acts on $\C$ by evaluation.
+We leave it to the reader to verify there is a natural isomorphism \[\C(A, FB) \cong \Strong_\C(A \times \homC(B, -), F),\] which we can use to describe optics for this action as elements of $\C(\homC(A, A'), \homC(S,S'))$.
+\end{remark}
+
+In the Haskell \lenslib{} library, the map $\C(A, A) \to \C(S,S)$ corresponding to a setter is called $\fover$: we think of a setter as allowing us to apply a function $A \to A$ over some parts of $S$.
+
+The laws for setters are a kind of functoriality:
 
@@
 \begin{align*}
-\fover \; \nameof{\id_A} &= \nameof{\id_S} \\
-({-} \circ =)(\fover \times \fover) &= \fover ({-} \circ =)
-\end{align*}
-where  $\circ$ denotes internal composition and $\nameof{\id_X} : 1 \to \homC(X, X)$ denotes the `name of' $\id_X$.
-\end{proposition}
-\begin{proof}
-We have a chain of isomorphisms
-\begin{align*}
-&\int^{M_1, M_2 \in \Strong_\C} \C(S, M_1 A) \times \C(M_1 A, M_2  A) \times \C(M_2 A, S) \\
-&\cong \int^{M_1, M_2 \in \Strong_\C} \Strong_\C(S \times \homC(A, -), M_1) \times \Strong_\C(M_1 A \times \homC(A, -), M_2) \times \C(M_2 A, S) \\
-&\cong \int^{M_2 \in \Strong_\C} \Strong_\C(S \times \homC(A, A) \times \homC(A, -), M_2) \times \C(M_2 A, S) \\
-&\cong \C(S \times \homC(A, A) \times \homC(A, A), S) \\
-&\cong \C(\homC(A, A) \times \homC(A, A), \homC(S,S))
-\end{align*}
+\fover(\id_A) &= \id_S \\
+\fover(f)\fover(g)&= \fover(fg)
+\end{align*}
+\end{proposition}
+\begin{proof}
 \todo{Worth writing out the rest?}
@@
 
-\todo{This previous section might also work just with monoidal closed? I don't see where cartesianness was used.}
+\todo{This section might also work just with monoidal closed? I don't see where cartesianness was used.}
 
@@
 \end{itemize}
-
-%\subsection{Indexed Optics}
-%\todo{
-%  This possibly looks like
-%  \begin{align*}
-%    \int^{M \in \M} \C(S, M(IA)) \times \C(M A', S')
-%  \end{align*}
-%  with another monoidal action $I$. The $I$ would need to distribute over $M$ in some way. ``Coindexed'' optics seem to have
-%  \begin{align*}
-%    \int^{M \in \M} \C(S, J(MA)) \times \C(M A', S')
-%  \end{align*}
-%  which is why they pass information `in the other direction' but still transform covariantly.
-%}
 
@@
 
+%\subsection{Indexed Optics}
+%\todo{
+%  This possibly looks like
+%  \begin{align*}
+%    \int^{M \in \M} \C(S, M(IA)) \times \C(M A', S')
+%  \end{align*}
+%  with another monoidal action $I$. The $I$ would need to distribute over $M$ in some way. ``Coindexed'' optics seem to have
+%  \begin{align*}
+%    \int^{M \in \M} \C(S, J(MA)) \times \C(M A', S')
+%  \end{align*}
+%  which is why they pass information `in the other direction' but still transform covariantly.
+%}
+
 \section{Conclusion}

### 2018-06-26 paper.tex
Couple more details

@@
 The universal property for $\Optic_\otimes$ given in this section is an argument for this being the ``morally correct'' tensor, although it does seem a little strange.
-When we later discuss lawful optics, we must use the unswitched tensor to maintain the invariant that a objects are of the form $(X, X)$.
+When we later discuss lawful optics, we are forced to use the unswitched tensor to maintain the invariant that our objects are of the form $(X, X)$.
 
@@
 \[
-  \begin{tikzcd}
+  \begin{tikzcd}[column sep = large]
     X \otimes Y \otimes Y^* \otimes X^* \ar[r, "X \otimes \varepsilon_Y \otimes X^*"]  \ar[dr, "\varepsilon_{X \otimes Y}", swap] & X \otimes X^* \ar[d, "\varepsilon_X"] \\
@@
 \begin{proof}
-  That morphisms of the form $\iota(f, g)$ constitute a category and that ${(-)}^*$ is a symmetric monoidal involution is clear: we have
+  That morphisms of the form $\iota(f, g)$ constitute a category is clear. The functor ${(-)}^*$ is a symmetric monoidal involution, in fact it is strictly so:
   \begin{align*}
@@
   To check extranaturality of $\varepsilon$, suppose we have a dualisable optic $\iota(f, g) : (S, S') \hto (T, T')$, so $f : S \to T$ and $g : T' \to S'$.
+Luckily here all the switching in the definitions scancels out!
 Extranaturality is witnessed by the equality of the string diagrams:
@@
   \end{center}
-  Symmetry:
+  For symmetry:
   \begin{center}
@@
   \end{center}
-  Monoidality: \todo{there is basically nothing to do in the graphical calculus}
+  And for monoidality there is essentially nothing to do in the graphical calculus. 
+  \begin{center}
+    \input{diagrams/counit-monoidal-left.tikz}
+    \qquad \raisebox{2cm}{$=$} \qquad
+    \input{diagrams/counit-monoidal-right.tikz}
+  \end{center}
 
@@
 \subsection{Effectful Optics}
-\newcommand{\monact}{\ltimes}
+\newcommand{\monact}{\rtimes}
 
@@
 Suppose $T$ is a strong monad with strength $\theta_{A, B} : A \otimes T B \to T(A \otimes B)$.
-For $A \in \C$, we have a functor $A \otimes - : \C_T \to \C_T$.
-On a morphism $f : X \to Y$ in $\C_T$, we define $A \otimes f : A \otimes X \to A \otimes Y$ to be the composite
+For $A \in \C$, we have a functor $A \otimes - : \C_T \to \C_T$ which on a morphism $f : X \to Y$ in $\C_T$ is defined to be the composite
 \begin{align*}
@@
 
-Our goal is to show that the assignment $A \mapsto A \otimes -$ extends to a monoidal functor $a : \C \to [\C_T, \C_T]$.
+Our goal is to show that the assignment $A \mapsto A \otimes -$ extends to a functor $a : \C \to [\C_T, \C_T]$.
 A morphism $f : A \to B$ in $\C$ induces a natural transformation $A \otimes - \to B \otimes -$ with components $A \otimes X \to T(B \otimes X)$ given by composing $A \otimes X \to B \otimes X$ with the unit of the monad.
-This transformation is natural by \todo{todo}.
-
-Finally, the functor $a$ is monoidal, with the structure maps given by the associativity and unit maps of $\C$. \todo{this uses that the strength commutes with unitors and associativity}
+Naturality is easy to check:
+\[\begin{tikzcd}
+A \otimes X \ar[r] \ar[d] & B \otimes X \ar[r] \ar[d] & T(B \otimes X) \ar[d] \\
+A \otimes TY \ar[r] \ar[d] & B \otimes TY \ar[r] \ar[d] & T(B \otimes TY) \ar[d] \\
+T(A \otimes Y) \ar[r] & T(B \otimes Y) \ar[r] & TT(B \otimes Y)
+\end{tikzcd}\]
+The upper left square commutes by functoriality of $\otimes$, lower left by naturality of the strength, the two right squares by naturality of the unit.
+
+Finally, this functor $a$ is monoidal, with the structure maps given by the associativity and unit maps of $\C$. \todo{this uses that the strength commutes with unitors and associativity}
 \end{proof}

### 2018-06-26 paper.tex
Explain Folds and fix some typos

@@
 \newcommand{\Review}{\mathbf{Review}}
+\newcommand{\Fold}{\mathbf{Fold}}
 
@@
 K &\cong \int^C KC \times \C(-,C) &
-K &\cong \int_C (KC)^{\C(C,-)} \\
+K &\cong \int_C \Set(\C(C,-), KC) \\
 H &\cong \int^C HC \times \C(C,-)  &
-H &\cong \int_C (HC)^{\C(-,C)}
-\end{align*}
-where the components of the isomorphisms at $X$ are given by inclusion with the identity morphism $\C(X, X)$ on the left, and projection onto the identity morphism on the right.
+H &\cong \int_C \Set(\C(-,C), HC)
+\end{align*}
+where the components of the isomorphisms at $X$ are given by inclusion with the identity morphism $\C(X, X)$ on the left, and evaluation at the identity morphism on the right.
 \qed
@@
 
-Because this coend takes place in $\Set$, we can use Lemma \ref{lemma:calculate-coend} to describe the set $\Optic_\otimes((S, S'), (A, A'))$ explicitly.
+Because this coend takes place in $\Set$, we can use Lemma \ref{lemma:calculate-coend} to describe $\Optic_\otimes((S, S'), (A, A'))$ explicitly.
 It is the set of pairs $(l, r)$, where $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, quotiented by the relation
@@
   To check extranaturality of $\varepsilon$, suppose we have a dualisable optic $\iota(f, g) : (S, S') \hto (T, T')$, so $f : S \to T$ and $g : T' \to S'$.
-Luckily here all the switching in the definitions scancels out!
+Luckily here all the switching in the definitions cancel out!
 Extranaturality is witnessed by the equality of the string diagrams:
@@
     &= \rep{(FS \otimes \phi_I^{-1}) \phi^{-1}_{S,I} (F \rho_S^{-1})}{(F \rho_{S'}) \phi_{S',I} (FS \otimes \phi_I)} \\
-    &= \rep{\rho_{FS}^{-1}}{\rho_{FS'} } \\
+    &= \rep{\rho_{FS}^{-1}}{\rho_{FS'}} \\
     &= \varepsilon_{(FS, FS')}
@@
   \begin{align*}
-  \phi &: F(I A) \to (F^\bullet I)(F_2A) \\
+  \phi &: F(I A) \to (F^\bullet I)(FA) \\
   \phi_{M,A} &: F(MA) \to (F^\bullet M)(F A)
@@
   Suppose we have two lawful optics $\rep{l}{r} : R \hto S$ and $\rep{l'}{r'} : S \hto A$, where $l : R \to MS$ and $l' : S \to NA$.
-We must show that $\rep{(Ml')l}{r (Mr') }$ is also a lawful optic.
+We must show that $\rep{(Ml')l}{r (Mr')}$ is also a lawful optic.
 The first equation is straightforward:
   \begin{align*}
-    \outside(\rep{l; (Ml')}{(Mr') ; r  })
+    \outside(\rep{l; (Ml')}{(Mr') ; r})
     &= l ; Ml' ; Mr' ; r \\
@@
   For the second, we must show
-  \[ \repthree{ l;(Ml')}{(Mr'); r;l;(Ml')}{(Mr') ; r } = \repthree{l;(Ml')}{\id_{MNA}}{(Mr') ; r }. \]
+  \[ \repthree{ l;(Ml')}{(Mr'); r;l;(Ml')}{(Mr') ; r} = \repthree{l;(Ml')}{\id_{MNA}}{(Mr') ; r}. \]
 
@@
   \end{align*}
-  And similarly for the other generating relation, $\repthree{l}{c;\phi_S}{r } = \repthree{l}{c}{\phi_S; r }$.
-
-  Therefore, the chain of relations proving $\repthree{l}{r;l}{r } = \repthree{l}{\id_{MA}}{r }$ can be replicated to show
-  \begin{align*}
-    \repthree{l;(Ml')}{(Mr');r;l;(Ml')}{(Mr') ; r } &= \repthree{l;(Ml')}{(Mr');\id_{MA};(Ml')}{(Mr') ; r },
-  \end{align*}
-  which is equal to $\repthree{l;(Ml')}{M(r'l')}{(Mr') ; r }$.
-
-  Similarly, a generating relation $\repthree{l';\psi_A}{c'}{r' } = \repthree{l'}{\psi_A ; c'}{r' }$ in \[\int^{N_1, N_2 \in \M} \C(S, N_1 A) \times \C(N_1 A, N_2 A) \times \C(M_2 A, S)\]
+  And similarly for the other generating relation, $\repthree{l}{c;\phi_S}{r} = \repthree{l}{c}{\phi_S; r}$.
+
+  Therefore, the chain of relations proving $\repthree{l}{r;l}{r} = \repthree{l}{\id_{MA}}{r}$ can be replicated to show
+  \begin{align*}
+    \repthree{l;(Ml')}{(Mr');r;l;(Ml')}{(Mr') ; r} &= \repthree{l;(Ml')}{(Mr');\id_{MA};(Ml')}{(Mr') ; r},
+  \end{align*}
+  which is equal to $\repthree{l;(Ml')}{M(r'l')}{(Mr') ; r}$.
+
+  Similarly, a generating relation $\repthree{l';\psi_A}{c'}{r'} = \repthree{l'}{\psi_A ; c'}{r'}$ in \[\int^{N_1, N_2 \in \M} \C(S, N_1 A) \times \C(N_1 A, N_2 A) \times \C(M_2 A, S)\]
   implies that
   \begin{align*}
-    \repthree{l;M(l';\psi_A)}{Mc'}{(Mr') ; r }
-    &= \repthree{l;Ml';M\psi_A}{Mc'}{(Mr') ; r } \\
-    &= \repthree{l;Ml'}{M\psi_A ; Mc'}{(Mr') ; r } \\
-    &= \repthree{l;Ml'}{M(\psi_A;c')}{(Mr') ; r }
-  \end{align*}
-  So again we can replicate the chain of relations proving $\repthree{l'}{r';l'}{r' } = \repthree{l'}{\id_{MA}}{r' }$ to show that
-  \[\repthree{l;(Ml')}{M(r'l')}{(Mr') ; r } = \repthree{l;(Ml')}{\id_{MNA}}{(Mr') ; r } \]
+    \repthree{l;M(l';\psi_A)}{Mc'}{(Mr') ; r}
+    &= \repthree{l;Ml';M\psi_A}{Mc'}{(Mr') ; r} \\
+    &= \repthree{l;Ml'}{M\psi_A ; Mc'}{(Mr') ; r} \\
+    &= \repthree{l;Ml'}{M(\psi_A;c')}{(Mr') ; r}
+  \end{align*}
+  So again we can replicate the chain of relations proving $\repthree{l'}{r';l'}{r'} = \repthree{l'}{\id_{MA}}{r'}$ to show that
+  \[\repthree{l;(Ml')}{M(r'l')}{(Mr') ; r} = \repthree{l;(Ml')}{\id_{MNA}}{(Mr') ; r} \]
 
@@
   \outside(\Optic(F)(\rep{l}{r}))
-  &= \outside(\rep{(Fl);\phi^{-1}_{M,A} }{\phi_{M,A'};(Fr) }) \\
+  &= \outside(\rep{(Fl);\phi^{-1}_{M,A}}{\phi_{M,A'};(Fr)}) \\
   &= (Fl);\phi^{-1}_{M,A};\phi_{M,A'};(Fr)\\
-  &= (Fl);(F_2r)\\
+  &= (Fl);(Fr)\\
   &= \id_{FS}
@@
 \begin{proposition}
-  Let $\rep{l}{r } : S \hto A$ be an optic. If $l;r = \id_S$ and $r;l = \phi A$ for some $\phi : M \to M$ in $\M$, then $\rep{l}{r }$ is lawful.
-\end{proposition}
-\begin{proof}
-  The $\outside(\rep{l}{r }) = l;r = \id_S$ is exactly the first condition. And for the second, we verify:
-  \begin{align*}
-    \twice(\rep{l}{r })
-    &= \repthree{l}{r;l}{r } \\
-    &= \repthree{l}{\phi A}{r } && \text{($r;l = \phi A$)}\\
-    &= \repthree{l (\phi A)}{\id_{MA}}{r } && \text{(coend relation)} \\
-    &= \repthree{l;r;l}{\id_{MA}}{r } && \text{($r;l = \phi A$ again)}\\
-    &= \repthree{l}{\id_{MA}}{r }  && \text{($l;r = \id_S$)}\\
-    &= \once(\rep{l}{r })
+  Let $\rep{l}{r} : S \hto A$ be an optic. If $l;r = \id_S$ and $r;l = \phi A$ for some $\phi : M \to M$ in $\M$, then $\rep{l}{r}$ is lawful.
+\end{proposition}
+\begin{proof}
+  The $\outside(\rep{l}{r}) = l;r = \id_S$ is exactly the first condition. And for the second, we verify:
+  \begin{align*}
+    \twice(\rep{l}{r})
+    &= \repthree{l}{r;l}{r} \\
+    &= \repthree{l}{\phi A}{r} && \text{($r;l = \phi A$)}\\
+    &= \repthree{l (\phi A)}{\id_{MA}}{r} && \text{(coend relation)} \\
+    &= \repthree{l;r;l}{\id_{MA}}{r} && \text{($r;l = \phi A$ again)}\\
+    &= \repthree{l}{\id_{MA}}{r}  && \text{($l;r = \id_S$)}\\
+    &= \once(\rep{l}{r})
   \end{align*}
@@
 
-Let $\inside : \Optic_\M(S, A) \to \int^{M \in \M} \C(M A, M A)$ be the map induced by $\inside(\rep{l}{r }) = \langle r ; l \rangle$.
+Let $\inside : \Optic_\M(S, A) \to \int^{M \in \M} \C(M A, M A)$ be the map induced by $\inside(\rep{l}{r}) = \langle r ; l \rangle$.
 We might ask that instead of requiring $r;l = \phi A$ exactly, we have $\langle r ; l \rangle = \langle \phi A \rangle$ in $\int^{M \in \M} \C(M A, M A)$.
@@
   Suppose $p : S \hto A$ satisfies $\outside(p) = \id_S$ and $\inside(p) = \langle \phi A \rangle$.
-Then there exists a representative $\rep{l}{r }$ such that $l ; r = \psi A$ on the nose for some (possibly different) $\psi : M \to M$.
+Then there exists a representative $\rep{l}{r}$ such that $l ; r = \psi A$ on the nose for some (possibly different) $\psi : M \to M$.
 \end{proposition}
@@
   We can now inductively apply the above argument to the shorter chain \[l'r' = u_1^2 \leftrightsquigarrow \dots \leftrightsquigarrow u_n^2 \leftrightsquigarrow (\psi A)^2 = \psi^2 A,\] obtained by squaring each morphism in the original chain, until we are left with a representative $\rep{l^*}{r^*}$ such that $r^*;l^* = \psi^N_A$, for some $N>0$.
-This pair $\rep{l^*}{r^* }$ is the required representative.
+This pair $\rep{l^*}{r^*}$ is the required representative.
 \end{proof}
@@
 This last set is the set of concrete lenses $\conc_\times((S, S'), (A, A'))$.
-Explicitly this isomorphism states that, given an optic $\rep{l}{r } : (S, S') \hto (A, A')$, the corresponding element of $\conc_\times((S, S'), (A, A'))$ is the pair $(\fget, \fput)$, where $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
+Explicitly this isomorphism states that, given an optic $\rep{l}{r} : (S, S') \hto (A, A')$, the corresponding element of $\conc_\times((S, S'), (A, A'))$ is the pair $(\fget, \fput)$, where $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
 In the other direction, given $(\fget, \fput)$, the corresponding optic has representative $\rep{[\id_S, \fget]}{\fput}$.
@@
   \begin{align*}
-    \Phi(\repthree{l}{c}{r }) = (&\pi_2 l, \\
+    \Phi(\repthree{l}{c}{r}) = (&\pi_2 l, \\
                                    &\pi_2 c (\pi_1 l \times A), \\
@@
   \]
-  is a witness that $\rep{\fput (i \times A)}{[j,\fget] } = \rep{\fput}{[\id_S, \fget] }$ as elements of $\Optic_\M(S, A)$.
+  is a witness that $\rep{\fput (i \times A)}{[j,\fget]} = \rep{\fput}{[\id_S, \fget]}$ as elements of $\Optic_\M(S, A)$.
 \end{proof}
@@
 \end{align*}
-If we are given a prism $\rep{l}{r } : (S, S') \hto (A, A')$ then associated $\freview$ and $\fmatching$ morphisms are given by $\freview = r \inr$ and $\fmatching = (r\inl \sqcup A)l$
+If we are given a prism $\rep{l}{r} : (S, S') \hto (A, A')$ then associated $\freview$ and $\fmatching$ morphisms are given by $\freview = r \inr$ and $\fmatching = (r\inl \sqcup A)l$
 
@@
   \[ \C(S, A) \times \C(A, A) \times \C(A, S) \]
-  The condition $\outside(\rep{l}{r }) = \id_S$ is the claim that $rl = \id_S$, and $\once(\rep{l}{r }) = (l, \id_A, r)$ is equal to $\twice(\rep{l}{r }) = (l, lr, r)$ iff $lr = \id_A$.
+  The condition $\outside(\rep{l}{r}) = \id_S$ is the claim that $rl = \id_S$, and $\once(\rep{l}{r}) = (l, \id_A, r)$ is equal to $\twice(\rep{l}{r}) = (l, lr, r)$ iff $lr = \id_A$.
 \end{proof}
@@
 Then, again, $\Strong_\C$ acts on $\C$ by evaluation.
-We leave it to the reader to verify there is a natural isomorphism \[\C(A, FB) \cong \Strong_\C(A \times \homC(B, -), F),\] which we can use to describe optics for this action as elements of $\C(\homC(A, A'), \homC(S,S'))$.
+We leave it to the reader to verify there is a natural isomorphism \[\C(S, FA) \cong \Strong_\C(\homC(A, -) \times S, F),\] which we can use to describe optics for this action as elements of $\C(\homC(A, A'), \homC(S,S'))$.
 \end{remark}
@@
 \subsection{Traversals}
-Let $\C = \Set$. \todo{define applicative/traversable functors}
+In this section we work in the case $\C = \Set$. \todo{define applicative/traversable functors}
 
 \begin{definition}
-The category $\Traversal_\C$ of traversals in $\C$ is the category of lawful optics for the action of $\Traversable_\C$ on $\C$ given by evaluation.
+The category $\Traversal$ of traversals is the category of lawful optics for the action of $\Traversable$ on $\Set$ given by evaluation.
 (Yes, the names $\Traversal$ vs\@.
@@
 \begin{align*}
-UR^*_{X, Y} Z = \Sigma_{n\in \bN} X^n \times \homC(Y^n,Z)
-\end{align*}
-Moreover, this correspondence forms an isomorphism of categories between $\Traversable$ and the Eilenberg-Moore category of coalgebras for $UR^*_{-, -}$, which we denote $\C_T$. \qed
+UR^*_{X, Y} Z = \Sigma_{n\in \bN} X^n \times \Set(Y^n,Z)
+\end{align*}
+Moreover, this correspondence forms an isomorphism of categories between $\Traversable$ and the Eilenberg-Moore category of coalgebras for $UR^*_{-, -}$, which we denote $\E$. \qed
 \end{proposition}
@@
 \begin{remark}
-In~\cite[Section 2.3]{ProfunctorOptics}, it is claimed that a traversal $S \hto A$ exhibits an isomorphism \[S \cong \Sigma_n A^n \times \homC(A^n,S).\] This appears to be a misreading of~\cite[Proposition 5.4]{SecondOrderFunctionals}.
+In~\cite[Section 2.3]{ProfunctorOptics}, it is claimed that a traversal $S \hto A$ exhibits an isomorphism \[S \cong \Sigma_n A^n \times \Set(A^n,S).\] This appears to be a misreading of~\cite[Proposition 5.4]{SecondOrderFunctionals}.
 \end{remark}
@@
 \begin{lemma}
-  For any objects $A, B \in \Set$ and traversable functor $F$, \[\C(FA, B) \cong \Traversable(F, \Sigma_n (-)^n \times \homC(A^n,B))\]
+  For any objects $A, B \in \Set$ and traversable functor $F$, \[\Set(FA, B) \cong \Traversable(F, \Sigma_n (-)^n \times \Set(A^n,B))\]
 naturally in $B$ and $F$.
-In other words, the functor \[(B \mapsto \Sigma_n (-)^n \times \homC(A^n,B)) : \C \to \Traversable\] is right adjoint to the evaluation-at-$A$ functor $-A : \Traversable \to \C$.
+In other words, the functor \[(B \mapsto \Sigma_n (-)^n \times \Set(A^n,B)) : \Set \to \Traversable\] is right adjoint to the evaluation-at-$A$ functor $-A : \Traversable \to \Set$.
 \end{lemma}
@@
 \begin{align*}
-L_T : \C^\op \times \C_T &\to \C \\
+L_T : \Set^\op \times \E &\to \Set \\
 (X, (F, f)) &\mapsto FX \\
-R_T : \C \times \C &\to \C_T \\
+R_T : \Set \times \Set &\to \E \\
 (Y, Z) &\mapsto (UR^*_{-, Y} Z, \varepsilon)
@@
 \begin{align*}
-L_T(A) : \C_T &\to \C \\
+L_T(A) : \E &\to \Set \\
 (F, f) &\mapsto FA \\
-R_T(A) : \C &\to \C_T \\
+R_T(A) : \Set &\to \E \\
 Z &\mapsto (UR^*_{-, A} Z, \varepsilon)
@@
 \begin{align*}
-\Optic_\Traversable((S, S'), (A, A')) &= \int^{F \in \Traversable} \C(S, F A) \times \C(F A', S') \\
-&\cong \int^{F \in \Traversable} \C(S, F A) \times \Traversable(F, \Sigma_n (-)^n \times \homC(A'^n,S')) \\
-&\cong \C(S, \Sigma_n A^n \times \homC(A'^n,S'))
+\Optic_\Traversable((S, S'), (A, A')) &= \int^{F \in \Traversable} \Set(S, F A) \times \Set(F A', S') \\
+&\cong \int^{F \in \Traversable} \Set(S, F A) \times \Traversable(F, \Sigma_n (-)^n \times \Set(A'^n,S')) \\
+&\cong \Set(S, \Sigma_n A^n \times \Set(A'^n,S'))
 \end{align*}
@@
   \end{align*}
-  which evaluated on an element $\repthree{l}{c}{r }$ is given by
+  which evaluated on an element $\repthree{l}{c}{r}$ is given by
   \begin{align*}
@@
   \end{align*}
-  Now suppose we are given an optic $p$ with corresponding element of $\conc_\otimes(S, A)$ is $\funzip$. Then \[\outside(\rep{\funzip }{\ev_{A, S} }) = \ev_{A, S} \; \funzip,\] giving the first law.
+  Now suppose we are given an optic $p$ with corresponding element of $\conc_\otimes(S, A)$ is $\funzip$. Then \[\outside(\rep{\funzip}{\ev_{A, S} }) = \ev_{A, S} \; \funzip,\] giving the first law.
 
@@
   \begin{align*}
-    \Phi(\once(\rep{\funzip }{\ev_{A, S} }))
-    &= \Phi(\repthree{\funzip }{\id_{\homC(A,S) \otimes A}}{\ev_{A, S} }) \\
+    \Phi(\once(\rep{\funzip}{\ev_{A, S}}))
+    &= \Phi(\repthree{\funzip}{\id_{\homC(A,S) \otimes A}}{\ev_{A, S} }) \\
     &= (\widetilde{(\tilde{\ev_{A, S}} \otimes A)\id_{\homC(A,S) \otimes A}} \otimes A)\funzip \\
@@
     &= (\coev_{\homC(A, S), A} \otimes A)\funzip \\
-    \Phi(\twice(\rep{\funzip }{\ev_{A, S} }))
-    &= \Phi(\repthree{\funzip }{\funzip \; \ev_{A, S}}{\ev_{A, S} }) \\
+    \Phi(\twice(\rep{\funzip}{\ev_{A, S} }))
+    &= \Phi(\repthree{\funzip}{\funzip \; \ev_{A, S}}{\ev_{A, S} }) \\
     &= (\widetilde{(\tilde{\ev_{A, S}} \otimes A)(\funzip \; \ev_{A, S})} \otimes A)\funzip \\
@@
 
-If we have a monoidal category $\M$ that acts on two different categories $\C_1$ and $\C_2$, we may well form the `optic' category:
+If we have a monoidal category $\M$ that acts on two different categories $\C_1$ and $\C_2$, we may form the `optic' category:
 \begin{align*}
@@
 To encode \mintinline{haskell}{Getter}s or \mintinline{haskell}{Review}s, we then set $\C_2$ or $\C_1$ to be the codiscrete category $\C_\mathsf{codisc}$ with the same set of objects as $\C$, so that all homsets are the one element set.
-In this way we indeed get categories $\Getter$ and $\Review$ that are isomorphic to $\C$ and $\C^\op$.
-The functor $\C \to \C_\mathsf{codisc}$ induces functors $\Lens \to \Getter$ and $\Prism \to \Review$.
+In this way we indeed get a category $\Getter$ that is isomorphic to $\C$.
+\begin{align*}
+\int^{M \in \M} \C(S, M \times A) \times \C_\mathsf{codisc}(M \times A', S')
+&\cong \int^{M \in \M} \C(S, M \times A) \\
+&\cong \C(S, 1 \times A) \\
+&\cong \C(S, A)
+\end{align*}
+This works for $\Review$ in the same way, putting $\C_\mathsf{codisc}$ on the left. The functor $\C \to \C_\mathsf{codisc}$ induces functors $\Lens \to \Getter$ and $\Prism \to \Review$.
+
+Finally, we encode $\Fold$s, which in $\Set$ are functions $S \to \mathrm{List}\,A$. The key is that the $\mathrm{List}$ functor is the terminal $\Traversable$ functor, so we have isomorphisms
+\begin{align*}
+&\int^{M \in \Traversable} \Set(S, MA) \times \Set_\mathsf{codisc}(MA', S') \\
+&\cong \int^{M \in \Traversable} \Set(S, MA) \\
+&\cong \Set(S, \mathrm{List}\,A)
+\end{align*}
 
@@
 %
-% One issue with the definition of optic given in the last section is that it could be difficult to determine when two optics $\rep{l}{r }, \langle l', r' \rangle : S \hto A$
+% One issue with the definition of optic given in the last section is that it could be difficult to determine when two optics $\rep{l}{r}, \langle l', r' \rangle : S \hto A$
 % are equal. For some choices of $\M$, however, we can reduce a zigzag of relations to a single one.
@@
 \begin{proof}
-  For any $P \in \Prof(\C, \C)$, there is a map $\eta : P \hto U \Phi_\M P$, given by $\eta(p) = \repthree{\id_A}{p}{\id_B }$.
+  For any $P \in \Prof(\C, \C)$, there is a map $\eta : P \hto U \Phi_\M P$, given by $\eta(p) = \repthree{\id_A}{p}{\id_B}$.
 
@@
   \begin{align*}
-    \repthree{l}{p}{r } = \Pastro_\M P(l, r) \alpha_{A, B, M} \; \eta(p)
+    \repthree{l}{p}{r} = \Pastro_\M P(l, r) \alpha_{A, B, M} \; \eta(p)
   \end{align*}
@@
   \begin{align*}
-    \hat{f}\alpha_{A,B,N}(\repthree{l}{p}{r })
-    &= \hat{f}(\repthree{Nl}{p}{Nr }) && \text{(definition of $\alpha$)}\\
+    \hat{f}\alpha_{A,B,N}(\repthree{l}{p}{r})
+    &= \hat{f}(\repthree{Nl}{p}{Nr}) && \text{(definition of $\alpha$)}\\
     &= T(Nl, Nr) \; \beta_{A, B, NM} \; f(p) && \text{(definition of $\hat{f}$)}\\
@@
 \begin{corollary}
-  A profunctor optic $p$ is determined by its component at $\Pastro_\M E_A$, and furthermore, this component is determined by its value on $\repfour{\id_A}{\id_A}{\id_A}{\id_A } \in (U \Pastro_\M E_A)(A, A)$.
+  A profunctor optic $p$ is determined by its component at $\Pastro_\M E_A$, and furthermore, this component is determined by its value on $\repfour{\id_A}{\id_A}{\id_A}{\id_A} \in (U \Pastro_\M E_A)(A, A)$.
 \end{corollary}
@@
   This is the content of the first two isomorphisms above.
-Explicitly, suppose $\hat{p} = \rep{l}{r }$ with $l : S \to MA$ and $r : MA \to S$.
+Explicitly, suppose $\hat{p} = \rep{l}{r}$ with $l : S \to MA$ and $r : MA \to S$.
 Then for any Tambara module $P$, the component of $p$ at $P$ is
@@
   \[
-    p_{\Pastro_\M E_A}(\repfour{\id_A}{\id_A}{\id_A}{\id_A }) = \repfour{l}{\id_A}{\id_A}{r }
+    p_{\Pastro_\M E_A}(\repfour{\id_A}{\id_A}{\id_A}{\id_A}) = \repfour{l}{\id_A}{\id_A}{r}
   \]
@@
 \begin{align*}
-  \Delta(\rep{l}{r }) &= \repthree{l}{lr}{r } \\
-  \varepsilon(\rep{l}{r }) &= rl
+  \Delta(\rep{l}{r}) &= \repthree{l}{lr}{r} \\
+  \varepsilon(\rep{l}{r}) &= rl
 \end{align*}
@@
 \subsection{The van Laarhoven Encoding}
-\todo{todo}
+
+Some optic variants can be encoded in a profunctor-like style without requiring the full complexity of profunctors.
+Chronologically this development came before profunctor optics, and was invented by Twan van Laarhoven \cite{VanLaarhovenPost}.
+
+The van Laarhoven encoding for \mintinline{haskell}{Lens}es and \mintinline{haskell}{Traversal}s is:
+\begin{minted}{haskell}
+type Lens s a      = forall f. Functor f     => (a -> f a) -> (s -> f s)
+type Traversal s a = forall f. Applicative f => (a -> f a) -> (s -> f s)
+type Setter s a    = forall f. Settable f    => (a -> f a) -> (s -> f s)
+\end{minted}
+What makes these particular optic variants work is that for \mintinline{haskell}{Lens}es, \mintinline{haskell}{Setter}s and \mintinline{haskell}{Traversal}s, the Tambara module that characterises them, $\Pastro_\M E_A$, can be written in the form \mintinline{haskell}{a -> f a} with \mintinline{haskell}{f} an instance of the relevant typeclass.
+Therefore, no expressive power is lost by restricting an optic to operate only on functions \mintinline{haskell}{a -> f a}, as the concrete description of the optic can be extracted from its value on that Tambara module.
+The same is not true for other optic variants, and indeed in the Haskell \lenslib{} library, \mintinline{haskell}{Prism}s and \mintinline{haskell}{Review}s use the profunctor encoding.
+
+The coend description can clarify which optic variants are likely to admit a van Laarhoven encoding.
+In each the above examples, the evaluation-at-$A$ functor $-A : \M \to \C$ has a right adjoint $R_A : \C \to \M$, so
+\begin{align*}
+\int^{F \in \M} \C(S, FA) \times \C(FA, S)
+&\cong \int^{F \in \M} \C(S, FA) \times \M(F, R_A S) \\
+&\cong \C(S,  (R_A S) \cdot A)
+\end{align*}
+The hope is then that one can devise a convenient typeclass that characterises functors of the form $R_A S$.
 

### 2018-07-04 paper.tex
Fill some gaps

@@
-\documentclass[11pt,a4paper]{article}
+\documentclass[11pt,letterpaper]{article}
 \usepackage{authblk}
@@
 \usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
+%\usepackage{geometry}
 \usepackage{minted}
@@
 \newcommand{\CoPoint}{\mathbf{CoPoint}}
+\newcommand{\App}{\mathbf{App}}
 \newcommand{\Traversable}{\mathbf{Traversable}}
+\newcommand{\IdxTraversable}{\mathbf{IdxTraversable}}
 
@@
 % Credit: Sam Buss
-\newbox\gnBoxA
-\newdimen\gnCornerHgt
-\setbox\gnBoxA=\hbox{$\ulcorner$}
-\global\gnCornerHgt=\ht\gnBoxA
-\newdimen\gnArgHgt
-\def\nameof #1{%
-    \setbox\gnBoxA=\hbox{$#1$}%
-    \gnArgHgt=\ht\gnBoxA%
-    \ifnum     \gnArgHgt<\gnCornerHgt \gnArgHgt=0pt%
-    \else \advance \gnArgHgt by -\gnCornerHgt%
-    \fi \raise\gnArgHgt\hbox{$\ulcorner$} \box\gnBoxA %
-    \raise\gnArgHgt\hbox{$\urcorner$}}
+%\newbox\gnBoxA
+%\newdimen\gnCornerHgt
+%\setbox\gnBoxA=\hbox{$\ulcorner$}
+%\global\gnCornerHgt=\ht\gnBoxA
+%\newdimen\gnArgHgt
+%\def\nameof #1{%
+%    \setbox\gnBoxA=\hbox{$#1$}%
+%    \gnArgHgt=\ht\gnBoxA%
+%    \ifnum     \gnArgHgt<\gnCornerHgt \gnArgHgt=0pt%
+%    \else \advance \gnArgHgt by -\gnCornerHgt%
+%    \fi \raise\gnArgHgt\hbox{$\ulcorner$} \box\gnBoxA %
+%    \raise\gnArgHgt\hbox{$\urcorner$}}
 
 % Special arrows
-\newcommand{\isoto}{\xrightarrow{\cong}}
+%\newcommand{\isoto}{\xrightarrow{\cong}}
 \newcommand{\hto}{\ensuremath{\,\mathaccent\shortmid\rightarrow\,}}
@@
 In its most concrete form, a \emph{lens} from $S$ to $A$ is a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$.
-From a software engineering standpoint, such a lens allows us to ``zoom in'' on $S$ to focus on a small part $A$, manipulate $A$ in some way, then ``zoom out'' and have our changes reflected $S$.
+From a software engineering standpoint, such a lens allows us to ``zoom in'' on $S$ to focus on a small part $A$, manipulate $A$ in some way, then ``zoom out'' and have our changes reflected in $S$.
 
@@
 
+%\todo{reference a whole bunch of bx and database stuff}
+
 Lenses were discovered to be just one of a hierarchy of data accessors, including prisms, setters, traversals, and more, collectively called \emph{optics}.
@@
 In Section~\ref{sec:profunctor-optics} we extend this to more of the optic hierarchy and translate the laws into the profunctor setting.
+
+\todo{Indexed optics?}
 
@@
 \begin{remark}
+  In this section we work with a fixed symmetric monoidal category $(\C, \otimes, I)$, with associator $\alpha$ and unitors $\lambda$ and $\rho$.
 To avoid getting lost in the notation we will use the standard cheat of omitting associativity morphisms and trust that the dedicated reader could insert them everywhere they are needed.
@@
 \begin{definition}
-  Let $\C$ be a symmetric monoidal category, and suppose we have two pairs of objects $(S, S')$ and $(A, A')$. An \emph{optic} $p : (S, S') \hto (A, A')$ is an element of the set
+  Given two pairs of objects of $\C$, say $(S, S')$ and $(A, A')$, an \emph{optic} $p : (S, S') \hto (A, A')$ is an element of the set
   \begin{align*}
@@
 Optics will always be written with a crossed arrow $\hto$, to distinguish them from morphisms of $\C$.
+
+\begin{remark}
+A common use of the coend relation is to introduce or cancel isomorphisms. Given $l : S \to M \otimes A$ and $r : M \otimes A \to S$, for any isomorphism $f : M \to N$ we have
+\begin{align*}
+\rep{l}{r} = \rep{(f^{-1} \otimes A)(f \otimes A)l}{r} = \rep{(f \otimes A)l}{r(f^{-1} \otimes A)}
+\end{align*}
+\end{remark}
 
@@
     &= \rep{(M \otimes \lambda^{-1}_A) l}{r (M\otimes  \lambda_{A'}} \\
-    &= \rep{(\lambda^{-1}_M \otimes  A) l}{r (\lambda_M \otimes A'} \\
-    &= \rep{l}{r (\lambda_M \otimes A') (\lambda^{-1}_M \otimes A')} \\
+    &= \rep{(\rho^{-1}_M \otimes  A) l}{r (\rho_M \otimes A'} \\
+    &= \rep{l}{r (\rho_M \otimes A') (\rho^{-1}_M \otimes A')} \\
     &= \rep{l}{r} \\
@@
   \end{align*}
-  In both cases we have used the naturality of $\lambda$ and the coend relations to move $\lambda^{-1}_M$ to the right-hand side, where it may be cancelled.
+  In both cases we have used the naturality of $\lambda$ followed by the coend relations to move $\lambda^{-1}_M$ to the right-hand side, where it may be cancelled with $\lambda_M$
 \end{proof}
@@
   \end{center}
-  These two diagrams are equivalen: We can use the naturality of the symmetry morphism to push $l_2$ and $r_2$ past the crossing to be next to $l_1$ and $r_1$ respectively.
+  These two diagrams are equivalent: We can use the naturality of the symmetry morphism to push $l_2$ and $r_2$ past the crossing to be next to $l_1$ and $r_1$ respectively.
 This creates two extra twists that can be cancelled in the center of the diagram (implicitly using the coend relation).
@@
 
-\todo{Is there a relationship between $\Optic_\otimes/(I, I)$ and $[2, \C]$?}
+%\todo{Is there a relationship between $\Optic_\otimes/(I, I)$ and $[2, \C]$?}
 
@@
 \begin{proposition}\label{prop:change-of-action-monoidal}
-  A monoidal functor $F : \C \to \D$ induces a functor $\Optic(F) : \Optic_\otimes \to \Optic_\D$.
+  A monoidal functor $F : \C \to \D$ induces a functor $\Optic(F) : \Optic_\C \to \Optic_\D$.
 \end{proposition}
@@
   \begin{align*}
-    \Optic(F)\rep{l}{r} := \rep{\phi^{-1}_{M,A} (Fl)}{(Fr) \phi_{M,A'}}
+    \Optic(F)(\rep{l}{r}) := \rep{\phi^{-1}_{M,A} (Fl)}{(Fr) \phi_{M,A'}}
   \end{align*}
   where $\phi_{M,A} : FM \otimes FA \to F(M \otimes A)$ is the structure map of the monoidal functor.
-  \todo{functoriality}
-  \todo{monoidality}
+  This preserves identities:
+  \begin{align*}
+  \Optic(F)(\id_{(S, S')}) 
+  &= \Optic(F)(\rep{\lambda^{-1}_S}{\lambda_{S'}}) \\
+  &= \rep{\phi^{-1}_{I,S} (F\lambda^{-1}_S)}{(F\lambda_{S'}) \phi_{I,S'}} \\
+  &= \rep{(\phi^{-1} \otimes S) \phi^{-1}_{I,S} (F\lambda^{-1}_S)}{(F\lambda_{S'}) \phi_{I,S'}(\phi \otimes S) } \\
+  &= \rep{(\phi^{-1} \otimes S) \phi^{-1}_{I,S} (F\lambda^{-1}_S)}{(F\lambda_{S'}) \phi_{I,S'}(\phi \otimes S) } \\
+  &= \rep{\lambda^{-1}_{FS}}{\lambda_{FS'}} \\
+  &= \id_{(FS, FS')}
+  \end{align*}
+  And given two optics $\rep{l}{r} : (S, S') \hto (A, A')$ and $\rep{l'}{r'} : (R, R') \hto (S, S')$ with residuals $M$ and $M'$, it preserves composition:
+\begin{align*}
+&\Optic(F)(\rep{l}{r} \circ \rep{l'}{r'})  \\
+&= \Optic(F)(\rep{(M' \otimes l)l'}{r'(M' \otimes r)}) \\
+&= \rep{\phi^{-1}_{M' \otimes M,A} F((M' \otimes l)l')}{F(r'(M' \otimes r)) \phi_{M' \otimes M,A'}} \\
+&= \rep{\phi^{-1}_{M' \otimes M,A} F(M' \otimes l)(Fl')}{(Fr') F(M' \otimes r) \phi_{M' \otimes M,A'}} \\
+&= \rep{(\phi^{-1}_{M', M} \otimes A)\phi^{-1}_{M' \otimes M,A} F(M' \otimes l)(Fl')}{(Fr') F(M' \otimes r) \phi_{M' \otimes M,A'}(\phi_{M', M} \otimes A)} \\
+&= \rep{(FM' \otimes \phi^{-1}_{M,A})\phi^{-1}_{M',M \otimes A}(F(M' \otimes l)) (Fl')}{(Fr') (F(M' \otimes r)) \phi_{M',M \otimes A'}  (FM' \otimes \phi_{M,A'})} \\
+&= \rep{(FM' \otimes \phi^{-1}_{M,A})(FM' \otimes Fl)\phi^{-1}_{M',S} (Fl')}{(Fr') \phi_{M',S'} (FM' \otimes Fr) (FM' \otimes \phi_{M,A'})} \\
+&= \rep{(FM' \otimes \phi^{-1}_{M,A} (Fl))(\phi^{-1}_{M',S} (Fl'))}{((Fr') \phi_{M',S'})(FM' \otimes (Fr) \phi_{M,A'})} \\
+&= \rep{\phi^{-1}_{M,A} (Fl)}{(Fr) \phi_{M,A'}} \circ \rep{\phi^{-1}_{M',S} (Fl')}{(Fr') \phi_{M',S'}} \\
+&= \Optic(F)(\rep{l}{r}) \circ \Optic(F)(\rep{l'}{r'}) 
+\end{align*}
+The critical move is adding the isomorphism $(\phi_{M', M} \otimes A)$ to both sides of the coend, so that the hexagon axiom for $F$ can be applied.
+
+The structure morphisms for monoidality are given by lifting the structure morphisms for $F$:
+\begin{align*}
+\phi_{(S, S'), (T, T')} &:= \iota(\phi_{S, T}, \phi_{S', T'}) &&: F(S, S') \otimes F(T, T') \hto F((S, S') \otimes (T, T')) \\
+\phi &:= \iota(\phi, \phi) &&: (I, I) \hto F(I, I)
+\end{align*}
+The axioms follow by lifting the axioms for $F$. More difficult is verifying naturality: \todo{naturality}
 \end{proof}
@@
 
-Note that because $\C_d$ is symmetric monoidal and has the same collection of objects as $\C$, the symmetric monoidal structure morphisms of $\C$ must be contained in $\C_d$.
+Note that because $\C_d$ is symmetric monoidal and has the same collection of objects as $\C$, the symmetric monoidal structure morphisms of $\C$ must be contained in $\C_d$ and so are dualisable.
 
@@
 
+\begin{remark}
+This definition of teleological category differs from the original one, in that the duality switches the order of the tensor product.
+We do this so that compact closed category are teleological, but the bookkeeping becomes more confusing.
+\end{remark}
+
 %\begin{example}
@@
 \begin{definition}
-  A \emph{teleological functor} $F : \C \to \D$ is a symmetric monoidal functor that restricts to a functor $F_d : \C_d \to \D_d$ on the dualisable subcategories, commutes with the duality and such that the counits are preserved:
+  A \emph{teleological functor} $F : \C \to \D$ is a symmetric monoidal functor that restricts to a functor $F_d : \C_d \to \D_d$ on the dualisable subcategories, commutes \todo{strictly?} with the duality and such that the counits are preserved:
   \[
    \begin{tikzcd}
-    F(X \otimes X^*) \ar[r, "\cong"]  \ar[d, "F\varepsilon_X", swap] & FX \otimes FX^* \ar[d, "\varepsilon_{FX}"] \\
-    FI \ar[r, "\cong", swap] & I
+    F(X \otimes X^*) \ar[r, "\phi_{X, X^*}"]  \ar[d, "F\varepsilon_X", swap] & FX \otimes FX^* \ar[d, "\varepsilon_{FX}"] \\
+    FI \ar[r, "\phi", swap] & I
   \end{tikzcd}
@@
 \begin{proof}
-  We must show that for a symmetric monoidal functor $F : \C \to \D$, the induced functor $F : \Optic_\otimes \to \Optic_\D$ is teleological.
+  We must show that for a symmetric monoidal functor $F : \C \to \D$, the induced functor $F : \Optic_\C \to \Optic_\D$ is teleological.
 
@@
 
-To establish the universal property of $\Optic_\otimes$, we will
+Our goal now is to establish the universal property of $\Optic_\otimes$. The following proposition gives that an optic decomposes in a canonical way:
 
@@
   \end{center}
-using naturality of the symmetry, and monoidality of the counit.
+using naturality of the symmetry and monoidality of the counit.
 \item Preservation of duals:
@@
 \end{align*}
-\item Monoidality: We have the isomorphism
+\item Monoidality: We have the isomorphism \[ \phi_{(S, S'),(T, T')} : K((S, S') \switched (T, T')) \to K(S, S') \otimes K(T, T')\] given by the composite
 \begin{align*}
@@
 &= F(S \otimes T) \otimes F(T' \otimes S')^* \\
-&\cong FS \otimes FT \otimes (FS')^* \otimes (FT')^* \\
-&\cong FS \otimes (FS')^* \otimes FT \otimes (FT')^* \\
+&\xrightarrow{\phi_{S, T} \otimes \phi_{T', S'}^*} FS \otimes FT \otimes (FS')^* \otimes (FT')^* \\
+&\xrightarrow{FS \otimes s \otimes (FT')^*} FS \otimes (FS')^* \otimes FT \otimes (FT')^* \\
 &= K(S, S') \otimes K(T, T')
@@
 by strictness of the monoidal unit.
-\todo{Show this is actually the morphism we want}
+This morphism is indeed equal to the composite $\varepsilon_{K(S, S')} \phi_{(S, S'), (S, S')^*}$, using extranaturality to commute the structure maps $\phi_{S, S'}$ of $F$ and the symmetry of $\T$ through $\varepsilon$.
+\todo{write details?}
 \end{itemize}
@@
     &= \repthree{l}{\phi A}{r} && \text{($r;l = \phi A$)}\\
-    &= \repthree{l (\phi A)}{\id_{MA}}{r} && \text{(coend relation)} \\
+    &= \repthree{l ; (\phi A)}{\id_{MA}}{r} && \text{(coend relation)} \\
     &= \repthree{l;r;l}{\id_{MA}}{r} && \text{($r;l = \phi A$ again)}\\
@@
   \end{align*}
-  Now suppose we are given a lens $(\fget, \fput)$, which in coend form is $\rep{[\id_S, \fget]}{\fput}$. Evaluating $\outside$ on this gives:
+  Now suppose we are given a lens $p$ that corresponds concretely to $(\fget, \fput)$, so $p = \rep{[\id_S, \fget]}{\fput}$. Evaluating $\outside$ on this gives:
   \begin{align*}
@@
   \end{alignat*}
-  So looking componentwise, $\Phi(\once(p))$ being equal to $\Phi(\twice(p))$ is exactly equivalent to the $\fput\fget$ and $\fput\fput$ laws holding.
+  So looking component-wise, $\Phi(\once(p))$ being equal to $\Phi(\twice(p))$ is exactly equivalent to the $\fput\fget$ and $\fput\fput$ laws holding.
 \end{proof}
@@
   Suppose $\C$ has pullbacks and that there is a morphism $x : 1 \to A$.
-If $\fget : S \to A$ and $\fput : S \times A \to S$ satisfy the concrete lens laws then there exists $C \in \C$ with $S \cong C \times A$.
+If $p : S \hto A$ satisfies the concrete lens laws then there exists $C \in \C$ and mutual inverses $l : S \to C \times A$ and $r : C \times A \to S$ so that $p = \rep{l}{r}$.
 \end{proposition}
@@
   \]
-  which commutes by the $\fput\fget$ law.
-Note that $ji = \id_C$ by the universal property of pullbacks.
-The claim is that $\fput (i \times A) : C \times A \to S$ and $[j,\fget] : S \to C \times A$ are mutual inverses.
-This is easily checked:
+  which commutes by the $\fput\fget$ law. Note that $ji = \id_C$ by the universal property of pullbacks.
+
+  Now take $l : [j,\fget] : S \to C \times A$  and $r : \fput (i \times A) : C \times A \to S$. That they are mutual inverses is easily checked:
   \begin{align*}
@@
 
-  Additionally, the commutative diagram
+  Finally, the commutative diagram
   \[
@@
 This characterisation of setters is maybe a little odd, in that we have ended up with a function of $\Set$s, rather than a description internal to $\C$.
-If we modify our definition of $\Setter$ slightly, we can get such an internal characterisation.
-
-Suppose $\C$ is cartesian closed and let $\Strong_\C$ be the category of \emph{strong functors}\cite{StrongFunctors} on $\C$.
+If we modify our definition of $\Setter$, we can get such an internal characterisation.
+Suppose $\C$ is cartesian closed and let $\Strong_\C$ be the category of \emph{strong functors} on $\C$.
+\todo{I define strong functor here because I also want to talk about strong monads later, should this definition wait for that?}
+
+\begin{definition}[\cite{StrongFunctors}]\label{def:strong-functor}
+  A \emph{(left) strong functor} is a functor $F : \C \to \C$ equipped with a natural transformation called the \emph{strength}:
+  \begin{align*}
+    \theta_{A,B} : A \otimes F B \to F(A \otimes B)
+  \end{align*}
+  such that the strength commutes with the unitor:
+  \[
+    \begin{tikzcd}
+      I \otimes F A \ar[r, "\theta_{1,A}"] \ar[d, "\cong" left]  & F(I \otimes A) \ar[d, "\cong" right] \\
+      F A \ar[r, equals] & F A
+    \end{tikzcd}
+  \]
+  and with associativity:
+  \[
+    \begin{tikzcd}
+      (A \otimes B) \otimes F C \ar[rr, "\theta_{A \otimes B, C}"] \ar[d, "\alpha_{A,B,FC}" left]  && F((A \otimes B) \otimes C) \ar[d, "F\alpha_{A,B,FC}" right] \\
+      A \otimes (B \otimes F C) \ar[r, "A \otimes \theta_{B,C}" below] & A \otimes F(B \otimes C) \ar[r, "\theta_{A, B\otimes C}" below] & F(A \otimes (B \otimes C))
+    \end{tikzcd}
+  \]
+  A \emph{strong natural transformation} $\tau : (F,\theta) \to (G,\theta')$ is a natural transformation that respects the strengths.
+There is an evident category $\Strong(\C)$ of strong endofunctors and strong natural transformations, and a forgetful functor $U : \Strong(\C) \to [\C, \C]$.
+%  \[
+%    \begin{tikzcd}
+%      A \otimes F B \ar[r, "\theta_{A,B}"] \ar[d, "A \otimes \tau_B" left]  & F(A \otimes B) \ar[d, "\tau_{A \otimes B}" right] \\
+%      A \otimes G B \ar[r, "\theta'_{A, B}"]& G(A \otimes B)
+%    \end{tikzcd}
+%  \]
+%
+\end{definition}
 Then, again, $\Strong_\C$ acts on $\C$ by evaluation.
 We leave it to the reader to verify there is a natural isomorphism \[\C(S, FA) \cong \Strong_\C(\homC(A, -) \times S, F),\] which we can use to describe optics for this action as elements of $\C(\homC(A, A'), \homC(S,S'))$.
+The use of strong functors here is due to the correspondence between tensorial strengths and ``$\C$-enrichments'' on a functor.
 \end{remark}
@@
 \subsection{Traversals}
-In this section we work in the case $\C = \Set$. \todo{define applicative/traversable functors}
+In this section we work in the case $\C = \Set$. \todo{explain the point of traversals}
+
+We begin by reviewing the defnitions of applicative and traversable functors \cite{AnInvestigationOfTheLawsOfTraversals}.
+
+\begin{definition}
+An \emph{applicative functor} $F : \C \to \C$ is a lax monoidal functor with a strength compatible with the monoidal structure, in the sense that
+\[
+\begin{tikzcd}[column sep = large]
+A \otimes FB \otimes FC \ar[r, "{\theta_{A, B} \otimes FC}"] \ar[d, swap, "{A \otimes \phi_{B, C}}"] & F(A \otimes B) \otimes FC \ar[d, "{\phi_{A \otimes B, C}}"] \\
+A \otimes F(B \otimes C) \ar[r, swap, "{\theta_{A, B \otimes C}}"] & F(A \otimes B \otimes C)
+\end{tikzcd}
+\]
+commutes.
+An \emph{applicative natural transformation} is one that is both monoidal and strong.
+Applicative functors and natural transformations form a monoidal category $\App$ under functor composition.
+\end{definition}
+
+\begin{definition}
+A \emph{traversable functor} is a functor $T : \C \to \C$ equipped with a distributive law $\delta_F : TF \to FT$ for $T$ over the action of $\App$ on $\C$ by evaluation.
+
+Explicitly, this means that the diagrams
+\[
+  \begin{tikzcd}
+    TF \ar[r, "\delta_F"] \ar[d, swap, "T\alpha"] & FT \ar[d, "T\alpha"] \\
+    TG \ar[r, swap, "\delta_G"] & GT
+  \end{tikzcd} \hspace{1cm}
+  \begin{tikzcd}
+    TFG \ar[dr, swap, "\delta_F G"] \ar[rr, "\delta_{FG}"] &  & FGT \\
+    & FTG \ar[ur, swap, "F \delta_G"] &
+  \end{tikzcd} \hspace{1cm}
+  \begin{tikzcd}
+    T\id_\C \ar[r, bend left, "\id_T"] \ar[r, bend right, swap, "\delta_{\id_\C}"] & \id_\C T
+  \end{tikzcd}
+\]
+in $[\C, \C]$ commute.
+\end{definition}
 
@@
 \end{align*}
-where $\homC(A', S')$ denotes the internal hom. If $\C$ is cartesian, this is of course isomorphic to the pair of maps discussed in the previous section.
+where $\homC(A', S')$ denotes the internal hom. If $\C$ is cartesian, this is of course isomorphic to the pair of maps discussed earlier.
 
@@
 \begin{proof}
+  Let $\overrightarrow{(-)} : \C(A \otimes B, C) \to \C(A, \homC(B, C))$ denote the homset bijection.
+
   We have an isomorphism:
@@
   \begin{align*}
-    \Phi(\repthree{l}{c}{r}) &= (\widetilde{(\tilde{r} \otimes A)c} \otimes A)l
-  \end{align*}
-  Now suppose we are given an optic $p$ with corresponding element of $\conc_\otimes(S, A)$ is $\funzip$. Then \[\outside(\rep{\funzip}{\ev_{A, S} }) = \ev_{A, S} \; \funzip,\] giving the first law.
+    \Phi(\repthree{l}{c}{r}) &= (\overrightarrow{(\overrightarrow{r} \otimes A)c} \otimes A)l
+  \end{align*}
+  Now suppose we are given an optic $p$ whose corresponding element of $\conc_\otimes(S, A)$ is $\funzip$. Then \[\outside(\rep{\funzip}{\ev_{A, S} }) = \ev_{A, S} \; \funzip,\] giving the first law.
 
@@
     &= \Phi(\repthree{\funzip}{\id_{\homC(A,S) \otimes A}}{\ev_{A, S} }) \\
-    &= (\widetilde{(\tilde{\ev_{A, S}} \otimes A)\id_{\homC(A,S) \otimes A}} \otimes A)\funzip \\
-    &= (\widetilde{(\id_{\homC(A, S)} \otimes A)} \otimes A)\funzip \\
+    &= (\overrightarrow{(\overrightarrow{\ev_{A, S}} \otimes A)\id_{\homC(A,S) \otimes A}} \otimes A)\funzip \\
+    &= (\overrightarrow{(\id_{\homC(A, S)} \otimes A)} \otimes A)\funzip \\
     &= (\coev_{\homC(A, S), A} \otimes A)\funzip \\
@@
     &= \Phi(\repthree{\funzip}{\funzip \; \ev_{A, S}}{\ev_{A, S} }) \\
-    &= (\widetilde{(\tilde{\ev_{A, S}} \otimes A)(\funzip \; \ev_{A, S})} \otimes A)\funzip \\
-    &= (\widetilde{(\funzip \; \ev_{A, S})} \otimes A)\funzip \\
+    &= (\overrightarrow{(\overrightarrow{\ev_{A, S}} \otimes A)(\funzip \; \ev_{A, S})} \otimes A)\funzip \\
+    &= (\overrightarrow{(\funzip \; \ev_{A, S})} \otimes A)\funzip \\
     &= ((\funzip \circ -) \otimes A)\funzip
   \end{align*}
-  \todo{Fix those overtildes}
-  So indeed the optic is lawful iff $\ev_{A, S} \; \funzip = \id_S$ and $(\coev_{\homC(A, S), A} \otimes A)\funzip = ((\funzip \circ -) \otimes A)\funzip$.
+  So indeed the optic is lawful iff the two concrete laws hold.
 \end{proof}
@@
 
-Polymorphic optics can be captured by the coend formalism as follows. Any action of a monoidal category $\M \times \C \to \C$ can be extended to act objectwise on a functor category:
+Polymorphic optics can be captured by the coend formalism as follows. Any action of a monoidal category $\M \times \C \to \C$ can be extended to act object-wise on a functor category:
 \begin{align*}
@@
 \end{align*}
-Functoriality follows from the requirement that $\theta$ commute with the unit and multiplication of $T$. \todo{Draw this out?}
-
-Our goal is to show that the assignment $A \mapsto A \otimes -$ extends to a functor $a : \C \to [\C_T, \C_T]$.
-A morphism $f : A \to B$ in $\C$ induces a natural transformation $A \otimes - \to B \otimes -$ with components $A \otimes X \to T(B \otimes X)$ given by composing $A \otimes X \to B \otimes X$ with the unit of the monad.
-Naturality is easy to check:
-\[\begin{tikzcd}
-A \otimes X \ar[r] \ar[d] & B \otimes X \ar[r] \ar[d] & T(B \otimes X) \ar[d] \\
-A \otimes TY \ar[r] \ar[d] & B \otimes TY \ar[r] \ar[d] & T(B \otimes TY) \ar[d] \\
-T(A \otimes Y) \ar[r] & T(B \otimes Y) \ar[r] & TT(B \otimes Y)
-\end{tikzcd}\]
-The upper left square commutes by functoriality of $\otimes$, lower left by naturality of the strength, the two right squares by naturality of the unit.
-
-Finally, this functor $a$ is monoidal, with the structure maps given by the associativity and unit maps of $\C$. \todo{this uses that the strength commutes with unitors and associativity}
+For details, see \cite[Theorem 4.2]{PremonoidalCategories}. Our goal is to show this extends to a monoidal functor $a : \C \to [\C_T, \C_T]$.
+
+A morphism $f : A \to B$ in $\C$ induces a natural transformation $A \otimes - \Rightarrow B \otimes -$ with components $A \otimes X \to T(B \otimes X)$ given by composing $A \otimes X \to B \otimes X$ with the unit of the monad.
+Naturality follows by the naturality of the strength and the unit of $T$.
+%Naturality is easy to check:
+%\[\begin{tikzcd}
+%A \otimes X \ar[r] \ar[d] & B \otimes X \ar[r] \ar[d] & T(B \otimes X) \ar[d] \\
+%A \otimes TY \ar[r] \ar[d] & B \otimes TY \ar[r] \ar[d] & T(B \otimes TY) \ar[d] \\
+%T(A \otimes Y) \ar[r] & T(B \otimes Y) \ar[r] & TT(B \otimes Y)
+%\end{tikzcd}\]
+%The upper left square commutes by functoriality of $\otimes$, lower left by naturality of the strength, the two right squares by naturality of the unit.
+
+Monoidality of $a$ is shown exactly by the commutative diagrams in the definition of strong functor, i.e. that the strength commutes with associator and left unitor of $\C$.
+
+\todo{I suspect there is a 1-to-1 correspondence between strengths on $T$ and actions of $\C$ on $\C_T$ by $A \otimes B$ on objects, is it worth proving this?}
 \end{proof}
@@
 
-\item \emph{Functor Optics} \todo{todo}
+%\item \emph{Functor Optics} \todo{todo}
 
@@
 Whether this is lawful or useful is not clear!
-
-\item \emph{Degenerate Optics} include the \mintinline{haskell}{Getter}s and \mintinline{haskell}{Review}s of the Haskell library, where an optic $(S, S') \hto (A, A')$ corresponds simply to a morphism $S \to A$ or $A' \to S'$ respectively.
-These do fit into the coend formalism, with a slight modification.
-
-If we have a monoidal category $\M$ that acts on two different categories $\C_1$ and $\C_2$, we may form the `optic' category:
-\begin{align*}
-  \Optic_\M((S, S'), (A, A')) := \int^{M \in \M} \C_1(S, MA) \times \C_2(MA', S')
-\end{align*}
-We lose, of course, the ability to talk about lawful optics.
-To encode \mintinline{haskell}{Getter}s or \mintinline{haskell}{Review}s, we then set $\C_2$ or $\C_1$ to be the codiscrete category $\C_\mathsf{codisc}$ with the same set of objects as $\C$, so that all homsets are the one element set.
-In this way we indeed get a category $\Getter$ that is isomorphic to $\C$.
-\begin{align*}
-\int^{M \in \M} \C(S, M \times A) \times \C_\mathsf{codisc}(M \times A', S')
-&\cong \int^{M \in \M} \C(S, M \times A) \\
-&\cong \C(S, 1 \times A) \\
-&\cong \C(S, A)
-\end{align*}
-This works for $\Review$ in the same way, putting $\C_\mathsf{codisc}$ on the left. The functor $\C \to \C_\mathsf{codisc}$ induces functors $\Lens \to \Getter$ and $\Prism \to \Review$.
-
-Finally, we encode $\Fold$s, which in $\Set$ are functions $S \to \mathrm{List}\,A$. The key is that the $\mathrm{List}$ functor is the terminal $\Traversable$ functor, so we have isomorphisms
-\begin{align*}
-&\int^{M \in \Traversable} \Set(S, MA) \times \Set_\mathsf{codisc}(MA', S') \\
-&\cong \int^{M \in \Traversable} \Set(S, MA) \\
-&\cong \Set(S, \mathrm{List}\,A)
-\end{align*}
-
-\todo{We actually haven't talked about profunctors yet, where should this go?} There is a corresponding notion of Tambara module for a profunctor between two different categories.
-A profunctor $P : \C^\op \times \C_\mathsf{codisc}$ essentially ignores its covariant argument; this explains the appearance of a \mintinline{haskell}{RightPhantom} typeclass or equivalent in many profunctor optic libraries.
 \end{itemize}
@@
 
-\todo{explain why this encoding is used}
+\todo{explain the benefits of this encoding}
 
@@
 \section{Mixed Optics}
-\todo{This hopefully will handle degenerate optics and indexed optics}
-
-%\subsection{Indexed Optics}
-%\todo{
-%  This possibly looks like
-%  \begin{align*}
-%    \int^{M \in \M} \C(S, M(IA)) \times \C(M A', S')
-%  \end{align*}
-%  with another monoidal action $I$. The $I$ would need to distribute over $M$ in some way. ``Coindexed'' optics seem to have
-%  \begin{align*}
-%    \int^{M \in \M} \C(S, J(MA)) \times \C(M A', S')
-%  \end{align*}
-%  which is why they pass information `in the other direction' but still transform covariantly.
-%}
+\todo{This hopefully will handle degenerate optics and indexed optics in a uniform way}
+
+\subsection{Lawful Mixed Optics}
+
+Suppose we have mixed optics
+
+\section{Examples Of Mixed Optics}
+
+\subsection{Degenerate Optics}
+
+Degenerate optics include the \mintinline{haskell}{Getter}s and \mintinline{haskell}{Review}s of the Haskell library, where an optic $(S, S') \hto (A, A')$ corresponds simply to a morphism $S \to A$ or $A' \to S'$ respectively.
+These do fit into the coend formalism, with a slight modification.
+
+If we have a monoidal category $\M$ that acts on two different categories $\C_1$ and $\C_2$, we may form the `optic' category:
+\begin{align*}
+  \Optic_\M((S, S'), (A, A')) := \int^{M \in \M} \C_1(S, MA) \times \C_2(MA', S')
+\end{align*}
+We lose, of course, the ability to talk about lawful optics.
+To encode \mintinline{haskell}{Getter}s or \mintinline{haskell}{Review}s, we then set $\C_2$ or $\C_1$ to be the codiscrete category $\C_\mathsf{codisc}$ with the same set of objects as $\C$, so that all homsets are the one element set.
+In this way we indeed get a category $\Getter$ that is isomorphic to $\C$.
+\begin{align*}
+\int^{M \in \M} \C(S, M \times A) \times \C_\mathsf{codisc}(M \times A', S') 
+&\cong \int^{M \in \M} \C(S, M \times A) \\
+&\cong \C(S, 1 \times A) \\
+&\cong \C(S, A)
+\end{align*}
+This works for $\Review$ in the same way, putting $\C_\mathsf{codisc}$ on the left. The functor $\C \to \C_\mathsf{codisc}$ induces functors $\Lens \to \Getter$ and $\Prism \to \Review$.
+
+Finally, we encode $\Fold$s, which in $\Set$ are functions $S \to \mathrm{List}\,A$. The key is that the $\mathrm{List}$ functor is the terminal $\Traversable$ \todo{ref}, so we have isomorphisms
+\begin{align*}
+&\int^{M \in \Traversable} \Set(S, MA) \times \Set_\mathsf{codisc}(MA', S') \\
+&\cong \int^{M \in \Traversable} \Set(S, MA) \\
+&\cong \Set(S, \mathrm{List}\,A)
+\end{align*}
+
+There is a corresponding notion of Tambara module for a profunctor between two different categories.
+A profunctor $P : \C^\op \times \C_\mathsf{codisc}$ essentially ignores its covariant argument; this explains the appearance of a \mintinline{haskell}{RightPhantom} typeclass or equivalent in many profunctor optic libraries.
+
+\subsection{Indexed Optics}
+
+\todo{Make sure I cite \cite{IndexedOpticsPost}}
+
+Suppose $\C$ is cartesian closed.
+
+\begin{proposition}
+The assignment $FX \mapsto (T\homC(I, F X))$ is a lax monoidal action of $\App$ on $\C$.
+\end{proposition}
+\begin{proof}
+\todo{todo}
+\end{proof}
+
+\begin{definition}
+A \emph{traversable functor indexed by $I$} is a functor $T : \C \to \C$ equipped with a distributive law $\delta_F : T(\homC(I, F-)) \to FT$ for $T$ between the $I$-indexed action of $\App$ on $\C$ and the action of $\App$ on $\C$ by evaluation.
+\end{definition}
+
+\begin{definition}
+The category of \emph{indexed traversable functors} $\IdxTraversable$ has as objects pairs $(T, I)$, where $I \in \C$ and $T : \C \to \C$ is a traversable functor indexed by $I$.
+A morphism $(T, I) \to (T', I')$ is a natural transformation $\alpha : T \to T'$ and morphism (note the direction!) $i : I' \to I$, such that $\alpha$ commutes with the distributive laws on both traversable functors, using $i$ to mediate between the index objects.
+\end{definition}
+
+\begin{proposition}
+$\IdxTraversable$ acts on $\C \times \C$ by $(T, I) \cdot (A, R) \mapsto (TA, \homC(I, R))$.
+\end{proposition}
+\begin{proof}
+\todo{todo}
+\end{proof}
+
+\subsection{Monotone Optics???}
 
@@
 \todo{Maybe some of the long equational manipulations could be done by commutative diagram, using a pair of dashed lines to signal the start and end value?}
+
+\todo{Somewhere spell out the connection between $\Pastro_\M E_A$ and $\Optic(-, A)$.}
+
+\todo{Talk about how the four `parameters' to $\Optic$ is not the same thing as the four parameters to Haskell lenses}
+
+\todo{Make sure I'm not using any $\Set$-only results too generally in the traversal section}
+
+\todo{Consistently use $\Rightarrow$ for natural transformations everywhere?}
+
+\todo{homset vs hom-set?}
+
+\todo{Move some proofs to appendix?}
 

### 2018-07-05 paper.tex
Some prose and lints

@@
 
-\newif\ifhideproofs
-% \hideproofstrue %uncomment to hide proofs
-\ifhideproofs
-\usepackage{environ}
-\NewEnviron{hide}{}
-\let\proof\hide
-\let\endproof\endhide
-\fi
+% \newif\ifhideproofs
+% % \hideproofstrue %uncomment to hide proofs
+% \ifhideproofs
+% \usepackage{environ}
+% \NewEnviron{hide}{}
+% \let\proof\hide
+% \let\endproof\endhide
+% \fi
 
@@
 
-The widely used Haskell \lenslib{} library contains implementations of all these optic variants: see \cite{LensLibrary}.
+The widely used Haskell \lenslib{} library contains implementations of all these optic variants: see~\cite{LensLibrary}.
 There, optics are written in a form known as the \emph{profunctor encoding}, which at first glance is completely different to that given in Section~\ref{sec:optics}.
@@
 
-\todo{Indexed optics?}
-
-More recently, concrete lenses have found use in compositional game theory \cite{CompositionalGameTheory}.
+More recently, concrete lenses have found use in compositional game theory~\cite{CompositionalGameTheory}.
 The $\fget$ function is thought of as mapping observations on the state of play to choices of what move to make.
@@
 \end{align*}
+\qed
 \end{theorem}
 
-\todo{more?}
-
 \section{Optics}\label{sec:optics}
@@
 We begin by defining the category of optics in a symmetric monoidal category $\C$.
-This category was first defined in \cite[Section 6]{Doubles} as the `double' of a monoidal category.
+This category was first defined in~\cite[Section 6]{Doubles} as the `double' of a monoidal category.
 There it was used for an entirely different purpose---to investigate the relationship between Tambara modules and the `center' of a monoidal category.
@@
 
-Because this coend takes place in $\Set$, we can use Lemma \ref{lemma:calculate-coend} to describe $\Optic_\otimes((S, S'), (A, A'))$ explicitly.
+Because this coend takes place in $\Set$, we can use Lemma~\ref{lemma:calculate-coend} to describe $\Optic_\otimes((S, S'), (A, A'))$ explicitly.
 It is the set of pairs $(l, r)$, where $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, quotiented by the relation
@@
     &= \rep{\lambda^{-1}_A}{\lambda_{A'}} \circ \rep{l}{r} \\
-    &= \rep{(M \otimes \lambda^{-1}_A) l}{r (M\otimes  \lambda_{A'}} \\
-    &= \rep{(\rho^{-1}_M \otimes  A) l}{r (\rho_M \otimes A'} \\
+    &= \rep{(M \otimes \lambda^{-1}_A) l}{r (M \otimes  \lambda_{A'})} \\
+    &= \rep{(\rho^{-1}_M \otimes  A) l}{r (\rho_M \otimes A')} \\
     &= \rep{l}{r (\rho_M \otimes A') (\rho^{-1}_M \otimes A')} \\
@@
 \begin{remark}
-  Note that the hom-sets of $\Optic_\otimes$ are given by a coend indexed by a possibly large category, so their existence is not guaranteed by the cocompleteness of $\Set$.
+  Note that the homsets of $\Optic_\otimes$ are given by a coend indexed by a possibly large category, so their existence is not guaranteed by the cocompleteness of $\Set$.
 We should be careful to only discuss $\Optic$ categories where we know that the coends exist by some other means, e.g., by exhibiting an isomorphism with some other set.
@@
     &= \rep{\lambda^{-1}_B f'}{g' \lambda_{B'}} \circ \rep{\lambda^{-1}_A f}{g \lambda_{A'}} \\
-    &= \rep{(I\otimes (\lambda^{-1}_B f'))\lambda^{-1}_A f}{g \lambda_{A'} (I\otimes (g' \lambda_{B'})} && \text{(By definition of $\circ$)}\\
-    &= \rep{(I \otimes \lambda^{-1}_B) (I \otimes f')\lambda^{-1}_A f}{g \lambda_{A'} (I \otimes g')(I\otimes \lambda_{B'}} && \text{(Functoriality of $I \otimes -$)}\\
-    &= \rep{(I\otimes \lambda^{-1}_B) \lambda^{-1}_B f' f}{g g' \lambda_{B'} (I\otimes \lambda_{B'}} && \text{(Naturality of $\lambda$)}\\
-    &= \rep{(\lambda^{-1}_I \otimes B) \lambda^{-1}_B f' f}{g g' \lambda_{B'} (\lambda_I \otimes B'} && \text{(Unitality of action)} \\
+    &= \rep{(I\otimes (\lambda^{-1}_B f'))\lambda^{-1}_A f}{g \lambda_{A'} (I\otimes (g' \lambda_{B'}))} && \text{(By definition of $\circ$)}\\
+    &= \rep{(I \otimes \lambda^{-1}_B) (I \otimes f')\lambda^{-1}_A f}{g \lambda_{A'} (I \otimes g')(I\otimes \lambda_{B'})} && \text{(Functoriality of $I \otimes -$)}\\
+    &= \rep{(I\otimes \lambda^{-1}_B) \lambda^{-1}_B f' f}{g g' \lambda_{B'} (I\otimes \lambda_{B'})} && \text{(Naturality of $\lambda$)}\\
+    &= \rep{(\lambda^{-1}_I \otimes B) \lambda^{-1}_B f' f}{g g' \lambda_{B'} (\lambda_I \otimes B')} && \text{(Unitality of action)} \\
     &= \rep{\lambda^{-1}_B f' f}{g g' \lambda_{B'} (\lambda_I \otimes B') (\lambda^{-1}_I \otimes B')} && \text{(Coend relation)}  \\
@@
   \begin{align*}
-    \left( (S, S') \switched (T, T') \right)^*
-    &= \left( S \otimes T, T' \otimes S' \right)^* \\
-    &= \left(T' \otimes S', S \otimes T  \right) \\
+    {\left( (S, S') \switched (T, T') \right)}^*
+    &= {\left( S \otimes T, T' \otimes S' \right)}^* \\
+    &= {\left(T' \otimes S', S \otimes T  \right)} \\
     &= (T', T) \switched (S', S) \\
-    &= (T, T')^* \switched (S, S')^*
+    &= {(T, T')}^* \switched {(S, S')}^*
   \end{align*}
@@
   \begin{align*}
-    \rep{l}{r} = ((A, I) \switched \varepsilon_{(M, I)} \switched (I, A'))(j(s_{M,A}l) \switched j(rs_{A',M})^*)
+    \rep{l}{r} = ((A, I) \switched \varepsilon_{(M, I)} \switched (I, A'))(j(s_{M,A}l) \switched j{(rs_{A',M})}^*)
   \end{align*}
@@
 
-\begin{theorem}
-  \label{optic-is-free-teleological-cat}
+\begin{theorem}\label{optic-is-free-teleological-cat}
   Suppose $\C$ is a strict symmetric monoidal category and $\T$ is a teleological category.
@@
   We begin by constructing $K$.
-Note that any $(S, S')$ in $\Optic_\otimes$ can be written as $j(S) \switched j(S')^*$, so on objects define $K(S, S') = FS \otimes (FS')^*$.
+Note that any $(S, S')$ in $\Optic_\otimes$ can be written as $j(S) \switched {j(S')}^*$, so on objects define $K(S, S') = FS \otimes {(FS')}^*$.
 Suppose $\rep{l}{r} : (S, S') \hto (A, A')$ is an optic.
@@
   \begin{align*}
-    \rep{l}{r} = ((A, I) \switched \varepsilon_{(M, I)} \switched (I, A'))(j(s_{M,A}l) \switched j(rs_{A', M})^*)
+    \rep{l}{r} = ((A, I) \switched \varepsilon_{(M, I)} \switched (I, A'))(j(s_{M,A}l) \switched {j(rs_{A', M})}^*)
   \end{align*}
@@
   \begin{align*}
-    K\rep{l}{r} = (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F(s_{M,A}l) \otimes (F(rs_{A', M}))^* )
+    K\rep{l}{r} = (FA \otimes \varepsilon_{FM} \otimes {(FA')}^*)(F(s_{M,A}l) \otimes {(F(rs_{A', M}))}^* )
   \end{align*}
@@
 \begin{align*}
-K((S, S')^*) 
+K({(S, S')}^*)
 = K(S', S)
-= FS' \otimes (FS)^*
-\cong (FS \otimes (FS')^*)^*
-= (K(S, S'))^*
+= FS' \otimes {(FS)}^*
+\cong {(FS \otimes {(FS')}^*)}^*
+= {(K(S, S'))}^*
 \end{align*}
@@
 &= K(S \otimes T, T' \otimes S) \\
-&= F(S \otimes T) \otimes F(T' \otimes S')^* \\
-&\xrightarrow{\phi_{S, T} \otimes \phi_{T', S'}^*} FS \otimes FT \otimes (FS')^* \otimes (FT')^* \\
-&\xrightarrow{FS \otimes s \otimes (FT')^*} FS \otimes (FS')^* \otimes FT \otimes (FT')^* \\
+&= F(S \otimes T) \otimes {F(T' \otimes S')}^* \\
+&\xrightarrow{\phi_{S, T} \otimes \phi_{T', S'}^*} FS \otimes FT \otimes {(FS')}^* \otimes {(FT')}^* \\
+&\xrightarrow{FS \otimes s \otimes (FT')^*} FS \otimes {(FS')}^* \otimes FT \otimes {(FT')}^* \\
 &= K(S, S') \otimes K(T, T')
@@
 K(I, I)
-&= FI \otimes (FI)^* \\
+&= FI \otimes {(FI)}^* \\
 &\cong I \otimes I^* \\
@@
     &= K(\rep{\lambda_A^{-1} f}{g \lambda_{A'}}) \\
-    &= (FA \otimes \varepsilon_{FI} \otimes (FA')^*)(F(s_{I,A}\lambda_A^{-1} f) \otimes (F(g \lambda_{A'}s_{A', I}))^* ) \\
-    &= (FA \otimes (FA')^*)(Ff \otimes (Fg)^* ) \\
-    &= Ff \otimes (Fg)^*
+    &= (FA \otimes \varepsilon_{FI} \otimes {(FA')}^*)(F(s_{I,A}\lambda_A^{-1} f) \otimes (F(g \lambda_{A'}s_{A', I}))^* ) \\
+    &= (FA \otimes {(FA')}^*)(Ff \otimes {(Fg)}^* ) \\
+    &= Ff \otimes {(Fg)}^*
 \end{align*}
@@
 by strictness of the monoidal unit.
-This morphism is indeed equal to the composite $\varepsilon_{K(S, S')} \phi_{(S, S'), (S, S')^*}$, using extranaturality to commute the structure maps $\phi_{S, S'}$ of $F$ and the symmetry of $\T$ through $\varepsilon$.
+This morphism is indeed equal to the composite $\varepsilon_{K(S, S')} \phi_{(S, S'), {(S, S')}^*}$, using extranaturality to commute the structure maps $\phi_{S, S'}$ of $F$ and the symmetry of $\T$ through $\varepsilon$.
 \todo{write details?}
@@
 
-The following are analogous to Propositions~\ref{prop-optic-is-cat} and \ref{prop:change-of-action-monoidal}.
+The following are analogous to Propositions~\ref{prop-optic-is-cat} and~\ref{prop:change-of-action-monoidal}.
 
@@
 
-      %       \begin{proposition}
-      %       \todo{Entrywise Coproduct}
-      %       \end{proposition}
-      %
-      %       \begin{remark}
-      %       The motivating example here is that of coproducts distributing over the tensor product.
-      %       \end{remark}
-
 \section{Lawful Optics}\label{sec:lawful-optics}
-\todo{intro}
-
-In this section I use $;$ to denote composition of $\C$ in diagrammatic order.
-The reason for this is that the coend relation can be applied simply by shifting the position of $\mid$ in a representative:
+Typically we want our optics to obey certain laws.
+The constant complement perspective suggests declaring an optic $\rep{l}{r}$ to be lawful if $l$ and $r$ are mutual inverses.
+There are a couple of issues with this definition.
+Firstly, it is not invariant under the coend relation, so the condition holding for one representative is no guarantee that it holds for any other.
+Still, we might say that an optic is lawful if it has \emph{some} representative that consists of mutual inverses.
+In our primary example of an optic variant, lenses in $\Set$, this does indeed correspond to the concrete lens laws.
+However, this fact relies on some extra structure possessed by $\Set$, the existence of pullbacks, and that all objects other than the empty set have a global element.
+
+In this section we make a different definition of lawful that at first seems strange, but which in the case of lenses corresponds \emph{exactly} to the three concrete lens laws with no additional assumptions on $\C$ required.
+As further justification for this definition, in Section~\ref{sec:profunctor-optics} we will see an interpretation of (unlawful) optics as maps between certain comonoid objects.
+Lawfulness corresponds exactly to this map being a comonoid homomorphism.
+
+\begin{remark}
+We use $;$ to denote composition of $\C$ in diagrammatic order. The reason for this is that the coend relation can be applied simply by shifting the position of $\mid$ in a representative:
 \begin{align*}
@@
 
-\begin{remark}
-  In this section we will focus only on optics of the form $p : (S,S) \hto (A, A)$.
-For brevity we will write $\Optic_\M((S, S), (A, A))$ as $\Optic_\M(S, A)$ and $p : (S, S) \hto (A, A)$ as $p : S \hto A$.
+  Also, in this section we focus only on optics of the form $p : (S,S) \hto (A, A)$.
+For brevity we will abbreviate $\Optic_\M((S, S), (A, A))$ as $\Optic_\M(S, A)$ and $p : (S, S) \hto (A, A)$ as $p : S \hto A$.
 \end{remark}
@@
 We will see that in all the common examples of optics, this specialises to the expected laws for that variant of optic.
-
-\begin{remark}
-The above definition of lawful does not match neatly with the constant complement idea, which might instead require that $r;l = \id_{MA}$ for some $M$.
-I argue that $\once(p) = \twice(p)$ is the correct condition for a few reasons.
-
-The main reason is that it corresponds precisely to the concrete lens laws with no additional requirements, whereas finding a complement for a lens requires further conditions on the category $\C$.
-
-Secondly, even if $r;l = \id_{MA}$ holds for a particular representative $\langle l, r \rangle$, the same is not likely to be true for a different representative.
-
-Finally, we will later see an interpretation of optics as morphisms between certain comonoid objects. Lawfulness corresponds exactly to a morphism being a comonoid morphism.
-\end{remark}
 
@@
 
-  We can now inductively apply the above argument to the shorter chain \[l'r' = u_1^2 \leftrightsquigarrow \dots \leftrightsquigarrow u_n^2 \leftrightsquigarrow (\psi A)^2 = \psi^2 A,\] obtained by squaring each morphism in the original chain, until we are left with a representative $\rep{l^*}{r^*}$ such that $r^*;l^* = \psi^N_A$, for some $N>0$.
+  We can now inductively apply the above argument to the shorter chain \[l'r' = u_1^2 \leftrightsquigarrow \dots \leftrightsquigarrow u_n^2 \leftrightsquigarrow {(\psi A)}^2 = \psi^2 A,\] obtained by squaring each morphism in the original chain, until we are left with a representative $\rep{l^*}{r^*}$ such that $r^*;l^* = \psi^N_A$, for some $N>0$.
 This pair $\rep{l^*}{r^*}$ is the required representative.
@@
 
-The above argument has a similar form to those that appear in \cite{OnTheTrace}, which considered (among other things) coends of the form $\int^{c \in \C} \C(c, Fc)$ for an endofunctor $F : \C \to \C$.
+The above argument has a similar form to those that appear in~\cite{OnTheTrace}, which considered (among other things) coends of the form $\int^{c \in \C} \C(c, Fc)$ for an endofunctor $F : \C \to \C$.
 
@@
 Once we choose a particular monoidal action $\M \to [\C, \C]$, we find an isomorphism between the set of optics $(S, S') \hto (A, A')$ and a set $\conc((S, S'), (A, A'))$ that is easier to describe.
-We follow \cite{ProfunctorOptics} (and others) in calling elements of $\conc$ \emph{concrete optics}.
+We follow~\cite{ProfunctorOptics} (and others) in calling elements of $\conc$ \emph{concrete optics}.
 There is no canonical choice for this set; our primary goal is to find a way to eliminate the coend so that we no longer have to deal with equivalence classes of morphisms.
@@
     &&&\pi_2 [\id_S, \fget]\fput (\pi_1 [\id_S, \fget] \times A), \\
-    &&& \fput (\pi_1 [\id_S, \fget]\fput (\pi_1 [\id_S, \fget] \times A) \times A)) \quad) \\
+    &&& \fput (\pi_1 [\id_S, \fget]\fput (\pi_1 [\id_S, \fget] \times A) \times A) \quad) \\
     %
@@
 
-\begin{proposition}[{Generalisation of \cite[Corollary 13]{AlgebrasAndUpdateStrategies}}]
+\begin{proposition}[{Generalisation of~\cite[Corollary 13]{AlgebrasAndUpdateStrategies}}]
   Suppose $\C$ has pullbacks and that there is a morphism $x : 1 \to A$.
@@
 \begin{remark}
-Much of the work on bidirectional transformations \cite{CombinatorsForBidirectionalTreeTransformations} considers lenses that are only `well-behaved', not `very well-behaved': they obey the $\fput\fget$ and $\fget\fput$ laws but not the $\fput\fput$ law.
+Much of the work on bidirectional transformations~\cite{CombinatorsForBidirectionalTreeTransformations} considers lenses that are only `well-behaved', not `very well-behaved': they obey the $\fput\fget$ and $\fget\fput$ laws but not the $\fput\fput$ law.
 
@@
 
-We begin by reviewing the defnitions of applicative and traversable functors \cite{AnInvestigationOfTheLawsOfTraversals}.
+We begin by reviewing the defnitions of applicative and traversable functors~\cite{AnInvestigationOfTheLawsOfTraversals}.
 
@@
 \begin{lemma}
-  For any objects $A, B \in \Set$ and traversable functor $F$, \[\Set(FA, B) \cong \Traversable(F, \Sigma_n (-)^n \times \Set(A^n,B))\]
+  For any objects $A, B \in \Set$ and traversable functor $F$, \[\Set(FA, B) \cong \Traversable(F, \Sigma_n {(-)}^n \times \Set(A^n,B))\]
 naturally in $B$ and $F$.
-In other words, the functor \[(B \mapsto \Sigma_n (-)^n \times \Set(A^n,B)) : \Set \to \Traversable\] is right adjoint to the evaluation-at-$A$ functor $-A : \Traversable \to \Set$.
+In other words, the functor \[(B \mapsto \Sigma_n {(-)}^n \times \Set(A^n,B)) : \Set \to \Traversable\] is right adjoint to the evaluation-at-$A$ functor $-A : \Traversable \to \Set$.
 \end{lemma}
@@
 \Optic_\Traversable((S, S'), (A, A')) &= \int^{F \in \Traversable} \Set(S, F A) \times \Set(F A', S') \\
-&\cong \int^{F \in \Traversable} \Set(S, F A) \times \Traversable(F, \Sigma_n (-)^n \times \Set(A'^n,S')) \\
+&\cong \int^{F \in \Traversable} \Set(S, F A) \times \Traversable(F, \Sigma_n {(-)}^n \times \Set(A'^n,S')) \\
 &\cong \Set(S, \Sigma_n A^n \times \Set(A'^n,S'))
@@
 
+\subsection{Polymorphic Optics}
+Haskell's optics allow \emph{polymorphic updates}, where the type of the codomain of the lens may be changed by an update, causing a corresponding change in the type of the domain.
+As an example, we permitted to use a lens into the \mintinline{haskell}{first} entry of a tuple in the following way:
+\begin{minted}{haskell}
+set first (1, 5) "hello" == ("hello", 5)
+\end{minted}
+This has changed the type from \mintinline{haskell}{(Int, Int)} to \mintinline{haskell}{(String, Int)}.
+
+Polymorphic optics can be captured by the coend formalism as follows. Any action of a monoidal category $\M \times \C \to \C$ can be extended to act object-wise on a functor category:
+\begin{align*}
+  \M \times [\D, \C] &\to [\D, \C] \\
+  (M, F) &\mapsto  M \cdot (F-)
+\end{align*}
+
+So in the above example, we have the product $\times$ acting pointwise on the functor category $\Set \to \Set$.
+Our example \mintinline{haskell}{first} is then an optic $F \hto G$, where $F = (-) \times \mintinline{haskell}{Int}$ and $G$ is the identity functor.
+
+Given such a polymorphic optic in $[\D, \C]$, we can always `monomorphise' to obtain an ordinary optic in $\C$.
+\begin{proposition}
+  There is a functor
+  \begin{align*}
+    \mathsf{mono} : \D \times \D^\op \times \Optic_{[\D, \C]} \to \Optic_\otimes
+  \end{align*}
+  that sends an object $(D, D') \in \D \times \D^\op$ and optic $\rep{l}{r} : (F, F') \hto (G, G')$ in $\Optic_{[\D, \C]}$ to the optic $\rep{l_D}{r_{D'}} : (FD, F'D') \hto (GD, G'D')$ in $\Optic_\M$.
+For fixed $(D, D) \in \D \times \D^\op$, this functor preserves lawfulness.
+\end{proposition}
+\begin{proof}
+  On an object $(D, D') \in \D \times \D^\op$, this is essentially the same as Proposition~\ref{prop:change-of-action} but with different functors on each side of the lens: the evaluation-at-$D$ functor $[\D, \C] \to \C$ on the left and evaluation-at-$D'$ on the right.
+
+  Given a morphism $(f, g) : (D_1, D'_1) \to (D_2, D'_2) \in \D \times \D^\op$ and an object $(F, F') \in \Optic_{[\D, \C]}$, there is an induced lens $\iota(Ff, F'g) : (FD_1, F'D'_1) \hto (FD_2, F'D'_2)$.
+Bifunctoriality of $\mathsf{mono}$ is ensured by the naturality of each $l$ and $r$ in the morphisms of $\Optic_{[\D, \C]}$.
+\end{proof}
+
+\begin{remark}\label{remark:four-parameters}
+\todo{Talk about how the four `parameters' to $\Optic$ is not the same thing as the four parameters to Haskell lenses}
+\end{remark}
+
+\todo{What about the pointwise tensor of an entire functor?}
+
 \subsection{Linear Lenses}\label{sec:linear-lenses}
@@
 \begin{proof}
-  Let $\overrightarrow{(-)} : \C(A \otimes B, C) \to \C(A, \homC(B, C))$ denote the homset bijection.
+  Let $\overrightarrow{(-)} : \C(A \otimes B, C) \to \C(A, \homC(B, C)) : \overleftarrow{(-)}$ denote the homset bijection, so $\coev_{A, B} = \overrightarrow{\id_{A \otimes B}}$ and $\ev_{A, B} = \overleftarrow{\id_{\homC(A, B)}}$.
 
@@
 \end{proof}
-
-\subsection{Polymorphic Optics}
-Haskell's optics \todo{has this appeared in DB theory?} allow \emph{polymorphic updates}, where the type of the codomain of the lens can be changed by an update, causing a corresponding change in the type of the domain.
-As an example, we permitted to use a lens into the \mintinline{haskell}{first} entry of a tuple in the following way:
-\begin{minted}{haskell}
-set first (1, 5) "hello" == ("hello", 5)
-\end{minted}
-Note that the type has been changed from \mintinline{haskell}{(Int, Int)} to \mintinline{haskell}{(String, Int)}.
-
-Polymorphic optics can be captured by the coend formalism as follows. Any action of a monoidal category $\M \times \C \to \C$ can be extended to act object-wise on a functor category:
-\begin{align*}
-  \M \times [\D, \C] &\to [\D, \C] \\
-  (M, F) &\mapsto  M \cdot (F-)
-\end{align*}
-
-So in the above example, we have the product $\times$ acting pointwise on the functor category $\Set \to \Set$.
-Our example \mintinline{haskell}{first} is then an optic $F \hto G$, where $F = (-) \times \mintinline{haskell}{Int}$ and $G$ is the identity functor.
-
-Given such a polymorphic optic in $[\D, \C]$, we can always `monomorphise' to obtain an ordinary optic in $\C$.
-\begin{proposition}
-  There is a functor
-  \begin{align*}
-    \mathsf{mono} : \D \times \D^\op \times \Optic_{[\D, \C]} \to \Optic_\otimes
-  \end{align*}
-  that sends an object $(D, D') \in \D \times \D^\op$ and optic $\rep{l}{r} : (F, F') \hto (G, G')$ in $\Optic_{[\D, \C]}$ to the optic $\rep{l_D}{r_{D'}} : (FD, F'D') \hto (GD, G'D')$ in $\Optic_\M$.
-For fixed $(D, D) \in \D \times \D^\op$, this functor preserves lawfulness.
-\end{proposition}
-\begin{proof}
-  On an object $(D, D') \in \D \times \D^\op$, this is essentially the same as Proposition~\ref{prop:change-of-action} but with different functors on each side of the lens: the evaluation-at-$D$ functor $[\D, \C] \to \C$ on the left and evaluation-at-$D'$ on the right.
-
-  Given a morphism $(f, g) : (D_1, D'_1) \to (D_2, D'_2) \in \D \times \D^\op$ and an object $(F, F') \in \Optic_{[\D, \C]}$, there is an induced lens $\iota(Ff, F'g) : (FD_1, F'D'_1) \hto (FD_2, F'D'_2)$.
-Bifunctoriality of $\mathsf{mono}$ is ensured by the naturality of each $l$ and $r$ in the morphisms of $\Optic_{[\D, \C]}$.
-\end{proof}
-
-\todo{What about the pointwise tensor of an entire functor?}
 
@@
 \end{align*}
-For details, see \cite[Theorem 4.2]{PremonoidalCategories}. Our goal is to show this extends to a monoidal functor $a : \C \to [\C_T, \C_T]$.
+For details, see~\cite[Theorem 4.2]{PremonoidalCategories}. Our goal is to show this extends to a monoidal functor $a : \C \to [\C_T, \C_T]$.
 
@@
 
-Monoidality of $a$ is shown exactly by the commutative diagrams in the definition of strong functor, i.e. that the strength commutes with associator and left unitor of $\C$.
+Monoidality of $a$ is shown exactly by the commutative diagrams in the definition of strong functor, i.e.\ that the strength commutes with associator and left unitor of $\C$.
 
@@
     \mu_S T(\ev_{A, TS}) \; \munzip &= \eta_S \\
-    T(\eta_{\homC(A, TS) \otimes A)}\coev_{\homC(A, TS), A} \otimes A)\munzip &= T((\munzip \circ_T -) \otimes A)\munzip 
+    T(\eta_{\homC(A, TS) \otimes A}\coev_{\homC(A, TS), A} \otimes A)\munzip &= T((\munzip \circ_T -) \otimes A)\munzip
   \end{align*}
@@
 \begin{proof}
-This is exactly analogous to Proposition \ref{prop:concrete-linear-lawful} for linear lenses, with the unit and multiplication of the monad inserted in the appropriate places.
+This is exactly analogous to Proposition~\ref{prop:concrete-linear-lawful} for linear lenses, with the unit and multiplication of the monad inserted in the appropriate places.
 %\begin{align*}
@@
 It is hard to get intuition for the meaning of the laws.
-The $\fget\fput$ law here appears easier to satisfy than the $\mathsf{MGetPut_0}$ law of \cite{ReflectionsOnMonadicLenses}, as $\mput$ is given access to the original state.
+The $\fget\fput$ law here appears easier to satisfy than the $\mathsf{MGetPut_0}$ law of~\cite{ReflectionsOnMonadicLenses}, as $\mput$ is given access to the original state.
 On the other hand, our $\fput\fget$ law seems difficult to satisfy: it must hold no matter what auxiliary state is provided.
@@
 
+\subsection{Degenerate Optics}
+
+The \mintinline{haskell}{Getter}s and \mintinline{haskell}{Review}s of the Haskell library, where an optic $(S, S') \hto (A, A')$ corresponds simply to a morphism $S \to A$ or $A' \to S'$ respectively.
+These do fit into the coend formalism, with a slight modification.
+
+If we have a monoidal category $\M$ that acts on two different categories $\C_1$ and $\C_2$, we may form the `optic' category:
+\begin{align*}
+  \Optic_\M((S, S'), (A, A')) := \int^{M \in \M} \C_1(S, MA) \times \C_2(MA', S')
+\end{align*}
+We lose, of course, the ability to talk about lawful optics.
+To encode \mintinline{haskell}{Getter}s or \mintinline{haskell}{Review}s, we then set $\C_2$ or $\C_1$ to be the codiscrete category $\C_\mathsf{codisc}$ with the same set of objects as $\C$, so that all homsets are the one element set.
+In this way we indeed get a category $\Getter$ that is isomorphic to $\C$.
+\begin{align*}
+\int^{M \in \M} \C(S, M \times A) \times \C_\mathsf{codisc}(M \times A', S')
+&\cong \int^{M \in \M} \C(S, M \times A) \\
+&\cong \C(S, 1 \times A) \\
+&\cong \C(S, A)
+\end{align*}
+This works for $\Review$ in the same way, putting $\C_\mathsf{codisc}$ on the left. The functor $\C \to \C_\mathsf{codisc}$ induces functors $\Lens \to \Getter$ and $\Prism \to \Review$.
+
+Finally, we encode $\Fold$s, which in $\Set$ are functions $S \to \mathrm{List}\,A$. The key is that the $\mathrm{List}$ functor is the terminal $\Traversable$ \todo{ref}, so we have isomorphisms
+\begin{align*}
+&\int^{M \in \Traversable} \Set(S, MA) \times \Set_\mathsf{codisc}(MA', S') \\
+&\cong \int^{M \in \Traversable} \Set(S, MA) \\
+&\cong \Set(S, \mathrm{List}\,A)
+\end{align*}
+
+There is a corresponding notion of Tambara module for a profunctor between two different categories.
+A profunctor $P : \C^\op \times \C_\mathsf{codisc}$ essentially ignores its covariant argument; this explains the appearance of a \mintinline{haskell}{RightPhantom} typeclass or equivalent in many profunctor optic libraries.
+
 \subsection{Further Examples}
@@
 \begin{itemize}
-\item \emph{``Achromatic'' Lenses} \cite[Section 5.2]{ProfunctorOpticsThesis} are lenses that also admit an operation $\fcreate : A \to S$.
+\item \emph{``Achromatic'' Lenses}~\cite[Section 5.2]{ProfunctorOpticsThesis} are lenses that also admit an operation $\fcreate : A \to S$.
 These are optics for the action of $\C$ on itself by $M \cdot A = (M \sqcup 1) \times A$, or equivalently, of the category of pointed objects of $\C$ on $\C$ by cartesian product.
@@
 %\end{align*}
-\item \emph{Affine Traversals} \cite{AffineTraversalPost} allow access to a target that may or may not be present.
+\item \emph{Affine Traversals}~\cite{AffineTraversalPost} allow access to a target that may or may not be present.
 Suppose $\C$ is cartesian closed and has binary coproducts.
@@
 
-\item \todo{This is speculative...} \emph{Monad Transformer Optics} \cite{MonadTransformerLensesTalk} were considered by Edward Kmett  as a method for embedding pieces of a monad transformer stack into the whole.
+\item \emph{Monad Transformer Optics} \cite{MonadTransformerLensesTalk} were considered by Edward Kmett  as a method for embedding pieces of a monad transformer stack into the whole.
 There is some debate about the correct categorical description of monad transformers~\cite{MonadTransformersAsMonoidTransformers, CalculatingMonadTransformersCategoryTheory}, so we do not attempt to say anything precise, but the perspective given here could help in a couple of ways.
@@
 If $P, Q \in \Prof(\C, \C)$ are equipped with module structures $\alpha$ and $\beta$ respectively, there is a canonical module structure on $P \odot Q$.
-Given $M \in \M$ and $A,B \in \C$, the structure map $(\alpha \odot \beta)_{A,B,M}$ is induced by
+Given $M \in \M$ and $A,B \in \C$, the structure map ${(\alpha \odot \beta)}_{A,B,M}$ is induced by
 \begin{align*}
@@
 \begin{proof}
-  This follows from abstract nonsense as the left adjoint of a strong monoidal functor, see \cite{Kelly1974}.
+  This follows from abstract nonsense as the left adjoint of a strong monoidal functor, see~\cite{Kelly1974}.
 \end{proof}
@@
 \begin{remark}
-  The right adjoint to $U$ is described in \cite{NotionsOfComputationAsMonoids} to investigate Haskell's \mintinline{haskell}{Arrow} typeclass.
+  The right adjoint to $U$ is described in~\cite{NotionsOfComputationAsMonoids} to investigate Haskell's \mintinline{haskell}{Arrow} typeclass.
 \end{remark}
@@
     &[\Tamb(\M), \Set]((U-)(A,A),(U-)(S,S)) \\
-    \cong \;&[\Tamb(\M), \Set](\Tamb(\M)(\Pastro_\M E_A, -), (U-)(S,S))  && \text{(by Lemma \ref{lemma-rep})}\\
+    \cong \;&[\Tamb(\M), \Set](\Tamb(\M)(\Pastro_\M E_A, -), (U-)(S,S))  && \text{(by Lemma~\ref{lemma-rep})}\\
     \cong \;&(U\Pastro_\M E_A)(S,S)  && \text{(by Yoneda)} \\
@@
 Some optic variants can be encoded in a profunctor-like style without requiring the full complexity of profunctors.
-Chronologically this development came before profunctor optics, and was invented by Twan van Laarhoven \cite{VanLaarhovenPost}.
-
-The van Laarhoven encoding for \mintinline{haskell}{Lens}es and \mintinline{haskell}{Traversal}s is:
+Chronologically this development came before profunctor optics, and was invented by Twan van Laarhoven~\cite{VanLaarhovenPost}.
+
+The van Laarhoven encoding for \mintinline{haskell}{Lens}es, \mintinline{haskell}{Traversal}s and \mintinline{haskell}{Setter}s is:
 \begin{minted}{haskell}
@@
 \end{minted}
-What makes these particular optic variants work is that for \mintinline{haskell}{Lens}es, \mintinline{haskell}{Setter}s and \mintinline{haskell}{Traversal}s, the Tambara module that characterises them, $\Pastro_\M E_A$, can be written in the form \mintinline{haskell}{a -> f a} with \mintinline{haskell}{f} an instance of the relevant typeclass.
+What makes these particular optic variants work is that the Tambara module that characterises them, $\Pastro_\M E_A$, can be written in the form \mintinline{haskell}{a -> f a} with \mintinline{haskell}{f} an instance of the corresponding typeclass.
 Therefore, no expressive power is lost by restricting an optic to operate only on functions \mintinline{haskell}{a -> f a}, as the concrete description of the optic can be extracted from its value on that Tambara module.
@@
 
-\section{Mixed Optics}
-\todo{This hopefully will handle degenerate optics and indexed optics in a uniform way}
-
-\subsection{Lawful Mixed Optics}
-
-Suppose we have mixed optics
-
-\section{Examples Of Mixed Optics}
-
-\subsection{Degenerate Optics}
-
-Degenerate optics include the \mintinline{haskell}{Getter}s and \mintinline{haskell}{Review}s of the Haskell library, where an optic $(S, S') \hto (A, A')$ corresponds simply to a morphism $S \to A$ or $A' \to S'$ respectively.
-These do fit into the coend formalism, with a slight modification.
-
-If we have a monoidal category $\M$ that acts on two different categories $\C_1$ and $\C_2$, we may form the `optic' category:
-\begin{align*}
-  \Optic_\M((S, S'), (A, A')) := \int^{M \in \M} \C_1(S, MA) \times \C_2(MA', S')
-\end{align*}
-We lose, of course, the ability to talk about lawful optics.
-To encode \mintinline{haskell}{Getter}s or \mintinline{haskell}{Review}s, we then set $\C_2$ or $\C_1$ to be the codiscrete category $\C_\mathsf{codisc}$ with the same set of objects as $\C$, so that all homsets are the one element set.
-In this way we indeed get a category $\Getter$ that is isomorphic to $\C$.
-\begin{align*}
-\int^{M \in \M} \C(S, M \times A) \times \C_\mathsf{codisc}(M \times A', S') 
-&\cong \int^{M \in \M} \C(S, M \times A) \\
-&\cong \C(S, 1 \times A) \\
-&\cong \C(S, A)
-\end{align*}
-This works for $\Review$ in the same way, putting $\C_\mathsf{codisc}$ on the left. The functor $\C \to \C_\mathsf{codisc}$ induces functors $\Lens \to \Getter$ and $\Prism \to \Review$.
-
-Finally, we encode $\Fold$s, which in $\Set$ are functions $S \to \mathrm{List}\,A$. The key is that the $\mathrm{List}$ functor is the terminal $\Traversable$ \todo{ref}, so we have isomorphisms
-\begin{align*}
-&\int^{M \in \Traversable} \Set(S, MA) \times \Set_\mathsf{codisc}(MA', S') \\
-&\cong \int^{M \in \Traversable} \Set(S, MA) \\
-&\cong \Set(S, \mathrm{List}\,A)
-\end{align*}
-
-There is a corresponding notion of Tambara module for a profunctor between two different categories.
-A profunctor $P : \C^\op \times \C_\mathsf{codisc}$ essentially ignores its covariant argument; this explains the appearance of a \mintinline{haskell}{RightPhantom} typeclass or equivalent in many profunctor optic libraries.
+\section{Future work}
 
@@
 
-\todo{Make sure I cite \cite{IndexedOpticsPost}}
+\todo{Make sure I cite~\cite{IndexedOpticsPost}}
 
@@
 
+\subsection{Mixed Optics}
+\todo{This hopefully will handle degenerate optics and indexed optics in a uniform way}
+
 \subsection{Monotone Optics???}
 
+\subsection{Symmetric Optics}
+
+\subsection{Learners}
+
 \section{Conclusion}
@@
 
-\todo{Talk about how the four `parameters' to $\Optic$ is not the same thing as the four parameters to Haskell lenses}
-
 \todo{Make sure I'm not using any $\Set$-only results too generally in the traversal section}
@@
 \todo{Consistently use $\Rightarrow$ for natural transformations everywhere?}
-
-\todo{homset vs hom-set?}
 

### 2018-07-09 paper.tex
Some details

@@
 \newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{conjecture}[theorem]{Conjecture}
 
@@
 \newcommand{\Optic}{\mathbf{Optic}}
+\newcommand{\Twoptic}{\mathbf{Optic}^2}
 \newcommand{\Lawful}{\mathbf{Lawful}}
@@
 
-We consider a lens well-behaved if it obeys the following laws:
+Often we want our lens to obey the following laws:
 \begin{itemize}
@@
 Each optic variant has a concrete description as a certain collection of maps, with attendant laws under which we consider them well-behaved.
-We begin in Section~\ref{sec:optics} by defining the \emph{category of optics} in a sufficiently general way to encompass almost all the optic variants in use in the wild.
+We begin in Section~\ref{sec:optics} by defining the \emph{category of optics} in a sufficiently general way to encompass almost all the optic variants in use in the wild, using lenses as a running example.
 Section~\ref{sec:lawful-optics} defines the equivalent of the lens laws for a generic category of optics.
-Then in Section~\ref{sec:examples} we see that these generic definitions specialise correctly to all the basic varieties of optic, including giving the correct laws.
+Then in Section~\ref{sec:examples} we see that these generic definitions specialise correctly to the other basic varieties of optic, including giving the correct laws.
 
@@
 Our definition is identical, other than flipping the direction of the morphisms to match the existing work on lenses, and restricting our attention to the unenriched setting.
-
-This section contains no discussion of laws. The optic category is  generalising the pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$, with no additional conditions imposed.
 
@@
 
-\begin{proposition}\label{prop-optic-is-cat}
+\begin{proposition}\label{prop:optic-is-cat}
   The above data form a category $\Optic_\otimes$.
@@
 \end{remark}
+
+If $\C$ is a category with finite products, then $\Lens = \Optic_\times$ is exactly the category of lenses described in the introduction.
+That optics correspond to pairs of $\fget$ and $\fput$ functions is shown via the following isomorphisms:
+\begin{align*}
+  \Optic_\times((S, S'), (A, A')) 
+  &= \int^{M \in \C} \C(S, M \times A) \times \C(M \times A', S') \\
+  &\cong \int^{M \in \C} \C(S, M) \times \C(S, A) \times \C(M \times A', S') && \text{(universal property of product)} \\
+  &\cong \C(S, A) \times \C(S \times A', S') && \text{(Yoneda reduction)}
+\end{align*}
+Let $\conc_\times((S, S'), (A, A'))$ denote this set of concrete lenses.
+Explicitly the isomorphism states that, given an optic $\rep{l}{r} : (S, S') \hto (A, A')$, the corresponding concrete lens is the pair $(\fget, \fput)$, where $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
+In the other direction, given $(\fget, \fput)$, the corresponding optic has representative $\rep{[\id_S, \fget]}{\fput}$.
+
+Using the isomorphism in both directions, we leave it to the reader to verify that composition in $\Optic_\times$ corresponds to ordinary composition of concrete lenses.
+(Of course, there is only one possible way such a collection of concrete maps could be composed!)
 
@@
 \begin{theorem}
-  $\Optic_\otimes$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit object is $(I, I)$, and the action on a pair of morphisms $\rep{l}{r} : S \hto A$ and $\rep{l'}{r'} : T \hto B$ is given by:
+  $\Optic_\otimes$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit object is $(I, I)$, and the action on a pair of morphisms $\rep{l}{r} : (S, S') \hto (A, A')$ and $\rep{l'}{r'} : (T, T') \hto (B, B')$ is given by:
   \begin{center}
@@
 There is some further useful structure in $\Optic_\otimes$.
-\begin{proposition}\label{prop-costates}
+\begin{proposition}\label{prop:costates}
   The set of costates $(S, S') \hto (I, I)$ is isomorphic to $\C(S, S')$.
@@
 
-\begin{proposition}\label{prop-optic-functor}
+\begin{proposition}\label{prop:optic-functor}
   Collectively this operation defines a 2-functor \[\Optic : \SymmMonCat \to \SymmMonCat.\] \qed
@@
   \end{align*}
-  And on morphisms $\rep{l}{r} : S \hto A$ and $\rep{l'}{r'} : T \hto B$ by:
+  And on morphisms $\rep{l}{r} : (S, S') \hto (A, A')$ and $\rep{l'}{r'} : (T, T') \hto (B, B')$ by:
   \begin{center}
@@
 \begin{definition}
-  A \emph{teleological functor} $F : \C \to \D$ is a symmetric monoidal functor that restricts to a functor $F_d : \C_d \to \D_d$ on the dualisable subcategories, commutes \todo{strictly?} with the duality and such that the counits are preserved:
+  A \emph{teleological functor} $F : \C \to \D$ is a symmetric monoidal functor that restricts to a functor $F_d : \C_d \to \D_d$ on the dualisable subcategories, commutes with the duality and such that the counits are preserved:
   \[
@@
 
-  Note that the diagrams that are required to commute in the definition of teleological category all terminate with the unit $I$, so in view of Proposition~\ref{prop-costates} we should not be surprised that they correspond to equality of maps in $\C$.
+  Note that the diagrams that are required to commute in the definition of teleological category all terminate with the unit $I$, so in view of Proposition~\ref{prop:costates} we should not be surprised that they correspond to equality of maps in $\C$.
 \end{proof}
@@
 \begin{proposition}
-  The functor $\Optic : \SymmMonCat \to \SymmMonCat$ of Proposition~\ref{prop-optic-functor} has its image in the subcategory $\Tele$.
+  The functor $\Optic : \SymmMonCat \to \SymmMonCat$ of Proposition~\ref{prop:optic-functor} has its image in the subcategory $\Tele$.
 \end{proposition}
@@
 
-\begin{proposition}\label{prop-optic-decompose}
+\begin{proposition}\label{prop:optic-decompose}
   Suppose $\rep{l}{r} : (S, S') \hto (A, A')$ has residual $M$. Then
@@
 
-The following are analogous to Propositions~\ref{prop-optic-is-cat} and~\ref{prop:change-of-action-monoidal}.
+The following are analogous to Propositions~\ref{prop:optic-is-cat} and~\ref{prop:change-of-action-monoidal}.
 
@@
 
+Let $\Twoptic_\M(S, A)$ \todo{(please come up with a better notation)} denote the set \[ \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S). \]
 Using the universal property of the coend, we define three maps:
@@
   \outside &: \Optic_\M(S, A) \to \C(S, S) \\
-  \once, \twice &: \Optic_\M(S, A) \to \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S)
+  \once, \twice &: \Optic_\M(S, A) \to \Twoptic_\M(S, A)
 \end{align*}
@@
 
-We will see that in all the common examples of optics, this specialises to the expected laws for that variant of optic.
-
-\begin{remark}
-  Jeremy Gibbons notes (originally in the case of ordinary lenses) that the first law is equivalent to requiring that $p$ composed with the connector $c_A$ is equal to the connector $c_S$.
-This is an appealing description from a string diagram standpoint, but I do not know if there is a similar description for the second law.
-\todo{Something to do with embedding $\Optic_\otimes$ into a compact closed category then using the unit to compose the lenses vertically?
-Should I draw a picture of this?}
-\end{remark}
-
-\begin{proposition}
-  There is an subcategory $\Lawful_\M$ of $\Optic_\M$ given by objects of the form $(S, S)$ and lawful optics between them.
-\end{proposition}
-\begin{proof}
-  The identity optic $\iota(\id_S, \id_S)$ is lawful:
-  \begin{align*}
-    \outside(\rep{\lambda^{-1}_S}{\lambda_{S}}) &= \lambda_{S} \lambda^{-1}_S = \id_S \\
-    \intertext{and}
-    \once(\rep{\lambda^{-1}_S}{\lambda_{S}})
-                                                          &= \repthree{\lambda^{-1}_S}{\id_{IA}}{\lambda_{S}} \\
-                                                          &= \repthree{\lambda^{-1}_S}{\lambda_{S};\lambda^{-1}_S}{\lambda_{S}} \\
-                                                          &= \twice(\rep{\lambda^{-1}_S}{\lambda_{S}})
-  \end{align*}
-
-  Suppose we have two lawful optics $\rep{l}{r} : R \hto S$ and $\rep{l'}{r'} : S \hto A$, where $l : R \to MS$ and $l' : S \to NA$.
-We must show that $\rep{(Ml')l}{r (Mr')}$ is also a lawful optic.
-The first equation is straightforward:
-  \begin{align*}
-    \outside(\rep{l; (Ml')}{(Mr') ; r})
-    &= l ; Ml' ; Mr' ; r \\
-    &= l ; M(l'r') ; r \\
-    &= l ; M\id_{NA} ; r \\
-    &= l ; r \\
-    &= \id_S
-  \end{align*}
-
-  For the second, we must show
-  \[ \repthree{ l;(Ml')}{(Mr'); r;l;(Ml')}{(Mr') ; r} = \repthree{l;(Ml')}{\id_{MNA}}{(Mr') ; r}. \]
-
-  We do this by showing that, in some sense, the expressions in the above equation respect the coend relations defining the codomains of $\once(\rep{l}{r})$ and $\once(\rep{l'}{r'})$.
-
-  So consider the generating relation $\repthree{ l;\phi_S}{c}{r} = \repthree{l}{\phi_S ; c}{r}$ in \[\int^{M_1, M_2 \in \M} \C(R, M_1 S) \times \C(M_1 S, M_2 S) \times \C(M_2 S, R).\]
-  This implies that
-  \begin{align*}
-    \repthree{l;\phi_S;(Ml')}{(Mr'); c ;(Ml')}{(Mr') ; r}
-    &= \repthree{l;(Ml');\phi_{NA}}{(Mr'); c ;(Ml')}{(Mr') ; r} && \text{(functoriality)} \\
-    &= \repthree{l;(Ml')}{\phi_{NA};(Mr'); c ;(Ml')}{(Mr') ; r} && \text{(coend relation)} \\
-    &= \repthree{l;(Ml')}{(Mr');\phi_{S}; c ;(Ml')}{(Mr') ; r} && \text{(functoriality)}
-  \end{align*}
-  And similarly for the other generating relation, $\repthree{l}{c;\phi_S}{r} = \repthree{l}{c}{\phi_S; r}$.
-
-  Therefore, the chain of relations proving $\repthree{l}{r;l}{r} = \repthree{l}{\id_{MA}}{r}$ can be replicated to show
-  \begin{align*}
-    \repthree{l;(Ml')}{(Mr');r;l;(Ml')}{(Mr') ; r} &= \repthree{l;(Ml')}{(Mr');\id_{MA};(Ml')}{(Mr') ; r},
-  \end{align*}
-  which is equal to $\repthree{l;(Ml')}{M(r'l')}{(Mr') ; r}$.
-
-  Similarly, a generating relation $\repthree{l';\psi_A}{c'}{r'} = \repthree{l'}{\psi_A ; c'}{r'}$ in \[\int^{N_1, N_2 \in \M} \C(S, N_1 A) \times \C(N_1 A, N_2 A) \times \C(M_2 A, S)\]
-  implies that
-  \begin{align*}
-    \repthree{l;M(l';\psi_A)}{Mc'}{(Mr') ; r}
-    &= \repthree{l;Ml';M\psi_A}{Mc'}{(Mr') ; r} \\
-    &= \repthree{l;Ml'}{M\psi_A ; Mc'}{(Mr') ; r} \\
-    &= \repthree{l;Ml'}{M(\psi_A;c')}{(Mr') ; r}
-  \end{align*}
-  So again we can replicate the chain of relations proving $\repthree{l'}{r';l'}{r'} = \repthree{l'}{\id_{MA}}{r'}$ to show that
-  \[\repthree{l;(Ml')}{M(r'l')}{(Mr') ; r} = \repthree{l;(Ml')}{\id_{MNA}}{(Mr') ; r} \]
-
-  We conclude that composition preserves lawfulness, so $\Lawful_\M$ is indeed a subcategory of $\Optic_\M$.
-\end{proof}
-
-\begin{proposition}
-  In the case that $\C$ is symmetric monoidal and $\M = \C$ acts by left-tensor, then $\Lawful_\otimes$ is symmetric monoidal with the unswitched tensor.
-\end{proposition}
-This would of course make no sense with the switched tensor, as the tensor of two objects would no longer be of the form $(X, X)$.
-\begin{proof}
-\todo{todo}
-\end{proof}
-
-\begin{proposition}
-  Suppose $F : (\M, \C) \to (\N, \D)$ is a morphism of actions. Then $\Optic(F) : \Optic_\M \to \Optic_\N$ restricts to a functor $\Lawful_\M \to \Lawful_\N$.
-\end{proposition}
-\begin{proof}
-  If $p = \rep{l}{r}$ is lawful, then verifying the first equation is easy:
-  \begin{align*}
-  \outside(\Optic(F)(\rep{l}{r}))
-  &= \outside(\rep{(Fl);\phi^{-1}_{M,A}}{\phi_{M,A'};(Fr)}) \\
-  &= (Fl);\phi^{-1}_{M,A};\phi_{M,A'};(Fr)\\
-  &= (Fl);(Fr)\\
-  &= \id_{FS}
-  \end{align*}
-  where $\phi_{M,A'} : (F^\bullet M)(FA) \to F(MA)$ is the structure map for $F$ commuting with the actions.
-
-  For the second equation, consider a generating relation $\repthree{l;\psi A}{c}{r} = \repthree{l}{\psi A ; c}{r}$. We can use the naturality of $\phi$ to show
-  \begin{align*}
-  \repthree{F(l;\psi A);\phi^{-1}_{M,A}}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr}
-  &= \repthree{Fl;F(\psi A);\phi^{-1}_{M,A}}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
-  &= \repthree{Fl;\phi^{-1}_{M',A};(F^\bullet \psi) A}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
-  &= \repthree{Fl;\phi^{-1}_{M',A}}{(F^\bullet \psi) A;\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
-  &= \repthree{Fl;\phi^{-1}_{M',A}}{\phi_{M',A};F(\psi A);Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
-  &= \repthree{Fl;\phi^{-1}_{M',A}}{\phi_{M',A};F(\psi A;c);\phi^{-1}_{N,A}}{\phi_{N,A};Fr}
-  \end{align*}
-  Similarly,
-  \begin{align*}
-    \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};F(\psi_A;r)}
-    &= \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};F(c;\psi A);\phi^{-1}_{N,A}}{\phi_{N,A};Fr}
-  \end{align*}
-
-  If $\rep{l}{r}$ is lawful, we can therefore replicate the chain of relations proving $\twice(\rep{l}{r}) = \once(\rep{l}{r})$ to show:
-  \begin{align*}
-  \twice(\Optic(F)(\rep{l}{r}))
-  &= \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};F(r;l);\phi^{-1}_{M,A}}{\phi_{M,A};Fr}  \\
-  &= \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};F(\id_{MA});\phi^{-1}_{M,A}}{\phi_{M,A};Fr}  \\
-  &= \repthree{Fl;\phi^{-1}_{M,A}}{\id_{(F^\bullet M)(FA)}}{\phi_{M,A};Fr}  \\
-  &= \once(\Optic(F)(\rep{l}{r}))
-  \end{align*}
-
-  \todo{There is probably a more conceptual way to do this}
-\end{proof}
-
-The requirement that $\once(p) = \twice(p)$ is mysterious, but there are sufficient conditions that are easier to verify.
-
-\begin{proposition}
-  Let $\rep{l}{r} : S \hto A$ be an optic. If $l;r = \id_S$ and $r;l = \phi A$ for some $\phi : M \to M$ in $\M$, then $\rep{l}{r}$ is lawful.
-\end{proposition}
-\begin{proof}
-  The $\outside(\rep{l}{r}) = l;r = \id_S$ is exactly the first condition. And for the second, we verify:
-  \begin{align*}
-    \twice(\rep{l}{r})
-    &= \repthree{l}{r;l}{r} \\
-    &= \repthree{l}{\phi A}{r} && \text{($r;l = \phi A$)}\\
-    &= \repthree{l ; (\phi A)}{\id_{MA}}{r} && \text{(coend relation)} \\
-    &= \repthree{l;r;l}{\id_{MA}}{r} && \text{($r;l = \phi A$ again)}\\
-    &= \repthree{l}{\id_{MA}}{r}  && \text{($l;r = \id_S$)}\\
-    &= \once(\rep{l}{r})
-  \end{align*}
-\end{proof}
-
-\begin{remark}
-  Even if $r;l = \phi A$ for some $\phi$, the same is not necessarily true of any other representative of the same optic.
-\end{remark}
-
-Let $\inside : \Optic_\M(S, A) \to \int^{M \in \M} \C(M A, M A)$ be the map induced by $\inside(\rep{l}{r}) = \langle r ; l \rangle$.
-We might ask that instead of requiring $r;l = \phi A$ exactly, we have $\langle r ; l \rangle = \langle \phi A \rangle$ in $\int^{M \in \M} \C(M A, M A)$.
-In fact, this is equivalent:
-
-\begin{proposition}\label{prop-onthenose}
-  Suppose $p : S \hto A$ satisfies $\outside(p) = \id_S$ and $\inside(p) = \langle \phi A \rangle$.
-Then there exists a representative $\rep{l}{r}$ such that $l ; r = \psi A$ on the nose for some (possibly different) $\psi : M \to M$.
-\end{proposition}
-\begin{proof}
-  The generating relation for $\int^{M \in \M} \C(M A, M A)$ is
-  \[ \langle f \phi_A \rangle = \langle \phi_A f \rangle \]
-  whenever $f : N A \to M A$ and $\phi : M \to N$. This relation $f \phi_A \rightsquigarrow \phi_A f$ is not likely to be symmetric or transitive in general.
-
-  Note that if $f \phi_A \rightsquigarrow \phi_A f$ then $f \phi_A f \phi_A \rightsquigarrow \phi_A f \phi_A f$. More generally, if $f \rightsquigarrow g$ then $f^n \rightsquigarrow g^n$ for any $n$.
-
-  Now let $\rep{l}{r}$ be a representative for $p$, so $rl = \id_S$ and $\langle lr \rangle = \langle \psi A\rangle$.
-There therefore exists a finite chain of relations $lr = u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n = \psi A$.
-Suppose the first relation faces rightward, so there exists a $k$ and $\phi$ with $r;l = \phi_A;k$ and $u_2 = k;\phi_A$.
-Define $l' = l;\phi_A$ and $r' = k;r$.
-Then:
-\begin{align*}
-\rep{l'}{r'}
-&= \rep{l ; \phi_A}{k ; r} \\
-&= \rep{l}{\phi_A ; k ; r} \\
-&= \rep{l}{r ; l; r} \\
-&= \rep{l}{r}
-\end{align*}
-This new representative satisfies
-\begin{align*}
-l';r' &= l;\phi_A;k;r = l;r;l;r = \id_S \\
-r';l' &= k;r;l;\phi_A = k;\phi_A;k;\phi_A = u_2^2
-\end{align*}
-
-  A symmetric argument shows that if instead the relation faces leftward, so $lr \leftsquigarrow u_2$, there again exists $l'$ and $r'$ so that $\rep{l}{r} = \rep{l'}{r'}$, and both $l';r' = \id_S$ and $r';l' = u_2^2$.
-
-  We can now inductively apply the above argument to the shorter chain \[l'r' = u_1^2 \leftrightsquigarrow \dots \leftrightsquigarrow u_n^2 \leftrightsquigarrow {(\psi A)}^2 = \psi^2 A,\] obtained by squaring each morphism in the original chain, until we are left with a representative $\rep{l^*}{r^*}$ such that $r^*;l^* = \psi^N_A$, for some $N>0$.
-This pair $\rep{l^*}{r^*}$ is the required representative.
-\end{proof}
-
-The above argument has a similar form to those that appear in~\cite{OnTheTrace}, which considered (among other things) coends of the form $\int^{c \in \C} \C(c, Fc)$ for an endofunctor $F : \C \to \C$.
-
-\section{Examples}\label{sec:examples}
-
-The general pattern is as follows.
-Once we choose a particular monoidal action $\M \to [\C, \C]$, we find an isomorphism between the set of optics $(S, S') \hto (A, A')$ and a set $\conc((S, S'), (A, A'))$ that is easier to describe.
-We follow~\cite{ProfunctorOptics} (and others) in calling elements of $\conc$ \emph{concrete optics}.
-There is no canonical choice for this set; our primary goal is to find a way to eliminate the coend so that we no longer have to deal with equivalence classes of morphisms.
-
-Ideally, we then also find a simplified description $\conctwice(S, A)$ for the set \[ \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S)\] appearing in the definition of a lawful optic.
-We can then ``read off'' what conditions on are needed on a concrete optic to ensure that the corresponding element of $\Optic_\M(S, A)$ is lawful.
-We will call these conditions the \emph{concrete} laws.
-
-It is worth emphasising that once a monoidal action has been chosen and a concrete description of the corresponding optics found, no further work is needed to show that the result forms a category of optics with a subcategory of lawful optics.
-This is especially useful when devising new optic variants, as we do later.
-
-We begin with the most common kinds of optic before moving to more exotic possibilities.
-
-\todo{There is a common pattern in some of these examples, where the evaluation-at-$A$ functor $-A : \M \to \C$ has a left or right adjoint. Is it worth abstracting this out?}
-
-\subsection{Lenses}
-
-Lenses form the ur-example of a category of optics.
-
-\begin{definition}
-  Suppose $\C$ has finite products, and let $\C$ act on itself via the bifunctor $\times : \C \times \C \to \C$.
-The \emph{category of lenses} $\Lens$ is the category of lawful optics with respect to this action.
-\end{definition}
-
-The optics for this action correspond exactly to pairs of $\fget$ and $\fput$ functions.
-\begin{align*}
-  \Optic_\times((S, S'), (A, A')) &= \int^{M \in \C} \C(S, M \times A) \times \C(M \times A', S') \\
-                                  &\cong \int^{M \in \C} \C(S, M) \times \C(S, A) \times \C(M \times A', S') && \text{(universal property of product)} \\
-                                  &\cong \C(S, A) \times \C(S \times A', S') && \text{(Yoneda reduction)}
-\end{align*}
-
-This last set is the set of concrete lenses $\conc_\times((S, S'), (A, A'))$.
-Explicitly this isomorphism states that, given an optic $\rep{l}{r} : (S, S') \hto (A, A')$, the corresponding element of $\conc_\times((S, S'), (A, A'))$ is the pair $(\fget, \fput)$, where $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
-In the other direction, given $(\fget, \fput)$, the corresponding optic has representative $\rep{[\id_S, \fget]}{\fput}$.
-
-\begin{remark}\label{lens-iota-not-faithful}
-  For the category of sets, the functor $\iota(-, -) : \Set \times \Set^\op \to \Optic_\times$ is not faithful.
-The problem is the empty set: the functor $0 \times (-)$ is not faithful.
-Any pair of maps $f : 0 \to A$, $g : A' \to S'$ yield equivalent optics $\iota(f, g)$, as the corresponding $\fget$ and $\fput$ functions must be the unique maps from $0$.
-\end{remark}
-
-\begin{remark}
-  In the case that $\C$ is cartesian closed, $\Optic_\times$ is monoidal closed via the astonishing formula
-  \begin{align*}
-    [(S, S'), (A, A')] := (\homC(S, A) \times \homC(S \times A', S'), \, S \times A')
-  \end{align*}
-  where $\homC(-, -)$ denotes the internal hom. For a proof see~\cite[Section 1.2]{DialecticaCategories}. This cannot be extended to non-cartesian closed categories, the isomorphism
-  \begin{align*}
-    \Optic_\times((S, S') \otimes (T, T'), (A, A')) \cong \Optic_\times((S, S'),  [(T, T'), (A, A')])
-  \end{align*}
-  uses the diagonal maps of $\C$ in an essential way.
-\end{remark}
-
-We now discuss lawful lenses.
-
-\begin{proposition}\label{prop-OpticImpliesLensLaws}
-  A concrete lens given by $\fget$ and $\fput$ is lawful (in our sense) if and it obeys the three lens laws.
-\end{proposition}
-\begin{proof}
-  We begin by giving
-  \[ \int^{M_1, M_2 \in \C} \C(S, M_1 \times A) \times \C(M_1 \times A, M_2 \times A) \times \C(M_2 \times A, S)\]
-  the same treatment as $\Optic_\times(S, A)$. By the same sorts of arguments as above \todo{is this worth writing out?}, this is isomorphic to
+Returning to ordinary lenses, we can show that this is equivalent to the laws we expect.
+
+\begin{proposition}\label{prop:lawful-lens-laws}
+  A concrete lens given by $\fget$ and $\fput$ is lawful (in our sense) iff it obeys the three concrete lens laws.
+\end{proposition}
+\begin{proof}
+  We begin by giving $\Twoptic_\times(S, A)$ the same treatment as $\Optic_\times(S, A)$.
+Using Yoneda reduction and the universal property of the product, as we did for lenses themselves, it is isomorphic to the set
   \[\conctwice_\times(S, A) := \C(S, A) \times \C(S \times A, A) \times \C(S \times A \times A, S)\]
@@
   \end{alignat*}
-  So looking component-wise, $\Phi(\once(p))$ being equal to $\Phi(\twice(p))$ is exactly equivalent to the $\fput\fget$ and $\fput\fput$ laws holding.
-\end{proof}
-
-If we ask more of our category $\C$, we can upgrade this result to show that a lens $S \hto A$ implies the existence of a complement $\C$ with $S \cong C \times A$.
+  So checking component-wise, $\Phi(\once(p))$ being equal to $\Phi(\twice(p))$ is exactly equivalent to the $\fput\fget$ and $\fput\fput$ laws holding.
+\end{proof}
+
+We will see that in all the other common examples of optics, this also specialises to the expected laws for that variant of optic.
+
+\begin{remark}
+  Jeremy Gibbons notes (originally in the case of ordinary lenses) that the first law is equivalent to requiring that $p$ composed with the connector $c_A$ is equal to the connector $c_S$.
+This is an appealing description from a string diagram standpoint, but it is not clear whether there is a similar description for the second law.
+% \todo{Something to do with embedding $\Optic_\otimes$ into a compact closed category then using the unit to compose the lenses vertically?
+Should I draw a picture of this?}
+\end{remark}
+
+\begin{proposition}\label{prop:lawful-category}
+  There is an subcategory $\Lawful_\M$ of $\Optic_\M$ given by objects of the form $(S, S)$ and lawful optics between them.
+\end{proposition}
+\begin{proof}
+  This will follow from our description of lawful profunctor optics later, but we give a direct proof.
+
+  The identity optic $\iota(\id_S, \id_S)$ is lawful:
+  \begin{align*}
+    \outside(\rep{\lambda^{-1}_S}{\lambda_{S}}) &= \lambda_{S} \lambda^{-1}_S = \id_S \\
+    \intertext{and}
+    \once(\rep{\lambda^{-1}_S}{\lambda_{S}})
+                                                          &= \repthree{\lambda^{-1}_S}{\id_{IA}}{\lambda_{S}} \\
+                                                          &= \repthree{\lambda^{-1}_S}{\lambda_{S};\lambda^{-1}_S}{\lambda_{S}} \\
+                                                          &= \twice(\rep{\lambda^{-1}_S}{\lambda_{S}})
+  \end{align*}
+
+  Suppose we have two lawful optics $\rep{l}{r} : R \hto S$ and $\rep{l'}{r'} : S \hto A$ with residuals $M$ and $N$ respectively.
+We must show that $\rep{(Ml')l}{r (Mr')}$ is also a lawful optic.
+Showing the first law is straightforward:
+  \begin{align*}
+    \outside(\rep{l; (Ml')}{(Mr') ; r})
+    &= l ; Ml' ; Mr' ; r \\
+    &= l ; M(l'r') ; r \\
+    &= l ; M\id_{NA} ; r \\
+    &= l ; r \\
+    &= \id_S
+  \end{align*}
+
+  For the second, we must show
+  \[ \repthree{ l;(Ml')}{(Mr'); r;l;(Ml')}{(Mr') ; r} = \repthree{l;(Ml')}{\id_{MNA}}{(Mr') ; r}. \]
+
+  We do this by showing that the expressions above respect the coend relations defining $\Twoptic_\M(R, S)$ and $\Twoptic_\M(S, A)$. In the first step we use the former to show
+  \[ \repthree{ l;(Ml')}{(Mr'); r;l;(Ml')}{(Mr') ; r} = \repthree{l;(Ml')}{(Mr'l')}{(Mr') ; r} \]
+  and in the second step, the latter to show
+  \[ \repthree{ l;(Ml')}{(Mr'l')}{(Mr') ; r} = \repthree{l;(Ml')}{\id_{MNA}}{(Mr') ; r}. \]
+
+  So consider the generating relation $\repthree{l;\phi_S}{c}{r} = \repthree{l}{\phi_S ; c}{r}$ in $\Twoptic_\M(R, S)$.
+A consequence is that we can transfer $\phi_S$ past $\rep{l'}{r'}$ in the expression:
+  \begin{align*}
+    \repthree{l;\phi_S;(Ml')}{(Mr'); c ;(Ml')}{(Mr') ; r}
+    &= \repthree{l;(Ml');\phi_{NA}}{(Mr'); c ;(Ml')}{(Mr') ; r} && \text{(functoriality)} \\
+    &= \repthree{l;(Ml')}{\phi_{NA};(Mr'); c ;(Ml')}{(Mr') ; r} && \text{(coend relation)} \\
+    &= \repthree{l;(Ml')}{(Mr');\phi_{S}; c ;(Ml')}{(Mr') ; r} && \text{(functoriality)}
+  \end{align*}
+  And similarly for the other generating relation, $\repthree{l}{c;\phi_S}{r} = \repthree{l}{c}{\phi_S; r}$.
+
+  If $\repthree{l}{r;l}{r} = \repthree{l}{\id_{MA}}{r}$, then there exists a finite chain of coend relations connecting them. Because of the above, this chain can be replicated to show
+  \begin{align*}
+    \repthree{l;(Ml')}{(Mr');r;l;(Ml')}{(Mr') ; r} &= \repthree{l;(Ml')}{(Mr');\id_{MA};(Ml')}{(Mr') ; r},
+  \end{align*}
+  which is equal to $\repthree{l;(Ml')}{M(r'l')}{(Mr') ; r}$.
+
+  Similarly, a generating relation $\repthree{l';\psi_A}{c'}{r'} = \repthree{l'}{\psi_A ; c'}{r'}$ in $\Twoptic_\M(S, A)$ implies that
+  \begin{align*}
+    \repthree{l;M(l';\psi_A)}{Mc'}{(Mr') ; r}
+    &= \repthree{l;Ml';M\psi_A}{Mc'}{(Mr') ; r} \\
+    &= \repthree{l;Ml'}{M\psi_A ; Mc'}{(Mr') ; r} \\
+    &= \repthree{l;Ml'}{M(\psi_A;c')}{(Mr') ; r}
+  \end{align*}
+  So again we can replicate the chain of relations proving $\repthree{l'}{r';l'}{r'} = \repthree{l'}{\id_{MA}}{r'}$ to show that
+  \[\repthree{l;(Ml')}{M(r'l')}{(Mr') ; r} = \repthree{l;(Ml')}{\id_{MNA}}{(Mr') ; r} \]
+
+  We conclude that composition preserves lawfulness, so $\Lawful_\M$ is indeed a subcategory of $\Optic_\M$.
+\end{proof}
+
+\begin{proposition}
+  If $f : S \to A$ and $g : A \to S$ are mutual inverses, then $\iota(f, g) : S \hto A$ is a lawful optic, so $\iota$ restricts to a functor $\mathrm{Core}(\C) \to \Lawful_\M$.
+\end{proposition}
+\begin{proof}
+The conditions are easy to check:
+\begin{align*}
+\outside(\iota(f, g)) &= \outside(\rep{\lambda_A^{-1} f}{g \lambda_{A}}) = g \lambda_{A} \lambda_A^{-1} f = g f = \id_S \\
+\twice(\iota(f, g)) 
+&= \repthree{\lambda_A^{-1} f}{\lambda_A^{-1} f g \lambda_{A}}{g \lambda_{A}} \\
+&= \repthree{\lambda_A^{-1} f}{\lambda_A^{-1} \lambda_{A}}{g \lambda_{A}} \\ 
+&= \repthree{\lambda_A^{-1} f}{\id_{IA}}{g \lambda_{A}} \\ 
+&= \once(\iota(f, g))
+\end{align*}
+\end{proof}
+
+\begin{proposition}
+  In the case that $\C$ is symmetric monoidal and $\M = \C$ acts by left-tensor, then $\Lawful_\otimes$ is symmetric monoidal with the unswitched tensor.
+\end{proposition}
+This would of course make no sense with the switched tensor, as the tensor of two objects would no longer be of the form $(X, X)$.
+\begin{proof}
+Due to the previous proposition, the structure maps of $\Optic_\M$ are all lawful.
+We just have to check that $\otimes : \Optic_\M \times \Optic_\M \to \Optic_\M$ restricts to a functor on $\Lawful_\M$.
+Given lawful optics $\rep{l}{r} : S \hto A$ and $\rep{l'}{r'} : T \hto B$ with residuals $N$ and $M$, the first law is easy to check.
+\begin{align*}
+\outside(\rep{l}{r} \otimes \rep{l'}{r'})
+&= \outside(\rep{(l \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B');(r \otimes r')}) \\
+&= (l \otimes l');(M \otimes s_{A,N} \otimes B);(M \otimes s_{A,N} \otimes B');(r \otimes r') \\
+&= (l \otimes l');(r \otimes r') \\
+&= \id_{S \otimes T}
+\end{align*}
+For the second, we follow the same strategy as Proposition~\ref{prop:lawful-category}, and show that the action of $\otimes$ on objects respects the coend relations in $\Twoptic_\M(S, A)$ and $\Twoptic_\M(T, B)$.
+
+Without loss of generality, we just check the case of $\repthree{l;\phi_S}{c}{r} = \repthree{l}{\phi_S ; c}{r}$:
+\begin{align*}
+&\repthree{(l;\phi_S \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B');(c \otimes c');(M \otimes s_{A,N} \otimes B)}{\dots} \\
+&= \repthree{(l \otimes l');(\phi_S \otimes N \otimes B);(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B');(c \otimes c');(M \otimes s_{A,N} \otimes B)}{\dots} \\
+&= \repthree{(l \otimes l');(\phi_S \otimes N \otimes B)}{(c \otimes c');(M \otimes s_{A,N} \otimes B)}{\dots} \\
+&= \repthree{(l \otimes l')}{(\phi_S \otimes N \otimes B);(c \otimes c');(M \otimes s_{A,N} \otimes B)}{\dots} \\
+&= \repthree{(l \otimes l')}{(\phi_S;c \otimes c');(M \otimes s_{A,N} \otimes B)}{\dots} \\
+&= \repthree{(l \otimes l');(M' \otimes s_{A,N} \otimes B)}{(M' \otimes s_{A,N} \otimes B);(\phi_S;c \otimes c');(M \otimes s_{A,N} \otimes B)}{\dots}
+\end{align*}
+So again, we can transplant the chain of relations proving $\repthree{l}{r;l}{r} = \repthree{l}{\id_{MA}}{r}$ and $\repthree{l'}{r';l'}{r'} = \repthree{l'}{\id_{NB}}{r'}$ to prove:
+\begin{align*}
+&\twice(\rep{l}{r} \otimes \rep{l'}{r'}) \\
+&= \twice(\rep{(l \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B');(r \otimes r')}) \\
+&=\repthree{(l \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B);(r \otimes r');(l \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B);(r \otimes r')} \\
+&= \repthree{(l \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B);(rl \otimes r'l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B);(r \otimes r')} \\
+&= \repthree{(l \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B);(\id_{M \otimes A} \otimes \id_{N \otimes B});(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B);(r \otimes r')} \\
+&= \repthree{(l \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B);(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B);(r \otimes r')} \\
+&= \repthree{(l \otimes l');(M \otimes s_{A,N} \otimes B)}{\id_{M \otimes N \otimes A \otimes B}}{(M \otimes s_{A,N} \otimes B);(r \otimes r')} \\
+&= \once(\rep{l}{r} \otimes \rep{l'}{r'})
+\end{align*}
+
+\todo{This suggests there's something general here I should actually be proving}
+\end{proof}
+
+\begin{proposition}
+  Suppose $F : (\M, \C) \to (\N, \D)$ is a morphism of actions. Then $\Optic(F) : \Optic_\M \to \Optic_\N$ restricts to a functor $\Lawful_\M \to \Lawful_\N$.
+\end{proposition}
+\begin{proof}
+  If $p = \rep{l}{r}$ is lawful, then verifying the first equation is easy:
+  \begin{align*}
+  \outside(\Optic(F)(\rep{l}{r}))
+  &= \outside(\rep{(Fl);\phi^{-1}_{M,A}}{\phi_{M,A'};(Fr)}) \\
+  &= (Fl);\phi^{-1}_{M,A};\phi_{M,A'};(Fr)\\
+  &= (Fl);(Fr)\\
+  &= \id_{FS}
+  \end{align*}
+  where $\phi_{M,A'} : (F^\bullet M)(FA) \to F(MA)$ is the structure map for $F$ commuting with the actions.
+
+  For the second equation, consider a generating relation $\repthree{l;\psi A}{c}{r} = \repthree{l}{\psi A ; c}{r}$. We can use the naturality of $\phi$ to show
+  \begin{align*}
+  \repthree{F(l;\psi A);\phi^{-1}_{M,A}}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr}
+  &= \repthree{Fl;F(\psi A);\phi^{-1}_{M,A}}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
+  &= \repthree{Fl;\phi^{-1}_{M',A};(F^\bullet \psi) A}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
+  &= \repthree{Fl;\phi^{-1}_{M',A}}{(F^\bullet \psi) A;\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
+  &= \repthree{Fl;\phi^{-1}_{M',A}}{\phi_{M',A};F(\psi A);Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
+  &= \repthree{Fl;\phi^{-1}_{M',A}}{\phi_{M',A};F(\psi A;c);\phi^{-1}_{N,A}}{\phi_{N,A};Fr}
+  \end{align*}
+  Similarly,
+  \begin{align*}
+    \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};F(\psi_A;r)}
+    &= \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};F(c;\psi A);\phi^{-1}_{N,A}}{\phi_{N,A};Fr}
+  \end{align*}
+
+  If $\rep{l}{r}$ is lawful, we can therefore replicate the chain of relations proving $\twice(\rep{l}{r}) = \once(\rep{l}{r})$ to show:
+  \begin{align*}
+  \twice(\Optic(F)(\rep{l}{r}))
+  &= \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};F(r;l);\phi^{-1}_{M,A}}{\phi_{M,A};Fr}  \\
+  &= \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};F(\id_{MA});\phi^{-1}_{M,A}}{\phi_{M,A};Fr}  \\
+  &= \repthree{Fl;\phi^{-1}_{M,A}}{\id_{(F^\bullet M)(FA)}}{\phi_{M,A};Fr}  \\
+  &= \once(\Optic(F)(\rep{l}{r}))
+  \end{align*}
+
+  \todo{There is probably a more conceptual way to do this}
+\end{proof}
+
+The requirement that $\once(p) = \twice(p)$ is mysterious, but there are sufficient conditions that are easier to verify.
+
+\begin{proposition}
+  Let $\rep{l}{r} : S \hto A$ be an optic. If $l;r = \id_S$ and $r;l = \phi A$ for some $\phi : M \to M$ in $\M$, then $\rep{l}{r}$ is lawful.
+\end{proposition}
+\begin{proof}
+  The $\outside(\rep{l}{r}) = l;r = \id_S$ is exactly the first condition. And for the second, we verify:
+  \begin{align*}
+    \twice(\rep{l}{r})
+    &= \repthree{l}{r;l}{r} \\
+    &= \repthree{l}{\phi A}{r} && \text{($r;l = \phi A$)}\\
+    &= \repthree{l ; (\phi A)}{\id_{MA}}{r} && \text{(coend relation)} \\
+    &= \repthree{l;r;l}{\id_{MA}}{r} && \text{($r;l = \phi A$ again)}\\
+    &= \repthree{l}{\id_{MA}}{r}  && \text{($l;r = \id_S$)}\\
+    &= \once(\rep{l}{r})
+  \end{align*}
+\end{proof}
+
+Even if $r;l = \phi A$ for some $\phi$, the same is not necessarily true of any other representative of the same optic.
+Let $\inside : \Optic_\M(S, A) \to \int^{M \in \M} \C(M A, M A)$ be the map induced by $\inside(\rep{l}{r}) = \langle r ; l \rangle$.
+We might ask that instead of requiring $r;l = \phi A$ exactly, we have $\langle r ; l \rangle = \langle \phi A \rangle$ in $\int^{M \in \M} \C(M A, M A)$.
+In fact, this is equivalent:
+
+\begin{proposition}\label{prop:onthenose}
+  Suppose $p : S \hto A$ satisfies $\outside(p) = \id_S$ and $\inside(p) = \langle \phi A \rangle$.
+Then there exists a representative $\rep{l}{r}$ such that $l ; r = \psi A$ on the nose for some (possibly different) $\psi : M \to M$.
+\end{proposition}
+\begin{proof}
+  The generating relation for $\int^{M \in \M} \C(M A, M A)$ is
+  \[ \langle f \phi_A \rangle = \langle \phi_A f \rangle \]
+  whenever $f : N A \to M A$ and $\phi : M \to N$. This relation $f \phi_A \rightsquigarrow \phi_A f$ is not likely to be symmetric or transitive in general.
+
+  Note that if $f \phi_A \rightsquigarrow \phi_A f$ then $f \phi_A f \phi_A \rightsquigarrow \phi_A f \phi_A f$. More generally, if $f \rightsquigarrow g$ then $f^n \rightsquigarrow g^n$ for any $n$.
+
+  Now let $\rep{l}{r}$ be a representative for $p$, so $rl = \id_S$ and $\langle lr \rangle = \langle \psi A\rangle$.
+There therefore exists a finite chain of relations $lr = u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n = \psi A$.
+Suppose the first relation faces rightward, so there exists a $k$ and $\phi$ with $r;l = \phi_A;k$ and $u_2 = k;\phi_A$.
+Define $l' = l;\phi_A$ and $r' = k;r$.
+Then:
+\begin{align*}
+\rep{l'}{r'}
+&= \rep{l ; \phi_A}{k ; r} \\
+&= \rep{l}{\phi_A ; k ; r} \\
+&= \rep{l}{r ; l; r} \\
+&= \rep{l}{r}
+\end{align*}
+This new representative satisfies
+\begin{align*}
+l';r' &= l;\phi_A;k;r = l;r;l;r = \id_S \\
+r';l' &= k;r;l;\phi_A = k;\phi_A;k;\phi_A = u_2^2
+\end{align*}
+
+  A symmetric argument shows that if instead the relation faces leftward, so $lr \leftsquigarrow u_2$, there again exists $l'$ and $r'$ so that $\rep{l}{r} = \rep{l'}{r'}$, and both $l';r' = \id_S$ and $r';l' = u_2^2$.
+
+  We can now inductively apply the above argument to the shorter chain \[l'r' = u_1^2 \leftrightsquigarrow \dots \leftrightsquigarrow u_n^2 \leftrightsquigarrow {(\psi A)}^2 = \psi^2 A,\] obtained by squaring each morphism in the original chain, until we are left with a representative $\rep{l^*}{r^*}$ such that $r^*;l^* = \psi^N_A$, for some $N>0$.
+This pair $\rep{l^*}{r^*}$ is the required representative.
+\end{proof}
+
+The above argument has a similar form to those that appear in~\cite{OnTheTrace}, which considered (among other things) coends of the form $\int^{c \in \C} \C(c, Fc)$ for an endofunctor $F : \C \to \C$.
+
+\section{Examples}\label{sec:examples}
+
+The general pattern is as follows.
+Once we choose a particular monoidal action $\M \to [\C, \C]$, we find an isomorphism between the set of optics $(S, S') \hto (A, A')$ and a set $\conc((S, S'), (A, A'))$ that is easier to describe.
+We follow~\cite{ProfunctorOptics} (and others) in calling elements of $\conc$ \emph{concrete optics}.
+There is no canonical choice for this set; our primary goal is to find a way to eliminate the coend so that we no longer have to deal with equivalence classes of morphisms.
+
+Ideally, we then also find a simplified description $\conctwice(S, A)$ for the set \[ \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S)\] appearing in the definition of a lawful optic.
+We can then ``read off'' what conditions on are needed on a concrete optic to ensure that the corresponding element of $\Optic_\M(S, A)$ is lawful.
+We will call these conditions the \emph{concrete laws}.
+
+It is worth emphasising that once a monoidal action has been chosen and a concrete description of the corresponding optics found, no further work is needed to show that the result forms a category with a subcategory of lawful optics.
+This is especially useful when devising new optic variants, as we do later.
+
+We begin with the most common kinds of optic before moving to more exotic possibilities.
+
+\todo{There is a common pattern in some of these examples, where the evaluation-at-$A$ functor $-A : \M \to \C$ has a left or right adjoint. Is it worth abstracting this out?}
+
+\subsection{Lenses}
+
+The founding example, that of lenses, has already been discussed in the previous sections. We add a couple of remarks.
+
+\begin{remark}\label{lens-iota-not-faithful}
+  For the category of sets, the functor $\iota : \Set \times \Set^\op \to \Optic_\times$ is not faithful.
+The problem is the empty set: the functor $0 \times (-)$ is not faithful.
+Any pair of maps $f : 0 \to A$, $g : A' \to S'$ yield equivalent optics $\iota(f, g)$, as the corresponding $\fget$ and $\fput$ functions must be the unique maps from $0$.
+\end{remark}
+
+\begin{remark}
+  In the case that $\C$ is cartesian closed, $\Optic_\times$ is monoidal closed via the astonishing formula
+  \begin{align*}
+    [(S, S'), (A, A')] := (\homC(S, A) \times \homC(S \times A', S'), \, S \times A')
+  \end{align*}
+  where $\homC(-, -)$ denotes the internal hom. For a proof see~\cite[Section 1.2]{DialecticaCategories}. This cannot be extended to non-cartesian closed categories, the isomorphism
+  \begin{align*}
+    \Optic_\times((S, S') \otimes (T, T'), (A, A')) \cong \Optic_\times((S, S'),  [(T, T'), (A, A')])
+  \end{align*}
+  uses the diagonal maps of $\C$ in an essential way.
+\end{remark}
+
+If we ask more of our category $\C$, we can show that a lens $S \hto A$ implies the existence of a complement $\C$ with $S \cong C \times A$.
 This doesn't appear to follow purely from the concrete lens laws---an argument that a definition of lawfulness based on constant complements is not the correct generalisation.
@@
   Suppose $\C$ has pullbacks and that there is a morphism $x : 1 \to A$.
-If $p : S \hto A$ satisfies the concrete lens laws then there exists $C \in \C$ and mutual inverses $l : S \to C \times A$ and $r : C \times A \to S$ so that $p = \rep{l}{r}$.
+If $p : S \hto A$ is lawful then there exists $C \in \C$ and mutual inverses $l : S \to C \times A$ and $r : C \times A \to S$ so that $p = \rep{l}{r}$.
 \end{proposition}
@@
 
-  Finally, the commutative diagram
-  \[
-    \begin{tikzcd}
-      C \times A \ar[r, "i \times A"] \ar[d, "\fput (i \times A)", swap] & S \times A \ar[d, "\fput"] \\
-      S \ar[r, equal] \ar[d, "{[j,\fget]}", swap] & S \ar[d, "{[\id_S, \fget]}"]  \\
-      C \times A \ar[r, "i \times A", swap] & S \times A
-    \end{tikzcd}
-  \]
-  is a witness that $\rep{\fput (i \times A)}{[j,\fget]} = \rep{\fput}{[\id_S, \fget]}$ as elements of $\Optic_\M(S, A)$.
-\end{proof}
-
-%\todo{There may be something generalisable here with ``monoidal factorisation systems''}
+  Finally, the coend relation gives that \[\rep{[j,\fget]}{\fput (i \times A)} = \rep{(i \times A)[j,\fget]}{\fput} = \rep{[\id_S, \fget]}{\fput}\] as elements of $\Optic_\M(S, A)$.
+\end{proof}
 
@@
 
-The following is then exactly the dual of Proposition~\ref{prop-OpticImpliesLensLaws}.
-\begin{proposition}\label{prop-OpticImpliesPrismLaws}
+The following is then exactly the dual of Proposition~\ref{prop:lawful-lens-laws}.
+\begin{proposition}\label{prop:lawful-prism-laws}
   If $p : S \hto A$ is a prism then the associated $\fmatching$ and $\freview$ functions satisfy the concrete prism laws. \qed
@@
 \begin{proof}
-  \[ \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S) \]
-  specialises in this case to just
+$\Twoptic_\M(S, A)$ specialises in this case to just
   \[ \C(S, A) \times \C(A, A) \times \C(A, S) \]
@@
 \end{align*}
+
+In the Haskell \lenslib{} library, the map $\C(A, A) \to \C(S,S)$ corresponding to a setter is called $\fover$: we think of a setter as allowing us to apply a morphism $A \to A$ over some parts of $S$.
+Tracing through the isomorphisms, the optic corresponding to $\fover$ is $\rep{}{}$.
+
+The laws for setters are a kind of functoriality:
+
+\begin{proposition}
+A setter $p : S \hto A$ is lawful iff
+\begin{align*}
+\fover(\id_A) &= \id_S \\
+\fover(f)\fover(g)&= \fover(fg)
+\end{align*}
+\end{proposition}
+\begin{proof}
+The key is concretely describing $\Twoptic_{[\C, \C]}(S, A)$ isomorphically as \[ \Set( \C(A, A) \times \C(A, A), \C(S, S) ).\] We leave the verification that the conditions are equivalent to the reader.
+\todo{Worth actually writing this out?}
+%Because a concrete setter is a function in $\Set$, it is enough to verify the equations pointwise. 
+\end{proof}
 
@@
 
-In the Haskell \lenslib{} library, the map $\C(A, A) \to \C(S,S)$ corresponding to a setter is called $\fover$: we think of a setter as allowing us to apply a function $A \to A$ over some parts of $S$.
-
-The laws for setters are a kind of functoriality:
-
-\begin{proposition}
-A setter $p : S \hto A$ is lawful iff
-\begin{align*}
-\fover(\id_A) &= \id_S \\
-\fover(f)\fover(g)&= \fover(fg)
-\end{align*}
-\end{proposition}
-\begin{proof}
-\todo{Worth writing out the rest?}
-\end{proof}
-
-\todo{This section might also work just with monoidal closed? I don't see where cartesianness was used.}
+%\todo{This section might also work just with monoidal closed? I don't see where cartesianness was used.}
 
 \subsection{Traversals}
-In this section we work in the case $\C = \Set$. \todo{explain the point of traversals}
-
+In this section we work in the case $\C = \Set$.
+Traversals allow us to traverse through a data structure, accumulating applicative (or monadic) actions as we go.
 We begin by reviewing the defnitions of applicative and traversable functors~\cite{AnInvestigationOfTheLawsOfTraversals}.
@@
 It is known that traversable functors correspond to coalgebras for a particular parameterised comonad.
-See~\cite{AlgebrasForParameterisedMonads} for the relevant definitions of parameterised monads and algebras.
+See~{\cite[Definition 4.1, 4.2]{SecondOrderFunctionals}}, also~\cite{AlgebrasForParameterisedMonads} for the relevant definitions of parameterised comonads and coalgebras.
 
@@
   \begin{align*}
-    \mathsf{mono} : \D \times \D^\op \times \Optic_{[\D, \C]} \to \Optic_\otimes
-  \end{align*}
-  that sends an object $(D, D') \in \D \times \D^\op$ and optic $\rep{l}{r} : (F, F') \hto (G, G')$ in $\Optic_{[\D, \C]}$ to the optic $\rep{l_D}{r_{D'}} : (FD, F'D') \hto (GD, G'D')$ in $\Optic_\M$.
+    \mathsf{mono} : \D \times \D^\op \times \Optic_{[\D, \C]} \to \Optic_\C
+  \end{align*}
+  that sends an object $(D, D') \in \D \times \D^\op$ and optic $\rep{l}{r} : (F, F') \hto (G, G')$ in $\Optic_{[\D, \C]}$ to the optic $\rep{l_D}{r_{D'}} : (FD, F'D') \hto (GD, G'D')$ in $\Optic_\C$.
 For fixed $(D, D) \in \D \times \D^\op$, this functor preserves lawfulness.
@@
 \begin{proof}
-  On an object $(D, D') \in \D \times \D^\op$, this is essentially the same as Proposition~\ref{prop:change-of-action} but with different functors on each side of the lens: the evaluation-at-$D$ functor $[\D, \C] \to \C$ on the left and evaluation-at-$D'$ on the right.
-
-  Given a morphism $(f, g) : (D_1, D'_1) \to (D_2, D'_2) \in \D \times \D^\op$ and an object $(F, F') \in \Optic_{[\D, \C]}$, there is an induced lens $\iota(Ff, F'g) : (FD_1, F'D'_1) \hto (FD_2, F'D'_2)$.
+  On an object $(D, D') \in \D \times \D^\op$, that we get a functor $\Optic_{[\D, \C]} \to \Optic_\C$ is essentially the same proof as Proposition~\ref{prop:change-of-action} but with different functors on each side of the lens: the evaluation-at-$D$ functor $[\D, \C] \to \C$ on the left and evaluation-at-$D'$ on the right.
+
+  For functoriality in $\D \times \D^\op$, given $(f, g) : (D_1, D'_1) \to (D_2, D'_2) \in \D \times \D^\op$ and an object $(F, F') \in \Optic_{[\D, \C]}$, there is an induced lens $\iota(Ff, F'g) : (FD_1, F'D'_1) \hto (FD_2, F'D'_2)$.
 Bifunctoriality of $\mathsf{mono}$ is ensured by the naturality of each $l$ and $r$ in the morphisms of $\Optic_{[\D, \C]}$.
@@
 
-\begin{remark}\label{remark:four-parameters}
-\todo{Talk about how the four `parameters' to $\Optic$ is not the same thing as the four parameters to Haskell lenses}
-\end{remark}
+%\begin{remark}\label{remark:four-parameters}
+%We note here that Haskell lenses 
+%\end{remark}
 
@@
 \begin{proof}
-  Let $\overrightarrow{(-)} : \C(A \otimes B, C) \to \C(A, \homC(B, C)) : \overleftarrow{(-)}$ denote the homset bijection, so $\coev_{A, B} = \overrightarrow{\id_{A \otimes B}}$ and $\ev_{A, B} = \overleftarrow{\id_{\homC(A, B)}}$.
+  Let \[\overrightarrow{(-)} : \C(A \otimes B, C) \to \C(A, \homC(B, C)) : \overleftarrow{(-)}\] denote the homset bijection, so 
+  \begin{align*}
+    \coev_{A, B} &:= \overrightarrow{\id_{A \otimes B}} \\
+    \ev_{A, B} &:= \overleftarrow{\id_{\homC(A, B)}}
+  \end{align*}
 
@@
   \begin{align*}
-    & \int^{M_1, M_2 \in \C} \C(S, M_1 \otimes A) \times \C(M_1 \otimes A, M_2 \otimes A) \times \C(M_2 \otimes A, S) \\
+  \Twoptic_\otimes(S, A)
+    &= \int^{M_1, M_2 \in \C} \C(S, M_1 \otimes A) \times \C(M_1 \otimes A, M_2 \otimes A) \times \C(M_2 \otimes A, S) \\
     &\cong \int^{M_1, M_2 \in \C} \C(S, M_1 \otimes A) \times \C(M_1, \homC(A, M_2 \otimes A)) \times \C(M_2, \homC(A, S)) \\
@@
 
-The \mintinline{haskell}{Getter}s and \mintinline{haskell}{Review}s of the Haskell library, where an optic $(S, S') \hto (A, A')$ corresponds simply to a morphism $S \to A$ or $A' \to S'$ respectively.
-These do fit into the coend formalism, with a slight modification.
+We finish with some almost-examples of optic variants, the \mintinline{haskell}{Getter}s and \mintinline{haskell}{Review}s of the Haskell library, where an optic $(S, S') \hto (A, A')$ corresponds simply to a morphism $S \to A$ or $A' \to S'$ respectively.
+These can fit into the coend formalism, with a slight modification.
 
@@
 We lose, of course, the ability to talk about lawful optics.
-To encode \mintinline{haskell}{Getter}s or \mintinline{haskell}{Review}s, we then set $\C_2$ or $\C_1$ to be the codiscrete category $\C_\mathsf{codisc}$ with the same set of objects as $\C$, so that all homsets are the one element set.
-In this way we indeed get a category $\Getter$ that is isomorphic to $\C$.
+To encode \mintinline{haskell}{Getter}s and \mintinline{haskell}{Review}s, we then set $\C_2$ or $\C_1$ to be the codiscrete category $\C_\mathsf{codisc}$, i.e.
+the category with the same set of objects as $\C$ but with all homsets the singleton set.
+In this way we indeed get a category $\Getter$ that is isomorphic to $\C$:
 \begin{align*}
@@
 
-Finally, we encode $\Fold$s, which in $\Set$ are functions $S \to \mathrm{List}\,A$. The key is that the $\mathrm{List}$ functor is the terminal $\Traversable$ \todo{ref}, so we have isomorphisms
+Finally, we can also encode \mintinline{haskell}{Fold}s, which in $\Set$ correspond to functions $S \to \mathrm{List}\,A$.
+The key is that the $\mathrm{List}$ functor is the terminal $\Traversable$, so we have isomorphisms
 \begin{align*}
@@
 
-There is a corresponding notion of Tambara module for a profunctor between two different categories.
-A profunctor $P : \C^\op \times \C_\mathsf{codisc}$ essentially ignores its covariant argument; this explains the appearance of a \mintinline{haskell}{RightPhantom} typeclass or equivalent in many profunctor optic libraries.
-
 \subsection{Further Examples}
-\todo{I probably don't have the standing to get away with saying} The dedicated reader may enjoy re-deriving the concrete representation and laws for the following optic varieties:
+The dedicated reader may enjoy deriving the concrete representation and laws for the following optic varieties:
 
@@
 
-%\item \emph{Functor Optics} \todo{todo}
-
-\item \emph{Monad Transformer Optics} \cite{MonadTransformerLensesTalk} were considered by Edward Kmett  as a method for embedding pieces of a monad transformer stack into the whole.
-There is some debate about the correct categorical description of monad transformers~\cite{MonadTransformersAsMonoidTransformers, CalculatingMonadTransformersCategoryTheory}, so we do not attempt to say anything precise, but the perspective given here could help in a couple of ways.
-
-Kmett considers optics for the operation of composing two monad transformers.
-The primary test-case was to embed \mintinline{haskell}{ReaderT} actions into \mintinline{haskell}{StateT} actions, but from the constant-complement perspective, this is impossible: \mintinline{haskell}{StateT} does not factor as the composite of \mintinline{haskell}{ReaderT} with some other monad transformer.
-In this setting the constant-complement laws may be asking too much, the optic laws in this paper may give the correct notion of lawfulness for monad transformers.
-
-Also, instead of considering optics within a category of monad transformers, we could instead look at optics for the action of monad transformers on monads.
-One can indeed define an optic $\mintinline{haskell}{State} \hto \mintinline{haskell}{Reader}$ that uses residual $\mintinline{haskell}{StateT}$.
-Whether this is lawful or useful is not clear!
+\item \emph{Adjunction Lenses}: For a category with finite products $\C$ and a monoidal adjunction $F \dashv U$, with $F : \C \to \D$ and $U : \D \to \C$.
+If $U$ is strong monoidal then $\D$ acts on $\C$ by $D \cdot A := D \times A$; as an example consider the free-forgetful adjunction between sets and monoids.
+Concrete optics for this action are given pairs in
+\[ \C(S, A) \times \C(UFS \times A', S') \]
+\todo{This example is a bit dumb, delete?}
 \end{itemize}
@@
 %
-%   For the forward direction, as in Proposition \ref{prop-onthenose} we induct on a zigzag \[(l, r) = (l_1, r_1) \leftrightsquigarrow \dots \leftrightsquigarrow (l_n, r_n) = (l', r'),\] where each pair $(l_i, r_i)$ has residual $M_i$.
+%   For the forward direction, as in Proposition \ref{prop:onthenose} we induct on a zigzag \[(l, r) = (l_1, r_1) \leftrightsquigarrow \dots \leftrightsquigarrow (l_n, r_n) = (l', r'),\] where each pair $(l_i, r_i)$ has residual $M_i$.
 As a base case, we can take the identity $\id_M : M \to M = M_1$.
@@
 
+\begin{remark}
+We do not explore this further in the current note, but there is a notion of Tambara module structure for profunctors between two different categories.
+This allows us to re-derive the profunctor encoding for degenerate optics.
+For example, in the case of \mintinline{haskell}{Getter}s, a profunctor $P : \C^\op \times \C_\mathsf{codisc}$ essentially ignores its covariant argument.
+This is captured exactly by the `\mintinline{haskell}{RightPhantom}' typeclass or its equivalent in profunctor optic libraries.
+\end{remark}
+
 There is an evident forgetful functor $U : \Tamb(\M) \to \Prof(\C, \C)$ that is strong monoidal. This forgetful functor has both a left and right adjoint; important for us is the left adjoint:
@@
 
-\begin{proposition}[Profunctor Optics are Optics]\label{prop-profunctor-optics-are-optics}
+\begin{proposition}[Profunctor Optics are Optics]\label{prop:profunctor-optics-are-optics}
   \begin{align*}
@@
 
-There is yet another isomorphic description of optics, which may be an unexplored avenue for generalisation.
+There is yet another isomorphic description of optics, which is an unexplored avenue for generalisation:
 
@@
 % \begin{proof}
-%   Let $\langle l, r \rangle$ be a representative for $p$ in $\Optic_\M(S,A)$ via the isomorphism of Proposition \ref{prop-profunctor-optics-are-optics}, so that
+%   Let $\langle l, r \rangle$ be a representative for $p$ in $\Optic_\M(S,A)$ via the isomorphism of Proposition \ref{prop:profunctor-optics-are-optics}, so that
 %   \begin{align*}
@@
 
-\section{Future work}
+\section{Future Work}
+
+There are many avenues for exploration! Here we include some speculation.
 
 \subsection{Indexed Optics}
-
-\todo{Make sure I cite~\cite{IndexedOpticsPost}}
-
-Suppose $\C$ is cartesian closed.
+As mentioned in the discussion on degenerate optics, there ought to be a generalisation of the $\Optic$ category such that the $l$ and $r$ sides lie in two different categories $\C_1$ and $\C_2$, bridged by an action of $\M$ on each.
+As well as giving a principled home to degenerate optics, this also allows us to describe \emph{indexed optics} categorically.
+
+The most interesting example is \emph{indexed traversals}, which, for example, allow access to the indices of the entries of a list as it is being traversed.
+
+We first need to define indexed traversals. Unfortunately this has many moving parts!
 
 \begin{proposition}
-The assignment $FX \mapsto (T\homC(I, F X))$ is a lax monoidal action of $\App$ on $\C$.
-\end{proposition}
-\begin{proof}
-\todo{todo}
-\end{proof}
+The assignment $F \cdot X \mapsto F \Set(I, X)$ is a lax monoidal action of $\App$ on $\Set$.
+\end{proposition}
+Call this the $I$-indexed action of $\App$ on $\Set$.
 
 \begin{definition}
-A \emph{traversable functor indexed by $I$} is a functor $T : \C \to \C$ equipped with a distributive law $\delta_F : T(\homC(I, F-)) \to FT$ for $T$ between the $I$-indexed action of $\App$ on $\C$ and the action of $\App$ on $\C$ by evaluation.
+A \emph{traversable functor indexed by $I$} is a functor $T : \Set \to \Set$ equipped with a distributive law $\delta_F : T(\Set(I, F-)) \to FT$ for $T$ between the $I$-indexed action of $\App$ on $\Set$ and the action of $\App$ on $\Set$ by evaluation.
 \end{definition}
@@
 \begin{definition}
-The category of \emph{indexed traversable functors} $\IdxTraversable$ has as objects pairs $(T, I)$, where $I \in \C$ and $T : \C \to \C$ is a traversable functor indexed by $I$.
+The category of \emph{indexed traversable functors} $\IdxTraversable$ has as objects pairs $(T, I)$, where $I \in \Set$ and $T : \Set \to \Set$ is a traversable functor indexed by $I$.
 A morphism $(T, I) \to (T', I')$ is a natural transformation $\alpha : T \to T'$ and morphism (note the direction!) $i : I' \to I$, such that $\alpha$ commutes with the distributive laws on both traversable functors, using $i$ to mediate between the index objects.
@@
 \begin{proposition}
-$\IdxTraversable$ acts on $\C \times \C$ by $(T, I) \cdot (A, R) \mapsto (TA, \homC(I, R))$.
-\end{proposition}
-\begin{proof}
-\todo{todo}
-\end{proof}
-
-\subsection{Mixed Optics}
-\todo{This hopefully will handle degenerate optics and indexed optics in a uniform way}
-
-\subsection{Monotone Optics???}
+$\IdxTraversable$ acts on $\C \times \C$ by $(T, I) \cdot (A, R) \mapsto (TA, \homC(I, R))$ and on $\C$ simply by $(T, I) \cdot A \mapsto TA$.
+\end{proposition}
+
+The idea for this action comes from \cite{IndexedOpticsPost}.
+
+\begin{conjecture}
+The category of indexed traversals corresponds to the category of mixed optics with the action of $\IdxTraversable$ on $\C \times \C$ on the left and $\C$ on the right.
+\end{conjecture}
+
+The obstacle to a good theory of mixed optics is finding the right notion of lawfulness.
+Specifically, profunctors $\C_1 \hto \C_2$ don't compose, so we cannot sensibly talk about comonoid objects in $\Prof(\C_1, \C_2)$.
+Here, techniques from \cite{MonadsNeedNotBeEndofunctors} may assist in providing a monoidal structure on $\Prof(\C_1, \C_2)$.
+
+\subsection{Monotonic Lenses}
+In the bidirectional transformation community, the $\fput\fput$ law is often considered too strong.
+In particular we have seen that in $\Set$, together with the other laws, it implies that $\fget$ must be a projection from a product.
+
+To overcome this, we work in $\Cat$, so that the objects under consideration have internal morphisms that we think of as updates.
+We modify $\fput$ so that instead of accepting an entire $A$ to overwrite the original in $S$ with, it requires a morphism in $A$ of the form $\fget(s) \to a'$.
+In this way we are restricted in what updates we may perform.
+This intuition is captured in the following definition:
+
+\begin{definition}[{\cite[Definition 4.1]{LensesFibrationsAndUniversalTranslations}}]
+A \emph{c-lens} $S \hto A$ in $\Cat$ is a pair of functors 
+\begin{align*}
+\fget &: S \to A \\
+\fput &: (\fget \downarrow \id_{A}) \to S
+\end{align*}
+such that a version of the three lens laws hold, where $(\fget \downarrow \id_{A})$ denotes the comma category construction. 
+\end{definition}
+
+We can rewrite this in a form that gives hope for a correspondence with some optic category:
+
+\todo{I don't know if this is known:}
+\begin{theorem}
+The data of a c-lens $S \hto A$ corresponds to a functor \[ S \to \int \Cat ((- / A), S) \] where $(-/A)$ denotes the slice category and $\int$ denotes (confusingly!) the Grothendieck construction.
+
+Furthermore, a c-lens lawful iff it is a coalgebra for the comonad of the adjunction
+\[
+\begin{tikzcd}[column sep = large]
+{[A, \Cat]} \ar[r, bend left, "\int"] \ar[r, phantom, "\bot" pos = 0.4] & \Cat \ar[l, bend left, "{X \mapsto [- \downarrow \id_A, X]}" below]
+\end{tikzcd}
+\]
+\qed
+\end{theorem}
+
+It is not clear whether there is an action on $\Cat$ that generates this description as its concrete optics. The location for an $A'$ to appear is missing! We remain optimistic:
+
+\begin{conjecture}
+c-lenses are lawful optics for some action on $\Cat$.
+\end{conjecture}
+
+\subsection{Functor and Monad Transformer Lenses} 
+These were considered by Edward Kmett~\cite{MonadTransformerLensesTalk}  as a method for embedding pieces of a monad transformer stack into the whole.
+There is some debate about the correct categorical description of monad transformers~\cite{MonadTransformersAsMonoidTransformers, CalculatingMonadTransformersCategoryTheory}, so we do not attempt to say anything precise, but the perspective given here could help in a couple of ways.
+
+Kmett considers optics for the operation of composing two monad transformers.
+The primary test-case was to embed \mintinline{haskell}{ReaderT} actions into \mintinline{haskell}{StateT} actions, but from the constant-complement perspective, this is impossible: \mintinline{haskell}{StateT} does not factor as the composite of \mintinline{haskell}{ReaderT} with some other monad transformer.
+In this setting the constant-complement laws may be asking too much, the optic laws given here might be the correct notion of lawfulness for monad transformers.
+
+Also, instead of considering optics within a category of monad transformers, we could instead look at optics for the action of monad transformers on monads.
+One can indeed define an optic $\mintinline{haskell}{State} \hto \mintinline{haskell}{Reader}$ that uses residual $\mintinline{haskell}{StateT}$.
+Whether this is lawful or useful is not clear!
 

### 2018-07-10 paper.tex
More quibbles

@@
 \usepackage{cite}
+\usepackage{multicol}
 
@@
 For a pair of maps $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\rep{l}{r} : (S, S') \hto (A, A')$ for their image in $\Optic_\otimes((S, S'), (A, A'))$, and say that $M$ is the residual for this representative.
-Optics will always be written with a crossed arrow $\hto$, to distinguish them from morphisms of $\C$.
+Optics will always be written with a crossed arrow $\hto$ to distinguish them from morphisms of $\C$.
+
+\begin{example}
+  For any three objects $M, A, A' \in \C$, there is the \emph{tautological} optic \[t_{M,A} : (M \otimes A, M \otimes A') \hto (A, A')\] given by $\rep{\id_{M \otimes A}}{\id_{M \otimes A'}}$.
+\end{example}
 
@@
 \end{remark}
-
-\begin{example}
-  For any three objects $M, A, A' \in \C$, there is the \emph{tautological} optic \[t_{M,A} : (M \otimes A, M \otimes A') \hto (A, A')\] which is given by $\rep{\id_{M \otimes A}}{\id_{M \otimes A}}$.
-\end{example}
 
@@
 
-If $\C$ is a category with finite products, then $\Lens = \Optic_\times$ is exactly the category of lenses described in the introduction.
-That optics correspond to pairs of $\fget$ and $\fput$ functions is shown via the following isomorphisms:
+\begin{remark}
+If $\C$ is a category with finite products, then $\Lens = \Optic_\times$ is exactly the category of lenses described in the introduction, so long as we restrict to optics of the form $(S, S) \hto (A, A)$.
+We see that optics correspond to pairs of $\fget$ and $\fput$ functions via the following isomorphisms:
 \begin{align*}
@@
 (Of course, there is only one possible way such a collection of concrete maps could be composed!)
+\end{remark}
 
@@
 This definition of teleological category differs from the original one, in that the duality switches the order of the tensor product.
-We do this so that compact closed category are teleological, but the bookkeeping becomes more confusing.
+We do this so that compact closed categories are teleological, but the bookkeeping does admittedly become more confusing.
 \end{remark}
@@
 \begin{definition}
-  A \emph{teleological functor} $F : \C \to \D$ is a symmetric monoidal functor that restricts to a functor $F_d : \C_d \to \D_d$ on the dualisable subcategories, commutes with the duality and such that the counits are preserved:
+  A \emph{teleological functor} $F : \C \to \D$ is a symmetric monoidal functor that restricts to a functor $F_d : \C_d \to \D_d$ on the dualisable subcategories, commutes with the duality via a monoidal natural isomorphism $d_X : F(X^*) \to (FX)^*$, and such that the counits are preserved:
+  \[
+   \begin{tikzcd}[column sep = large]
+    F(X \otimes X^*) \ar[r, "\phi_{X, X^*}"]  \ar[d, "F\varepsilon_X", swap] & FX \otimes F(X^*) \ar[r, "FX \otimes d_X"] & FX \otimes (FX)^* \ar[d, "\varepsilon_{FX}"] \\
+    FI \ar[rr, "\phi", swap] & & I
+  \end{tikzcd}
+  \]
+
+  A \emph{teleological natural transformation} $\alpha : F \Rightarrow G$ is a monoidal natural transformation whose components are all dualisable and that is additionally compatible with the dualisation:
   \[
   \begin{tikzcd}
-    F(X \otimes X^*) \ar[r, "\phi_{X, X^*}"]  \ar[d, "F\varepsilon_X", swap] & FX \otimes FX^* \ar[d, "\varepsilon_{FX}"] \\
-    FI \ar[r, "\phi", swap] & I
+    (FX)^* \ar[r, "\cong"]  \ar[d, "(\alpha_X)^*", swap] & F(X^*) \ar[d, "\alpha_{X^*}"] \\
+    (GX)^* \ar[r, "\cong", swap] & G(X^*)
   \end{tikzcd}
@@
 
-%\begin{definition}
-%  A \emph{teleological natural transformation} $\alpha : F \Rightarrow G$ is a monoidal natural transformation that is additionally compatible with the dualisation:
-%  \[
-%  \begin{tikzcd}
-%    (FX)^* \ar[r, "\cong"]  \ar[d, "(\alpha_X)^*", swap] & F(X^*) \ar[d, "\alpha_{X^*}"] \\
-%    (GX)^* \ar[r, "\cong", swap] & G(X^*)
-%  \end{tikzcd}
-%  \]
-%  whenever $\alpha_X$ is dualisable. \todo{Does adding this condition make sense?}
-%\end{definition}
-
-Together we have $\Tele$, the subcategory of $\SymmMonCat$ given by teleological categories and teleological functors.
-There are evident functors $U : \Tele \to \SymmMonCat$ and ${(-)}_d : \Tele \to \SymmMonCat$, that take a teleological category to its underlying symmetric monoidal category and subcategory of dualisable morphisms respectively.
+Together we have $\Tele$, the sub-2-category of $\SymmMonCat$ given by teleological categories, teleological functors and teleological natural transformations.
+There are evident strict 2-functors $U : \Tele \to \SymmMonCat$ and ${(-)}_d : \Tele \to \SymmMonCat$, that take a teleological category to its underlying symmetric monoidal category and subcategory of dualisable morphisms respectively.
 
@@
 For all symmetric monoidal functors $F : \C \to \T_d$, there exists a teleological functor $K : \Optic_\otimes \to \T$, unique up to teleological natural isomorphism with the property $Kj \cong F$.
+  Furthermore, $\Optic : \SymmMonCat \to \Tele$ is left biadjoint to the underlying dualisable morphisms functor ${(-)}_d : \Tele \to \SymmMonCat$.
 \end{theorem}
 \begin{proof}
+  \todo{Notes: I think uniqueness is easy but I don't know how best to phrase it.
+I might instead be able to do something 1-categorical, so having the property $Kj = F$ strictly.
+This would possibly be easier but would involve using strict monoidal functors everywhere that strictly preserve duals, and having $I^* = I$.
+This is true for $\Optic$, but is that actually what we want in general?
+The teleological category definition is so contrived I can probably just make it whatever I need it to be, but that's a bit unsatisfying.}
+
   We begin by constructing $K$.
-Note that any $(S, S')$ in $\Optic_\otimes$ can be written as $j(S) \switched {j(S')}^*$, so on objects define $K(S, S') = FS \otimes {(FS')}^*$.
+Note that any $(S, S')$ in $\Optic_\otimes$ can be written as $j(S) \switched {j(S')}^*$, so we define $K(S, S') = FS \otimes {(FS')}^*$.
 Suppose $\rep{l}{r} : (S, S') \hto (A, A')$ is an optic.
@@
   \end{align*}
-  So up to isomorphism we are forced to define
+  So in order for $Kj \cong F$ to hold, we define
   \begin{align*}
@@
 \end{itemize}
-\end{proof}
-
-\begin{theorem}
-$\Optic : \SymmMonCat \to \Tele$ is left biadjoint to the underlying dualisable morphisms functor ${(-)}_d : \Tele \to \SymmMonCat$
-\end{theorem}
-\begin{proof}
-\todo{figure out exactly what else needs proving}
-\end{proof}
+
+To conclude biadjointness it remains to show that for any symmetric monoidal category $\C$ and teleological category $\T$, restriction along $j : \C \to \Optic_\C$ defines an equivalence of categories \[\Tele(\Optic_\C, \T) \simeq \SymmMonCat(\C, \T_d).
+\]
+The restriction of a functor along $j$ indeed has its image in the subcategory $\T_d$, as by definition $j(f) = \iota(f, I)$ is dualisable.
+And given two teleological functors $K, L : \Optic_\C \to \T$, the whiskering of a teleological natural transformation $\alpha : K \Rightarrow L$ by $j$ is a well defined natural transformation $\beta : K j \Rightarrow L j$ in $\SymmMonCat(\C, \T_d)$ as the components of teleological natural transformations must be dualisable.
+
+We provide an inverse to this whiskering operation as follows.
+If $\beta : K j \Rightarrow L j$ is a monoidal natural transformation, define $\alpha : K \Rightarrow L$ to be the natural transformation with components:
+\begin{align*}
+K(S, S') = K(j(S) \switched {j(S')}^*) \xrightarrow{\phi} Kj(S) \otimes K({j(S')}^*) \xrightarrow{\beta_S \otimes \beta_{S'}^*} Lj(S) \otimes L({j(S')}^*) \xrightarrow{\phi^{-1}} L(j(S) \switched {j(S')}^*) = L(S, S')
+\end{align*}
+\todo{Not quite right, we should be using $d_X$} We leave showing that this is an inverse to the reader.
+\end{proof}
+
+\begin{remark}
+The above theorem and its proof have much in common with \cite[Proposition 5.2]{JoyalStreetVerity}, which gave a similar universal property for their $\mathrm{Int}$ construction on traced monoidal categories.
+\end{remark}
 
@@
 
-Without loss of generality, we just check the case of $\repthree{l;\phi_S}{c}{r} = \repthree{l}{\phi_S ; c}{r}$:
+Without loss of generality, we just check the case of $\repthree{l;\phi_S}{c}{r} = \repthree{l}{\phi_S ; c}{r}$. (The right entry is identical in all expressions, so we omit it.)
 \begin{align*}
@@
 &= \twice(\rep{(l \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B');(r \otimes r')}) \\
-&=\repthree{(l \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B);(r \otimes r');(l \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B);(r \otimes r')} \\
-&= \repthree{(l \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B);(rl \otimes r'l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B);(r \otimes r')} \\
-&= \repthree{(l \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B);(\id_{M \otimes A} \otimes \id_{N \otimes B});(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B);(r \otimes r')} \\
-&= \repthree{(l \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B);(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B);(r \otimes r')} \\
-&= \repthree{(l \otimes l');(M \otimes s_{A,N} \otimes B)}{\id_{M \otimes N \otimes A \otimes B}}{(M \otimes s_{A,N} \otimes B);(r \otimes r')} \\
+&=\repthree{\dots}{(M \otimes s_{A,N} \otimes B);(r \otimes r');(l \otimes l');(M \otimes s_{A,N} \otimes B)}{\dots} \\
+&= \repthree{\dots}{(M \otimes s_{A,N} \otimes B);(rl \otimes r'l');(M \otimes s_{A,N} \otimes B)}{\dots} \\
+&= \repthree{\dots}{(M \otimes s_{A,N} \otimes B);(\id_{M \otimes A} \otimes \id_{N \otimes B});(M \otimes s_{A,N} \otimes B)}{\dots} \\
+&= \repthree{\dots}{(M \otimes s_{A,N} \otimes B);(M \otimes s_{A,N} \otimes B)}{\dots} \\
+&= \repthree{\dots}{\id_{M \otimes N \otimes A \otimes B}}{\dots} \\
 &= \once(\rep{l}{r} \otimes \rep{l'}{r'})
@@
 \begin{proposition}
-If $T : \C \to \C$ is a strong monad then $\C$ acts on $\C_T$ by $X \cdot Y \mapsto X \otimes Y$.
+If $T : \C \to \C$ is a strong monad then $\C$ acts on $\C_T$ by $X \cdot Y := X \otimes Y$.
 \end{proposition}
@@
 
-A morphism $f : A \to B$ in $\C$ induces a natural transformation $A \otimes - \Rightarrow B \otimes -$ with components $A \otimes X \to T(B \otimes X)$ given by composing $A \otimes X \to B \otimes X$ with the unit of the monad.
+A morphism $f : A \to B$ in $\C$ induces a natural transformation $A \otimes - \Rightarrow B \otimes -$ of functors $\C_T \to \C_T$, with components $A \otimes X \to T(B \otimes X)$ given by composing $A \otimes X \to B \otimes X$ with the unit of the monad.
 Naturality follows by the naturality of the strength and the unit of $T$.
@@
 \end{proposition}
-  Or, if you prefer do-notation:
+  Or, if you prefer do-notation, the two laws are:
+\begin{multicols}{2}
 \begin{minted}{haskell}
@@
 return s
-
+\end{minted} 
+~\columnbreak
+\begin{minted}{haskell}
 do (c, a) <- munzip s
@@
 \end{minted}
+\end{multicols}
+
 \begin{proof}
@@
 %
+%The simplest nontrivial monad we could try is the maybe monad.
+%
 %\begin{definition}
@@
 %\begin{align*}
-%P X = X \sqcup 1
+%T X = X \sqcup 1
 %\end{align*}
-%\todo{todo: define its unit, multiplication and strength}
+%with unit $\eta_X : X \to X \sqcup 1$ the inclusion, multiplication $\mu_X : (X \sqcup 1) \sqcup 1 \to X \sqcup 1$ given by the fold map $1 \sqcup 1 \to 1$, and strength $\theta_{A, B}$ given by the composite
+%\[
+%A \times (B \sqcup 1) \to (A \times B) \sqcup (A \times 1) \to (A \times B) \sqcup 1
+%\]
+%using the unique map $A \times 1 \to 1$.
 %\end{definition}
+%
 
@@
 \end{minted}
-is lawful iff:
+is lawful iff: \\
+\begin{minipage}{\textwidth}
+\begin{multicols}{3}
 \begin{minted}{haskell}
@@
 return s
-
+\end{minted}
+~\columnbreak
+\begin{minted}{haskell}
 do s' <- mput s q a
@@
 return a
-
-let (s', q') = runState (mput s q1 a1) q2
+\end{minted}
+~\columnbreak
+\begin{minted}{haskell}
+let (s', q') 
+  = runState (mput s q1 a1) q2
 in mput s' q' a2
@@
 \end{minted}
+\end{multicols}
+\end{minipage}
 \end{proposition}
@@
 \begin{remark}
-Of course, this notion of effectful lens may not be useful!
+Of course, this notion of effectful lens may not be useful at all!
 It is hard to get intuition for the meaning of the laws.
 The $\fget\fput$ law here appears easier to satisfy than the $\mathsf{MGetPut_0}$ law of~\cite{ReflectionsOnMonadicLenses}, as $\mput$ is given access to the original state.
-On the other hand, our $\fput\fget$ law seems difficult to satisfy: it must hold no matter what auxiliary state is provided.
+On the other hand, our $\fput\fget$ law seems very difficult to satisfy: no matter what auxiliary state is provided, putting then getting must leave the state unchanged.
 \end{remark}
@@
 \end{align*}
-The category $\mathsf{Aff}$ acts on $\C$ by $(P, Q) \cdot A = P \sqcup (Q \times A)$. A concrete representation of the optics for this action is \[\C(S, S' \sqcup (\homC(A', S') \times A)).\]
+The category $\mathsf{Aff}$ acts on $\C$ by $(P, Q) \cdot A = P \sqcup (Q \times A)$, in fact, $\mathsf{Aff}$ is cooked up exactly as the closure of the actions $- \times A$ and $- \sqcup A$ under composition.
+A concrete representation of the optics for this action is \[\C(S, S' \sqcup (\homC(A', S') \times A)).\]
 
@@
 \item \emph{Adjunction Lenses}: For a category with finite products $\C$ and a monoidal adjunction $F \dashv U$, with $F : \C \to \D$ and $U : \D \to \C$.
-If $U$ is strong monoidal then $\D$ acts on $\C$ by $D \cdot A := D \times A$; as an example consider the free-forgetful adjunction between sets and monoids.
+If $U$ is strong monoidal then $\D$ acts on $\C$ by $UD \cdot A := D \times A$; as an example consider the free-forgetful adjunction between sets and monoids.
 Concrete optics for this action are given pairs in
@@
 \subsection{Learners}
+A recent paper \cite{BackpropAsFunctor} in applied category theory describes a compositional approach to machine learning, with a category whose morphisms describe learning algorithms.
+
+\begin{definition}[{\cite[Definition 2.1]{BackpropAsFunctor}}]
+For $A$ and $B$ sets, a \emph{learner} $A \hto B$ is a tuple $(P, I, U, r)$ where $P$ is a set, and $I$, $U$, and $r$ are functions of shape:
+\begin{align*}
+I &: P \times A \to B \\
+U &: P \times A \times B \to P \\
+r &: P \times A \times B \to A
+\end{align*}
+\end{definition}
+To form a category, it is required to consider learners up to an equivalence relation on the sets $P$.
+But there may be a slicker method: note that the data of a learner is describing an element of the coend
+\begin{align*}
+\int^{P, Q \in \Set} \Set(P \times A, Q \times B) \times \Set(Q \times B, P \times A) 
+\end{align*}
+via the isomorphisms
+\begin{align*}
+&\int^{P, Q \in \Set} \Set(P \times A, Q \times B) \times \Set(Q \times B, P \times A) \\
+&\cong \int^{P, Q \in \Set} \Set(P \times A, Q) \times \Set(P \times A, B) \times \Set(Q \times B, P \times A) \\
+&\cong \int^{P \in \Set} \Set(P \times A, B) \times \Set(P \times A \times B, P \times A) \\
+&\cong \int^{P \in \Set} \Set(P \times A, B) \times \Set(P \times A \times B, P) \times \Set(P \times A \times B, A)
+\end{align*}
+Composition of learners can be defined analogously to composition for optics.
+This perspective explains the minor fussing around required in dealing with equivalence classes of learners, and suggests a generalisation to other monoidal settings.
 

### 2018-07-11 paper.tex
.

@@
 \end{itemize}
-We will call such lenses \emph{lawful}. (The names of the laws make more sense when the equations are written with composition in diagrammatic order!)
+We will call such lenses \emph{lawful}.
+(The names of the laws make more sense when the equations are written with composition in diagrammatic order!) Lenses form a category with a subcategory of lawful lenses.
 
@@
 We begin in Section~\ref{sec:optics} by defining the \emph{category of optics} in a sufficiently general way to encompass almost all the optic variants in use in the wild, using lenses as a running example.
-Section~\ref{sec:lawful-optics} defines the equivalent of the lens laws for a generic category of optics.
+Section~\ref{sec:lawful-optics} defines the equivalent of the lens laws for a general category of optics.
 Then in Section~\ref{sec:examples} we see that these generic definitions specialise correctly to the other basic varieties of optic, including giving the correct laws.
@@
 
+Our definition of optic has as domain and codomain \emph{pairs} of objects of $\C$.
+This generality is important for the applications to game theory; for ordinary lenses we restrict our attention to pairs with the same object in both entries.
+
 \begin{remark}
@@
 \end{example}
-
-\begin{remark}
-A common use of the coend relation is to introduce or cancel isomorphisms. Given $l : S \to M \otimes A$ and $r : M \otimes A \to S$, for any isomorphism $f : M \to N$ we have
-\begin{align*}
-\rep{l}{r} = \rep{(f^{-1} \otimes A)(f \otimes A)l}{r} = \rep{(f \otimes A)l}{r(f^{-1} \otimes A)}
-\end{align*}
-\end{remark}
 
@@
   \end{center}
-  We will therefore omit the vertical cut point between $l$ and $r$ in subsequent diagrams; any choice yields a representative of same optic.
+  We will therefore omit the vertical cut point between $l$ and $r$ in most subsequent diagrams; any choice yields a representative of same optic.
+\end{remark}
+
+\begin{remark}
+A common use of the coend relation is to introduce or cancel isomorphisms. Given $l : S \to M \otimes A$ and $r : M \otimes A \to S$, for any isomorphism $f : M \to N$ we have
+\begin{align*}
+\rep{l}{r} = \rep{(f^{-1} \otimes A)(f \otimes A)l}{r} = \rep{(f \otimes A)l}{r(f^{-1} \otimes A)}
+\end{align*}
+Diagrammatically, this is the equality
+  \begin{center}
+    \input{diagrams/generic-optic.tikz}
+    \qquad \raisebox{1.5cm}{$=$} \qquad
+    \input{diagrams/generic-optic-with-iso.tikz}
+  \end{center}
 \end{remark}
@@
 \end{align*}
-So by the universal property of coends, it suffices to construct natural maps
+So by the universal property of coends, it suffices to construct maps
 \begin{align*}
@@
 \end{align*}
-for each $M, N \in \C$. For this we use the composites
+natural in $M$ and $N$. For these we use the composites
 \begin{align*}
@@
   \input{diagrams/generic-optic-noline.tikz}
-  \qquad\raisebox{1.5cm}{$\circ$}\qquad
+  \quad\raisebox{1.5cm}{$\circ$}\qquad
   \input{diagrams/generic-optic2-noline.tikz} \\
@@
 We should be careful to only discuss $\Optic$ categories where we know that the coends exist by some other means, e.g., by exhibiting an isomorphism with some other set.
-For all of the examples given later, we provide such an isomorphism.
+For all of the examples we give, we provide such an isomorphism.
 \end{remark}
@@
 \begin{remark}
-If $\C$ is a category with finite products, then $\Lens = \Optic_\times$ is exactly the category of lenses described in the introduction, so long as we restrict to optics of the form $(S, S) \hto (A, A)$.
+If $\C$ is a category with finite products, then $\Lens = \Optic_\times$ is exactly the category of lenses described in the introduction, so long as we restrict to optics of shape $(S, S) \hto (A, A)$.
 We see that optics correspond to pairs of $\fget$ and $\fput$ functions via the following isomorphisms:
@@
 Using the isomorphism in both directions, we leave it to the reader to verify that composition in $\Optic_\times$ corresponds to ordinary composition of concrete lenses.
-(Of course, there is only one possible way such a collection of concrete maps could be composed!)
+(Of course, there is only one possible way such a collection of morphisms could be sensibly composed!)
 \end{remark}
@@
   Note that because $\iota(S, S') = (S, S')$, required equations for $\iota$ to be a monoidal functor hold by definition (although we don't yet know that $\Optic_\otimes$ is monoidal).
-The pentagon and triangle equations then hold in $\Optic_\otimes$, as they are the image of the same axioms in $\C \times \C^\op$ under $\iota$.
+The pentagon and triangle equations then hold in $\Optic_\otimes$, as they are the image of the same diagrams in $\C \times \C^\op$ under $\iota$.
 The only remaining thing to verify is that these structure maps are natural in $\Optic_\otimes$.
@@
 \begin{remark}
-  In the Haskell \lenslib{} library, the monoidal product on optics is denoted ``\texttt{alongside}'' for the product and ``\texttt{without}'' for the coproduct.
+  In the Haskell \lenslib{} library, the monoidal product on optics is denoted ``\mintinline{haskell}{alongside}'' for the product and ``\mintinline{haskell}{without}'' for the coproduct.
 \end{remark}
@@
 
-In particular, for any $S \in \C$, the identity $\id_S$ yields an optic $c_S = \rep{\rho_S^{-1}}{\rho_S} : (S, S) \hto (I, I)$, that we will call the connector:
+In particular, for any $S \in \C$, the identity $\id_S$ yields an optic $c_S = \rep{\rho_S^{-1}}{\rho_S} : (S, S) \hto (I, I)$, that we will call the \emph{connector}:
 \begin{center}
@@
 \end{align*}
-The axioms follow by lifting the axioms for $F$. More difficult is verifying naturality: \todo{naturality}
+The axioms follow by lifting the axioms for $F$. More difficult is verifying naturality: \todo{todo!}
 \end{proof}
@@
 
-Our goal now is to establish the universal property of $\Optic_\otimes$. The following proposition gives that an optic decomposes in a canonical way:
+Our goal now is to establish the universal property of $\Optic_\otimes$. The following proposition gives that every optic decomposes in a canonical way:
 
@@
 In our primary example of an optic variant, lenses in $\Set$, this does indeed correspond to the concrete lens laws.
-However, this fact relies on some extra structure possessed by $\Set$, the existence of pullbacks, and that all objects other than the empty set have a global element.
+However, this fact relies on some extra structure possessed by $\Set$: the existence of pullbacks, and that all objects other than the empty set have a global element.
 
@@
 
+The optic laws only make sense for optics of the form $p : (S,S) \hto (A, A)$.
+In this section we will abbreviate $\Optic_\M((S, S), (A, A))$ as $\Optic_\M(S, A)$ and $p : (S, S) \hto (A, A)$ as $p : S \hto A$.
+
 \begin{remark}
@@
 
-\todo{Should I switch everything else to use diagrammatic order?}
-
-  Also, in this section we focus only on optics of the form $p : (S,S) \hto (A, A)$.
-For brevity we will abbreviate $\Optic_\M((S, S), (A, A))$ as $\Optic_\M(S, A)$ and $p : (S, S) \hto (A, A)$ as $p : S \hto A$.
+\todo{Should I switch the entire paper into using diagrammatic order?}
 \end{remark}
@@
 
-We will see that in all the other common examples of optics, this also specialises to the expected laws for that variant of optic.
+We will see that in all the other common examples of optics, this also gives the expected laws for that variant of optic.
 
@@
 
-The requirement that $\once(p) = \twice(p)$ is mysterious, but there are sufficient conditions that are easier to verify.
+We end with some commentary on the optic laws. The requirement that $\once(p) = \twice(p)$ is mysterious, but there are sufficient conditions that are easier to verify.
 
@@
 This is especially useful when devising new optic variants, as we do later.
-
-We begin with the most common kinds of optic before moving to more exotic possibilities.
-
-\todo{There is a common pattern in some of these examples, where the evaluation-at-$A$ functor $-A : \M \to \C$ has a left or right adjoint. Is it worth abstracting this out?}
 
@@
 
+\subsection{Coalgebraic Optics}\label{sec:coalgebraic}
+
+There is a common pattern in some of the examples to follow: the evaluation-at-$A$ functor $-A : \M \to \C$ has a right adjoint, say $R_A : \C \to \M$.
+
+In this case we can always eliminate the coend and find a concrete description of an optic:
+\begin{align*}
+&\int^{F \in \M} \C(S, F\cdot A) \times \C(F\cdot A', S') \\
+&\cong \int^{F \in \M} \C(S, F \cdot A) \times \M(F, R_{A'} S') \\
+&\cong \C(S,  (R_{A'} S') \cdot A)
+\end{align*}
+
+\begin{theorem}\label{thm:optics-are-coalgebras}
+An concrete optic $p : S \to  (R_{A} S) \cdot A$ is lawful iff it is a coalgebra for the comonad $X \mapsto (R_{A} X) \cdot A$.
+\end{theorem}
+\begin{proof}
+\todo{todo!}
+\end{proof}
+
+\begin{remark}
+This theorem is a generalisation of \cite[Section 3.2]{RelatingAlgebraicAndCoalgebraic} for lenses.
+\end{remark}
+
 \subsection{Setters}\label{sec:setters}
@@
 To devise the concrete form of a setter, we use the following proposition.
-This is a generalisation of~\cite[Proposition 2.2]{SecondOrderFunctionals}, and helps to explain why the store comonad is so important.
+This is a generalisation of~\cite[Proposition 2.2]{SecondOrderFunctionals}, and helps to explain why the store comonad is so important in the theory of lenses.
 
 \begin{proposition}
-If $\C$ is cotensored over $\Set$ then the evaluation-at-$A$ functor $-A : [\C, \C] \to \C$ has a right adjoint given by $S \mapsto S^{\C(-, A)}$.
-
-If $\C$ is tensored over $\Set$ then $-A : [\C, \C] \to \C$ has a left adjoint given by $S \mapsto \C(A, -) \cdot S$.
+If $\C$ is powered over $\Set$ then the evaluation-at-$A$ functor $-A : [\C, \C] \to \C$ has a right adjoint given by $S \mapsto S^{\C(-, A)}$.
+
+If $\C$ is copowered over $\Set$ then $-A : [\C, \C] \to \C$ has a left adjoint given by $S \mapsto \C(A, -) \cdot S$.
 \end{proposition}
@@
 
-We can use either of the above adjunctions to describe setters concretely:
+Recall that any category with coproducts is copowered over $\Set$ and any category with products is powered over $\Set$.
+
+We could immediately use the previous section to give a coalgebraic description of setters and their laws, but with a little more manipulation we get a form that looks more familiar:
 \begin{align*}
@@
 In the Haskell \lenslib{} library, the map $\C(A, A) \to \C(S,S)$ corresponding to a setter is called $\fover$: we think of a setter as allowing us to apply a morphism $A \to A$ over some parts of $S$.
-Tracing through the isomorphisms, the optic corresponding to $\fover$ is $\rep{}{}$.
-
-The laws for setters are a kind of functoriality:
+Tracing through the isomorphisms, the optic corresponding to $\fover$ is $\rep{l}{r}$ where $l : S \to \C(A, A) \cdot S$ is the inclusion with the identity morphism $\id_A$ and $r : \C(A, A') \cdot S \to S'$ is the transpose of $\fover$ along the adjunction defining the copower.
+
+The laws for setters in this form are a kind of functoriality:
 
@@
 \begin{proof}
-The key is concretely describing $\Twoptic_{[\C, \C]}(S, A)$ isomorphically as \[ \Set( \C(A, A) \times \C(A, A), \C(S, S) ).\] We leave the verification that the conditions are equivalent to the reader.
+The key is concretely describing $\Twoptic_{[\C, \C]}(S, A)$ as \[ \Set( \C(A, A) \times \C(A, A), \C(S, S) ).\] We leave the verification that the conditions are equivalent to the reader.
 \todo{Worth actually writing this out?}
@@
 
+\todo{The rest of this section should probably be rewritten to use the free applicative functor instead of the confusing parameterised comonad business}
+
 It is known that traversable functors correspond to coalgebras for a particular parameterised comonad.
-See~{\cite[Definition 4.1, 4.2]{SecondOrderFunctionals}}, also~\cite{AlgebrasForParameterisedMonads} for the relevant definitions of parameterised comonads and coalgebras.
+See~{\cite[Definitions 4.1 and 4.2]{SecondOrderFunctionals}}, also~\cite{AlgebrasForParameterisedMonads} for the relevant definitions of parameterised comonads and coalgebras.
 
@@
 % Experts will recognise $UR^*_{-, -}$ as the free applicative functor \cite{FreeApplicativeFunctors} on the functor $R_{X,Y} Z = X \times Y \to Z$.
-
-\begin{remark}
-In~\cite[Section 2.3]{ProfunctorOptics}, it is claimed that a traversal $S \hto A$ exhibits an isomorphism \[S \cong \Sigma_n A^n \times \Set(A^n,S).\] This appears to be a misreading of~\cite[Proposition 5.4]{SecondOrderFunctionals}.
-\end{remark}
-
-The language of coalgebras now allows us to characterise traversals.
 
@@
 \begin{align*}
-L_T : \Set^\op \times \E &\to \Set \\
+L_T : \Set \times \E &\to \Set \\
 (X, (F, f)) &\mapsto FX \\
@@
 
-We then reach the same characterisation of traversals as~\cite{ProfunctorOptics}:
+We can then use the coalgebraic pattern from earlier to reach the same concrete description of traversals as found in~\cite{ProfunctorOptics}.
 \begin{align*}
@@
 
-\todo{laws}
+The concrete laws for this representation are the coalgebra laws.
+These laws, however, are not the ones usually presented for traversals.
+Instead, versions of the profunctor laws are used, see Section~\ref{sec:profunctor-optics}.
 
 \begin{remark}
-A careful analysis would be needed to describe traversals in some other category, in particular, the description of $UR^*$ does not make sense if $\C$ is not locally cartesian closed.
+In~\cite[Section 2.3]{ProfunctorOptics}, it is further claimed that a traversal $S \hto A$ exhibits an isomorphism $S \cong \Sigma_n A^n \times \Set(A^n,S)$.
+This cannot possibly be true---consider the traversable functor $X \times -$.
+The claim appears to be a misreading of~\cite[Proposition 5.4]{SecondOrderFunctionals}.
 \end{remark}
+
+%\begin{remark}
+%A careful analysis would be needed to describe traversals in some other category, in particular, the description of $UR^*$ does not make sense if $\C$ is not locally cartesian closed.
+%\end{remark}
 
@@
     \cong \;& (U \Phi_\M E_A)(S,S) \\
-    = \;&\int^{M \in \M} \C(S, MA) \times \C(MA, S) \\
     = \;&\Optic_\M(S, A)
@@
 What makes these particular optic variants work is that the Tambara module that characterises them, $\Pastro_\M E_A$, can be written in the form \mintinline{haskell}{a -> f a} with \mintinline{haskell}{f} an instance of the corresponding typeclass.
-Therefore, no expressive power is lost by restricting an optic to operate only on functions \mintinline{haskell}{a -> f a}, as the concrete description of the optic can be extracted from its value on that Tambara module.
+Specifically, these are the optics that admit a coalgebraic description; see Section~\ref{sec:coalgebraic}.
+
+Therefore, no expressive power is lost by restricting an optic to operate only on functions of shape \mintinline{haskell}{a -> f a}, as the entire concrete description of the optic can be extracted from its value on that Tambara module.
 The same is not true for other optic variants, and indeed in the Haskell \lenslib{} library, \mintinline{haskell}{Prism}s and \mintinline{haskell}{Review}s use the profunctor encoding.
 
-The coend description can clarify which optic variants are likely to admit a van Laarhoven encoding.
-In each the above examples, the evaluation-at-$A$ functor $-A : \M \to \C$ has a right adjoint $R_A : \C \to \M$, so
-\begin{align*}
-\int^{F \in \M} \C(S, FA) \times \C(FA, S)
-&\cong \int^{F \in \M} \C(S, FA) \times \M(F, R_A S) \\
-&\cong \C(S,  (R_A S) \cdot A)
-\end{align*}
-The hope is then that one can devise a convenient typeclass that characterises functors of the form $R_A S$.
-
 \section{Future Work}
 
-There are many avenues for exploration! Here we include some speculation.
+There are many avenues for exploration! Here we make some speculations.
 
@@
 
-\subsection{Symmetric Optics}
-
 \subsection{Learners}
@@
 
-\todo{Make sure I'm not using any $\Set$-only results too generally in the traversal section}
-
 \todo{Consistently use $\Rightarrow$ for natural transformations everywhere?}

### 2018-07-16 paper.tex
Show that iota lifts natural isomorphisms

@@
 This category was first defined in~\cite[Section 6]{Doubles} as the `double' of a monoidal category.
-There it was used for an entirely different purpose---to investigate the relationship between Tambara modules and the `center' of a monoidal category.
+There it was used for a completely different purpose---to investigate the relationship between Tambara modules and the `center' of a monoidal category.
 Our definition is identical, other than flipping the direction of the morphisms to match the existing work on lenses, and restricting our attention to the unenriched setting.
@@
 \begin{proposition}
-  There is a functor $\iota : \C \times \C^\op \to \Optic_\otimes$, which is given on objects by $\iota(S, S') = (S, S')$ and for a morphism $(f, g) : (S, S') \to (A, A')$ by $\iota(f, g) = \rep{\lambda_A^{-1} f}{g \lambda_{A'}}$.
+  There is a functor $\iota : \C \times \C^\op \to \Optic_\otimes$, which on objects is given by $\iota(S, S') = (S, S')$ and on a morphism $(f, g) : (S, S') \to (A, A')$ by $\iota(f, g) = \rep{\lambda_A^{-1} f}{g \lambda_{A'}}$.
 \end{proposition}
@@
 
+\begin{proposition}\label{prop:change-of-action-monoidal}
+  A monoidal functor $F : \C \to \D$ induces a functor $\Optic(F) : \Optic_\C \to \Optic_\D$.
+On objects this is $\Optic(F)(S, S') = (FS, FS')$, and on a morphism $\rep{l}{r} : (S, S') \to (A, A')$, is
+  \begin{align*}
+    \Optic(F)(\rep{l}{r}) := \rep{\phi^{-1}_{M,A} (Fl)}{(Fr) \phi_{M,A'}}
+  \end{align*}
+  where $\phi_{M,A} : FM \otimes FA \to F(M \otimes A)$ is the structure map of the monoidal functor. Graphically:
+  \begin{center}
+    \input{diagrams/induced-by-functor.tikz}
+  \end{center}
+\end{proposition}
+\begin{proof}
+
+  This preserves identities:
+  \begin{align*}
+  \Optic(F)(\id_{(S, S')})
+  &= \Optic(F)(\rep{\lambda^{-1}_S}{\lambda_{S'}}) \\
+  &= \rep{\phi^{-1}_{I,S} (F\lambda^{-1}_S)}{(F\lambda_{S'}) \phi_{I,S'}} \\
+  &= \rep{(\phi^{-1} \otimes S) \phi^{-1}_{I,S} (F\lambda^{-1}_S)}{(F\lambda_{S'}) \phi_{I,S'}(\phi \otimes S) } \\
+  &= \rep{(\phi^{-1} \otimes S) \phi^{-1}_{I,S} (F\lambda^{-1}_S)}{(F\lambda_{S'}) \phi_{I,S'}(\phi \otimes S) } \\
+  &= \rep{\lambda^{-1}_{FS}}{\lambda_{FS'}} \\
+  &= \id_{(FS, FS')}
+  \end{align*}
+  And given two optics $\rep{l}{r} : (S, S') \hto (A, A')$ and $\rep{l'}{r'} : (R, R') \hto (S, S')$ with residuals $M$ and $M'$, it preserves composition:
+\begin{align*}
+&\Optic(F)(\rep{l}{r} \circ \rep{l'}{r'})  \\
+&= \Optic(F)(\rep{(M' \otimes l)l'}{r'(M' \otimes r)}) \\
+&= \rep{\phi^{-1}_{M' \otimes M,A} F((M' \otimes l)l')}{F(r'(M' \otimes r)) \phi_{M' \otimes M,A'}} \\
+&= \rep{\phi^{-1}_{M' \otimes M,A} F(M' \otimes l)(Fl')}{(Fr') F(M' \otimes r) \phi_{M' \otimes M,A'}} \\
+&= \rep{(\phi^{-1}_{M', M} \otimes A)\phi^{-1}_{M' \otimes M,A} F(M' \otimes l)(Fl')}{(Fr') F(M' \otimes r) \phi_{M' \otimes M,A'}(\phi_{M', M} \otimes A)} \\
+&= \rep{(FM' \otimes \phi^{-1}_{M,A})\phi^{-1}_{M',M \otimes A}(F(M' \otimes l)) (Fl')}{(Fr') (F(M' \otimes r)) \phi_{M',M \otimes A'}  (FM' \otimes \phi_{M,A'})} \\
+&= \rep{(FM' \otimes \phi^{-1}_{M,A})(FM' \otimes Fl)\phi^{-1}_{M',S} (Fl')}{(Fr') \phi_{M',S'} (FM' \otimes Fr) (FM' \otimes \phi_{M,A'})} \\
+&= \rep{(FM' \otimes \phi^{-1}_{M,A} (Fl))(\phi^{-1}_{M',S} (Fl'))}{((Fr') \phi_{M',S'})(FM' \otimes (Fr) \phi_{M,A'})} \\
+&= \rep{\phi^{-1}_{M,A} (Fl)}{(Fr) \phi_{M,A'}} \circ \rep{\phi^{-1}_{M',S} (Fl')}{(Fr') \phi_{M',S'}} \\
+&= \Optic(F)(\rep{l}{r}) \circ \Optic(F)(\rep{l'}{r'})
+\end{align*}
+The critical move is adding the isomorphism $(\phi_{M', M} \otimes A)$ to both sides of the coend, so that the hexagon axiom for $F$ can be applied.
+\end{proof}
+
+\begin{proposition}
+$\iota : \C \times \C^\op \to \Optic_\otimes$ ``lifts natural isomorphisms'', in the following sense.
+Given monoidal functors $F, G : \C \to \D$ and a monoidal natural isomorphism $\alpha : F \Rightarrow G$, there is an induced natural isomorphism $\Optic(\alpha) : \Optic(F) \Rightarrow \Optic(G)$ with components:
+\begin{align*}
+\Optic(\alpha)_{(S, S')} &: (FS, FS') \to (GS, GS') \\
+\Optic(\alpha)_{(S, S')} &:= \iota(\alpha_{S}, \alpha^{-1}_{S'})
+\end{align*}
+\end{proposition}
+\begin{proof}
+Suppose $\phi$ and $\psi$ are the structure maps for $F$ and $G$ respectively.
+We just have to show naturality, i.e.
+that for $p : (S, S') \hto (A, A')$ in $\D$, the equation \[\Optic(\alpha)_{(A, A')} \circ \Optic(F)(p) = \Optic(G)(p) \circ \Optic(\alpha)_{(S, S')}\] holds.
+On the left we have:
+  \begin{center}
+    \input{diagrams/iota-lift-step1.tikz}
+  \end{center}
+  Use the coend relation to place an $\alpha$ on either side:
+  \begin{center}
+    \input{diagrams/iota-lift-step2.tikz}
+  \end{center}
+  And then monoidality of $\alpha$ to commute it past $\phi$.
+  \begin{center}
+    \input{diagrams/iota-lift-step3.tikz}
+  \end{center}
+  Finally, $\alpha$ pushes through $F l$ and $F r$ by naturality.
+  \begin{center}
+    \input{diagrams/iota-lift-step4.tikz}
+  \end{center}
+  This is the diagram for $\Optic(G)(p) \circ \Optic(\alpha)_{(S, S')}$.
+\end{proof}
+
 \begin{theorem}
@@
   These two diagrams are equivalent: We can use the naturality of the symmetry morphism to push $l_2$ and $r_2$ past the crossing to be next to $l_1$ and $r_1$ respectively.
-This creates two extra twists that can be cancelled in the center of the diagram (implicitly using the coend relation).
+This creates two extra twists that can be cancelled in the center of the diagram (via the coend relation).
 
@@
 The pentagon and triangle equations then hold in $\Optic_\otimes$, as they are the image of the same diagrams in $\C \times \C^\op$ under $\iota$.
-The only remaining thing to verify is that these structure maps are natural in $\Optic_\otimes$.
-
-  Let us check that $\alpha_{(R, R'), (S, S'), (T, T')}$ is natural in $(R, R')$. Suppose $\rep{l}{r} : (Q, Q') \hto (R, R')$ is an optic with residual $M$.
-  \begin{align*}
-    &\alpha_{(R, R'), (S, S'), (T, T')} \circ (f \otimes (S, S')) \otimes (T, T') \\
-    &= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1})  \circ (\rep{l}{r} \otimes (S, S')) \otimes (T, T') \\
-    &= \rep{\lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T}}{\alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'}}  \circ \rep{(l \otimes S) \otimes T}{(r \otimes S') \otimes T'} \\
-    &= \rep{(M \otimes \lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T})((l \otimes S) \otimes T)}{((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} )} \\
-    &=\rep{(M \otimes \alpha_{R,S,T})((l \otimes S) \otimes T)}{((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} )} \\
-    &= \rep{(l \otimes (S \otimes T))\alpha_{Q,S,T}}{\alpha_{Q',S',T'}^{-1}(r \otimes (S' \otimes T'))} \\
-    &= \rep{(I \otimes l \otimes (S \otimes T)) \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}}{(I \times r \otimes (S' \otimes T')) \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')}} \\
-    &= \rep{l \otimes (S \otimes T)}{r \otimes (S' \otimes T')} \circ \rep{\lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}}{\alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')} } \\
-    &= \rep{l}{r} \otimes ((S, S') \otimes (T, T')) \circ \iota(\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}) \\
-    &= f \otimes ((S, S') \otimes (T, T')) \circ \alpha_{(Q, Q'), (S, S'), (T, T')}
-  \end{align*}
-
-Naturality in the other variables is similar, as is the naturality of the unitors.
-  \todo{convert this to a string diagram?}
+The only remaining thing to verify is that these structure maps are natural in $\Optic_\otimes$, but this follows from the previous proposition.
+
+%  Let us check that $\alpha_{(R, R'), (S, S'), (T, T')}$ is natural in $(R, R')$. Suppose $\rep{l}{r} : (Q, Q') \hto (R, R')$ is an optic with residual $M$.
+%  \begin{align*}
+%    &\alpha_{(R, R'), (S, S'), (T, T')} \circ (f \otimes (S, S')) \otimes (T, T') \\
+%    &= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1})  \circ (\rep{l}{r} \otimes (S, S')) \otimes (T, T') \\
+%    &= \rep{\lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T}}{\alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'}}  \circ \rep{(l \otimes S) \otimes T}{(r \otimes S') \otimes T'} \\
+%    &= \rep{(M \otimes \lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T})((l \otimes S) \otimes T)}{((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} )} \\
+%    &=\rep{(M \otimes \alpha_{R,S,T})((l \otimes S) \otimes T)}{((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} )} \\
+%    &= \rep{(l \otimes (S \otimes T))\alpha_{Q,S,T}}{\alpha_{Q',S',T'}^{-1}(r \otimes (S' \otimes T'))} \\
+%    &= \rep{(I \otimes l \otimes (S \otimes T)) \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}}{(I \otimes r \otimes (S' \otimes T')) \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')}} \\
+%    &= \rep{l \otimes (S \otimes T)}{r \otimes (S' \otimes T')} \circ \rep{\lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}}{\alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')} } \\
+%    &= \rep{l}{r} \otimes ((S, S') \otimes (T, T')) \circ \iota(\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}) \\
+%    &= f \otimes ((S, S') \otimes (T, T')) \circ \alpha_{(Q, Q'), (S, S'), (T, T')}
+%  \end{align*}
+%
+%Naturality in the other variables is similar, as is the naturality of the unitors.
+%  \todo{convert this to a string diagram?}
 \end{proof}
@@
 \end{proof}
+
+\begin{proposition}\label{prop:change-of-action-monoidal}
+  For monoidal $F : \C \to \D$, the induced $\Optic(F) : \Optic_\C \to \Optic_\D$ is also monoidal.
+\end{proposition}
+\begin{proof}
+The structure morphisms for monoidality are given by lifting the structure morphisms for $F$:
+\begin{align*}
+\phi_{(S, S'), (T, T')} &:= \iota(\phi_{S, T}, \phi_{S', T'}) &&: F(S, S') \otimes F(T, T') \hto F((S, S') \otimes (T, T')) \\
+\phi &:= \iota(\phi, \phi) &&: (I, I) \hto F(I, I)
+\end{align*}
+The axioms follow by lifting the axioms for $F$. More difficult is verifying naturality: \todo{todo!}
+\end{proof}
+
+To summarise:
+
+\begin{proposition}\label{prop:optic-functor}
+  Collectively this operation defines a 2-functor \[\Optic : \SymmMonCat \to \SymmMonCat.\] \qed
+\end{proposition}
+\todo{Haven't actually checked natural transformations}
+\todo{Also we run into the large coend issue again, it's not defined on every symm mon cat.}
 
@@
 
-There is some further useful structure in $\Optic_\otimes$.
+Finally, there is a little we can say about maps out of and in to the monoidal unit. Such maps are typically called states and costates.
 \begin{proposition}\label{prop:costates}
@@
 \end{proof}
-
-\begin{proposition}\label{prop:change-of-action-monoidal}
-  A monoidal functor $F : \C \to \D$ induces a functor $\Optic(F) : \Optic_\C \to \Optic_\D$.
-\end{proposition}
-\begin{proof}
-  On objects this is simply $\Optic(F)(S, S') = (FS, FS')$. On a morphism $\rep{l}{r} : (S, S') \to (A, A')$, we define
-  \begin{align*}
-    \Optic(F)(\rep{l}{r}) := \rep{\phi^{-1}_{M,A} (Fl)}{(Fr) \phi_{M,A'}}
-  \end{align*}
-  where $\phi_{M,A} : FM \otimes FA \to F(M \otimes A)$ is the structure map of the monoidal functor.
-  This preserves identities:
-  \begin{align*}
-  \Optic(F)(\id_{(S, S')})
-  &= \Optic(F)(\rep{\lambda^{-1}_S}{\lambda_{S'}}) \\
-  &= \rep{\phi^{-1}_{I,S} (F\lambda^{-1}_S)}{(F\lambda_{S'}) \phi_{I,S'}} \\
-  &= \rep{(\phi^{-1} \otimes S) \phi^{-1}_{I,S} (F\lambda^{-1}_S)}{(F\lambda_{S'}) \phi_{I,S'}(\phi \otimes S) } \\
-  &= \rep{(\phi^{-1} \otimes S) \phi^{-1}_{I,S} (F\lambda^{-1}_S)}{(F\lambda_{S'}) \phi_{I,S'}(\phi \otimes S) } \\
-  &= \rep{\lambda^{-1}_{FS}}{\lambda_{FS'}} \\
-  &= \id_{(FS, FS')}
-  \end{align*}
-  And given two optics $\rep{l}{r} : (S, S') \hto (A, A')$ and $\rep{l'}{r'} : (R, R') \hto (S, S')$ with residuals $M$ and $M'$, it preserves composition:
-\begin{align*}
-&\Optic(F)(\rep{l}{r} \circ \rep{l'}{r'})  \\
-&= \Optic(F)(\rep{(M' \otimes l)l'}{r'(M' \otimes r)}) \\
-&= \rep{\phi^{-1}_{M' \otimes M,A} F((M' \otimes l)l')}{F(r'(M' \otimes r)) \phi_{M' \otimes M,A'}} \\
-&= \rep{\phi^{-1}_{M' \otimes M,A} F(M' \otimes l)(Fl')}{(Fr') F(M' \otimes r) \phi_{M' \otimes M,A'}} \\
-&= \rep{(\phi^{-1}_{M', M} \otimes A)\phi^{-1}_{M' \otimes M,A} F(M' \otimes l)(Fl')}{(Fr') F(M' \otimes r) \phi_{M' \otimes M,A'}(\phi_{M', M} \otimes A)} \\
-&= \rep{(FM' \otimes \phi^{-1}_{M,A})\phi^{-1}_{M',M \otimes A}(F(M' \otimes l)) (Fl')}{(Fr') (F(M' \otimes r)) \phi_{M',M \otimes A'}  (FM' \otimes \phi_{M,A'})} \\
-&= \rep{(FM' \otimes \phi^{-1}_{M,A})(FM' \otimes Fl)\phi^{-1}_{M',S} (Fl')}{(Fr') \phi_{M',S'} (FM' \otimes Fr) (FM' \otimes \phi_{M,A'})} \\
-&= \rep{(FM' \otimes \phi^{-1}_{M,A} (Fl))(\phi^{-1}_{M',S} (Fl'))}{((Fr') \phi_{M',S'})(FM' \otimes (Fr) \phi_{M,A'})} \\
-&= \rep{\phi^{-1}_{M,A} (Fl)}{(Fr) \phi_{M,A'}} \circ \rep{\phi^{-1}_{M',S} (Fl')}{(Fr') \phi_{M',S'}} \\
-&= \Optic(F)(\rep{l}{r}) \circ \Optic(F)(\rep{l'}{r'})
-\end{align*}
-The critical move is adding the isomorphism $(\phi_{M', M} \otimes A)$ to both sides of the coend, so that the hexagon axiom for $F$ can be applied.
-
-The structure morphisms for monoidality are given by lifting the structure morphisms for $F$:
-\begin{align*}
-\phi_{(S, S'), (T, T')} &:= \iota(\phi_{S, T}, \phi_{S', T'}) &&: F(S, S') \otimes F(T, T') \hto F((S, S') \otimes (T, T')) \\
-\phi &:= \iota(\phi, \phi) &&: (I, I) \hto F(I, I)
-\end{align*}
-The axioms follow by lifting the axioms for $F$. More difficult is verifying naturality: \todo{todo!}
-\end{proof}
-
-\begin{proposition}\label{prop:optic-functor}
-  Collectively this operation defines a 2-functor \[\Optic : \SymmMonCat \to \SymmMonCat.\] \qed
-\end{proposition}
-\todo{Haven't actually checked natural transformations}
-\todo{Also we run into the large coend issue again, it's not defined on every symm mon cat.}
 
@@
 
+%Ross Street:
+%More usually - . b has a right adjoint. This is the same as saying that the M-actegory
+%C is an M-category (hom enriched in M) which is tensored. So we have
+%
+%M(m, \hat{C}(b,a)) \cong C(m.b , a)
+
 \subsection{Setters}\label{sec:setters}
@@
 We cannot possibly use the three $\fput$/$\fget$ style lens laws in this setting as we lack projections, but using the same techniques as for cartesian lenses above we can devise some new ones:
+
+\todo{These are just the coalgebra laws (hopefully)}
 
@@
 The category $\mathsf{Aff}$ acts on $\C$ by $(P, Q) \cdot A = P \sqcup (Q \times A)$, in fact, $\mathsf{Aff}$ is cooked up exactly as the closure of the actions $- \times A$ and $- \sqcup A$ under composition.
-A concrete representation of the optics for this action is \[\C(S, S' \sqcup (\homC(A', S') \times A)).\]
+A concrete affine traversal is an element of \[\C(S, S' \sqcup (\homC(A', S') \times A)).\]
 
 Affine traversals are described in the folklore as pairs of maps $\C(S, A \sqcup S') \times \C(S\times A', S')$.
-Such a pair does determine an affine traversal, but in fact gives more information than is necessary: the right-hand map need not be defined at all $S$.
+Such a pair does determine an affine traversal, but gives more information than is necessary: the right-hand map need not be defined at all $S$.
 
@@
 \begin{conjecture}
-c-lenses are lawful optics for some action on $\Cat$.
+c-lenses are the lawful optics for some action on $\Cat$.
 \end{conjecture}

### 2018-07-16 paper.tex
Fill in coalgebra section

@@
 \DeclareMathOperator{\im}{im}
+\newcommand{\act}{\cdot}
 
@@
 This doesn't appear to follow purely from the concrete lens laws---an argument that a definition of lawfulness based on constant complements is not the correct generalisation.
+For completeness we include a proof in our notation.
 
@@
     \Optic_1((S, S'), (A, A')) &= \int^{M \in 1} \C(S, MA) \times \C(MA', S') \\
-                               &\cong \C(S, \star \cdot A) \times \C(\star \cdot A', S') \\
+                               &\cong \C(S, \star \act A) \times \C(\star \act A', S') \\
                                &\cong \C(S, A) \times \C(A', S')
@@
 
-There is a common pattern in some of the examples to follow: the evaluation-at-$A$ functor $-A : \M \to \C$ has a right adjoint, say $R_A : \C \to \M$.
+There is a common pattern in many of the examples to follow: for every object $A \in \C$, the evaluation-at-$A$ functor $-A : \M \to \C$ has a right adjoint, say $R_A : \C \to \M$.
+To fix notation, let \[\overrightarrow{(-)} : \C(F \act A, S) \to \M(F, R_{A} S) : \overleftarrow{(-)}\] denote the homset bijection, so the unit and counit are:
+  \begin{align*}
+  	\eta_F &: F \to R_A (F \act A) \\
+    \eta_F &:= \overrightarrow{\id_{F \act A}} \\
+    \varepsilon_{S} &: (R_A S) \cdot A \to S \\
+    \varepsilon_{S} &:= \overleftarrow{\id_{R_{A} S}}
+  \end{align*}
+
+\begin{remark}
+It is shown in~\cite[Section 6]{ANoteOnActions} that, at least in the case $\M$ is right closed, to give such an action is equivalent to giving a ``copowered $\M$-category $\C$''.
+\todo{Pointed out to me years ago when I emailed Ross Street, but I didn't understand what he was saying}
+\end{remark}
 
@@
 \begin{align*}
-&\int^{F \in \M} \C(S, F\cdot A) \times \C(F\cdot A', S') \\
-&\cong \int^{F \in \M} \C(S, F \cdot A) \times \M(F, R_{A'} S') \\
-&\cong \C(S,  (R_{A'} S') \cdot A)
-\end{align*}
+&\int^{F \in \M} \C(S, F\act A) \times \C(F\act A', S') \\
+&\cong \int^{F \in \M} \C(S, F \act A) \times \M(F, R_{A'} S') \\
+&\cong \C(S,  (R_{A'} S') \act A)
+\end{align*}
+A concrete optic is therefore a map $\funzip : S \to (R_{A'} S') \act A$.
+The above isomorphism sends $\funzip$ to the element $\rep{\funzip}{\varepsilon_{S'}}$.
+In the other direction, given $\rep{l}{r}$ we have $\funzip = (\overrightarrow{r} \otimes A)l$.
 
 \begin{theorem}\label{thm:optics-are-coalgebras}
-An concrete optic $p : S \to  (R_{A} S) \cdot A$ is lawful iff it is a coalgebra for the comonad $X \mapsto (R_{A} X) \cdot A$.
+An concrete optic $\funzip : S \to  (R_{A} S) \act A$ is lawful iff it is a coalgebra for the comonad $X \mapsto (R_{A} X) \act A$.
 \end{theorem}
 \begin{proof}
-\todo{todo!}
-\end{proof}
-
-\begin{remark}
-This theorem is a generalisation of \cite[Section 3.2]{RelatingAlgebraicAndCoalgebraic} for lenses.
-\end{remark}
-
-%Ross Street:
-%More usually - . b has a right adjoint. This is the same as saying that the M-actegory
-%C is an M-category (hom enriched in M) which is tensored. So we have
-%
-%M(m, \hat{C}(b,a)) \cong C(m.b , a)
+By adjointness and Yoneda reduction we have an isomorphism $\Phi : \Twoptic_\M(S, A) \to \C(S, R_A (R_A S \act A) \act A)$ given by
+\begin{align*}
+&\Twoptic_\M(S, A) \\
+&= \int^{M_1, M_2 \in \M} \C(S, M_1 \act A) \times \C(M_1 \act A, M_2 \act A) \times \C(M_2 \act A, S) \\
+&\cong \int^{M_1, M_2 \in \M} \C(S, M_1 \act A) \times \M(M_1, R_A (M_2 \act A)) \times \M(M_2, R_A S) \\
+&\cong \int^{M_1, M_2 \in \M} \C(S, M_1 \act A) \times \M(M_1, R_A (M_2 \act A)) \times \M(M_2, R_A S) \\
+&\cong \int^{M_1 \in \M} \C(S, M_1 \act A) \times \M(M_1, R_A (R_A S \act A)) \\
+&\cong \C(S, R_A (R_A S \act A) \act A)
+\end{align*}
+  which evaluated on an element $\repthree{l}{c}{r}$ is given by
+  \begin{align*}
+    \Phi(\repthree{l}{c}{r}) &= (\overrightarrow{(\overrightarrow{r} \act A)c} \act A)l
+  \end{align*}
+
+So now interpreting the optic laws, find
+\[\outside(\rep{\funzip}{\varepsilon_{S} }) = \varepsilon_{S} \; \funzip = \id_S \] is exactly the coalgebra unit law, and equality of
+  \begin{align*}
+    \Phi(\once(\rep{\funzip}{\varepsilon_S}))
+    &= \Phi(\repthree{\funzip}{\id_{(R_{A} S) \act A}}{\varepsilon_S }) \\
+    &= (\overrightarrow{(\overrightarrow{\varepsilon_S} \act A)\id_{(R_{A} S) \act A}} \act A)\funzip \\
+    &= (\overrightarrow{(\id_{R_A S} \act A)} \act A)\funzip \\
+    &= (\overrightarrow{\id_{R_A S \act A}} \act A)\funzip \\
+    &= (\eta_{R_A S} \act A) \funzip \\
+    \Phi(\twice(\rep{\funzip}{\varepsilon_S }))
+    &= \Phi(\repthree{\funzip}{\funzip \; \varepsilon_S}{\varepsilon_S }) \\
+    &= (\overrightarrow{(\overrightarrow{\varepsilon_S} \act A)(\funzip \; \varepsilon_S)} \act A)\funzip \\
+    &= (\overrightarrow{(\funzip \; \varepsilon_S)} \act A)\funzip \\
+    &= (R_A (\funzip) \act A)\funzip
+  \end{align*}
+is exactly the coalgebra multiplication law.
+\end{proof}
 
@@
 We leave it to the reader to verify there is a natural isomorphism \[\C(S, FA) \cong \Strong_\C(\homC(A, -) \times S, F),\] which we can use to describe optics for this action as elements of $\C(\homC(A, A'), \homC(S,S'))$.
-The use of strong functors here is due to the correspondence between tensorial strengths and ``$\C$-enrichments'' on a functor.
+%The use of strong functors here is due to the correspondence between tensorial strengths and ``$\C$-enrichments'' on a functor.
 \end{remark}
@@
 In this section we work in the case $\C = \Set$.
-Traversals allow us to traverse through a data structure, accumulating applicative (or monadic) actions as we go.
+Traversals allow us to traverse through a data structure, accumulating applicative actions as we go.
 We begin by reviewing the defnitions of applicative and traversable functors~\cite{AnInvestigationOfTheLawsOfTraversals}.
@@
 An \emph{applicative natural transformation} is one that is both monoidal and strong.
-Applicative functors and natural transformations form a monoidal category $\App$ under functor composition.
+Applicative functors and natural transformations form a monoidal category $\App$ with the tensor given by functor composition.
 \end{definition}
@@
 \begin{align*}
-\Optic_\Traversable((S, S'), (A, A')) &= \int^{F \in \Traversable} \Set(S, F A) \times \Set(F A', S') \\
-&\cong \int^{F \in \Traversable} \Set(S, F A) \times \Traversable(F, \Sigma_n {(-)}^n \times \Set(A'^n,S')) \\
-&\cong \Set(S, \Sigma_n A^n \times \Set(A'^n,S'))
+\Optic_\Traversable((S, S'), (A, A')) &\cong \Set(S, \Sigma_n A^n \times \Set(A'^n,S'))
 \end{align*}
@@
 
-\begin{remark}
-Traversable functors can be described as a particular class of polynomial functors known as finitary containers. It may be possible to generalise this to other classes of polynomial functors.
-\end{remark}
+%\begin{remark}
+%Traversable functors can be described as a particular class of polynomial functors known as finitary containers. It may be possible to generalise this to other classes of polynomial functors.
+%\end{remark}
 
@@
   \M \times [\D, \C] &\to [\D, \C] \\
-  (M, F) &\mapsto  M \cdot (F-)
+  (M, F) &\mapsto  M \act (F-)
 \end{align*}
@@
 
-If $\C$ is closed monoidal, but not necessarily cartesian, we can use the tensor-hom adjunction to eliminate the coend:
-
-\begin{align*}
-  \Optic_\otimes((S, S'), (A, A')) &= \int^{M \in \C} \C(S, M \otimes A) \times \C(M \otimes A', S') \\
-                                   &\cong \int^{M \in \C} \C(S, M \otimes A) \times \C(M, \homC(A',S')) \\
-                                   &\cong \C(S, \homC(A',S') \otimes A)
-\end{align*}
-where $\homC(A', S')$ denotes the internal hom. If $\C$ is cartesian, this is of course isomorphic to the pair of maps discussed earlier.
-
-A concrete linear lens is therefore a map $\funzip : S \to \homC(A',S') \otimes A$.
-The above isomorphism sends $\funzip$ to the element $\rep{\funzip}{\ev_{A', S'}}$, where $\ev_{A', S'} : \homC(A',S') \otimes A' \to S'$ is the evaluation map.
-In the other direction, given $\rep{l}{r}$ we have $\funzip = (\tilde r \otimes A)l$ where $\tilde r : M \to \homC(A', S')$ denotes the transpose of $r$.
-
-We cannot possibly use the three $\fput$/$\fget$ style lens laws in this setting as we lack projections, but using the same techniques as for cartesian lenses above we can devise some new ones:
-
-\todo{These are just the coalgebra laws (hopefully)}
+If $\C$ is closed monoidal but not necessarily cartesian, we can still define the category of \emph{linear lenses} to be $\Optic_\otimes$.
+The internal hom provides a right adjoint to the evaluation-at-$A$ functor, so we have immediately
+\begin{align*}
+  \Optic_\otimes((S, S'), (A, A')) &\cong \C(S, \homC(A',S') \otimes A)
+\end{align*}
+where $\homC(A', S')$ denotes the internal hom. If $\C$ is cartesian, this is of course isomorphic to the set of $(\fget, \fput)$ functions discussed earlier.
+
+We cannot possibly use the three $\fput$/$\fget$ style lens laws in this setting as we lack projections, but specialising the coalgebra laws gives us:
 
@@
   where \[ \funzip \circ - : \homC(A, S) \to \homC(A, \homC(A, S) \otimes A) \] denotes internal composition and \[\coev_{\homC(A, S), A} : \homC(A, S) \to \homC(A, \homC(A, S) \otimes A)\] is coevaluation.
-  \todo{I obviously need better names for the laws}
-\end{proposition}
-\begin{proof}
-  Let \[\overrightarrow{(-)} : \C(A \otimes B, C) \to \C(A, \homC(B, C)) : \overleftarrow{(-)}\] denote the homset bijection, so 
-  \begin{align*}
-    \coev_{A, B} &:= \overrightarrow{\id_{A \otimes B}} \\
-    \ev_{A, B} &:= \overleftarrow{\id_{\homC(A, B)}}
-  \end{align*}
-
-  We have an isomorphism:
-  \begin{align*}
-  \Twoptic_\otimes(S, A)
-    &= \int^{M_1, M_2 \in \C} \C(S, M_1 \otimes A) \times \C(M_1 \otimes A, M_2 \otimes A) \times \C(M_2 \otimes A, S) \\
-    &\cong \int^{M_1, M_2 \in \C} \C(S, M_1 \otimes A) \times \C(M_1, \homC(A, M_2 \otimes A)) \times \C(M_2, \homC(A, S)) \\
-    &\cong \int^{M_1 \in \C} \C(S, M_1 \otimes A) \times \C(M_1, \homC(A, \homC(A, S) \otimes A)) \\
-    &\cong \C(S, \homC(A, \homC(A, S) \otimes A) \otimes A)
-  \end{align*}
-  which evaluated on an element $\repthree{l}{c}{r}$ is given by
-  \begin{align*}
-    \Phi(\repthree{l}{c}{r}) &= (\overrightarrow{(\overrightarrow{r} \otimes A)c} \otimes A)l
-  \end{align*}
-  Now suppose we are given an optic $p$ whose corresponding element of $\conc_\otimes(S, A)$ is $\funzip$. Then \[\outside(\rep{\funzip}{\ev_{A, S} }) = \ev_{A, S} \; \funzip,\] giving the first law.
-
-  Now we evaluate $\Phi(\once(p))$ and $\Phi(\twice(p))$.
-  \begin{align*}
-    \Phi(\once(\rep{\funzip}{\ev_{A, S}}))
-    &= \Phi(\repthree{\funzip}{\id_{\homC(A,S) \otimes A}}{\ev_{A, S} }) \\
-    &= (\overrightarrow{(\overrightarrow{\ev_{A, S}} \otimes A)\id_{\homC(A,S) \otimes A}} \otimes A)\funzip \\
-    &= (\overrightarrow{(\id_{\homC(A, S)} \otimes A)} \otimes A)\funzip \\
-    &= (\coev_{\homC(A, S), A} \otimes A)\funzip \\
-    \Phi(\twice(\rep{\funzip}{\ev_{A, S} }))
-    &= \Phi(\repthree{\funzip}{\funzip \; \ev_{A, S}}{\ev_{A, S} }) \\
-    &= (\overrightarrow{(\overrightarrow{\ev_{A, S}} \otimes A)(\funzip \; \ev_{A, S})} \otimes A)\funzip \\
-    &= (\overrightarrow{(\funzip \; \ev_{A, S})} \otimes A)\funzip \\
-    &= ((\funzip \circ -) \otimes A)\funzip
-  \end{align*}
-  So indeed the optic is lawful iff the two concrete laws hold.
-\end{proof}
+  \todo{I obviously need better names for the laws} \qed
+\end{proposition}
+
+\begin{remark}
+We have essentially rederived the result given in \cite[Section 3.2]{RelatingAlgebraicAndCoalgebraic} for ordinary lenses, but we note that cartesianness was not required.
+\end{remark}
 
@@
 \begin{proposition}
-If $T : \C \to \C$ is a strong monad then $\C$ acts on $\C_T$ by $X \cdot Y := X \otimes Y$.
+If $T : \C \to \C$ is a strong monad then $\C$ acts on $\C_T$ by $X \act Y := X \otimes Y$.
 \end{proposition}
@@
 \item \emph{``Achromatic'' Lenses}~\cite[Section 5.2]{ProfunctorOpticsThesis} are lenses that also admit an operation $\fcreate : A \to S$.
-These are optics for the action of $\C$ on itself by $M \cdot A = (M \sqcup 1) \times A$, or equivalently, of the category of pointed objects of $\C$ on $\C$ by cartesian product.
+These are optics for the action of $\C$ on itself by $M \act A = (M \sqcup 1) \times A$, or equivalently, of the category of pointed objects of $\C$ on $\C$ by cartesian product.
 Concrete achromatic lenses $S \hto A$ are elements of the set \[\C(S, \homC(A', S') \sqcup 1) \times \C(S, A) \times \C(A', S').\]
@@
 %  \Optic((S, S'), (A, A'))
-%  &= \int^{M \in \C} \C(S, M \cdot A) \times \C(M \cdot A', S') \\
+%  &= \int^{M \in \C} \C(S, M \act A) \times \C(M \act A', S') \\
 %  &= \int^{M \in \C} \C(S, (M \sqcup 1) \times A) \times \C((M \sqcup 1) \times A', S') \\
@@
 \end{align*}
-The category $\mathsf{Aff}$ acts on $\C$ by $(P, Q) \cdot A = P \sqcup (Q \times A)$, in fact, $\mathsf{Aff}$ is cooked up exactly as the closure of the actions $- \times A$ and $- \sqcup A$ under composition.
+The category $\mathsf{Aff}$ acts on $\C$ by $(P, Q) \act A = P \sqcup (Q \times A)$, in fact, $\mathsf{Aff}$ is cooked up exactly as the closure of the actions $- \times A$ and $- \sqcup A$ under composition.
 A concrete affine traversal is an element of \[\C(S, S' \sqcup (\homC(A', S') \times A)).\]
@@
 %\begin{align*}
-%  (P', Q') \cdot (P, Q) \cdot A
-%  &= (P', Q') \cdot  (P \sqcup (Q \times A)) \\
+%  (P', Q') \act (P, Q) \act A
+%  &= (P', Q') \act  (P \sqcup (Q \times A)) \\
 %  &= P' \sqcup (Q' \times (P \sqcup (Q \times A))) \\
 %  &\cong P' \sqcup (Q' \times P) \sqcup (Q' \times Q \times A) \\
-%  &= (P' \sqcup (Q' \times P) , Q' \times Q) \cdot A \\
-%  &= ((P', Q') \otimes (P, Q)) \cdot A
+%  &= (P' \sqcup (Q' \times P) , Q' \times Q) \act A \\
+%  &= ((P', Q') \otimes (P, Q)) \act A
 %\end{align*}
 %\begin{remark}
-%  It is important here that the morphisms in $\mathsf{Aff}$ are only those that arise from pairs of morphisms $P \to P'$ and $Q \to Q'$, although in principle there may be other natural transformations between the corresponding functors $(P, Q) \cdot -$ and $(P', Q') \cdot -$.
+%  It is important here that the morphisms in $\mathsf{Aff}$ are only those that arise from pairs of morphisms $P \to P'$ and $Q \to Q'$, although in principle there may be other natural transformations between the corresponding functors $(P, Q) \act -$ and $(P', Q') \act -$.
 %\end{remark}
@@
 %  \Optic_{\mathsf{Aff}}((S, S'), (A, A'))
-%  &= \int^{M \in \mathsf{Aff}} \C(S, M \cdot A) \times \C(M \cdot A', S') \\
-%  &\cong \int^{P,Q \in \C} \C(S, (P,Q) \cdot A) \times \C((P,Q) \cdot A', S') \\
+%  &= \int^{M \in \mathsf{Aff}} \C(S, M \act A) \times \C(M \act A', S') \\
+%  &\cong \int^{P,Q \in \C} \C(S, (P,Q) \act A) \times \C((P,Q) \act A', S') \\
 %  &= \int^{P,Q \in \C} \C(S, P \sqcup (Q \times A)) \times \C(P \sqcup (Q \times A'), S') \\
@@
 \item \emph{Adjunction Lenses}: For a category with finite products $\C$ and a monoidal adjunction $F \dashv U$, with $F : \C \to \D$ and $U : \D \to \C$.
-If $U$ is strong monoidal then $\D$ acts on $\C$ by $UD \cdot A := D \times A$; as an example consider the free-forgetful adjunction between sets and monoids.
+If $U$ is strong monoidal then $\D$ acts on $\C$ by $UD \act A := D \times A$; as an example consider the free-forgetful adjunction between sets and monoids.
 Concrete optics for this action are given pairs in
@@
 \begin{proposition}
-The assignment $F \cdot X \mapsto F \Set(I, X)$ is a lax monoidal action of $\App$ on $\Set$.
+The assignment $F \act X \mapsto F \Set(I, X)$ is a lax monoidal action of $\App$ on $\Set$.
 \end{proposition}
@@
 \begin{proposition}
-$\IdxTraversable$ acts on $\C \times \C$ by $(T, I) \cdot (A, R) \mapsto (TA, \homC(I, R))$ and on $\C$ simply by $(T, I) \cdot A \mapsto TA$.
+$\IdxTraversable$ acts on $\C \times \C$ by $(T, I) \act (A, R) \mapsto (TA, \homC(I, R))$ and on $\C$ simply by $(T, I) \act A \mapsto TA$.
 \end{proposition}

### 2018-07-24 paper.tex
Start on a mixed optics section

@@
 \newcommand{\act}{\cdot}
+\newcommand{\codisc}{\mathsf{codisc}}
 
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:iota-functor}
   There is a functor $\iota : \C \times \C^\op \to \Optic_\otimes$, which on objects is given by $\iota(S, S') = (S, S')$ and on a morphism $(f, g) : (S, S') \to (A, A')$ by $\iota(f, g) = \rep{\lambda_A^{-1} f}{g \lambda_{A'}}$.
@@
 
-\begin{proposition}\label{prop:change-of-action-monoidal}
+\begin{proposition}
   For monoidal $F : \C \to \D$, the induced $\Optic(F) : \Optic_\C \to \Optic_\D$ is also monoidal.
@@
 An \emph{action of $\M$ on $\C$} is a monoidal functor $a : \M \to [\C, \C]$.
-For two objects $M \in \M$ and $A \in \C$, the action $a(M)(A)$ is abbreviated $MA$.
+For two objects $M \in \M$ and $A \in \C$, the action $a(M)(A)$ is abbreviated $M \act A$ or $MA$.
 The tensor product in $\M$ will also be written as juxtaposition, so $(NM)A \cong N(MA)$.
@@
 
-The following are analogous to Propositions~\ref{prop:optic-is-cat} and~\ref{prop:change-of-action-monoidal}.
-
 \begin{proposition}
-  We have a category $\Optic_\M$ and a functor $\iota : \C \times \C^\op \to \Optic_\M$. \qed
+  We have a category $\Optic_\M$ and a functor $\iota : \C \times \C^\op \to \Optic_\M$ defined analogously to Propositions~\ref{prop:optic-is-cat} and~\ref{prop:iota-functor}. \qed
 \end{proposition}
@@
 \begin{definition}
-Given two categories equipped with monoidal actions $(\M, \C)$ and $(\N, D)$, a \emph{morphism of actions} is a monoidal functor $F^\bullet : \M \to N$ and a functor $F : \C \to \D$ that commutes with the actions, in the sense that there exist natural isomorphisms
+Given two categories equipped with monoidal actions $(\M, \C)$ and $(\N, \D)$, a \emph{morphism of actions} is a monoidal functor $F^\bullet : \M \to N$ and a functor $F : \C \to \D$ that commutes with the actions, in the sense that there exist natural isomorphisms
   \begin{align*}
@@
 satisfying conditions analogous to those for a monoidal functor.
+
+%A morphism of actions is \emph{lax} if $\phi$ and $\phi_{M,A}$ are not necessarily invertible, and \emph{oplax} if they face the other direction. \todo{Do I need laxness in $F^\bullet$?}
 \end{definition}
@@
 \begin{proposition}\label{prop:change-of-action}
-If $F : (\M, \C) \to (\N, D)$, is a morphism of actions, there is an induced functor $\Optic(F) : \Optic_\M \to \Optic_\N$. \qed
+If $F : (\M, \C) \to (\N, \D)$, is a morphism of actions, there is an induced functor $\Optic(F) : \Optic_\M \to \Optic_\N$. \qed
 \end{proposition}
@@
 \begin{proof}
-  We begin by giving $\Twoptic_\times(S, A)$ the same treatment as $\Optic_\times(S, A)$.
-Using Yoneda reduction and the universal property of the product, as we did for lenses themselves, it is isomorphic to the set
-  \[\conctwice_\times(S, A) := \C(S, A) \times \C(S \times A, A) \times \C(S \times A \times A, S)\]
-  with the isomorphism given by
+  We begin by giving $\Twoptic_\times(S, A)$ the same treatment as $\Optic_\times(S, A)$. Using Yoneda reduction and the universal property of the product as we did for lenses themselves, we have:
+  \begin{align*}
+  \Twoptic_\times(S, A)
+  &= \int^{M_1, M_2 \in \C} \C(S, M_1 \times A) \times \C(M_1 \times A, M_2 \times A) \times \C(M_2 \times A, S) \\
+  &\cong \int^{M_1, M_2 \in \C} \C(S, M_1) \times \C(S, A) \times \C(M_1 \times A, M_2 \times A) \times \C(M_2 \times A, S) \\
+  &\cong \int^{M_2 \in \C} \C(S, A) \times \C(S \times A, M_2 \times A) \times \C(M_2 \times A, S) \\
+  &\cong \int^{M_2 \in \C} \C(S, A) \times \C(S \times A, M_2) \times \C(S \times A, A) \times \C(M_2 \times A, S) \\
+  &\cong \C(S, A) \times \C(S \times A, A) \times \C(S \times A \times A, S)
+  \end{align*}
+  Call this last set $\conctwice_\times(S, A)$. Written equationally, the isomorphism $\Phi : \Twoptic_\times(S, A) \to \conctwice_\times(S, A)$ is given by:
   \begin{align*}
@@
 \begin{definition}
-  Suppose $\C$ has finite coproducts, and let $\C$ act on itself via the bifunctor $\sqcup : \C \times \C \to \C$.
-The \emph{category of prisms} is the category of lawful optics with respect to $\sqcup$.
+  Suppose $\C$ has finite coproducts. The \emph{category of prisms} is the category of lawful optics with respect to the coproduct $\sqcup$.
 \end{definition}
@@
 
-There is a common pattern in many of the examples to follow: for every object $A \in \C$, the evaluation-at-$A$ functor $-A : \M \to \C$ has a right adjoint, say $R_A : \C \to \M$.
+There is a common pattern in many of the examples to follow: for every object $A \in \C$, the evaluation-at-$A$ functor $- \act A : \M \to \C$ has a right adjoint, say $R_A : \C \to \M$.
 To fix notation, let \[\overrightarrow{(-)} : \C(F \act A, S) \to \M(F, R_{A} S) : \overleftarrow{(-)}\] denote the homset bijection, so the unit and counit are:
@@
 The above isomorphism sends $\funzip$ to the element $\rep{\funzip}{\varepsilon_{S'}}$.
-In the other direction, given $\rep{l}{r}$ we have $\funzip = (\overrightarrow{r} \otimes A)l$.
+In the other direction, given $\rep{l}{r}$ we have $\funzip = (\overrightarrow{r} \act A)l$.
 
@@
 (Yes, the names $\Traversal$ vs\@.
-$\Traversable$ are confusing.)
+$\Traversable$ are confusing!)
 \end{definition}
@@
 
-Suppose $\C$ is a monoidal closed category and $T : \C \to \C$ is a strong monad. We can find a concrete description of the optics for the action $\monact$, using the same method as for linear lenses.
-
-\begin{align*}
-\Optic((S, S'), (A, A'))
-&= \int^{M \in \C} \C_T(S, M \monact A) \times \C_T(M \monact A', S') \\
-&= \int^{M \in \C} \C_T(S, M \monact A) \times \C(M \otimes A', T S') \\
-&\cong \int^{M \in \C} \C_T(S, M \monact A) \times \C(M, \homC(A', T S')) \\
-&\cong \C_T(S, \homC(A', T S') \monact A) \\
-&\cong \C(S, T(\homC(A', T S') \otimes A))
-\end{align*}
-
-Concrete effectful lenses therefore consist of a single morphism $\munzip : S \to T(\homC(A', T S') \otimes A)$.
-The category $\C$ includes into $\C_T$ in a way that preserves the action of $\C$, so there is an induced inclusion $\Optic_\otimes \to \Optic_\monact$.
+Suppose $\C$ is a monoidal closed category and $T : \C \to \C$ is a strong monad. Then the evaluation-at-$A$ functor has a right adjoint:
+\begin{align*}
+\C_T(M \monact A', S') 
+&= \C(M \times A', T S') \\
+&\cong \C(M, \homC(A', T S'))
+\end{align*}
+Using the coalgebraic description, we see that concrete effectful lenses consist of a single morphism \[\munzip : S \to T(\homC(A', T S') \otimes A).\] The optic laws in this case specialise to:
 
@@
   where \[ \munzip \circ_T - : \homC(A, TS) \to \homC(A, T(\homC(A, TS) \otimes A)) \] denotes internal Kleisli composition and \[\coev_{\homC(A, TS), A} : \homC(A, TS) \to \homC(A, \homC(A, TS) \otimes A) \] is coevaluation.
+\qed
 \end{proposition}
@@
 
-\begin{proof}
-This is exactly analogous to Proposition~\ref{prop:concrete-linear-lawful} for linear lenses, with the unit and multiplication of the monad inserted in the appropriate places.
-%\begin{align*}
-%&\int^{M, N \in \C} \C_T(S, M \monact A) \times \C_T(M \monact A, N \monact A) \times \C_T(N \monact A, S) \\
-%&\cong \int^{M, N \in \C} \C_T(S, M \monact A) \times \C_T(M \monact A, N \monact A) \times \C(N, \homC(A, TS)) \\
-%&\cong \int^{M \in \C} \C_T(S, M \monact A) \times \C_T(M \monact A, \homC(A, TS) \monact A)\\
-%&\cong \int^{M \in \C} \C_T(S, M \monact A) \times \C(M \times A, T(\homC(A, TS) \times A))\\
-%&\cong \int^{M \in \C} \C_T(S, M \monact A) \times \C(M, \homC(A, T(\homC(A, TS) \monact A)))\\
-%&\cong \C_T(S, \homC(A, T(\homC(A, TS) \times A)) \times A) \\
-%&\cong \C(S, T(\homC(A, T(\homC(A, TS) \times A)) \times A))
-%\end{align*}
-\end{proof}
+The category $\C$ includes into $\C_T$ in a way that preserves the action of $\C$, so there is an induced inclusion $\Optic_\otimes \to \Optic_\monact$.
 
@@
 
+Suppose $\C$ is cartesian closed.
+
 \begin{definition}
@@
 
-Working in a cartesian closed category, we can find a concrete description of optics for the action $\monact : \C \times \C_{T_Q} \to \C_{T_Q}$ that is closer to that for ordinary lenses.
+We can find a concrete description of optics for the action $\monact : \C \times \C_{T_Q} \to \C_{T_Q}$ that is closer to that for ordinary lenses.
 \begin{align*}
@@
 \end{minted}
-is lawful iff: \\
+is lawful iff the following three laws hold: \\
 \begin{minipage}{\textwidth}
@@
 
-\subsection{Degenerate Optics}
-
-We finish with some almost-examples of optic variants, the \mintinline{haskell}{Getter}s and \mintinline{haskell}{Review}s of the Haskell library, where an optic $(S, S') \hto (A, A')$ corresponds simply to a morphism $S \to A$ or $A' \to S'$ respectively.
-These can fit into the coend formalism, with a slight modification.
-
-If we have a monoidal category $\M$ that acts on two different categories $\C_1$ and $\C_2$, we may form the `optic' category:
-\begin{align*}
-  \Optic_\M((S, S'), (A, A')) := \int^{M \in \M} \C_1(S, MA) \times \C_2(MA', S')
-\end{align*}
-We lose, of course, the ability to talk about lawful optics.
-To encode \mintinline{haskell}{Getter}s and \mintinline{haskell}{Review}s, we then set $\C_2$ or $\C_1$ to be the codiscrete category $\C_\mathsf{codisc}$, i.e.
-the category with the same set of objects as $\C$ but with all homsets the singleton set.
-In this way we indeed get a category $\Getter$ that is isomorphic to $\C$:
-\begin{align*}
-\int^{M \in \M} \C(S, M \times A) \times \C_\mathsf{codisc}(M \times A', S')
-&\cong \int^{M \in \M} \C(S, M \times A) \\
-&\cong \C(S, 1 \times A) \\
-&\cong \C(S, A)
-\end{align*}
-This works for $\Review$ in the same way, putting $\C_\mathsf{codisc}$ on the left. The functor $\C \to \C_\mathsf{codisc}$ induces functors $\Lens \to \Getter$ and $\Prism \to \Review$.
-
-Finally, we can also encode \mintinline{haskell}{Fold}s, which in $\Set$ correspond to functions $S \to \mathrm{List}\,A$.
-The key is that the $\mathrm{List}$ functor is the terminal $\Traversable$, so we have isomorphisms
-\begin{align*}
-&\int^{M \in \Traversable} \Set(S, MA) \times \Set_\mathsf{codisc}(MA', S') \\
-&\cong \int^{M \in \Traversable} \Set(S, MA) \\
-&\cong \Set(S, \mathrm{List}\,A)
-\end{align*}
-
 \subsection{Further Examples}
@@
 These are optics for the action of $\C$ on itself by $M \act A = (M \sqcup 1) \times A$, or equivalently, of the category of pointed objects of $\C$ on $\C$ by cartesian product.
-Concrete achromatic lenses $S \hto A$ are elements of the set \[\C(S, \homC(A', S') \sqcup 1) \times \C(S, A) \times \C(A', S').\]
+Concrete achromatic lenses $(S, S') \hto (A, A')$ are elements of the set \[\C(S, \homC(A', S') \sqcup 1) \times \C(S, A) \times \C(A', S').\]
 %\begin{align*}
@@
 
+\item \emph{Grates}~\cite{GratesPost} are optics for the contravariant action of a monoidal closed category $\C$ on itself by $X \cdot A \mapsto \homC(X, A)$.
+Concretely these correspond to morphisms \[ \C(\homC(\homC(S, A), A'), S').
+\]
+
 \item \emph{Adjunction Lenses}: For a category with finite products $\C$ and a monoidal adjunction $F \dashv U$, with $F : \C \to \D$ and $U : \D \to \C$.
@@
 
+\section{Mixed Optics}\label{sec:mixed-optics}
+
+We can generalise the definition of $\Optic$ so that the two halves lie in different categories, allowing us to capture a few more optic variants found in the wild.
+Suppose $\C_1$ and $\C_2$ are categories that are each acted on by a common monoidal category $\M$.
+
+\begin{definition}
+  Given two objects of $\C_1 \times \C_2^\op$, say $(S, S')$ and $(A, A')$, an \emph{optic} $p : (S, S') \hto (A, A')$ is an element of the set
+  \begin{align*}
+    \Optic_\otimes((S, S'), (A, A')) := \int^{M \in \M} \C_1(S, M \act A) \times \C_2(M \act A', S')
+  \end{align*}
+\end{definition}
+
+Several results from Section~\ref{sec:optics} continue to hold:
+\begin{proposition}\label{prop:mixed-optic-is-cat}
+  The above data form a category $\Optic_{\M, \C_1, \C_2}$. \todo{notation?} \qed
+\end{proposition}
+\begin{proposition}
+  There is a functor $\iota : \C_1 \times \C_2^\op \to \Optic_{\M, \C_1, \C_2}$, which on objects is given by $\iota(S, S') = (S, S')$ and on a morphism $(f, g) : (S, S') \to (A, A')$ by \[\iota(f, g) = \rep{(\lambda^{\C_1}_A)^{-1} f}{g \lambda^{\C_2}_{A'}},\] where $\lambda^{\C_1}_A : A \to IA$ in $\C_1$ and $\lambda^{\C_2}_{A'} : A' \to IA'$ in $\C_2$.
+\qed
+\end{proposition}
+\begin{proposition}\label{prop:mixed-change-of-action}
+  Given two morphisms of actions $F_1 : (\M, \C_1) \to (\N, \D_1)$ and $F_2 : (\M, \C_2) \to (\N, \D_2)$, there is an induced functor $\Optic(F_1, F_2) : \Optic_{\M, \C_1, \C_2} \to \Optic_{\N, \D_1, \D_2}$.
+\qed
+\end{proposition}
+
+The notion of lawfulness used earlier breaks down in this setting, as the definition of $\Twoptic(S, A)$ only makes sense when $\C_1 = \C_2$. The following definition gives a reasonable approximation.
+
+\begin{definition}
+If $F_1 : (\M, \C_1) \to (\N, \D)$ and $F_2 : (\M, \C_2) \to (\N, \D)$, a mixed optic $p : (S, S) \hto (A, A)$ in $\Optic_{\M, \C_1, \C_2}$ is \emph{lawful relative to $(F_1, F_2)$} if its image under $\Optic(F_1, F_2)$ is lawful.
+\end{definition}
+
+\subsection{Examples}
+
+\subsubsection{Degenerate Optics}
+
+The \mintinline{haskell}{Getter}s and \mintinline{haskell}{Review}s of the Haskell lens library corresponds simply to a morphisms $S \to A$ and $A' \to S'$ respectively.
+These are examples of mixed optics as follows.
+
+Recall that for any category $\C$, there is a category $\C_\codisc$ with the same objects, but where every homset is the singleton set.
+For any action of $\M$ on $\C$ there is a corresponding action of $\M$ on $\C_\codisc$ that has the same action on objects, and a morphism of actions $i : (\M, \C) \to (\M, \C_\codisc)$ which is the identity on objects.
+
+Now for a category with finite products $\C$, define $\Getter$ to be the category of mixed optics $\Optic_{\times, \C, \C_\codisc}$. This is indeed isomorphic to $\C$:
+\begin{align*}
+&\int^{M \in \M} \C(S, M \times A) \times \C_\codisc(M \times A', S')\\
+&\cong \int^{M \in \M} \C(S, M \times A) \\
+&\cong \C(S, 1 \times A) \\
+&\cong \C(S, A)
+\end{align*}
+This works for $\Review := \Optic_{\sqcup, \C_\codisc, \C}$ in the same way. There are induced functors $\Optic(\id_\C, i) : \Lens \to \Getter$ and $\Optic(i, \id_\C) : \Prism \to \Review$.
+
+\begin{remark}
+If we we are working linearly, we should not expect $\Optic_{\otimes, \C, \C_\codisc}$ to be described so neatly; the above isomorphism relies on the unit of the monoidal structure being terminal.
+\end{remark}
+
+Finally, we can also encode the category of \mintinline{haskell}{Fold}s which in $\Set$ correspond to functions $S \to \mathrm{List}\,A$.
+Define $\Fold := \Optic_{\Traversable, \C, \C_\codisc}$.
+The key is that the $\mathrm{List}$ functor is the terminal $\Traversable$ functor, so we have isomorphisms
+\begin{align*}
+&\int^{M \in \Traversable} \Set(S, MA) \times \Set_\codisc(MA', S') \\
+&\cong \int^{M \in \Traversable} \Set(S, MA) \\
+&\cong \Set(S, \mathrm{List}\,A)
+\end{align*}
+There is an induced functor $\Optic(\id_C, i) : \Traversal \to \Fold$.
+
+\subsubsection{Indexed Optics}
+As well as giving a principled home to degenerate optics, the notion of mixed optics also allows us to describe \emph{indexed optics} categorically.
+The most interesting example of an indexed optic variant is the \emph{indexed traversal}, which, for example, allows access to the indices of the entries of a list as it is being traversed.
+
+We first need to define indexed traversable functors. Unfortunately this has many moving parts!
+
+\begin{proposition}
+The assignment $F \act X \mapsto F \Set(I, X)$ is a lax monoidal action of $\App$ on $\Set$, called the \emph{$I$-indexed action of $\App$ on $\Set$}.
+\end{proposition}
+
+\begin{definition}
+A \emph{traversable functor indexed by $I$} is a functor $T : \Set \to \Set$ equipped with a distributive law $\delta_F : T(\Set(I, F-)) \to FT$ for $T$ between the $I$-indexed action of $\App$ on $\Set$ and the action of $\App$ on $\Set$ by evaluation.
+\end{definition}
+
+\begin{definition}
+The category of \emph{indexed traversable functors} $\IdxTraversable$ has as objects pairs $(T, I)$, where $I \in \Set$ and $T : \Set \to \Set$ is a traversable functor indexed by $I$.
+A morphism $(T, I) \to (T', I')$ is a natural transformation $\alpha : T \to T'$ and morphism (note the direction!) $i : I' \to I$, such that $\alpha$ commutes with the distributive laws on both traversable functors, using $i$ to mediate between the index objects.
+\end{definition}
+
+\begin{proposition}
+$\IdxTraversable$ acts on $\C \times \C$ by $(T, I) \act (A, R) \mapsto (TA, \homC(I, R))$ and on $\C$ simply by $(T, I) \act A \mapsto TA$.
+\end{proposition}
+
+The idea for this action comes from \cite{IndexedOpticsPost}.
+
+\begin{conjecture}
+The category of indexed traversals corresponds to the category of mixed optics with the action of $\IdxTraversable$ on $\C \times \C$ on the left and $\C$ on the right.
+\end{conjecture}
+
+The obstacle to a good theory of mixed optics is finding the right notion of lawfulness.
+Specifically, profunctors $\C_1 \hto \C_2$ don't compose, so we cannot sensibly talk about comonoid objects in $\Prof(\C_1, \C_2)$.
+Here, techniques from \cite{MonadsNeedNotBeEndofunctors} may assist in providing a monoidal structure on $\Prof(\C_1, \C_2)$.
+
 \section{Profunctor Optics}\label{sec:profunctor-optics}
@@
 
-\begin{remark}
+\begin{remark} \todo{use this?}
 We do not explore this further in the current note, but there is a notion of Tambara module structure for profunctors between two different categories.
@@
 \begin{proposition}[Profunctor Optics are Optics]\label{prop:profunctor-optics-are-optics}
+\todo{Use $(S, S') \hto (A, A')$ here}
   \begin{align*}
@@
   using parametricity as a proxy for naturality.
+  \todo{I've just noticed, isn't this a cheat? This would be naturality wrt ALL profunctor morphisms, not just morphisms of Tambara modules. Can I find a place where this breaks?} 
 \end{remark}
@@
 
+\begin{remark}
+A consequence is that the laws typically given for $\Traversal$s actually only need to be checked for the applicative functor we called $UR^*$.
+In Haskell this is implemented as \mintinline{haskell}{FunList}~\cite{FunListPost} or \mintinline{haskell}{Bazaar}~\cite{LensLibrary}.
+\end{remark}
+
 \section{Future Work}
@@
 There are many avenues for exploration! Here we make some speculations.
-
-\subsection{Indexed Optics}
-As mentioned in the discussion on degenerate optics, there ought to be a generalisation of the $\Optic$ category such that the $l$ and $r$ sides lie in two different categories $\C_1$ and $\C_2$, bridged by an action of $\M$ on each.
-As well as giving a principled home to degenerate optics, this also allows us to describe \emph{indexed optics} categorically.
-
-The most interesting example is \emph{indexed traversals}, which, for example, allow access to the indices of the entries of a list as it is being traversed.
-
-We first need to define indexed traversals. Unfortunately this has many moving parts!
-
-\begin{proposition}
-The assignment $F \act X \mapsto F \Set(I, X)$ is a lax monoidal action of $\App$ on $\Set$.
-\end{proposition}
-Call this the $I$-indexed action of $\App$ on $\Set$.
-
-\begin{definition}
-A \emph{traversable functor indexed by $I$} is a functor $T : \Set \to \Set$ equipped with a distributive law $\delta_F : T(\Set(I, F-)) \to FT$ for $T$ between the $I$-indexed action of $\App$ on $\Set$ and the action of $\App$ on $\Set$ by evaluation.
-\end{definition}
-
-\begin{definition}
-The category of \emph{indexed traversable functors} $\IdxTraversable$ has as objects pairs $(T, I)$, where $I \in \Set$ and $T : \Set \to \Set$ is a traversable functor indexed by $I$.
-A morphism $(T, I) \to (T', I')$ is a natural transformation $\alpha : T \to T'$ and morphism (note the direction!) $i : I' \to I$, such that $\alpha$ commutes with the distributive laws on both traversable functors, using $i$ to mediate between the index objects.
-\end{definition}
-
-\begin{proposition}
-$\IdxTraversable$ acts on $\C \times \C$ by $(T, I) \act (A, R) \mapsto (TA, \homC(I, R))$ and on $\C$ simply by $(T, I) \act A \mapsto TA$.
-\end{proposition}
-
-The idea for this action comes from \cite{IndexedOpticsPost}.
-
-\begin{conjecture}
-The category of indexed traversals corresponds to the category of mixed optics with the action of $\IdxTraversable$ on $\C \times \C$ on the left and $\C$ on the right.
-\end{conjecture}
-
-The obstacle to a good theory of mixed optics is finding the right notion of lawfulness.
-Specifically, profunctors $\C_1 \hto \C_2$ don't compose, so we cannot sensibly talk about comonoid objects in $\Prof(\C_1, \C_2)$.
-Here, techniques from \cite{MonadsNeedNotBeEndofunctors} may assist in providing a monoidal structure on $\Prof(\C_1, \C_2)$.
 
@@
 \begin{conjecture}
-c-lenses are the lawful optics for some action on $\Cat$.
+c-lenses are the lawful (possibly mixed) optics for some action on $\Cat$.
 \end{conjecture}
@@
 \end{definition}
-To form a category, it is required to consider learners up to an equivalence relation on the sets $P$.
-But there may be a slicker method: note that the data of a learner is describing an element of the coend
+To form a category, one must consider learners up to an equivalence relation on the sets $P$.
+There is an alternate slick description of the set of learners $A \hto B$: note that the data of a learner is describing an element of the coend
 \begin{align*}
@@
 Composition of learners can be defined analogously to composition for optics.
-This perspective explains the minor fussing around required in dealing with equivalence classes of learners, and suggests a generalisation to other monoidal settings.
+This perspective explains the slight fussing around required in dealing with equivalence classes of learners, and suggests a generalisation to other monoidal settings.
 
@@
 
-\todo{Move some proofs to appendix?}
+\todo{Move some proofs to an appendix?}
+
+\todo{Find an example where the lens laws are definitely not equivalent}
 

### 2018-07-30 paper.tex
State of play

@@
 \newcommand{\Fold}{\mathbf{Fold}}
+\newcommand{\IdxLens}{\mathbf{IdxLens}}
+\newcommand{\IdxTraversal}{\mathbf{IdxTraversal}}
 
@@
 \newcommand{\codisc}{\mathsf{codisc}}
+\DeclareMathOperator*{\colim}{\mathrm{colim}}
+
+\newcommand*\circled[1]{\tikz[baseline={([yshift=-0.65ex]current bounding box.center)}]{
+   \node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
+\newcommand{\actL}{{\circled{\tiny$\mathsf{L}$}}}
+\newcommand{\actR}{{\circled{\tiny$\mathsf{R}$}}}
 
@@
 
-In its most concrete form, a \emph{lens} from $S$ to $A$ is a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$.
-From a software engineering standpoint, such a lens allows us to ``zoom in'' on $S$ to focus on a small part $A$, manipulate $A$ in some way, then ``zoom out'' and have our changes reflected in $S$.
-
-Often we want our lens to obey the following laws:
-\begin{itemize}
-\item ``$\fput\fget$'': $\fget \; \fput = \pi_2$ as maps $S \times A \to A$, so that any update to $A$ should be represented faithfully in $S$;
-\item ``$\fget\fput$'': $\fput [\id_S, \fget] = \id_S$ as maps $S \to S$, so that if $A$ is not changed then $S$ should not change; and,
-\item ``$\fput\fput$'': $\fput (\fput \times A) = \fput \, \pi_{1, 3}$ as maps $S \times A \times A \to S$, so any update to $A$ completely overwrites previous updates.
-\end{itemize}
-We will call such lenses \emph{lawful}.
-(The names of the laws make more sense when the equations are written with composition in diagrammatic order!) Lenses form a category with a subcategory of lawful lenses.
-
+In its most concrete form, a \emph{lens}~\cite{CombinatorsForBidirectionalTreeTransformations} from a set $S$ to a set $A$ is a pair of maps ${\fget : S \to A}$ and ${\fput : S \times A \to S}$.
+From an engineering standpoint, such a lens allows us to ``zoom in'' on $S$ to focus on a small part $A$, manipulate $A$ in some way, then ``zoom out'' and have our changes reflected in $S$.
+
+So that our lenses better conform to this intuitive idea of ``zooming in'', we often want them satisfy some conditions known as the \emph{lens laws}:
+\begin{center}
+\begin{minipage}[b]{0.33333\textwidth}
+\begin{center}
+\[ 
+\begin{tikzcd}
+S \times A \ar[rr, "\fput"] \ar[dr, "\pi_2", swap] && S \ar[dl, "\fget"] \\
+& A
+\end{tikzcd}
+\]
+\hspace{0.8cm}$\fput\fget$
+\end{center}
+\end{minipage}%
+\begin{minipage}[b]{0.33333\textwidth}
+\begin{center}
+\[ 
+\begin{tikzcd}
+S \ar[rr, "{[\id_S, \fget]}"] \ar[dr, "\id_S", swap] && S \times A \ar[dl, "\fput"] \\
+& A
+\end{tikzcd}
+\]
+\hspace{-0.8cm}$\fget\fput$
+\end{center}
+\end{minipage}%
+\begin{minipage}[b]{0.33333\textwidth}
+\begin{center}
+\[ 
+\begin{tikzcd}
+S \times A \times A \ar[r, "\fput \times A"] \ar[d, "\pi_{1, 3}", swap] & S \times A\ar[d, "\fput"] \\
+S \times A \ar[r, "\fput", swap] & A
+\end{tikzcd}
+\]
+\quad$\fput\fput$
+\end{center}
+\end{minipage}%
+\end{center}
+The $\fput\fget$ law states that any update to $A$ is represented faithfully in $S$.
+The $\fget\fput$ law states that if $A$ is not changed then neither is $S$; and finally, the $\fput\fput$ law states that any update to $A$ completely overwrites previous updates.
+
+%Lenses form a category, with the composition of lenses $T \hto S$ and $S \hto A$ as indicated:
+%\begin{align*}
+%\fget &: T \xrightarrow{\fget_1} S \xrightarrow{\fget_2} A \\
+%\fput &: T \times A \xrightarrow{[\id_T, \fget_1, \id_A]} T \times S \times A \xrightarrow{T \times \fput_2} T \times S \xrightarrow{\fput_1} T
+%\end{align*}
+%This composition preserves lawfulness.
 %\todo{reference a whole bunch of bx and database stuff}
@@
 Then in Section~\ref{sec:examples} we see that these generic definitions specialise correctly to the other basic varieties of optic, including giving the correct laws.
+We include Section~\ref{sec:mixed-optics} a more speculative discussion of ``mixed optics'', which include indexed and coindexed lenses and traversals.
 
@@
 
+\begin{lemma}[Mute coends]
+Consider a functor $F : \C \to \E$ as a functor $\C^\op \times \C \to \E$ that ignores its contravariant argument. Then \[ \int^C F(C) \cong  \colim F. \] \qed
+\end{lemma}
+
 \section{Optics}\label{sec:optics}
 
-We begin by defining the category of optics in a symmetric monoidal category $\C$.
+We begin by defining the category of optics for a symmetric monoidal category $\C$.
 This category was first defined in~\cite[Section 6]{Doubles} as the `double' of a monoidal category.
@@
 
-Our definition of optic has as domain and codomain \emph{pairs} of objects of $\C$.
-This generality is important for the applications to game theory; for ordinary lenses we restrict our attention to pairs with the same object in both entries.
+Our definition of optic has as domain and codomain \emph{pairs} of objects of $\C$, one of which behaves covariantly and the other contravariantly.
+For example, our lenses will be pairs of maps $\fget : S \to A$ and $\fput : S \times A' \to S'$.
+This generality is important for the applications to game theory, and in fact helps in calculations by making the covariant and contravariant positions more difficult to confuse.
+Readers more familiar with lenses should ignore the primes.
 
@@
 Because this coend takes place in $\Set$, we can use Lemma~\ref{lemma:calculate-coend} to describe $\Optic_\otimes((S, S'), (A, A'))$ explicitly.
-It is the set of pairs $(l, r)$, where $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, quotiented by the relation
+It is the set of pairs $(l, r)$, where $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, quotiented by the equivalence relation generated by relations of the form
 \begin{align*}
@@
 
-For a pair of maps $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\rep{l}{r} : (S, S') \hto (A, A')$ for their image in $\Optic_\otimes((S, S'), (A, A'))$, and say that $M$ is the residual for this representative.
+For a pair of maps $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\rep{l}{r} : (S, S') \hto (A, A')$ for their image in $\Optic_\otimes((S, S'), (A, A'))$, and say that the object $M$ is the residual for this representative.
 Optics will always be written with a crossed arrow $\hto$ to distinguish them from morphisms of $\C$.
@@
   \end{center}
-  reading left to right, so the left half of the diagram represents $l$ and the right half $r$. The relation imposed by the coend equates the following two diagrams:
+  reading left to right, so the left half of the diagram represents $l$ and the right half $r$. The relation imposed by the coend can be graphically expressed as:
   \begin{center}
@@
   \end{center}
-  We will therefore omit the vertical cut point between $l$ and $r$ in most subsequent diagrams; any choice yields a representative of same optic.
+  We will therefore omit the vertical cut between $l$ and $r$ in most subsequent diagrams; any choice yields a representative of same optic.
 \end{remark}
@@
 
-Two optics can be composed as follows: \todo{I give possibly too much detail here.} We wish to construct a map
-\begin{align*}
-  &\left(\int^{M \in \C} \C(S, M \otimes A) \times \C(M \otimes A', S')\right) \times \left(\int^{M \in \C} \C(R, M \otimes S) \times \C(M \otimes S', R')\right) \\ &
-                                                                                                                                                                       \quad \to \int^{M \in \C} \C(R, M \otimes A) \times \C(M \otimes A', R').
-\end{align*}
-The product in $\Set$ preserves colimits, so in particular coends. Using this fact and the Fubini theorem for coends, the domain is isomorphic to
-\begin{align*}
-  \int^{(M, N) \in \C \times \C} \C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(R, N \otimes S) \times \C(N \otimes S', R').
-\end{align*}
-So by the universal property of coends, it suffices to construct maps
-\begin{align*}
-  & \C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(R, N \otimes S) \times \C(N \otimes S', R') \\ &
-                                                                                                              \quad \to \int^{M \in \C} \C(R, M \otimes A) \times \C(M \otimes A', R').
-\end{align*}
-natural in $M$ and $N$. For these we use the composites
-\begin{align*}
-  &\C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(R, N \otimes S) \times \C(N \otimes S', R')\\
-  \to \,& \C(N \otimes S, N \otimes M \otimes A) \times \C(N \otimes M \otimes A', N \otimes S') \times \C(R, N \otimes S) \times \C(N \otimes S', R') && \text{(functoriality of $N \otimes  -$)} \\
-  \to \,& \C(R, N \otimes  M \otimes A) \times \C(N \otimes M \otimes A', R') && \text{(composition in $\C$)} \\
-  \to \,&\int^{M \in \M} \C(R, M \otimes A) \times \C(M \otimes A', R') && \text{($\copr_{N \otimes M}$)}
-\end{align*}
-In other words, let $\rep{l'}{r'} : (R, R') \hto (S, S')$ and $\rep{l}{r} : (S, S') \hto (A, A')$ with $M$ the residual for $\rep{l'}{r'}$.
-The composite is then: $\rep{l}{r} \circ \rep{l'}{r'} = \rep{(M \otimes l)l'}{r'(M \otimes r)}$.
-
-Graphically, this is substituting the first optic for the hole of the second:
+Two optics can be composed as follows. The easiest interpretation is graphical: composition of optics corresponds to substituting the first optic for the hole of the second:
 \begin{center}
@@
 \end{center}
+
+More formally, we wish to construct a map
+\begin{align*}
+  &\left(\int^{M \in \C} \C(S, M \otimes A) \times \C(M \otimes A', S')\right) \times \left(\int^{N \in \C} \C(R, N \otimes S) \times \C(N \otimes S', R')\right) \\ 
+  &\quad \to \int^{M \in \C} \C(R, M \otimes A) \times \C(M \otimes A', R').
+\end{align*}
+The product in $\Set$ preserves colimits, so in particular coends. Using this fact and the Fubini theorem for coends, the domain is isomorphic to
+\begin{align*}
+  \int^{(M, N) \in \C \times \C} \C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(R, N \otimes S) \times \C(N \otimes S', R').
+\end{align*}
+So by the universal property of coends, it suffices to construct maps
+\begin{align*}
+  & \C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(R, N \otimes S) \times \C(N \otimes S', R') \\ &
+                                                                                                              \quad \to \int^{M \in \C} \C(R, M \otimes A) \times \C(M \otimes A', R').
+\end{align*}
+natural in $M$ and $N$. For these we use the composites
+\begin{align*}
+  &\C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(R, N \otimes S) \times \C(N \otimes S', R')\\
+  \to \,& \C(N \otimes S, N \otimes M \otimes A) \times \C(N \otimes M \otimes A', N \otimes S') \times \C(R, N \otimes S) \times \C(N \otimes S', R') && \text{(functoriality of $N \otimes  -$)} \\
+  \to \,& \C(R, N \otimes  M \otimes A) \times \C(N \otimes M \otimes A', R') && \text{(composition in $\C$)} \\
+  \to \,&\int^{M \in \M} \C(R, M \otimes A) \times \C(M \otimes A', R') && \text{($\copr_{N \otimes M}$)}
+\end{align*}
+Written equationally, suppose $\rep{l'}{r'} : (R, R') \hto (S, S')$ and $\rep{l}{r} : (S, S') \hto (A, A')$ are optics with $M$ the residual for $\rep{l'}{r'}$.
+The composite $(R, R') \hto (A, A')$ is then: \[\rep{l}{r} \circ \rep{l'}{r'} := \rep{(M \otimes l)l'}{r'(M \otimes r)}.\]
 
@@
 Using the isomorphism in both directions, we leave it to the reader to verify that composition in $\Optic_\times$ corresponds to ordinary composition of concrete lenses.
-(Of course, there is only one possible way such a collection of morphisms could be sensibly composed!)
+(Of course, there is only one sensible way to compose such a collection of morphisms!)
 \end{remark}
@@
 The tensor product in $\M$ will also be written as juxtaposition, so $(NM)A \cong N(MA)$.
+
+An action is \emph{lax} if $a$ is instead a lax monoidal functor.
 \end{definition}
@@
 To fix notation, let \[\overrightarrow{(-)} : \C(F \act A, S) \to \M(F, R_{A} S) : \overleftarrow{(-)}\] denote the homset bijection, so the unit and counit are:
-  \begin{align*}
+    \begin{equation*}
+    \begin{aligned}[t]
   	\eta_F &: F \to R_A (F \act A) \\
-    \eta_F &:= \overrightarrow{\id_{F \act A}} \\
+    \eta_F &:= \overrightarrow{\id_{F \act A}}
+    \end{aligned}
+    \qquad\qquad\qquad
+    \begin{aligned}[t]
     \varepsilon_{S} &: (R_A S) \cdot A \to S \\
     \varepsilon_{S} &:= \overleftarrow{\id_{R_{A} S}}
-  \end{align*}
-
+    \end{aligned}
+\end{equation*}
 \begin{remark}
@@
 \end{align*}
-The category $\mathsf{Aff}$ acts on $\C$ by $(P, Q) \act A = P \sqcup (Q \times A)$, in fact, $\mathsf{Aff}$ is cooked up exactly as the closure of the actions $- \times A$ and $- \sqcup A$ under composition.
+The category $\mathsf{Aff}$ acts on $\C$ by $(P, Q) \act A = P \sqcup (Q \times A)$, in fact, $\mathsf{Aff}$ is cooked up to act on $\C$ exactly by the closure of the actions $- \times A$ and $- \sqcup A$ under composition.
 A concrete affine traversal is an element of \[\C(S, S' \sqcup (\homC(A', S') \times A)).\]
@@
 
+\todo{This bit is very much in progress, skip to Section~\ref{sec:profunctor-optics}}
+
 We can generalise the definition of $\Optic$ so that the two halves lie in different categories, allowing us to capture a few more optic variants found in the wild.
-Suppose $\C_1$ and $\C_2$ are categories that are each acted on by a common monoidal category $\M$.
+Suppose $\C_L$ and $\C_L$ are categories that are each acted on by a common monoidal category $\M$.
+Write these actions as $\actL$ and $\actR$ respectively.
 
 \begin{definition}
-  Given two objects of $\C_1 \times \C_2^\op$, say $(S, S')$ and $(A, A')$, an \emph{optic} $p : (S, S') \hto (A, A')$ is an element of the set
-  \begin{align*}
-    \Optic_\otimes((S, S'), (A, A')) := \int^{M \in \M} \C_1(S, M \act A) \times \C_2(M \act A', S')
+  Given two objects of $\C_L \times \C_R^\op$, say $(S, S')$ and $(A, A')$, an \emph{optic} $p : (S, S') \hto (A, A')$ is an element of the set
+  \begin{align*}
+    \Optic_{\actL, \actR}((S, S'), (A, A')) := \int^{M \in \M} \C_L(S, M \actL A) \times \C_R(M \actR A', S')
   \end{align*}
@@
 \begin{proposition}\label{prop:mixed-optic-is-cat}
-  The above data form a category $\Optic_{\M, \C_1, \C_2}$. \todo{notation?} \qed
+  $\Optic_{\actL, \actR}$ is a category. \qed
 \end{proposition}
 \begin{proposition}
-  There is a functor $\iota : \C_1 \times \C_2^\op \to \Optic_{\M, \C_1, \C_2}$, which on objects is given by $\iota(S, S') = (S, S')$ and on a morphism $(f, g) : (S, S') \to (A, A')$ by \[\iota(f, g) = \rep{(\lambda^{\C_1}_A)^{-1} f}{g \lambda^{\C_2}_{A'}},\] where $\lambda^{\C_1}_A : A \to IA$ in $\C_1$ and $\lambda^{\C_2}_{A'} : A' \to IA'$ in $\C_2$.
+  There is a functor $\iota : \C_L \times \C_R^\op \to \Optic_{\actL, \actR}$, which on objects is given by $\iota(S, S') = (S, S')$ and on a morphism $(f, g) : (S, S') \to (A, A')$ by \[\iota(f, g) = \rep{(\lambda^{\C_L}_A)^{-1} f}{g \lambda^{\C_R}_{A'}},\] where $\lambda^{\C_L}_A : A \to IA$ in $\C_L$ and $\lambda^{\C_R}_{A'} : A' \to IA'$ in $\C_R$.
 \qed
@@
 \begin{proposition}\label{prop:mixed-change-of-action}
-  Given two morphisms of actions $F_1 : (\M, \C_1) \to (\N, \D_1)$ and $F_2 : (\M, \C_2) \to (\N, \D_2)$, there is an induced functor $\Optic(F_1, F_2) : \Optic_{\M, \C_1, \C_2} \to \Optic_{\N, \D_1, \D_2}$.
+  Given two morphisms of actions $F_L : (\M, \C_L) \to (\N, \D_L)$ and $F_R : (\M, \C_R) \to (\N, \D_R)$, there is an induced functor $\Optic(F_L, F_R) : \Optic_{\actL_1, \actR_1} \to \Optic_{\actL_2, \actR_2}$.
 \qed
@@
 
-The notion of lawfulness used earlier breaks down in this setting, as the definition of $\Twoptic(S, A)$ only makes sense when $\C_1 = \C_2$. The following definition gives a reasonable approximation.
+The notion of lawfulness used earlier breaks down in this setting, as the definition of $\Twoptic(S, A)$ only makes sense when $\C_L = \C_R$. The following definition gives a reasonable approximation.
 
 \begin{definition}
-If $F_1 : (\M, \C_1) \to (\N, \D)$ and $F_2 : (\M, \C_2) \to (\N, \D)$, a mixed optic $p : (S, S) \hto (A, A)$ in $\Optic_{\M, \C_1, \C_2}$ is \emph{lawful relative to $(F_1, F_2)$} if its image under $\Optic(F_1, F_2)$ is lawful.
+If $F_L : (\M, \C_L) \to (\N, \D)$ and $F_R : (\M, \C_R) \to (\N, \D)$, a mixed optic $p : (S, S) \hto (A, A)$ in $\Optic_{\actL, \actR}$ is \emph{lawful relative to $(F_L, F_R)$} if its image under $\Optic(F_L, F_R)$ in $\Optic_\N$ is lawful.
 \end{definition}
 
-\subsection{Examples}
-
-\subsubsection{Degenerate Optics}
+\subsection{Degenerate Optics}
 
@@
 \end{align*}
-This works for $\Review := \Optic_{\sqcup, \C_\codisc, \C}$ in the same way. There are induced functors $\Optic(\id_\C, i) : \Lens \to \Getter$ and $\Optic(i, \id_\C) : \Prism \to \Review$.
+The only sensible notion of lawfulness for $\Getter$s is lawfulness relative to $(i, \id_{\C_\codisc})$, but all optics in $\Optic_{\C_\codisc}$ are trivially lawful.
+
+One defines $\Review := \Optic_{\sqcup, \C_\codisc, \C}$ in the same way. There are induced functors $\Optic(\id_\C, i) : \Lens \to \Getter$ and $\Optic(i, \id_\C) : \Prism \to \Review$.
 
@@
 
-\subsubsection{Indexed Optics}
+\subsection{Indexed Lenses}
 As well as giving a principled home to degenerate optics, the notion of mixed optics also allows us to describe \emph{indexed optics} categorically.
-The most interesting example of an indexed optic variant is the \emph{indexed traversal}, which, for example, allows access to the indices of the entries of a list as it is being traversed.
-
-We first need to define indexed traversable functors. Unfortunately this has many moving parts!
+The most interesting example of an indexed optic variant is the \emph{indexed traversal}, which, for example, allows one to know the index of an entry of a list as one is traversing it.
+As a warmup, however, let us look at \emph{indexed lenses}, which provide access to an index alongside a target, but do not allow updates to the index.
+
+Suppose $\C$ is cartesian closed, and has an initial object. \todo{check which of these we need} We define two actions of $\C \times \C$, the first on $\C$ and the second on $\C \times \C$:
+\begin{align*}
+(M, R) \actL (A, I) &:= M \times R \times A \\
+(M, R) \actR (A, I) &:= (M \times A, R \times I)
+\end{align*}
+\todo{I could call this the ``indexed product action'' but the term indexed product is already taken of course}
+
+%\begin{definition}
+%The category of \emph{indexed lenses} $\IdxLens$ in $\C$ is the category of mixed optics with $\C \times \C^\op$ acting on the left, and the ordinary product action on the right.
+%\end{definition}
+
+%Then:
+%\begin{align*}
+%  &\int^{(M, R) \in \C \times \C^\op} (\C \times \C)((S, J), (M, R) \cdot (A, I)) \times \C(M \times A', S') \\
+%  &\cong \int^{M \in \C, R \in \C^\op} (\C \times \C)((S, J), (M \times A \times I, \homC(R, I))) \times \C(M \times A', S') \\
+%  &\cong \int^{M \in \C, R \in \C^\op} \C(S, M \times A \times I) \times \C(J, \homC(R, I)) \times \C(M \times A', S') \\
+%  &\cong \int^{R \in \C^\op} \C(S, A \times I) \times \C(J \times R, I) \times \C(S \times A', S') \\
+%  &\cong \C(S, A \times I) \times \C(J \times 0, I) \times \C(S \times A', S') \\
+%  &\cong \C(S, A \times I) \times \C(S \times A', S')
+%\end{align*}
+
+\begin{align*}
+  &\int^{(M, R) \in \C \times \C} \C(S, (M, R) \actL A) \times (\C \times \C)((M, R) \cdot (A', I'), (S', J')) \\
+  &\cong \int^{(M, R) \in \C \times \C} \C(S, M \times R \times A) \times \C(M \times A', S') \times \C(R \times I', J') \\
+  &\cong  \C(S, A) \times \C(S \times A', S') \times \C(S \times I', J')
+\end{align*}
+
+\todo{talk about polymorphism to manage the indices}
+
+\todo{do the rest of this}
+
+\subsection{Indexed Traversals}
+
+Returning to indexed traversals, we first need to define indexed traversable functors.
+Unfortunately this has many moving parts!
+For simplicity we will restrict our attention to $\C = \Set$, although the results here may be applicable more generally.
 
 \begin{proposition}
-The assignment $F \act X \mapsto F \Set(I, X)$ is a lax monoidal action of $\App$ on $\Set$, called the \emph{$I$-indexed action of $\App$ on $\Set$}.
-\end{proposition}
+The assignment $F \act X \mapsto \Set(R, FX)$ is a lax action of $\App$ on $\Set$, called the \emph{$R$-indexed action of $\App$ on $\Set$}.
+\end{proposition}
+\begin{proof}
+The structure map for the lax action is given by the composite
+\begin{align*}
+F \act (G \act X) &= \Set(R, F\Set(R, GX)) \\
+&\to \Set(R, \Set(FR, FGX)) \\
+&\to \Set(R \times FR, FGX) \\
+&\to \Set(R \times R, FGX) \\
+&\to \Set(R, FGX) = (FG) \act X
+\end{align*}
+\todo{more}
+\end{proof}
 
 \begin{definition}
-A \emph{traversable functor indexed by $I$} is a functor $T : \Set \to \Set$ equipped with a distributive law $\delta_F : T(\Set(I, F-)) \to FT$ for $T$ between the $I$-indexed action of $\App$ on $\Set$ and the action of $\App$ on $\Set$ by evaluation.
+A \emph{traversable functor indexed by $R$} is a functor $T : \Set \to \Set$ equipped with a distributive law $\delta_F : T(\Set(R, F-)) \to FT$ for $T$ between the $R$-indexed action of $\App$ on $\Set$ and the (unindexed) action of $\App$ on $\Set$ by evaluation.
 \end{definition}
@@
 \begin{definition}
-The category of \emph{indexed traversable functors} $\IdxTraversable$ has as objects pairs $(T, I)$, where $I \in \Set$ and $T : \Set \to \Set$ is a traversable functor indexed by $I$.
-A morphism $(T, I) \to (T', I')$ is a natural transformation $\alpha : T \to T'$ and morphism (note the direction!) $i : I' \to I$, such that $\alpha$ commutes with the distributive laws on both traversable functors, using $i$ to mediate between the index objects.
+The category of \emph{indexed traversable functors} $\IdxTraversable$ has as objects pairs $(T, R)$, where $R \in \Set$ and $T : \Set \to \Set$ is a traversable functor indexed by $R$.
+A morphism $(T, R) \to (T', R')$ is a natural transformation $\alpha : T \to T'$ and morphism (note the direction!) $r : R' \to R$, such that $\alpha$ commutes with the distributive laws on both traversable functors, using $r$ to mediate between the index objects.
+\todo{draw this out}
 \end{definition}
@@
 \begin{proposition}
-$\IdxTraversable$ acts on $\C \times \C$ by $(T, I) \act (A, R) \mapsto (TA, \homC(I, R))$ and on $\C$ simply by $(T, I) \act A \mapsto TA$.
+$\IdxTraversable$ acts on $\C \times \C$ by $(T, R) \act (A, I) \mapsto (TA, \homC(R, I))$ and on $\C$ simply by $(T, R) \act A \mapsto TA$.
 \end{proposition}
@@
 
-The obstacle to a good theory of mixed optics is finding the right notion of lawfulness.
-Specifically, profunctors $\C_1 \hto \C_2$ don't compose, so we cannot sensibly talk about comonoid objects in $\Prof(\C_1, \C_2)$.
-Here, techniques from \cite{MonadsNeedNotBeEndofunctors} may assist in providing a monoidal structure on $\Prof(\C_1, \C_2)$.
+\subsection{Coindexed Optics}
 
@@
 Parametricity guarantees a form of (di)naturality for $M$, $A$ and $B$, but as with any definition in Haskell, the equations required of a Tambara module must be checked by hand.
-\end{remark}
-
-\begin{remark} \todo{use this?}
-We do not explore this further in the current note, but there is a notion of Tambara module structure for profunctors between two different categories.
-This allows us to re-derive the profunctor encoding for degenerate optics.
-For example, in the case of \mintinline{haskell}{Getter}s, a profunctor $P : \C^\op \times \C_\mathsf{codisc}$ essentially ignores its covariant argument.
-This is captured exactly by the `\mintinline{haskell}{RightPhantom}' typeclass or its equivalent in profunctor optic libraries.
 \end{remark}
@@
 
+\subsection{Mixed Optics}
+\todo{todo?}
+There is a notion of Tambara module structure for profunctors between two different categories.
+This allows us to re-derive the profunctor encoding for degenerate optics.
+For example, in the case of \mintinline{haskell}{Getter}s, a profunctor $P : \C^\op \times \C_\mathsf{codisc}$ essentially ignores its covariant argument.
+This is captured exactly by the `\mintinline{haskell}{RightPhantom}' typeclass or its equivalent in profunctor optic libraries.
+
 \subsection{The van Laarhoven Encoding}
@@
 
+\todo{Consider deleting all `remark' blocks and trying to integrate the comments with the prose}
+
 \todo{Figure out the right section numbering style}

### 2018-07-30 paper.tex
Delete most remark blocks, still have to go through and try to integrate them better with the rest of the text

@@
 
-\begin{remark}
   In this section we work with a fixed symmetric monoidal category $(\C, \otimes, I)$, with associator $\alpha$ and unitors $\lambda$ and $\rho$.
 To avoid getting lost in the notation we will use the standard cheat of omitting associativity morphisms and trust that the dedicated reader could insert them everywhere they are needed.
-\end{remark}
 
@@
   For any three objects $M, A, A' \in \C$, there is the \emph{tautological} optic \[t_{M,A} : (M \otimes A, M \otimes A') \hto (A, A')\] given by $\rep{\id_{M \otimes A}}{\id_{M \otimes A'}}$.
+
+  We also have the \emph{identity} optic $\id_{(S, S')} : (S, S') \hto (S, S')$, given by $\rep{\lambda^{-1}_S}{\lambda_{S'}}$, where $\lambda_S : I \otimes S \to S$ is the left unitor for $S$ and similarly for $S'$.
 \end{example}
 
-\begin{remark}
   Elements of $\Optic_\otimes((S, S'), (A, A'))$ have an appealing
@@
   We will therefore omit the vertical cut between $l$ and $r$ in most subsequent diagrams; any choice yields a representative of same optic.
-\end{remark}
-
-\begin{remark}
+
 A common use of the coend relation is to introduce or cancel isomorphisms. Given $l : S \to M \otimes A$ and $r : M \otimes A \to S$, for any isomorphism $f : M \to N$ we have
@@
   \end{center}
-\end{remark}
-
-Two optics can be composed as follows. The easiest interpretation is graphical: composition of optics corresponds to substituting the first optic for the hole of the second:
+
+Optics compose as follows. The easiest interpretation is graphical: composition corresponds to substituting the first optic for the hole of the second:
 \begin{center}
@@
 
-The identity optic $(S, S') \hto (S, S')$ is given by $\rep{\lambda^{-1}_S}{\lambda_{S'}}$, where $\lambda_S : I \otimes S \to S$ is the left unitor for $S$:
+The identity optic is drawn as
 \begin{center}
@@
 It is common in string diagrams to omit unitors and the unit object unless they are necessary to make sense of the diagram.
-In this case, we would draw:
+We therefore prefer to draw the identity morphism as:
 \begin{center}
@@
 
-\begin{remark}
-  Note that the homsets of $\Optic_\otimes$ are given by a coend indexed by a possibly large category, so their existence is not guaranteed by the cocompleteness of $\Set$.
-We should be careful to only discuss $\Optic$ categories where we know that the coends exist by some other means, e.g., by exhibiting an isomorphism with some other set.
-For all of the examples we give, we provide such an isomorphism.
-\end{remark}
+  Note that the homsets of $\Optic_\otimes$ are given by a coend indexed by a possibly large category.
+If $\C$ is small then the coends always exist, but if not, their existence is not guaranteed by the cocompleteness of $\Set$.
+In this case we should be careful to only discuss $\Optic$ categories where we know that the coends exist by some other means, e.g., by exhibiting an isomorphism with a set.
+For all of the examples we give later, we provide such a isomorphism.
 
@@
 
-\begin{remark}
   This functor is not necessarily faithful, see Remark~\ref{lens-iota-not-faithful}.
-\end{remark}
 
@@
 
-\begin{remark}
   In the Haskell \lenslib{} library, the monoidal product on optics is denoted ``\mintinline{haskell}{alongside}'' for the product and ``\mintinline{haskell}{without}'' for the coproduct.
-\end{remark}
 
 \begin{proposition}
-  If $\C$ is a strict symmetric monoidal category then $\Optic_\otimes$ is also strict.
+  If $\C$ is a strict symmetric monoidal category then $\Optic_\otimes$ is strict, and $\iota : \C \times \C^\op \to \Optic_\otimes$ is a strict monoidal functor.
 \end{proposition}
@@
 If the latter are identities, then so are the former---the identity morphisms in $\Optic_\otimes$ are by definition $\iota(\id_S, \id_S')$.
-\end{proof}
-
-\begin{proposition}
-  $\iota : \C \times \C^\op \to \Optic_\otimes$ is a strict monoidal functor.
-\end{proposition}
-\begin{proof}
-  This is clear, as the structure morphisms in $\Optic_\otimes$ are exactly the structure morphisms in $\C \times \C^\op$ under $\iota$.
+
+  That $\iota$ is strict is clear, as the structure morphisms in $\Optic_\otimes$ are exactly the structure morphisms in $\C \times \C^\op$ under $\iota$.
 \end{proof}
@@
 \begin{proposition}\label{prop:optic-functor}
-  Collectively this operation defines a 2-functor \[\Optic : \SymmMonCat \to \SymmMonCat.\] \qed
-\end{proposition}
+  Collectively this operation defines a 2-functor \[\Optic : \SymmMonCat \to \SymmMonCat,\] where $\SymmMonCat$ denotes the 2-category of (small) symmetric monoidal categories. \qed
+\end{proposition}
+\begin{proof}
+\todo{Actually check this carefully}
 \todo{Haven't actually checked natural transformations}
-\todo{Also we run into the large coend issue again, it's not defined on every symm mon cat.}
+\end{proof}
 
@@
 
-Finally, there is a little we can say about maps out of and in to the monoidal unit. Such maps are typically called states and costates.
+Finally, there is a little we can say about maps out of and in to the monoidal unit. Such maps in a monoidal category are typically called states and costates.
 \begin{proposition}\label{prop:costates}
@@
 In particular, for any $S \in \C$, the identity $\id_S$ yields an optic $c_S = \rep{\rho_S^{-1}}{\rho_S} : (S, S) \hto (I, I)$, that we will call the \emph{connector}:
-\begin{center}
-  \input{diagrams/connector-full.tikz}
-\end{center}
-Or, again omitting the unitors:
+%\begin{center}
+%  \input{diagrams/connector-full.tikz}
+%\end{center}
+%Or, again omitting the unitors:
 \begin{center}
@@
   \end{align*}
-
 \end{proof}
@@
 \begin{example}
+  Any compact closed category is a teleological category, where every morphism is dualisable and the unit morphisms have been forgotten.
+
   Any symmetric monoidal category with terminal monoidal unit is trivially teleological, setting the dualisable morphisms to be the structure maps of the monoidal category.
@@
 
-\begin{example}
-  Any compact closed category is a teleological category, where every morphism is dualisable and the unit morphisms have been forgotten.
-\end{example}
-
-\begin{remark}
 This definition of teleological category differs from the original one, in that the duality switches the order of the tensor product.
 We do this so that compact closed categories are teleological, but the bookkeeping does admittedly become more confusing.
-\end{remark}
 
@@
 
-\begin{remark}
-  Jeremy Gibbons notes (originally in the case of ordinary lenses) that the first law is equivalent to requiring that $p$ composed with the connector $c_A$ is equal to the connector $c_S$.
+%\begin{remark}
+%  Jeremy Gibbons notes (originally in the case of ordinary lenses) that the first law is equivalent to requiring that $p$ composed with the connector $c_A$ is equal to the connector $c_S$.
 This is an appealing description from a string diagram standpoint, but it is not clear whether there is a similar description for the second law.
@@
 Should I draw a picture of this?}
-\end{remark}
+%\end{remark}
 
@@
 
-Even if $r;l = \phi A$ for some $\phi$, the same is not necessarily true of any other representative of the same optic.
+Even if $r;l = \phi A$ for some $\phi$, the same is not necessarily true for other representatives of the same optic.
 Let $\inside : \Optic_\M(S, A) \to \int^{M \in \M} \C(M A, M A)$ be the map induced by $\inside(\rep{l}{r}) = \langle r ; l \rangle$.
@@
 \begin{proof}
-  The key is that in $\Set$, for any map $f : X \to Y$, the set $Y$ is equal to the union of $\im f$ and its complement.
+  The key is that for any map $f : X \to Y$ in $\Set$, the codomain $Y$ is equal to the union of $\im f$ and its complement.
 The first law implies that $\freview$ is injective, so $S \cong C \sqcup A$ for some complement $C$.
@@
 \end{equation*}
-\begin{remark}
 It is shown in~\cite[Section 6]{ANoteOnActions} that, at least in the case $\M$ is right closed, to give such an action is equivalent to giving a ``copowered $\M$-category $\C$''.
 \todo{Pointed out to me years ago when I emailed Ross Street, but I didn't understand what he was saying}
-\end{remark}
 
@@
 
-\begin{remark}
 This characterisation of setters is maybe a little odd, in that we have ended up with a function of $\Set$s, rather than a description internal to $\C$.
-If we modify our definition of $\Setter$, we can get such an internal characterisation.
+If we modify our definition of $\Setter$, we do get an internal characterisation.
 Suppose $\C$ is cartesian closed and let $\Strong_\C$ be the category of \emph{strong functors} on $\C$.
@@
 %The use of strong functors here is due to the correspondence between tensorial strengths and ``$\C$-enrichments'' on a functor.
-\end{remark}
 
@@
 
-\begin{remark}
 We have essentially rederived the result given in \cite[Section 3.2]{RelatingAlgebraicAndCoalgebraic} for ordinary lenses, but we note that cartesianness was not required.
-\end{remark}
 
@@
 
-\begin{remark}
 Of course, this notion of effectful lens may not be useful at all!
@@
 On the other hand, our $\fput\fget$ law seems very difficult to satisfy: no matter what auxiliary state is provided, putting then getting must leave the state unchanged.
-\end{remark}
 
@@
 
-\begin{remark}
 If we we are working linearly, we should not expect $\Optic_{\otimes, \C, \C_\codisc}$ to be described so neatly; the above isomorphism relies on the unit of the monoidal structure being terminal.
-\end{remark}
 
@@
 
-\begin{remark}
   In the code, the \mintinline{haskell}{Strong} typeclass corresponds to supplying the structure map $\alpha$ for a profunctor \texttt{p}.
 Parametricity guarantees a form of (di)naturality for $M$, $A$ and $B$, but as with any definition in Haskell, the equations required of a Tambara module must be checked by hand.
-\end{remark}
-
-There is an evident forgetful functor $U : \Tamb(\M) \to \Prof(\C, \C)$ that is strong monoidal. This forgetful functor has both a left and right adjoint; important for us is the left adjoint:
+
+There is an evident forgetful functor $U : \Tamb(\M) \to \Prof(\C, \C)$ that is strong monoidal.
+This forgetful functor has both a left and right adjoint; important for us is the left adjoint: (The right adjoint to $U$ is described in~\cite{NotionsOfComputationAsMonoids}, used there to investigate Haskell's \mintinline{haskell}{Arrow} typeclass.)
 
@@
 \end{proof}
-
-\begin{remark}
-  The right adjoint to $U$ is described in~\cite{NotionsOfComputationAsMonoids} to investigate Haskell's \mintinline{haskell}{Arrow} typeclass.
-\end{remark}
 
@@
 
-\begin{remark}
   This proposition justifies the profunctor encoding
@@
   \todo{I've just noticed, isn't this a cheat? This would be naturality wrt ALL profunctor morphisms, not just morphisms of Tambara modules. Can I find a place where this breaks?}
-\end{remark}
 
@@
 
-\begin{remark}
   For Haskell's profunctor lenses, these laws take the form:
@@
 \end{minted}
-\end{remark}
 
@@
 
-\begin{remark}
 A consequence is that the laws typically given for $\Traversal$s actually only need to be checked for the applicative functor we called $UR^*$.
 In Haskell this is implemented as \mintinline{haskell}{FunList}~\cite{FunListPost} or \mintinline{haskell}{Bazaar}~\cite{LensLibrary}.
-\end{remark}
 

### 2018-08-01 paper.tex
Finish proving Optic is a 2-functor

@@
 
-In its most concrete form, a \emph{lens}~\cite{CombinatorsForBidirectionalTreeTransformations} from a set $S$ to a set $A$ is a pair of maps ${\fget : S \to A}$ and ${\fput : S \times A \to S}$.
-From an engineering standpoint, such a lens allows us to ``zoom in'' on $S$ to focus on a small part $A$, manipulate $A$ in some way, then ``zoom out'' and have our changes reflected in $S$.
+In its most concrete form, a \emph{lens} $S \hto A$ is a pair of maps ${\fget : S \to A}$ and ${\fput : S \times A \to S}$.
+From an engineering standpoint, such a lens allows us to ``zoom in'' on $S$ to focus on a small part $A$, manipulate $A$ in some way, then ``zoom out'' and have our changes reflected in $S$~\cite{CombinatorsForBidirectionalTreeTransformations}.
 
@@
 \]
-\hspace{-0.8cm}$\fget\fput$
+\hspace{-0.6cm}$\fget\fput$
 \end{center}
@@
 
-%Lenses form a category, with the composition of lenses $T \hto S$ and $S \hto A$ as indicated:
-%\begin{align*}
-%\fget &: T \xrightarrow{\fget_1} S \xrightarrow{\fget_2} A \\
-%\fput &: T \times A \xrightarrow{[\id_T, \fget_1, \id_A]} T \times S \times A \xrightarrow{T \times \fput_2} T \times S \xrightarrow{\fput_1} T
-%\end{align*}
+Lenses form a category, with the composition of lenses $(\fget_1, \fput_1) : T \hto S$ and $(\fget_2, \fput_2) : S \hto A$ as indicated:
+\begin{align*}
+\fget &: T \xrightarrow{\fget_1} S \xrightarrow{\fget_2} A \\
+\fput &: T \times A \xrightarrow{[\id_T, \fget_1] \times A} T \times S \times A \xrightarrow{T \times \fput_2} T \times S \xrightarrow{\fput_1} T
+\end{align*}
 %This composition preserves lawfulness.
@@
 
-Lenses were discovered to be just one of a hierarchy of data accessors, including prisms, setters, traversals, and more, collectively called \emph{optics}.
+Lenses were discovered to be just one of a hierarchy of data accessors, including prisms, setters, traversals and more, collectively called \emph{optics}.
 Each optic variant has a concrete description as a certain collection of maps, with attendant laws under which we consider them well-behaved.
@@
 
-  We check associativity of composition equationally.
-Suppose we have representatives of three optics $\rep{l_1}{r_1} : (R, R) \hto (S, S')$, $\rep{l_2}{r_2} : (S, S') \hto (A, A')$ and $\rep{l_3}{r_3} : (A, A') \hto (B, B')$, that have residuals $M$, $N$ and $P$ respectively.
-As in the definition of composition, the Fubini theorem for coends allows us to choose these representatives simultaneously.
-Then:
+  We check associativity of composition equationally.  Suppose we have representatives of three optics 
+\begin{align*}
+  \rep{l_1}{r_1} &: (R, R) \hto (S, S') \\
+  \rep{l_2}{r_2} &: (S, S') \hto (A, A') \\
+  \rep{l_3}{r_3} &: (A, A') \hto (B, B'),
+\end{align*}
+that have residuals $M$, $N$ and $P$ respectively. As in the definition of composition, the Fubini theorem for coends allows us to choose these representatives simultaneously. Then:
   \begin{align*}
@@
   \end{align*}
-  In both cases we have used the naturality of $\lambda$ followed by the coend relations to move $\lambda^{-1}_M$ to the right-hand side, where it may be cancelled with $\lambda_M$
+  In both cases we have used the naturality of $\lambda$ followed by the coend relation to move $\lambda^{-1}_M$ to the right-hand side, where it may be cancelled with $\lambda_M$.
 \end{proof}
@@
 If $\C$ is small then the coends always exist, but if not, their existence is not guaranteed by the cocompleteness of $\Set$.
-In this case we should be careful to only discuss $\Optic$ categories where we know that the coends exist by some other means, e.g., by exhibiting an isomorphism with a set.
+In this case we should be careful to only discuss $\Optic$ categories where we know that the coends exist by some other means, e.g., by exhibiting an isomorphism of $\Optic_\C((S, S'), (A, A'))$ with a set.
 For all of the examples we give later, we provide such a isomorphism.
@@
   \end{center}
-
-\end{proof}
-
-  This functor is not necessarily faithful, see Remark~\ref{lens-iota-not-faithful}.
+\end{proof}
+%  This functor is not necessarily faithful, see Remark~\ref{lens-iota-not-faithful}.
+
+There are some other easy-to-construct optics; specifically, optics out of  and into the monoidal unit $(I, I)$. Such maps in a monoidal category are typically called states and costates.
+\begin{proposition}\label{prop:costates}
+  The set of costates $(S, S') \hto (I, I)$ is isomorphic to $\C(S, S')$.
+\end{proposition}
+\begin{proof}
+  \begin{align*}
+    \Optic_\otimes((S, S'), (I, I))
+    &= \int^{M \in \C} \C(S, M \otimes I) \times \C(M \otimes I, S') \\
+    &\cong \int^{M \in \C} \C(S, M) \times \C(M, S') \\
+    &\cong \C(S, S')
+  \end{align*}
+  by Yoneda reduction.
+\end{proof}
+
+%\todo{Is there a relationship between $\Optic_\otimes/(I, I)$ and $[2, \C]$?}
+
+In particular, for any $S \in \C$, the identity $\id_S$ yields an optic $c_S = \rep{\rho_S^{-1}}{\rho_S} : (S, S) \hto (I, I)$, that we will call the \emph{connector}:
+%\begin{center}
+%  \input{diagrams/connector-full.tikz}
+%\end{center}
+%Or, again omitting the unitors:
+\begin{center}
+  \input{diagrams/connector.tikz}
+\end{center}
+
+\begin{proposition}
+  Suppose the monoidal unit $I$ of $\C$ is terminal. Then the set of states $(I, I) \hto (A, A')$ is isomorphic to $\C(I, A)$.
+\end{proposition}
+\begin{proof}
+  First, note that
+  \begin{align*}
+    \Optic_\otimes((I,I), (A,A'))
+    &= \int^{M \in \C} \C(I, M \otimes A) \times \C(M \otimes A', I) \\
+    &\cong \int^{M \in \C} \C(I, M \otimes A).
+  \end{align*}
+  as $I$ is terminal.
+The interior of this coend is mute in the contravariant position, so the coend is equal to the colimit of the functor $\C(I, - \otimes A) : \C \to \Set$.
+But $\C$ has terminal object $I$, so \[\int^{M \in \C} \C(I, M \otimes A) \cong \C(I, I \otimes A) \cong \C(I, A).\]
+\end{proof}
+
+The remainder of this section comprises a proof of the following fact:
+
+\begin{theorem}\label{thm:optic-functor}
+  Collectively the $\Optic_\C$ construction defines a strict 2-functor \[\Optic : \SymmMonCat \to \SymmMonCat,\] where $\SymmMonCat$ denotes the 2-category of (small) symmetric monoidal categories, symmetric monoidal functors and monoidal natural transformations.
+\end{theorem}
 
@@
 
-\begin{proposition}
+\begin{lemma}\label{lem:iota-commute-with-opticf}
+$\iota$ commutes with $\Optic(F)$, in the sense that
+\[ \Optic(F)(\iota(f, g)) = \iota(Ff, Fg) \]
+\end{lemma}
+\begin{proof}
+This is a straightforward calculation:
+  \begin{align*}
+    \Optic(F)\iota(f, g)
+    &= \Optic(F)(\rep{\lambda_A^{-1} f}{g \lambda_{A'}}) \\
+    &= \rep{\phi^{-1}_{I,A} (F(\lambda_A^{-1} f))}{(F(g \lambda_{A'})) \phi_{I,A'}} \\
+    &= \rep{\phi^{-1}_{I,A} (F\lambda_A^{-1}) (Ff)}{(Fg)(F \lambda_{A'}) \phi_{I,A'}} \\
+    &= \rep{(\phi^{-1}_I \otimes FA) \phi^{-1}_{I,A} (F\lambda_A^{-1}) (Ff)}{(Fg)(F \lambda_{A'}) \phi_{I,A'} (\phi_I \otimes FA)} \\
+    &= \rep{\lambda_{FA}^{-1} (Ff)}{(Fg)\lambda_{FA'}} \\
+    &= \iota(Ff, Fg)
+  \end{align*}
+\end{proof}
+
+\begin{proposition}\label{prop:iota-naturality}
 $\iota : \C \times \C^\op \to \Optic_\otimes$ ``lifts natural isomorphisms'', in the following sense.
@@
   \end{center}
-  Use the coend relation to place an $\alpha$ on either side:
+  We use the coend relation to place an $\alpha$ on either side:
   \begin{center}
@@
   \end{center}
-  Finally, $\alpha$ pushes through $F l$ and $F r$ by naturality.
+  Finally, $\alpha$ commutes with $F l$ and $F r$ by naturality.
   \begin{center}
@@
 
-  Let us check functoriality of $\otimes$. Suppose we have optics:
+  To check functoriality of $\otimes$, suppose we have optics
   \begin{align*}
@@
     \rep{p_1}{q_1} : (T_1, T_1') &\hto (T_2, T_2') \\
-    \rep{p_2}{q_2} : (T_2, T_2') &\hto (T_3, T_3')
+    \rep{p_2}{q_2} : (T_2, T_2') &\hto (T_3, T_3').
   \end{align*}
@@
 \end{align*}
-The axioms follow by lifting the axioms for $F$. More difficult is verifying naturality: \todo{todo!}
-\end{proof}
-
-To summarise:
-
-\begin{proposition}\label{prop:optic-functor}
-  Collectively this operation defines a 2-functor \[\Optic : \SymmMonCat \to \SymmMonCat,\] where $\SymmMonCat$ denotes the 2-category of (small) symmetric monoidal categories. \qed
-\end{proposition}
-\begin{proof}
-\todo{Actually check this carefully}
-\todo{Haven't actually checked natural transformations}
+The monoidality axioms follow by lifting the axioms for $F$. Naturality follows by Proposition~\ref{prop:iota-naturality}.
+\end{proof}
+
+\begin{proof}[Proof of Theorem \ref{thm:optic-functor}]
+The functor is well defined on its domain: if $\C$ is small then $\Optic_\C$ exists. There are only a few properties that remain to be checked:
+
+First, functoriality on 1-cells, i.e., that for monoidal functors $F : \C \to \D$ and $G : \D \to \E$ we have
+\[ \Optic(G) \circ \Optic(F) = \Optic(G \circ F).\]
+On objects this is clear, as $\Optic(F)(S, S') = (FS, FS')$. On a morphism $\rep{l}{r} : (S, S') \hto (A, A')$ in $\C$, we check:
+\begin{align*}
+(\Optic(G) \circ \Optic(F))(\rep{l}{r}) 
+&= \Optic(G) \left(\rep{\phi^{-1}_{M,A} (Fl)}{(Fr) \phi_{M,A'}}\right) \\
+&= \rep{\psi^{-1}_{FM,FA} (G(\phi^{-1}_{M,A} (Fl)))}{(G((Fr) \phi_{M,A'}))\psi_{FM,FA'}} \\
+&= \rep{\psi^{-1}_{FM,FA} (G\phi^{-1}_{M,A}) (GFl)}{(GFr) (G\phi_{M,A'})\psi_{FM,FA'}} \\
+&=\Optic(G \circ F)(\rep{l}{r})
+\end{align*}
+where $\phi$ and $\psi$ denote the structure maps for $F$ and $G$ respectively, and in the last step we use that $(G\phi_{M,A'})\psi_{FM,FA'}$ is by definition the structure map for $G \circ F$.
+Checking that the identity is preserved is similar.
+
+Secondly, we note that $\Optic$ acts functorially on 2-cells. The action on 2-cells is given by Proposition~\ref{prop:iota-naturality}, and functoriality follows by the functoriality of $\iota$.
+
+Finally, we check that horizontal composition is preserved.
+Horizontal composition in $\SymmMonCat$ is defined in terms of whiskering and vertical composition, so it suffices to verify that whiskering is preserved.
+But indeed it is:
+\begin{align*}
+\Optic(F\alpha)_{(S, S')} 
+&= \iota((F\alpha)_{S}, (F\alpha)^{-1}_{S'}) \\
+&= \iota(F(\alpha_{S}), F(\alpha_{S'}^{-1})) \\
+&= (\Optic(F)\Optic(\alpha))_{(S, S')} 
+\end{align*}
+by Lemma~\ref{lem:iota-commute-with-opticf}, and
+\begin{align*}
+\Optic(\alpha G)_{(S, S')} 
+&= \iota(\alpha_{GS}, \alpha_{GS'}^{-1}) \\
+&= \iota((\alpha G)_{S}, (\alpha G)_{S'}^{-1}) \\
+&= (\Optic(\alpha)\Optic(G))_{(S, S')} 
+\end{align*}
 \end{proof}
@@
 % \end{proof}
-
-Finally, there is a little we can say about maps out of and in to the monoidal unit. Such maps in a monoidal category are typically called states and costates.
-\begin{proposition}\label{prop:costates}
-  The set of costates $(S, S') \hto (I, I)$ is isomorphic to $\C(S, S')$.
-\end{proposition}
-\begin{proof}
-  \begin{align*}
-    \Optic_\otimes((S, S'), (I, I))
-    &= \int^{M \in \C} \C(S, M \otimes I) \times \C(M \otimes I, S') \\
-    &\cong \int^{M \in \C} \C(S, M) \times \C(M, S') \\
-    &\cong \C(S, S')
-  \end{align*}
-\end{proof}
-
-%\todo{Is there a relationship between $\Optic_\otimes/(I, I)$ and $[2, \C]$?}
-
-In particular, for any $S \in \C$, the identity $\id_S$ yields an optic $c_S = \rep{\rho_S^{-1}}{\rho_S} : (S, S) \hto (I, I)$, that we will call the \emph{connector}:
-%\begin{center}
-%  \input{diagrams/connector-full.tikz}
-%\end{center}
-%Or, again omitting the unitors:
-\begin{center}
-  \input{diagrams/connector.tikz}
-\end{center}
-
-\begin{proposition}
-  Suppose the monoidal unit $I$ of $\C$ is terminal. Then the set of states $(I, I) \hto (A, A')$ is isomorphic to $\C(I, A)$.
-\end{proposition}
-\begin{proof}
-  First, note that
-  \begin{align*}
-    \Optic_\otimes((I,I), (A,A'))
-    &= \int^{M \in \C} \C(I, M \otimes A) \times \C(M \otimes A', I) \\
-    &\cong \int^{M \in \C} \C(I, M \otimes A).
-  \end{align*}
-  Because the interior of this coend is mute in the contravariant position, the coend is equal to the colimit of the functor $\C(I, - \otimes A) : \C \to \Set$.
-But $\C$ has a terminal object, so $\int^{M \in \C} \C(I, M \otimes A) \cong \C(I, I \otimes A) \cong \C(I, A)$.
-\end{proof}
 
@@
   Any compact closed category is a teleological category, where every morphism is dualisable and the unit morphisms have been forgotten.
-
 Any symmetric monoidal category with terminal monoidal unit is trivially teleological, setting the dualisable morphisms to be the structure maps of the monoidal category.
@@
 
-This definition of teleological category differs from the original one, in that the duality switches the order of the tensor product.
+This definition of teleological category differs from the one given in~\cite{CoherenceForLenses}, in that the duality switches the order of the tensor product.
 We do this so that compact closed categories are teleological, but the bookkeeping does admittedly become more confusing.
@@
 
-The definition of teleological category suggests a string diagram calculus similar to that for compact closed categories, but where only counits exist, and only morphisms known to be dualisable may be passed around a counit by extranaturality.
+The definition of teleological category suggests a string diagram calculus similar to that for compact closed categories, but where only counits exist and only morphisms known to be dualisable may be passed around a counit.
 We have of course not proven that such a calculus is sound for teleological categories, but we trust that a sceptical reader could verify our arguments equationally.
@@
   To check extranaturality of $\varepsilon$, suppose we have a dualisable optic $\iota(f, g) : (S, S') \hto (T, T')$, so $f : S \to T$ and $g : T' \to S'$.
-Luckily here all the switching in the definitions cancel out!
+Happily, all the switching in the definitions cancels out!
 Extranaturality is witnessed by the equality of the string diagrams:
@@
   \end{center}
-  For symmetry:
+  Symmetry of $\varepsilon$ by:
   \begin{center}
@@
   \end{center}
-  And for monoidality there is essentially nothing to do in the graphical calculus.
+  And for monoidality of $\varepsilon$ there is essentially nothing to do in the graphical calculus:
   \begin{center}
@@
 \begin{proposition}
-  The functor $\Optic : \SymmMonCat \to \SymmMonCat$ of Proposition~\ref{prop:optic-functor} has its image in the subcategory $\Tele$.
-\end{proposition}
-\begin{proof}
-  We must show that for a symmetric monoidal functor $F : \C \to \D$, the induced functor $F : \Optic_\C \to \Optic_\D$ is teleological.
-
-  First, $F$ preserves the dualisable morphisms. If $\iota(f, g) : (S, S') \hto (A, A')$,
-  \begin{align*}
-    F\iota(f, g)
-    &= F(\rep{\lambda_A^{-1} f}{g \lambda_{A'}}) \\
-    &= \rep{\phi^{-1}_{I,A} (F(\lambda_A^{-1} f))}{(F(g \lambda_{A'})) \phi_{I,A'}} \\
-    &= \rep{\phi^{-1}_{I,A} (F\lambda_A^{-1}) (Ff)}{(Fg)(F \lambda_{A'}) \phi_{I,A'}} \\
-    &= \rep{(\phi^{-1}_I \otimes FA) \phi^{-1}_{I,A} (F\lambda_A^{-1}) (Ff)}{(Fg)(F \lambda_{A'}) \phi_{I,A'} (\phi_I \otimes FA)} \\
-    &= \rep{\lambda_{FA}^{-1} (Ff)}{(Fg)\lambda_{FA'}} \\
-    &= \iota(Ff, Fg)
-  \end{align*}
-
-  And it also preserves the counits:
-  \begin{align*}
-    F(\varepsilon_{(S, S')})
-    &= F(c_{S \otimes S'}) \\
-    &= F(\rep{\rho_S^{-1}}{\rho_{S'}}) \\
+  The 2-functor $\Optic : \SymmMonCat \to \SymmMonCat$ of Theorem~\ref{thm:optic-functor} has its image in the sub-2-category $\Tele$.
+\end{proposition}
+\begin{proof}
+  We must show that for a symmetric monoidal functor $F : \C \to \D$, the induced functor $\Optic(F) : \Optic_\C \to \Optic_\D$ is teleological.
+That $\Optic(F)$ preserves the dualisable morphisms is exactly Lemma~\ref{lem:iota-commute-with-opticf}.
+It also preserves the counits:
+  \begin{align*}
+    \Optic(F)(\varepsilon_{(S, S')})
+    &= \Optic(F)(c_{S \otimes S'}) \\
+    &= \Optic(F)(\rep{\rho_S^{-1}}{\rho_{S'}}) \\
     &= \rep{\phi^{-1}_{S,I} (F \rho_S^{-1})}{(F \rho_{S'}) \phi_{S',I}} \\
@@
 
-%  \todo{This works fine when $\C$ is not strict}
+For a natural transformation $\alpha : F \Rightarrow F'$, the induced natural transformation $\Optic(\alpha) : \Optic(F) \Rightarrow \Optic(F')$ has dualisable components by definition.
+Compatibility with the dualisation functor is immediate: for any object $(S, S')$, we have $(\Optic(\alpha)_{(S, S')})^* = \Optic(\alpha)_{(S, S')^*}$ on the nose.
 \end{proof}
@@
   \]
-  A \emph{strong natural transformation} $\tau : (F,\theta) \to (G,\theta')$ is a natural transformation that respects the strengths.
+  A \emph{strong natural transformation} $\tau : (F,\theta) \Rightarrow (G,\theta')$ is a natural transformation that respects the strengths.
 There is an evident category $\Strong(\C)$ of strong endofunctors and strong natural transformations, and a forgetful functor $U : \Strong(\C) \to [\C, \C]$.
@@
 The category of \emph{indexed traversable functors} $\IdxTraversable$ has as objects pairs $(T, R)$, where $R \in \Set$ and $T : \Set \to \Set$ is a traversable functor indexed by $R$.
-A morphism $(T, R) \to (T', R')$ is a natural transformation $\alpha : T \to T'$ and morphism (note the direction!) $r : R' \to R$, such that $\alpha$ commutes with the distributive laws on both traversable functors, using $r$ to mediate between the index objects.
+A morphism $(T, R) \to (T', R')$ is a natural transformation $\alpha : T \Rightarrow T'$ and morphism (note the direction!) $r : R' \to R$, such that $\alpha$ commutes with the distributive laws on both traversable functors, using $r$ to mediate between the index objects.
 \todo{draw this out}
@@
 
-For $p : S \hto A$, let $\tilde{p} : (U-)(A,A) \rightarrow (U-)(S,S)$ denote the corresponding natural transformation under this isomorphism, and for $t : (U-)(A,A) \rightarrow (U-)(S,S)$, let $\hat{t} : S \hto A$ be the corresponding optic.
+For $p : S \hto A$, let $\tilde{p} : (U-)(A,A) \Rightarrow (U-)(S,S)$ denote the corresponding natural transformation under this isomorphism, and for $t : (U-)(A,A) \Rightarrow (U-)(S,S)$, let $\hat{t} : S \hto A$ be the corresponding optic.
 
@@
   For an object $X$ in a monoidal category $(\C, \otimes, I)$, a comonoid structure $(X,\Delta,\varepsilon)$ is equivalent to a lax monoidal structure on $\C(X, -)$.
-Further, comonoid morphisms $(X_1,\Delta_1,\varepsilon_1) \to (X_2,\Delta_2,\varepsilon_2)$ are equivalent to monoidal natural transformations $\C(X, -) \to \C(Y, -)$.
+Further, comonoid morphisms $(X_1,\Delta_1,\varepsilon_1) \to (X_2,\Delta_2,\varepsilon_2)$ are equivalent to monoidal natural transformations $\C(X, -) \Rightarrow \C(Y, -)$.
 \end{lemma}
@@
 \begin{theorem}
-  $p : S \hto A$ is a lawful optic iff the associated natural transformation $\tilde{p} : (U-)(A,A) \to (U-)(S,S)$ is monoidal with respect to the canonical lax monoidal structures on $(U-)(A,A)$ and $(U-)(S,S)$.
+  $p : S \hto A$ is a lawful optic iff the associated natural transformation $\tilde{p} : (U-)(A,A) \Rightarrow (U-)(S,S)$ is monoidal with respect to the canonical lax monoidal structures on $(U-)(A,A)$ and $(U-)(S,S)$.
 \end{theorem}
@@
 To form a category, one must consider learners up to an equivalence relation on the sets $P$.
-There is an alternate slick description of the set of learners $A \hto B$: note that the data of a learner is describing an element of the coend
+There is an alternate slick description of the set of learners $A \hto B$, that goes as follows.
+Note that the data of a learner is describing an element of the coend
 \begin{align*}
@@
 Composition of learners can be defined analogously to composition for optics.
-This perspective explains the slight fussing around required in dealing with equivalence classes of learners, and suggests a generalisation to other monoidal settings.
+This perspective explains the slight fussing around required in dealing with equivalence classes of learners, and suggests a generalisation to other monoidal categories.
 
@@
 
-\todo{Consider deleting all `remark' blocks and trying to integrate the comments with the prose}
-
 \todo{Figure out the right section numbering style}
@@
 \todo{Somewhere spell out the connection between $\Pastro_\M E_A$ and $\Optic(-, A)$.}
-
-\todo{Consistently use $\Rightarrow$ for natural transformations everywhere?}
 

### 2018-08-06 paper.tex
State of play before I try and finish teleological bit

@@
 
-Lenses form a category, with the composition of lenses $(\fget_1, \fput_1) : T \hto S$ and $(\fget_2, \fput_2) : S \hto A$ as indicated:
+Lenses form a category, with the composition of two lenses $(\fget_1, \fput_1) : T \hto S$ and $(\fget_2, \fput_2) : S \hto A$ as indicated:
 \begin{align*}
@@
 \end{align*}
-%This composition preserves lawfulness.
-%\todo{reference a whole bunch of bx and database stuff}
+If the two input lenses are lawful, the composite is as well.
 
@@
 We begin in Section~\ref{sec:optics} by defining the \emph{category of optics} in a sufficiently general way to encompass almost all the optic variants in use in the wild, using lenses as a running example.
+The category of lenses is precisely the result of this construction when applied to a category with finite products.
 Section~\ref{sec:lawful-optics} defines the equivalent of the lens laws for a general category of optics.
 Then in Section~\ref{sec:examples} we see that these generic definitions specialise correctly to the other basic varieties of optic, including giving the correct laws.
-We include Section~\ref{sec:mixed-optics} a more speculative discussion of ``mixed optics'', which include indexed and coindexed lenses and traversals.
+We include in Section~\ref{sec:mixed-optics} a more speculative discussion of ``mixed optics'', which include indexed and coindexed lenses and traversals.
 
@@
 \begin{theorem}\label{thm:optic-functor}
-  Collectively the $\Optic_\C$ construction defines a strict 2-functor \[\Optic : \SymmMonCat \to \SymmMonCat,\] where $\SymmMonCat$ denotes the 2-category of (small) symmetric monoidal categories, symmetric monoidal functors and monoidal natural transformations.
+  The $\Optic_\C$ construction extends to a strict 2-functor \[\Optic : \SymmMonCat \to \SymmMonCat,\] where $\SymmMonCat$ denotes the 2-category of (small) symmetric monoidal categories, symmetric monoidal functors and monoidal natural transformations.
 \end{theorem}
@@
 \begin{proposition}\label{prop:change-of-action-monoidal}
-  A monoidal functor $F : \C \to \D$ induces a functor $\Optic(F) : \Optic_\C \to \Optic_\D$.
-On objects this is $\Optic(F)(S, S') = (FS, FS')$, and on a morphism $\rep{l}{r} : (S, S') \to (A, A')$, is
+  A monoidal functor $F : \C \to \D$ induces a functor $\Optic(F) : \Optic_\C \to \Optic_\D$, that on objects is $\Optic(F)(S, S') = (FS, FS')$ and on a morphism $\rep{l}{r} : (S, S') \to (A, A')$, is
   \begin{align*}
@@
   \end{align*}
-  where $\phi_{M,A} : FM \otimes FA \to F(M \otimes A)$ is the structure map of the monoidal functor. Graphically:
+  where $\phi_{M,A} : FM \otimes FA \to F(M \otimes A)$ denotes the structure map of the monoidal functor. Graphically:
   \begin{center}
@@
 \end{align*}
-The critical move is adding the isomorphism $(\phi_{M', M} \otimes A)$ to both sides of the coend, so that the hexagon axiom for $F$ can be applied.
+The critical move is adding the isomorphism $(\phi_{M', M} \otimes A)$ to both sides of the coend, so that the hexagon axiom for $F$ may be applied.
 \end{proof}
@@
 \begin{align*}
-\Optic(\alpha)_{(S, S')} &: (FS, FS') \to (GS, GS') \\
-\Optic(\alpha)_{(S, S')} &:= \iota(\alpha_{S}, \alpha^{-1}_{S'})
+{\Optic(\alpha)}_{(S, S')} &: (FS, FS') \to (GS, GS') \\
+{\Optic(\alpha)}_{(S, S')} &:= \iota(\alpha_{S}, \alpha^{-1}_{S'})
 \end{align*}
@@
 Suppose $\phi$ and $\psi$ are the structure maps for $F$ and $G$ respectively.
-We just have to show naturality, i.e.
-that for $p : (S, S') \hto (A, A')$ in $\D$, the equation \[\Optic(\alpha)_{(A, A')} \circ \Optic(F)(p) = \Optic(G)(p) \circ \Optic(\alpha)_{(S, S')}\] holds.
+We just have to show naturality, i.e.\ that for $p : (S, S') \hto (A, A')$ in $\D$, the equation \[\Optic(\alpha)_{(A, A')} \circ \Optic(F)(p) = \Optic(G)(p) \circ \Optic(\alpha)_{(S, S')}\] holds.
 On the left we have:
@@
   \end{center}
-  This is the diagram for $\Optic(G)(p) \circ \Optic(\alpha)_{(S, S')}$.
+  This is the diagram for $\Optic(G)(p) \circ {\Optic(\alpha)}_{(S, S')}$.
 \end{proof}
@@
 
-\begin{proof}[Proof of Theorem \ref{thm:optic-functor}]
+\begin{proof}[Proof of Theorem~\ref{thm:optic-functor}]
 The functor is well defined on its domain: if $\C$ is small then $\Optic_\C$ exists. There are only a few properties that remain to be checked:
@@
 \begin{align*}
-\Optic(F\alpha)_{(S, S')} 
-&= \iota((F\alpha)_{S}, (F\alpha)^{-1}_{S'}) \\
+{\Optic(F\alpha)}_{(S, S')}
+&= \iota({(F\alpha)}_{S}, {(F\alpha)}^{-1}_{S'}) \\
 &= \iota(F(\alpha_{S}), F(\alpha_{S'}^{-1})) \\
-&= (\Optic(F)\Optic(\alpha))_{(S, S')} 
+&= {(\Optic(F)\Optic(\alpha))}_{(S, S')}
 \end{align*}
@@
 \begin{align*}
-\Optic(\alpha G)_{(S, S')} 
+{\Optic(\alpha G)}_{(S, S')}
 &= \iota(\alpha_{GS}, \alpha_{GS'}^{-1}) \\
-&= \iota((\alpha G)_{S}, (\alpha G)_{S'}^{-1}) \\
-&= (\Optic(\alpha)\Optic(G))_{(S, S')} 
+&= \iota({(\alpha G)}_{S}, {(\alpha G)}_{S'}^{-1}) \\
+&= {(\Optic(\alpha)\Optic(G))}_{(S, S')}
 \end{align*}
@@
 
-We assume in this section that $\C$ is a \emph{strict} symmetric monoidal category. It will be convenient to equip $\Optic_\otimes$ with a slightly different symmetric monoidal structure.
+We assume in this section that $\C$ is a \emph{strict} monoidal category. It will be convenient to equip $\Optic_\otimes$ with a slightly different symmetric monoidal structure.
 
@@
 
+We now define the structure on a monoidal category universally provided by the $\Optic$ construction.
+
 \begin{definition}[Compare {\cite[Definition 5.1]{CoherenceForLenses}}]
@@
   \item A symmetric monoidal subcategory $\C_d$ of \emph{dualisable morphisms} containing all the objects of $\C$, with an involutive symmetric monoidal functor ${(-)}^* : \C_d \to \overline{\C_d^\op}$, where---not finding a standard symbol for such a thing---we mean $\overline{\C_d^\op}$ to be the category with both the direction of the arrows \emph{and} the order of the tensor flipped: ${(A \otimes B)}^* \cong B^* \otimes A^*$.
-Note that there is therefore a canonical isomorphism $\phi : I \cong I^*$
+Note that there is therefore also a canonical isomorphism $\phi : I \cong I^*$
   \item A symmetric monoidal extranatural family of morphisms $\varepsilon_X : X \otimes X^* \to I$, called \emph{counits}, natural with respect to the morphisms in $\C_d$.
@@
   Any compact closed category is a teleological category, where every morphism is dualisable and the unit morphisms have been forgotten.
-Any symmetric monoidal category with terminal monoidal unit is trivially teleological, setting the dualisable morphisms to be the structure maps of the monoidal category.
 \end{example}
-
-This definition of teleological category differs from the one given in~\cite{CoherenceForLenses}, in that the duality switches the order of the tensor product.
+\begin{example}
+  Any symmetric monoidal category with terminal monoidal unit is trivially teleological, setting the dualisable morphisms to be all isomorphisms.
+\end{example}
+
+This definition of teleological category differs from the original given in~\cite{CoherenceForLenses}, in that the duality switches the order of the tensor product.
 We do this so that compact closed categories are teleological, but the bookkeeping does admittedly become more confusing.
@@
 \begin{definition}
-  A \emph{teleological functor} $F : \C \to \D$ is a symmetric monoidal functor that restricts to a functor $F_d : \C_d \to \D_d$ on the dualisable subcategories, commutes with the duality via a monoidal natural isomorphism $d_X : F(X^*) \to (FX)^*$, and such that the counits are preserved:
+  A \emph{teleological functor} $F : \C \to \D$ is a symmetric monoidal functor that restricts to a functor $F_d : \C_d \to \D_d$ on the dualisable subcategories, commutes with the duality via a monoidal natural isomorphism $d_X : F(X^*) \to {(FX)}^*$, and such that the counits are preserved:
   \[
@@
   \begin{tikzcd}
-    (FX)^* \ar[r, "\cong"]  \ar[d, "(\alpha_X)^*", swap] & F(X^*) \ar[d, "\alpha_{X^*}"] \\
-    (GX)^* \ar[r, "\cong", swap] & G(X^*)
+    {(FX)}^* \ar[r, "\cong"]  \ar[d, "(\alpha_X)^*", swap] & F(X^*) \ar[d, "\alpha_{X^*}"] \\
+    {(GX)}^* \ar[r, "\cong", swap] & G(X^*)
   \end{tikzcd}
@@
 For a natural transformation $\alpha : F \Rightarrow F'$, the induced natural transformation $\Optic(\alpha) : \Optic(F) \Rightarrow \Optic(F')$ has dualisable components by definition.
-Compatibility with the dualisation functor is immediate: for any object $(S, S')$, we have $(\Optic(\alpha)_{(S, S')})^* = \Optic(\alpha)_{(S, S')^*}$ on the nose.
+Compatibility with the dualisation functor is immediate: for any object $(S, S')$, we have $({\Optic(\alpha)}_{(S, S')})^* = {\Optic(\alpha)}_{(S, S')^*}$ on the nose.
 \end{proof}
@@
 \begin{theorem}\label{optic-is-free-teleological-cat}
-  Suppose $\C$ is a strict symmetric monoidal category and $\T$ is a teleological category.
+  Suppose $\C$ is a symmetric strict monoidal category and $\T$ is a teleological category.
 For all symmetric monoidal functors $F : \C \to \T_d$, there exists a teleological functor $K : \Optic_\otimes \to \T$, unique up to teleological natural isomorphism with the property $Kj \cong F$.
@@
 &\xrightarrow{\phi_{S, T} \otimes \phi_{T', S'}^*} FS \otimes FT \otimes {(FS')}^* \otimes {(FT')}^* \\
-&\xrightarrow{FS \otimes s \otimes (FT')^*} FS \otimes {(FS')}^* \otimes FT \otimes {(FT')}^* \\
+&\xrightarrow{FS \otimes s \otimes {(FT')}^*} FS \otimes {(FS')}^* \otimes FT \otimes {(FT')}^* \\
 &= K(S, S') \otimes K(T, T')
@@
     &= K(\rep{\lambda_A^{-1} f}{g \lambda_{A'}}) \\
-    &= (FA \otimes \varepsilon_{FI} \otimes {(FA')}^*)(F(s_{I,A}\lambda_A^{-1} f) \otimes (F(g \lambda_{A'}s_{A', I}))^* ) \\
+    &= (FA \otimes \varepsilon_{FI} \otimes {(FA')}^*)(F(s_{I,A}\lambda_A^{-1} f) \otimes {(F(g \lambda_{A'}s_{A', I}))}^* ) \\
     &= (FA \otimes {(FA')}^*)(Ff \otimes {(Fg)}^* ) \\
@@
 &= K(\rep{\rho_{S \otimes S'}^{-1}}{\rho_{S \otimes S'}}) \\
-&= (FI \otimes \varepsilon_{F(S \otimes S')} \otimes (FI)^*)(F(s_{S \otimes S',I}\rho_{S \otimes S'}^{-1}) \otimes (F(\rho_{S \otimes S'} s_{I, S \otimes S'}))^* ) \\
-&= (\varepsilon_{F(S \otimes S')})(F(S \otimes S') \otimes F(S \otimes S')^* ) \\
+&= (FI \otimes \varepsilon_{F(S \otimes S')} \otimes {(FI)}^*)(F(s_{S \otimes S',I}\rho_{S \otimes S'}^{-1}) \otimes (F(\rho_{S \otimes S'} s_{I, S \otimes S'}))^* ) \\
+&= (\varepsilon_{F(S \otimes S')})(F(S \otimes S') \otimes F{(S \otimes S')}^* ) \\
 &= \varepsilon_{F(S \otimes S')}
@@
 \begin{remark}
-The above theorem and its proof have much in common with \cite[Proposition 5.2]{JoyalStreetVerity}, which gave a similar universal property for their $\mathrm{Int}$ construction on traced monoidal categories.
+The above theorem and its proof have much in common with~\cite[Proposition 5.2]{JoyalStreetVerity}, which gave a similar universal property for their $\mathrm{Int}$ construction on traced monoidal categories.
 \end{remark}
@@
 
-We have essentially rederived the result given in \cite[Section 3.2]{RelatingAlgebraicAndCoalgebraic} for ordinary lenses, but we note that cartesianness was not required.
+We have essentially rederived the result given in~\cite[Section 3.2]{RelatingAlgebraicAndCoalgebraic} for ordinary lenses, but we note that cartesianness was not required.
 
@@
 
-Of course, this notion of effectful lens may not be useful at all!
+Of course, this notion of effectful lens may not be useful!
 It is hard to get intuition for the meaning of the laws.
@@
 \begin{proposition}
-  There is a functor $\iota : \C_L \times \C_R^\op \to \Optic_{\actL, \actR}$, which on objects is given by $\iota(S, S') = (S, S')$ and on a morphism $(f, g) : (S, S') \to (A, A')$ by \[\iota(f, g) = \rep{(\lambda^{\C_L}_A)^{-1} f}{g \lambda^{\C_R}_{A'}},\] where $\lambda^{\C_L}_A : A \to IA$ in $\C_L$ and $\lambda^{\C_R}_{A'} : A' \to IA'$ in $\C_R$.
+  There is a functor $\iota : \C_L \times \C_R^\op \to \Optic_{\actL, \actR}$, which on objects is given by $\iota(S, S') = (S, S')$ and on a morphism $(f, g) : (S, S') \to (A, A')$ by \[\iota(f, g) = \rep{{(\lambda^{\C_L}_A)}^{-1} f}{g \lambda^{\C_R}_{A'}},\] where $\lambda^{\C_L}_A : A \to IA$ in $\C_L$ and $\lambda^{\C_R}_{A'} : A' \to IA'$ in $\C_R$.
 \qed
@@
 
-Suppose $\C$ is cartesian closed, and has an initial object. \todo{check which of these we need} We define two actions of $\C \times \C$, the first on $\C$ and the second on $\C \times \C$:
-\begin{align*}
-(M, R) \actL (A, I) &:= M \times R \times A \\
+Suppose $\C$ has finite products. We define two actions of $\C \times \C$, the first on $\C$ and the second on $\C \times \C$:
+\begin{align*}
+(M, R) \actL A &:= M \times R \times A \\
 (M, R) \actR (A, I) &:= (M \times A, R \times I)
 \end{align*}
-\todo{I could call this the ``indexed product action'' but the term indexed product is already taken of course}
-
-%\begin{definition}
-%The category of \emph{indexed lenses} $\IdxLens$ in $\C$ is the category of mixed optics with $\C \times \C^\op$ acting on the left, and the ordinary product action on the right.
-%\end{definition}
-
-%Then:
-%\begin{align*}
-%  &\int^{(M, R) \in \C \times \C^\op} (\C \times \C)((S, J), (M, R) \cdot (A, I)) \times \C(M \times A', S') \\
-%  &\cong \int^{M \in \C, R \in \C^\op} (\C \times \C)((S, J), (M \times A \times I, \homC(R, I))) \times \C(M \times A', S') \\
-%  &\cong \int^{M \in \C, R \in \C^\op} \C(S, M \times A \times I) \times \C(J, \homC(R, I)) \times \C(M \times A', S') \\
-%  &\cong \int^{R \in \C^\op} \C(S, A \times I) \times \C(J \times R, I) \times \C(S \times A', S') \\
-%  &\cong \C(S, A \times I) \times \C(J \times 0, I) \times \C(S \times A', S') \\
-%  &\cong \C(S, A \times I) \times \C(S \times A', S')
-%\end{align*}
-
-\begin{align*}
-  &\int^{(M, R) \in \C \times \C} \C(S, (M, R) \actL A) \times (\C \times \C)((M, R) \cdot (A', I'), (S', J')) \\
+
+\begin{definition}
+The category of \emph{indexed lenses} $\IdxLens$ in $\C$ is the category of mixed optics $\Optic_{\actL, \actR}$ with the action as above.
+\end{definition}
+
+We calculate:
+\begin{align*}
+  &\Optic_{\actL, \actR}((S, (S', J')), (A, (A', I'))) \\
+  &\cong \int^{(M, R) \in \C \times \C} \C(S, (M, R) \actL A) \times (\C \times \C)((M, R) \actR (A', I'), (S', J')) \\
   &\cong \int^{(M, R) \in \C \times \C} \C(S, M \times R \times A) \times \C(M \times A', S') \times \C(R \times I', J') \\
@@
 
-The idea for this action comes from \cite{IndexedOpticsPost}.
+The idea for this action comes from~\cite{IndexedOpticsPost}.
 
@@
 \begin{definition}
-  For an object $A \in \C$, the \emph{exchange profunctor} $E_A$ is defined to be $\C(-, A) \times \C(A, {=})$.
+  For a pair of objects $A, A' \in \C$, the \emph{exchange profunctor} $E_{A, A'}$ is defined to be $\C(-, A) \times \C(A', {=})$.
 \end{definition}
@@
 Given a profunctor, or indeed a Tambara module, we can evaluate it at any two objects of $\C$.
-This process is functorial in the choice of Tambara module, giving a functor $(U-)(A,A) : \Tamb(\M) \to \Set$.
+This process is functorial in the choice of Tambara module, giving a functor $(U-)(A,A') : \Tamb(\M) \to \Set$.
 
 \begin{lemma}\label{lemma-rep}
-  The functor $(U-)(A,A) : \Tamb(\M) \to \Set$ is representable: there is a natural isomorphism
-  $(U-)(A,A) \cong \Tamb(\M)(\Pastro_\M E_A, -)$
+  The functor $(U-)(A,A') : \Tamb(\M) \to \Set$ is representable: there is a natural isomorphism
+  $(U-)(A,A') \cong \Tamb(\M)(\Pastro_\M E_{A, A'}, -)$
 \end{lemma}
@@
   \begin{align*}
-    &(U-)(A,A) \\
-    \cong \;&\int_{X,Y \in \C} \Set(\C(X,A) \times \C(A,Y), (U-)(X,Y)) && \text{(by Yoneda reduction twice)} \\
-    =\;&\int_{X,Y \in \C} \Set(E_A(X,Y), (U-)(X,Y)) && \text{(by definition)}\\
-    \cong \;&\Prof(E_A, U-) && \text{(natural transformations as ends)} \\
-    \cong \;&\Tamb(\M)(\Pastro_\M E_A, -) && \text{(by adjointness)}
+    &(U-)(A,A') \\
+    \cong \;&\int_{X,Y \in \C} \Set(\C(X,A) \times \C(A',Y), (U-)(X,Y)) && \text{(by Yoneda reduction twice)} \\
+    =\;&\int_{X,Y \in \C} \Set(E_{A, A'}(X,Y), (U-)(X,Y)) && \text{(by definition)}\\
+    \cong \;&\Prof(E_{A, A'}, U-) && \text{(natural transformations as ends)} \\
+    \cong \;&\Tamb(\M)(\Pastro_\M E_{A, A'}, -) && \text{(by adjointness)}
   \end{align*}
@@
 \begin{proposition}[Profunctor Optics are Optics]\label{prop:profunctor-optics-are-optics}
-\todo{Use $(S, S') \hto (A, A')$ here}
-  \begin{align*}
-    [\Tamb(\M), \Set]((U-)(A,A),(U-)(S,S)) &\cong \Optic_\M(S, A)
+  \begin{align*}
+    [\Tamb(\M), \Set]((U-)(A,A'),(U-)(S,S')) &\cong \Optic_\M((S, S'), (A, A'))
   \end{align*}
@@
   \begin{align*}
-    &[\Tamb(\M), \Set]((U-)(A,A),(U-)(S,S)) \\
-    \cong \;&[\Tamb(\M), \Set](\Tamb(\M)(\Pastro_\M E_A, -), (U-)(S,S))  && \text{(by Lemma~\ref{lemma-rep})}\\
-    \cong \;&(U\Pastro_\M E_A)(S,S)  && \text{(by Yoneda)} \\
-    = \;&\int^{M \in \M} \int^{C,D \in \C} \C(S, MC) \times E_A(C,D) \times \C(MD,S) \\
-    = \;&\int^{M \in \M} \int^{C,D \in \C} \C(S, MC) \times \C(C,A) \times \C(A,D) \times \C(MD,S) \\
-    \cong \;&\int^{M \in \M} \C(S, MA) \times \C(MA, S)  && \text{(by Yoneda reduction twice)} \\
-    = \;&\Optic_\M(S, A)
-  \end{align*}
-  The same proof works in the more general case of $\Optic_\M((S, S'), (A,A'))$, defining $E_{A, A'}$ to be $\C(-, A) \times \C(A', {=})$.
+    &[\Tamb(\M), \Set]((U-)(A,A'),(U-)(S,S')) \\
+    \cong \;&[\Tamb(\M), \Set](\Tamb(\M)(\Pastro_\M E_{A, A'}, -), (U-)(S,S'))  && \text{(by Lemma~\ref{lemma-rep})}\\
+    \cong \;&(U\Pastro_\M E_{A, A'})(S,S')  && \text{(by Yoneda)} \\
+    = \;&\int^{M \in \M} \int^{C,D \in \C} \C(S, MC) \times E_{A, A'}(C,D) \times \C(MD,S') \\
+    = \;&\int^{M \in \M} \int^{C,D \in \C} \C(S, MC) \times \C(C,A) \times \C(A',D) \times \C(MD,S') \\
+    \cong \;&\int^{M \in \M} \C(S, MA) \times \C(MA', S')  && \text{(by Yoneda reduction twice)} \\
+    = \;&\Optic_\M((S, S'), (A, A'))
+  \end{align*}
 \end{proof}
@@
 
-For $p : S \hto A$, let $\tilde{p} : (U-)(A,A) \Rightarrow (U-)(S,S)$ denote the corresponding natural transformation under this isomorphism, and for $t : (U-)(A,A) \Rightarrow (U-)(S,S)$, let $\hat{t} : S \hto A$ be the corresponding optic.
+For $p : (S, S') \hto (A, A')$, let $\tilde{p} : (U-)(A,A') \Rightarrow (U-)(S,S')$ denote the corresponding natural transformation under this isomorphism, and for $t : (U-)(A,A') \Rightarrow (U-)(S,S')$, let $\hat{t} : (S, S') \hto (A, A')$ be the corresponding optic.
 
 \begin{corollary}
-  A profunctor optic $p$ is determined by its component at $\Pastro_\M E_A$, and furthermore, this component is determined by its value on $\repfour{\id_A}{\id_A}{\id_A}{\id_A} \in (U \Pastro_\M E_A)(A, A)$.
+  A profunctor optic $p$ is determined by its component at $\Pastro_\M E_{A, A'}$, and furthermore, this component is determined by its value on $\repfour{\id_A}{\id_A}{\id_{A'}}{\id_{A'}} \in (U \Pastro_\M E_{A, A'})(A, A')$.
 \end{corollary}
@@
   This is the content of the first two isomorphisms above.
-Explicitly, suppose $\hat{p} = \rep{l}{r}$ with $l : S \to MA$ and $r : MA \to S$.
+Explicitly, suppose $\hat{p} = \rep{l}{r}$ with $l : S \to MA$ and $r : MA' \to S'$.
 Then for any Tambara module $P$, the component of $p$ at $P$ is
   \begin{align*}
-    p_P = (UP)(l,r) \alpha_{A,A,M}
+    p_P = (UP)(l,r) \alpha_{A,A',M}
   \end{align*}
@@
   \[
-    p_{\Pastro_\M E_A}(\repfour{\id_A}{\id_A}{\id_A}{\id_A}) = \repfour{l}{\id_A}{\id_A}{r}
+    p_{\Pastro_\M E_{A, A'}}(\repfour{\id_A}{\id_A}{\id_{A'}}{\id_{A'}}) = \repfour{l}{\id_A}{\id_{A'}}{r}
   \]
@@
 \begin{proposition}
-  $\Optic_\M(S, A)$ is isomorphic to $\Prof(E_S, U \Phi_\M E_A)$.
-\end{proposition}
-\begin{proof}
-  \begin{align*}
-    &\Prof(E_S, U \Phi_\M E_A) \\
-    \cong\;&\int_{X,Y \in \C} \Set(E_S(X,Y), (U \Phi_\M E_A)(X,Y)) \\
-    = \;&\int_{X,Y \in \C} \Set(\C(X,A) \times \C(A,Y), (U \Phi_\M E_A)(X,Y)) \\
-    \cong \;& (U \Phi_\M E_A)(S,S) \\
-    = \;&\Optic_\M(S, A)
+  $\Optic_\M((S, S'), (A, A'))$ is isomorphic to $\Prof(E_{S, S'}, U \Phi_\M E_{A, A'})$.
+\end{proposition}
+\begin{proof}
+  \begin{align*}
+    &\Prof(E_{S, S'}, U \Phi_\M E_{A, A'}) \\
+    \cong\;&\int_{X,Y \in \C} \Set(E_{S, S'}(X,Y), (U \Phi_\M E_{A, A'})(X,Y)) \\
+    = \;&\int_{X,Y \in \C} \Set(\C(X,S) \times \C(S',Y), (U \Phi_\M E_{A, A'})(X,Y)) \\
+    \cong \;& (U \Phi_\M E_{A, A'})(S,S') \\
+    = \;&\Optic_\M((S, S'), (A, A'))
   \end{align*}
@@
 \subsection{Learners}
-A recent paper \cite{BackpropAsFunctor} in applied category theory describes a compositional approach to machine learning, with a category whose morphisms describe learning algorithms.
+A recent paper in applied category theory~\cite{BackpropAsFunctor} describes a compositional approach to machine learning, with a category whose morphisms describe learning algorithms.
 

### 2018-08-06 paper.tex
A note on states and costates

@@
 In this case we should be careful to only discuss $\Optic$ categories where we know that the coends exist by some other means, e.g., by exhibiting an isomorphism of $\Optic_\C((S, S'), (A, A'))$ with a set.
-For all of the examples we give later, we provide such a isomorphism.
+For all of the examples we give later we provide such a isomorphism.
 
@@
 \end{align*}
-Let $\conc_\times((S, S'), (A, A'))$ denote this set of concrete lenses.
+%Let $\conc_\times((S, S'), (A, A'))$ denote this set of concrete lenses. 
 Explicitly the isomorphism states that, given an optic $\rep{l}{r} : (S, S') \hto (A, A')$, the corresponding concrete lens is the pair $(\fget, \fput)$, where $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
@@
   \end{align*}
-  by Yoneda reduction.
+  by Yoneda reduction, so a state $\rep{l}{r} : (S, S') \hto (I, I)$ corresponds to the morphism $rl : S \to S'$, and a morphism $f : S \to S'$ corresponds to the state $\rep{\rho_S^{-1}}{f \rho_S} : (S, S') \hto (I, I)$
 \end{proof}
@@
 
-In particular, for any $S \in \C$, the identity $\id_S$ yields an optic $c_S = \rep{\rho_S^{-1}}{\rho_S} : (S, S) \hto (I, I)$, that we will call the \emph{connector}:
+In particular, for any $S \in \C$, the identity $\id_S$ yields an optic $c_S = \rep{\rho_S^{-1}}{\rho_S} : (S, S) \hto (I, I)$ that we call the \emph{connector}:
 %\begin{center}
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:states}
   Suppose the monoidal unit $I$ of $\C$ is terminal. Then the set of states $(I, I) \hto (A, A')$ is isomorphic to $\C(I, A)$.
@@
 But $\C$ has terminal object $I$, so \[\int^{M \in \C} \C(I, M \otimes A) \cong \C(I, I \otimes A) \cong \C(I, A).\]
+
+  Explicitly, a state $f : I \to A$ in $\C$ corresponds to the optic $\rep{\lambda_A^{-1} f}{!_{I \times A'}} : (I, I) \hto (A, A')$, where $!_{I \times A'} : I \times A' \to I$ is the unique map.
 \end{proof}
@@
 
-  A \emph{teleological natural transformation} $\alpha : F \Rightarrow G$ is a monoidal natural transformation whose components are all dualisable and that is additionally compatible with the dualisation:
-  \[
-  \begin{tikzcd}
-    {(FX)}^* \ar[r, "\cong"]  \ar[d, "(\alpha_X)^*", swap] & F(X^*) \ar[d, "\alpha_{X^*}"] \\
-    {(GX)}^* \ar[r, "\cong", swap] & G(X^*)
-  \end{tikzcd}
-  \]
+%  A \emph{teleological natural transformation} $\alpha : F \Rightarrow G$ is a monoidal natural transformation whose components are all dualisable and that is additionally compatible with the dualisation:
+%  \[
+%  \begin{tikzcd}
+%    {(FX)}^* \ar[r, "\cong"]  \ar[d, "(\alpha_X)^*", swap] & F(X^*) \ar[d, "\alpha_{X^*}"] \\
+%    {(GX)}^* \ar[r, "\cong", swap] & G(X^*)
+%  \end{tikzcd}
+%  \]
 \end{definition}
@@
 
+We can check when our basic examples of optics are lawful.
+
 \begin{proposition}
-  If $f : S \to A$ and $g : A \to S$ are mutual inverses, then $\iota(f, g) : S \hto A$ is a lawful optic, so $\iota$ restricts to a functor $\mathrm{Core}(\C) \to \Lawful_\M$.
+If $p = \rep{l}{r} : S \hto A$ is an optic such that $l$ and $r$ are mutual inverses, then $p$ is lawful.
 \end{proposition}
@@
 \begin{align*}
-\outside(\iota(f, g)) &= \outside(\rep{\lambda_A^{-1} f}{g \lambda_{A}}) = g \lambda_{A} \lambda_A^{-1} f = g f = \id_S \\
-\twice(\iota(f, g))
-&= \repthree{\lambda_A^{-1} f}{\lambda_A^{-1} f g \lambda_{A}}{g \lambda_{A}} \\
-&= \repthree{\lambda_A^{-1} f}{\lambda_A^{-1} \lambda_{A}}{g \lambda_{A}} \\
-&= \repthree{\lambda_A^{-1} f}{\id_{IA}}{g \lambda_{A}} \\
-&= \once(\iota(f, g))
-\end{align*}
+\outside(\rep{l}{r}) &= r l = \id_S \\
+\twice(\rep{l}{r})
+&= \repthree{l}{lr}{r} \\
+&= \repthree{l}{\id_{MA}}{r} \\
+&= \once(\rep{l}{r})
+\end{align*}
+\end{proof}
+
+\begin{corollary}\label{cor:iota-lawful}
+  If $f : S \to A$ and $g : A \to S$ are mutual inverses, then $\iota(f, g) : S \hto A$ is a lawful optic, so $\iota$ restricts to a functor $\iota : \mathrm{Core}(\C) \to \Lawful_\M$. \qed
+\end{corollary}
+
+\begin{proposition}
+A costate $p : (S, S) \hto (I, I)$ corresponding to a morphism $f : S \to S$ via Proposition~\ref{prop:costates} is lawful iff $f = \id_S$.
+\end{proposition}
+\begin{proof}
+The first law states that $\outside(p) = \id_S$, so if $p$ is lawful we have
+\[  \id_S = \outside(\rep{\rho_S^{-1}}{f \rho_S}) =  f \rho_S\rho_S^{-1} = f \]
+On the other hand, if $f  = \id_S$ then $\rep{\rho_S^{-1}}{\rho_S}$ is lawful because its components are mutual inverses.
 \end{proof}
@@
 \begin{proof}
-Due to the previous proposition, the structure maps of $\Optic_\M$ are all lawful.
+Due to Corollary~\ref{cor:iota-lawful}, the structure maps of $\Optic_\M$ are all lawful.
 We just have to check that $\otimes : \Optic_\M \times \Optic_\M \to \Optic_\M$ restricts to a functor on $\Lawful_\M$.

### 2018-08-13 paper.tex
Fix up teleological section

@@
 \documentclass[11pt,letterpaper]{article}
+\usepackage{microtype}
 \usepackage{authblk}
@@
 \usepackage{multicol}
+\usepackage{tocloft}
 
@@
 \newcommand{\T}{\mathscr{T}}
+\renewcommand{\S}{\mathscr{S}}
 
@@
 \newcommand{\SymmMonCat}{\mathbf{SymmMonCat}}
+\newcommand{\StrictSymmMonCat}{\mathbf{StrictSymmMonCat}}
+
 \newcommand{\Tele}{\mathbf{Tele}}
+\newcommand{\StrictTele}{\mathbf{StrictTele}}
 \newcommand{\Tamb}{\mathbf{Tamb}}
@@
 \DeclareMathOperator*{\colim}{\mathrm{colim}}
+\newcommand{\teletimes}{\mathbin{\boxtimes}}
 
@@
 
-% Credit: Sam Buss
-%\newbox\gnBoxA
-%\newdimen\gnCornerHgt
-%\setbox\gnBoxA=\hbox{$\ulcorner$}
-%\global\gnCornerHgt=\ht\gnBoxA
-%\newdimen\gnArgHgt
-%\def\nameof #1{%
-%    \setbox\gnBoxA=\hbox{$#1$}%
-%    \gnArgHgt=\ht\gnBoxA%
-%    \ifnum     \gnArgHgt<\gnCornerHgt \gnArgHgt=0pt%
-%    \else \advance \gnArgHgt by -\gnCornerHgt%
-%    \fi \raise\gnArgHgt\hbox{$\ulcorner$} \box\gnBoxA %
-%    \raise\gnArgHgt\hbox{$\urcorner$}}
-
 % Special arrows
@@
 
-% \newif\ifhideproofs
-% % \hideproofstrue %uncomment to hide proofs
-% \ifhideproofs
-% \usepackage{environ}
-% \NewEnviron{hide}{}
-% \let\proof\hide
-% \let\endproof\endhide
-% \fi
-
 \title{Categories of Optics}
@@
 \maketitle
+
+\setcounter{tocdepth}{1}
+\setlength\cftparskip{-8pt}
+\microtypesetup{protrusion=false}
+\tableofcontents
+\microtypesetup{protrusion=true}
 
@@
   For any three objects $M, A, A' \in \C$, there is the \emph{tautological} optic \[t_{M,A} : (M \otimes A, M \otimes A') \hto (A, A')\] given by $\rep{\id_{M \otimes A}}{\id_{M \otimes A'}}$.
-
-  We also have the \emph{identity} optic $\id_{(S, S')} : (S, S') \hto (S, S')$, given by $\rep{\lambda^{-1}_S}{\lambda_{S'}}$, where $\lambda_S : I \otimes S \to S$ is the left unitor for $S$ and similarly for $S'$.
 \end{example}
@@
 
+  We also have the \emph{identity} optic $\id_{(S, S')} : (S, S') \hto (S, S')$, given by $\rep{\lambda^{-1}_S}{\lambda_{S'}}$, where $\lambda_S : I \otimes S \to S$ is the left unitor for $S$ and similarly for $S'$.
+
 The identity optic is drawn as
@@
 
+\begin{theorem}
+  $\Optic_\otimes$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit object is $(I, I)$, and the action on a pair of morphisms $\rep{l}{r} : (S, S') \hto (A, A')$ and $\rep{l'}{r'} : (T, T') \hto (B, B')$ is given by:
+  \begin{center}
+    \input{diagrams/tensor-on-morphisms.tikz}
+  \end{center}
+\end{theorem}
+\begin{proof}
+  Suppose the two optics have residuals $M$ and $N$ respectively. Written equationally, their tensor is:
+  \begin{align*}
+    \rep{l}{r} \otimes \rep{l'}{r'} &:= \rep{(M \otimes s_{A,N} \otimes B)(l \otimes l')}{(r \otimes r')(M \otimes s_{A',N} \otimes B')}
+  \end{align*}
+  This is well-defined, as the calculus of string diagrams allows us to combine the coend relation on each optic to establish the coend relation for the compound diagram. \todo{draw this?}
+
+  To check functoriality of $\otimes$, suppose we have optics
+  \begin{align*}
+    \rep{l_1}{r_1} : (S_1, S_1') &\hto (S_2, S_2') \\
+    \rep{l_2}{r_2} : (S_2, S_2') &\hto (S_3, S_3') \\
+    \rep{p_1}{q_1} : (T_1, T_1') &\hto (T_2, T_2') \\
+    \rep{p_2}{q_2} : (T_2, T_2') &\hto (T_3, T_3').
+  \end{align*}
+  The string diagram for $(\rep{l_2}{r_2} \circ \rep{l_1}{r_1}) \otimes (\rep{p_2}{q_2} \circ \rep{p_1}{q_1})$ is:
+  \begin{center}
+    \input{diagrams/tensor-functorial-left.tikz}
+  \end{center}
+  And for $(\rep{l_2}{r_2} \otimes \rep{p_2}{q_2}) \circ (\rep{l_1}{r_1} \otimes \rep{p_1}{q_1})$ is:
+  \begin{center}
+    \input{diagrams/tensor-functorial-right.tikz}
+  \end{center}
+  These two diagrams are equivalent: We can use the naturality of the symmetry morphism to push $l_2$ and $r_2$ past the crossing to be next to $l_1$ and $r_1$ respectively.
+This creates two extra twists that can be cancelled in the center of the diagram (via the coend relation).
+
+  %%%% Note: The following is the above argument written equationally:
+  % For future convenience, note that
+  % \begin{align*}
+  %   \langle l, r \rangle \otimes (T, T') &= \langle (M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T') \rangle \\
+  %   &= \langle (\lambda^{-1}_M \otimes A \otimes T)(M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T')(\lambda_M \otimes A' \otimes T') \rangle \\
+  %   &= \langle l \otimes T, r \otimes T' \rangle
+  % \end{align*}
+  % Now we check functoriality. Suppose we have:
+  % \begin{align*}
+  %   \langle l_1, r_1 \rangle : (S_1, S_1') &\hto (S_2, S_2') \\
+  %   \langle l_2, r_2 \rangle : (S_2, S_2') &\hto (S_3, S_3') \\
+  %   \langle p_1, q_1 \rangle : (T_1, T_1') &\hto (T_2, T_2') \\
+  %   \langle p_2, q_2 \rangle : (T_2, T_2') &\hto (T_3, T_3')
+  % \end{align*}
+  % with residuals $M_1, M_2, N_1, N_2$ respectively. Then: \todo {(This is a mess. String diagram?)}
+  % \begin{align*}
+  %   &(\langle l_2, r_2 \rangle \otimes \langle p_2, q_2 \rangle) \circ (\langle l_1, r_1 \rangle \otimes \langle p_1, q_1 \rangle) \\
+  %   = \; &\langle (M_2 \otimes s_{S_3,N_2} \otimes T_3)(l_2 \otimes p_2), (r_2 \otimes q_2)(M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+  %   &\circ \langle (M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), (r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2') \rangle \\
+  %   = \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes N_1 \otimes l_2 \otimes p_2)(M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), \\
+  %   &\;(r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2')(M_1 \otimes N_1 \otimes r_2 \otimes q_2)(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+  %   = \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)(M_1 \otimes  l_2 \otimes N_1 \otimes p_2)(l_1 \otimes p_1), \\
+  %   &\;(r_1 \otimes q_1)(M_1 \otimes r_2 \otimes N_1 \otimes q_2)(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+  %   = \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1), \\
+  %   &\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
+  %   = \; & \text{\todo{(Add a $s_{M_2, N_1}$ to either side of the coend, then appeal to coherence)}} \\
+  %   = \; &\langle (M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S_3} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1) ,  \\
+  %   &\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S'_3} \otimes T'_3) \rangle \\
+  %   = \; &\langle (M_1 \otimes l_2)l_1, r_1(M_1 \otimes r_2) \rangle \otimes \langle (N_1 \otimes p_2)p_1, q_1(N_1 \otimes q_2) \rangle \\
+  %   = \; &(\langle l_2, r_2 \rangle  \circ \langle l_1, r_1 \rangle) \otimes (\langle p_2, q_2 \rangle \circ \langle p_1, q_1 \rangle)
+  % \end{align*}
+
+  The structure morphisms are all lifted from the structure morphisms in $\C \times \C^\op$:
+  \begin{align*}
+    \alpha_{(R, R'), (S, S'), (T, T')} &:= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1}) \\
+    \lambda_{(S, S')} &:= \iota(\lambda_{S}, \lambda_{S'}^{-1}) \\
+    \rho_{(S, S')} &:= \iota(\rho_{S}, \rho_{S'}^{-1}) \\
+    s_{(S, S'), (T, T')} &:= \iota(s_{S, T}, s_{T', S'})
+  \end{align*}
+
+  Note that because $\iota(S, S') = (S, S')$, required equations for $\iota$ to be a monoidal functor hold by definition (although we don't yet know that $\Optic_\otimes$ is monoidal).
+The pentagon and triangle equations then hold in $\Optic_\otimes$, as they are the image of the same diagrams in $\C \times \C^\op$ under $\iota$.
+The only remaining thing to verify is that these structure maps are natural in $\Optic_\otimes$, but this follows from the previous proposition.
+
+%  Let us check that $\alpha_{(R, R'), (S, S'), (T, T')}$ is natural in $(R, R')$. Suppose $\rep{l}{r} : (Q, Q') \hto (R, R')$ is an optic with residual $M$.
+%  \begin{align*}
+%    &\alpha_{(R, R'), (S, S'), (T, T')} \circ (f \otimes (S, S')) \otimes (T, T') \\
+%    &= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1})  \circ (\rep{l}{r} \otimes (S, S')) \otimes (T, T') \\
+%    &= \rep{\lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T}}{\alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'}}  \circ \rep{(l \otimes S) \otimes T}{(r \otimes S') \otimes T'} \\
+%    &= \rep{(M \otimes \lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T})((l \otimes S) \otimes T)}{((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} )} \\
+%    &=\rep{(M \otimes \alpha_{R,S,T})((l \otimes S) \otimes T)}{((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} )} \\
+%    &= \rep{(l \otimes (S \otimes T))\alpha_{Q,S,T}}{\alpha_{Q',S',T'}^{-1}(r \otimes (S' \otimes T'))} \\
+%    &= \rep{(I \otimes l \otimes (S \otimes T)) \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}}{(I \otimes r \otimes (S' \otimes T')) \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')}} \\
+%    &= \rep{l \otimes (S \otimes T)}{r \otimes (S' \otimes T')} \circ \rep{\lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}}{\alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')} } \\
+%    &= \rep{l}{r} \otimes ((S, S') \otimes (T, T')) \circ \iota(\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}) \\
+%    &= f \otimes ((S, S') \otimes (T, T')) \circ \alpha_{(Q, Q'), (S, S'), (T, T')}
+%  \end{align*}
+%
+%Naturality in the other variables is similar, as is the naturality of the unitors.
+%  \todo{convert this to a string diagram?}
+\end{proof}
+
+  In the Haskell \lenslib{} library, the monoidal product on optics is denoted ``\mintinline{haskell}{alongside}'' for the product and ``\mintinline{haskell}{without}'' for the coproduct.
+
 The remainder of this section comprises a proof of the following fact:
@@
 \begin{theorem}\label{thm:optic-functor}
-  The $\Optic_\C$ construction extends to a strict 2-functor \[\Optic : \SymmMonCat \to \SymmMonCat,\] where $\SymmMonCat$ denotes the 2-category of (small) symmetric monoidal categories, symmetric monoidal functors and monoidal natural transformations.
+  The $\Optic_\otimes$ construction extends to a functor \[\Optic : \SymmMonCat \to \SymmMonCat,\] where $\SymmMonCat$ denotes the (1-)category of (small) symmetric monoidal categories and symmetric monoidal functors.
 \end{theorem}
@@
   \begin{align*}
-    \Optic(F)\iota(f, g)
+    \Optic(F)(\iota(f, g))
     &= \Optic(F)(\rep{\lambda_A^{-1} f}{g \lambda_{A'}}) \\
@@
 
-\begin{theorem}
-  $\Optic_\otimes$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit object is $(I, I)$, and the action on a pair of morphisms $\rep{l}{r} : (S, S') \hto (A, A')$ and $\rep{l'}{r'} : (T, T') \hto (B, B')$ is given by:
-  \begin{center}
-    \input{diagrams/tensor-on-morphisms.tikz}
-  \end{center}
-\end{theorem}
-\begin{proof}
-  Suppose the two optics have residuals $M$ and $N$ respectively. Written equationally, their tensor is:
-  \begin{align*}
-    \rep{l}{r} \otimes \rep{l'}{r'} &:= \rep{(M \otimes s_{A,N} \otimes B)(l \otimes l')}{(r \otimes r')(M \otimes s_{A',N} \otimes B')}
-  \end{align*}
-  This is well-defined, as the calculus of string diagrams allows us to combine the coend relation on each optic to establish the coend relation for the compound diagram. \todo{draw this?}
-
-  To check functoriality of $\otimes$, suppose we have optics
-  \begin{align*}
-    \rep{l_1}{r_1} : (S_1, S_1') &\hto (S_2, S_2') \\
-    \rep{l_2}{r_2} : (S_2, S_2') &\hto (S_3, S_3') \\
-    \rep{p_1}{q_1} : (T_1, T_1') &\hto (T_2, T_2') \\
-    \rep{p_2}{q_2} : (T_2, T_2') &\hto (T_3, T_3').
-  \end{align*}
-  The string diagram for $(\rep{l_2}{r_2} \circ \rep{l_1}{r_1}) \otimes (\rep{p_2}{q_2} \circ \rep{p_1}{q_1})$ is:
-  \begin{center}
-    \input{diagrams/tensor-functorial-left.tikz}
-  \end{center}
-  And for $(\rep{l_2}{r_2} \otimes \rep{p_2}{q_2}) \circ (\rep{l_1}{r_1} \otimes \rep{p_1}{q_1})$ is:
-  \begin{center}
-    \input{diagrams/tensor-functorial-right.tikz}
-  \end{center}
-  These two diagrams are equivalent: We can use the naturality of the symmetry morphism to push $l_2$ and $r_2$ past the crossing to be next to $l_1$ and $r_1$ respectively.
-This creates two extra twists that can be cancelled in the center of the diagram (via the coend relation).
-
-  %%%% Note: The following is the above argument written equationally:
-  % For future convenience, note that
-  % \begin{align*}
-  %   \langle l, r \rangle \otimes (T, T') &= \langle (M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T') \rangle \\
-  %   &= \langle (\lambda^{-1}_M \otimes A \otimes T)(M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T')(\lambda_M \otimes A' \otimes T') \rangle \\
-  %   &= \langle l \otimes T, r \otimes T' \rangle
-  % \end{align*}
-  % Now we check functoriality. Suppose we have:
-  % \begin{align*}
-  %   \langle l_1, r_1 \rangle : (S_1, S_1') &\hto (S_2, S_2') \\
-  %   \langle l_2, r_2 \rangle : (S_2, S_2') &\hto (S_3, S_3') \\
-  %   \langle p_1, q_1 \rangle : (T_1, T_1') &\hto (T_2, T_2') \\
-  %   \langle p_2, q_2 \rangle : (T_2, T_2') &\hto (T_3, T_3')
-  % \end{align*}
-  % with residuals $M_1, M_2, N_1, N_2$ respectively. Then: \todo {(This is a mess. String diagram?)}
-  % \begin{align*}
-  %   &(\langle l_2, r_2 \rangle \otimes \langle p_2, q_2 \rangle) \circ (\langle l_1, r_1 \rangle \otimes \langle p_1, q_1 \rangle) \\
-  %   = \; &\langle (M_2 \otimes s_{S_3,N_2} \otimes T_3)(l_2 \otimes p_2), (r_2 \otimes q_2)(M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-  %   &\circ \langle (M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), (r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2') \rangle \\
-  %   = \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes N_1 \otimes l_2 \otimes p_2)(M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), \\
-  %   &\;(r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2')(M_1 \otimes N_1 \otimes r_2 \otimes q_2)(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-  %   = \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)(M_1 \otimes  l_2 \otimes N_1 \otimes p_2)(l_1 \otimes p_1), \\
-  %   &\;(r_1 \otimes q_1)(M_1 \otimes r_2 \otimes N_1 \otimes q_2)(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-  %   = \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1), \\
-  %   &\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-  %   = \; & \text{\todo{(Add a $s_{M_2, N_1}$ to either side of the coend, then appeal to coherence)}} \\
-  %   = \; &\langle (M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S_3} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1) ,  \\
-  %   &\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S'_3} \otimes T'_3) \rangle \\
-  %   = \; &\langle (M_1 \otimes l_2)l_1, r_1(M_1 \otimes r_2) \rangle \otimes \langle (N_1 \otimes p_2)p_1, q_1(N_1 \otimes q_2) \rangle \\
-  %   = \; &(\langle l_2, r_2 \rangle  \circ \langle l_1, r_1 \rangle) \otimes (\langle p_2, q_2 \rangle \circ \langle p_1, q_1 \rangle)
-  % \end{align*}
-
-  The structure morphisms are all lifted from the structure morphisms in $\C \times \C^\op$:
-  \begin{align*}
-    \alpha_{(R, R'), (S, S'), (T, T')} &:= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1}) \\
-    \lambda_{(S, S')} &:= \iota(\lambda_{S}, \lambda_{S'}^{-1}) \\
-    \rho_{(S, S')} &:= \iota(\rho_{S}, \rho_{S'}^{-1}) \\
-    s_{(S, S'), (T, T')} &:= \iota(s_{S, T}, s_{T', S'})
-  \end{align*}
-
-  Note that because $\iota(S, S') = (S, S')$, required equations for $\iota$ to be a monoidal functor hold by definition (although we don't yet know that $\Optic_\otimes$ is monoidal).
-The pentagon and triangle equations then hold in $\Optic_\otimes$, as they are the image of the same diagrams in $\C \times \C^\op$ under $\iota$.
-The only remaining thing to verify is that these structure maps are natural in $\Optic_\otimes$, but this follows from the previous proposition.
-
-%  Let us check that $\alpha_{(R, R'), (S, S'), (T, T')}$ is natural in $(R, R')$. Suppose $\rep{l}{r} : (Q, Q') \hto (R, R')$ is an optic with residual $M$.
-%  \begin{align*}
-%    &\alpha_{(R, R'), (S, S'), (T, T')} \circ (f \otimes (S, S')) \otimes (T, T') \\
-%    &= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1})  \circ (\rep{l}{r} \otimes (S, S')) \otimes (T, T') \\
-%    &= \rep{\lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T}}{\alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'}}  \circ \rep{(l \otimes S) \otimes T}{(r \otimes S') \otimes T'} \\
-%    &= \rep{(M \otimes \lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T})((l \otimes S) \otimes T)}{((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} )} \\
-%    &=\rep{(M \otimes \alpha_{R,S,T})((l \otimes S) \otimes T)}{((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} )} \\
-%    &= \rep{(l \otimes (S \otimes T))\alpha_{Q,S,T}}{\alpha_{Q',S',T'}^{-1}(r \otimes (S' \otimes T'))} \\
-%    &= \rep{(I \otimes l \otimes (S \otimes T)) \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}}{(I \otimes r \otimes (S' \otimes T')) \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')}} \\
-%    &= \rep{l \otimes (S \otimes T)}{r \otimes (S' \otimes T')} \circ \rep{\lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}}{\alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')} } \\
-%    &= \rep{l}{r} \otimes ((S, S') \otimes (T, T')) \circ \iota(\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}) \\
-%    &= f \otimes ((S, S') \otimes (T, T')) \circ \alpha_{(Q, Q'), (S, S'), (T, T')}
-%  \end{align*}
-%
-%Naturality in the other variables is similar, as is the naturality of the unitors.
-%  \todo{convert this to a string diagram?}
-\end{proof}
-
-  In the Haskell \lenslib{} library, the monoidal product on optics is denoted ``\mintinline{haskell}{alongside}'' for the product and ``\mintinline{haskell}{without}'' for the coproduct.
-
-\begin{proposition}
-  If $\C$ is a strict symmetric monoidal category then $\Optic_\otimes$ is strict, and $\iota : \C \times \C^\op \to \Optic_\otimes$ is a strict monoidal functor.
-\end{proposition}
-\begin{proof}
-  The structure maps of $\Optic_\otimes$ are given by $\iota$ applied to the structure maps of $\C$.
-If the latter are identities, then so are the former---the identity morphisms in $\Optic_\otimes$ are by definition $\iota(\id_S, \id_S')$.
-
-  That $\iota$ is strict is clear, as the structure morphisms in $\Optic_\otimes$ are exactly the structure morphisms in $\C \times \C^\op$ under $\iota$.
-\end{proof}
-
 \begin{proposition}
@@
 \begin{proof}[Proof of Theorem~\ref{thm:optic-functor}]
-The functor is well defined on its domain: if $\C$ is small then $\Optic_\C$ exists. There are only a few properties that remain to be checked:
-
-First, functoriality on 1-cells, i.e., that for monoidal functors $F : \C \to \D$ and $G : \D \to \E$ we have
+The functor is well defined on its domain: if $\C$ is small then $\Optic_\C$ exists.
+The only property left to check is functoriality, i.e.
+that for monoidal functors $F : \C \to \D$ and $G : \D \to \E$ we have
 \[ \Optic(G) \circ \Optic(F) = \Optic(G \circ F).\]
@@
 Checking that the identity is preserved is similar.
-
-Secondly, we note that $\Optic$ acts functorially on 2-cells. The action on 2-cells is given by Proposition~\ref{prop:iota-naturality}, and functoriality follows by the functoriality of $\iota$.
-
-Finally, we check that horizontal composition is preserved.
+%
+%Secondly, we note that $\Optic$ acts functorially on 2-cells. The action on 2-cells is given by Proposition~\ref{prop:iota-naturality}, and functoriality follows by the functoriality of $\iota$.
+%
+%Finally, we check that horizontal composition is preserved.
 Horizontal composition in $\SymmMonCat$ is defined in terms of whiskering and vertical composition, so it suffices to verify that whiskering is preserved.
 But indeed it is:
-\begin{align*}
-{\Optic(F\alpha)}_{(S, S')}
-&= \iota({(F\alpha)}_{S}, {(F\alpha)}^{-1}_{S'}) \\
-&= \iota(F(\alpha_{S}), F(\alpha_{S'}^{-1})) \\
-&= {(\Optic(F)\Optic(\alpha))}_{(S, S')}
-\end{align*}
-by Lemma~\ref{lem:iota-commute-with-opticf}, and
-\begin{align*}
-{\Optic(\alpha G)}_{(S, S')}
-&= \iota(\alpha_{GS}, \alpha_{GS'}^{-1}) \\
-&= \iota({(\alpha G)}_{S}, {(\alpha G)}_{S'}^{-1}) \\
-&= {(\Optic(\alpha)\Optic(G))}_{(S, S')}
-\end{align*}
+%\begin{align*}
+%{\Optic(F\alpha)}_{(S, S')}
+%&= \iota({(F\alpha)}_{S}, {(F\alpha)}^{-1}_{S'}) \\
+%&= \iota(F(\alpha_{S}), F(\alpha_{S'}^{-1})) \\
+%&= {(\Optic(F)\Optic(\alpha))}_{(S, S')}
+%\end{align*}
+%by Lemma~\ref{lem:iota-commute-with-opticf}, and
+%\begin{align*}
+%{\Optic(\alpha G)}_{(S, S')}
+%&= \iota(\alpha_{GS}, \alpha_{GS'}^{-1}) \\
+%&= \iota({(\alpha G)}_{S}, {(\alpha G)}_{S'}^{-1}) \\
+%&= {(\Optic(\alpha)\Optic(G))}_{(S, S')}
+%\end{align*}
 \end{proof}
@@
 %   \todo{This might not actually be true..}
-% \end{proof}
+%\end{proof}
+
+This doesn't extend to a strict 2-functor $\SymmMonCat \to \SymmMonCat$, as there is only an action of $\Optic$ on natural \emph{isomorphisms}.
+It is however functorial on natural isomorphisms, giving a 2-functor on the `homwise-core' of $\SymmMonCat$.
+We do not explore this any further in the present note.
+
+\begin{proposition}
+  If $\C$ is a strict symmetric monoidal category then $\Optic_\otimes$ is strict, and $\iota : \C \times \C^\op \to \Optic_\otimes$ is a strict monoidal functor.
+For $F$ a strict monoidal functor, the induced $\Optic(F)$ is also strict.
+\end{proposition}
+\begin{proof}
+  The structure maps of $\Optic_\otimes$ are given by $\iota$ applied to the structure maps of $\C$.
+If the latter are identities, then so are the former---the identity morphisms in $\Optic_\otimes$ are by definition $\iota(\id_S, \id_S')$.
+
+  That $\iota$ is strict is clear, as the structure morphisms in $\Optic_\otimes$ are exactly the structure morphisms in $\C \times \C^\op$ under $\iota$.
+
+  Finally, the structure morphisms of $\Optic(F)$ are lifted from $F$, so if the latter is strict then so is the former.
+\end{proof}
 
 \subsection{Teleological Categories}\label{sec:teleological-categories}
-\todo{I think there are strictness issues in this section, but the idea is correct}
-
 In this section we establish a universal property of the $\Optic$ construction.
@@
 
-We assume in this section that $\C$ is a \emph{strict} monoidal category. It will be convenient to equip $\Optic_\otimes$ with a slightly different symmetric monoidal structure.
+It will be convenient to equip $\Optic_\otimes$ with a slightly different symmetric monoidal structure.
 
@@
 \begin{proposition}
-  $(\Optic_\otimes, \switched, (I, I))$ is a symmetric monoidal category that is monoidally equivalent to $\Optic_\otimes$ with the unswitched tensor.
+  $(\Optic_\otimes, \switched, (I, I))$ is a symmetric monoidal category. 
+  %that is monoidally equivalent to $\Optic_\otimes$ with the unswitched tensor.
 \end{proposition}
@@
 
-  The categories are monoidally equivalent via the identity functor \[\id : (\Optic_\otimes, \switched, (I, I)) \to (\Optic_\otimes, \otimes, (I, I)),\] where the structure isomorphisms making this functor monoidal are given by
-  \begin{align*}
-    \iota(\id_{S \otimes S'}, s_{T, T'}) : \id(S, S') \otimes \id(T, T') \to \id((S, S') \switched (T, T'))
-  \end{align*}
+%  The categories are monoidally equivalent via the identity functor \[\id : (\Optic_\otimes, \switched, (I, I)) \to (\Optic_\otimes, \otimes, (I, I)),\] where the structure isomorphisms making this functor monoidal are given by
+%  \begin{align*}
+%    \iota(\id_{S \otimes S'}, s_{T, T'}) : \id(S, S') \otimes \id(T, T') \to \id((S, S') \switched (T, T'))
+%  \end{align*}
 \end{proof}
@@
 
-We now define the structure on a monoidal category universally provided by the $\Optic$ construction.
+We now define the structure on a symmetric monoidal category universally provided by the $\Optic$ construction.
 
 \begin{definition}[Compare {\cite[Definition 5.1]{CoherenceForLenses}}]
-  A \emph{teleological category is} a symmetric monoidal category $(\C, \otimes, I)$, equipped with:
+  A \emph{teleological category is} a symmetric monoidal category $(\T, \teletimes, I)$, equipped with:
   \begin{itemize}
-  \item A symmetric monoidal subcategory $\C_d$ of \emph{dualisable morphisms} containing all the objects of $\C$, with an involutive symmetric monoidal functor ${(-)}^* : \C_d \to \overline{\C_d^\op}$, where---not finding a standard symbol for such a thing---we mean $\overline{\C_d^\op}$ to be the category with both the direction of the arrows \emph{and} the order of the tensor flipped: ${(A \otimes B)}^* \cong B^* \otimes A^*$.
+  \item A symmetric monoidal subcategory $\T_d$ of \emph{dualisable morphisms} containing all the objects of $\T$, with an involutive symmetric monoidal functor ${(-)}^* : \T_d \to \T_d^\op$, where---not finding a standard symbol for such a thing---we mean $\T_d^\op$ to be the category with both the direction of the arrows \emph{and} the order of the tensor flipped: ${(A \otimes B)}^* \cong B^* \otimes A^*$.
 Note that there is therefore also a canonical isomorphism $\phi : I \cong I^*$
-  \item A symmetric monoidal extranatural family of morphisms $\varepsilon_X : X \otimes X^* \to I$, called \emph{counits}, natural with respect to the morphisms in $\C_d$.
+  \item A symmetric monoidal extranatural family of morphisms $\varepsilon_X : X \otimes X^* \to I$, called \emph{counits}, natural with respect to the morphisms in $\T_d$.
   \end{itemize}
 \end{definition}
-Unpacking the definition, $\varepsilon$ being a symmetric monoidal extranatural transformation amounts to the following diagrams in $\C$ commuting:
+Unpacking the definition, $\varepsilon$ being a symmetric monoidal extranatural transformation amounts to the following diagrams in $\T$ commuting:
 \[
   \begin{tikzcd}
-    X \otimes Y^* \ar[r, "f \otimes Y^*"]  \ar[d, "X \otimes f^*", swap] & Y \otimes Y^* \ar[d, "\varepsilon_Y"] \\
-    X \otimes X^* \ar[r, "\varepsilon_X", swap] & I
+    X \teletimes Y^* \ar[r, "f \teletimes Y^*"]  \ar[d, "X \teletimes f^*", swap] & Y \teletimes Y^* \ar[d, "\varepsilon_Y"] \\
+    X \teletimes X^* \ar[r, "\varepsilon_X", swap] & I
   \end{tikzcd} \hspace{1cm}
   \begin{tikzcd}
-    X^* \otimes X \ar[r, "\sigma"]  \ar[dr, "\varepsilon_{X^*}", swap] & X \otimes X^* \ar[d, "\varepsilon_X"] \\
+    X^* \teletimes X \ar[r, "s"]  \ar[dr, "\varepsilon_{X^*}", swap] & X \teletimes X^* \ar[d, "\varepsilon_X"] \\
     & I
@@
   \begin{tikzcd}[column sep = large]
-    X \otimes Y \otimes Y^* \otimes X^* \ar[r, "X \otimes \varepsilon_Y \otimes X^*"]  \ar[dr, "\varepsilon_{X \otimes Y}", swap] & X \otimes X^* \ar[d, "\varepsilon_X"] \\
+    X \teletimes Y \teletimes Y^* \teletimes X^* \ar[r, "X \teletimes \varepsilon_Y \teletimes X^*"]  \ar[dr, "\varepsilon_{X \teletimes Y}", swap] & X \teletimes X^* \ar[d, "\varepsilon_X"] \\
     & I
@@
   \begin{tikzcd}
-    I \otimes I^* \ar[r,"I \otimes \phi"] \ar[dr, swap, "\varepsilon_I"] & I \ar[d, equal] \\
+    I \teletimes I^* \ar[r,"I \teletimes \phi"] \ar[dr, swap, "\varepsilon_I"] & I \ar[d, equal] \\
     & I
@@
 \]
-where $f : X \to Y$ is in $\C_d$.
+where $f : X \to Y$ is in $\T_d$.
 
@@
 
-Note that because $\C_d$ is symmetric monoidal and has the same collection of objects as $\C$, the symmetric monoidal structure morphisms of $\C$ must be contained in $\C_d$ and so are dualisable.
+Note that because $\T_d$ is symmetric monoidal and has the same collection of objects as $\T$, the symmetric monoidal structure morphisms of $\T$ must be contained in $\T_d$ and so are dualisable.
 
@@
 \begin{definition}
-  A \emph{teleological functor} $F : \C \to \D$ is a symmetric monoidal functor that restricts to a functor $F_d : \C_d \to \D_d$ on the dualisable subcategories, commutes with the duality via a monoidal natural isomorphism $d_X : F(X^*) \to {(FX)}^*$, and such that the counits are preserved:
+  A \emph{teleological functor} $F : \T \to \S$ is a symmetric monoidal functor that restricts to a functor $F_d : \T_d \to \S_d$ on the dualisable subcategories, commutes with the duality via a monoidal natural isomorphism $d_X : F(X^*) \to {(FX)}^*$, and such that the counits are preserved:
   \[
    \begin{tikzcd}[column sep = large]
-    F(X \otimes X^*) \ar[r, "\phi_{X, X^*}"]  \ar[d, "F\varepsilon_X", swap] & FX \otimes F(X^*) \ar[r, "FX \otimes d_X"] & FX \otimes (FX)^* \ar[d, "\varepsilon_{FX}"] \\
+    F(X \teletimes X^*) \ar[r, "\phi_{X, X^*}"]  \ar[d, "F\varepsilon_X", swap] & FX \teletimes F(X^*) \ar[r, "FX \teletimes d_X"] & FX \teletimes (FX)^* \ar[d, "\varepsilon_{FX}"] \\
     FI \ar[rr, "\phi", swap] & & I
@@
   \]
-
-%  A \emph{teleological natural transformation} $\alpha : F \Rightarrow G$ is a monoidal natural transformation whose components are all dualisable and that is additionally compatible with the dualisation:
-%  \[
-%  \begin{tikzcd}
-%    {(FX)}^* \ar[r, "\cong"]  \ar[d, "(\alpha_X)^*", swap] & F(X^*) \ar[d, "\alpha_{X^*}"] \\
-%    {(GX)}^* \ar[r, "\cong", swap] & G(X^*)
-%  \end{tikzcd}
-%  \]
 \end{definition}
 
-Together we have $\Tele$, the sub-2-category of $\SymmMonCat$ given by teleological categories, teleological functors and teleological natural transformations.
-There are evident strict 2-functors $U : \Tele \to \SymmMonCat$ and ${(-)}_d : \Tele \to \SymmMonCat$, that take a teleological category to its underlying symmetric monoidal category and subcategory of dualisable morphisms respectively.
-
-The definition of teleological category suggests a string diagram calculus similar to that for compact closed categories, but where only counits exist and only morphisms known to be dualisable may be passed around a counit.
+Together we have $\Tele$, the subcategory of $\SymmMonCat$ given by teleological categories and teleological functors. There are evident functors 
+\begin{align*}
+U &: \Tele \to \SymmMonCat \\
+{(-)}_d &: \Tele \to \SymmMonCat 
+\end{align*}
+that take a teleological category to its underlying symmetric monoidal category and subcategory of dualisable morphisms respectively.
+
+The definition of teleological category suggests a string diagram calculus similar to that for compact closed categories, but where only counits are allowed and only morphisms known to be dualisable may be passed around a counit.
 We have of course not proven that such a calculus is sound for teleological categories, but we trust that a sceptical reader could verify our arguments equationally.
@@
 \begin{proof}
-  That morphisms of the form $\iota(f, g)$ constitute a category is clear. The functor ${(-)}^*$ is a symmetric monoidal involution, in fact it is strictly so:
+  Morphisms of the form $\iota(f, g)$ constitute a symmetric monoidal subcategory is clear, they are the image of the monoidal functor $\iota$.
+
+  The functor ${(-)}^*$ is a symmetric monoidal involution, in fact it is strictly so:
   \begin{align*}
@@
 \begin{proposition}
-  The 2-functor $\Optic : \SymmMonCat \to \SymmMonCat$ of Theorem~\ref{thm:optic-functor} has its image in the sub-2-category $\Tele$.
-\end{proposition}
-\begin{proof}
+  The functor $\Optic : \SymmMonCat \to \SymmMonCat$ of Theorem~\ref{thm:optic-functor} has its image in the subcategory $\Tele$.
+\end{proposition}
+\begin{proof}
+ We have seen that $\Optic_\C$ is always teleological.
 We must show that for a symmetric monoidal functor $F : \C \to \D$, the induced functor $\Optic(F) : \Optic_\C \to \Optic_\D$ is teleological.
@@
 
-For a natural transformation $\alpha : F \Rightarrow F'$, the induced natural transformation $\Optic(\alpha) : \Optic(F) \Rightarrow \Optic(F')$ has dualisable components by definition.
+%For a natural transformation $\alpha : F \Rightarrow F'$, the induced natural transformation $\Optic(\alpha) : \Optic(F) \Rightarrow \Optic(F')$ has components of the form $\iota(\alpha_{S}, \alpha^{-1}_{S'})$ that are dualisable by definition.
 Compatibility with the dualisation functor is immediate: for any object $(S, S')$, we have $({\Optic(\alpha)}_{(S, S')})^* = {\Optic(\alpha)}_{(S, S')^*}$ on the nose.
@@
 
-Our goal now is to establish the universal property of $\Optic_\otimes$. The following proposition gives that every optic decomposes in a canonical way:
+We will establish the universal property in the somewhat contrived case of \emph{strict} symmetric monoidal categories and \emph{strict} monoidal functors, but anticipate that this result could be weakened to non-strict symmetric monoidal categories at the cost of checking vastly more coherences.
+
+\begin{definition}
+A teleological category is \emph{strict} if it is strict as a symmetric monoidal category and ${(-)}^*$ is a strict monoidal involution, so ${(A \teletimes B)}^* = B^* \teletimes A^*$ and $I^* = I$, and also ${(A^*)}^* = A$.
+A teleological functor is \emph{strict} if it is strict as a symmetric monoidal functor and strictly preserves the duality and counits.
+\end{definition}
+
+We have previously noted that $\Optic_\otimes$ is strict monoidal if $\C$ is, and that in that case the duality is strict. There are functors
+\begin{align*}
+\Optic &: \StrictSymmMonCat \to \StrictTele \\
+U &: \StrictTele \to \StrictSymmMonCat \\
+{(-)}_d &: \StrictTele \to \StrictSymmMonCat 
+\end{align*}
+
+The crux is the following proposition that decomposes every optic in a canonical way.
 
@@
 
-\begin{theorem}\label{optic-is-free-teleological-cat}
-  Suppose $\C$ is a symmetric strict monoidal category and $\T$ is a teleological category.
-For all symmetric monoidal functors $F : \C \to \T_d$, there exists a teleological functor $K : \Optic_\otimes \to \T$, unique up to teleological natural isomorphism with the property $Kj \cong F$.
-  Furthermore, $\Optic : \SymmMonCat \to \Tele$ is left biadjoint to the underlying dualisable morphisms functor ${(-)}_d : \Tele \to \SymmMonCat$.
-\end{theorem}
-\begin{proof}
-  \todo{Notes: I think uniqueness is easy but I don't know how best to phrase it.
-I might instead be able to do something 1-categorical, so having the property $Kj = F$ strictly.
-This would possibly be easier but would involve using strict monoidal functors everywhere that strictly preserve duals, and having $I^* = I$.
-This is true for $\Optic$, but is that actually what we want in general?
-The teleological category definition is so contrived I can probably just make it whatever I need it to be, but that's a bit unsatisfying.}
-
-  We begin by constructing $K$.
-Note that any $(S, S')$ in $\Optic_\otimes$ can be written as $j(S) \switched {j(S')}^*$, so we define $K(S, S') = FS \otimes {(FS')}^*$.
+This also holds for monoidal categories that are not necessarily strict, if unit object and unitors are inserted in the appropriate places.
+
+\begin{proposition}
+  Suppose $(\C, \otimes, I)$ is a symmetric strict monoidal category and $(\T, \teletimes, I, {(-)}^*, \varepsilon)$ is a strict teleological category.
+Given a strict symmetric monoidal functor $F : \C \to \T_d$, there exists a unique strict teleological functor $K : \Optic_\otimes \to \T$ with the property $Kj = F$.
+\end{proposition}
+\begin{proof}
+  We construct $K$ as follows.
+Note that any object $(S, S')$ in $\Optic_\otimes$ can be written uniquely as $j(S) \switched {j(S')}^*$, so we are forced to define $K(S, S') = FS \teletimes {(FS')}^*$.
 Suppose $\rep{l}{r} : (S, S') \hto (A, A')$ is an optic.
@@
   \end{align*}
-  So in order for $Kj \cong F$ to hold, we define
-  \begin{align*}
-    K\rep{l}{r} = (FA \otimes \varepsilon_{FM} \otimes {(FA')}^*)(F(s_{M,A}l) \otimes {(F(rs_{A', M}))}^* )
-  \end{align*}
+  So if a $K$ with $Kj = F$ exists, it must hold that
+  \begin{align*}
+      K\rep{l}{r} 
+      &= K((A, I) \switched \varepsilon_{(M, I)} \switched (I, A')) K(j(s_{M,A}l) \switched {j(rs_{A', M})}^*) \\
+      &= (K(A, I) \teletimes K\varepsilon_{(M, I)} \teletimes K(I, A')) (K(j(s_{M,A}l)) \teletimes K( {j(rs_{A', M})}^*) \\
+      &= (FA \teletimes \varepsilon_{FM} \teletimes {(FA')}^*) (K(j(s_{M,A}l)) \teletimes K( {j(rs_{A', M})}^*) \\
+      &= (FA \teletimes \varepsilon_{FM} \teletimes {(FA')}^*) (F(s_{M,A}l) \teletimes F(rs_{A', M})^*)
+  \end{align*}
+  by functoriality, monoidality, and preservation of duals and counits.
+We therefore take \[  K\rep{l}{r} = (FA \teletimes \varepsilon_{FM} \teletimes {(FA')}^*) (F(s_{M,A}l) \teletimes F(rs_{A', M})^*)) \] as our definition of $K$.
 The diagram for $K\rep{l}{r}$ in $\T$ is as follows:
@@
   \end{center}
-
 %  \begin{align*}
@@
 %  \end{align*}
-
-There are now a lot of things to check.
+There are now several things to check.
 \begin{itemize}
@@
 using naturality of the symmetry and monoidality of the counit.
+\item Monoidality:
+\begin{align*}
+K((S, S') \switched (T, T'))
+&= K(S \otimes T, T' \otimes S) \\
+&= F(S \otimes T) \teletimes {F(T' \otimes S')}^* \\
+&= FS \teletimes FT \teletimes {(FS')}^* \teletimes {(FT')}^* \\
+&= FS \teletimes {(FS')}^* \teletimes FT \teletimes {(FT')}^* \\
+&= K(S, S') \teletimes K(T, T')
+\end{align*}
+and
+\begin{align*}
+K(I, I)
+&= FI \teletimes {(FI)}^* \\
+&= I \teletimes I^* \\
+&= I
+\end{align*}
+%That these obey the required coherences is straightforward. %More difficult is showing that the first isomorphism is natural in $(S, S')$ and $(T, T')$: \todo{todo}
 \item Preservation of duals:
@@
 = K(S', S)
-= FS' \otimes {(FS)}^*
-\cong {(FS \otimes {(FS')}^*)}^*
+= FS' \teletimes {(FS)}^*
+= {(FS \teletimes {(FS')}^*)}^*
 = {(K(S, S'))}^*
 \end{align*}
-\item Monoidality: We have the isomorphism \[ \phi_{(S, S'),(T, T')} : K((S, S') \switched (T, T')) \to K(S, S') \otimes K(T, T')\] given by the composite
-\begin{align*}
-K((S, S') \switched (T, T'))
-&= K(S \otimes T, T' \otimes S) \\
-&= F(S \otimes T) \otimes {F(T' \otimes S')}^* \\
-&\xrightarrow{\phi_{S, T} \otimes \phi_{T', S'}^*} FS \otimes FT \otimes {(FS')}^* \otimes {(FT')}^* \\
-&\xrightarrow{FS \otimes s \otimes {(FT')}^*} FS \otimes {(FS')}^* \otimes FT \otimes {(FT')}^* \\
-&= K(S, S') \otimes K(T, T')
-\end{align*}
-using the symmetry of $\T$, and
-\begin{align*}
-K(I, I)
-&= FI \otimes {(FI)}^* \\
-&\cong I \otimes I^* \\
-&\cong I
-\end{align*}
-That these obey the required coherences is straightforward. More difficult is showing that the first isomorphism is natural in $(S, S')$ and $(T, T')$: \todo{todo}
+
 \item Preservation of dualisable morphisms:  For a morphism $\iota(f, g)$:
@@
     &= K(\rep{\lambda_A^{-1} f}{g \lambda_{A'}}) \\
-    &= (FA \otimes \varepsilon_{FI} \otimes {(FA')}^*)(F(s_{I,A}\lambda_A^{-1} f) \otimes {(F(g \lambda_{A'}s_{A', I}))}^* ) \\
-    &= (FA \otimes {(FA')}^*)(Ff \otimes {(Fg)}^* ) \\
-    &= Ff \otimes {(Fg)}^*
+    &= (FA \teletimes \varepsilon_{FI} \teletimes {(FA')}^*)(F(s_{I,A}\lambda_A^{-1} f) \teletimes {(F(g \lambda_{A'}s_{A', I}))}^* ) \\
+    &= (FA \teletimes {(FA')}^*)(Ff \teletimes {(Fg)}^* ) \\
+    &= Ff \teletimes {(Fg)}^*
 \end{align*}
@@
 &= K(\rep{\rho_{S \otimes S'}^{-1}}{\rho_{S \otimes S'}}) \\
-&= (FI \otimes \varepsilon_{F(S \otimes S')} \otimes {(FI)}^*)(F(s_{S \otimes S',I}\rho_{S \otimes S'}^{-1}) \otimes (F(\rho_{S \otimes S'} s_{I, S \otimes S'}))^* ) \\
-&= (\varepsilon_{F(S \otimes S')})(F(S \otimes S') \otimes F{(S \otimes S')}^* ) \\
-&= \varepsilon_{F(S \otimes S')}
-\end{align*}
-by strictness of the monoidal unit.
-This morphism is indeed equal to the composite $\varepsilon_{K(S, S')} \phi_{(S, S'), {(S, S')}^*}$, using extranaturality to commute the structure maps $\phi_{S, S'}$ of $F$ and the symmetry of $\T$ through $\varepsilon$.
-\todo{write details?}
+&= (FI \teletimes \varepsilon_{F(S \otimes S')} \teletimes {(FI)}^*)(F(s_{S \otimes S',I}\rho_{S \otimes S'}^{-1}) \teletimes (F(\rho_{S \otimes S'} s_{I, S \otimes S'}))^* ) \\
+&= (\varepsilon_{F(S \otimes S')})(F(S \otimes S') \teletimes F{(S \otimes S')}^* ) \\
+&= \varepsilon_{F(S \otimes S')} \\
+&= \varepsilon_{FS \otimes FS'} \\
+&= \varepsilon_{FS}(FS \otimes \varepsilon_{FS'} \otimes {(FS)}^*) \\
+&= \varepsilon_{FS}(FS \otimes \varepsilon_{{FS'}^*} \otimes {(FS)}^*) \\
+&= \varepsilon_{FS \otimes {FS'}^*} \\
+&= \varepsilon_{K(S, S')}
+\end{align*}
+The critical move is applying the equality $\varepsilon_{FS'} = \varepsilon_{{FS'}^*}$, which follows because $\varepsilon$ is a symmetric monoidal transformation and the duality is strict.
 \end{itemize}
 
-To conclude biadjointness it remains to show that for any symmetric monoidal category $\C$ and teleological category $\T$, restriction along $j : \C \to \Optic_\C$ defines an equivalence of categories \[\Tele(\Optic_\C, \T) \simeq \SymmMonCat(\C, \T_d).
+%To conclude biadjointness it remains to show that for any symmetric monoidal category $\C$ and teleological category $\T$, restriction along $j : \C \to \Optic_\C$ defines an equivalence of categories \[\Tele(\Optic_\C, \T) \simeq \SymmMonCat(\C, \T_d).
 \]
-The restriction of a functor along $j$ indeed has its image in the subcategory $\T_d$, as by definition $j(f) = \iota(f, I)$ is dualisable.
-And given two teleological functors $K, L : \Optic_\C \to \T$, the whiskering of a teleological natural transformation $\alpha : K \Rightarrow L$ by $j$ is a well defined natural transformation $\beta : K j \Rightarrow L j$ in $\SymmMonCat(\C, \T_d)$ as the components of teleological natural transformations must be dualisable.
-
-We provide an inverse to this whiskering operation as follows.
+%The restriction of a functor $K$ along $j$ indeed has its image in the subcategory $\T_d$, as by definition $j(f) = \iota(f, \id_I)$ is dualisable and $K$ preserves dualisable morphisms.
+The construction of $K$ given earlier establishes that the restriction functor is essentially surjective, so
+%
+%Given two teleological functors $K, L : \Optic_\C \to \T$, the whiskering of a teleological natural transformation $\alpha : K \Rightarrow L$ by $j$ is a well defined natural transformation $\beta : K j \Rightarrow L j$ in $\SymmMonCat(\C, \T_d)$ as the components of teleological natural transformations are required to be dualisable.
+%
+%We provide an inverse to this whiskering operation as follows.
 If $\beta : K j \Rightarrow L j$ is a monoidal natural transformation, define $\alpha : K \Rightarrow L$ to be the natural transformation with components:
-\begin{align*}
-K(S, S') = K(j(S) \switched {j(S')}^*) \xrightarrow{\phi} Kj(S) \otimes K({j(S')}^*) \xrightarrow{\beta_S \otimes \beta_{S'}^*} Lj(S) \otimes L({j(S')}^*) \xrightarrow{\phi^{-1}} L(j(S) \switched {j(S')}^*) = L(S, S')
-\end{align*}
-\todo{Not quite right, we should be using $d_X$} We leave showing that this is an inverse to the reader.
+%\begin{align*}
+%K(S, S') = K(j(S) \switched {j(S')}^*) \xrightarrow{\phi} Kj(S) \teletimes K({j(S')}^*) \xrightarrow{\beta_S \teletimes \beta_{S'}^*} Lj(S) \teletimes L({j(S')}^*) \xrightarrow{\phi^{-1}} L(j(S) \switched {j(S')}^*) = L(S, S')
+%\end{align*}
+%\todo{Not quite right, we should be using $d_X$} We leave showing that this is an inverse to the reader.
+%
+%\todo{pseudonaturality of that equivalence of categories is missing}
+\end{proof}
+
+\begin{theorem}\label{thm:optic-is-free-teleological-cat}
+  $\Optic : \StrictSymmMonCat \to \StrictTele$ is left adjoint to the `underlying dualisable morphisms' functor ${(-)}_d : \StrictTele \to \StrictSymmMonCat$.
+\end{theorem}
+\begin{proof}
+Precomposition with $j$ gives a function
+\begin{align*}
+\StrictTele(\Optic_\C, \T) \to \StrictSymmMonCat(\C, \T_d)
+\end{align*}
+and the previous proposition states that this is a isomorphism.
+
+This is automatically natural in $\T$. Naturality in $\C$ follows by Lemma~\ref{lem:iota-commute-with-opticf}. 
 \end{proof}
@@
 \end{remark}
+
+Working with strict monoidal categories made it significantly easier to prove the universal property.
+There is likely to be a 2-categorical universal property of $\Optic$ for non-strict monoidal categories, so long as we restrict our attention to the sub-2-category $\SymmMonCat_\mathrm{homcore}$ of $\SymmMonCat$ that only contains natural isomorphisms.
+We leave this to future work:
+
+\begin{definition}
+  A \emph{teleological natural isomorphism} $\alpha : F \Rightarrow G$ is a monoidal natural isomorphism whose components are all dualisable and that is additionally compatible with the dualisation:
+  \[
+  \begin{tikzcd}
+    {(FX)}^* \ar[r, "\cong"]  \ar[d, "(\alpha_X)^*", swap] & F(X^*) \ar[d, "\alpha_{X^*}"] \\
+    {(GX)}^* \ar[r, "\cong", swap] & G(X^*)
+  \end{tikzcd}
+  \]
+  There is a (strict) 2-category $\Tele$ consisting of teleological categories, functors and natural isomorphisms.
+\end{definition}
+
+\begin{conjecture}
+\[ \Optic : \SymmMonCat_\mathrm{homcore} \to \Tele \] is left biadjoint to \[(-)_d : \Tele \to \SymmMonCat_\mathrm{homcore}\]
+\end{conjecture}
 
@@
 
-We will see that in all the other common examples of optics, this also gives the expected laws for that variant of optic.
+We can also check when some other of our basic optics are lawful.
+
+\begin{proposition}
+If $p = \rep{l}{r} : S \hto A$ is an optic such that $l$ and $r$ are mutual inverses, then $p$ is lawful.
+\end{proposition}
+\begin{proof}
+The conditions are easy to check:
+\begin{align*}
+\outside(\rep{l}{r}) &= r l = \id_S \\
+\twice(\rep{l}{r})
+&= \repthree{l}{lr}{r} \\
+&= \repthree{l}{\id_{MA}}{r} \\
+&= \once(\rep{l}{r})
+\end{align*}
+\end{proof}
+
+\begin{corollary}\label{cor:iota-lawful}
+  If $f : S \to A$ and $g : A \to S$ are mutual inverses, then $\iota(f, g) : S \hto A$ is a lawful optic, so $\iota$ restricts to a functor $\iota : \mathrm{Core}(\C) \to \Lawful_\M$. \qed
+\end{corollary}
+
+\begin{corollary}\label{cor:tautological-lawful}
+   For any two objects $A \in \C$ and $M \in \M$, the tautological optic $MA \hto A$ is lawful. \qed
+\end{corollary}
+
+\begin{proposition}
+A costate $p : (S, S) \hto (I, I)$ corresponding to a morphism $f : S \to S$ via Proposition~\ref{prop:costates} is lawful iff $f = \id_S$.
+\end{proposition}
+\begin{proof}
+The first law states that $\outside(p) = \id_S$, so if $p$ is lawful we have
+\[  \id_S = \outside(\rep{\rho_S^{-1}}{f \rho_S}) =  f \rho_S\rho_S^{-1} = f \]
+On the other hand, if $f  = \id_S$ then $\rep{\rho_S^{-1}}{\rho_S}$ is lawful because its components are mutual inverses.
+\end{proof}
 
@@
   This will follow from our description of lawful profunctor optics later, but we give a direct proof.
-
-  The identity optic $\iota(\id_S, \id_S)$ is lawful:
-  \begin{align*}
-    \outside(\rep{\lambda^{-1}_S}{\lambda_{S}}) &= \lambda_{S} \lambda^{-1}_S = \id_S \\
-    \intertext{and}
-    \once(\rep{\lambda^{-1}_S}{\lambda_{S}})
-                                                          &= \repthree{\lambda^{-1}_S}{\id_{IA}}{\lambda_{S}} \\
-                                                          &= \repthree{\lambda^{-1}_S}{\lambda_{S};\lambda^{-1}_S}{\lambda_{S}} \\
-                                                          &= \twice(\rep{\lambda^{-1}_S}{\lambda_{S}})
-  \end{align*}
+The identity optic is lawful as by definition it has a representative $\rep{\lambda_S^{-1}}{\lambda_S}$ consisting of mutual inverses.
+We just have to show that lawfulness is preserved under composition.
 
@@
 
-  For the second, we must show
+  For the second law, we must show that
   \[ \repthree{ l;(Ml')}{(Mr'); r;l;(Ml')}{(Mr') ; r} = \repthree{l;(Ml')}{\id_{MNA}}{(Mr') ; r}. \]
-
-  We do this by showing that the expressions above respect the coend relations defining $\Twoptic_\M(R, S)$ and $\Twoptic_\M(S, A)$. In the first step we use the former to show
-  \[ \repthree{ l;(Ml')}{(Mr'); r;l;(Ml')}{(Mr') ; r} = \repthree{l;(Ml')}{(Mr'l')}{(Mr') ; r} \]
-  and in the second step, the latter to show
-  \[ \repthree{ l;(Ml')}{(Mr'l')}{(Mr') ; r} = \repthree{l;(Ml')}{\id_{MNA}}{(Mr') ; r}. \]
-
-  So consider the generating relation $\repthree{l;\phi_S}{c}{r} = \repthree{l}{\phi_S ; c}{r}$ in $\Twoptic_\M(R, S)$.
-A consequence is that we can transfer $\phi_S$ past $\rep{l'}{r'}$ in the expression:
+  The idea is that, by the lawfulness of $\rep{l}{r}$ and $\rep{l'}{r'}$, there are chains of coend relations that prove
+  \begin{align*}
+  \repthree{l}{r;l}{r} &= \repthree{l}{\id_{MS}}{r} \\
+  \repthree{l'}{r';l'}{r'} &= \repthree{l'}{\id_{NA}}{r'}
+  \end{align*}
+  The result is achieved by splicing these chains of relations together appropriately.
+
+  So consider one of the generating relations $\repthree{l;\phi_S}{c}{r} = \repthree{l}{\phi_S ; c}{r}$ in $\Twoptic_\M(R, S)$. By the naturality of $\phi_A$, we calculate:
   \begin{align*}
@@
 
-  If $\repthree{l}{r;l}{r} = \repthree{l}{\id_{MA}}{r}$, then there exists a finite chain of coend relations connecting them. Because of the above, this chain can be replicated to show
-  \begin{align*}
-    \repthree{l;(Ml')}{(Mr');r;l;(Ml')}{(Mr') ; r} &= \repthree{l;(Ml')}{(Mr');\id_{MA};(Ml')}{(Mr') ; r},
-  \end{align*}
-  which is equal to $\repthree{l;(Ml')}{M(r'l')}{(Mr') ; r}$.
-
-  Similarly, a generating relation $\repthree{l';\psi_A}{c'}{r'} = \repthree{l'}{\psi_A ; c'}{r'}$ in $\Twoptic_\M(S, A)$ implies that
+  So indeed by replicating the same chain of relations that proves $\repthree{l}{r;l}{r} =\repthree{l}{\id_{MS}}{r}$, we see
+  \begin{align*}
+    \repthree{l;(Ml')}{(Mr');r;l;(Ml')}{(Mr') ; r} 
+    &= \repthree{l;(Ml')}{(Mr');\id_{MS};(Ml')}{(Mr') ; r} \\
+    &= \repthree{l;(Ml')}{M(r';l')}{(Mr') ; r}.
+  \end{align*}
+
+  Now that the $r;l$ in the center has been cleared away, we turn to the chain of relations proving $\repthree{l'}{r';l'}{r'} = \repthree{l'}{\id_{NA}}{r'}$.
+A generating relation $\repthree{l';\psi_A}{c'}{r'} = \repthree{l'}{\psi_A ; c'}{r'}$ in $\Twoptic_\M(S, A)$ implies that
   \begin{align*}
@@
   \end{align*}
-  So again we can replicate the chain of relations proving $\repthree{l'}{r';l'}{r'} = \repthree{l'}{\id_{MA}}{r'}$ to show that
-  \[\repthree{l;(Ml')}{M(r'l')}{(Mr') ; r} = \repthree{l;(Ml')}{\id_{MNA}}{(Mr') ; r} \]
-
-  We conclude that composition preserves lawfulness, so $\Lawful_\M$ is indeed a subcategory of $\Optic_\M$.
-\end{proof}
-
-We can check when our basic examples of optics are lawful.
-
-\begin{proposition}
-If $p = \rep{l}{r} : S \hto A$ is an optic such that $l$ and $r$ are mutual inverses, then $p$ is lawful.
-\end{proposition}
-\begin{proof}
-The conditions are easy to check:
-\begin{align*}
-\outside(\rep{l}{r}) &= r l = \id_S \\
-\twice(\rep{l}{r})
-&= \repthree{l}{lr}{r} \\
-&= \repthree{l}{\id_{MA}}{r} \\
-&= \once(\rep{l}{r})
-\end{align*}
-\end{proof}
-
-\begin{corollary}\label{cor:iota-lawful}
-  If $f : S \to A$ and $g : A \to S$ are mutual inverses, then $\iota(f, g) : S \hto A$ is a lawful optic, so $\iota$ restricts to a functor $\iota : \mathrm{Core}(\C) \to \Lawful_\M$. \qed
-\end{corollary}
-
-\begin{proposition}
-A costate $p : (S, S) \hto (I, I)$ corresponding to a morphism $f : S \to S$ via Proposition~\ref{prop:costates} is lawful iff $f = \id_S$.
-\end{proposition}
-\begin{proof}
-The first law states that $\outside(p) = \id_S$, so if $p$ is lawful we have
-\[  \id_S = \outside(\rep{\rho_S^{-1}}{f \rho_S}) =  f \rho_S\rho_S^{-1} = f \]
-On the other hand, if $f  = \id_S$ then $\rep{\rho_S^{-1}}{\rho_S}$ is lawful because its components are mutual inverses.
+  And similarly for the generating relation on the other side. So again we can replicate the chain of relations proving $\repthree{l'}{r';l'}{r'} = \repthree{l'}{\id_{MA}}{r'}$ to show that
+  \begin{align*}
+    \repthree{l;(Ml')}{M(r';l')}{(Mr') ; r} 
+    &= \repthree{l;(Ml')}{M(\id_{NA})}{(Mr') ; r} \\
+    &= \repthree{l;(Ml')}{\id_{MNA}}{(Mr') ; r}
+  \end{align*}
+as required. We conclude that composition preserves lawfulness, so $\Lawful_\M$ is indeed a subcategory of $\Optic_\M$.
 \end{proof}
@@
 \end{proposition}
-This would of course make no sense with the switched tensor, as the tensor of two objects would no longer be of the form $(X, X)$.
+This would of course make no sense with the switched tensor, as the tensor of two objects would typically no longer be of the form $(X, X)$.
 \begin{proof}
@@
 We just have to check that $\otimes : \Optic_\M \times \Optic_\M \to \Optic_\M$ restricts to a functor on $\Lawful_\M$.
-Given lawful optics $\rep{l}{r} : S \hto A$ and $\rep{l'}{r'} : T \hto B$ with residuals $N$ and $M$, the first law is easy to check.
-\begin{align*}
-\outside(\rep{l}{r} \otimes \rep{l'}{r'})
-&= \outside(\rep{(l \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B');(r \otimes r')}) \\
-&= (l \otimes l');(M \otimes s_{A,N} \otimes B);(M \otimes s_{A,N} \otimes B');(r \otimes r') \\
-&= (l \otimes l');(r \otimes r') \\
-&= \id_{S \otimes T}
-\end{align*}
-For the second, we follow the same strategy as Proposition~\ref{prop:lawful-category}, and show that the action of $\otimes$ on objects respects the coend relations in $\Twoptic_\M(S, A)$ and $\Twoptic_\M(T, B)$.
-
-Without loss of generality, we just check the case of $\repthree{l;\phi_S}{c}{r} = \repthree{l}{\phi_S ; c}{r}$. (The right entry is identical in all expressions, so we omit it.)
-\begin{align*}
-&\repthree{(l;\phi_S \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B');(c \otimes c');(M \otimes s_{A,N} \otimes B)}{\dots} \\
-&= \repthree{(l \otimes l');(\phi_S \otimes N \otimes B);(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B');(c \otimes c');(M \otimes s_{A,N} \otimes B)}{\dots} \\
-&= \repthree{(l \otimes l');(\phi_S \otimes N \otimes B)}{(c \otimes c');(M \otimes s_{A,N} \otimes B)}{\dots} \\
-&= \repthree{(l \otimes l')}{(\phi_S \otimes N \otimes B);(c \otimes c');(M \otimes s_{A,N} \otimes B)}{\dots} \\
-&= \repthree{(l \otimes l')}{(\phi_S;c \otimes c');(M \otimes s_{A,N} \otimes B)}{\dots} \\
-&= \repthree{(l \otimes l');(M' \otimes s_{A,N} \otimes B)}{(M' \otimes s_{A,N} \otimes B);(\phi_S;c \otimes c');(M \otimes s_{A,N} \otimes B)}{\dots}
-\end{align*}
-So again, we can transplant the chain of relations proving $\repthree{l}{r;l}{r} = \repthree{l}{\id_{MA}}{r}$ and $\repthree{l'}{r';l'}{r'} = \repthree{l'}{\id_{NB}}{r'}$ to prove:
-\begin{align*}
-&\twice(\rep{l}{r} \otimes \rep{l'}{r'}) \\
-&= \twice(\rep{(l \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B');(r \otimes r')}) \\
-&=\repthree{\dots}{(M \otimes s_{A,N} \otimes B);(r \otimes r');(l \otimes l');(M \otimes s_{A,N} \otimes B)}{\dots} \\
-&= \repthree{\dots}{(M \otimes s_{A,N} \otimes B);(rl \otimes r'l');(M \otimes s_{A,N} \otimes B)}{\dots} \\
-&= \repthree{\dots}{(M \otimes s_{A,N} \otimes B);(\id_{M \otimes A} \otimes \id_{N \otimes B});(M \otimes s_{A,N} \otimes B)}{\dots} \\
-&= \repthree{\dots}{(M \otimes s_{A,N} \otimes B);(M \otimes s_{A,N} \otimes B)}{\dots} \\
-&= \repthree{\dots}{\id_{M \otimes N \otimes A \otimes B}}{\dots} \\
-&= \once(\rep{l}{r} \otimes \rep{l'}{r'})
-\end{align*}
-
-\todo{This suggests there's something general here I should actually be proving}
+
+Given two lawful optics $p : S \hto A$ and $q : T \hto B$, the first law for $p \otimes q$ follows immediately from the first law for $p$ and $q$.
+To prove the second law, we follow the same strategy as used in the previous proposition: the two chains of relations proving $p$ and $q$  lawful can be combined to prove the law for $p \otimes q$.
+
+%Given two lawful optics $\rep{l}{r} : S \hto A$ and $\rep{l'}{r'} : T \hto B$ with residuals $N$ and $M$, the first law is easy to check.
+%\begin{align*}
+%\outside(\rep{l}{r} \otimes \rep{l'}{r'})
+%&= \outside(\rep{(l \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B');(r \otimes r')}) \\
+%&= (l \otimes l');(M \otimes s_{A,N} \otimes B);(M \otimes s_{A,N} \otimes B');(r \otimes r') \\
+%&= (l \otimes l');(r \otimes r') \\
+%&= \id_{S \otimes T}
+%\end{align*}
+%For the second, we follow the same strategy as Proposition~\ref{prop:lawful-category}, and show that the action of $\otimes$ on objects respects the coend relations in $\Twoptic_\M(S, A)$ and $\Twoptic_\M(T, B)$.
+%
+%Without loss of generality, we just check the case of $\repthree{l;\phi_S}{c}{r} = \repthree{l}{\phi_S ; c}{r}$. (The right entry is identical in all expressions, so we omit it.)
+%\begin{align*}
+%&\repthree{(l;\phi_S \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B');(c \otimes c');(M \otimes s_{A,N} \otimes B)}{\dots} \\
+%&= \repthree{(l \otimes l');(\phi_S \otimes N \otimes B);(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B');(c \otimes c');(M \otimes s_{A,N} \otimes B)}{\dots} \\
+%&= \repthree{(l \otimes l');(\phi_S \otimes N \otimes B)}{(c \otimes c');(M \otimes s_{A,N} \otimes B)}{\dots} \\
+%&= \repthree{(l \otimes l')}{(\phi_S \otimes N \otimes B);(c \otimes c');(M \otimes s_{A,N} \otimes B)}{\dots} \\
+%&= \repthree{(l \otimes l')}{(\phi_S;c \otimes c');(M \otimes s_{A,N} \otimes B)}{\dots} \\
+%&= \repthree{(l \otimes l');(M' \otimes s_{A,N} \otimes B)}{(M' \otimes s_{A,N} \otimes B);(\phi_S;c \otimes c');(M \otimes s_{A,N} \otimes B)}{\dots}
+%\end{align*}
+%So again, we can transplant the chain of relations proving $\repthree{l}{r;l}{r} = \repthree{l}{\id_{MA}}{r}$ and $\repthree{l'}{r';l'}{r'} = \repthree{l'}{\id_{NB}}{r'}$ to prove:
+%\begin{align*}
+%&\twice(\rep{l}{r} \otimes \rep{l'}{r'}) \\
+%&= \twice(\rep{(l \otimes l');(M \otimes s_{A,N} \otimes B)}{(M \otimes s_{A,N} \otimes B');(r \otimes r')}) \\
+%&=\repthree{\dots}{(M \otimes s_{A,N} \otimes B);(r \otimes r');(l \otimes l');(M \otimes s_{A,N} \otimes B)}{\dots} \\
+%&= \repthree{\dots}{(M \otimes s_{A,N} \otimes B);(rl \otimes r'l');(M \otimes s_{A,N} \otimes B)}{\dots} \\
+%&= \repthree{\dots}{(M \otimes s_{A,N} \otimes B);(\id_{M \otimes A} \otimes \id_{N \otimes B});(M \otimes s_{A,N} \otimes B)}{\dots} \\
+%&= \repthree{\dots}{(M \otimes s_{A,N} \otimes B);(M \otimes s_{A,N} \otimes B)}{\dots} \\
+%&= \repthree{\dots}{\id_{M \otimes N \otimes A \otimes B}}{\dots} \\
+%&= \once(\rep{l}{r} \otimes \rep{l'}{r'})
+%\end{align*}
+%
+%\todo{This suggests there's something general here I should actually be proving}
 \end{proof}
@@
   \outside(\Optic(F)(\rep{l}{r}))
-  &= \outside(\rep{(Fl);\phi^{-1}_{M,A}}{\phi_{M,A'};(Fr)}) \\
+  &= \outside\left(\rep{(Fl);\phi^{-1}_{M,A}}{\phi_{M,A'};(Fr)}\right) \\
   &= (Fl);\phi^{-1}_{M,A};\phi_{M,A'};(Fr)\\
@@
   \end{align*}
-  where $\phi_{M,A'} : (F^\bullet M)(FA) \to F(MA)$ is the structure map for $F$ commuting with the actions.
+  where $\phi_{M,A'} : (F^\bullet M)(FA) \to F(MA)$ is the structure map that commutes $F$ with the actions.
 
@@
   \end{align*}
-
-  \todo{There is probably a more conceptual way to do this}
 \end{proof}
@@
 \begin{proof}
-  The $\outside(\rep{l}{r}) = l;r = \id_S$ is exactly the first condition. And for the second, we verify:
+  The statement $\outside(\rep{l}{r}) = l;r = \id_S$ is exactly the first law. And for the second, we verify:
   \begin{align*}
@@
   Suppose $p : S \hto A$ satisfies $\outside(p) = \id_S$ and $\inside(p) = \langle \phi A \rangle$.
-Then there exists a representative $\rep{l}{r}$ such that $l ; r = \psi A$ on the nose for some (possibly different) $\psi : M \to M$.
+Then there exists a representative $\rep{l}{r}$ such that $r;l = \psi A$ on the nose for some (possibly different) $\psi : M \to M$.
 \end{proposition}
@@
   The generating relation for $\int^{M \in \M} \C(M A, M A)$ is
-  \[ \langle f \phi_A \rangle = \langle \phi_A f \rangle \]
-  whenever $f : N A \to M A$ and $\phi : M \to N$. This relation $f \phi_A \rightsquigarrow \phi_A f$ is not likely to be symmetric or transitive in general.
-
-  Note that if $f \phi_A \rightsquigarrow \phi_A f$ then $f \phi_A f \phi_A \rightsquigarrow \phi_A f \phi_A f$. More generally, if $f \rightsquigarrow g$ then $f^n \rightsquigarrow g^n$ for any $n$.
-
-  Now let $\rep{l}{r}$ be a representative for $p$, so $rl = \id_S$ and $\langle lr \rangle = \langle \psi A\rangle$.
-There therefore exists a finite chain of relations $lr = u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n = \psi A$.
+  \[ \langle f; \phi_A \rangle = \langle \phi_A; f \rangle \]
+  whenever $f : N A \to M A$ and $\phi : M \to N$.
+This relation $f; \phi_A \rightsquigarrow \phi_A; f$ is not likely to be symmetric or transitive in general.
+Note that if $f; \phi_A \rightsquigarrow \phi_A; f$ then $f ;\phi_A ;f; \phi_A \rightsquigarrow \phi_A ;f ;\phi_A; f$.
+More generally, if $f \rightsquigarrow g$ then $f^n \rightsquigarrow g^n$ for any $n$.
+
+  Now let $\rep{l}{r}$ be a representative for $p$, so $l;r = \id_S$ and $\langle r;l \rangle = \langle \psi A\rangle$.
+There therefore exists a finite chain of relations $r;l = u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n = \psi A$.
 Suppose the first relation faces rightward, so there exists a $k$ and $\phi$ with $r;l = \phi_A;k$ and $u_2 = k;\phi_A$.
@@
 It is shown in~\cite[Section 6]{ANoteOnActions} that, at least in the case $\M$ is right closed, to give such an action is equivalent to giving a ``copowered $\M$-category $\C$''.
+In most cases of interest to us, however, $\M$ is not right closed.
 \todo{Pointed out to me years ago when I emailed Ross Street, but I didn't understand what he was saying}
@@
 \begin{proof}
-By adjointness and Yoneda reduction we have an isomorphism $\Phi : \Twoptic_\M(S, A) \to \C(S, R_A (R_A S \act A) \act A)$ given by
+By adjointness and Yoneda reduction we have an isomorphism \[\Phi : \Twoptic_\M(S, A) \to \C(S, R_A (R_A S \act A) \act A)\] given by
 \begin{align*}
@@
 \end{align*}
-  which evaluated on an element $\repthree{l}{c}{r}$ is given by
+  which evaluated on an element $\repthree{l}{c}{r}$ is
   \begin{align*}
@@
 
-The category $\C$ includes into $\C_T$ in a way that preserves the action of $\C$, so there is an induced inclusion $\Optic_\otimes \to \Optic_\monact$.
-
-If we choose a specific monad, we can hope to simplify the description of concrete effectful lenses and their laws.
+The inclusion of $\C$ into $\C_T$ preserves the action of $\C$, so there is an induced inclusion $\Optic_\otimes \to \Optic_\monact$.
+
+If we choose a specific monad, we can hope to simplify the description of a concrete effectful optic and its laws.
 
@@
 
+\subsubsection{Writer Lenses}
+We begin with a simple example. Suppose $\C$ has finite products.
+\begin{definition}
+The \emph{writer monad} for a monoid $W$ is defined by
+\begin{align*}
+T_W X = X \times W
+\end{align*}
+The unit, multiplication of $T_W$ are given by pairing with the unit and multiplication of $W$, and the strength is simply the associativity morphism.
+\end{definition}
+
+We can find a more explicit description of concrete effectful lenses for this monad.
+\begin{align*}
+\Optic((S, S'), (A, A'))
+&= \int^{M \in \C} \C_{T_W}(S, M \monact A) \times \C_{T_W}(M \monact A', S') \\
+&= \int^{M \in \C} \C(S, M \times A \times W) \times \C_{T_W}(M \monact A', S') \\
+&\cong \int^{M \in \C} \C(S, M) \times \C(S, A\times W) \times \C_{T_W}(M \monact A', S') \\
+&\cong \C_{T_W}(S, A) \times \C_{T_W}(S \times A', S')
+\end{align*}
+Fortunately, concrete writer lenses correspond to $\fget$ and $\fput$ functions in the Kleisli category of $T_W$.
+
 \subsubsection{Stateful Lenses}
@@
 \begin{definition}
-The \emph{state monad} is defined by
+The \emph{state monad} with state $Q$ is defined by
 \begin{align*}
@@
 \end{align*}
-where $Q$ is the set of states.
 \todo{todo: define its unit, multiplication and strength}
@@
 Of course, this notion of effectful lens may not be useful!
-It is hard to get intuition for the meaning of the laws.
+It is hard to get intuition for the meaning of the laws, but they seem to suffer from the same deficiencies that other attempts do: they are too strong.
 The $\fget\fput$ law here appears easier to satisfy than the $\mathsf{MGetPut_0}$ law of~\cite{ReflectionsOnMonadicLenses}, as $\mput$ is given access to the original state.
-On the other hand, our $\fput\fget$ law seems very difficult to satisfy: no matter what auxiliary state is provided, putting then getting must leave the state unchanged.
+However, our $\fput\fget$ law seems very difficult to satisfy: no matter what auxiliary state is provided, $\fput$ting then $\fget$ting must leave the state unchanged.
 
@@
 
-\todo{This bit is very much in progress, skip to Section~\ref{sec:profunctor-optics}}
-
 We can generalise the definition of $\Optic$ so that the two halves lie in different categories, allowing us to capture a few more optic variants found in the wild.
-Suppose $\C_L$ and $\C_L$ are categories that are each acted on by a common monoidal category $\M$.
-Write these actions as $\actL$ and $\actR$ respectively.
+Suppose $\C_L$ and $\C_R$ are categories that are acted on by a common monoidal category $\M$.
+Write these actions as $\actL : \M \to [\C_L, \C_L]$ and $\actR : \M \to [\C_R, \C_R]$ respectively.
 
@@
 
-Several results from Section~\ref{sec:optics} continue to hold:
+Several results from Section~\ref{sec:optics} have analogues in this setting.
 \begin{proposition}\label{prop:mixed-optic-is-cat}
@@
 
-Finally, we can also encode the category of \mintinline{haskell}{Fold}s which in $\Set$ correspond to functions $S \to \mathrm{List}\,A$.
-Define $\Fold := \Optic_{\Traversable, \C, \C_\codisc}$.
-The key is that the $\mathrm{List}$ functor is the terminal $\Traversable$ functor, so we have isomorphisms
+Finally, we can also encode the category of \mintinline{haskell}{Fold}s. In $\Set$, a fold $S \hto A$ corresponds to a function $S \to \mathrm{List}\,A$. Define 
+\begin{align*}
+\Fold := \Optic_{\Traversable, \C, \C_\codisc}
+\end{align*}
+The key is that the $\mathrm{List}$ functor is the terminal $\Traversable$ functor. We therefore have isomorphisms
 \begin{align*}
@@
 
-Suppose $\C$ has finite products. We define two actions of $\C \times \C$, the first on $\C$ and the second on $\C \times \C$:
-\begin{align*}
-(M, R) \actL A &:= M \times R \times A \\
-(M, R) \actR (A, I) &:= (M \times A, R \times I)
+Suppose $\C$ is cartesian closed. We define two actions of $\C \times \C$, the first on $\C$ and the second on $\C \times \C^\op$:
+\begin{align*}
+M \actL A  &:= M \times A\\
+M \actR (A, I) &:= (M \times A, \homC(M, I))
 \end{align*}
@@
 \begin{definition}
-The category of \emph{indexed lenses} $\IdxLens$ in $\C$ is the category of mixed optics $\Optic_{\actL, \actR}$ with the action as above.
+The category of \emph{indexed lenses} $\IdxLens$ in $\C$ is the category of mixed optics $\Optic_{\actL, \actR}$ with the actions as given above.
 \end{definition}
-
-We calculate:
+Describing concrete indexed lenses is straightforward:
 \begin{align*}
   &\Optic_{\actL, \actR}((S, (S', J')), (A, (A', I'))) \\
-  &\cong \int^{(M, R) \in \C \times \C} \C(S, (M, R) \actL A) \times (\C \times \C)((M, R) \actR (A', I'), (S', J')) \\
-  &\cong \int^{(M, R) \in \C \times \C} \C(S, M \times R \times A) \times \C(M \times A', S') \times \C(R \times I', J') \\
-  &\cong  \C(S, A) \times \C(S \times A', S') \times \C(S \times I', J')
+  &= \int^{M \in \C} \C(S, M \actL A) \times (\C \times \C^\op)(M \actR (A', I'), (S', J')) \\
+  &\cong \int^{M \in \C} \C(S, M \times A) \times (\C \times \C^\op)((M \times A', \homC(M, I')), (S', J')) \\
+  &\cong \int^{M \in \C} \C(S, M \times A) \times \C(M \times A', S') \times \C^\op(\homC(M, I'), J') \\
+  &\cong \int^{M \in \C} \C(S, M \times A) \times \C(M \times A', S') \times \C(J', \homC(M, I')) \\
+  &\cong \C(S, A) \times \C(S \times A', S') \times (S \times J', I')
 \end{align*}
@@
 
-\todo{do the rest of this}
+\begin{remark}
+There appears to be some flexibility in what actions are used here. To have the indices behave covariantly rather than contravariantly, we could have $\C$ act on $\C$ and $\C \times \C$ as follows:
+\begin{align*}
+M \actL A &:= M \times A \\
+M \actR (A, I) &:= (M \times A, M \times I)
+\end{align*}
+which gives concrete optics in the form
+\begin{align*}
+\C(S, A) \times \C(S \times A', S') \times \C(S \times I', J').
+\end{align*}
+We chose the previous, more contorted actions so that indexed lenses are more clearly related to indexed traversals, which we define presently.
+%We calculate:
+%\begin{align*}
+%  &\Optic_{\actL, \actR}((S, (S', J')), (A, (A', I'))) \\
+%  &\cong \int^{(M, R) \in \C \times \C} \C(S, (M, R) \actL A) \times (\C \times \C)((M, R) \actR (A', I'), (S', J')) \\
+%  &\cong \int^{(M, R) \in \C \times \C} \C(S, M \times R \times A) \times \C(M \times A', S') \times \C(R \times I', J') \\
+%  &\cong  \C(S, A) \times \C(S \times A', S') \times \C(S \times I', J')
+%\end{align*}
+\end{remark}
 
@@
 \begin{proposition}
-The assignment $F \act X \mapsto \Set(R, FX)$ is a lax action of $\App$ on $\Set$, called the \emph{$R$-indexed action of $\App$ on $\Set$}.
+The assignment $F \act X \mapsto \Set(R, FX)$ extends to a lax action of $\App$ on $\Set$, called the \emph{$R$-indexed action of $\App$ on $\Set$}.
 \end{proposition}

### 2018-08-15 paper.tex
Suggestions by Alex

@@
 \usepackage{tocloft}
+\usepackage{enumerate}
 
@@
 \newcommand{\teletimes}{\mathbin{\boxtimes}}
+\newcommand{\defeq}{\mathrel{\vcentcolon=}}
 
@@
 S \ar[rr, "{[\id_S, \fget]}"] \ar[dr, "\id_S", swap] && S \times A \ar[dl, "\fput"] \\
-& A
+& S
 \end{tikzcd}
@@
 \end{center}
+We call such lenses lawful.
 The $\fput\fget$ law states that any update to $A$ is represented faithfully in $S$.
@@
 \end{align*}
-If the two input lenses are lawful, the composite is as well.
-
-Lenses were discovered to be just one of a hierarchy of data accessors, including prisms, setters, traversals and more, collectively called \emph{optics}.
+If the two input lenses are lawful then the composite is as well, so we find there is a subcategory of lawful lenses.
+
+Lenses were discovered to be just one of a hierarchy of data accessors, including prisms, setters, traversals and more.
+These are collectively called \emph{optics} and have been best explored in the widely uesd Haskell \lenslib{} library: see~\cite{LensLibrary}.
 Each optic variant has a concrete description as a certain collection of maps, with attendant laws under which we consider them well-behaved.
@@
 Section~\ref{sec:lawful-optics} defines the equivalent of the lens laws for a general category of optics.
-Then in Section~\ref{sec:examples} we see that these generic definitions specialise correctly to the other basic varieties of optic, including giving the correct laws.
+Then in Section~\ref{sec:examples} we see that these generic definitions specialise correctly to the other basic varieties of optic, including the laws.
 We include in Section~\ref{sec:mixed-optics} a more speculative discussion of ``mixed optics'', which include indexed and coindexed lenses and traversals.
 
-The widely used Haskell \lenslib{} library contains implementations of all these optic variants: see~\cite{LensLibrary}.
-There, optics are written in a form known as the \emph{profunctor encoding}, which at first glance is completely different to that given in Section~\ref{sec:optics}.
-As this note was being written, Bartosz Milewski~\cite{ProfunctorOpticsPost} independently described the relationship between some forms of optic and their profunctor encoding.
+In the Haskell \lenslib{} library, optics are written in a form known as the \emph{profunctor encoding}, which at first glance is completely different to that given in Section~\ref{sec:optics}.
+As this was being written, Bartosz Milewski~\cite{ProfunctorOpticsPost} independently described the isomorphism between some forms of optic and their profunctor encoding.
 In Section~\ref{sec:profunctor-optics} we extend this to more of the optic hierarchy and translate the laws into the profunctor setting.
@@
 The aim of the present paper is to fill this gap, with the hope that a better understanding of the general structure of these categories will make it easier to generalise to new and exotic settings.
-This is particularly important with the advent of linear types in Haskell, which enables a new branch of the lens family tree, and with the new applications to game theory.
-
-\todo{Contributions:
+This is particularly important with the advent of linear types in Haskell, which enables a new branch of the lens family tree, and also with the new applications to game theory.
+
+\subsection{Contributions}
+\todo{
   \begin{itemize}
@@
 
-In this paper we will make frequent use of the (co)end calculus. For a comprehensive introduction to ends and coends, see~\cite{CoendCofriend}. The most important results for us are:
+In this paper we will make frequent use of the (co)end calculus.
+For a comprehensive introduction to ends and coends, see~\cite{CoendCofriend}.
+We write $\copr_X : F(X, X) \to \int^{X \in \M} F(X, X)$ for the structure maps of a coend.
+The most important results for us regarding ends and coends are:
 
@@
 
-\begin{lemma}[Ninja Yoneda Lemma/Yoneda Reduction]
+\begin{lemma}[Ninja Yoneda Lemma/Yoneda Reduction]\label{lem:yoneda-reduction}
 For every functor $K : \C^\op \to \Set$ and $H : \C \to \Set$, we have the following natural isomorphisms:
 \begin{align*}
-K &\cong \int^C KC \times \C(-,C) &
-K &\cong \int_C \Set(\C(C,-), KC) \\
-H &\cong \int^C HC \times \C(C,-)  &
-H &\cong \int_C \Set(\C(-,C), HC)
-\end{align*}
-where the components of the isomorphisms at $X$ are given by inclusion with the identity morphism $\C(X, X)$ on the left, and evaluation at the identity morphism on the right.
+KX &\cong \int^{C \in \C} KC \times \C(X,C) &
+KX &\cong \int_{C \in \C} \Set(\C(C,X), KC) \\
+HX &\cong \int^{C \in \C} HC \times \C(C,X)  &
+HX &\cong \int_{C \in \C} \Set(\C(X,C), HC)
+\end{align*}
+where the isomorphisms are given by inclusion with the identity morphism $\C(X, X)$ for the left two, and evaluation at the identity morphism on the right.
 \qed
@@
 \begin{align*}
-\int^C \int^D F(C,C,D,D) \cong \int^{(C,D)} F(C,C,D,D) \cong \int^D \int^C F(C,C,D,D)
+\int^{C \in \C} \int^{D \in \D} F(C,C,D,D) \cong \int^{(C,D) \in \C \times \D} F(C,C,D,D) \cong \int^{D \in \D} \int^{C \in \C} F(C,C,D,D)
 \end{align*}
@@
 \begin{lemma}[Mute coends]
-Consider a functor $F : \C \to \E$ as a functor $\C^\op \times \C \to \E$ that ignores its contravariant argument. Then \[ \int^C F(C) \cong  \colim F. \] \qed
+Consider a functor $F : \C \to \E$ as a functor $\C^\op \times \C \to \E$ that ignores its contravariant argument. Then \[ \int^{C \in \C} F(C) \cong \colim F. \] \qed
 \end{lemma}
@@
 
-We begin by defining the category of optics for a symmetric monoidal category $\C$.
+We begin by defining the category of optics for a symmetric monoidal category.
 This category was first defined in~\cite[Section 6]{Doubles} as the `double' of a monoidal category.
@@
   \begin{align*}
-    \Optic_\otimes((S, S'), (A, A')) := \int^{M \in \C} \C(S, M \otimes A) \times \C(M \otimes A', S')
+    \Optic_\C((S, S'), (A, A')) := \int^{M \in \C} \C(S, M \otimes A) \times \C(M \otimes A', S')
   \end{align*}
@@
 
-Because this coend takes place in $\Set$, we can use Lemma~\ref{lemma:calculate-coend} to describe $\Optic_\otimes((S, S'), (A, A'))$ explicitly.
+Because this coend takes place in $\Set$, we can use Lemma~\ref{lemma:calculate-coend} to describe $\Optic_\C((S, S'), (A, A'))$ explicitly.
 It is the set of pairs $(l, r)$, where $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, quotiented by the equivalence relation generated by relations of the form
@@
 
-For a pair of maps $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\rep{l}{r} : (S, S') \hto (A, A')$ for their image in $\Optic_\otimes((S, S'), (A, A'))$, and say that the object $M$ is the residual for this representative.
+For a pair of maps $l : S \to M \otimes A$ and $r : M \otimes A' \to S'$, we write $\rep{l}{r} : (S, S') \hto (A, A')$ for their image in $\Optic_\C((S, S'), (A, A'))$, and say that the object $M$ is the \emph{residual} for this representative.
 Optics will always be written with a crossed arrow $\hto$ to distinguish them from morphisms of $\C$.
 
-\begin{example}
-  For any three objects $M, A, A' \in \C$, there is the \emph{tautological} optic \[t_{M,A} : (M \otimes A, M \otimes A') \hto (A, A')\] given by $\rep{\id_{M \otimes A}}{\id_{M \otimes A'}}$.
-\end{example}
-
-  Elements of $\Optic_\otimes((S, S'), (A, A'))$ have an appealing
+  The residual $M$ should be thought of as a kind of `scratch space'; information from $S$ that we need to remember to construct $S'$.
+The quotienting imposed by the coend means we cannot inspect this temporary information, indeed, there is not even a canonical choice for the object $M$ in general, given an optic $S \hto A$.
+
+  Elements of $\Optic_\C((S, S'), (A, A'))$ have an appealing
   interpretation as string diagrams with a ``hole'' missing. We draw the
@@
   \end{center}
-  reading left to right, so the left half of the diagram represents $l$ and the right half $r$. The relation imposed by the coend can be graphically expressed as:
+  reading left to right, so the left half of the diagram represents $l$ and the right half $r$. The relation expressed by the coend can be graphically expressed as:
   \begin{center}
     \input{diagrams/coend-relation-left.tikz}
-    \qquad
+    \hspace{0.7cm} \raisebox{1.35cm}{$\sim$} \hspace{1cm}
     \input{diagrams/coend-relation-right.tikz}
@@
     \input{diagrams/generic-optic.tikz}
-    \qquad \raisebox{1.5cm}{$=$} \qquad
+    \hspace{0.8cm} \raisebox{1.5cm}{$=$} \hspace{1cm}
     \input{diagrams/generic-optic-with-iso.tikz}
@@
 
-Optics compose as follows. The easiest interpretation is graphical: composition corresponds to substituting the first optic for the hole of the second:
+  \begin{example}
+  ~\begin{enumerate}[(1)]
+  \item  For any three objects $M, A, A' \in \C$, there is the \emph{tautological} optic \[t_{M,A,A'} : (M \otimes A, M \otimes A') \hto (A, A')\] given by $\rep{\id_{M \otimes A}}{\id_{M \otimes A'}}$.
+  This would be drawn as follows:
   \begin{center}
-  \input{diagrams/generic-optic-noline.tikz}
-  \quad\raisebox{1.5cm}{$\circ$}\qquad
-  \input{diagrams/generic-optic2-noline.tikz} \\
-  \raisebox{1.5cm}{$:=$}\qquad
-  \input{diagrams/optic-composition.tikz}
+  \input{diagrams/tautological-optic.tikz}
   \end{center}
 
-More formally, we wish to construct a map
-\begin{align*}
-  &\left(\int^{M \in \C} \C(S, M \otimes A) \times \C(M \otimes A', S')\right) \times \left(\int^{N \in \C} \C(R, N \otimes S) \times \C(N \otimes S', R')\right) \\
-  &\quad \to \int^{M \in \C} \C(R, M \otimes A) \times \C(M \otimes A', R').
-\end{align*}
-The product in $\Set$ preserves colimits, so in particular coends. Using this fact and the Fubini theorem for coends, the domain is isomorphic to
-\begin{align*}
-  \int^{(M, N) \in \C \times \C} \C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(R, N \otimes S) \times \C(N \otimes S', R').
-\end{align*}
-So by the universal property of coends, it suffices to construct maps
-\begin{align*}
-  & \C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(R, N \otimes S) \times \C(N \otimes S', R') \\ &
-                                                                                                              \quad \to \int^{M \in \C} \C(R, M \otimes A) \times \C(M \otimes A', R').
-\end{align*}
-natural in $M$ and $N$. For these we use the composites
-\begin{align*}
-  &\C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(R, N \otimes S) \times \C(N \otimes S', R')\\
-  \to \,& \C(N \otimes S, N \otimes M \otimes A) \times \C(N \otimes M \otimes A', N \otimes S') \times \C(R, N \otimes S) \times \C(N \otimes S', R') && \text{(functoriality of $N \otimes  -$)} \\
-  \to \,& \C(R, N \otimes  M \otimes A) \times \C(N \otimes M \otimes A', R') && \text{(composition in $\C$)} \\
-  \to \,&\int^{M \in \M} \C(R, M \otimes A) \times \C(M \otimes A', R') && \text{($\copr_{N \otimes M}$)}
-\end{align*}
-Written equationally, suppose $\rep{l'}{r'} : (R, R') \hto (S, S')$ and $\rep{l}{r} : (S, S') \hto (A, A')$ are optics with $M$ the residual for $\rep{l'}{r'}$.
-The composite $(R, R') \hto (A, A')$ is then: \[\rep{l}{r} \circ \rep{l'}{r'} := \rep{(M \otimes l)l'}{r'(M \otimes r)}.\]
-
-  We also have the \emph{identity} optic $\id_{(S, S')} : (S, S') \hto (S, S')$, given by $\rep{\lambda^{-1}_S}{\lambda_{S'}}$, where $\lambda_S : I \otimes S \to S$ is the left unitor for $S$ and similarly for $S'$.
+  \item We also have the \emph{identity} optic $\id_{(S, S')} : (S, S') \hto (S, S')$, given by $\rep{\lambda^{-1}_S}{\lambda_{S'}}$, where $\lambda_S : I \otimes S \to S$ is the left unitor for $S$ and similarly for $S'$.
 
@@
 \end{center}
+  \end{enumerate}
+\end{example}
+
+Optics compose as follows. The easiest interpretation is graphical: composition corresponds to substituting the first optic for the hole of the second:
+\begin{center}
+  \input{diagrams/generic-optic-noline.tikz}
+  \hspace{0.9cm} \raisebox{1.5cm}{$\circ$} \hspace{1cm}
+  \input{diagrams/generic-optic2-noline.tikz} \\
+  \raisebox{1.5cm}{$:=$}\qquad
+  \input{diagrams/optic-composition.tikz}
+\end{center}
+
+More formally, we wish to construct a map
+\begin{align*}
+  &\left(\int^{M \in \C} \C(S, M \otimes A) \times \C(M \otimes A', S')\right) \times \left(\int^{N \in \C} \C(R, N \otimes S) \times \C(N \otimes S', R')\right) \\
+  &\quad \to \int^{M \in \C} \C(R, M \otimes A) \times \C(M \otimes A', R').
+\end{align*}
+The product in $\Set$ preserves colimits, so in particular coends. Using this fact and the Fubini theorem for coends, the domain is isomorphic to
+\begin{align*}
+  \int^{(M, N) \in \C \times \C} \C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(R, N \otimes S) \times \C(N \otimes S', R').
+\end{align*}
+So by the universal property of coends, it suffices to construct maps
+\begin{align*}
+  & \C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(R, N \otimes S) \times \C(N \otimes S', R') \\ &
+                                                                                                              \quad \to \int^{M \in \C} \C(R, M \otimes A) \times \C(M \otimes A', R').
+\end{align*}
+natural in $M$ and $N$. For these we use the composites
+\begin{align*}
+  &\C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(R, N \otimes S) \times \C(N \otimes S', R')\\
+  \to \,& \C(N \otimes S, N \otimes M \otimes A) \times \C(N \otimes M \otimes A', N \otimes S') \times \C(R, N \otimes S) \times \C(N \otimes S', R') && \text{(functoriality of $N \otimes  -$)} \\
+  \to \,& \C(R, N \otimes  M \otimes A) \times \C(N \otimes M \otimes A', R') && \text{(composition in $\C$)} \\
+  \to \,&\int^{P \in \M} \C(R, P \otimes A) \times \C(P \otimes A', R') && \text{($\copr_{N \otimes M}$)}
+\end{align*}
+Written equationally, suppose $\rep{l'}{r'} : (R, R') \hto (S, S')$ and $\rep{l}{r} : (S, S') \hto (A, A')$ are optics with $M$ the residual for $\rep{l'}{r'}$.
+The composite $(R, R') \hto (A, A')$ is then: \[\rep{l}{r} \circ \rep{l'}{r'} := \rep{(M \otimes l)l'}{r'(M \otimes r)}.\]
 
 \begin{proposition}\label{prop:optic-is-cat}
-  The above data form a category $\Optic_\otimes$.
-\end{proposition}
-\begin{proof}
-  In~\cite[Section 6]{Doubles} this is proven abstractly, by exhibiting this category as the Kleisli category for a monad in the bicategory $\Prof$. Here we prove the conditions directly.
+  The above data form a category $\Optic_\C$.
+\end{proposition}
+\begin{proof}
+  In~\cite[Section 6]{Doubles} this is proven abstractly, by exhibiting this category as the Kleisli category for a monad in the bicategory $\Prof$. We prefer a direct proof.
 
@@
 \end{align*}
-that have residuals $M$, $N$ and $P$ respectively. As in the definition of composition, the Fubini theorem for coends allows us to choose these representatives simultaneously. Then:
+that have residuals $M$, $N$ and $P$ respectively. We must choose these representatives simultaneously but, as in the definition of composition, this is allowed by the Fubini theorem. Then:
   \begin{align*}
@@
 
-  Note that the homsets of $\Optic_\otimes$ are given by a coend indexed by a possibly large category.
+  Note that the homsets of $\Optic_\C$ are given by a coend indexed by a possibly large category.
 If $\C$ is small then the coends always exist, but if not, their existence is not guaranteed by the cocompleteness of $\Set$.
-In this case we should be careful to only discuss $\Optic$ categories where we know that the coends exist by some other means, e.g., by exhibiting an isomorphism of $\Optic_\C((S, S'), (A, A'))$ with a set.
+In this case we should be careful to only discuss optic categories where we know that the coends exist by some other means, e.g., by exhibiting an isomorphism of $\Optic_\C((S, S'), (A, A'))$ with a set.
 For all of the examples we give later we provide such a isomorphism.
@@
 \begin{remark}
-If $\C$ is a category with finite products, then $\Lens = \Optic_\times$ is exactly the category of lenses described in the introduction, so long as we restrict to optics of shape $(S, S) \hto (A, A)$.
+If $\C$ is a category with finite products, then $\Lens \defeq \Optic_\C$ is the category of lenses described in the introduction, so long as we restrict to optics of shape $(S, S) \hto (A, A)$.
 We see that optics correspond to pairs of $\fget$ and $\fput$ functions via the following isomorphisms:
 \begin{align*}
-  \Optic_\times((S, S'), (A, A'))
+  \Lens((S, S'), (A, A'))
   &= \int^{M \in \C} \C(S, M \times A) \times \C(M \times A', S') \\
@@
 \end{align*}
-%Let $\conc_\times((S, S'), (A, A'))$ denote this set of concrete lenses. 
-Explicitly the isomorphism states that, given an optic $\rep{l}{r} : (S, S') \hto (A, A')$, the corresponding concrete lens is the pair $(\fget, \fput)$, where $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
-In the other direction, given $(\fget, \fput)$, the corresponding optic has representative $\rep{[\id_S, \fget]}{\fput}$.
-
-Using the isomorphism in both directions, we leave it to the reader to verify that composition in $\Optic_\times$ corresponds to ordinary composition of concrete lenses.
+This last step deserves some explanation.
+We are applying the isomorphism $KX \cong \int^{C \in \C} \C(X,C) \times KC$ of Lemma~\ref{lem:yoneda-reduction} to the case $X = S$ and $K = \C(S, A) \times \C(- \times A', S')$.
+
+Explicitly the isomorphism states that, given an optic $\rep{l}{r} : (S, S') \hto (A, A')$, the corresponding concrete lens is the pair $\fget : S \to A$ and $\fput : S \times A' \to S'$, where $\fget = \pi_2 l$ and $\fput = r (\pi_1 l \times A)$.
+In the other direction, given $(\fget, \fput)$, the corresponding optic is represented by $\rep{[\id_S, \fget]}{\fput}$.
+
+We leave it to the reader to verify that composition in $\Lens$ corresponds to ordinary composition of concrete lenses using this isomorphism in both directions.
 (Of course, there is only one sensible way to compose such a collection of morphisms!)
@@
 
-The remainder of this section comprises some useful observations that were not made in~\cite{Doubles}.
+%The remainder of this section comprises some useful observations that were not made in~\cite{Doubles}.
 
 \begin{proposition}\label{prop:iota-functor}
-  There is a functor $\iota : \C \times \C^\op \to \Optic_\otimes$, which on objects is given by $\iota(S, S') = (S, S')$ and on a morphism $(f, g) : (S, S') \to (A, A')$ by $\iota(f, g) = \rep{\lambda_A^{-1} f}{g \lambda_{A'}}$.
+  There is a functor $\iota : \C \times \C^\op \to \Optic_\C$, which on objects is given by $\iota(S, S') = (S, S')$ and on a morphism $(f, g) : (S, S') \to (A, A')$ by $\iota(f, g) = \rep{\lambda_A^{-1} f}{g \lambda_{A'}}$.
 \end{proposition}
@@
 
-  This preserves identities, as the identity on an object $(S, S')$ in $\Optic_\otimes$ is defined to be exactly $\rep{\lambda^{-1}_S}{\lambda_{S'}}$.
+  This preserves identities, as the identity on an object $(S, S')$ in $\Optic_\C$ is defined to be exactly $\rep{\lambda^{-1}_S}{\lambda_{S'}}$.
 To check functoriality, suppose we have $(f, g) : (S, S') \to (A, A')$ and $(f', g') : (A, A') \to (B, B')$ in $\C \times \C^\op$.
@@
 
-There are some other easy-to-construct optics; specifically, optics out of  and into the monoidal unit $(I, I)$. Such maps in a monoidal category are typically called states and costates.
+There are some other easy-to-construct optics; specifically, optics out of  and into the monoidal unit $(I, I)$.
+Such maps in a monoidal category are sometimes called states and costates~\cite{CategoricalQuantumMechanics}.
 \begin{proposition}\label{prop:costates}
@@
   \begin{align*}
-    \Optic_\otimes((S, S'), (I, I))
+    \Optic_\C((S, S'), (I, I))
     &= \int^{M \in \C} \C(S, M \otimes I) \times \C(M \otimes I, S') \\
@@
 
-%\todo{Is there a relationship between $\Optic_\otimes/(I, I)$ and $[2, \C]$?}
+%\todo{Is there a relationship between $\Optic_\C/(I, I)$ and $[2, \C]$?}
 
@@
   \begin{align*}
-    \Optic_\otimes((I,I), (A,A'))
+    \Optic_\C((I,I), (A,A'))
     &= \int^{M \in \C} \C(I, M \otimes A) \times \C(M \otimes A', I) \\
@@
 \begin{theorem}
-  $\Optic_\otimes$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit object is $(I, I)$, and the action on a pair of morphisms $\rep{l}{r} : (S, S') \hto (A, A')$ and $\rep{l'}{r'} : (T, T') \hto (B, B')$ is given by:
+  $\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit object is $(I, I)$, and the action on a pair of morphisms $\rep{l}{r} : (S, S') \hto (A, A')$ and $\rep{l'}{r'} : (T, T') \hto (B, B')$ is given by:
   \begin{center}
@@
   \end{align*}
-  This is well-defined, as the calculus of string diagrams allows us to combine the coend relation on each optic to establish the coend relation for the compound diagram. \todo{draw this?}
-
+  This does not depend on the choice of representatives, as demonstrated by the equivalence of the following diagrams:
+  \begin{center}
+    \input{diagrams/tensor-on-morphisms-defined-left.tikz}
+    \input{diagrams/tensor-on-morphisms-defined-right.tikz}
+  \end{center}
   To check functoriality of $\otimes$, suppose we have optics
@@
   \end{center}
-  These two diagrams are equivalent: We can use the naturality of the symmetry morphism to push $l_2$ and $r_2$ past the crossing to be next to $l_1$ and $r_1$ respectively.
-This creates two extra twists that can be cancelled in the center of the diagram (via the coend relation).
+  These two diagrams are equivalent: we can use the naturality of the symmetry morphism to push $l_2$ and $r_2$ past the crossing to be next to $l_1$ and $r_1$ respectively.
+This creates two extra twists that can be cancelled in the center of the diagram.
 
@@
 
-  Note that because $\iota(S, S') = (S, S')$, required equations for $\iota$ to be a monoidal functor hold by definition (although we don't yet know that $\Optic_\otimes$ is monoidal).
-The pentagon and triangle equations then hold in $\Optic_\otimes$, as they are the image of the same diagrams in $\C \times \C^\op$ under $\iota$.
-The only remaining thing to verify is that these structure maps are natural in $\Optic_\otimes$, but this follows from the previous proposition.
+  Note that because $\iota(S, S') = (S, S')$, required equations for $\iota$ to be a monoidal functor hold by definition (although we don't yet know that $\Optic_\C$ is monoidal).
+The pentagon and triangle equations then hold in $\Optic_\C$, as they are the image of the same diagrams in $\C \times \C^\op$ under $\iota$.
+The only remaining thing to verify is that these structure maps are natural in $\Optic_\C$, but this follows from the previous proposition.
 
@@
 
-  In the Haskell \lenslib{} library, the monoidal product on optics is denoted ``\mintinline{haskell}{alongside}'' for the product and ``\mintinline{haskell}{without}'' for the coproduct.
+%  In the Haskell \lenslib{} library, the monoidal product on optics is denoted ``\mintinline{haskell}{alongside}'' for the product and ``\mintinline{haskell}{without}'' for the coproduct.
 
@@
 \begin{theorem}\label{thm:optic-functor}
-  The $\Optic_\otimes$ construction extends to a functor \[\Optic : \SymmMonCat \to \SymmMonCat,\] where $\SymmMonCat$ denotes the (1-)category of (small) symmetric monoidal categories and symmetric monoidal functors.
+  The $\Optic_\C$ construction extends to a functor \[\Optic : \SymmMonCat \to \SymmMonCat,\] where $\SymmMonCat$ denotes the (1-)category of (small) symmetric monoidal categories and strong symmetric monoidal functors.
 \end{theorem}
@@
 % \begin{theorem}
-%   $\Optic_\otimes$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit is $(I, I)$, and the action on morphisms induced by
+%   $\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit is $(I, I)$, and the action on morphisms induced by
 %   \begin{align*}
@@
 %
-%   Note that because $\iota(S, S') = (S, S')$, required equations for $\iota$ to be a monoidal functor hold by definition (although we don't yet know that $\Optic_\otimes$ is monoidal).
-The pentagon and triangle axioms then hold in $\Optic_\otimes$, as they are the image of the same axioms in $\C \times \C^\op$ under $\iota$.
-The only remaining thing to verify is that these structure maps are natural in $\Optic_\otimes$.
+%   Note that because $\iota(S, S') = (S, S')$, required equations for $\iota$ to be a monoidal functor hold by definition (although we don't yet know that $\Optic_\C$ is monoidal).
+The pentagon and triangle axioms then hold in $\Optic_\C$, as they are the image of the same axioms in $\C \times \C^\op$ under $\iota$.
+The only remaining thing to verify is that these structure maps are natural in $\Optic_\C$.
 %
@@
 \begin{proposition}\label{prop:iota-naturality}
-$\iota : \C \times \C^\op \to \Optic_\otimes$ ``lifts natural isomorphisms'', in the following sense.
+$\iota : \C \times \C^\op \to \Optic_\C$ ``lifts natural isomorphisms'', in the following sense.
 Given monoidal functors $F, G : \C \to \D$ and a monoidal natural isomorphism $\alpha : F \Rightarrow G$, there is an induced natural isomorphism $\Optic(\alpha) : \Optic(F) \Rightarrow \Optic(G)$ with components:
@@
 We just have to show naturality, i.e.\ that for $p : (S, S') \hto (A, A')$ in $\D$, the equation \[\Optic(\alpha)_{(A, A')} \circ \Optic(F)(p) = \Optic(G)(p) \circ \Optic(\alpha)_{(S, S')}\] holds.
+Suppose $p = \rep{l}{r}$ with residual $M$.
 On the left we have:
@@
 % \begin{proposition}
-%   Any isomorphism $p : (S, S') \hto (A, A')$ in $\Optic_\otimes$ is of the form $\iota(f, g)$ for two isomorphisms $S \to A$ and $A' \to S'$ in $\C$.
+%   Any isomorphism $p : (S, S') \hto (A, A')$ in $\Optic_\C$ is of the form $\iota(f, g)$ for two isomorphisms $S \to A$ and $A' \to S'$ in $\C$.
 % \end{proposition}
@@
 \begin{proposition}
-  If $\C$ is a strict symmetric monoidal category then $\Optic_\otimes$ is strict, and $\iota : \C \times \C^\op \to \Optic_\otimes$ is a strict monoidal functor.
+  If $\C$ is a strict symmetric monoidal category then $\Optic_\C$ is strict, and $\iota : \C \times \C^\op \to \Optic_\C$ is a strict monoidal functor.
 For $F$ a strict monoidal functor, the induced $\Optic(F)$ is also strict.
@@
 \begin{proof}
-  The structure maps of $\Optic_\otimes$ are given by $\iota$ applied to the structure maps of $\C$.
-If the latter are identities, then so are the former---the identity morphisms in $\Optic_\otimes$ are by definition $\iota(\id_S, \id_S')$.
-
-  That $\iota$ is strict is clear, as the structure morphisms in $\Optic_\otimes$ are exactly the structure morphisms in $\C \times \C^\op$ under $\iota$.
+  The structure maps of $\Optic_\C$ are given by $\iota$ applied to the structure maps of $\C$.
+If the latter are identities, then so are the former---the identity morphisms in $\Optic_\C$ are by definition $\iota(\id_S, \id_S')$.
+
+  That $\iota$ is strict is clear, as the structure morphisms in $\Optic_\C$ are exactly the structure morphisms in $\C \times \C^\op$ under $\iota$.
 
@@
 
-It will be convenient to equip $\Optic_\otimes$ with a slightly different symmetric monoidal structure.
+It will be convenient to equip $\Optic_\C$ with a slightly different symmetric monoidal structure.
 
 \begin{definition}
-  The \emph{switched} monoidal product on $\Optic_\otimes$ is given on objects by
+  The \emph{switched} monoidal product on $\Optic_\C$ is given on objects by
   \begin{align*}
@@
 
-The universal property for $\Optic_\otimes$ given in this section is an argument for this being the ``morally correct'' tensor, although it does seem a little strange.
+The universal property for $\Optic_\C$ given in this section is an argument for this being the ``morally correct'' tensor, although it does seem a little strange.
 When we later discuss lawful optics, we are forced to use the unswitched tensor to maintain the invariant that our objects are of the form $(X, X)$.
@@
 \begin{proposition}
-  $(\Optic_\otimes, \switched, (I, I))$ is a symmetric monoidal category. 
-  %that is monoidally equivalent to $\Optic_\otimes$ with the unswitched tensor.
-\end{proposition}
-\begin{proof}
-  The proof that $(\Optic_\otimes, \switched, (I, I))$ is symmetric monoidal is nearly identical to that for the unswitched tensor.
+  $(\Optic_\C, \switched, (I, I))$ is a symmetric monoidal category. 
+  %that is monoidally equivalent to $\Optic_\C$ with the unswitched tensor.
+\end{proposition}
+\begin{proof}
+  The proof that $(\Optic_\C, \switched, (I, I))$ is symmetric monoidal is nearly identical to that for the unswitched tensor.
 Note that due to the switching, the structure morphisms are slightly different:
@@
 
-%  The categories are monoidally equivalent via the identity functor \[\id : (\Optic_\otimes, \switched, (I, I)) \to (\Optic_\otimes, \otimes, (I, I)),\] where the structure isomorphisms making this functor monoidal are given by
+%  The categories are monoidally equivalent via the identity functor \[\id : (\Optic_\C, \switched, (I, I)) \to (\Optic_\C, \otimes, (I, I)),\] where the structure isomorphisms making this functor monoidal are given by
 %  \begin{align*}
@@
 \begin{remark}
-  Just as in the unswitched case, if $\C$ is a strict monoidal category than so is $(\Optic_\otimes, \switched, (I, I))$.
+  Just as in the unswitched case, if $\C$ is a strict monoidal category than so is $(\Optic_\C, \switched, (I, I))$.
 \end{remark}
@@
 \begin{proposition}
-  $\Optic_\otimes$ forms a teleological category, where:
+  $\Optic_\C$ forms a teleological category, where:
   \begin{itemize}
@@
 
-We have previously noted that $\Optic_\otimes$ is strict monoidal if $\C$ is, and that in that case the duality is strict. There are functors
+We have previously noted that $\Optic_\C$ is strict monoidal if $\C$ is, and that in that case the duality is strict. There are functors
 \begin{align*}
@@
   \end{align*}
-  where $j : \C \to \Optic_\otimes$ is the functor $j(A) := \iota(A, I)$.
+  where $j : \C \to \Optic_\C$ is the functor $j(A) := \iota(A, I)$.
 \end{proposition}
@@
   Suppose $(\C, \otimes, I)$ is a symmetric strict monoidal category and $(\T, \teletimes, I, {(-)}^*, \varepsilon)$ is a strict teleological category.
-Given a strict symmetric monoidal functor $F : \C \to \T_d$, there exists a unique strict teleological functor $K : \Optic_\otimes \to \T$ with the property $Kj = F$.
+Given a strict symmetric monoidal functor $F : \C \to \T_d$, there exists a unique strict teleological functor $K : \Optic_\C \to \T$ with the property $Kj = F$.
 \end{proposition}
@@
   We construct $K$ as follows.
-Note that any object $(S, S')$ in $\Optic_\otimes$ can be written uniquely as $j(S) \switched {j(S')}^*$, so we are forced to define $K(S, S') = FS \teletimes {(FS')}^*$.
+Note that any object $(S, S')$ in $\Optic_\C$ can be written uniquely as $j(S) \switched {j(S')}^*$, so we are forced to define $K(S, S') = FS \teletimes {(FS')}^*$.
 Suppose $\rep{l}{r} : (S, S') \hto (A, A')$ is an optic.
@@
 For two objects $M \in \M$ and $A \in \C$, the action $a(M)(A)$ is abbreviated $M \act A$ or $MA$.
-The tensor product in $\M$ will also be written as juxtaposition, so $(NM)A \cong N(MA)$.
-
-An action is \emph{lax} if $a$ is instead a lax monoidal functor.
+The tensor product in $\M$ will also be written as juxtaposition, so $(NM)A \cong N(MA)$.% An action is \emph{lax} if $a$ is instead a lax monoidal functor.
 \end{definition}
@@
 \end{align*}
+This subsumes the earlier definition, taking $\M = \C$ and having $\C$ act on itself via left-tensor:
+\begin{align*}
+a : \C &\to [\C, \C] \\
+X &\mapsto X \otimes -
+\end{align*}
+We henceforth write this case as $\Optic_\otimes$, to emphasise the action on $\C$ that is used.
 
@@
 \begin{definition}
-If $F_L : (\M, \C_L) \to (\N, \D)$ and $F_R : (\M, \C_R) \to (\N, \D)$, a mixed optic $p : (S, S) \hto (A, A)$ in $\Optic_{\actL, \actR}$ is \emph{lawful relative to $(F_L, F_R)$} if its image under $\Optic(F_L, F_R)$ in $\Optic_\N$ is lawful.
+If $F_L : (\M, \C_L) \to (\N, \D)$ and $F_R : (\M, \C_R) \to (\N, \D)$ are morphisms of actions, a mixed optic $p : (S, S) \hto (A, A)$ in $\Optic_{\actL, \actR}$ is \emph{lawful relative to $(F_L, F_R)$} if its image under $\Optic(F_L, F_R)$ in $\Optic_\N$ is lawful.
 \end{definition}
@@
 
-Suppose $\C$ is cartesian closed. We define two actions of $\C \times \C$, the first on $\C$ and the second on $\C \times \C^\op$:
+Suppose $\C$ is cartesian closed. We define two actions of $\C$, the first on $\C$ and the second on $\C \times \C^\op$:
 \begin{align*}
@@
   &\cong \int^{M \in \C} \C(S, M \times A) \times \C(M \times A', S') \times \C(J', \homC(M, I')) \\
-  &\cong \C(S, A) \times \C(S \times A', S') \times (S \times J', I')
+  &\cong \int^{M \in \C} \C(S, M) \times \C(S, A) \times \C(M \times A', S') \times \C(M \times J', I') \\
+  &\cong \C(S, A) \times \C(S \times A', S') \times \C(S \times J', I')
 \end{align*}

### 2018-08-18 paper.tex
Fix up lawful profunctor bit

@@
 \newcommand{\fover}{\textsc{Over}}
+\newcommand{\findex}{\textsc{Index}}
 
@@
 
-\title{Categories of Optics}
+\title{Categories of Optics (Draft)}
 \author{Mitchell Riley}
@@
 
-So that our lenses better conform to this intuitive idea of ``zooming in'', we often want them satisfy some conditions known as the \emph{lens laws}:
+So that our lenses better adhere to this intuitive idea of ``zooming in'', we often want them satisfy some conditions known as the \emph{lens laws}:
 \begin{center}
@@
 Then in Section~\ref{sec:examples} we see that these generic definitions specialise correctly to the other basic varieties of optic, including the laws.
-We include in Section~\ref{sec:mixed-optics} a more speculative discussion of ``mixed optics'', which include indexed and coindexed lenses and traversals.
+% We include in Section~\ref{sec:mixed-optics} a more speculative discussion of ``mixed optics'', which include indexed and coindexed lenses and traversals.
 
@@
 As this was being written, Bartosz Milewski~\cite{ProfunctorOpticsPost} independently described the isomorphism between some forms of optic and their profunctor encoding.
-In Section~\ref{sec:profunctor-optics} we extend this to more of the optic hierarchy and translate the laws into the profunctor setting.
+In Section~\ref{sec:profunctor-optics} we review this equivalence and verify that the folklore profunctor optic laws are equivalent to lawfulness as defined here.
 
@@
 
-Much of what is known about lenses and their variants is folklore, and careful verification of some of their categorical properties has been lacking.
+Much of what is known about optics is folklore, and careful verification of some of their categorical properties has been lacking.
 The aim of the present paper is to fill this gap, with the hope that a better understanding of the general structure of these categories will make it easier to generalise to new and exotic settings.
-This is particularly important with the advent of linear types in Haskell, which enables a new branch of the lens family tree, and also with the new applications to game theory.
+This is particularly important with the advent of linear types in Haskell, enabling a new branch of the lens family tree, and also with the new applications to game theory.
 
 \subsection{Contributions}
-\todo{
   \begin{itemize}
-  \item A definition of optics that uses the monoidal action of one category of another. This general enough to encompass lenses, setters, traversals, and more exotic things.
-  \item A definition of lawfulness that specialises in the correct way in and allows us to easily derive concrete laws for new kids of optic.
-Importantly, in the general case this definition is less strict than the `constant complement' definition.
-  \item A universal property satisfied by the category of optics in the monoidal case
-  \item A categorical description of optic laws as the homomorphism condition on a morphism between certain comonoids
-  \item An attempt to isolate what $\Set$-like properties are being used in some places
+  \item An careful account of the folkloric optic construction in an arbitrary symmetric monoidal category $\C$, summarised compactly as giving a functor $\Optic : \SymmMonCat \to \SymmMonCat$ (Section~\ref{sec:optics}),
+  \item A characterisation of the $\Optic$ construction as freely adding counits to a set of `dualisable morphisms' (Section~\ref{sec:teleological-categories}),
+  \item A definition of lawfulness for a general optic category that specialises in the correct way to known cases and allows us to easily derive concrete laws for new kids of optic (Section~\ref{sec:lawful-optics}),
+  \item Commentary on the optic variants used most frequently in the wild (Section~\ref{sec:examples}),
+  \item A proof that lawfulness as defined here is equivalent to the folklore profunctor lens laws. (Section~\ref{sec:profunctor-optics})
   \end{itemize}
-}
 
@@
 \begin{lemma}[Coend as coequaliser]\label{lemma:calculate-coend}
-If $\E$ is cocomplete, the coend of $P : \M^\op \times \M \to \E$ can be calculated as the coequaliser in the diagram
+If $\E$ is cocomplete and $\M$ is small, the coend of $P : \M^\op \times \M \to \E$ can be calculated as the coequaliser in the diagram
 \[
@@
   The residual $M$ should be thought of as a kind of `scratch space'; information from $S$ that we need to remember to construct $S'$.
-The quotienting imposed by the coend means we cannot inspect this temporary information, indeed, there is not even a canonical choice for the object $M$ in general, given an optic $S \hto A$.
+The quotienting imposed by the coend means we cannot inspect this temporary information, indeed, given an optic $S \hto A$ there is not even a canonical choice for the object $M$ in general.
 
@@
   \end{center}
-  reading left to right, so the left half of the diagram represents $l$ and the right half $r$. The relation expressed by the coend can be graphically expressed as:
+  reading left to right, so the portion of the diagram to the left of the line represents $l$ and the right portion $r$. The relation expressed by the coend can be drawn graphically as:
   \begin{center}
@@
 \end{align*}
-and the previous proposition states that this is a isomorphism.
-
-This is automatically natural in $\T$. Naturality in $\C$ follows by Lemma~\ref{lem:iota-commute-with-opticf}. 
+and the previous proposition states that this is a isomorphism. This is automatically natural in $\T$. Naturality in $\C$ follows by Lemma~\ref{lem:iota-commute-with-opticf}. 
 \end{proof}
@@
 \end{align*}
-
-\todo{Should I switch the entire paper into using diagrammatic order?}
+%\todo{Should I switch the entire paper into using diagrammatic order?}
 \end{remark}
 
-Let $\Twoptic_\M(S, A)$ \todo{(please come up with a better notation)} denote the set \[ \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S). \]
+Let $\Twoptic_\M(S, A)$ denote the set \[ \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S). \]
 Using the universal property of the coend, we define three maps:
@@
   We now have to slog through evaluating $\Phi(\once(p))$ and $\Phi(\twice(p))$.
+  \begingroup
+  \allowdisplaybreaks
   \begin{alignat*}{3}
@@
   \end{alignat*}
+  \endgroup
   So checking component-wise, $\Phi(\once(p))$ being equal to $\Phi(\twice(p))$ is exactly equivalent to the $\fput\fget$ and $\fput\fput$ laws holding.
@@
   \begin{align*}
-    \Optic_\times((S, S') \otimes (T, T'), (A, A')) \cong \Optic_\times((S, S'),  [(T, T'), (A, A')])
+    \Lens((S, S') \otimes (T, T'), (A, A')) \cong \Lens((S, S'),  [(T, T'), (A, A')])
   \end{align*}
@@
                                 &= [j\fput [\id_S,x !_S] \fput (i \times A), \pi_2] && \\
-                                &= [j\fput [\id_S, x !_S] \pi_1 (i \times A), \pi_2] && \text{(by $\fput\fput$ \todo{todo: detail})}\\
+                                &= [j\fput [\id_S, x !_S] \pi_1 (i \times A), \pi_2] && \text{(by $\fput\fput$)}\\ %  \todo{todo: detail}
                                 &= [jij \pi_1 (i \times A), \pi_2] && \\
@@
 \begin{definition}
-  Suppose $\C$ has finite coproducts. The \emph{category of prisms} is the category of lawful optics with respect to the coproduct $\sqcup$.
+  Suppose $\C$ has finite coproducts. The \emph{category of prisms} is the category of lawful optics with respect to the coproduct $\sqcup$: $\Prism \defeq \Optic_\sqcup$.
 \end{definition}
@@
 \begin{align*}
-  \Optic_\sqcup((S, S'), (A, A')) &= \int^{M \in \C} \C(S, M \sqcup A) \times \C(M \sqcup A', S') \\
+  \Prism((S, S'), (A, A')) &= \int^{M \in \C} \C(S, M \sqcup A) \times \C(M \sqcup A', S') \\
                                   &\cong \int^{M \in \C} \C(S, M \sqcup A) \times \C(M, S') \times \C(A, S') && \text{(universal property of coproduct)} \\
@@
 In most cases of interest to us, however, $\M$ is not right closed.
-\todo{Pointed out to me years ago when I emailed Ross Street, but I didn't understand what he was saying}
-
-In this case we can always eliminate the coend and find a concrete description of an optic:
-\begin{align*}
-&\int^{F \in \M} \C(S, F\act A) \times \C(F\act A', S') \\
+%\todo{Pointed out to me years ago when I emailed Ross Street, but I didn't understand what he was saying}
+
+When we have such a right adjoint, we can always find a concrete description of an optic:
+\begin{align*}
+\Optic_\M((S, S'), (A, A')) &= \int^{F \in \M} \C(S, F\act A) \times \C(F\act A', S') \\
 &\cong \int^{F \in \M} \C(S, F \act A) \times \M(F, R_{A'} S') \\
@@
 
-So now interpreting the optic laws, find
+So now interpreting the optic laws, we find
 \[\outside(\rep{\funzip}{\varepsilon_{S} }) = \varepsilon_{S} \; \funzip = \id_S \] is exactly the coalgebra unit law, and equality of
@@
 
-We could immediately use the previous section to give a coalgebraic description of setters and their laws, but with a little more manipulation we get a form that looks more familiar:
+We could immediately use the previous section to give a coalgebraic description of setters and their laws, but with a little manipulation we get a form that looks more familiar:
 \begin{align*}
@@
 The key is concretely describing $\Twoptic_{[\C, \C]}(S, A)$ as \[ \Set( \C(A, A) \times \C(A, A), \C(S, S) ).\] We leave the verification that the conditions are equivalent to the reader.
-\todo{Worth actually writing this out?}
+%\todo{Worth actually writing this out?}
 %Because a concrete setter is a function in $\Set$, it is enough to verify the equations pointwise.
@@
 Suppose $\C$ is cartesian closed and let $\Strong_\C$ be the category of \emph{strong functors} on $\C$.
-\todo{I define strong functor here because I also want to talk about strong monads later, should this definition wait for that?}
+%\todo{I define strong functor here because I also want to talk about strong monads later, should this definition wait for that?}
 
@@
 \begin{definition}
-The category $\Traversal$ of traversals is the category of lawful optics for the action of $\Traversable$ on $\Set$ given by evaluation.
-(Yes, the names $\Traversal$ vs\@.
-$\Traversable$ are confusing!)
+The category $\Traversal$ of traversals is the category of lawful optics for the action of $\Traversable$ on $\Set$ given by evaluation. (Yes, the names $\Traversal$/$\Traversable$ are confusing!)
 \end{definition}
 
-\todo{The rest of this section should probably be rewritten to use the free applicative functor instead of the confusing parameterised comonad business}
+%\todo{The rest of this section should probably be rewritten to use the free applicative functor instead of the confusing parameterised comonad business}
 
@@
 \begin{align*}
-\Optic_\Traversable((S, S'), (A, A')) &\cong \Set(S, \Sigma_n A^n \times \Set(A'^n,S'))
+\Traversal((S, S'), (A, A')) &\cong \Set(S, \Sigma_n A^n \times \Set(A'^n,S'))
 \end{align*}
@@
 
-\todo{What about the pointwise tensor of an entire functor?}
+%\todo{What about the pointwise tensor of an entire functor?}
 
@@
   where \[ \funzip \circ - : \homC(A, S) \to \homC(A, \homC(A, S) \otimes A) \] denotes internal composition and \[\coev_{\homC(A, S), A} : \homC(A, S) \to \homC(A, \homC(A, S) \otimes A)\] is coevaluation.
-  \todo{I obviously need better names for the laws} \qed
+  %\todo{I obviously need better names for the laws} 
+  \qed
 \end{proposition}
@@
 
-\todo{I suspect there is a 1-to-1 correspondence between strengths on $T$ and actions of $\C$ on $\C_T$ by $A \otimes B$ on objects, is it worth proving this?}
+%\todo{I suspect there is a 1-to-1 correspondence between strengths on $T$ and actions of $\C$ on $\C_T$ by $A \otimes B$ on objects, is it worth proving this?}
 \end{proof}
@@
 \end{align*}
-Using the coalgebraic description, we see that concrete effectful lenses consist of a single morphism \[\munzip : S \to T(\homC(A', T S') \otimes A).\] The optic laws in this case specialise to:
+Using the coalgebraic description, we see that concrete effectful lenses consist of a single morphism in $\C$ \[\munzip : S \to T(\homC(A', T S') \otimes A).\] The optic laws in this case specialise to:
 
@@
 \end{align*}
-\todo{todo: define its unit, multiplication and strength}
+%This is the monad for the tensor-hom adjunction. There are a pair of useful morphisms in the Kleisli category:
+%\begin{align*}
+%\textsc{GetState} &: 1 \to Q \\
+%\textsc{PutState} &: Q \to 1
+%\end{align*}
+%where $\textsc{GetState}$ is the transpose of the diagonal map $1 \times Q \cong Q \to Q \times Q$, and $\textsc{PutState}$ is the transpose of the second projection $Q \times Q \to Q \cong 1 \times Q$.
 \end{definition}
 
-We can find a concrete description of optics for the action $\monact : \C \times \C_{T_Q} \to \C_{T_Q}$ that is closer to that for ordinary lenses.
-\begin{align*}
-\Optic((S, S'), (A, A'))
+We call optics for the action $\monact : \C \times \C_{T_Q} \to \C_{T_Q}$ \emph{stateful lenses}. We can find a concrete description that is closer to that for ordinary lenses:
+\begin{align*}
+\Optic_\monact((S, S'), (A, A'))
 &= \int^{M \in \C} \C_{T_Q}(S, M \monact A) \times \C_{T_Q}(M \monact A', S') \\
@@
 By analogy with ordinary lenses, let us call these maps $\mget$ and $\mput$. 
-
-\todo{Explain how composition works in code?}
+The induced composition of effectful lenses is a little intricate, and is possibly best explained in code.
+The composite $\mget$ is straightforward, just the composite of $\mget_1$ and $\mget_2$ in the Kleisli category.
+For $\mput$ however, there is some curious plumbing of the state into different places.
+Tracing through the isomorphism, two stateful lenses $(\mget_1, \mput_1) : (T, T') \hto (S, S')$ and $(\mget_2, \mput_2) : (S, S') \hto (A, A')$ compose as follows.
+\begin{minted}{haskell}
+mget t = do
+  s <- mget1 t
+  mget2 s
+
+mput t q a = do 
+  start <- getState
+  s <- mget1 t
+  q' <- getState
+  putState start
+
+  s' <- mput1 s q' a
+  mput2 t q s'
+\end{minted}
 
 \begin{proposition}
-\todo{Translate this from code}
 A stateful lens given by
@@
 \end{minipage}
-\end{proposition}
-We may as well also name these the $\fget\fput$, $\fput\fget$ and $\fput\fput$ laws.
-\begin{proof}
+By analogy we call these the $\fget\fput$, $\fput\fget$ and $\fput\fput$ laws.
+\end{proposition}
+
+%\begin{proof}
 %We similarly calculate
@@
 %\end{align*}
-\todo{This is a mess}
-\end{proof}
+%\todo{This is a mess}
+%\end{proof}
 
 Of course, this notion of effectful lens may not be useful!
-It is hard to get intuition for the meaning of the laws, but they seem to suffer from the same deficiencies that other attempts do: they are too strong.
+It is hard to get intuition for the meaning of the laws, but they seem to suffer from the same deficiency that other attempts at effectful lenses do: they are too strong.
 The $\fget\fput$ law here appears easier to satisfy than the $\mathsf{MGetPut_0}$ law of~\cite{ReflectionsOnMonadicLenses}, as $\mput$ is given access to the original state.
-However, our $\fput\fget$ law seems very difficult to satisfy: no matter what auxiliary state is provided, $\fput$ting then $\fget$ting must leave the state unchanged.
-
-\todo{Try out some examples given in other papers?}
+However, our $\fput\fget$ law seems very restrictive: no matter what auxiliary state is provided, $\fput$ting then $\fget$ting must leave the state unchanged.
 
@@
 
-\item \emph{Adjunction Lenses}: For a category with finite products $\C$ and a monoidal adjunction $F \dashv U$, with $F : \C \to \D$ and $U : \D \to \C$.
+%\item \emph{Adjunction Lenses}: For a category with finite products $\C$ and a monoidal adjunction $F \dashv U$, with $F : \C \to \D$ and $U : \D \to \C$.
 If $U$ is strong monoidal then $\D$ acts on $\C$ by $UD \act A := D \times A$; as an example consider the free-forgetful adjunction between sets and monoids.
-Concrete optics for this action are given pairs in
-\[ \C(S, A) \times \C(UFS \times A', S') \]
-\todo{This example is a bit dumb, delete?}
+Concrete optics for this action are given by elements of
+%\[ \C(S, A) \times \C(UFS \times A', S') \]
+%\todo{This example is a bit dumb, delete?}
 \end{itemize}
@@
 
-\section{Mixed Optics}\label{sec:mixed-optics}
-
-We can generalise the definition of $\Optic$ so that the two halves lie in different categories, allowing us to capture a few more optic variants found in the wild.
-Suppose $\C_L$ and $\C_R$ are categories that are acted on by a common monoidal category $\M$.
-Write these actions as $\actL : \M \to [\C_L, \C_L]$ and $\actR : \M \to [\C_R, \C_R]$ respectively.
-
-\begin{definition}
-  Given two objects of $\C_L \times \C_R^\op$, say $(S, S')$ and $(A, A')$, an \emph{optic} $p : (S, S') \hto (A, A')$ is an element of the set
-  \begin{align*}
-    \Optic_{\actL, \actR}((S, S'), (A, A')) := \int^{M \in \M} \C_L(S, M \actL A) \times \C_R(M \actR A', S')
-  \end{align*}
-\end{definition}
-
-Several results from Section~\ref{sec:optics} have analogues in this setting.
-\begin{proposition}\label{prop:mixed-optic-is-cat}
-  $\Optic_{\actL, \actR}$ is a category. \qed
-\end{proposition}
-\begin{proposition}
-  There is a functor $\iota : \C_L \times \C_R^\op \to \Optic_{\actL, \actR}$, which on objects is given by $\iota(S, S') = (S, S')$ and on a morphism $(f, g) : (S, S') \to (A, A')$ by \[\iota(f, g) = \rep{{(\lambda^{\C_L}_A)}^{-1} f}{g \lambda^{\C_R}_{A'}},\] where $\lambda^{\C_L}_A : A \to IA$ in $\C_L$ and $\lambda^{\C_R}_{A'} : A' \to IA'$ in $\C_R$.
-\qed
-\end{proposition}
-\begin{proposition}\label{prop:mixed-change-of-action}
-  Given two morphisms of actions $F_L : (\M, \C_L) \to (\N, \D_L)$ and $F_R : (\M, \C_R) \to (\N, \D_R)$, there is an induced functor $\Optic(F_L, F_R) : \Optic_{\actL_1, \actR_1} \to \Optic_{\actL_2, \actR_2}$.
-\qed
-\end{proposition}
-
-The notion of lawfulness used earlier breaks down in this setting, as the definition of $\Twoptic(S, A)$ only makes sense when $\C_L = \C_R$. The following definition gives a reasonable approximation.
-
-\begin{definition}
-If $F_L : (\M, \C_L) \to (\N, \D)$ and $F_R : (\M, \C_R) \to (\N, \D)$ are morphisms of actions, a mixed optic $p : (S, S) \hto (A, A)$ in $\Optic_{\actL, \actR}$ is \emph{lawful relative to $(F_L, F_R)$} if its image under $\Optic(F_L, F_R)$ in $\Optic_\N$ is lawful.
-\end{definition}
-
-\subsection{Degenerate Optics}
-
-The \mintinline{haskell}{Getter}s and \mintinline{haskell}{Review}s of the Haskell lens library corresponds simply to a morphisms $S \to A$ and $A' \to S'$ respectively.
-These are examples of mixed optics as follows.
-
-Recall that for any category $\C$, there is a category $\C_\codisc$ with the same objects, but where every homset is the singleton set.
-For any action of $\M$ on $\C$ there is a corresponding action of $\M$ on $\C_\codisc$ that has the same action on objects, and a morphism of actions $i : (\M, \C) \to (\M, \C_\codisc)$ which is the identity on objects.
-
-Now for a category with finite products $\C$, define $\Getter$ to be the category of mixed optics $\Optic_{\times, \C, \C_\codisc}$. This is indeed isomorphic to $\C$:
-\begin{align*}
-&\int^{M \in \M} \C(S, M \times A) \times \C_\codisc(M \times A', S')\\
-&\cong \int^{M \in \M} \C(S, M \times A) \\
-&\cong \C(S, 1 \times A) \\
-&\cong \C(S, A)
-\end{align*}
-The only sensible notion of lawfulness for $\Getter$s is lawfulness relative to $(i, \id_{\C_\codisc})$, but all optics in $\Optic_{\C_\codisc}$ are trivially lawful.
-
-One defines $\Review := \Optic_{\sqcup, \C_\codisc, \C}$ in the same way. There are induced functors $\Optic(\id_\C, i) : \Lens \to \Getter$ and $\Optic(i, \id_\C) : \Prism \to \Review$.
-
-If we we are working linearly, we should not expect $\Optic_{\otimes, \C, \C_\codisc}$ to be described so neatly; the above isomorphism relies on the unit of the monoidal structure being terminal.
-
-Finally, we can also encode the category of \mintinline{haskell}{Fold}s. In $\Set$, a fold $S \hto A$ corresponds to a function $S \to \mathrm{List}\,A$. Define 
-\begin{align*}
-\Fold := \Optic_{\Traversable, \C, \C_\codisc}
-\end{align*}
-The key is that the $\mathrm{List}$ functor is the terminal $\Traversable$ functor. We therefore have isomorphisms
-\begin{align*}
-&\int^{M \in \Traversable} \Set(S, MA) \times \Set_\codisc(MA', S') \\
-&\cong \int^{M \in \Traversable} \Set(S, MA) \\
-&\cong \Set(S, \mathrm{List}\,A)
-\end{align*}
-There is an induced functor $\Optic(\id_C, i) : \Traversal \to \Fold$.
-
-\subsection{Indexed Lenses}
-As well as giving a principled home to degenerate optics, the notion of mixed optics also allows us to describe \emph{indexed optics} categorically.
-The most interesting example of an indexed optic variant is the \emph{indexed traversal}, which, for example, allows one to know the index of an entry of a list as one is traversing it.
-As a warmup, however, let us look at \emph{indexed lenses}, which provide access to an index alongside a target, but do not allow updates to the index.
-
-Suppose $\C$ is cartesian closed. We define two actions of $\C$, the first on $\C$ and the second on $\C \times \C^\op$:
-\begin{align*}
-M \actL A  &:= M \times A\\
-M \actR (A, I) &:= (M \times A, \homC(M, I))
-\end{align*}
-
-\begin{definition}
-The category of \emph{indexed lenses} $\IdxLens$ in $\C$ is the category of mixed optics $\Optic_{\actL, \actR}$ with the actions as given above.
-\end{definition}
-Describing concrete indexed lenses is straightforward:
-\begin{align*}
-  &\Optic_{\actL, \actR}((S, (S', J')), (A, (A', I'))) \\
-  &= \int^{M \in \C} \C(S, M \actL A) \times (\C \times \C^\op)(M \actR (A', I'), (S', J')) \\
-  &\cong \int^{M \in \C} \C(S, M \times A) \times (\C \times \C^\op)((M \times A', \homC(M, I')), (S', J')) \\
-  &\cong \int^{M \in \C} \C(S, M \times A) \times \C(M \times A', S') \times \C^\op(\homC(M, I'), J') \\
-  &\cong \int^{M \in \C} \C(S, M \times A) \times \C(M \times A', S') \times \C(J', \homC(M, I')) \\
-  &\cong \int^{M \in \C} \C(S, M) \times \C(S, A) \times \C(M \times A', S') \times \C(M \times J', I') \\
-  &\cong \C(S, A) \times \C(S \times A', S') \times \C(S \times J', I')
-\end{align*}
-
-\todo{talk about polymorphism to manage the indices}
-
-\begin{remark}
-There appears to be some flexibility in what actions are used here. To have the indices behave covariantly rather than contravariantly, we could have $\C$ act on $\C$ and $\C \times \C$ as follows:
-\begin{align*}
-M \actL A &:= M \times A \\
-M \actR (A, I) &:= (M \times A, M \times I)
-\end{align*}
-which gives concrete optics in the form
-\begin{align*}
-\C(S, A) \times \C(S \times A', S') \times \C(S \times I', J').
-\end{align*}
-We chose the previous, more contorted actions so that indexed lenses are more clearly related to indexed traversals, which we define presently.
-%We calculate:
-%\begin{align*}
-%  &\Optic_{\actL, \actR}((S, (S', J')), (A, (A', I'))) \\
-%  &\cong \int^{(M, R) \in \C \times \C} \C(S, (M, R) \actL A) \times (\C \times \C)((M, R) \actR (A', I'), (S', J')) \\
-%  &\cong \int^{(M, R) \in \C \times \C} \C(S, M \times R \times A) \times \C(M \times A', S') \times \C(R \times I', J') \\
-%  &\cong  \C(S, A) \times \C(S \times A', S') \times \C(S \times I', J')
-%\end{align*}
-\end{remark}
-
-\subsection{Indexed Traversals}
-
-Returning to indexed traversals, we first need to define indexed traversable functors.
-Unfortunately this has many moving parts!
-For simplicity we will restrict our attention to $\C = \Set$, although the results here may be applicable more generally.
-
-\begin{proposition}
-The assignment $F \act X \mapsto \Set(R, FX)$ extends to a lax action of $\App$ on $\Set$, called the \emph{$R$-indexed action of $\App$ on $\Set$}.
-\end{proposition}
-\begin{proof}
-The structure map for the lax action is given by the composite
-\begin{align*}
-F \act (G \act X) &= \Set(R, F\Set(R, GX)) \\
-&\to \Set(R, \Set(FR, FGX)) \\
-&\to \Set(R \times FR, FGX) \\
-&\to \Set(R \times R, FGX) \\
-&\to \Set(R, FGX) = (FG) \act X
-\end{align*}
-\todo{more}
-\end{proof}
-
-\begin{definition}
-A \emph{traversable functor indexed by $R$} is a functor $T : \Set \to \Set$ equipped with a distributive law $\delta_F : T(\Set(R, F-)) \to FT$ for $T$ between the $R$-indexed action of $\App$ on $\Set$ and the (unindexed) action of $\App$ on $\Set$ by evaluation.
-\end{definition}
-
-\begin{definition}
-The category of \emph{indexed traversable functors} $\IdxTraversable$ has as objects pairs $(T, R)$, where $R \in \Set$ and $T : \Set \to \Set$ is a traversable functor indexed by $R$.
-A morphism $(T, R) \to (T', R')$ is a natural transformation $\alpha : T \Rightarrow T'$ and morphism (note the direction!) $r : R' \to R$, such that $\alpha$ commutes with the distributive laws on both traversable functors, using $r$ to mediate between the index objects.
-\todo{draw this out}
-\end{definition}
-
-\begin{proposition}
-$\IdxTraversable$ acts on $\C \times \C$ by $(T, R) \act (A, I) \mapsto (TA, \homC(R, I))$ and on $\C$ simply by $(T, R) \act A \mapsto TA$.
-\end{proposition}
-
-The idea for this action comes from~\cite{IndexedOpticsPost}.
-
-\begin{conjecture}
-The category of indexed traversals corresponds to the category of mixed optics with the action of $\IdxTraversable$ on $\C \times \C$ on the left and $\C$ on the right.
-\end{conjecture}
-
-\subsection{Coindexed Optics}
-
-\section{Profunctor Optics}\label{sec:profunctor-optics}
-The Haskell \lenslib{} library implements optics using what is known as the \emph{profunctor encoding}. Lenses are defined as follows:
-
+\section{The Profunctor Encoding}\label{sec:profunctor-optics}
+To use optics in practice, one could take the definition of the optic category and translate it almost verbatim into code---using an existential type in place of the coend.
+In Haskell syntax, lenses would be defined as:
 \begin{minted}{haskell}
-class Profunctor p => Strong p where
-  second' :: p a b -> p (c, a) (c, b)
-
-type Lens s a = forall p. Strong p => p a a -> p s s
+data Lens s s' a a' = forall m. Lens {
+  l :: s -> (m, a),
+  r :: (m, a') -> s'
+}
 \end{minted}
-
-\todo{explain the benefits of this encoding}
+This not the approach taken in the \lenslib{} library!
+Instead the somewhat indirect \emph{profunctor encoding} is used.
+(This is not quite true, for a few reasons the \lenslib{} library actually uses the closely related \emph{van Laarhoven encoding}, see Section~\ref{sec:van-laarhoven}.
+The Purescript \texttt{purescript-profunctor-lenses} library~\cite{PurescriptLibrary} does use the profunctor encoding directly.)
+
+The equivalence between the profunctor encoding and optics as described earlier has been explored in~\cite{ProfunctorOptics} and~\cite{ProfunctorOpticsPost}.
+We begin by reviewing this equivalence from a categorical perspective before investigating how the optic laws manifest in this setting.
 
@@
   \begin{align*}
-    \alpha_{A,B,M} : P(A,B) \to P(MA, MB)
-  \end{align*}
-  natural in $A$ and $B$, and dinatural in $M$, and such that $\alpha_{A,B,I} = \id_{P(A,B)}$, and $\alpha$ commutes with the tensor of $\M$:
+    \zeta_{A,B,M} : P(A,B) \to P(MA, MB)
+  \end{align*}
+  natural in $A$ and $B$, dinatural in $M$, and such that $\zeta$ commutes with the action of $\M$:
   \[
     \begin{tikzcd}
-      P(A,B) \ar[r, "\alpha_{A,B,M}"] \ar[dr, "\alpha_{A, B, NM}" below left] & P(MA, MB) \ar[d, "\alpha_{MA, MB, N}" right] \\
-      & P(NMA, NMB)
+      P(A,B) \ar[r, "\zeta_{A,B,M}"] \ar[d, "\zeta_{A, B, NM}" swap] & P(MA, MB) \ar[d, "\zeta_{MA, MB, N}" right] \\
+      P((NM)A), (NM)B) \ar[r, "\alpha_{N, M, A}" swap] & P(N(MA), N(MB))
+    \end{tikzcd}
+    \qquad
+    \begin{tikzcd}
+      P(A,B) \ar[r, "\zeta_{A,B,I}"] \ar[dr, equal] & P(IA, IB) \ar[d, "{P(\lambda_A^{-1}, \lambda_B)}" right] \\
+      & P(A, B)
     \end{tikzcd}
@@
 
-Note that the identity profunctor $I$ has a canonical Tambara module structure for any $\M$ given by functoriality.
-
-If $P, Q \in \Prof(\C, \C)$ are equipped with module structures $\alpha$ and $\beta$ respectively, there is a canonical module structure on $P \odot Q$.
-Given $M \in \M$ and $A,B \in \C$, the structure map ${(\alpha \odot \beta)}_{A,B,M}$ is induced by
+Note that the identity profunctor $I$ has a canonical Tambara module structure $\zeta_{A, B, M} : \C(A, B) \to \C(MA, MB)$ for any $\M$ given by functoriality.
+
+If $P, Q \in \Prof(\C, \C)$ are equipped with module structures $\zeta$ and $\xi$ respectively, there is a canonical module structure on $P \odot Q$.
+Given $M \in \M$ and $A,B \in \C$, the structure map ${(\zeta \odot \xi)}_{A,B,M}$ is induced by
 \begin{align*}
   &P(A,C) \times Q(C,B)  \\
-  \xrightarrow{\alpha_{A,C,M} \times \beta_{C,B,M}} \quad& P(MA, MC) \times Q(MC, MB) \\
+  \xrightarrow{\zeta_{A,C,M} \times \xi_{C,B,M}} \quad& P(MA, MC) \times Q(MC, MB) \\
   \xrightarrow{\copr_{MC}} \quad&\int^{C \in \C} P(MA, C) \times Q(C, MB) \\
@@
 \begin{definition}
-  There is a category $\Tamb(\M)$ of Tambara modules and natural transformations that respect the module structure, in the sense that for any $l : P \to Q$, the diagram
+  There is a category $\Tamb_\M$ of Tambara modules and natural transformations that respect the module structure, in the sense that for any $l : P \to Q$, the diagram
   \[
     \begin{tikzcd}
-      P(A,B) \ar[r, "\alpha_{A,B,M}"] \ar[d, "l_{A,B}" left] & P(MA, MB) \ar[d, "l_{MA, MB}" right] \\
-      Q(A,B) \ar[r, "\beta_{A,B,M}"] & Q(MA, MB)
+      P(A,B) \ar[r, "\zeta_{A,B,M}"] \ar[d, "l_{A,B}" left] & P(MA, MB) \ar[d, "l_{MA, MB}" right] \\
+      Q(A,B) \ar[r, "\xi_{A,B,M}" swap] & Q(MA, MB)
     \end{tikzcd}
@@
 This category is monoidal with respect to $\odot$ as given above with monoidal unit $I$.
-
-  In the code, the \mintinline{haskell}{Strong} typeclass corresponds to supplying the structure map $\alpha$ for a profunctor \texttt{p}.
-Parametricity guarantees a form of (di)naturality for $M$, $A$ and $B$, but as with any definition in Haskell, the equations required of a Tambara module must be checked by hand.
-
-There is an evident forgetful functor $U : \Tamb(\M) \to \Prof(\C, \C)$ that is strong monoidal.
+There is an evident forgetful functor $U : \Tamb_\M \to \Prof(\C, \C)$ that is strong monoidal.
 This forgetful functor has both a left and right adjoint; important for us is the left adjoint: (The right adjoint to $U$ is described in~\cite{NotionsOfComputationAsMonoids}, used there to investigate Haskell's \mintinline{haskell}{Arrow} typeclass.)
@@
 \begin{definition}[{\cite[Section 5]{Doubles}}]
-  Let $\Pastro_\M : \Prof(\C, \C) \to \Tamb(\M)$ be the functor:
+  Let $\Pastro_\M : \Prof(\C, \C) \to \Tamb_\M$ be the functor:
   \begin{align*}
@@
   \end{align*}
-  The module structure $\alpha_{A,B,M} : \Pastro_\M P(A,B) \to \Pastro_\M P (MA, MB)
+  The module structure $\zeta_{A,B,M} : \Pastro_\M P(A,B) \to \Pastro_\M P (MA, MB)
   $ is induced by the maps
@@
   \end{align*}
-  for all $C, D \in \C$ and $N \in \M$. Equationally, this is $\alpha_{A,B,M}(\repthree{l}{p}{r} ) = \repthree{Ml}{p}{Mr} $.
+  for all $C, D \in \C$ and $N \in \M$. Equationally, this is $\zeta_{A,B,M}(\repthree{l}{p}{r} ) = \repthree{Ml}{p}{Mr} $.
 \end{definition}
@@
 \begin{proposition}
-  $\Pastro_\M : \Prof(\C, \C) \to \Tamb(\M)$ is left adjoint to $U : \Tamb(\M) \to \Prof(\C, \C)$.
-\end{proposition}
-\begin{proof}
-  For any $P \in \Prof(\C, \C)$, there is a map $\eta : P \hto U \Phi_\M P$, given by $\eta(p) = \repthree{\id_A}{p}{\id_B}$.
+  $\Pastro_\M : \Prof(\C, \C) \to \Tamb_\M$ is left adjoint to $U : \Tamb_\M \to \Prof(\C, \C)$.
+\end{proposition}
+\begin{proof}
+  For any $P \in \Prof(\C, \C)$, there is a map $\eta : P \hto U \Pastro_\M P$, given by $\eta(p) = \repthree{\id_A}{p}{\id_B}$.
 
@@
   \begin{align*}
-    \repthree{l}{p}{r} = \Pastro_\M P(l, r) \alpha_{A, B, M} \; \eta(p)
-  \end{align*}
-  where $\alpha_{A, B, M}$ is the module structure map for $\Pastro_\M P$.
-
-  Now suppose $T \in \Tamb(\M)$ is a Tambara module with structure map $\beta$.
-We would like to show that for any map $f : P \hto UT$, there exists a unique $\hat f : \Phi_\M P \hto T$ so that $f$ factors as \[P \xrightarrow{\eta} U \Phi_\M P \xrightarrow{U\hat f} UT.
+    \repthree{l}{p}{r} = (\Pastro_\M P(l, r)) \zeta_{A, B, M} \; \eta(p)
+  \end{align*}
+  where $\zeta_{A, B, M}$ is the module structure map for $\Pastro_\M P$.
+
+  Now suppose $T \in \Tamb_\M$ is a Tambara module with structure map $\xi$.
+We would like to show that for any map $f : P \hto UT$, there exists a unique $\hat f : \Pastro_\M P \hto T$ so that $f$ factors as \[P \xrightarrow{\eta} U \Pastro_\M P \xrightarrow{U\hat f} UT.
 \]
 
-  The data of such a map $\hat f : \Phi_\M P \hto T$ is a natural transformation between the underlying profunctors.
-For the factorisation property to hold, we must have that $\hat{f}\eta(p) = f(p)$ for any $p \in P(A,B)$, but then the action on the remainder of $\Phi_\M P(A, B)$ is fixed:
-  \begin{align*}
-    \hat{f}(\repthree{l}{p}{r}) &= \hat{f}(\Pastro_\M P(l, r) \alpha_{A, B, M} \; \eta(p)) \\
-                                     &=T(l, r) \; \beta_{A, B, N} \; f(p)
+  The data of such a map $\hat f : \Pastro_\M P \hto T$ is a natural transformation between the underlying profunctors.
+For the factorisation property to hold, we must have that $\hat{f}\eta(p) = f(p)$ for any $p \in P(A,B)$, but then the action on the remainder of $\Pastro_\M P(A, B)$ is fixed:
+  \begin{align*}
+    \hat{f}(\repthree{l}{p}{r}) 
+    &= \hat{f}(\Pastro_\M P(l, r) \zeta_{A, B, M} \; \eta(p)) \\
+    &=T(l, r) \; \xi_{A, B, N} \; f(p)
   \end{align*}
@@
   \begin{align*}
-    \hat{f}\alpha_{A,B,N}(\repthree{l}{p}{r})
-    &= \hat{f}(\repthree{Nl}{p}{Nr}) && \text{(definition of $\alpha$)}\\
-    &= T(Nl, Nr) \; \beta_{A, B, NM} \; f(p) && \text{(definition of $\hat{f}$)}\\
-    &= T(Nl, Nr) \beta_{MA,MB,N} \; \beta_{A, B, M} \; f(p) && \text{($\beta$ commutes with tensor in $\M$)} \\
-    &= \beta_{A,B,N} T(l, r) \; \beta_{A, B, M} \; f(p) && \text{(naturality of $\beta$)} \\
-    &= \beta_{A,B,N} \hat{f} (\repthree{l}{p}{r}) && \text{(definition of $\hat{f}$)}
+    \hat{f}\zeta_{A,B,N}(\repthree{l}{p}{r})
+    &= \hat{f}(\repthree{Nl}{p}{Nr}) && \text{(definition of $\zeta$)}\\
+    &= T(Nl, Nr) \; \xi_{A, B, NM} \; f(p) && \text{(definition of $\hat{f}$)}\\
+    &= T(Nl, Nr) \xi_{MA,MB,N} \; \xi_{A, B, M} \; f(p) && \text{($\xi$ commutes with tensor in $\M$)} \\
+    &= \xi_{A,B,N} T(l, r) \; \xi_{A, B, M} \; f(p) && \text{(naturality of $\xi$)} \\
+    &= \xi_{A,B,N} \hat{f} (\repthree{l}{p}{r}) && \text{(definition of $\hat{f}$)}
   \end{align*}
@@
 \begin{corollary}
-  $\Pastro_\M$ is oplax monoidal.
+  $\Pastro_\M$ (and therefore also $U \Pastro_\M$) is oplax monoidal.
 \end{corollary}
 \begin{proof}
-  This follows from abstract nonsense as the left adjoint of a strong monoidal functor, see~\cite{Kelly1974}.
+  This follows from abstract nonsense as $\Pastro_\M$ is the left adjoint of a strong monoidal functor, see~\cite{Kelly1974}.
 \end{proof}
@@
 Given a profunctor, or indeed a Tambara module, we can evaluate it at any two objects of $\C$.
-This process is functorial in the choice of Tambara module, giving a functor $(U-)(A,A') : \Tamb(\M) \to \Set$.
+This process is functorial in the choice of Tambara module, giving a functor $(U-)(A,A') : \Tamb_\M \to \Set$.
 
 \begin{lemma}\label{lemma-rep}
-  The functor $(U-)(A,A') : \Tamb(\M) \to \Set$ is representable: there is a natural isomorphism
-  $(U-)(A,A') \cong \Tamb(\M)(\Pastro_\M E_{A, A'}, -)$
+  The functor $(U-)(A,A') : \Tamb_\M \to \Set$ is representable: there is a isomorphism $(U-)(A,A') \cong \Tamb_\M(\Pastro_\M E_{A, A'}, -)$
 \end{lemma}
 \begin{proof}
-  We have the chain of natural isomorphisms:
+  We have the chain of isomorphisms:
   \begin{align*}
@@
     \cong \;&\Prof(E_{A, A'}, U-) && \text{(natural transformations as ends)} \\
-    \cong \;&\Tamb(\M)(\Pastro_\M E_{A, A'}, -) && \text{(by adjointness)}
-  \end{align*}
-\end{proof}
+    \cong \;&\Tamb_\M(\Pastro_\M E_{A, A'}, -) && \text{(by adjointness)}
+  \end{align*}
+\end{proof}
+
+Note that the value of $\Pastro_\M E_{A, A'}$ at $(X,Y)$ is precisely the set of optics $(X, Y) \hto (A, A')$:
+\begin{align*}
+\Pastro_\M E_{A, A'} (X, Y)
+&= \int^{M \in \M} \int^{C,D \in \C} \C(X, MC) \times E_{A, A'}(C,D) \times  \C(MD, Y) \\
+&= \int^{M \in \M} \int^{C,D \in \C} \C(X, MC) \times \C(C, A) \times \C(A', D) \times \C(MD, Y) \\
+&\cong \int^{M \in \M} \C(X, MA) \times \C(MA', Y)
+\end{align*}
+For convenience we identify $\Pastro_\M E_{A, A'}(X,Y)$ with $\Optic_\M((X, Y), (A, A'))$.
 
@@
   \begin{align*}
-    [\Tamb(\M), \Set]((U-)(A,A'),(U-)(S,S')) &\cong \Optic_\M((S, S'), (A, A'))
+    [\Tamb_\M, \Set]((U-)(A,A'),(U-)(S,S')) &\cong \Optic_\M((S, S'), (A, A'))
   \end{align*}
@@
   \begin{align*}
-    &[\Tamb(\M), \Set]((U-)(A,A'),(U-)(S,S')) \\
-    \cong \;&[\Tamb(\M), \Set](\Tamb(\M)(\Pastro_\M E_{A, A'}, -), (U-)(S,S'))  && \text{(by Lemma~\ref{lemma-rep})}\\
+    &[\Tamb_\M, \Set]((U-)(A,A'),(U-)(S,S')) \\
+    \cong \;&[\Tamb_\M, \Set](\Tamb_\M(\Pastro_\M E_{A, A'}, -), (U-)(S,S'))  && \text{(by Lemma~\ref{lemma-rep})}\\
     \cong \;&(U\Pastro_\M E_{A, A'})(S,S')  && \text{(by Yoneda)} \\
-    = \;&\int^{M \in \M} \int^{C,D \in \C} \C(S, MC) \times E_{A, A'}(C,D) \times \C(MD,S') \\
-    = \;&\int^{M \in \M} \int^{C,D \in \C} \C(S, MC) \times \C(C,A) \times \C(A',D) \times \C(MD,S') \\
-    \cong \;&\int^{M \in \M} \C(S, MA) \times \C(MA', S')  && \text{(by Yoneda reduction twice)} \\
     = \;&\Optic_\M((S, S'), (A, A'))
@@
 
-  This proposition justifies the profunctor encoding
-\begin{minted}{haskell}
-type Lens s a = forall p. Strong p => p a a -> p s s
-\end{minted}
-  using parametricity as a proxy for naturality.
-  \todo{I've just noticed, isn't this a cheat? This would be naturality wrt ALL profunctor morphisms, not just morphisms of Tambara modules. Can I find a place where this breaks?}
-
 For $p : (S, S') \hto (A, A')$, let $\tilde{p} : (U-)(A,A') \Rightarrow (U-)(S,S')$ denote the corresponding natural transformation under this isomorphism, and for $t : (U-)(A,A') \Rightarrow (U-)(S,S')$, let $\hat{t} : (S, S') \hto (A, A')$ be the corresponding optic.
@@
 \begin{corollary}
-  A profunctor optic $p$ is determined by its component at $\Pastro_\M E_{A, A'}$, and furthermore, this component is determined by its value on $\repfour{\id_A}{\id_A}{\id_{A'}}{\id_{A'}} \in (U \Pastro_\M E_{A, A'})(A, A')$.
+  A profunctor optic $t$ is determined by its component at $\Pastro_\M E_{A, A'}$, and furthermore, this component is determined by its value on $\rep{\lambda_A^{-1}}{\lambda_{A'}} \in (U \Pastro_\M E_{A, A'})(A, A')$.
 \end{corollary}
@@
   This is the content of the first two isomorphisms above.
-Explicitly, suppose $\hat{p} = \rep{l}{r}$ with $l : S \to MA$ and $r : MA' \to S'$.
-Then for any Tambara module $P$, the component of $p$ at $P$ is
-  \begin{align*}
-    p_P = (UP)(l,r) \alpha_{A,A',M}
-  \end{align*}
-  where $\alpha$ is the module structure for $P$. In particular,
+Explicitly, suppose $p = \rep{l}{r}$ with $l : S \to MA$ and $r : MA' \to S'$.
+Then for any Tambara module $P$, the component of $\tilde{p}$ at $P$ is
+  \begin{align*}
+    \tilde{p}_P = (UP)(l,r) \zeta_{A,A',M}
+  \end{align*}
+  where $\zeta$ is the module structure for $P$. In particular,
   \[
-    p_{\Pastro_\M E_{A, A'}}(\repfour{\id_A}{\id_A}{\id_{A'}}{\id_{A'}}) = \repfour{l}{\id_A}{\id_{A'}}{r}
+    \tilde{p}_{\Pastro_\M E_{A, A'}}(\rep{\lambda_A^{-1}}{\lambda_{A'}}) = \rep{l}{r}
   \]
@@
 
-There is yet another isomorphic description of optics, which is an unexplored avenue for generalisation:
+We finish with one final isomorphic description of an optic:
 
 \begin{proposition}
-  $\Optic_\M((S, S'), (A, A'))$ is isomorphic to $\Prof(E_{S, S'}, U \Phi_\M E_{A, A'})$.
-\end{proposition}
-\begin{proof}
-  \begin{align*}
-    &\Prof(E_{S, S'}, U \Phi_\M E_{A, A'}) \\
-    \cong\;&\int_{X,Y \in \C} \Set(E_{S, S'}(X,Y), (U \Phi_\M E_{A, A'})(X,Y)) \\
-    = \;&\int_{X,Y \in \C} \Set(\C(X,S) \times \C(S',Y), (U \Phi_\M E_{A, A'})(X,Y)) \\
-    \cong \;& (U \Phi_\M E_{A, A'})(S,S') \\
-    = \;&\Optic_\M((S, S'), (A, A'))
-  \end{align*}
+  $\Optic_\M((S, S'), (A, A'))$ is isomorphic to $\Tamb_\M(\Pastro_\M E_{S, S'}, \Pastro_\M E_{A, A'})$.
+\end{proposition}
+\begin{proof}
+This follows from the previous two propositions and the Yoneda lemma:
+\begin{align*}
+  &\Optic_\M((S, S'), (A, A')) \\
+  &\cong [\Tamb_\M, \Set]((U-)(A,A'),(U-)(S,S')) \\
+  &\cong [\Tamb_\M, \Set](\Tamb_\M(\Pastro_\M E_{A, A'}, -),\Tamb_\M(\Pastro_\M E_{S, S'}, -)) \\
+    &\cong \Tamb_\M(\Pastro_\M E_{S, S'}, \Pastro_\M E_{A, A'})
+\end{align*}
+Explicitly, an optic $p = \rep{l}{r}$ corresponds to the natural transformation with components:
+\begin{align*}
+t_{X, Y} : \Pastro_\M E_{S, S'}(X, Y) \to \Pastro_\M E_{A, A'}(X, Y) \\
+t_{X, Y}(\rep{f}{g}) = \rep{(Ml)f}{g(Mr)}
+\end{align*}
+where $M$ is the residual for the representative $\rep{f}{g}$.
+This is exactly the formula for optic composition!
 \end{proof}
@@
 
-The exchange profunctor has a canonical comonoid structure, where the comultiplication $\Delta : E_A \to E_A \odot E_A$ and counit $\varepsilon : E_A(X, Y) \to \C(X, Y)$ are given by
-\begin{align*}
-  \Delta((f, g)) &= \repfour{f}{\id_A}{\id_A}{g}  \\
-  \varepsilon((f, g)) &= gf
-\end{align*}
-Because $\Pastro_\M$ is oplax monoidal, the profunctor $U\Pastro_\M E_A$ has an induced comonoid structure, given by
-\begin{align*}
-  \Delta(\rep{l}{r}) &= \repthree{l}{lr}{r} \\
+The exchange profunctor $E_{A, A}$, hereafter abbreviated to $E_A$, has a comonoid structure, where the comultiplication $\Delta : E_A \to E_A \odot E_A$ and counit $\varepsilon : E_A \to \C$ are given by
+\begin{align*}
+  \Delta_{X, Y} : (E_A)(X, Y) &\to (E_A \odot E_A)(X, Y) \\
+  \Delta_{X, Y}(\rep{f}{g}) &= \repthree{f}{\id_A}{g}  \\
+  \varepsilon_{X, Y} : (E_A)(X, Y) &\to \C(X, Y) \\
+  \varepsilon_{X, Y}(\rep{f}{g}) &= gf
+\end{align*}
+respectively. Here we have identified $E_A \odot E_A$ with the profunctor $\C(-, A) \times \C(A, A) \times \C(A, =)$, via the isomorphism
+\begin{align*}
+E_A \odot E_A 
+&= \int^{Z \in \C} E_A(-, Z) \times E_A(Z, =) \\
+&= \int^{Z \in \C} \C(-, A) \times \C(A, Z) \times \C(Z, A) \times \C(A, =) \\
+&\cong \C(-, A) \times \C(A, A) \times \C(A, =) 
+\end{align*}
+
+Because $\Pastro_\M$ is oplax monoidal, the Tambara module $\Pastro_\M E_A$ has an induced comonoid structure, in this case given by
+\begin{align*}
+  \Delta_{X, Y} : (\Pastro_\M E_A)(X, Y) &\to (\Pastro_\M E_A \odot \Pastro_\M E_A)(X, Y) \\
+  \Delta(\rep{l}{r}) &= \repthree{l}{\id_{MA}}{r} \\
+  \varepsilon_{X, Y} : (\Pastro_\M E_A)(X, Y) &\to \C(X, Y) \\
   \varepsilon(\rep{l}{r}) &= rl
@@
 
-Comparing these definitions with the definition of a lawful optic, we have immediately:
-
-\begin{proposition}
-  An optic $p : S \hto A$ is lawful iff the corresponding natural transformation $E_S \rightarrow U \Phi_\M E_A$ is a comonoid morphism. \qed
-\end{proposition}
+The connection with lawfulness is hopefully now evident!
+
+\begin{proposition}\label{prop:lawful-if-homomorphism}
+  An optic $p : S \hto A$ is lawful iff the corresponding natural transformation $\Pastro_\M E_S \rightarrow \Pastro_\M E_A$ is a comonoid homomorphism.
+\end{proposition}
+\begin{proof}
+For $t : \Pastro_\M E_S \rightarrow \Pastro_\M E_A$ to be a comonoid homomorphism means that the following diagrams commute for every $X, Y \in \C$:
+  \[
+    \begin{tikzcd}
+    (\Pastro_\M E_S)(X, Y) \ar[r, "t_{X, Y}"] \ar[d, "\varepsilon_{X,Y}" swap] & (\Pastro_\M E_A)(X, Y) \ar[d, "\varepsilon_{X,Y}"] \\
+    \C(X, Y) \ar[r, equals] & \C(X, Y)
+    \end{tikzcd}
+    \quad
+    \begin{tikzcd}
+      (\Pastro_\M E_S)(X, Y) \ar[r, "t_{X, Y}"] \ar[d, "\Delta_{X, Y}" swap] & (\Pastro_\M E_A)(X, Y) \ar[d, "\Delta_{X, Y}"] \\
+      (\Pastro_\M E_S \odot \Pastro_\M E_S)(X, Y) \ar[r, "(t \odot t)_{X, Y}" swap] & (\Pastro_\M E_A \odot \Pastro_\M E_A)(X, Y)
+    \end{tikzcd}
+  \]
+  Suppose $t$ corresponds to an optic with representative $\rep{l}{r}$ with residual $M$ and we have an element $\rep{f}{g} : (\Pastro_\M E_S)(X, Y)$ with residual $N$. The left diagram requires that 
+  \begin{align*}
+  g(Nr)(Nl)f = gf,
+  \end{align*}
+  as an element of $\C(X, Y)$. This is certainly true as $rl = \id_S$. The right diagram claims that 
+  \begin{align*}
+  \repthree{(Nl)f}{\id_{NMA}}{g(N r)} = \repthree{(Nl)f}{(N r)(Nl)}{g(N r)}
+  \end{align*}
+  But this holds by exactly the same argument as used in Proposition~\ref{prop:lawful-category} to show that the composite of lawful optics is lawful: by transplanting the relations showing the second optic law for $\rep{l}{r}$
+
+  For the backward direction, consider the above diagrams specialised to $X = Y = S$.
+Tracing the element $\rep{\lambda_S^{-1}}{\lambda_S} \in (\Pastro_\M E_S)(S, S)$ around the commutative diagrams yields precisely the first and second optic laws respectively.
+\end{proof}
 
@@
 \begin{lemma}
-  For an object $X$ in a monoidal category $(\C, \otimes, I)$, a comonoid structure $(X,\Delta,\varepsilon)$ is equivalent to a lax monoidal structure on $\C(X, -)$.
-Further, comonoid morphisms $(X_1,\Delta_1,\varepsilon_1) \to (X_2,\Delta_2,\varepsilon_2)$ are equivalent to monoidal natural transformations $\C(X, -) \Rightarrow \C(Y, -)$.
+  For an object $X$ in a monoidal category $(\C, \otimes, I)$, a comonoid structure $(X,\Delta,\varepsilon)$ is equivalent to a lax monoidal structure on the functor $\C(X, -) : \C \to \Set$, considering $\Set$ as a monoidal category with respect to $\times$.
+
+  Further, a morphism $(X_1,\Delta_1,\varepsilon_1) \to (X_2,\Delta_2,\varepsilon_2)$ is a comonoid homomorphism iff the induced natural transformation $\C(X_2, -) \Rightarrow \C(X_1, -)$ is monoidal.
 \end{lemma}
@@
   \end{align*}
-  by $\phi = \varepsilon$ and $\phi_{A, B}(f, g) = (f \otimes g) \Delta$.
-
-  From such a lax monoidal structure, we recover the comonoid maps by $\varepsilon = \phi$ and $\Delta = \phi_{X, X}(\id_X, \id_X)$.
-
-  \todo{check equations, and the rest}
+  by $\phi = \varepsilon$ and $\phi_{A, B}(f, g) = (f \otimes g) \Delta$. The coherences follow straightforwardly using the comonoid axioms and functoriality of $\otimes$.
+
+  In the other direction,  we recover the comonoid maps by $\varepsilon = \phi$ and $\Delta = \phi_{X, X}(\id_X, \id_X)$.
 \end{proof}
@@
 \begin{proof}
-  $p : S \hto A$ is lawful iff $E_S \rightarrow U \Phi_\M E_A$ is a comonoid morphism, iff $\Phi_\M E_S \rightarrow \Phi_\M E_A$ is a comonoid morphism by adjointness. Now apply the previous lemma.
-\end{proof}
-
-  For Haskell's profunctor lenses, these laws take the form:
+$p : S \hto A$ is lawful iff the corresponding $\Pastro_\M E_S \to \Pastro_\M E_A$ is a comonoid homomorphism, iff $\tilde{p} : (U-)(A,A) \Rightarrow (U-)(S,S)$ is a comonoid homomorphism.
+\end{proof}
+
+\subsection{Implementation}
+We review quickly how the profunctor encoding is translated into code in the Haskell~\cite{LensLibrary} and Purescript~\cite{PurescriptLibrary} libraries. We define a typeclass for profunctors:
 \begin{minted}{haskell}
-l :: Tambara m p => p a a -> p s s
-
+class Profunctor p where
+  dimap :: (a -> b) -> (c -> d) -> p b c -> p a d
+\end{minted}
+To be considered a valid instance of \mintinline{haskell}{Profunctor}, the function \mintinline{haskell}{dimap} must behave functorially.
+Now, for each optic variant we wish to define, we create a typeclass for the corresponding Tambara module.
+In the case of $\Lens$es, this typeclass is named \mintinline{haskell}{Strong}:
+\begin{minted}{haskell}
+class Profunctor p => Strong p where
+  second :: p a b -> p (c, a) (c, b)
+\end{minted}
+This \mintinline{haskell}{second} function is the equivalent of the structure map $\zeta$ for the Tambara module.
+We require this map to satisfy the Tambara module coherences, but as with any definition in Haskell, these equations must be checked manually.
+
+Now the type of lenses $(S, S') \hto (A, A')$ is the direct translation of the set of natural transformations $(U-)(A,A') \Rightarrow (U-)(S,S')$:
+\begin{minted}{haskell}
+type Lens s s' a a' = forall p. Strong p => p a a' -> p s s'
+\end{minted}
+where we use parametricity in \mintinline{haskell}{p} as a proxy for naturality. A profunctor lens 
+\begin{minted}{haskell}
+l : forall p. Strong p => p a a -> p s s}
+\end{minted}
+is lawful if it is monoidal as a natural transformation. In code this is:
+\begin{minted}{haskell}
 l id == id
@@
 
-% \begin{proposition}
-%   If $p : S \hto A$ is a lawful optic then the associated natural transformation $\tilde{p} : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal.
-% \end{proposition}
-% \begin{proof}
-%   Let $\langle l, r \rangle$ be a representative for $p$ in $\Optic_\M(S,A)$ via the isomorphism of Proposition \ref{prop:profunctor-optics-are-optics}, so that
-%   \begin{align*}
-%     \tilde{p}_P = (UP)(l,r) \alpha_{A,A,M}
-%   \end{align*}
-%   on each Tambara module $P$.
-%
-%   To show $\tilde{p}$ is monoidal, we must show that both
-%   \[
-%     \begin{tikzcd}
-%       UP(A,A) \times UQ(A,A) \ar[r, "\tilde{p}_P \times \tilde{p}_Q"] \ar[d, swap] & UP(S, S) \times UQ(S, S)  \ar[d] \\
-%       U(P \odot Q)(A,A)  \ar[r, "\tilde{p}_{P \odot Q}", swap] & U(P \odot Q)(S,S)
-%     \end{tikzcd}
-%   \]
-%   and
-%   \[
-%     \begin{tikzcd}
-%       1 \ar[d] \ar[dr] & \\
-%       UI(A,A)  \ar[r, "\tilde{p}_I", swap] & UI(S,S)
-%     \end{tikzcd}
-%   \]
-%   commute. For the first we have
-%   \begin{align*}
-%     \langle (\tilde{p}_P \times \tilde{p}_Q)(x, y) \rangle &= \langle (UP)(l,r) \alpha_{A,A,M} x,  (UQ)(l,r) \beta_{A,A,M} y\rangle \\
-%     &= \langle (UP)(l,lr) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(by the coend relations)} \\
-%     &= \langle (UP)(l,\phi A) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $lr = \phi A$)} \\
-%     &= \langle (UP)((\phi A)l,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(by the coend relations again)} \\
-%     &= \langle (UP)(lrl,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $lr = \phi A$ again)} \\
-%     &= \langle (UP)(l,\id_{MA}) \alpha_{A,A,M} x, (UQ)(\id_{MA},r) \beta_{A,A,M} y\rangle && \text{(as $rl = \id_S$)} \\
-%     &= (U(P \odot Q))(l,r) \langle \alpha_{A,A,M} x, \beta_{A,A,M} y \rangle && \text{(by definition of $P \odot Q$)} \\
-%     &= (U(P \odot Q))(l,r) (\alpha_{A,A,M} \odot \beta_{A,A,M}) \langle x, y \rangle && \text{(by definition of $\alpha \odot \beta$)} \\
-%     &= \tilde{p}_{P \odot Q} \langle x, y \rangle
-%   \end{align*}
-%   And for the second:
-%   \begin{align*}
-%     \tilde{p}_I(\id_A) = (UI)(l,r) (M \id_A) = r \id_{MA} l = rl = \id_S
-%   \end{align*}
-%   as required.
-% \end{proof}
-%
-%% \begin{proposition}
-%%   Let $\C = \Set$ and suppose $p : S \hto A$ is a lens such that the associated natural transformation $p : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal. Then $p$ is lawful.
-%% \end{proposition}
-%% \begin{proof}
-%%   \todo{Show that it satisfies the getput, putget and putput laws. This strategy works only with $\times$ and in $\Set$.}
-%% \end{proof}
-%
-% \todo{Here are some thoughts:}
-% The converse is more difficult, and unfortunately requires another fiddly proof by induction on the coend relation.
-The idea is that any profunctor optic is characterised by its component at $\Pastro_\M E_A$, so the result should follow from the commutativity of the square for lax monoidality when $P = Q = \Pastro_\M E_A$.
-%
-% For the remainder of the section, fix a lax monoidal natural transformation $t : (U-)(A,A) \to (U-)(S,S)$ and suppose $\hat{t} = \langle l, r \rangle$ for $l : S \to MA$ and $r : MA \to S$.
-Commutativity of the triangle implies immediately that $rl = \id_S$.
-%
-% Unwinding definitions, commutativity of the square states that
-% \begin{align*}
-%   \langle l, lr, r \rangle = \langle l, \id_{MA}, r \rangle
-% \end{align*}
-% as elements of
-% \begin{align*}
-%   \int^{M,N\in \M} \C(S, MA) \times \C(MA, NA) \times \C(NA, S)
-% \end{align*}
-% Our goal is to show that this implies $\langle lr \rangle = \langle \phi A \rangle$ for some $\phi : M \to M$ in $\M$.
-%
-% \todo{describe the coend relation on this set}
-%
-% \newcommand{\rightrightsquigarrow}{\mathrel{\substack{\textstyle\rightsquigarrow\\[-0.6ex]
-% \textstyle\rightsquigarrow}}}
-% \newcommand{\leftleftsquigarrow}{\mathrel{\substack{\textstyle\leftsquigarrow\\[-0.6ex]
-% \textstyle\leftsquigarrow}}}
-%
-% \begin{align*}
-%   &\int^{N,M} \C(S, M \times A) \times \C(M \times A, N \times A) \times \C(N \times A, S) \\
-%   &= \int^{N,M} \C(S, M) \times \C(S, A) \times \C(M \times A, N \times A) \times \C(N \times A, S) \\
-%   &= \int^{N} \C(S, A) \times \C(S \times A, N \times A) \times \C(N \times A, S) \\
-%   &= \int^{N} \C(S, A) \times \C(S \times A, N) \times \C(S \times A, A) \times \C(N \times A, S) \\
-%   &= \C(S, A) \times \C(S \times A, A) \times \C(S \times A \times A, S) \\
-% \end{align*}
-% Here $\langle l, c, r \rangle$ is sent to $(l \pi_2, (l \pi_1, \id_A) c \pi_2, ((l \pi_1, \id_A) c, \id_A) r)$
-%
-% \todo{Do this for the linear lens too}
-% \begin{theorem}
-%   If $t : (U-)(A,A) \to (U-)(S,S)$ is lax monoidal, then $\hat{t} : S \hto A$ is a lawful optic.
-% \end{theorem}
-% \begin{proof}
-%
-% \end{proof}
-
-\subsection{Mixed Optics}
-\todo{todo?}
-There is a notion of Tambara module structure for profunctors between two different categories.
-This allows us to re-derive the profunctor encoding for degenerate optics.
-For example, in the case of \mintinline{haskell}{Getter}s, a profunctor $P : \C^\op \times \C_\mathsf{codisc}$ essentially ignores its covariant argument.
-This is captured exactly by the `\mintinline{haskell}{RightPhantom}' typeclass or its equivalent in profunctor optic libraries.
-
-\subsection{The van Laarhoven Encoding}
+%The profunctor encoding has a number of benefits.
+The primary benefit is that the typeclass system allows optics to automatically degrade from one variant to another as needed.
+For example, if we wish to also encode $\Traversal$s, we would define the corresponding class of Tambara modules
+%\begin{minted}{haskell}
+%class Strong p => Wandering p where
+%  wander :: Traversable f => p a b -> p (f a) (f b)
+%\end{minted}
+%Note that \mintinline{haskell}{Strong} is a superclass. An instance of \mintinline{haskell}{Wandering} is required to behave the same way 
+%So given a 
+%
+%
+%Another benefit is that optics compose via ordinary function composition
+
+\subsection{The van Laarhoven Encoding}\label{sec:van-laarhoven}
 
 Some optic variants can be encoded in a profunctor-like style without requiring the full complexity of profunctors.
-Chronologically this development came before profunctor optics, and was invented by Twan van Laarhoven~\cite{VanLaarhovenPost}.
+Chronologically this development came before profunctor optics, and was first introduced by Twan van Laarhoven~\cite{VanLaarhovenPost}.
 
@@
 \end{minted}
-What makes these particular optic variants work is that the Tambara module that characterises them, $\Pastro_\M E_A$, can be written in the form \mintinline{haskell}{a -> f a} with \mintinline{haskell}{f} an instance of the corresponding typeclass.
-Specifically, these are the optics that admit a coalgebraic description; see Section~\ref{sec:coalgebraic}.
-
-Therefore, no expressive power is lost by restricting an optic to operate only on functions of shape \mintinline{haskell}{a -> f a}, as the entire concrete description of the optic can be extracted from its value on that Tambara module.
+What allows such a description to work for these optic variants is that the Tambara module that characterises them, $\Pastro_\M E_A$, can be written in the form \mintinline{haskell}{a -> f a} with \mintinline{haskell}{f} an instance of the corresponding typeclass.
+Specifically, these are the optics that admit a coalgebraic description; the ones for which the evaluation-at-$A$ functor has a right adjoint.
+
+No expressive power is lost by restricting an optic to operate only on functions of shape \mintinline{haskell}{a -> f a}, as the entire concrete description of the optic can be extracted from its value on that particular Tambara module.
 The same is not true for other optic variants, and indeed in the Haskell \lenslib{} library, \mintinline{haskell}{Prism}s and \mintinline{haskell}{Review}s use the profunctor encoding.
 
-A consequence is that the laws typically given for $\Traversal$s actually only need to be checked for the applicative functor we called $UR^*$.
-In Haskell this is implemented as \mintinline{haskell}{FunList}~\cite{FunListPost} or \mintinline{haskell}{Bazaar}~\cite{LensLibrary}.
+A consequence is that the laws typically given for $\Traversal$s actually only need to be checked for the applicative functor we earlier called $UR^*$.
+In Haskell this functor is implemented as \mintinline{haskell}{FunList}~\cite{FunListPost} or \mintinline{haskell}{Bazaar}~\cite{LensLibrary}.
 
@@
 
-There are many avenues for exploration! Here we make some speculations.
+There are many avenues for future exploration!
+
+\subsection{Mixed Optics}
+
+One can define generalise the definition of $\Optic$ so that the two halves lie in different categories.
+Suppose $\C_L$ and $\C_R$ are categories that are acted on by a common monoidal category $\M$.
+Write these actions as $\actL : \M \to [\C_L, \C_L]$ and $\actR : \M \to [\C_R, \C_R]$ respectively.
+
+\begin{definition}
+  Given two objects of $\C_L \times \C_R^\op$, say $(S, S')$ and $(A, A')$, a \emph{mixed optic} $p : (S, S') \hto (A, A')$ for $\actL$ and $\actR$ is an element of the set
+  \begin{align*}
+    \Optic_{\actL, \actR}((S, S'), (A, A')) := \int^{M \in \M} \C_L(S, M \actL A) \times \C_R(M \actR A', S')
+  \end{align*}
+\end{definition}
+One can show that $\Optic_{\actL, \actR}$ forms a category. Less clear is what notion of lawfulness is appropriate in this setting.
+
+Examples of mixed optics include the \emph{degenerate optics} of the \lenslib{} library: \mintinline{haskell}{Getter}s \mintinline{haskell}{Review}s and \mintinline{haskell}{Fold}s.
+The mixed optic formalism also appears able to capture \emph{indexed optics} such as \mintinline{haskell}{IndexedLens}es and \mintinline{haskell}{IndexedTraversal}s~\cite{ProfunctorOpticsPost}.
+The latter, for example, allow access to the index of the elements of a list as it is being traversed.
 
@@
 To overcome this, we work in $\Cat$, so that the objects under consideration have internal morphisms that we think of as updates.
-We modify $\fput$ so that instead of accepting an entire $A$ to overwrite the original in $S$ with, it requires a morphism in $A$ of the form $\fget(s) \to a'$.
+We modify $\fput$ so that instead of accepting an element of $A$ to overwrite the original in $S$ with, it requires a morphism in $A$ of the form $\fget(s) \to a'$.
 In this way we are restricted in what updates we may perform.
@@
 
-\todo{I don't know if this is known:}
+%\todo{I don't know if this is known:}
 \begin{theorem}
@@
 
-It is not clear whether there is an action on $\Cat$ that generates this description as its concrete optics. The location for an $A'$ to appear is missing! We remain optimistic:
+It is not clear whether there is an action on $\Cat$ that generates this description as its concrete optics. There doesn't seem to be a natural place for an $A'$ to appear! We remain optimistic:
 
@@
 
-\section{Conclusion}
-
-\todo{Figure out the right section numbering style}
-
-\todo{Maybe some of the long equational manipulations could be done by commutative diagram, using a pair of dashed lines to signal the start and end value?}
-
-\todo{Somewhere spell out the connection between $\Pastro_\M E_A$ and $\Optic(-, A)$.}
-
-\todo{Move some proofs to an appendix?}
-
-\todo{Find an example where the lens laws are definitely not equivalent}
+%\section{Conclusion}
+%
+%\todo{Maybe some of the long equational manipulations could be done by commutative diagram, using a pair of dashed lines to signal the start and end value?}
+%
+%\todo{Move some proofs to an appendix?}
+%
+%\todo{Find an example where the lens laws are definitely not equivalent}
 

### 2018-08-18 mixed.tex
Add mixed.tex

\documentclass[11pt,letterpaper]{article}
\usepackage{microtype}
\usepackage{authblk}
% \usepackage[utf8]{inputenc}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\let\amssquare\square
\usepackage{mathtools}
% \usepackage{stmaryrd}
% \usepackage{tensor}
\usepackage[mathscr]{eucal}
\usepackage{url}
% \usepackage{marvosym}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
%\usepackage{geometry}
\usepackage{minted}
\usepackage{cite}
\usepackage{multicol}
\usepackage{tocloft}
\usepackage{enumerate}

\usepackage{tikz-cd}
\usetikzlibrary{positioning}
\usetikzlibrary{fit}
\usetikzlibrary{cd}
\usetikzlibrary{arrows}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.markings}
\tikzset{ed/.style={auto,inner sep=2pt,font=\scriptsize}} %edges
\tikzset{>=stealth'}
\tikzset{vert/.style={draw,circle, minimum size=6mm, inner sep=0pt, fill=white}}
\tikzset{vertbig/.style={draw,circle, minimum size=8mm, inner sep=0pt, fill=white}}
\tikzset{->-/.style={decoration={
      markings,
      mark=at position #1 with {\arrow{>}}},postaction={decorate}}}

\usepackage[hidelinks]{hyperref} % Should be imported LAST

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[subsection]
% \newtheorem{axiom}[theorem]{Axiom}
\newtheorem*{theoremstar}{Theorem}
% \newtheorem{fact}[theorem]{Fact}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
% \newtheorem{convention}[theorem]{Convention}
% \newtheorem{construction}[theorem]{Construction}
\newtheorem{example}[theorem]{Example}
% \newtheorem{examples}[theorem]{Examples}
% \newtheorem{notation}[theorem]{Notation}
\newtheorem{remark}[theorem]{Remark}
% \newtheorem{idea}[theorem]{Idea}
% \newtheorem{question}[theorem]{Question}

\newcommand{\C}{\mathscr{C}}
\newcommand{\homC}{\underline{\C}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\E}{\mathscr{E}}
\newcommand{\M}{\mathscr{M}}
\newcommand{\N}{\mathscr{N}}
\newcommand{\T}{\mathscr{T}}
\renewcommand{\S}{\mathscr{S}}

\newcommand{\bN}{\mathbb{N}}
\newcommand{\bZ}{\mathbb{Z}}

\newcommand{\lenslib}{\texttt{lens}}

\newcommand{\Pastro}{\Phi}
% \newcommand{\Pastro}{\mathrm{Pastro}}
\newcommand{\Double}{\mathcal{D}}

% Categories
\newcommand{\Set}{\mathbf{Set}}
\newcommand{\Cat}{\mathbf{Cat}}
%\newcommand{\Hask}{\mathbf{Hask}}
\newcommand{\Prof}{\mathbf{Prof}}
\newcommand{\Core}{\mathbf{Core}}
\newcommand{\MonCat}{\mathbf{MonCat}}
\newcommand{\LaxMonCat}{\mathbf{LaxMonCat}}
\newcommand{\SymmMonCat}{\mathbf{SymmMonCat}}
\newcommand{\StrictSymmMonCat}{\mathbf{StrictSymmMonCat}}

\newcommand{\Tele}{\mathbf{Tele}}
\newcommand{\StrictTele}{\mathbf{StrictTele}}
\newcommand{\Tamb}{\mathbf{Tamb}}

\newcommand{\Endo}{\mathbf{Endo}}
\newcommand{\Strong}{\mathbf{Strong}}
\newcommand{\Point}{\mathbf{Point}}
\newcommand{\CoPoint}{\mathbf{CoPoint}}
\newcommand{\App}{\mathbf{App}}
\newcommand{\Traversable}{\mathbf{Traversable}}
\newcommand{\IdxTraversable}{\mathbf{IdxTraversable}}

\newcommand{\Act}{\mathbf{Act}}
\newcommand{\Optic}{\mathbf{Optic}}
\newcommand{\Twoptic}{\mathbf{Optic}^2}
\newcommand{\Lawful}{\mathbf{Lawful}}
%\newcommand{\SemiOptic}{\mathbf{SemiOptic}}
\newcommand{\Lens}{\mathbf{Lens}}
\newcommand{\Prism}{\mathbf{Prism}}
\newcommand{\Setter}{\mathbf{Setter}}
\newcommand{\Traversal}{\mathbf{Traversal}}
\newcommand{\Getter}{\mathbf{Getter}}
\newcommand{\Review}{\mathbf{Review}}
\newcommand{\Fold}{\mathbf{Fold}}
\newcommand{\IdxLens}{\mathbf{IdxLens}}
\newcommand{\IdxTraversal}{\mathbf{IdxTraversal}}

\newcommand{\switched}{\mathbin{\tilde{\otimes}}}

\newcommand{\conc}{\mathbb{C}}
\newcommand{\conctwice}{\mathbb{C}^2}

\newcommand{\id}{\mathrm{id}}
\newcommand{\op}{\mathrm{op}}
\newcommand{\const}{\mathrm{const}}
\DeclareMathOperator{\ob}{ob}
\DeclareMathOperator{\copr}{copr}
\newcommand{\inl}{\mathrm{inl}}
\newcommand{\inr}{\mathrm{inr}}
\DeclareMathOperator{\im}{im}
\newcommand{\act}{\cdot}
\newcommand{\codisc}{\mathsf{codisc}}
\DeclareMathOperator*{\colim}{\mathrm{colim}}
\newcommand{\teletimes}{\mathbin{\boxtimes}}
\newcommand{\defeq}{\mathrel{\vcentcolon=}}

\newcommand*\circled[1]{\tikz[baseline={([yshift=-0.65ex]current bounding box.center)}]{
   \node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
\newcommand{\actL}{{\circled{\tiny$\mathsf{L}$}}}
\newcommand{\actR}{{\circled{\tiny$\mathsf{R}$}}}

\newcommand{\rep}[2]{{\ensuremath \left\langle #1 \mid #2 \right\rangle}}
\newcommand{\repthree}[3]{{\ensuremath \langle #1 \mid #2 \mid #3 \rangle}}
\newcommand{\repfour}[4]{{\ensuremath \langle #1 \mid #2 \mid #3 \mid #4 \rangle}}

\newcommand{\fget}{\textsc{Get}}
\newcommand{\fput}{\textsc{Put}}
\newcommand{\fmodify}{\textsc{Modify}}
\newcommand{\freview}{\textsc{Review}}
\newcommand{\fcreate}{\textsc{Create}}
\newcommand{\fmatching}{\textsc{Matching}}
\newcommand{\funzip}{\textsc{Unzip}}
\newcommand{\fover}{\textsc{Over}}
\newcommand{\findex}{\textsc{Index}}

\newcommand{\mget}{\textsc{MGet}}
\newcommand{\mput}{\textsc{MPut}}
\newcommand{\munzip}{\textsc{Munzip}}

\newcommand{\inside}{\mathsf{inside}}
\newcommand{\outside}{\mathsf{outside}}
\newcommand{\once}{\mathsf{once}}
\newcommand{\twice}{\mathsf{twice}}

% Special arrows
%\newcommand{\isoto}{\xrightarrow{\cong}}
\newcommand{\hto}{\ensuremath{\,\mathaccent\shortmid\rightarrow\,}}

\makeatletter
\providecommand{\leftsquigarrow}{%
  \mathrel{\mathpalette\reflect@squig\relax}%
}
\newcommand{\reflect@squig}[2]{%
  \reflectbox{$\m@th#1\rightsquigarrow$}%
}
\makeatother

% Draft helpers
\newcommand{\todo}[1]{\textcolor{red}{\small #1}}

\title{Mixed Optics}
\author{Mitchell Riley}
\affil{Wesleyan University \\ \texttt{mvriley@wesleyan.edu}}
\begin{document}
\maketitle

\section{Mixed Optics}\label{sec:mixed-optics}

We can generalise the definition of $\Optic$ so that the two halves lie in different categories, allowing us to capture a few more optic variants found in the wild. Suppose $\C_L$ and $\C_R$ are categories that are acted on by a common monoidal category $\M$. Write these actions as $\actL : \M \to [\C_L, \C_L]$ and $\actR : \M \to [\C_R, \C_R]$ respectively.

\begin{definition}
  Given two objects of $\C_L \times \C_R^\op$, say $(S, S')$ and $(A, A')$, an \emph{optic} $p : (S, S') \hto (A, A')$ is an element of the set
  \begin{align*}
    \Optic_{\actL, \actR}((S, S'), (A, A')) := \int^{M \in \M} \C_L(S, M \actL A) \times \C_R(M \actR A', S')
  \end{align*}
\end{definition}

Several results from Section~\ref{sec:optics} have analogues in this setting.
\begin{proposition}\label{prop:mixed-optic-is-cat}
  $\Optic_{\actL, \actR}$ forms a category. \qed
\end{proposition}
\begin{proposition}
  There is a functor $\iota : \C_L \times \C_R^\op \to \Optic_{\actL, \actR}$, which on objects is given by $\iota(S, S') = (S, S')$ and on a morphism $(f, g) : (S, S') \to (A, A')$ by \[\iota(f, g) = \rep{{(\lambda^{\C_L}_A)}^{-1} f}{g \lambda^{\C_R}_{A'}},\] where $\lambda^{\C_L}_A : A \to IA$ in $\C_L$ and $\lambda^{\C_R}_{A'} : A' \to IA'$ in $\C_R$. \qed
\end{proposition}
\begin{proposition}\label{prop:mixed-change-of-action}
  Given two morphisms of actions $F_L : (\M, \C_L) \to (\N, \D_L)$ and $F_R : (\M, \C_R) \to (\N, \D_R)$, there is an induced functor $\Optic(F_L, F_R) : \Optic_{\actL_1, \actR_1} \to \Optic_{\actL_2, \actR_2}$. \qed
\end{proposition}

The notion of lawfulness used earlier breaks down in this setting, as the definition of $\Twoptic(S, A)$ only makes sense when $\C_L = \C_R$. The following definition gives a reasonable approximation.

\begin{definition}
If $F_L : (\M, \C_L) \to (\N, \D)$ and $F_R : (\M, \C_R) \to (\N, \D)$ are morphisms of actions, a mixed optic $p : (S, S) \hto (A, A)$ in $\Optic_{\actL, \actR}$ is \emph{lawful relative to $(F_L, F_R)$} if its image under $\Optic(F_L, F_R)$ in $\Optic_\N$ is lawful.
\end{definition}

\subsection{Degenerate Optics}

The \mintinline{haskell}{Getter}s and \mintinline{haskell}{Review}s of the Haskell lens library corresponds simply to a morphisms $S \to A$ and $A' \to S'$ respectively. These are in fact examples of mixed optics.

Recall that for any category $\C$, there is a category $\C_\codisc$ with the same objects, but where every homset is the singleton set. For any action of $\M$ on $\C$ there is a corresponding action of $\M$ on $\C_\codisc$ that has the same action on objects. There is a morphism of actions $i : (\M, \C) \to (\M, \C_\codisc)$.

For a category with finite products $\C$, define $\Getter$ to be the category of mixed optics where $\C$ acts on $\C$ via $\times$ on the left, and on $\C_\codisc$ also by $\times$. This category is indeed equivalent to $\C$:
\begin{align*}
\Getter((S, S'), (A, A')) 
&\defeq \int^{M \in \M} \C(S, M \times A) \times \C_\codisc(M \times A', S')\\
&\cong \int^{M \in \M} \C(S, M \times A) \\
&\cong \C(S, 1 \times A) \\
&\cong \C(S, A)
\end{align*}
The only sensible notion of lawfulness for $\Getter$s is lawfulness relative to $(i, \id_{\C_\codisc})$, but all optics in $\Optic_{\C_\codisc}$ are trivially lawful.

\begin{remark}
If we we are working linearly, we should not expect $\Optic_{\otimes, \otimes_\codisc}$ to be described so neatly; the above isomorphism relies on the unit of the monoidal structure being terminal.
\end{remark}

One defines $\Review := \Optic_{\sqcup, \sqcup_\codisc}$ analogously. There are induced functors $\Optic(\id_\C, i) : \Lens \to \Getter$ and $\Optic(i, \id_\C) : \Prism \to \Review$.

Finally, we can also encode the category of \mintinline{haskell}{Fold}s. In $\Set$, a fold $S \hto A$ corresponds to a function $S \to \mathrm{List}\,A$. Define 
\begin{align*}
\Fold := \Optic_{\Traversable, \C, \C_\codisc}
\end{align*}
The key is that the $\mathrm{List}$ functor is the terminal $\Traversable$ functor. We therefore have isomorphisms
\begin{align*}
&\int^{M \in \Traversable} \Set(S, MA) \times \Set_\codisc(MA', S') \\
&\cong \int^{M \in \Traversable} \Set(S, MA) \\
&\cong \Set(S, \mathrm{List}\,A)
\end{align*}
There is an induced functor $\Optic(\id_C, i) : \Traversal \to \Fold$.

\subsection{Indexed Lenses}
As well as giving a principled home to degenerate optics, the notion of mixed optics also allows us to describe \emph{indexed optics} categorically. The most interesting example of an indexed optic variant is the \emph{indexed traversal}, which, for example, allows one to know the index of an entry of a list as one is traversing it. As a warmup, however, let us look at \emph{indexed lenses}, which provide access to an index alongside a target, but do not allow updates to the index.

Implementing indexed optics by `passing through' the indices is based on ideas from~\cite{IndexedOpticsPost}.

Suppose $\C$ is cartesian closed. We define two actions of $\C$, the first on $\C$ and the second on $\C \times \C^\op$:
\begin{align*}
M \actL A  &:= M \times A\\
M \actR (A, I) &:= (M \times A, \homC(M, I))
\end{align*}

\begin{definition}
The category of \emph{indexed lenses} $\IdxLens$ in $\C$ is the category of mixed optics $\Optic_{\actL, \actR}$ with the actions as given above.
\end{definition}
Describing concrete indexed lenses is straightforward:
\begin{align*}
  &\Optic_{\actL, \actR}((S, (S', J')), (A, (A', I'))) \\
  &= \int^{M \in \C} \C(S, M \actL A) \times (\C \times \C^\op)(M \actR (A', I'), (S', J')) \\
  &\cong \int^{M \in \C} \C(S, M \times A) \times (\C \times \C^\op)((M \times A', \homC(M, I')), (S', J')) \\
  &\cong \int^{M \in \C} \C(S, M \times A) \times \C(M \times A', S') \times \C^\op(\homC(M, I'), J') \\
  &\cong \int^{M \in \C} \C(S, M \times A) \times \C(M \times A', S') \times \C(J', \homC(M, I')) \\
  &\cong \int^{M \in \C} \C(S, M) \times \C(S, A) \times \C(M \times A', S') \times \C(M \times J', I') \\
  &\cong \C(S, A) \times \C(S \times A', S') \times \C(S \times J', I')
\end{align*}
Let us call this third, new map $\findex : S \times J' \to I'$.

The presence of $J'$ above allows us to chain together indexed lenses and have the the resulting lens remember both indices that appeared. Specifically, in practice our indexed lenses are of shape
\[ 
(S, (S, J)) \hto (A, (A, I \times J))
\]
and natural in $J$, so we can choose a specific instantiation of $J$ as necessary to make the indexed lenses composable. \todo{more detail?}

There is a morphism of actions $U : (\actR, \C \times \C^\op) \to (\times, \C)$ that simply projects to the first component. An indexed lens is lawful relative to $(\id_\C, U)$ if the underlying lens is lawful. This \emph{doesn't}, however, guarantee some properties we might expect of a lawful lens. For example, we might prefer that $\fput$ does not change the index. It is unclear whether such a law fits in this framework.

\begin{remark}
There appears to be some flexibility in what actions we use to define indexed lenses. To have the indices behave covariantly rather than contravariantly, we could have $\C$ act on $\C$ and $\C \times \C$ as follows:
\begin{align*}
M \actL A &:= M \times A \\
M \actR (A, I) &:= (M \times A, M \times I)
\end{align*}
which gives concrete optics in the form
\begin{align*}
\C(S, A) \times \C(S \times A', S') \times \C(S \times I', J').
\end{align*}
We chose the previous, slightly more contorted actions so that indexed lenses are more clearly related to indexed traversals, which we define presently.
%We calculate:
%\begin{align*}
%  &\Optic_{\actL, \actR}((S, (S', J')), (A, (A', I'))) \\
%  &\cong \int^{(M, R) \in \C \times \C} \C(S, (M, R) \actL A) \times (\C \times \C)((M, R) \actR (A', I'), (S', J')) \\
%  &\cong \int^{(M, R) \in \C \times \C} \C(S, M \times R \times A) \times \C(M \times A', S') \times \C(R \times I', J') \\
%  &\cong  \C(S, A) \times \C(S \times A', S') \times \C(S \times I', J')
%\end{align*}
\end{remark}

\subsection{Indexed Traversals}

Returning to indexed traversals, we first need to define indexed traversable functors. Unfortunately this has many moving parts! For simplicity we will restrict our attention to $\C = \Set$, although it may be possible to apply the results more generally.

\begin{proposition}
The assignment $F \act X \mapsto \Set(R, FX)$ extends to a lax action of $\App$ on $\Set$, called the \emph{$R$-indexed action of $\App$ on $\Set$}.
\end{proposition}
\begin{proof}
The structure map for the lax action is given by the composite
\begin{align*}
F \act (G \act X) &= \Set(R, F\Set(R, GX)) \\
&\to \Set(R, \Set(FR, FGX)) \\
&\to \Set(R \times FR, FGX) \\
&\to \Set(R \times R, FGX) \\
&\to \Set(R, FGX) = (FG) \act X
\end{align*}
\todo{more}
\end{proof}

\begin{definition}
A \emph{traversable functor indexed by $R$} is a functor $T : \Set \to \Set$ equipped with a distributive law $\delta_F : T(\Set(R, F-)) \to FT$ for $T$ between the $R$-indexed action of $\App$ on $\Set$ and the (unindexed) action of $\App$ on $\Set$ by evaluation.
\end{definition}

\begin{definition}
The category of \emph{indexed traversable functors} $\IdxTraversable$ has as objects pairs $(T, R)$, where $R \in \Set$ and $T : \Set \to \Set$ is a traversable functor indexed by $R$. A morphism $(T, R) \to (T', R')$ is a natural transformation $\alpha : T \Rightarrow T'$ and morphism (note the direction!) $r : R' \to R$, such that $\alpha$ commutes with the distributive laws on both traversable functors, using $r$ to mediate between the index objects. \todo{draw this out}
\end{definition}

\begin{proposition}
$\IdxTraversable$ acts on $\C \times \C$ by $(T, R) \act (A, I) \mapsto (TA, \homC(R, I))$ and on $\C$ simply by $(T, R) \act A \mapsto TA$.
\end{proposition}

\begin{conjecture}
The category of indexed traversals corresponds to the category of mixed optics with the action of $\IdxTraversable$ on $\C \times \C$ on the left and $\C$ on the right.
\end{conjecture}

\subsection{Implementation}
\todo{todo?}
There is a notion of Tambara module structure for profunctors between two different categories. This allows us to re-derive the profunctor encoding for degenerate optics. For example, in the case of \mintinline{haskell}{Getter}s, a profunctor $P : \C^\op \times \C_\mathsf{codisc}$ essentially ignores its covariant argument. This is captured exactly by the `\mintinline{haskell}{RightPhantom}' typeclass or its equivalent in profunctor optic libraries.

\bibliographystyle{alpha}
\bibliography{optics.bib}
\end{document}

### 2018-08-19 paper.tex
Delete a lot of old commented out stuff

@@
 In the Haskell \lenslib{} library, optics are written in a form known as the \emph{profunctor encoding}, which at first glance is completely different to that given in Section~\ref{sec:optics}.
-As this was being written, Bartosz Milewski~\cite{ProfunctorOpticsPost} independently described the isomorphism between some forms of optic and their profunctor encoding.
+As this was being written, Bartosz Milewski~\cite{ProfunctorOpticsPost} independently described the isomorphism between optics and their profunctor encoding.
 In Section~\ref{sec:profunctor-optics} we review this equivalence and verify that the folklore profunctor optic laws are equivalent to lawfulness as defined here.
@@
   \end{itemize}
-
-%\todo{Past work:
-%  \begin{itemize}
-%  \item The Haskell lens people: edwardk, shachaf, xplat, roconnor...
-%  \item The Doubles paper
-%  \item Bartosz's blog post which was written about the same time I started this. (Only tensor-like optics, no discussion of laws, confusion about enrichment(?))
-%  \item The profunctor optics paper out of Oxford. (No generality, nothing categorical, no discussion of laws)
-%  \item Very old Dialectica category stuff
-%  \end{itemize}
-%}
 
@@
 The only remaining thing to verify is that these structure maps are natural in $\Optic_\C$, but this follows from the previous proposition.
-
-%  Let us check that $\alpha_{(R, R'), (S, S'), (T, T')}$ is natural in $(R, R')$. Suppose $\rep{l}{r} : (Q, Q') \hto (R, R')$ is an optic with residual $M$.
-%  \begin{align*}
-%    &\alpha_{(R, R'), (S, S'), (T, T')} \circ (f \otimes (S, S')) \otimes (T, T') \\
-%    &= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1})  \circ (\rep{l}{r} \otimes (S, S')) \otimes (T, T') \\
-%    &= \rep{\lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T}}{\alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'}}  \circ \rep{(l \otimes S) \otimes T}{(r \otimes S') \otimes T'} \\
-%    &= \rep{(M \otimes \lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T})((l \otimes S) \otimes T)}{((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} )} \\
-%    &=\rep{(M \otimes \alpha_{R,S,T})((l \otimes S) \otimes T)}{((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} )} \\
-%    &= \rep{(l \otimes (S \otimes T))\alpha_{Q,S,T}}{\alpha_{Q',S',T'}^{-1}(r \otimes (S' \otimes T'))} \\
-%    &= \rep{(I \otimes l \otimes (S \otimes T)) \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}}{(I \otimes r \otimes (S' \otimes T')) \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')}} \\
-%    &= \rep{l \otimes (S \otimes T)}{r \otimes (S' \otimes T')} \circ \rep{\lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}}{\alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')} } \\
-%    &= \rep{l}{r} \otimes ((S, S') \otimes (T, T')) \circ \iota(\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}) \\
-%    &= f \otimes ((S, S') \otimes (T, T')) \circ \alpha_{(Q, Q'), (S, S'), (T, T')}
-%  \end{align*}
-%
-%Naturality in the other variables is similar, as is the naturality of the unitors.
-%  \todo{convert this to a string diagram?}
 \end{proof}
@@
 \end{theorem}
-
-% \todo{This doesn't give us the structure of a `framing', we can only lift vertical arrows to horizontal arrows facing one direction.}
-
-% \begin{theorem}
-%   $\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit is $(I, I)$, and the action on morphisms induced by
-%   \begin{align*}
-%     &\C(S, M \otimes A) \times \C(M \otimes A', S') \times \C(T, N \otimes B) \times \C(N \otimes B', T')\\
-%     \to \quad&\C(S \otimes T, M \otimes A \otimes N \otimes B) \times \C(M \otimes A' \otimes N \otimes B', S' \otimes T') && \text{(action of $\otimes$ on morphisms in $\C$)}\\
-%     \to \quad&\C(S \otimes T, M \otimes N \otimes A \otimes B) \times \C(M \otimes N \otimes A' \otimes B', S' \otimes T') && \text{($\otimes$ in $\C$ is symmetric)}\\
-%     \to \quad&\int^{M \in \C} \C(S \otimes T, M \otimes A \otimes B) \times \C(M \otimes A' \otimes B', S' \otimes T') && \text{(inclusion into coend)}
-%   \end{align*}
-% \end{theorem}
-% \begin{proof}
-%   Equationally, suppose we have representatives $(l, r) : (S \to M \otimes A, M \otimes A' \to S')$ and $(l', r') : (T \to N \otimes B, N \otimes B' \to T')$. Then:
-%   \begin{align*}
-%     \langle l, r \rangle \otimes \langle l', r' \rangle &:= \langle (M \otimes s_{A,N} \otimes B)(l \otimes l'), (r \otimes r')(M \otimes s_{A',N} \otimes B') \rangle
-%   \end{align*}
-%   This is functorial, as suggested by the equivalence of the following string diagrams:
-%   \todo{todo}
-%%   For future convenience, note that
-%%   \begin{align*}
-%%     \langle l, r \rangle \otimes (T, T') &= \langle (M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T') \rangle \\
-%%     &= \langle (\lambda^{-1}_M \otimes A \otimes T)(M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T')(\lambda_M \otimes A' \otimes T') \rangle \\
-%%     &= \langle l \otimes T, r \otimes T' \rangle
-%%   \end{align*}
-%%   Now we check functoriality. Suppose we have:
-%%   \begin{align*}
-%%     \langle l_1, r_1 \rangle : (S_1, S_1') &\hto (S_2, S_2') \\
-%%     \langle l_2, r_2 \rangle : (S_2, S_2') &\hto (S_3, S_3') \\
-%%     \langle p_1, q_1 \rangle : (T_1, T_1') &\hto (T_2, T_2') \\
-%%     \langle p_2, q_2 \rangle : (T_2, T_2') &\hto (T_3, T_3')
-%%   \end{align*}
-%%   with residuals $M_1, M_2, N_1, N_2$ respectively. Then: \todo {(This is a mess. String diagram?)}
-%%   \begin{align*}
-%%     &(\langle l_2, r_2 \rangle \otimes \langle p_2, q_2 \rangle) \circ (\langle l_1, r_1 \rangle \otimes \langle p_1, q_1 \rangle) \\
-%%     = \; &\langle (M_2 \otimes s_{S_3,N_2} \otimes T_3)(l_2 \otimes p_2), (r_2 \otimes q_2)(M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-%%     &\circ \langle (M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), (r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2') \rangle \\
-%%     = \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes N_1 \otimes l_2 \otimes p_2)(M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), \\
-%%     &\;(r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2')(M_1 \otimes N_1 \otimes r_2 \otimes q_2)(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-%%     = \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)(M_1 \otimes  l_2 \otimes N_1 \otimes p_2)(l_1 \otimes p_1), \\
-%%     &\;(r_1 \otimes q_1)(M_1 \otimes r_2 \otimes N_1 \otimes q_2)(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-%%     = \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1), \\
-%%     &\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-%%     = \; & \text{\todo{(Add a $s_{M_2, N_1}$ to either side of the coend, then appeal to coherence)}} \\
-%%     = \; &\langle (M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S_3} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1) ,  \\
-%%     &\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S'_3} \otimes T'_3) \rangle \\
-%%     = \; &\langle (M_1 \otimes l_2)l_1, r_1(M_1 \otimes r_2) \rangle \otimes \langle (N_1 \otimes p_2)p_1, q_1(N_1 \otimes q_2) \rangle \\
-%%     = \; &(\langle l_2, r_2 \rangle  \circ \langle l_1, r_1 \rangle) \otimes (\langle p_2, q_2 \rangle \circ \langle p_1, q_1 \rangle)
-%%   \end{align*}
-%
-%   The structure morphisms are all lifted from the structure morphisms in $\C$:
-%   \begin{align*}
-%     \alpha_{(R, R'), (S, S'), (T, T')} &:= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1}) \\
-%     \lambda_{(S, S')} &:= \iota(\lambda_{(S, S')}, \lambda_{(S, S')}^{-1}) \\
-%     \rho_{(S, S')} &:= (\rho_{(S, S')}, \rho_{(S, S')}^{-1}) \\
-%     s_{(S, S'), (T, T')} &:= \iota(s_{S, T}, s_{T', S'})
-%   \end{align*}
-%
-%   Note that because $\iota(S, S') = (S, S')$, required equations for $\iota$ to be a monoidal functor hold by definition (although we don't yet know that $\Optic_\C$ is monoidal).
-The pentagon and triangle axioms then hold in $\Optic_\C$, as they are the image of the same axioms in $\C \times \C^\op$ under $\iota$.
-The only remaining thing to verify is that these structure maps are natural in $\Optic_\C$.
-%
-%   Let us check that $\alpha_{(R, R'), (S, S'), (T, T')}$ is natural in $(R, R')$. Suppose $f : (Q, Q') \hto (R, R')$ has representative $(l, r) : (Q \to M \otimes R, M \otimes R' \to Q')$, then:
-%   \begin{align*}
-%     &\alpha_{(R, R'), (S, S'), (T, T')} \circ (f \otimes (S, S')) \otimes (T, T') \\
-%     &= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1})  \circ (\langle l, r \rangle \otimes (S, S')) \otimes (T, T') \\
-%     &= \langle\lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} \rangle  \circ \left\langle (l \otimes S) \otimes T, (r \otimes S') \otimes T' \right\rangle \\
-%     &=\left\langle (M \otimes \lambda_{R \otimes (S \otimes T)}\alpha_{R,S,T})((l \otimes S) \otimes T), ((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} \lambda^{-1}_{(R' \otimes S') \otimes T'} ) \right\rangle \\
-%     &=\left\langle (M \otimes \alpha_{R,S,T})((l \otimes S) \otimes T), ((r \otimes S') \otimes T') (M \otimes \alpha_{R',S',T'}^{-1} )\right\rangle \\
-%     &=\left\langle (l \otimes (S \otimes T))\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}(r \otimes (S' \otimes T')) \right\rangle \\
-%     &= \langle (I \otimes l \otimes (S \otimes T)) \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}, (I \times r \otimes (S' \otimes T')) \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')}\rangle \\
-%     &= \langle l \otimes (S \otimes T), r \otimes (S' \otimes T')\rangle \circ \left\langle \lambda_{Q \otimes (S \otimes T)}\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1} \lambda^{-1}_{Q' \otimes (S' \otimes T')} \right\rangle \\
-%     &= \langle l, r \rangle \otimes ((S, S') \otimes (T, T')) \circ \iota(\alpha_{Q,S,T}, \alpha_{Q',S',T'}^{-1}) \\
-%     &= f \otimes ((S, S') \otimes (T, T')) \circ \alpha_{(Q, Q'), (S, S'), (T, T')}
-%   \end{align*}
-%   \todo{There is some cheating going on here, composition actually adds an extra $\alpha$, but that wouldn't get in the way.}
-% \end{proof}
 
@@
 
-% \begin{proposition}
-%   Any isomorphism $p : (S, S') \hto (A, A')$ in $\Optic_\C$ is of the form $\iota(f, g)$ for two isomorphisms $S \to A$ and $A' \to S'$ in $\C$.
-% \end{proposition}
-% \begin{proof}
-%   \todo{This might not actually be true..}
-%\end{proof}
-
 This doesn't extend to a strict 2-functor $\SymmMonCat \to \SymmMonCat$, as there is only an action of $\Optic$ on natural \emph{isomorphisms}.
@@
 Note that there is therefore also a canonical isomorphism $\phi : I \cong I^*$
-  \item A symmetric monoidal extranatural family of morphisms $\varepsilon_X : X \otimes X^* \to I$, called \emph{counits}, natural with respect to the morphisms in $\T_d$.
+  \item A symmetric monoidal extranatural family of morphisms $\varepsilon_X : X \otimes X^* \to I$, called \emph{counits}, natural with respect to the dualisable morphisms.
   \end{itemize}
@@
 \]
-where $f : X \to Y$ is in $\T_d$.
+where $f : X \to Y$ is dualisable.
 
@@
 
-% \begin{remark}
-%   Compact closed categories very nearly form examples of teleological categories.
-In a compact closed category, there are canonical isomorphisms $(X \otimes Y)^* \cong Y^* \otimes X^*$.
-In a teleological category, however, duality does not reverse the order of the tensor.
-\todo{If $\C$ is strict, as it is here, does this matter?}
-% \end{remark}
-
 Note that because $\T_d$ is symmetric monoidal and has the same collection of objects as $\T$, the symmetric monoidal structure morphisms of $\T$ must be contained in $\T_d$ and so are dualisable.
@@
 %\end{example}
-
-%There are few surprises in the following definitions.
 
@@
 
-      %       \todo{They stress about the empty set, have I avoided that issue?}
-
 \begin{proposition}
@@
 \end{proof}
-
-      %       \begin{proposition}
-      %       Suppose $\langle l, r \rangle : (S, S') \hto (A, A')$ has residual $M$. Then
-      %       \begin{align*}
-      %       \langle l, r \rangle = (\varepsilon_{(M, I)} \otimes (A, A'))\iota(l, r).
-      %     \end{align*}
-      %       \end{proposition}
-      %       \begin{proof}
-      %       First note that because $\C$ is strict monoidal, the counit $\varepsilon_{(M, I)} : (M \otimes I, M \otimes I) = (M, M) \hto (I, I)$ is equal to the connector $c_M : (M, M) \hto (I, I)$.
-      %
-      %       The claim then holds, as any optic
-      %       \begin{center}
-      %       \input{diagrams/generic-optic-noline.tikz}
-      %       \end{center}
-      %       is equal to the composite
-      %       \begin{center}
-      %       \input{diagrams/optic-decomposed.tikz}
-      %       \end{center}
-      %       where we have drawn the normally invisible strings corresponding to the unit $I$.
-      %       \end{proof}
 
@@
 As further justification for this definition, in Section~\ref{sec:profunctor-optics} we will see an interpretation of (unlawful) optics as maps between certain comonoid objects.
-Lawfulness corresponds exactly to this map being a comonoid homomorphism.
+Lawfulness in our sense corresponds exactly to this map being a comonoid homomorphism.
 
@@
   \end{align*}
-  Call this last set $\conctwice_\times(S, A)$. Written equationally, the isomorphism $\Phi : \Twoptic_\times(S, A) \to \conctwice_\times(S, A)$ is given by:
+%  Call this last set $\conctwice_\times(S, A)$. Written equationally, the isomorphism $\Phi : \Twoptic_\times(S, A) \to \conctwice_\times(S, A)$ is given by:
+  Written equationally, the isomorphism $\Phi : \Twoptic_\times(S, A) \to \C(S, A) \times \C(S \times A, A) \times \C(S \times A \times A, S)$ is given by:
   \begin{align*}
@@
 Suppose $\C$ is cartesian closed and let $\Strong_\C$ be the category of \emph{strong functors} on $\C$.
-%\todo{I define strong functor here because I also want to talk about strong monads later, should this definition wait for that?}
 
@@
 There is an evident category $\Strong(\C)$ of strong endofunctors and strong natural transformations, and a forgetful functor $U : \Strong(\C) \to [\C, \C]$.
-%  \[
-%    \begin{tikzcd}
-%      A \otimes F B \ar[r, "\theta_{A,B}"] \ar[d, "A \otimes \tau_B" left]  & F(A \otimes B) \ar[d, "\tau_{A \otimes B}" right] \\
-%      A \otimes G B \ar[r, "\theta'_{A, B}"]& G(A \otimes B)
-%    \end{tikzcd}
-%  \]
-%
 \end{definition}
@@
 \end{proof}
-
-%\begin{remark}\label{remark:four-parameters}
-%We note here that Haskell lenses
-%\end{remark}
-
-%\todo{What about the pointwise tensor of an entire functor?}
 
@@
 \]
-
-%\item \emph{Adjunction Lenses}: For a category with finite products $\C$ and a monoidal adjunction $F \dashv U$, with $F : \C \to \D$ and $U : \D \to \C$.
-If $U$ is strong monoidal then $\D$ acts on $\C$ by $UD \act A := D \times A$; as an example consider the free-forgetful adjunction between sets and monoids.
-Concrete optics for this action are given by elements of
-%\[ \C(S, A) \times \C(UFS \times A', S') \]
-%\todo{This example is a bit dumb, delete?}
 \end{itemize}
-
-% \subsection{Equivalence of Optics}
-%
-% One issue with the definition of optic given in the last section is that it could be difficult to determine when two optics $\rep{l}{r}, \langle l', r' \rangle : S \hto A$
-% are equal. For some choices of $\M$, however, we can reduce a zigzag of relations to a single one.
-%
-% \todo{This may work in general with some huge number of conditions: something like $-A$ reflects monomorphisms and preserves binary coproducts, all subobjects in $\M$ have complements.}
-%
-% \begin{proposition}
-%   Suppose all epimorphisms split in $\C$, and that $- \times A : \C \to \C$ reflects epis.
-Then two lenses $\langle l, r \rangle$ and $\langle l', r' \rangle :  S \hto A$ with residuals $M$ and $N$ respectively are equal iff there exists an morphism $\phi : M \to N$ such that $(\phi \times A)l = l'$ and $r = r' (\phi \times A)$.
-% \end{proposition}
-% \begin{proof}
-%   The backward direction is clear: the morphism $\phi$ is a witness that $\langle l, r \rangle \rightsquigarrow \langle l', r' \rangle$, so the two optics are equal.
-%
-%%   note that $p$ and $q$ must have identical $\fget$ and $\fput$ functions:
-%%   \begin{align*}
-%%     \fget &= \pi_2 l = \pi_2 l' \\
-%%     \fput &= r (\pi_1 l \times A) = r' (\pi_1 l' \times A)
-%%   \end{align*}
-%   For the forward direction, note that the map $(\pi_1 l \times A)$ is a retraction: it has the section $(r, \pi_2)$:
-%   \begin{align*}
-%     (\pi_1 l \times A)(r, \pi_2) = (\pi_1 l r, \pi_2) = (\pi_1, \pi_2) = \id_{S \times A}
-%   \end{align*}
-%   Now by assumption, $\pi_1 l : S \to M$ is an epi, so has a retraction $f : M \to S$. The claim is that $\phi = \pi_1 l' f$ is the required morphism $M \to N$.
-%
-%   The situation is summarised in the following diagram, which other than the dashed line, we know commutes.
-%   \[
-%     \begin{tikzcd}
-%       M \times A \ar[r, "{f \times A}", dashed, bend left = 50] \ar[d, "r", swap] & S \times A \ar[d, "\fput"] \ar[r, "{\pi_1 l' \times A}"] \ar[l, "{\pi_1 l \times A}", swap] & N \times A \ar[d, "r'"] \\
-%       S \ar[r, equal] \ar[d, "l", swap] & S \ar[d, "{[\id_S, \fget]}"] \ar[r, equal] & S \ar[d, "l'"] \\
-%       M \times A & S \times A \ar[r] \ar[l] & N \times A
-%     \end{tikzcd}
-%   \]
-%   We can now calculate:
-%   \begin{align*}
-%     r = r(\pi_1 l f \times A) = \fput (f \times A) = r' (\pi_1 l' f \times A) = r'(\phi \times A)
-%   \end{align*}
-%   as required. The equation relating $l$ and $l'$ follows immediately as they are the inverses of $r$ and $r'$.
-% \end{proof}
-%
-% The conditions of the above Proposition hold in $\Set$, so long as $A$ is not empty.
-
-% Old attempt:
-% \begin{definition}
-%   A functor $F : \C \to \D$ satisfies the \emph{splitting morphism condition} (SM) if, for every $f : A \to B$ in $\C$ such that $Ff$ is a split monomorphism, there exists a $g : B \to A$ such that $F(gf) = \id_{FA}$.
-%
-%   Similarly, $F$ satisfies the \emph{splitting epimorphism condition} (SE) if for every $f : A \to B$ in $\C$ such that $Ff$ is a split epimorphism, there exists a $g : B \to A$ such that $F(fg) = \id_{FB}$.
-% \end{definition}
-%
-% These definitions are identical to ones given in a (as far as I can tell totally unrelated) paper on triangulated categories \cite{ObjectiveTriangleFunctors}.
-The conditions are not too difficult to satisfy:
-%
-% \begin{proposition}[\todo{cite}]
-%   If $F$ is full then it satisfies (SM) and (SE).
-% \end{proposition}
-% \begin{proof}
-%
-% \end{proof}
-%
-% \begin{proposition}[\todo{cite}]
-%   If $F$ is faithful then it satisfies (SM) and (SE).
-% \end{proposition}
-% \begin{proof}
-%
-% \end{proof}
-%
-% \begin{theorem}
-%   Suppose we have two optics $\langle l, r \rangle$ and $\langle l', r' \rangle \in \Optic_\M(S, A)$ with residuals $M$ and $N$ respectively, and suppose $\M$ has the property that the ``evaluation-at-$A$'' functor $(-A) : \M \to \C$ satisfies (SM) and (SE).
-Then the two optics are equal iff there exists an morphism $\phi : M \to N$ such that $\phi_A l = l'$ and $r = r' \phi_A$.
-% \end{theorem}
-% \begin{proof}
-%   The backward direction is clear: the morphism $\phi$ is a witness that $\langle l, r \rangle \rightsquigarrow \langle l', r' \rangle$, so the two optics are equal.
-%
-%   For the forward direction, as in Proposition \ref{prop:onthenose} we induct on a zigzag \[(l, r) = (l_1, r_1) \leftrightsquigarrow \dots \leftrightsquigarrow (l_n, r_n) = (l', r'),\] where each pair $(l_i, r_i)$ has residual $M_i$.
-As a base case, we can take the identity $\id_M : M \to M = M_1$.
-Now suppose we already have a morphism $\phi : M \to M_{i-1}$ that satisfies $\phi_A l = l_{i-1}$ and $r = r_{i-1} \phi_A$.
-There are two cases to consider:
-%
-%   If $(l_{i-1}, r_{i-1}) \rightsquigarrow (l_i, r_i)$, then by definition we have a $\psi : M_{i-1}\to M_i$ that satisfies the equations $\psi_A l_{i-1} = l_i$ and $r_{i-1} = r_i \psi_A$.
-Therefore the composite $\psi\phi$ satisfies $(\psi\phi)_A l = \psi_A l_{i-1} = l_i$ and $r = r_{i-1} \phi_A = r_i (\psi \phi)_A$, so $\psi\phi : M \to M_i$ is the required morphism.
-%
-%   If instead $(l_{i-1}, r_{i-1}) \leftsquigarrow (l_i, r_i)$, we have a morphism in the opposite direction $\psi : M_i \to M_{i-1}$, with $\psi_A l_i = l_{i-1}$ and $r_i = r_{i-1} \psi_A$, as shown in the following commutative diagram
-%   \[
-%     \begin{tikzcd}
-%       M A \ar[r, "\phi_A"] \ar[d, "r", swap] & M_{i-1} A \ar[d, "r_{i-1}"] & M_i A \ar[l, "\psi_A", swap] \ar[d, "r_i"]\\
-%       S \ar[r, equal] \ar[d, "l", swap] & S \ar[r, equal] \ar[d, "l_{i-1}"] & S \ar[d, "l_i"] \\
-%       M A \ar[r, "\phi_A", swap] & M_{i-1} A & M_i A \ar[l, "\psi_A"]
-%     \end{tikzcd}
-%   \]
-%   To construct a morphism $M \to M_i$ we have to perform a slightly awkward switchback maneuver. First note that $\phi_A$ is a split monomorphism, as $(l r_{i-1}) \phi_A = lr = \id_{MA}$.
-%
-%   By condition (SM), therefore, there is a morphism $\gamma : M_{i-1} \to M$ such that $\gamma_A \phi_A = \id_{MA}$. But now, the composite $\gamma_A \psi_A : M_i \to M$ is a split epimorphism:
-%   \begin{align*}
-%     (\gamma_A \psi_A)(l_i r) = \gamma_A l_{i-1} r = \gamma_A \phi_A l r = \gamma_A \phi_A = \id_{MA}
-%   \end{align*}
-%   and by condition (SE), there is a morphism $\theta : M \to M_i$ with $\gamma_A \psi_A \theta_A = \id_{MA}$.
-It remains to show that $\theta_A l = l_i$ and $r = r_i \theta_A$.
-First some intermediate steps:
-%   \begin{align*}
-%     r \gamma_A = r_{i-1} l_{i-1} r \gamma_A = r_{i-1} \phi_A l r \gamma_A = r_{i-1} \phi_A \gamma_A =
-%   \end{align*}
-%   So finally:
-%   \begin{align*}
-%     r &= r \gamma_A \psi_A \theta_A
-%   \end{align*}
-%   \todo{picture}
-% \end{proof}
 
@@
 \begin{definition}
-  Suppose a category $\C$ is acted on by $(\M, \otimes, I)$ and let $P \in \Prof(\C, \C)$ be a profunctor. A \emph{Tambara module structure for $\M$} on $P$ is a family of maps:
+  Suppose a category $\C$ is acted on by $(\M, \otimes, I)$ and let $P \in \Prof(\C, \C)$ be a profunctor. A \emph{Tambara module structure for $\M$ on $P$} is a family of maps:
   \begin{align*}
@@
 \begin{proof}
-  For a comonoid $(X,\Delta,\varepsilon)$, define a lax monoidal structure
-  \begin{align*}
-    \phi &: 1 \to \C(X, I) \\
-    \phi_{A, B} &: \C(X, A) \times \C(X, B) \to \C(X, A \otimes B)
-  \end{align*}
-  by $\phi = \varepsilon$ and $\phi_{A, B}(f, g) = (f \otimes g) \Delta$. The coherences follow straightforwardly using the comonoid axioms and functoriality of $\otimes$.
-
-  In the other direction,  we recover the comonoid maps by $\varepsilon = \phi$ and $\Delta = \phi_{X, X}(\id_X, \id_X)$.
+This is a follow-your-nose result!
+%  For a comonoid $(X,\Delta,\varepsilon)$, define a lax monoidal structure
+%  \begin{align*}
+%    \phi &: 1 \to \C(X, I) \\
+%    \phi_{A, B} &: \C(X, A) \times \C(X, B) \to \C(X, A \otimes B)
+%  \end{align*}
+%  by $\phi = \varepsilon$ and $\phi_{A, B}(f, g) = (f \otimes g) \Delta$. The coherences follow straightforwardly using the comonoid axioms and functoriality of $\otimes$.
+%
+%  In the other direction,  we recover the comonoid maps by $\varepsilon = \phi$ and $\Delta = \phi_{X, X}(\id_X, \id_X)$.
 \end{proof}
@@
 \begin{proof}
-$p : S \hto A$ is lawful iff the corresponding $\Pastro_\M E_S \to \Pastro_\M E_A$ is a comonoid homomorphism, iff $\tilde{p} : (U-)(A,A) \Rightarrow (U-)(S,S)$ is a comonoid homomorphism.
+\begin{align*}
+& p : S \hto A \text{ is lawful} \\
+\Leftrightarrow\; & \Pastro_\M E_S \to \Pastro_\M E_A \text{ is a comonoid homomorphism} \\
+\Leftrightarrow\; & \Tamb_\M(\Pastro_\M E_A, -) \Rightarrow \Tamb_\M(\Pastro_\M E_S, -) \text{ is a monoidal natural transformation} \\
+\Leftrightarrow\; & (U-)(A, A) \Rightarrow (U-)(S, S) \text{ is a monoidal natural transformation}
+\end{align*}
 \end{proof}

### 2018-09-02 optics.tex
Rename paper.tex to optics.tex

--- 2018-08-19 paper.tex
@@
 %\usepackage{geometry}
-\usepackage{minted}
+\usepackage[frozencache]{minted}
 \usepackage{cite}
@@
 
-\title{Categories of Optics (Draft)}
+\title{Categories of Optics}
 \author{Mitchell Riley}
@@
 These are collectively called \emph{optics} and have been best explored in the widely uesd Haskell \lenslib{} library: see~\cite{LensLibrary}.
-Each optic variant has a concrete description as a certain collection of maps, with attendant laws under which we consider them well-behaved.
+Each optic variant has a concrete description as a certain collection of maps, with attendant laws under which we consider them well-behaved, similar to the pair $(\fget, \fput)$ above and the lens laws.
 We begin in Section~\ref{sec:optics} by defining the \emph{category of optics} in a sufficiently general way to encompass almost all the optic variants in use in the wild, using lenses as a running example.
@@
 In the Haskell \lenslib{} library, optics are written in a form known as the \emph{profunctor encoding}, which at first glance is completely different to that given in Section~\ref{sec:optics}.
-As this was being written, Bartosz Milewski~\cite{ProfunctorOpticsPost} independently described the isomorphism between optics and their profunctor encoding.
-In Section~\ref{sec:profunctor-optics} we review this equivalence and verify that the folklore profunctor optic laws are equivalent to lawfulness as defined here.
+As this was being written, Milewski~\cite{ProfunctorOpticsPost} and Boisseau and Gibbons~\cite{YouNeeda} independently described the isomorphism between optics and their profunctor encoding.
+In Section~\ref{sec:profunctor-optics} we review this isomorphism and verify that the folklore profunctor optic laws are equivalent to lawfulness as defined here.
 
@@
 The $\fput$ function computes the utility of the moves that the players make.
-There is interest in generalising this to a probabilistic setting, but it is not clear what the right replacement for concrete lenses is.
-
-Much of what is known about optics is folklore, and careful verification of some of their categorical properties has been lacking.
+There is interest in generalising this to a probabilistic setting, but it is not yet clear what the right replacement for concrete lenses is.
+
+Much of what is known about optics is folklore, and careful verification of some of their categorical properties has been lacking, especially when working in categories other than $\Set$ (or $\Set$-like categories such as $\mathbf{Hask}$).
 The aim of the present paper is to fill this gap, with the hope that a better understanding of the general structure of these categories will make it easier to generalise to new and exotic settings.
@@
   \begin{itemize}
-  \item An careful account of the folkloric optic construction in an arbitrary symmetric monoidal category $\C$, summarised compactly as giving a functor $\Optic : \SymmMonCat \to \SymmMonCat$ (Section~\ref{sec:optics}),
-  \item A characterisation of the $\Optic$ construction as freely adding counits to a set of `dualisable morphisms' (Section~\ref{sec:teleological-categories}),
-  \item A definition of lawfulness for a general optic category that specialises in the correct way to known cases and allows us to easily derive concrete laws for new kids of optic (Section~\ref{sec:lawful-optics}),
+  \item A careful account of the folklore optic construction in an arbitrary symmetric monoidal category $\C$, which we show extends to a functor $\Optic : \SymmMonCat \to \SymmMonCat$ (Section~\ref{sec:optics}),
+  \item A universal property of the $\Optic$ construction as freely adding counits to a category of `dualisable morphisms' (Section~\ref{sec:teleological-categories}),
+  \item A definition of lawfulness for a general optic category that specialises in the correct way to known cases and allows us to derive concrete laws for new kinds of optic (Section~\ref{sec:lawful-optics}),
   \item Commentary on the optic variants used most frequently in the wild (Section~\ref{sec:examples}),
-  \item A proof that lawfulness as defined here is equivalent to the folklore profunctor lens laws. (Section~\ref{sec:profunctor-optics})
+  \item A proof that lawfulness as defined here is equivalent to the folklore profunctor optic laws (Section~\ref{sec:profunctor-optics}).
   \end{itemize}
@@
 
-%\todo{Is there a relationship between $\Optic_\C/(I, I)$ and $[2, \C]$?}
-
 In particular, for any $S \in \C$, the identity $\id_S$ yields an optic $c_S = \rep{\rho_S^{-1}}{\rho_S} : (S, S) \hto (I, I)$ that we call the \emph{connector}:
@@
 This creates two extra twists that can be cancelled in the center of the diagram.
-
-  %%%% Note: The following is the above argument written equationally:
-  % For future convenience, note that
-  % \begin{align*}
-  %   \langle l, r \rangle \otimes (T, T') &= \langle (M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T') \rangle \\
-  %   &= \langle (\lambda^{-1}_M \otimes A \otimes T)(M \otimes s_{A,I} \otimes T)(l \otimes \lambda_T), (r \otimes \lambda^{-1}_{T'})(M \otimes s_{A',I}\otimes T')(\lambda_M \otimes A' \otimes T') \rangle \\
-  %   &= \langle l \otimes T, r \otimes T' \rangle
-  % \end{align*}
-  % Now we check functoriality. Suppose we have:
-  % \begin{align*}
-  %   \langle l_1, r_1 \rangle : (S_1, S_1') &\hto (S_2, S_2') \\
-  %   \langle l_2, r_2 \rangle : (S_2, S_2') &\hto (S_3, S_3') \\
-  %   \langle p_1, q_1 \rangle : (T_1, T_1') &\hto (T_2, T_2') \\
-  %   \langle p_2, q_2 \rangle : (T_2, T_2') &\hto (T_3, T_3')
-  % \end{align*}
-  % with residuals $M_1, M_2, N_1, N_2$ respectively. Then: \todo {(This is a mess. String diagram?)}
-  % \begin{align*}
-  %   &(\langle l_2, r_2 \rangle \otimes \langle p_2, q_2 \rangle) \circ (\langle l_1, r_1 \rangle \otimes \langle p_1, q_1 \rangle) \\
-  %   = \; &\langle (M_2 \otimes s_{S_3,N_2} \otimes T_3)(l_2 \otimes p_2), (r_2 \otimes q_2)(M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-  %   &\circ \langle (M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), (r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2') \rangle \\
-  %   = \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes N_1 \otimes l_2 \otimes p_2)(M_1 \otimes s_{S_2,N_1} \otimes T_2)(l_1 \otimes p_1), \\
-  %   &\;(r_1 \otimes q_1)(M_1 \otimes s_{S_2',N_1} \otimes T_2')(M_1 \otimes N_1 \otimes r_2 \otimes q_2)(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-  %   = \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)(M_1 \otimes  l_2 \otimes N_1 \otimes p_2)(l_1 \otimes p_1), \\
-  %   &\;(r_1 \otimes q_1)(M_1 \otimes r_2 \otimes N_1 \otimes q_2)(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-  %   = \; & \langle (M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3,N_2} \otimes T_3)(M_1 \otimes s_{(M_2 \otimes S_3),N_1} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1), \\
-  %   &\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes s_{(M_2 \otimes S_3'),N_1} \otimes T_3')(M_1 \otimes N_1 \otimes M_2 \otimes s_{S_3',N_2} \otimes T_3') \rangle \\
-  %   = \; & \text{\todo{(Add a $s_{M_2, N_1}$ to either side of the coend, then appeal to coherence)}} \\
-  %   = \; &\langle (M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S_3} \otimes T_3)((M_1 \otimes l_2)l_1\otimes (N_1 \otimes p_2)p_1) ,  \\
-  %   &\;(r_1(M_1 \otimes r_2) \otimes q_1(N_1 \otimes q_2))(M_1 \otimes M_2 \otimes s_{(N_1 \otimes N_2),S'_3} \otimes T'_3) \rangle \\
-  %   = \; &\langle (M_1 \otimes l_2)l_1, r_1(M_1 \otimes r_2) \rangle \otimes \langle (N_1 \otimes p_2)p_1, q_1(N_1 \otimes q_2) \rangle \\
-  %   = \; &(\langle l_2, r_2 \rangle  \circ \langle l_1, r_1 \rangle) \otimes (\langle p_2, q_2 \rangle \circ \langle p_1, q_1 \rangle)
-  % \end{align*}
 
@@
   \begin{itemize}
-  \item A symmetric monoidal subcategory $\T_d$ of \emph{dualisable morphisms} containing all the objects of $\T$, with an involutive symmetric monoidal functor ${(-)}^* : \T_d \to \T_d^\op$, where---not finding a standard symbol for such a thing---we mean $\T_d^\op$ to be the category with both the direction of the arrows \emph{and} the order of the tensor flipped: ${(A \otimes B)}^* \cong B^* \otimes A^*$.
+  \item A symmetric monoidal subcategory $\T_d$ of \emph{dualisable morphisms} containing all the objects of $\T$, with an involutive symmetric monoidal functor ${(-)}^* : \T_d \to \T_d^\op$, where---not finding a standard symbol for such a thing---we mean $\T_d^\op$ to be the category with both the direction of the arrows \emph{and} the order of the tensor flipped: ${(A \teletimes B)}^* \cong B^* \teletimes A^*$.
 Note that there is therefore also a canonical isomorphism $\phi : I \cong I^*$
-  \item A symmetric monoidal extranatural family of morphisms $\varepsilon_X : X \otimes X^* \to I$, called \emph{counits}, natural with respect to the dualisable morphisms.
+  \item A symmetric monoidal extranatural family of morphisms $\varepsilon_X : X \teletimes X^* \to I$, called \emph{counits}, natural with respect to the dualisable morphisms.
   \end{itemize}
@@
 \begin{example}
-  Any compact closed category is a teleological category, where every morphism is dualisable and the unit morphisms have been forgotten.
-\end{example}
-\begin{example}
-  Any symmetric monoidal category with terminal monoidal unit is trivially teleological, setting the dualisable morphisms to be all isomorphisms.
+  ~\begin{enumerate}[(1)]
+  \item Any compact closed category is a teleological category, where every morphism is dualisable and the unit morphisms have been forgotten.
+  \item Any symmetric monoidal category with terminal monoidal unit is trivially teleological, setting the dualisable morphisms to be all isomorphisms.
+  \end{enumerate}
 \end{example}
@@
 
-Together we have $\Tele$, the subcategory of $\SymmMonCat$ given by teleological categories and teleological functors. There are evident functors 
+Together we have $\Tele$, the category of teleological categories and teleological functors. There are evident functors 
 \begin{align*}
@@
                                 &= [j\fput [\id_S,x !_S] \fput (i \times A), \pi_2] && \\
-                                &= [j\fput [\id_S, x !_S] \pi_1 (i \times A), \pi_2] && \text{(by $\fput\fput$)}\\ %  \todo{todo: detail}
+                                &= [j\fput [\id_S, x !_S] \pi_1 (i \times A), \pi_2] && \text{(by $\fput\fput$)}\\   
                                 &= [jij \pi_1 (i \times A), \pi_2] && \\
@@
 
-Lenses that satisfy the first two laws correspond to pairs $\rep{l}{r}$ such that $rl = \id_S$ and $\pi_2lr = \pi_2$.
+Lenses that satisfy only the two laws correspond to pairs $\rep{l}{r}$ such that $rl = \id_S$ and $\pi_2lr = \pi_2$.
 This condition seems unavoidably tied to the product structure on $\C$; there is no obvious way generalise this to other optics variants.
@@
 \begin{definition}
-The category $\Traversal$ of traversals is the category of lawful optics for the action of $\Traversable$ on $\Set$ given by evaluation. (Yes, the names $\Traversal$/$\Traversable$ are confusing!)
+The category $\Traversal$ of traversals is the category of optics for the action of $\Traversable$ on $\Set$ given by evaluation. (Yes, the names $\Traversal$/$\Traversable$ are confusing!)
 \end{definition}
@@
 \begin{minted}{haskell}
-l : forall p. Strong p => p a a -> p s s}
+l :: forall p. Strong p => p a a -> p s s
 \end{minted}
@@
 \end{minted}
-What allows such a description to work for these optic variants is that the Tambara module that characterises them, $\Pastro_\M E_A$, can be written in the form \mintinline{haskell}{a -> f a} with \mintinline{haskell}{f} an instance of the corresponding typeclass.
-Specifically, these are the optics that admit a coalgebraic description; the ones for which the evaluation-at-$A$ functor has a right adjoint.
-
-No expressive power is lost by restricting an optic to operate only on functions of shape \mintinline{haskell}{a -> f a}, as the entire concrete description of the optic can be extracted from its value on that particular Tambara module.
+What allows such a description to work for these optic variants is that the Tambara module that characterises them, $\Pastro_\M E_A$, can be written in the form $\C(-, \mintinline{haskell}{f}=)$ for some \mintinline{haskell}{f} that is an instance of the corresponding typeclass.
+This is possible in particular for the optic variants that admit a coalgebraic description; the ones for which the evaluation-at-$A$ functor has a right adjoint.
+
+No expressive power is lost by defining an optic to operate only on functions of the shape \mintinline{haskell}{a -> f a'}, as the entire concrete description of the optic can be extracted from its value on that particular Tambara module.
 The same is not true for other optic variants, and indeed in the Haskell \lenslib{} library, \mintinline{haskell}{Prism}s and \mintinline{haskell}{Review}s use the profunctor encoding.
@@
 \begin{theorem}
-The data of a c-lens $S \hto A$ corresponds to a functor \[ S \to \int \Cat ((- / A), S) \] where $(-/A)$ denotes the slice category and $\int$ denotes (confusingly!) the Grothendieck construction.
+The data of a c-lens $S \hto A$ corresponds to a functor \[ S \to \int [(- / A), S] \] where $(-/A)$ denotes the slice category and $\int$ denotes (confusingly!) the Grothendieck construction.
 

### 2018-09-02 optics.tex
Add abstract

@@
 
+\begin{abstract}
+Bidirectional data accessors such as lenses, prisms and traversals are all instances of the same general `optic' construction.
+We give a careful account of this construction and show that it extends to a functor from the category of symmetric monoidal categories to itself.
+We also show that this construction enjoys a universal property: it freely adds counit morphisms to a symmetric monoidal category.
+Missing in the folklore is a general definition of `lawfulness' that applies directly to any optic category.
+We provide such a definition and show that it is equivalent to the folklore profunctor optic laws.
+\end{abstract}
+
 \setcounter{tocdepth}{1}
@@
 Each optic variant has a concrete description as a certain collection of maps, with attendant laws under which we consider them well-behaved, similar to the pair $(\fget, \fput)$ above and the lens laws.
-We begin in Section~\ref{sec:optics} by defining the \emph{category of optics} in a sufficiently general way to encompass almost all the optic variants in use in the wild, using lenses as a running example.
-The category of lenses is precisely the result of this construction when applied to a category with finite products.
+We begin in Section~\ref{sec:optics} by defining the \emph{category of optics} for a symmetric monoidal category in a sufficiently general way to encompass almost all the optic variants in use in the wild, using lenses as a running example.
+The category of lenses is precisely the result of this construction when applied to a symmetric monoidal category where the tensor is given by binary product.
 Section~\ref{sec:lawful-optics} defines the equivalent of the lens laws for a general category of optics.
@@
 %  \end{align*}
-There are now several things to check.
+It remains to show that $K$ so defined is indeed a strict teleological functor. There are several things to check:
 \begin{itemize}

### 2018-09-03 optics.tex
Edits

@@
 %\usepackage{geometry}
-\usepackage[frozencache]{minted}
+\usepackage{minted}
 \usepackage{cite}
@@
   \begin{align*}
-    \id_{A, A'} \circ \rep{l}{r}
+    \id_{A, A'} \circ \rep{l}{r} \\
     &= \rep{\lambda^{-1}_A}{\lambda_{A'}} \circ \rep{l}{r} \\
@@
 
-\begin{remark}
+\begin{proposition}
 If $\C$ is a category with finite products, then $\Lens \defeq \Optic_\C$ is the category of lenses described in the introduction, so long as we restrict to optics of shape $(S, S) \hto (A, A)$. 
+\end{proposition}
+\begin{proof}
 We see that optics correspond to pairs of $\fget$ and $\fput$ functions via the following isomorphisms:
@@
 (Of course, there is only one sensible way to compose such a collection of morphisms!)
-\end{remark}
+\end{proof}
 
@@
   \end{align*}
-  where $\phi_{M,A} : FM \otimes FA \to F(M \otimes A)$ denotes the structure map of the monoidal functor. Graphically:
+  where $\phi_{M,A} : FM \otimes FA \to F(M \otimes A)$ and $\phi_I : I \to FI$ denote the structure maps of the monoidal functor. Graphically:
   \begin{center}
@@
   \begin{align*}
-  \Optic(F)(\id_{(S, S')})
-  &= \Optic(F)(\rep{\lambda^{-1}_S}{\lambda_{S'}}) \\
-  &= \rep{\phi^{-1}_{I,S} (F\lambda^{-1}_S)}{(F\lambda_{S'}) \phi_{I,S'}} \\
-  &= \rep{(\phi^{-1} \otimes S) \phi^{-1}_{I,S} (F\lambda^{-1}_S)}{(F\lambda_{S'}) \phi_{I,S'}(\phi \otimes S) } \\
-  &= \rep{(\phi^{-1} \otimes S) \phi^{-1}_{I,S} (F\lambda^{-1}_S)}{(F\lambda_{S'}) \phi_{I,S'}(\phi \otimes S) } \\
-  &= \rep{\lambda^{-1}_{FS}}{\lambda_{FS'}} \\
+  &\Optic(F)(\id_{(S, S')}) \\
+  &= \Optic(F)(\rep{\lambda^{-1}_S}{\lambda_{S'}}) &&\text{(Definition of $\id$)} \\
+  &= \rep{\phi^{-1}_{I,S} (F\lambda^{-1}_S)}{(F\lambda_{S'}) \phi_{I,S'}} && \text{(Definition of $\Optic(F)$)} \\
+  &= \rep{(\phi_I^{-1} \otimes S) \phi^{-1}_{I,S} (F\lambda^{-1}_S)}{(F\lambda_{S'}) \phi_{I,S'}(\phi_I \otimes S) } && \text{(Introducing isomorphism to both sides)} \\
+  &= \rep{\lambda^{-1}_{FS}}{\lambda_{FS'}} &&\text{($F$ is a monoidal functor)} \\
   &= \id_{(FS, FS')}
@@
   And given two optics $\rep{l}{r} : (S, S') \hto (A, A')$ and $\rep{l'}{r'} : (R, R') \hto (S, S')$ with residuals $M$ and $M'$, it preserves composition:
+\begingroup
+\allowdisplaybreaks
 \begin{align*}
 &\Optic(F)(\rep{l}{r} \circ \rep{l'}{r'})  \\
+&\qquad \text{(Definition of $\circ$)} \\
 &= \Optic(F)(\rep{(M' \otimes l)l'}{r'(M' \otimes r)}) \\
+&\qquad \text{(Definition of $\Optic(F)$)} \\
 &= \rep{\phi^{-1}_{M' \otimes M,A} F((M' \otimes l)l')}{F(r'(M' \otimes r)) \phi_{M' \otimes M,A'}} \\
+&\qquad \text{(Functoriality of $F$)} \\
 &= \rep{\phi^{-1}_{M' \otimes M,A} F(M' \otimes l)(Fl')}{(Fr') F(M' \otimes r) \phi_{M' \otimes M,A'}} \\
+&\qquad \text{(Introducing isomorphism to both sides)} \\
 &= \rep{(\phi^{-1}_{M', M} \otimes A)\phi^{-1}_{M' \otimes M,A} F(M' \otimes l)(Fl')}{(Fr') F(M' \otimes r) \phi_{M' \otimes M,A'}(\phi_{M', M} \otimes A)} \\
+&\qquad \text{(Hexagon axiom for $F$)} \\
 &= \rep{(FM' \otimes \phi^{-1}_{M,A})\phi^{-1}_{M',M \otimes A}(F(M' \otimes l)) (Fl')}{(Fr') (F(M' \otimes r)) \phi_{M',M \otimes A'}  (FM' \otimes \phi_{M,A'})} \\
+&\qquad \text{(Naturality of $\phi$)} \\
 &= \rep{(FM' \otimes \phi^{-1}_{M,A})(FM' \otimes Fl)\phi^{-1}_{M',S} (Fl')}{(Fr') \phi_{M',S'} (FM' \otimes Fr) (FM' \otimes \phi_{M,A'})} \\
+&\qquad \text{(Functoriality of $\otimes$)} \\
 &= \rep{(FM' \otimes \phi^{-1}_{M,A} (Fl))(\phi^{-1}_{M',S} (Fl'))}{((Fr') \phi_{M',S'})(FM' \otimes (Fr) \phi_{M,A'})} \\
+&\qquad \text{(Definition of $\circ$)} \\
 &= \rep{\phi^{-1}_{M,A} (Fl)}{(Fr) \phi_{M,A'}} \circ \rep{\phi^{-1}_{M',S} (Fl')}{(Fr') \phi_{M',S'}} \\
+&\qquad \text{(Definition of $\Optic(F)$)} \\
 &= \Optic(F)(\rep{l}{r}) \circ \Optic(F)(\rep{l'}{r'})
 \end{align*}
+\endgroup
 The critical move is adding the isomorphism $(\phi_{M', M} \otimes A)$ to both sides of the coend, so that the hexagon axiom for $F$ may be applied.
@@
   \begin{align*}
-    \Optic(F)(\iota(f, g))
+    & \Optic(F)(\iota(f, g)) \\
+    &\qquad \text{(Definition of $iota$)} \\    
     &= \Optic(F)(\rep{\lambda_A^{-1} f}{g \lambda_{A'}}) \\
+    &\qquad \text{(Definition of $\Optic(F)$)} \\    
     &= \rep{\phi^{-1}_{I,A} (F(\lambda_A^{-1} f))}{(F(g \lambda_{A'})) \phi_{I,A'}} \\
+    &\qquad \text{(Functoriality of $F$)} \\    
     &= \rep{\phi^{-1}_{I,A} (F\lambda_A^{-1}) (Ff)}{(Fg)(F \lambda_{A'}) \phi_{I,A'}} \\
+    &\qquad \text{(Introducing $\phi_I$ to both sides)} \\    
     &= \rep{(\phi^{-1}_I \otimes FA) \phi^{-1}_{I,A} (F\lambda_A^{-1}) (Ff)}{(Fg)(F \lambda_{A'}) \phi_{I,A'} (\phi_I \otimes FA)} \\
+    &\qquad \text{($F$ is a monoidal functor)} \\    
     &= \rep{\lambda_{FA}^{-1} (Ff)}{(Fg)\lambda_{FA'}} \\
+    &\qquad \text{(Definition of $\iota$)} \\    
     &= \iota(Ff, Fg)
@@
 \end{align*}
-The monoidality axioms follow by lifting the axioms for $F$. Naturality follows by Proposition~\ref{prop:iota-naturality}.
+The monoidality axioms follow by lifting the axioms for $F$ and naturality follows by Proposition~\ref{prop:iota-naturality}.
 \end{proof}
@@
   If $\C$ is a strict symmetric monoidal category then $\Optic_\C$ is strict, and $\iota : \C \times \C^\op \to \Optic_\C$ is a strict monoidal functor.
-For $F$ a strict monoidal functor, the induced $\Optic(F)$ is also strict.
+For $F : \C \to \D$ a strict monoidal functor, the induced functor $\Optic(F) : \Optic_\C \to \Optic_\D$ is also strict.
 \end{proposition}
@@
   \begin{align*}
-    \Optic(F)(\varepsilon_{(S, S')})
-    &= \Optic(F)(c_{S \otimes S'}) \\
-    &= \Optic(F)(\rep{\rho_S^{-1}}{\rho_{S'}}) \\
-    &= \rep{\phi^{-1}_{S,I} (F \rho_S^{-1})}{(F \rho_{S'}) \phi_{S',I}} \\
-    &= \rep{(FS \otimes \phi_I^{-1}) \phi^{-1}_{S,I} (F \rho_S^{-1})}{(F \rho_{S'}) \phi_{S',I} (FS \otimes \phi_I)} \\
-    &= \rep{\rho_{FS}^{-1}}{\rho_{FS'}} \\
-    &= \varepsilon_{(FS, FS')}
+    &\Optic(F)(\varepsilon_{(S, S')})  \\
+    &= \Optic(F)(c_{S \otimes S'}) && \text{(Definition of the counit)} \\
+    &= \Optic(F)(\rep{\rho_S^{-1}}{\rho_{S'}}) && \text{(Definition of the $c$)} \\
+    &= \rep{\phi^{-1}_{S,I} (F \rho_S^{-1})}{(F \rho_{S'}) \phi_{S',I}}&& \text{(Definition of the $\Optic(F)$)} \\ 
+    &= \rep{(FS \otimes \phi_I^{-1}) \phi^{-1}_{S,I} (F \rho_S^{-1})}{(F \rho_{S'}) \phi_{S',I} (FS \otimes \phi_I)} && \text{(Introduce $\phi_I$ to both sides)} \\
+    &= \rep{\rho_{FS}^{-1}}{\rho_{FS'}} && \text{($F$ is monoidal)} \\
+    &= \varepsilon_{(FS, FS')} && \text{(Definition of the counit)}
   \end{align*}
@@
 
-We will establish the universal property in the somewhat contrived case of \emph{strict} symmetric monoidal categories and \emph{strict} monoidal functors, but anticipate that this result could be weakened to non-strict symmetric monoidal categories at the cost of checking vastly more coherences.
+We will establish the universal property in the somewhat contrived case of \emph{strict} symmetric monoidal categories and \emph{strict} monoidal functors, but anticipate that this result could be weakened to non-strict symmetric monoidal categories at the cost of checking far more coherences.
 
@@
       &= K((A, I) \switched \varepsilon_{(M, I)} \switched (I, A')) K(j(s_{M,A}l) \switched {j(rs_{A', M})}^*) \\
-      &= (K(A, I) \teletimes K\varepsilon_{(M, I)} \teletimes K(I, A')) (K(j(s_{M,A}l)) \teletimes K( {j(rs_{A', M})}^*) \\
-      &= (FA \teletimes \varepsilon_{FM} \teletimes {(FA')}^*) (K(j(s_{M,A}l)) \teletimes K( {j(rs_{A', M})}^*) \\
+      &\qquad\text{($K$ is monoidal)} \\
+      &= (K(A, I) \teletimes K\varepsilon_{(M, I)} \teletimes K(I, A')) (K(j(s_{M,A}l)) \teletimes K( {j(rs_{A', M})}^*)) \\
+      &\qquad\text{($K$ preserves the counit and duality)} \\
+      &= (K(A, I) \teletimes \varepsilon_{K(M,I)} \teletimes K(I, A')) (K(j(s_{M,A}l)) \teletimes K( {j(rs_{A', M})})^*) \\
+      &\qquad\text{($K$ satisfies $Kj = F$)} \\
       &= (FA \teletimes \varepsilon_{FM} \teletimes {(FA')}^*) (F(s_{M,A}l) \teletimes F(rs_{A', M})^*)
   \end{align*}
-  by functoriality, monoidality, and preservation of duals and counits.
   We therefore take \[  K\rep{l}{r} = (FA \teletimes \varepsilon_{FM} \teletimes {(FA')}^*) (F(s_{M,A}l) \teletimes F(rs_{A', M})^*)) \] as our definition of $K$.
@@
 \begin{proof}
-  We begin by giving $\Twoptic_\times(S, A)$ the same treatment as $\Optic_\times(S, A)$. Using Yoneda reduction and the universal property of the product as we did for lenses themselves, we have:
+  We begin by giving $\Twoptic_\times(S, A)$ the same treatment as $\Optic_\times(S, A)$. Using the universal property of the product and Yoneda reduction twice each, we have:
   \begin{align*}
@@
 \begin{align*}
-\outside(\rep{l}{r}) &= r l = \id_S \\
+\outside(\rep{l}{r}) &= l;r = \id_S \\
 \twice(\rep{l}{r})
-&= \repthree{l}{lr}{r} \\
+&= \repthree{l}{r;l}{r} \\
 &= \repthree{l}{\id_{MA}}{r} \\

### 2018-09-03 optics.tex
Put in a dot for the action everywhere

@@
 An \emph{action of $\M$ on $\C$} is a monoidal functor $a : \M \to [\C, \C]$.
-For two objects $M \in \M$ and $A \in \C$, the action $a(M)(A)$ is abbreviated $M \act A$ or $MA$.
-The tensor product in $\M$ will also be written as juxtaposition, so $(NM)A \cong N(MA)$.% An action is \emph{lax} if $a$ is instead a lax monoidal functor.
+For two objects $M \in \M$ and $A \in \C$, the action $a(M)(A)$ is abbreviated $M \act A$.
 \end{definition}
@@
 \begin{align*}
-  \Optic_\M((S, S'), (A, A')) := \int^{M \in \M} \C(S, MA) \times \C(MA', S')
+  \Optic_\M((S, S'), (A, A')) := \int^{M \in \M} \C(S, M \act A) \times \C(M \act A', S')
 \end{align*}
@@
   \phi &: F(I A) \to (F^\bullet I)(FA) \\
-  \phi_{M,A} &: F(MA) \to (F^\bullet M)(F A)
+  \phi_{M,A} &: F(M \act A) \to (F^\bullet M) \act (F A)
   \end{align*}
@@
 \begin{align*}
-\rep{l;\phi A}{r} = \rep{l}{\phi A;r}
+\rep{l;(\phi \act A)}{r} = \rep{l}{(\phi \act A);r}
 \end{align*}
@@
 
-Let $\Twoptic_\M(S, A)$ denote the set \[ \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S). \]
+Let $\Twoptic_\M(S, A)$ denote the set \[ \int^{M_1, M_2 \in \M} \C(S, M_1 \act A) \times \C(M_1 \act A, M_2 \act A) \times \C(M_2 \act A, S). \]
 Using the universal property of the coend, we define three maps:
@@
   \outside(\rep{l}{r}) &= l;r \\
-  \once(\rep{l}{r}) &= \repthree{l}{\id_{MA}}{r} \\
+  \once(\rep{l}{r}) &= \repthree{l}{\id_{M\act A}}{r} \\
   \twice(\rep{l}{r}) &= \repthree{l}{r;l}{r}
@@
   \begin{align*}
-    \Phi(\repthree{l}{c}{r}) = (&\pi_2 l, \\
-                                   &\pi_2 c (\pi_1 l \times A), \\
-                                   &r(\pi_1 c (\pi_1 l \times A) \times A))
+    \Phi(\repthree{l}{c}{r}) = (\quad&l;\pi_2, \\
+                                       &(l;\pi_1 \times A);c;\pi_2, \\
+                                       &((l;\pi_1 \times A);c;\pi_1 \times A);r \quad )
   \end{align*}
@@
   \begin{align*}
-    \outside(\rep{[\id_S, \fget]}{\fput}) = \fput [\id_S, \fget]
+    \outside(\rep{[\id_S, \fget]}{\fput}) = [\id_S, \fget];\fput 
   \end{align*}
@@
     \Phi(&&\repthree{[\id_S, \fget]}{\id_{S \times A}}{\fput}) \\
-    &= (&&\pi_2 [\id_S, \fget], \\
-    &&&\pi_2 \id_{S \times A} (\pi_1 [\id_S, \fget] \times A), \\
-    &&& \fput (\pi_1 \id_{S \times A} (\pi_1 [\id_S, \fget] \times A) \times A) \quad) \\
+    &= (&& [\id_S, \fget];\pi_2, \\
+    &&& ( [\id_S, \fget];\pi_1 \times A);\id_{S \times A};\pi_2, \\
+    &&& (( [\id_S, \fget];\pi_1 \times A);\id_{S \times A};\pi_1 \times A) ; \fput \quad) \\
     %
@@
     &&& \pi_2, \\
-    &&& \fput \pi_{1,3} \quad) \\
+    &&& \pi_{1,3} ;\fput \quad) \\
     %%%%
@@
     \Phi(\twice(\rep{[\id_S, \fget]}{\fput})) &=
-    \Phi(&&\repthree{[\id_S, \fget]}{[\id_S, \fget]\fput}{\fput}) \\
-    &= (&&\pi_2 [\id_S, \fget], \\
-    &&&\pi_2 [\id_S, \fget]\fput (\pi_1 [\id_S, \fget] \times A), \\
-    &&& \fput (\pi_1 [\id_S, \fget]\fput (\pi_1 [\id_S, \fget] \times A) \times A) \quad) \\
+    \Phi(&&\repthree{[\id_S, \fget]}{\fput;[\id_S, \fget]}{\fput}) \\
+    &= (&& [\id_S, \fget];\pi_2, \\
+    &&& ([\id_S, \fget];\pi_1  \times A);\fput;[\id_S, \fget];\pi_2, \\
+    &&& (([\id_S, \fget];\pi_1  \times A);\fput;[\id_S, \fget];\pi_1 \times A);\fput \quad) \\
     %
     &= (&&\fget, \\
-    &&& \fget \; \fput (\id_S \times A), \\
-    &&& \fput (\fput (\id_S \times A) \times A) \quad) \\
+    &&& (\id_S \times A);\fput;\fget, \\
+    &&& ((\id_S \times A);\fput  \times A);\fput \quad) \\
     %
     &= (&&\fget, \\
-    &&& \fget \; \fput, \\
-    &&& \fput (\fput \times A) \quad)
+    &&& \fput;\fget, \\
+    &&& (\fput \times A);\fput \quad)
   \end{alignat*}
   \endgroup
-  So checking component-wise, $\Phi(\once(p))$ being equal to $\Phi(\twice(p))$ is exactly equivalent to the $\fput\fget$ and $\fput\fput$ laws holding.
+  So comparing component-wise, $\Phi(\once(p))$ being equal to $\Phi(\twice(p))$ is exactly equivalent to the $\fput\fget$ and $\fput\fput$ laws holding.
 \end{proof}
@@
 &= \repthree{l}{r;l}{r} \\
-&= \repthree{l}{\id_{MA}}{r} \\
+&= \repthree{l}{\id_{M\act A}}{r} \\
 &= \once(\rep{l}{r})
@@
 \begin{corollary}\label{cor:tautological-lawful}
-   For any two objects $A \in \C$ and $M \in \M$, the tautological optic $MA \hto A$ is lawful. \qed
+   For any two objects $A \in \C$ and $M \in \M$, the tautological optic $M \act A \hto A$ is lawful. \qed
 \end{corollary}
@@
 The first law states that $\outside(p) = \id_S$, so if $p$ is lawful we have
-\[  \id_S = \outside(\rep{\rho_S^{-1}}{f \rho_S}) =  f \rho_S\rho_S^{-1} = f \]
+\[  \id_S = \outside(\rep{\rho_S^{-1}}{\rho_S;f}) =  \rho_S^{-1};\rho_S;f = f \]
 On the other hand, if $f  = \id_S$ then $\rep{\rho_S^{-1}}{\rho_S}$ is lawful because its components are mutual inverses.
@@
   Suppose we have two lawful optics $\rep{l}{r} : R \hto S$ and $\rep{l'}{r'} : S \hto A$ with residuals $M$ and $N$ respectively.
-We must show that $\rep{(Ml')l}{r (Mr')}$ is also a lawful optic.
+We must show that $\rep{l;(M\act l')}{(M\act r');r}$ is also a lawful optic.
 Showing the first law is straightforward:
   \begin{align*}
-    \outside(\rep{l; (Ml')}{(Mr') ; r})
-    &= l ; Ml' ; Mr' ; r \\
-    &= l ; M(l'r') ; r \\
-    &= l ; M\id_{NA} ; r \\
+    \outside(\rep{l; (M\act l')}{(M\act r') ; r})
+    &= l ; (M \act l') ; (M \act r') ; r \\
+    &= l ; (M \act l'r') ; r \\
+    &= l ; (M \act \id_{NA}) ; r \\
     &= l ; r \\
@@
   For the second law, we must show that
-  \[ \repthree{ l;(Ml')}{(Mr'); r;l;(Ml')}{(Mr') ; r} = \repthree{l;(Ml')}{\id_{MNA}}{(Mr') ; r}. \]
+  \[ \repthree{ l;(M\act l')}{(M\act r'); r;l;(M\act l')}{(M\act r') ; r} = \repthree{l;(M\act l')}{\id_{MNA}}{(M\act r') ; r}. \]
   The idea is that, by the lawfulness of $\rep{l}{r}$ and $\rep{l'}{r'}$, there are chains of coend relations that prove
@@
   \end{align*}
-  The result is achieved by splicing these chains of relations together appropriately.
-
-  So consider one of the generating relations $\repthree{l;\phi_S}{c}{r} = \repthree{l}{\phi_S ; c}{r}$ in $\Twoptic_\M(R, S)$. By the naturality of $\phi_A$, we calculate:
-  \begin{align*}
-    \repthree{l;\phi_S;(Ml')}{(Mr'); c ;(Ml')}{(Mr') ; r}
-    &= \repthree{l;(Ml');\phi_{NA}}{(Mr'); c ;(Ml')}{(Mr') ; r} && \text{(functoriality)} \\
-    &= \repthree{l;(Ml')}{\phi_{NA};(Mr'); c ;(Ml')}{(Mr') ; r} && \text{(coend relation)} \\
-    &= \repthree{l;(Ml')}{(Mr');\phi_{S}; c ;(Ml')}{(Mr') ; r} && \text{(functoriality)}
+  The result is achieved by splicing these chains of relations together in the following way.
+
+  Consider one of the generating relations $\repthree{l;(\phi \act S)}{c}{r} = \repthree{l}{(\phi \act S) ; c}{r}$ in $\Twoptic_\M(R, S)$. By the naturality of $\phi_A$, we calculate:
+  \begin{align*}
+    \repthree{l;(\phi \act S);(M \act l')}{(M\act r'); c ;(M\act l')}{(M\act r') ; r}
+    &= \repthree{l;(M \act l');(\phi \act NA)}{(M \act r'); c ;(M \act l')}{(M \act r') ; r} && \text{(functoriality)} \\
+    &= \repthree{l;(M \act l')}{\phi_{NA};(M \act r'); c ;(M \act l')}{(M \act r') ; r} && \text{(coend relation)} \\
+    &= \repthree{l;(M \act l')}{(M \act r');\phi_{S}; c ;(M \act l')}{(M \act r') ; r} && \text{(functoriality)}
   \end{align*}
@@
 
-  So indeed by replicating the same chain of relations that proves $\repthree{l}{r;l}{r} =\repthree{l}{\id_{MS}}{r}$, we see
-  \begin{align*}
-    \repthree{l;(Ml')}{(Mr');r;l;(Ml')}{(Mr') ; r} 
-    &= \repthree{l;(Ml')}{(Mr');\id_{MS};(Ml')}{(Mr') ; r} \\
-    &= \repthree{l;(Ml')}{M(r';l')}{(Mr') ; r}.
+  So indeed by replicating the same chain of relations that proves $\repthree{l}{r;l}{r} =\repthree{l}{\id_{M \act S}}{r}$, we see
+  \begin{align*}
+    \repthree{l;(M \act l')}{(M \act r');r;l;(M \act l')}{(M \act r') ; r} 
+    &= \repthree{l;(M \act l')}{(M \act r');\id_{M \act S};(M \act l')}{(M \act r') ; r} \\
+    &= \repthree{l;(M \act l')}{(M \act r';l')}{(M \act r') ; r}.
   \end{align*}
@@
   \begin{align*}
-    \repthree{l;M(l';\psi_A)}{Mc'}{(Mr') ; r}
-    &= \repthree{l;Ml';M\psi_A}{Mc'}{(Mr') ; r} \\
-    &= \repthree{l;Ml'}{M\psi_A ; Mc'}{(Mr') ; r} \\
-    &= \repthree{l;Ml'}{M(\psi_A;c')}{(Mr') ; r}
-  \end{align*}
-  And similarly for the generating relation on the other side. So again we can replicate the chain of relations proving $\repthree{l'}{r';l'}{r'} = \repthree{l'}{\id_{MA}}{r'}$ to show that
-  \begin{align*}
-    \repthree{l;(Ml')}{M(r';l')}{(Mr') ; r} 
-    &= \repthree{l;(Ml')}{M(\id_{NA})}{(Mr') ; r} \\
-    &= \repthree{l;(Ml')}{\id_{MNA}}{(Mr') ; r}
+    \repthree{l;(M \act l';\psi_A)}{M \act c'}{(M \act r') ; r}
+    &= \repthree{l;(M\act l');(M \act \psi \act A}{M \act c'}{(M \act r') ; r} \\
+    &= \repthree{l;(M \act l')}{(M \act \psi \act A) ; (M \act c')}{(M\act r') ; r} \\
+    &= \repthree{l;(M \act l')}{M \act ((\psi \act A);c')}{(M \act r') ; r}
+  \end{align*}
+  And similarly for the generating relation on the other side. So again we can replicate the chain of relations proving $\repthree{l'}{r';l'}{r'} = \repthree{l'}{\id_{M\act A}}{r'}$ to show that
+  \begin{align*}
+    \repthree{l;(M \act l')}{(M \act r';l')}{(M \act r') ; r} 
+    &= \repthree{l;(M \act l')}{M(\id_{N\act A})}{(M \act r') ; r} \\
+    &= \repthree{l;(M \act l')}{\id_{M \act N \act A}}{(M \act r') ; r}
   \end{align*}
@@
   \end{align*}
-  where $\phi_{M,A'} : (F^\bullet M)(FA) \to F(MA)$ is the structure map that commutes $F$ with the actions.
-
-  For the second equation, consider a generating relation $\repthree{l;\psi A}{c}{r} = \repthree{l}{\psi A ; c}{r}$. We can use the naturality of $\phi$ to show
-  \begin{align*}
-  \repthree{F(l;\psi A);\phi^{-1}_{M,A}}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr}
-  &= \repthree{Fl;F(\psi A);\phi^{-1}_{M,A}}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
-  &= \repthree{Fl;\phi^{-1}_{M',A};(F^\bullet \psi) A}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
-  &= \repthree{Fl;\phi^{-1}_{M',A}}{(F^\bullet \psi) A;\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
-  &= \repthree{Fl;\phi^{-1}_{M',A}}{\phi_{M',A};F(\psi A);Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
-  &= \repthree{Fl;\phi^{-1}_{M',A}}{\phi_{M',A};F(\psi A;c);\phi^{-1}_{N,A}}{\phi_{N,A};Fr}
+  where $\phi_{M,A'} : (F^\bullet M) \act (FA) \to F(M \act A)$ is the structure map that commutes $F$ with the actions.
+
+  For the second equation, consider a generating relation $\repthree{l;(\psi \act A)}{c}{r} = \repthree{l}{(\psi \act A) ; c}{r}$. We can use the naturality of $\phi$ to show
+  \begin{align*}
+  \repthree{F(l;\psi \act A);\phi^{-1}_{M,A}}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr}
+  &= \repthree{Fl;F(\psi \act A);\phi^{-1}_{M,A}}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
+  &= \repthree{Fl;\phi^{-1}_{M',A};(F^\bullet \psi) \act A}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
+  &= \repthree{Fl;\phi^{-1}_{M',A}}{(F^\bullet \psi) \act A;\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
+  &= \repthree{Fl;\phi^{-1}_{M',A}}{\phi_{M',A};F(\psi \act A);Fc;\phi^{-1}_{N,A}}{\phi_{N,A};Fr} \\
+  &= \repthree{Fl;\phi^{-1}_{M',A}}{\phi_{M',A};F(\psi \act A;c);\phi^{-1}_{N,A}}{\phi_{N,A};Fr}
   \end{align*}
@@
   \begin{align*}
-    \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};F(\psi_A;r)}
-    &= \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};F(c;\psi A);\phi^{-1}_{N,A}}{\phi_{N,A};Fr}
+    \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};Fc;\phi^{-1}_{N,A}}{\phi_{N,A};F((\psi \act A);r)}
+    &= \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};F(c;(\psi \act A));\phi^{-1}_{N,A}}{\phi_{N,A};Fr}
   \end{align*}
@@
   &= \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};F(r;l);\phi^{-1}_{M,A}}{\phi_{M,A};Fr}  \\
-  &= \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};F(\id_{MA});\phi^{-1}_{M,A}}{\phi_{M,A};Fr}  \\
-  &= \repthree{Fl;\phi^{-1}_{M,A}}{\id_{(F^\bullet M)(FA)}}{\phi_{M,A};Fr}  \\
+  &= \repthree{Fl;\phi^{-1}_{M,A}}{\phi_{M,A};F(\id_{M \act A});\phi^{-1}_{M,A}}{\phi_{M,A};Fr}  \\
+  &= \repthree{Fl;\phi^{-1}_{M,A}}{\id_{(F^\bullet M) \act (FA)}}{\phi_{M,A};Fr}  \\
   &= \once(\Optic(F)(\rep{l}{r}))
@@
 \begin{proposition}
-  Let $\rep{l}{r} : S \hto A$ be an optic. If $l;r = \id_S$ and $r;l = \phi A$ for some $\phi : M \to M$ in $\M$, then $\rep{l}{r}$ is lawful.
+  Let $\rep{l}{r} : S \hto A$ be an optic. If $l;r = \id_S$ and $r;l = \phi \act A$ for some $\phi : M \to M$ in $\M$, then $\rep{l}{r}$ is lawful.
 \end{proposition}
@@
     &= \repthree{l}{r;l}{r} \\
-    &= \repthree{l}{\phi A}{r} && \text{($r;l = \phi A$)}\\
-    &= \repthree{l ; (\phi A)}{\id_{MA}}{r} && \text{(coend relation)} \\
-    &= \repthree{l;r;l}{\id_{MA}}{r} && \text{($r;l = \phi A$ again)}\\
-    &= \repthree{l}{\id_{MA}}{r}  && \text{($l;r = \id_S$)}\\
+    &= \repthree{l}{\phi \act A}{r} && \text{($r;l = \phi \act A$)}\\
+    &= \repthree{l ; (\phi \act A)}{\id_{M\act A}}{r} && \text{(coend relation)} \\
+    &= \repthree{l;r;l}{\id_{M\act A}}{r} && \text{($r;l = \phi \act A$ again)}\\
+    &= \repthree{l}{\id_{M\act A}}{r}  && \text{($l;r = \id_S$)}\\
     &= \once(\rep{l}{r})
@@
 Even if $r;l = \phi A$ for some $\phi$, the same is not necessarily true for other representatives of the same optic.
-Let $\inside : \Optic_\M(S, A) \to \int^{M \in \M} \C(M A, M A)$ be the map induced by $\inside(\rep{l}{r}) = \langle r ; l \rangle$.
-We might ask that instead of requiring $r;l = \phi A$ exactly, we have $\langle r ; l \rangle = \langle \phi A \rangle$ in $\int^{M \in \M} \C(M A, M A)$.
+Let $\inside : \Optic_\M(S, A) \to \int^{M \in \M} \C(M \act  A, M \act  A)$ be the map induced by $\inside(\rep{l}{r}) = \langle r ; l \rangle$.
+We might ask that instead of requiring $r;l = \phi A$ exactly, we have $\langle r ; l \rangle = \langle \phi A \rangle$ in $\int^{M \in \M} \C(M \act  A, M \act  A)$.
 In fact, this is equivalent:
@@
 \begin{proof}
-  The generating relation for $\int^{M \in \M} \C(M A, M A)$ is
+  The generating relation for $\int^{M \in \M} \C(M \act  A, M \act  A)$ is
   \[ \langle f; \phi_A \rangle = \langle \phi_A; f \rangle \]
-  whenever $f : N A \to M A$ and $\phi : M \to N$.
-This relation $f; \phi_A \rightsquigarrow \phi_A; f$ is not likely to be symmetric or transitive in general.
-Note that if $f; \phi_A \rightsquigarrow \phi_A; f$ then $f ;\phi_A ;f; \phi_A \rightsquigarrow \phi_A ;f ;\phi_A; f$.
+  whenever $f : N \act A \to M \act A$ and $\phi : M \to N$.
+This relation $f; (\phi \act A) \rightsquigarrow (\phi \act A); f$ is not likely to be symmetric or transitive in general.
+Note that if $f; (\phi \act A) \rightsquigarrow (\phi \act A); f$ then $f ;(\phi \act A) ;f; (\phi \act A) \rightsquigarrow (\phi \act A) ;f ;(\phi \act A); f$.
 More generally, if $f \rightsquigarrow g$ then $f^n \rightsquigarrow g^n$ for any $n$.
 
-  Now let $\rep{l}{r}$ be a representative for $p$, so $l;r = \id_S$ and $\langle r;l \rangle = \langle \psi A\rangle$.
-There therefore exists a finite chain of relations $r;l = u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n = \psi A$.
-Suppose the first relation faces rightward, so there exists a $k$ and $\phi$ with $r;l = \phi_A;k$ and $u_2 = k;\phi_A$.
-Define $l' = l;\phi_A$ and $r' = k;r$.
+  Now let $\rep{l}{r}$ be a representative for $p$, so $l;r = \id_S$ and $\langle r;l \rangle = \langle \psi \act A\rangle$.
+There therefore exists a finite chain of relations $r;l = u_1 \leftrightsquigarrow \dots \leftrightsquigarrow u_n = \psi \act A$.
+Suppose the first relation faces rightward, so there exists a $k$ and $\phi$ with $r;l = (\phi \act A);k$ and $u_2 = k;(\phi \act A)$.
+Define $l' = l;(\phi \act A)$ and $r' = k;r$.
 Then:
@@
 \rep{l'}{r'}
-&= \rep{l ; \phi_A}{k ; r} \\
-&= \rep{l}{\phi_A ; k ; r} \\
+&= \rep{l ; (\phi \act A)}{k ; r} \\
+&= \rep{l}{(\phi \act A) ; k ; r} \\
 &= \rep{l}{r ; l; r} \\
@@
 \begin{align*}
-l';r' &= l;\phi_A;k;r = l;r;l;r = \id_S \\
-r';l' &= k;r;l;\phi_A = k;\phi_A;k;\phi_A = u_2^2
+l';r' &= l;(\phi \act A);k;r = l;r;l;r = \id_S \\
+r';l' &= k;r;l;(\phi \act A) = k;(\phi \act A);k;(\phi \act A) = u_2^2
 \end{align*}
@@
 
-  We can now inductively apply the above argument to the shorter chain \[l'r' = u_1^2 \leftrightsquigarrow \dots \leftrightsquigarrow u_n^2 \leftrightsquigarrow {(\psi A)}^2 = \psi^2 A,\] obtained by squaring each morphism in the original chain, until we are left with a representative $\rep{l^*}{r^*}$ such that $r^*;l^* = \psi^N_A$, for some $N>0$.
+  We can now inductively apply the above argument to the shorter chain \[l'r' = u_1^2 \leftrightsquigarrow \dots \leftrightsquigarrow u_n^2 \leftrightsquigarrow {(\psi \act A)}^2 = \psi^2 \act A,\] obtained by squaring each morphism in the original chain, until we are left with a representative $\rep{l^*}{r^*}$ such that $r^*;l^* = \psi^N \act A$, for some $N>0$.
 This pair $\rep{l^*}{r^*}$ is the required representative.
@@
 
-Ideally, we then also find a simplified description $\conctwice(S, A)$ for the set \[ \int^{M_1, M_2 \in \M} \C(S, M_1 A) \times \C(M_1 A, M_2 A) \times \C(M_2 A, S)\] appearing in the definition of a lawful optic.
+Ideally, we then also find a simplified description $\conctwice(S, A)$ for the set \[ \int^{M_1, M_2 \in \M} \C(S, M_1 \act A) \times \C(M_1 \act A, M_2 \act A) \times \C(M_2 \act A, S)\] appearing in the definition of a lawful optic.
 We can then ``read off'' what conditions on are needed on a concrete optic to ensure that the corresponding element of $\Optic_\M(S, A)$ is lawful.
@@
   \begin{align*}
-    \Optic_1((S, S'), (A, A')) &= \int^{M \in 1} \C(S, MA) \times \C(MA', S') \\
+    \Optic_1((S, S'), (A, A')) &= \int^{M \in 1} \C(S, M \act A) \times \C(M \act A', S') \\
                                &\cong \C(S, \star \act A) \times \C(\star \act A', S') \\
@@
     \begin{aligned}[t]
-    \varepsilon_{S} &: (R_A S) \cdot A \to S \\
+    \varepsilon_{S} &: (R_A S) \act A \to S \\
     \varepsilon_{S} &:= \overleftarrow{\id_{R_{A} S}}
@@
 
-If $\C$ is copowered over $\Set$ then $-A : [\C, \C] \to \C$ has a left adjoint given by $S \mapsto \C(A, -) \cdot S$.
+If $\C$ is copowered over $\Set$ then $-A : [\C, \C] \to \C$ has a left adjoint given by $S \mapsto \C(A, -) \bullet S$, where $\bullet$ denotes the copower.
 \end{proposition}
@@
 &\cong \int_X \Set(\C(A, X), \C(S, FX)) \\
-&\cong \int_X \C(\C(A, X) \cdot S, FX) \\
-&\cong [\C, \C](\C(A, -) \cdot S, F)
+&\cong \int_X \C(\C(A, X) \bullet S, FX) \\
+&\cong [\C, \C](\C(A, -) \bullet S, F)
 \end{align*}
@@
   \Setter_\C((S, S'), (A, A')) &= \int^{F \in [\C, \C]} \C(S, FA) \times \C(FA', S') \\
-                               &\cong \int^{F \in [\C, \C]} [\C, \C](\C(A, -) \cdot S, F) \times \C(FA', S') \\
-                               &\cong \C(\C(A, A') \cdot S, S') \\
+                               &\cong \int^{F \in [\C, \C]} [\C, \C](\C(A, -) \bullet S, F) \times \C(FA', S') \\
+                               &\cong \C(\C(A, A') \bullet S, S') \\
                                &\cong \Set(\C(A, A'), \C(S, S'))
@@
 In the Haskell \lenslib{} library, the map $\C(A, A) \to \C(S,S)$ corresponding to a setter is called $\fover$: we think of a setter as allowing us to apply a morphism $A \to A$ over some parts of $S$.
-Tracing through the isomorphisms, the optic corresponding to $\fover$ is $\rep{l}{r}$ where $l : S \to \C(A, A) \cdot S$ is the inclusion with the identity morphism $\id_A$ and $r : \C(A, A') \cdot S \to S'$ is the transpose of $\fover$ along the adjunction defining the copower.
+Tracing through the isomorphisms, the optic corresponding to $\fover$ is $\rep{l}{r}$ where $l : S \to \C(A, A) \bullet S$ is the inclusion with the identity morphism $\id_A$ and $r : \C(A, A') \bullet S \to S'$ is the transpose of $\fover$ along the adjunction defining the copower.
 
@@
 
-\item \emph{Grates}~\cite{GratesPost} are optics for the contravariant action of a monoidal closed category $\C$ on itself by $X \cdot A \mapsto \homC(X, A)$.
+\item \emph{Grates}~\cite{GratesPost} are optics for the contravariant action of a monoidal closed category $\C$ on itself by $X \act A \mapsto \homC(X, A)$.
 Concretely these correspond to morphisms \[ \C(\homC(\homC(S, A), A'), S').
@@
   \begin{align*}
-    \zeta_{A,B,M} : P(A,B) \to P(MA, MB)
+    \zeta_{A,B,M} : P(A,B) \to P(M \act A, M\act B)
   \end{align*}
@@
     \begin{tikzcd}
-      P(A,B) \ar[r, "\zeta_{A,B,M}"] \ar[d, "\zeta_{A, B, NM}" swap] & P(MA, MB) \ar[d, "\zeta_{MA, MB, N}" right] \\
-      P((NM)A), (NM)B) \ar[r, "\alpha_{N, M, A}" swap] & P(N(MA), N(MB))
+      P(A,B) \ar[r, "\zeta_{A,B,M}"] \ar[d, "\zeta_{A, B, N\otimes M}" swap] & P(M \act A, M \act B) \ar[d, "\zeta_{M \act A, M \act B, N}" right] \\
+      P((N\otimes M) \act A), (N\otimes M) \act B) \ar[r, "\alpha_{N, M, A}" swap] & P(N\act (M\act A), N\act (M \act B))
     \end{tikzcd}
@@
     \begin{tikzcd}
-      P(A,B) \ar[r, "\zeta_{A,B,I}"] \ar[dr, equal] & P(IA, IB) \ar[d, "{P(\lambda_A^{-1}, \lambda_B)}" right] \\
+      P(A,B) \ar[r, "\zeta_{A,B,I}"] \ar[dr, equal] & P(I\act A, I\act B) \ar[d, "{P(\lambda_A^{-1}, \lambda_B)}" right] \\
       & P(A, B)
@@
 
-Note that the identity profunctor $I$ has a canonical Tambara module structure $\zeta_{A, B, M} : \C(A, B) \to \C(MA, MB)$ for any $\M$ given by functoriality.
+Note that the identity profunctor $I$ has a canonical Tambara module structure $\zeta_{A, B, M} : \C(A, B) \to \C(M \act A, M \act B)$ for any $\M$ given by functoriality.
 
@@
   &P(A,C) \times Q(C,B)  \\
-  \xrightarrow{\zeta_{A,C,M} \times \xi_{C,B,M}} \quad& P(MA, MC) \times Q(MC, MB) \\
-  \xrightarrow{\copr_{MC}} \quad&\int^{C \in \C} P(MA, C) \times Q(C, MB) \\
-  = \quad&(P \odot Q)(MA, MB)
+  \xrightarrow{\zeta_{A,C,M} \times \xi_{C,B,M}} \quad& P(M\act A, M\act C) \times Q(M\act C, M\act B) \\
+  \xrightarrow{\copr_{M\act C}} \quad&\int^{C \in \C} P(M\act A, C) \times Q(C, M\act B) \\
+  = \quad&(P \odot Q)(M\act A, M\act B)
 \end{align*}
@@
     \begin{tikzcd}
-      P(A,B) \ar[r, "\zeta_{A,B,M}"] \ar[d, "l_{A,B}" left] & P(MA, MB) \ar[d, "l_{MA, MB}" right] \\
-      Q(A,B) \ar[r, "\xi_{A,B,M}" swap] & Q(MA, MB)
+      P(A,B) \ar[r, "\zeta_{A,B,M}"] \ar[d, "l_{A,B}" left] & P(M\act A, M\act B) \ar[d, "l_{M\act A, M\act B}" right] \\
+      Q(A,B) \ar[r, "\xi_{A,B,M}" swap] & Q(M \act A, M \act B)
     \end{tikzcd}
@@
   \begin{align*}
-    \Pastro_\M(P) := \int^{M \in \M}  \C(-, M{=}) \odot P \odot \C(M-, {=})
+    \Pastro_\M(P) := \int^{M \in \M}  \C(-, M\act {=}) \odot P \odot \C(M\act -, {=})
   \end{align*}
@@
   \begin{align*}
-    \Pastro_\M(P)(A,B) := \int^{M \in \M} \int^{C,D \in \C} \C(A, MC) \times P(C,D) \times  \C(MD, B)
-  \end{align*}
-  The module structure $\zeta_{A,B,M} : \Pastro_\M P(A,B) \to \Pastro_\M P (MA, MB)
+    \Pastro_\M(P)(A,B) := \int^{M \in \M} \int^{C,D \in \C} \C(A, M\act C) \times P(C,D) \times  \C(M \act D, B)
+  \end{align*}
+  The module structure $\zeta_{A,B,M} : \Pastro_\M P(A,B) \to \Pastro_\M P (M\act A, M\act B)
   $ is induced by the maps
   \begin{align*}
-    &\C(A, NC) \times P(C,D) \times  \C(ND, B) \\
-    \xrightarrow{\text{functoriality}} \quad& \C(MA, MNC) \times P(C,D) \times  \C(MND, MB) \\
-    \xrightarrow{\copr_{MN}} \quad&\int^{N \in \M} \int^{C,D \in \C} \C(MA, NC) \times P(C,D) \times  \C(ND, MB) \\
-    = \quad&\Pastro_\M P (MA, MB)
-  \end{align*}
-  for all $C, D \in \C$ and $N \in \M$. Equationally, this is $\zeta_{A,B,M}(\repthree{l}{p}{r} ) = \repthree{Ml}{p}{Mr} $.
+    &\C(A, N\act C) \times P(C,D) \times  \C(N\act D, B) \\
+    \xrightarrow{\text{functoriality}} \quad& \C(M\act A, M\act N\act C) \times P(C,D) \times  \C(M\act N\act D, M\act B) \\
+    \xrightarrow{\copr_{M\otimes N}} \quad&\int^{N \in \M} \int^{C,D \in \C} \C(M\act A, N\act C) \times P(C,D) \times  \C(N\act D, M\act B) \\
+    = \quad&\Pastro_\M P (M \act A, M \act B)
+  \end{align*}
+  for all $C, D \in \C$ and $N \in \M$. Equationally, this is $\zeta_{A,B,M}(\repthree{l}{p}{r} ) = \repthree{M\act l}{p}{M\act r} $.
 \end{definition}
@@
     \hat{f}\zeta_{A,B,N}(\repthree{l}{p}{r})
-    &= \hat{f}(\repthree{Nl}{p}{Nr}) && \text{(definition of $\zeta$)}\\
-    &= T(Nl, Nr) \; \xi_{A, B, NM} \; f(p) && \text{(definition of $\hat{f}$)}\\
-    &= T(Nl, Nr) \xi_{MA,MB,N} \; \xi_{A, B, M} \; f(p) && \text{($\xi$ commutes with tensor in $\M$)} \\
+    &= \hat{f}(\repthree{N\act l}{p}{N\act r}) && \text{(definition of $\zeta$)}\\
+    &= T(N\act l, N\act r) \; \xi_{A, B, N \otimes M} \; f(p) && \text{(definition of $\hat{f}$)}\\
+    &= T(N\act l, N\act r) \xi_{M\act A,M\act B,N} \; \xi_{A, B, M} \; f(p) && \text{($\xi$ commutes with tensor in $\M$)} \\
     &= \xi_{A,B,N} T(l, r) \; \xi_{A, B, M} \; f(p) && \text{(naturality of $\xi$)} \\
@@
 \Pastro_\M E_{A, A'} (X, Y)
-&= \int^{M \in \M} \int^{C,D \in \C} \C(X, MC) \times E_{A, A'}(C,D) \times  \C(MD, Y) \\
-&= \int^{M \in \M} \int^{C,D \in \C} \C(X, MC) \times \C(C, A) \times \C(A', D) \times \C(MD, Y) \\
-&\cong \int^{M \in \M} \C(X, MA) \times \C(MA', Y)
+&= \int^{M \in \M} \int^{C,D \in \C} \C(X, M\act C) \times E_{A, A'}(C,D) \times  \C(M\act D, Y) \\
+&= \int^{M \in \M} \int^{C,D \in \C} \C(X, M\act C) \times \C(C, A) \times \C(A', D) \times \C(M\act D, Y) \\
+&\cong \int^{M \in \M} \C(X, M\act A) \times \C(M\act A', Y)
 \end{align*}
@@
   This is the content of the first two isomorphisms above.
-Explicitly, suppose $p = \rep{l}{r}$ with $l : S \to MA$ and $r : MA' \to S'$.
+Explicitly, suppose $p = \rep{l}{r}$ with $l : S \to M\act A$ and $r : M\act A' \to S'$.
 Then for any Tambara module $P$, the component of $\tilde{p}$ at $P$ is
@@
 t_{X, Y} : \Pastro_\M E_{S, S'}(X, Y) \to \Pastro_\M E_{A, A'}(X, Y) \\
-t_{X, Y}(\rep{f}{g}) = \rep{(Ml)f}{g(Mr)}
+t_{X, Y}(\rep{f}{g}) = \rep{(M\act l)f}{g(M\act r)}
 \end{align*}
@@
   \Delta_{X, Y} : (\Pastro_\M E_A)(X, Y) &\to (\Pastro_\M E_A \odot \Pastro_\M E_A)(X, Y) \\
-  \Delta(\rep{l}{r}) &= \repthree{l}{\id_{MA}}{r} \\
+  \Delta(\rep{l}{r}) &= \repthree{l}{\id_{M\act A}}{r} \\
   \varepsilon_{X, Y} : (\Pastro_\M E_A)(X, Y) &\to \C(X, Y) \\
@@
   \begin{align*}
-  \repthree{(Nl)f}{\id_{NMA}}{g(N r)} = \repthree{(Nl)f}{(N r)(Nl)}{g(N r)}
+  \repthree{(N\act l)f}{\id_{N\act M\act A}}{g(N \act r)} = \repthree{(N\act l)f}{(N\act r)(N\act l)}{g(N\act r)}
   \end{align*}

### 2018-09-06 optics.tex
Typoes/fixes

@@
 \usepackage{minted}
+%\usepackage[finalizecache]{minted}
+%\usepackage[frozencache]{minted}
 \usepackage{cite}
@@
 \affil{Wesleyan University \\ \texttt{mvriley@wesleyan.edu}}
+\date{\vspace{-5ex}}
 \begin{document}
@@
 
-In the Haskell \lenslib{} library, optics are written in a form known as the \emph{profunctor encoding}, which at first glance is completely different to that given in Section~\ref{sec:optics}.
+When implementing optics, library authors often use a form known as the \emph{profunctor encoding}, which at first glance is completely different to that given in Section~\ref{sec:optics}.
 As this was being written, Milewski~\cite{ProfunctorOpticsPost} and Boisseau and Gibbons~\cite{YouNeeda} independently described the isomorphism between optics and their profunctor encoding.
@@
 The $\fget$ function is thought of as mapping observations on the state of play to choices of what move to make.
-The $\fput$ function computes the utility of the moves that the players make.
+The $\fput$ function computes the utility of the moves that the players choose.
 There is interest in generalising this to a probabilistic setting, but it is not yet clear what the right replacement for concrete lenses is.
@@
 Much of what is known about optics is folklore, and careful verification of some of their categorical properties has been lacking, especially when working in categories other than $\Set$ (or $\Set$-like categories such as $\mathbf{Hask}$).
-The aim of the present paper is to fill this gap, with the hope that a better understanding of the general structure of these categories will make it easier to generalise to new and exotic settings.
+The aim of the present paper is to fill this gap, with the hope that a better understanding of the general structure of these categories will make it easier to generalise optics to new and exotic settings.
 This is particularly important with the advent of linear types in Haskell, enabling a new branch of the lens family tree, and also with the new applications to game theory.
@@
 
-\begin{lemma}[Mute coends]
+\begin{lemma}[Mute coends]\label{lem:mute-coend}
 Consider a functor $F : \C \to \E$ as a functor $\C^\op \times \C \to \E$ that ignores its contravariant argument. Then \[ \int^{C \in \C} F(C) \cong \colim F. \] \qed
@@
 There it was used for a completely different purpose---to investigate the relationship between Tambara modules and the `center' of a monoidal category.
-Our definition is identical, other than flipping the direction of the morphisms to match the existing work on lenses, and restricting our attention to the unenriched setting.
+Our definition is almost identical, the only differences being that we have flipped the direction of the morphisms to match the existing work on lenses and restricted our attention to the unenriched setting.
 
@@
 \begin{proof}
-  In~\cite[Section 6]{Doubles} this is proven abstractly, by exhibiting this category as the Kleisli category for a monad in the bicategory $\Prof$. We prefer a direct proof.
-
-  We check associativity of composition equationally.  Suppose we have representatives of three optics
+  In~\cite[Section 6]{Doubles} this is proven abstractly by exhibiting this category as the Kleisli category for a monad in the bicategory $\Prof$. We prefer a direct proof.
+
+  Suppose we have representatives of three optics
 \begin{align*}
@@
   \begin{align*}
-    \id_{A, A'} \circ \rep{l}{r} \\
+    \id_{A, A'} \circ \rep{l}{r}
     &= \rep{\lambda^{-1}_A}{\lambda_{A'}} \circ \rep{l}{r} \\
@@
   \end{align*}
-  In both cases we have used the naturality of $\lambda$ followed by the coend relation to move $\lambda^{-1}_M$ to the right-hand side, where it may be cancelled with $\lambda_M$.
+  In both cases we have used the coend relation to cancel an isomorphism appearing on both sides of an optic.
 \end{proof}
@@
   Note that the homsets of $\Optic_\C$ are given by a coend indexed by a possibly large category.
-If $\C$ is small then the coends always exist, but if not, their existence is not guaranteed by the cocompleteness of $\Set$.
-In this case we should be careful to only discuss optic categories where we know that the coends exist by some other means, e.g., by exhibiting an isomorphism of $\Optic_\C((S, S'), (A, A'))$ with a set.
+If $\C$ is small then these coends always exist, but if $\C$ is not small their existence is not guaranteed by the cocompleteness of $\Set$.
+Because of this we should be careful to only discuss optic categories where we know that the coends exist by some other means, e.g., by exhibiting an isomorphism of $\Optic_\C((S, S'), (A, A'))$ with a set.
 For all of the examples we give later we provide such a isomorphism.
@@
 \begin{proposition}
-If $\C$ is a category with finite products, then $\Lens \defeq \Optic_\C$ is the category of lenses described in the introduction, so long as we restrict to optics of shape $(S, S) \hto (A, A)$. 
+If $\C$ is a category with finite products, then $\Lens \defeq \Optic_\C$ is the category of lenses described in the introduction (so long as we restrict to optics of shape $(S, S) \hto (A, A)$). 
 \end{proposition}
@@
 
-We leave it to the reader to verify that composition in $\Lens$ corresponds to ordinary composition of concrete lenses using this isomorphism in both directions.
+We leave it to the reader to verify that composition in $\Lens$ corresponds to ordinary composition of concrete lenses by using this isomorphism in both directions.
 (Of course, there is only one sensible way to compose such a collection of morphisms!)
@@
 \begin{proposition}\label{prop:iota-functor}
-  There is a functor $\iota : \C \times \C^\op \to \Optic_\C$, which on objects is given by $\iota(S, S') = (S, S')$ and on a morphism $(f, g) : (S, S') \to (A, A')$ by $\iota(f, g) = \rep{\lambda_A^{-1} f}{g \lambda_{A'}}$.
+  There is a functor $\iota : \C \times \C^\op \to \Optic_\C$, which on objects is given by $\iota(S, S') = (S, S')$ and on morphisms $(f, g) : (S, S') \to (A, A')$ by $\iota(f, g) = \rep{\lambda_A^{-1} f}{g \lambda_{A'}}$.
 \end{proposition}
@@
   as $I$ is terminal.
-The interior of this coend is mute in the contravariant position, so the coend is equal to the colimit of the functor $\C(I, - \otimes A) : \C \to \Set$.
-But $\C$ has terminal object $I$, so \[\int^{M \in \C} \C(I, M \otimes A) \cong \C(I, I \otimes A) \cong \C(I, A).\]
+The interior of this coend is mute in the contravariant position, so the coend is equal to the colimit of the functor $\C(I, - \otimes A) : \C \to \Set$ by Lemma~\ref{lem:mute-coend}.
+But $\C$ has terminal object $I$, so
+\begin{align*}
+  \int^{M \in \C} \C(I, M \otimes A) 
+  &\cong \colim \C(I, - \otimes A) \\
+  &\cong \C(I, I \otimes A) \\
+  &\cong \C(I, A)
+\end{align*}
 
@@
 \end{proof}
-
-\begin{theorem}
-  $\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit object is $(I, I)$, and the action on a pair of morphisms $\rep{l}{r} : (S, S') \hto (A, A')$ and $\rep{l'}{r'} : (T, T') \hto (B, B')$ is given by:
-  \begin{center}
-    \input{diagrams/tensor-on-morphisms.tikz}
-  \end{center}
-\end{theorem}
-\begin{proof}
-  Suppose the two optics have residuals $M$ and $N$ respectively. Written equationally, their tensor is:
-  \begin{align*}
-    \rep{l}{r} \otimes \rep{l'}{r'} &:= \rep{(M \otimes s_{A,N} \otimes B)(l \otimes l')}{(r \otimes r')(M \otimes s_{A',N} \otimes B')}
-  \end{align*}
-  This does not depend on the choice of representatives, as demonstrated by the equivalence of the following diagrams:
-  \begin{center}
-    \input{diagrams/tensor-on-morphisms-defined-left.tikz}
-    \input{diagrams/tensor-on-morphisms-defined-right.tikz}
-  \end{center}
-  To check functoriality of $\otimes$, suppose we have optics
-  \begin{align*}
-    \rep{l_1}{r_1} : (S_1, S_1') &\hto (S_2, S_2') \\
-    \rep{l_2}{r_2} : (S_2, S_2') &\hto (S_3, S_3') \\
-    \rep{p_1}{q_1} : (T_1, T_1') &\hto (T_2, T_2') \\
-    \rep{p_2}{q_2} : (T_2, T_2') &\hto (T_3, T_3').
-  \end{align*}
-  The string diagram for $(\rep{l_2}{r_2} \circ \rep{l_1}{r_1}) \otimes (\rep{p_2}{q_2} \circ \rep{p_1}{q_1})$ is:
-  \begin{center}
-    \input{diagrams/tensor-functorial-left.tikz}
-  \end{center}
-  And for $(\rep{l_2}{r_2} \otimes \rep{p_2}{q_2}) \circ (\rep{l_1}{r_1} \otimes \rep{p_1}{q_1})$ is:
-  \begin{center}
-    \input{diagrams/tensor-functorial-right.tikz}
-  \end{center}
-  These two diagrams are equivalent: we can use the naturality of the symmetry morphism to push $l_2$ and $r_2$ past the crossing to be next to $l_1$ and $r_1$ respectively.
-This creates two extra twists that can be cancelled in the center of the diagram.
-
-  The structure morphisms are all lifted from the structure morphisms in $\C \times \C^\op$:
-  \begin{align*}
-    \alpha_{(R, R'), (S, S'), (T, T')} &:= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1}) \\
-    \lambda_{(S, S')} &:= \iota(\lambda_{S}, \lambda_{S'}^{-1}) \\
-    \rho_{(S, S')} &:= \iota(\rho_{S}, \rho_{S'}^{-1}) \\
-    s_{(S, S'), (T, T')} &:= \iota(s_{S, T}, s_{T', S'})
-  \end{align*}
-
-  Note that because $\iota(S, S') = (S, S')$, required equations for $\iota$ to be a monoidal functor hold by definition (although we don't yet know that $\Optic_\C$ is monoidal).
-The pentagon and triangle equations then hold in $\Optic_\C$, as they are the image of the same diagrams in $\C \times \C^\op$ under $\iota$.
-The only remaining thing to verify is that these structure maps are natural in $\Optic_\C$, but this follows from the previous proposition.
-\end{proof}
-
-%  In the Haskell \lenslib{} library, the monoidal product on optics is denoted ``\mintinline{haskell}{alongside}'' for the product and ``\mintinline{haskell}{without}'' for the coproduct.
 
@@
 \begin{proposition}\label{prop:change-of-action-monoidal}
-  A monoidal functor $F : \C \to \D$ induces a functor $\Optic(F) : \Optic_\C \to \Optic_\D$, that on objects is $\Optic(F)(S, S') = (FS, FS')$ and on a morphism $\rep{l}{r} : (S, S') \to (A, A')$, is
-  \begin{align*}
-    \Optic(F)(\rep{l}{r}) := \rep{\phi^{-1}_{M,A} (Fl)}{(Fr) \phi_{M,A'}}
+  A monoidal functor $F : \C \to \D$ induces a functor $\Optic(F) : \Optic_\C \to \Optic_\D$, given on objects by $\Optic(F)(S, S') = (FS, FS')$ and on morphisms $\rep{l}{r} : (S, S') \to (A, A')$ by
+  \begin{align*}
+    \Optic(F)(\rep{l}{r}) := \rep{\phi^{-1}_{M,A} (Fl)}{(Fr) \phi_{M,A'}},
   \end{align*}
@@
     & \Optic(F)(\iota(f, g)) \\
-    &\qquad \text{(Definition of $iota$)} \\    
+    &\qquad \text{(Definition of $\iota$)} \\    
     &= \Optic(F)(\rep{\lambda_A^{-1} f}{g \lambda_{A'}}) \\
@@
 \end{proof}
+
+\begin{theorem}
+  $\Optic_\C$ is symmetric monoidal, where $(S, S') \otimes (T, T') = (S \otimes T, S' \otimes T')$, the unit object is $(I, I)$, and the action on a pair of morphisms $\rep{l}{r} : (S, S') \hto (A, A')$ and $\rep{l'}{r'} : (T, T') \hto (B, B')$ is given by:
+  \begin{center}
+    \input{diagrams/tensor-on-morphisms.tikz}
+  \end{center}
+\end{theorem}
+\begin{proof}
+  Suppose the two optics have residuals $M$ and $N$ respectively. Written equationally, their tensor is:
+  \begin{align*}
+    \rep{l}{r} \otimes \rep{l'}{r'} &:= \rep{(M \otimes s_{A,N} \otimes B)(l \otimes l')}{(r \otimes r')(M \otimes s_{A',N} \otimes B')}
+  \end{align*}
+  This does not depend on the choice of representatives, as demonstrated by the equivalence of the following diagrams:
+  \begin{center}
+    \input{diagrams/tensor-on-morphisms-defined-left.tikz}
+    \input{diagrams/tensor-on-morphisms-defined-right.tikz}
+  \end{center}
+  To check functoriality of $\otimes$, suppose we have optics
+  \begin{align*}
+    \rep{l_1}{r_1} : (S_1, S_1') &\hto (S_2, S_2') \\
+    \rep{l_2}{r_2} : (S_2, S_2') &\hto (S_3, S_3') \\
+    \rep{p_1}{q_1} : (T_1, T_1') &\hto (T_2, T_2') \\
+    \rep{p_2}{q_2} : (T_2, T_2') &\hto (T_3, T_3').
+  \end{align*}
+  The string diagram for $(\rep{l_2}{r_2} \circ \rep{l_1}{r_1}) \otimes (\rep{p_2}{q_2} \circ \rep{p_1}{q_1})$ is:
+  \begin{center}
+    \input{diagrams/tensor-functorial-left.tikz}
+  \end{center}
+  And for $(\rep{l_2}{r_2} \otimes \rep{p_2}{q_2}) \circ (\rep{l_1}{r_1} \otimes \rep{p_1}{q_1})$ is:
+  \begin{center}
+    \input{diagrams/tensor-functorial-right.tikz}
+  \end{center}
+  These two diagrams are equivalent: we can use the naturality of the symmetry morphism to push $l_2$ and $r_2$ past the crossing to be next to $p_2$ and $q_2$ respectively.
+This creates two extra twists that can be cancelled in the center of the diagram.
+
+  The structure morphisms are all lifted from the structure morphisms in $\C \times \C^\op$:
+  \begin{align*}
+    \alpha_{(R, R'), (S, S'), (T, T')} &:= \iota(\alpha_{R,S,T}, \alpha_{R',S',T'}^{-1}) \\
+    \lambda_{(S, S')} &:= \iota(\lambda_{S}, \lambda_{S'}^{-1}) \\
+    \rho_{(S, S')} &:= \iota(\rho_{S}, \rho_{S'}^{-1}) \\
+    s_{(S, S'), (T, T')} &:= \iota(s_{S, T}, s_{T', S'})
+  \end{align*}
+
+  Note that because $\iota(S, S') = (S, S')$, the equations required  to hold for $\iota$ to be a monoidal functor hold by definition (although we don't yet know that $\Optic_\C$ is monoidal).
+The pentagon and triangle equations then hold in $\Optic_\C$, as they are the image of the same diagrams in $\C \times \C^\op$ under $\iota$.
+The only remaining thing to verify is that these structure maps are natural in $\Optic_\C$, but this follows from the previous proposition.
+\end{proof}
+
+%  In the Haskell \lenslib{} library, the monoidal product on optics is denoted ``\mintinline{haskell}{alongside}'' for the product and ``\mintinline{haskell}{without}'' for the coproduct.
 
@@
   The structure maps of $\Optic_\C$ are given by $\iota$ applied to the structure maps of $\C$.
-If the latter are identities, then so are the former---the identity morphisms in $\Optic_\C$ are by definition $\iota(\id_S, \id_S')$.
+If the latter are identities, then so are the former---the identity morphisms in $\Optic_\C$ are by definition $\iota(\id_S, \id_{S'})$.
 
@@
 
-It will be convenient to equip $\Optic_\C$ with a slightly different symmetric monoidal structure.
+It will be convenient to equip $\Optic_\C$ with a slightly different symmetric monoidal structure:
 
@@
 \begin{definition}[Compare {\cite[Definition 5.1]{CoherenceForLenses}}]
-  A \emph{teleological category is} a symmetric monoidal category $(\T, \teletimes, I)$, equipped with:
+  A \emph{teleological category} is a symmetric monoidal category $(\T, \teletimes, I)$, equipped with:
   \begin{itemize}
@@
 Note that there is therefore also a canonical isomorphism $\phi : I \cong I^*$
-  \item A symmetric monoidal extranatural family of morphisms $\varepsilon_X : X \teletimes X^* \to I$, called \emph{counits}, natural with respect to the dualisable morphisms.
+  \item A symmetric monoidal extranatural family of morphisms $\varepsilon_X : X \teletimes X^* \to I$, called \emph{counits}, natural with respect to the \emph{dualisable} morphisms.
   \end{itemize}
@@
   \begin{tikzcd}
-    X^* \teletimes X \ar[r, "s"]  \ar[dr, "\varepsilon_{X^*}", swap] & X \teletimes X^* \ar[d, "\varepsilon_X"] \\
-    & I
+    X^* \teletimes X \ar[r, "s"] \ar[d, "\cong" swap]  & X \teletimes X^* \ar[d, "\varepsilon_X"] \\
+   X^* \teletimes {(X^*)}^* \ar[r, "\varepsilon_{X^*}", swap] & I
   \end{tikzcd}\]
@@
   \begin{tikzcd}[column sep = large]
-    X \teletimes Y \teletimes Y^* \teletimes X^* \ar[r, "X \teletimes \varepsilon_Y \teletimes X^*"]  \ar[dr, "\varepsilon_{X \teletimes Y}", swap] & X \teletimes X^* \ar[d, "\varepsilon_X"] \\
-    & I
+    X \teletimes Y \teletimes Y^* \teletimes X^* \ar[r, "X \teletimes \varepsilon_Y \teletimes X^*"] \ar[d, "\cong" swap]  & X \teletimes X^* \ar[d, "\varepsilon_X"] \\
+   X \teletimes Y \teletimes (X \teletimes Y)^* \ar[r, "\varepsilon_{X \teletimes Y}", swap] & I
   \end{tikzcd} \hspace{1cm}
   \begin{tikzcd}
-    I \teletimes I^* \ar[r,"I \teletimes \phi"] \ar[dr, swap, "\varepsilon_I"] & I \ar[d, equal] \\
+    I \teletimes I^* \ar[r,"I \teletimes \phi"] \ar[dr, swap, "\varepsilon_I"] & I \teletimes I \ar[d, "\cong"] \\
     & I
@@
     F(X \teletimes X^*) \ar[r, "\phi_{X, X^*}"]  \ar[d, "F\varepsilon_X", swap] & FX \teletimes F(X^*) \ar[r, "FX \teletimes d_X"] & FX \teletimes (FX)^* \ar[d, "\varepsilon_{FX}"] \\
-    FI \ar[rr, "\phi", swap] & & I
+    FI \ar[rr, "\phi_I", swap] & & I
   \end{tikzcd}
@@
   \item The dualisable morphisms are all morphisms of the form $\iota(f, g)$;
-  \item The involution is given on objects by ${(S, S')}^* := (S', S)$, and on morphisms by \[\iota{(f, g)}^* := \iota(g, f);\]
+  \item The involution is given on objects by ${(S, S')}^* := (S', S)$, and on morphisms by $\iota{(f, g)}^* := \iota(g, f)$;
   \item The counit $\varepsilon_{(S, S')} : (S, S') \switched {(S, S')}^* = (S \otimes S', S \otimes S') \to (I, I)$ is given by the connector: \[\varepsilon_{(S, S')} := c_{S \otimes S'}.\]
@@
 \begin{proof}
-  Morphisms of the form $\iota(f, g)$ constitute a symmetric monoidal subcategory is clear, they are the image of the monoidal functor $\iota$.
+  That morphisms of the form $\iota(f, g)$ constitute a symmetric monoidal subcategory is clear, they are the image of the symmetric monoidal functor $\iota$.
 
@@
 \begin{proposition}
-  The functor $\Optic : \SymmMonCat \to \SymmMonCat$ of Theorem~\ref{thm:optic-functor} has its image in the subcategory $\Tele$.
+  The functor $\Optic : \SymmMonCat \to \SymmMonCat$ of Theorem~\ref{thm:optic-functor} extends to a functor to $\Tele$.
 \end{proposition}
@@
 
-This also holds for monoidal categories that are not necessarily strict, if unit object and unitors are inserted in the appropriate places.
+This also holds for monoidal categories that are not necessarily strict, if the unit object and unitors are inserted in the appropriate places.
 
 \begin{proposition}
-  Suppose $(\C, \otimes, I)$ is a symmetric strict monoidal category and $(\T, \teletimes, I, {(-)}^*, \varepsilon)$ is a strict teleological category.
+  Suppose $(\C, \otimes, I)$ is a strict symmetric monoidal category and $(\T, \teletimes, I, {(-)}^*, \varepsilon)$ is a strict teleological category.
 Given a strict symmetric monoidal functor $F : \C \to \T_d$, there exists a unique strict teleological functor $K : \Optic_\C \to \T$ with the property $Kj = F$.
@@
 \begin{definition}
-Given two categories equipped with monoidal actions $(\M, \C)$ and $(\N, \D)$, a \emph{morphism of actions} is a monoidal functor $F^\bullet : \M \to N$ and a functor $F : \C \to \D$ that commutes with the actions, in the sense that there exist natural isomorphisms
-  \begin{align*}
-  \phi &: F(I A) \to (F^\bullet I)(FA) \\
+Given two categories equipped with monoidal actions $(\M, \C)$ and $(\N, \D)$, a \emph{morphism of actions} is a monoidal functor $F^\bullet : \M \to N$ and a functor $F : \C \to \D$ that commutes with the actions, in the sense that there exists a natural isomorphism
+  \begin{align*}
   \phi_{M,A} &: F(M \act A) \to (F^\bullet M) \act (F A)
@@
 \begin{proposition}\label{prop:change-of-action}
-If $F : (\M, \C) \to (\N, \D)$, is a morphism of actions, there is an induced functor $\Optic(F) : \Optic_\M \to \Optic_\N$. \qed
+If $F : (\M, \C) \to (\N, \D)$ is a morphism of actions, there is an induced functor $\Optic(F) : \Optic_\M \to \Optic_\N$. \qed
 \end{proposition}
@@
 Typically we want our optics to obey certain laws.
-The constant complement perspective suggests declaring an optic $\rep{l}{r}$ to be lawful if $l$ and $r$ are mutual inverses.
+The `constant-complement' perspective suggests declaring an optic $\rep{l}{r}$ to be lawful if $l$ and $r$ are mutual inverses.
 There are a couple of issues with this definition.
@@
 In our primary example of an optic variant, lenses in $\Set$, this does indeed correspond to the concrete lens laws.
-However, this fact relies on some extra structure possessed by $\Set$: the existence of pullbacks, and that all objects other than the empty set have a global element.
-
-In this section we make a different definition of lawful that at first seems strange, but which in the case of lenses corresponds \emph{exactly} to the three concrete lens laws with no additional assumptions on $\C$ required.
+However, this fact relies on some extra structure possessed by $\Set$: the existence of pullbacks, and that all objects (other than the empty set) have a global element.
+
+In this section we make a different definition of lawfulness that at first seems strange, but which in the case of lenses corresponds \emph{exactly} to the three concrete lens laws with no additional assumptions on $\C$ required.
 As further justification for this definition, in Section~\ref{sec:profunctor-optics} we will see an interpretation of (unlawful) optics as maps between certain comonoid objects.
@@
 \begin{proposition}\label{prop:lawful-lens-laws}
-  A concrete lens given by $\fget$ and $\fput$ is lawful (in our sense) iff it obeys the three concrete lens laws.
-\end{proposition}
-\begin{proof}
-  We begin by giving $\Twoptic_\times(S, A)$ the same treatment as $\Optic_\times(S, A)$. Using the universal property of the product and Yoneda reduction twice each, we have:
+  A concrete lens described by $\fget$ and $\fput$ is lawful (in our sense) iff it obeys the three concrete lens laws.
+\end{proposition}
+\begin{proof}
+  We begin by giving $\Twoptic_\times(S, A)$ the same treatment as we did $\Optic_\times(S, A)$. Using the universal property of the product and Yoneda reduction twice each, we have:
   \begin{align*}
@@
   \begin{align*}
-  \repthree{l}{r;l}{r} &= \repthree{l}{\id_{MS}}{r} \\
-  \repthree{l'}{r';l'}{r'} &= \repthree{l'}{\id_{NA}}{r'}
+  \repthree{l}{r;l}{r} &= \repthree{l}{\id_{M \act S}}{r} \\
+  \repthree{l'}{r';l'}{r'} &= \repthree{l'}{\id_{N \act A}}{r'}
   \end{align*}
@@
 
-  Consider one of the generating relations $\repthree{l;(\phi \act S)}{c}{r} = \repthree{l}{(\phi \act S) ; c}{r}$ in $\Twoptic_\M(R, S)$. By the naturality of $\phi_A$, we calculate:
-  \begin{align*}
-    \repthree{l;(\phi \act S);(M \act l')}{(M\act r'); c ;(M\act l')}{(M\act r') ; r}
-    &= \repthree{l;(M \act l');(\phi \act NA)}{(M \act r'); c ;(M \act l')}{(M \act r') ; r} && \text{(functoriality)} \\
-    &= \repthree{l;(M \act l')}{\phi_{NA};(M \act r'); c ;(M \act l')}{(M \act r') ; r} && \text{(coend relation)} \\
-    &= \repthree{l;(M \act l')}{(M \act r');\phi_{S}; c ;(M \act l')}{(M \act r') ; r} && \text{(functoriality)}
-  \end{align*}
-  And similarly for the other generating relation, $\repthree{l}{c;\phi_S}{r} = \repthree{l}{c}{\phi_S; r}$.
+  Consider one of the generating relations $\repthree{l;(\phi \act S)}{c}{r} = \repthree{l}{(\phi \act S) ; c}{r}$ in $\Twoptic_\M(R, S)$, where $\phi : M \to M'$.
+By the functoriality of the action, we calculate:
+  \begin{align*}
+    &\repthree{l;(\phi \act S);(M' \act l')}{(M'\act r'); c ;(M\act l')}{(M\act r') ; r} \\
+    &= \repthree{l;(M \act l');(\phi \act N \act A)}{(M' \act r'); c ;(M \act l')}{(M \act r') ; r} && \text{(functoriality)} \\
+    &= \repthree{l;(M \act l')}{(\phi \act N \act A);(M' \act r'); c ;(M \act l')}{(M \act r') ; r} && \text{(coend relation)} \\
+    &= \repthree{l;(M \act l')}{(M \act r');(\phi \cdot S); c ;(M \act l')}{(M \act r') ; r} && \text{(functoriality)}
+  \end{align*}
+  And similarly for the other generating relation, $\repthree{l}{c;(\phi \act S)}{r} = \repthree{l}{c}{(\phi \act S); r}$.
 
@@
 
-  Now that the $r;l$ in the center has been cleared away, we turn to the chain of relations proving $\repthree{l'}{r';l'}{r'} = \repthree{l'}{\id_{NA}}{r'}$.
-A generating relation $\repthree{l';\psi_A}{c'}{r'} = \repthree{l'}{\psi_A ; c'}{r'}$ in $\Twoptic_\M(S, A)$ implies that
-  \begin{align*}
-    \repthree{l;(M \act l';\psi_A)}{M \act c'}{(M \act r') ; r}
-    &= \repthree{l;(M\act l');(M \act \psi \act A}{M \act c'}{(M \act r') ; r} \\
+  Now that the $r;l$ in the center has been cleared away, we turn to the chain of relations proving $\repthree{l'}{r';l'}{r'} = \repthree{l'}{\id_{N\act A}}{r'}$.
+A generating relation $\repthree{l';(\psi \act A)}{c'}{r'} = \repthree{l'}{(\psi \act A) ; c'}{r'}$ in $\Twoptic_\M(S, A)$ implies that
+  \begin{align*}
+    \repthree{l;(M \act l';\psi \act A)}{M \act c'}{(M \act r') ; r}
+    &= \repthree{l;(M\act l');(M \act \psi \act A)}{M \act c'}{(M \act r') ; r} \\
     &= \repthree{l;(M \act l')}{(M \act \psi \act A) ; (M \act c')}{(M\act r') ; r} \\
@@
 
-Even if $r;l = \phi A$ for some $\phi$, the same is not necessarily true for other representatives of the same optic.
+Even if $r;l = \phi \act A$ for some $\phi$, the same is not necessarily true for other representatives of the same optic.
 Let $\inside : \Optic_\M(S, A) \to \int^{M \in \M} \C(M \act  A, M \act  A)$ be the map induced by $\inside(\rep{l}{r}) = \langle r ; l \rangle$.
-We might ask that instead of requiring $r;l = \phi A$ exactly, we have $\langle r ; l \rangle = \langle \phi A \rangle$ in $\int^{M \in \M} \C(M \act  A, M \act  A)$.
+We might ask that instead of requiring $r;l = \phi \act A$ exactly, we have $\langle r ; l \rangle = \langle \phi \act A \rangle$ in $\int^{M \in \M} \C(M \act  A, M \act  A)$.
 In fact, this is equivalent:
@@
 \begin{proposition}\label{prop:onthenose}
-  Suppose $p : S \hto A$ satisfies $\outside(p) = \id_S$ and $\inside(p) = \langle \phi A \rangle$.
-Then there exists a representative $\rep{l}{r}$ such that $r;l = \psi A$ on the nose for some (possibly different) $\psi : M \to M$.
+  Suppose $p : S \hto A$ satisfies $\outside(p) = \id_S$ and $\inside(p) = \langle \phi \act A \rangle$.
+Then there exists a representative $\rep{l}{r}$ such that $r;l = \psi \act A$ on the nose for some (possibly different) $\psi : M \to M$.
 \end{proposition}
@@
   The generating relation for $\int^{M \in \M} \C(M \act A, M \act  A)$ is
-  \[ \langle f; \phi_A \rangle = \langle \phi_A; f \rangle \]
+  \[ \langle f; (\phi \act A) \rangle = \langle (\phi \act A); f \rangle \]
   whenever $f : N \act A \to M \act A$ and $\phi : M \to N$.
@@
 
-Ideally, we then also find a simplified description $\conctwice(S, A)$ for the set \[ \int^{M_1, M_2 \in \M} \C(S, M_1 \act A) \times \C(M_1 \act A, M_2 \act A) \times \C(M_2 \act A, S)\] appearing in the definition of a lawful optic.
+Ideally, we then also find a simplified description $\conctwice(S, A)$ for the set $\Twoptic_\C(S, A)$.
 We can then ``read off'' what conditions on are needed on a concrete optic to ensure that the corresponding element of $\Optic_\M(S, A)$ is lawful.
@@
 \begin{definition}
-  Suppose $\C$ has finite coproducts. The \emph{category of prisms} is the category of lawful optics with respect to the coproduct $\sqcup$: $\Prism \defeq \Optic_\sqcup$.
+  Suppose $\C$ has finite coproducts. The \emph{category of prisms} is the category of optics with respect to the coproduct $\sqcup$: $\Prism \defeq \Optic_\sqcup$.
 \end{definition}
@@
 \begin{proposition}\label{prop:lawful-prism-laws}
-  If $p : S \hto A$ is a prism then the associated $\fmatching$ and $\freview$ functions satisfy the concrete prism laws. \qed
+  If $p : S \hto A$ is a lawful prism then the associated $\fmatching$ and $\freview$ functions satisfy the concrete prism laws. \qed
 \end{proposition}
@@
 \begin{theorem}\label{thm:optics-are-coalgebras}
-An concrete optic $\funzip : S \to  (R_{A} S) \act A$ is lawful iff it is a coalgebra for the comonad $X \mapsto (R_{A} X) \act A$.
+A concrete optic $\funzip : S \to  (R_{A} S) \act A$ is lawful iff it is a coalgebra for the comonad $X \mapsto (R_{A} X) \act A$.
 \end{theorem}
@@
 So now interpreting the optic laws, we find
-\[\outside(\rep{\funzip}{\varepsilon_{S} }) = \varepsilon_{S} \; \funzip = \id_S \] is exactly the coalgebra unit law, and equality of
+\[\outside(\rep{\funzip}{\varepsilon_{S} }) = \varepsilon_{S} \; \funzip = \id_S \] is exactly the coalgebra counit law, and equality of
   \begin{align*}
@@
   \end{align*}
-is exactly the coalgebra multiplication law.
+is exactly the coalgebra comultiplication law.
 \end{proof}
@@
 \begin{definition}
-  The \emph{category of setters} $\Setter_\C$ is the category of lawful optics for the action of $[\C, \C]$ on $\C$ by evaluation.
+  The \emph{category of setters} $\Setter_\C$ is the category of optics for the action of $[\C, \C]$ on $\C$ by evaluation.
 \end{definition}
@@
 Traversals allow us to traverse through a data structure, accumulating applicative actions as we go.
-We begin by reviewing the defnitions of applicative and traversable functors~\cite{AnInvestigationOfTheLawsOfTraversals}.
+We begin by reviewing the definitions of applicative and traversable functors~\cite{AnInvestigationOfTheLawsOfTraversals}.
 
@@
 
-\begin{remark}
-In~\cite[Section 2.3]{ProfunctorOptics}, it is further claimed that a traversal $S \hto A$ exhibits an isomorphism $S \cong \Sigma_n A^n \times \Set(A^n,S)$.
+%\begin{remark}
+%In~\cite[Section 2.3]{ProfunctorOptics}, it is further claimed that a traversal $S \hto A$ exhibits an isomorphism $S \cong \Sigma_n A^n \times \Set(A^n,S)$.
 This cannot possibly be true---consider the traversable functor $X \times -$.
 The claim appears to be a misreading of~\cite[Proposition 5.4]{SecondOrderFunctionals}.
-\end{remark}
+%\end{remark}
 
@@
 \begin{definition}
-The Kleisli category $\C_T$ of a monad $T$ has the same objects as $\C$, with morphisms $X \to Y$ given by morphisms $X \to TY$.
-Identities are given by the unit of $T$, and the composite of two morphisms $f : X \to Y$ and $g : Y \to Z$ in $\C_T$ is given by
+The Kleisli category $\C_T$ of a monad $T$ has the same objects as $\C$, with morphisms $X \to Y$ in $\C_T$ given by morphisms $X \to TY$ in $\C$.
+Identity morphisms are given by the unit of $T$, and the composite of two morphisms $f : X \to Y$ and $g : Y \to Z$ in $\C_T$ is given by
 \begin{align*}
@@
 %\end{align*}
-\item \emph{Affine Traversals}~\cite{AffineTraversalPost} allow access to a target that may or may not be present.
+\item \emph{Affine Traversals}~\cite{SecondOrderFunctionals} allow access to a target that may or may not be present.
 Suppose $\C$ is cartesian closed and has binary coproducts.
@@
 \end{minted}
-This not the approach taken in the \lenslib{} library!
+This not the approach usually taken in implementations!
 Instead the somewhat indirect \emph{profunctor encoding} is used.
-(This is not quite true, for a few reasons the \lenslib{} library actually uses the closely related \emph{van Laarhoven encoding}, see Section~\ref{sec:van-laarhoven}.
+(This is not quite true for the Haskell \lenslib{} library, for a few reasons \lenslib{} uses the closely related \emph{van Laarhoven encoding}, see Section~\ref{sec:van-laarhoven}.
 The Purescript \texttt{purescript-profunctor-lenses} library~\cite{PurescriptLibrary} does use the profunctor encoding directly.)
@@
 
-Note that the identity profunctor $I$ has a canonical Tambara module structure $\zeta_{A, B, M} : \C(A, B) \to \C(M \act A, M \act B)$ for any $\M$ given by functoriality.
+Note that the identity profunctor $I$ has a canonical Tambara module structure $\zeta_{A, B, M} : \C(A, B) \to \C(M \act A, M \act B)$ for any $\M$, given by functoriality.
 
@@
   For any $P \in \Prof(\C, \C)$, there is a map $\eta : P \hto U \Pastro_\M P$, given by $\eta(p) = \repthree{\id_A}{p}{\id_B}$.
-
-  Suppose we have an element $\repthree{l}{p}{r} \in \Pastro_\M P(A,B)$. Then one can check that this element is equal to
+Suppose we have an element $\repthree{l}{p}{r} \in \Pastro_\M P(A,B)$.
+One can check that this element is equal to
   \begin{align*}
@@
 
-  Now suppose $T \in \Tamb_\M$ is a Tambara module with structure map $\xi$.
-We would like to show that for any map $f : P \hto UT$, there exists a unique $\hat f : \Pastro_\M P \hto T$ so that $f$ factors as \[P \xrightarrow{\eta} U \Pastro_\M P \xrightarrow{U\hat f} UT.
+  If $T \in \Tamb_\M$ is a Tambara module with structure map $\xi$, we would like to show that for any map $f : P \hto UT$ there exists a unique $\hat f : \Pastro_\M P \hto T$ so that $f$ factors as \[P \xrightarrow{\eta} U \Pastro_\M P \xrightarrow{U\hat f} UT.
 \]
@@
   The data of such a map $\hat f : \Pastro_\M P \hto T$ is a natural transformation between the underlying profunctors.
-For the factorisation property to hold, we must have that $\hat{f}\eta(p) = f(p)$ for any $p \in P(A,B)$, but then the action on the remainder of $\Pastro_\M P(A, B)$ is fixed:
+For the factorisation property to hold we must have that $\hat{f}\eta(p) = f(p)$ for any $p \in P(A,B)$, but then the action on the remainder of $\Pastro_\M P(A, B)$ is fixed:
   \begin{align*}
@@
 \end{minted}
+where
+\begin{minted}{haskell}
+data Procompose p q d c where
+  Procompose :: p x c -> q d x -> Procompose p q d c
+\end{minted}
+equipped with appropriate \mintinline{haskell}{Profunctor} and \mintinline{haskell}{Strong} instances denotes profunctor/Tambara module composition.
 
@@
 No expressive power is lost by defining an optic to operate only on functions of the shape \mintinline{haskell}{a -> f a'}, as the entire concrete description of the optic can be extracted from its value on that particular Tambara module.
-The same is not true for other optic variants, and indeed in the Haskell \lenslib{} library, \mintinline{haskell}{Prism}s and \mintinline{haskell}{Review}s use the profunctor encoding.
+The same is not true for other optic variants, and indeed in the Haskell \lenslib{} library, \mintinline{haskell}{Prism}s and \mintinline{haskell}{Review}s take a form much closer to the profunctor encoding.
+(The \lenslib{} library does not use \emph{precisely} the profunctor encoding even here, for backwards compatibility reasons.)
 
@@
 
-One can define generalise the definition of $\Optic$ so that the two halves lie in different categories.
+One can generalise the definition of $\Optic$ so that the two halves lie in different categories.
 Suppose $\C_L$ and $\C_R$ are categories that are acted on by a common monoidal category $\M$.
@@
 \end{definition}
-One can show that $\Optic_{\actL, \actR}$ forms a category. Less clear is what notion of lawfulness is appropriate in this setting.
-
-Examples of mixed optics include the \emph{degenerate optics} of the \lenslib{} library: \mintinline{haskell}{Getter}s \mintinline{haskell}{Review}s and \mintinline{haskell}{Fold}s.
+$\Optic_{\actL, \actR}$ forms a category. It is not so clear what notion of lawfulness is appropriate in this setting.
+
+Examples of mixed optics include the \emph{degenerate optics} of the \lenslib{} library: \mintinline{haskell}{Getter}s, \mintinline{haskell}{Review}s and \mintinline{haskell}{Fold}s.
 The mixed optic formalism also appears able to capture \emph{indexed optics} such as \mintinline{haskell}{IndexedLens}es and \mintinline{haskell}{IndexedTraversal}s~\cite{ProfunctorOpticsPost}.
-The latter, for example, allow access to the index of the elements of a list as it is being traversed.
 
@@
 
-To overcome this, we work in $\Cat$, so that the objects under consideration have internal morphisms that we think of as updates.
-We modify $\fput$ so that instead of accepting an element of $A$ to overwrite the original in $S$ with, it requires a morphism in $A$ of the form $\fget(s) \to a'$.
+To overcome this we work in $\Cat$, so that the objects under consideration have internal morphisms that we think of as updates.
+We modify $\fput$ so that instead of accepting an object $a$ of $A$ to overwrite the original in $S$ with, it requires a morphism in $A$ of the form $\fget(s) \to a$.
 In this way we are restricted in what updates we may perform.
-This intuition is captured in the following definition:
+This is captured in the following definition:
 
@@
 
-Furthermore, a c-lens lawful iff it is a coalgebra for the comonad of the adjunction
+Furthermore, a c-lens is lawful iff it is a coalgebra for the comonad of the adjunction
 \[
 \begin{tikzcd}[column sep = large]
-{[A, \Cat]} \ar[r, bend left, "\int"] \ar[r, phantom, "\bot" pos = 0.4] & \Cat \ar[l, bend left, "{X \mapsto [- \downarrow \id_A, X]}" below]
+{[A^\op, \Cat]} \ar[r, bend left, "\int"] \ar[r, phantom, "\bot" pos = 0.4] & \Cat \ar[l, bend left, "{X \mapsto [(-/A), X]}" below]
 \end{tikzcd}

### 2018-09-07 optics.tex
Couple more

@@
 When implementing optics, library authors often use a form known as the \emph{profunctor encoding}, which at first glance is completely different to that given in Section~\ref{sec:optics}.
-As this was being written, Milewski~\cite{ProfunctorOpticsPost} and Boisseau and Gibbons~\cite{YouNeeda} independently described the isomorphism between optics and their profunctor encoding.
+(The Haskell \lenslib{} library itself actually uses a variant called the \emph{van Laarhoven encoding}, for both historical and efficiency reasons.) As this was being written, Milewski~\cite{ProfunctorOpticsPost} and Boisseau and Gibbons~\cite{YouNeeda} independently described the isomorphism between optics and their profunctor encoding.
 In Section~\ref{sec:profunctor-optics} we review this isomorphism and verify that the folklore profunctor optic laws are equivalent to lawfulness as defined here.
@@
     &= l ; (M \act l'r') ; r \\
-    &= l ; (M \act \id_{NA}) ; r \\
+    &= l ; (M \act \id_{N \act A}) ; r \\
     &= l ; r \\
@@
   For the second law, we must show that
-  \[ \repthree{ l;(M\act l')}{(M\act r'); r;l;(M\act l')}{(M\act r') ; r} = \repthree{l;(M\act l')}{\id_{MNA}}{(M\act r') ; r}. \]
+  \[ \repthree{ l;(M\act l')}{(M\act r'); r;l;(M\act l')}{(M\act r') ; r} = \repthree{l;(M\act l')}{\id_{M \act N \act A}}{(M\act r') ; r}. \]
   The idea is that, by the lawfulness of $\rep{l}{r}$ and $\rep{l'}{r'}$, there are chains of coend relations that prove
@@
 \end{minted}
-equipped with appropriate \mintinline{haskell}{Profunctor} and \mintinline{haskell}{Strong} instances denotes profunctor/Tambara module composition.
+denotes profunctor/Tambara module composition, once equipped with appropriate \mintinline{haskell}{Profunctor} and \mintinline{haskell}{Strong} instances.
 
